### 2019-06-03 paper/iacr.tex
Both versions of paper (MRL and IACR)

\documentclass{article}

\usepackage{enumerate}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{remark}{Remark}[section]
\newtheorem{example}{Example}[section]
\newtheorem{defn}{Definition}[section]
\newtheorem{assu}{Assumption}[section]

\title{Compact linkable ring signatures and applications}
\author[1]{Brandon Goodell}
\author[1]{Sarang Noether}
\author[2]{\texttt{RandomRun}}
\affil[1]{Monero Research Lab, \texttt{\{surae,sarang\}@getmonero.org}}
\affil[2]{Independent researcher}
\date{}

\begin{document}
\maketitle

\begin{abstract}
We describe an efficient linkable ring signature scheme, compact linkable spontaneous anonymous group (CLSAG) signatures, for use in confidential transactions. Compared to the existing signature scheme used in Monero, CLSAG signatures are both smaller and more efficient to generate and verify for ring sizes of interest. We generalize the construction and show how it can be used to produce signatures with coins of different type in the same transaction.
\end{abstract}

\section{Introduction}
Ring signatures are used in Monero to provide transaction signer ambiguity. Originally, a simple Schnorr-like linkable ring signature \cite{liu2004linkable} was used that included previous one-time output public keys as possible signers. Later, the addition of Pedersen commitments to hide amounts necessitated a generalization to the signature \cite{noether2016ring} in order to prove transaction balance without revealing the signer.

The current ring signature construction used in Monero, MLSAG signatures, scale linearly with the number of ring members included in the signature. In particular, they require the inclusion of two scalars per ring member.

We note that the MLSAG signature scheme, while general enough to permit linking across multiple sets of input keys, is in practice used as a hybrid approach to a linkable ring signature. Indeed, each signature input consists of two keys: the first is a standard one-time output public key, and the second is a key computed using the associated Pedersen commitments. Linkability is only used for the first key, to ensure that double-spending does not occur.

This construction is flexible. For example, the format can be used for usual ring confidential transactions or could be modified to describe \textit{colored ring confidential transactions} with multiple so-called coin colors, allowing users to transact with multiple assets simultaneously.

\subsection{Our contribution}

In this work, we introduce a $d$-dimensional linkable ring multisignature ($d$-LRMS) scheme suitable for use in a colored ring confidential transaction scheme with $d$ colors. Our scheme is \textit{compact} in the sense that signature size scales with the sum of ring size and the dimension $d$; that is, increasing $d$ yields the same additional number of signature elements, regardless of the ring size. We prove our scheme is unforgeable up to the hardness of the $k$-one-more discrete logarithm problem.

We call our signature scheme $d$-dimensional compact linkable spontaneous anonymous group ($d$-CLSAG) signatures. We demonstrate how to use this scheme for ring confidential transactions in Monero by replacing multi-layered linkable spontaneous anonymous group (MLSAG) signatures with $d$-CLSAG signatures.  The resulting scheme is more efficient in both signature size and verification time than current Monero transaction structures, and can be seamlessly integrated into the Monero transaction protocol.

\section{Notation}

In this document, we denote algorithms with typefont majuscule English letters like $\texttt{A}$, $\texttt{B}$, or $\texttt{O}$, or typefont names like $\texttt{Setup}$, $\texttt{KeyGen}$, and so on.

Group parameters are denoted as a tuple $(p, \mathbb{G}, d, G)$ where $\mathbb{G}$ is an elliptic curve group with prime order $p$, $d$ is a dimension, and $G$ is a generator of $\mathbb{G}$. We denote integers, bits, indices, and scalars in $\mathbb{Z}/p\mathbb{Z}$ with minuscule English letters $x, y, z, b, c, i, j, k$, etc.\ and we denote group elements with majuscule English letters, $G, X, W$, and so on. We use miniscule Greek letters like $\sigma$ to describe signatures and majuscule calligraphic Latin letters like $\mathfrak{T}$ when describing linkability tags.

We denote column vectors in boldface, e.g.\ $(x_1, \ldots, x_d)^\top = \textbf{x}$, and matrices in underlined boldface, e.g.\ $((x_{1,1}, x_{1,2}, \ldots, x_{1,n}), \ldots, (x_{d,1}, \ldots, x_{d,n})) = (\textbf{x}_1, \textbf{x}_2, \ldots, \textbf{x}_n) = \underline{\textbf{x}}$ is a $d\times n$ matrix. We denote the Hadamard product of two vectors with $\circ$, so for any $\textbf{x} = (x_1, x_2, \ldots, x_d) = (x_i)_{i=1}^{d}$, and for any $\textbf{y} = (y_i)_{i=1}^{d}$, we denote the sequence $(x_i \cdot y_i)_{i=1}^{d}$ with $\textbf{x} \circ \textbf{y}$. We denote bitwise concatenation with the symbol $\mid \mid$.

We distinguish oracles with calligraphic font, e.g.\ $\mathcal{CO}$ denotes a corruption oracle, $\mathcal{SO}$ denotes a signing oracle. If the codomain of a random oracle is the field of scalars $\mathbb{Z}/p\mathbb{Z}$, we denote this $\mathcal{H}^s$ (hash-to-scalar). If the codomain is $\mathbb{G}$, we denote this $\mathcal{H}^p$ (hash-to-point).

\section{Linkable ring multisignatures}

In this section, we recall linkable ring signature (LRS) schemes, we modify the definition to account for $d$-dimensional keys for linkable ring multisignature (LRMS) schemes, and we provide two examples. We emphasize that our description does not present multisignatures as computed between mutually untrusted parties. We use the term to mean a $d$-of-$d$ threshold multisignature with all keys controlled by the same signer; in particular, we have none of the communication steps necessary for computing a multisignature.

\subsection{LRS and LRMS schemes}

\begin{defn}[LRS]\label{def:lrs}
A \textit{linkable ring signature scheme} is a tuple $(\texttt{Setup}, \texttt{KeyGen}, \texttt{Sign}, \texttt{Verify}, \texttt{Link})$ satisfying the following. 
\begin{itemize}
\item $\texttt{Setup}(1^\lambda) \to \textit{par}$. $\texttt{Setup}$ takes as input a security parameter $1^\lambda$, produces some public parameters $\textit{par}$.

\item $\texttt{KeyGen}(1^\lambda, \textit{par}) \to (sk, pk)$. $\texttt{KeyGen}$ takes as input a security parameter $1^\lambda$ and public parameters $\textit{par}$. $\texttt{KeyGen}$ produces as output a private-public keypair $(sk, pk)$.

\item $\texttt{Sign}\left(1^\lambda, \textit{par}, (m, \textbf{pk}, sk)\right) \to \left\{\bot_{\texttt{Sign}}, (\sigma, \mathfrak{T})\right\}$. $\texttt{Sign}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, an arbitrary message $m \in \left\{0,1\right\}^*$, an ad hoc \textit{ring} of public keys $\textbf{pk} = \left\{pk_1, \ldots, pk_n\right\}$, and a secret key $sk$. $\texttt{Sign}$ produces as output either a distinguished failure symbol $\textit{out} = \bot_{\texttt{Sign}}$ or a signature-tag pair $\textit{out} = (\sigma, \mathfrak{T})$.

\item $\texttt{Verify}\left(1^\lambda, \textit{par}, (m, \textbf{pk}, (\sigma, \mathfrak{T}))\right) \to \left\{0,1\right\}$. $\texttt{Verify}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, a message $m$, a ring of public keys $\textbf{pk}$, and a signature-tag pair $(\sigma, \mathfrak{T})$. $\texttt{Verify}$ produces as output a bit $b \in \left\{0,1\right\}$.

\item $\texttt{Link}\left(1^\lambda, \textit{par}, (\sigma, \mathfrak{T}), (\sigma^\prime, \mathfrak{T}^\prime)\right)$. $\texttt{Link}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, and a pair of signature-tag pairs $(\sigma, \mathfrak{T}), (\sigma^\prime, \mathfrak{T}^\prime)$. $\texttt{Link}$ produces as output a bit $b \in \left\{0,1\right\}$. 
\end{itemize}
\end{defn}

We extend this to a scheme with $d$-dimensional keys.

\begin{defn}[$d$-LRMS]
A \textit{$d$-dimensional linkable ring multisignature scheme} is a tuple of algorithms $(\texttt{Setup}, \texttt{KeyGen}, \texttt{Sign}, \texttt{Verify}, \texttt{Link})$ satisfying the following. 
\begin{itemize}
\item $\texttt{Setup}(1^\lambda) \to \textit{par}$. $\texttt{Setup}$ works as described in \ref{def:lrs}.

\item $\texttt{KeyGen}(1^\lambda, \textit{par}) \to (\textbf{sk}, \textbf{pk})$. $\texttt{KeyGen}$ takes as input a security parameter $1^\lambda$ and public parameters $\textit{par}$. $\texttt{KeyGen}$ produces as output a private-public keypair $(\textbf{sk}, \textbf{pk})$ where each key is a $d$-dimensional vector. We refer to the first coordinate of each of these keys as the \textit{linking key} and the $d-1$ remaining coordinates (if there are any) are the \textit{auxiliary keys}.

\item $\texttt{Sign}\left(1^\lambda, \textit{par}, (m, \underline{\textbf{pk}}, \textbf{sk})\right) \to \left\{\bot_{\texttt{Sign}}, (\sigma, \mathfrak{T})\right\}$. $\texttt{Sign}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, a message $m$, a vector of public keys $\underline{\textbf{pk}} = \left\{\textbf{pk}_1, \ldots, \textbf{pk}_n\right\}$ where each $\textbf{pk}_i$ is a $d$-dimensional public key, and a $d$-dimensional secret key $\textbf{sk}$. $\texttt{Sign}$ produces as output either a distinguished failure symbol $\bot_{\texttt{Sign}}$ or a signature-tag pair $(\sigma, \mathfrak{T})$.

\item $\texttt{Verify}\left(1^\lambda, \textit{par}, (m, \underline{\textbf{pk}}, (\sigma, \mathfrak{T}))\right) \rightarrow \left\{0,1\right\}$. $\texttt{Verify}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, a message $m$, a matrix of public keys $\underline{\textbf{pk}}$, and a signature-tag pair $(\sigma, \mathfrak{T})$. $\texttt{Verify}$ produces as output a bit $b \in \left\{0,1\right\}$.

\item  $\texttt{Link}\left(1^\lambda, \textit{par}, (\sigma, \mathfrak{T}), (\sigma^\prime, \mathfrak{T}^\prime)\right)$. $\texttt{Link}$ works as described in \ref{def:lrs}.
\end{itemize}
\end{defn}

We refer to the linkability tag as the \textit{key image} for consistency with terminology in Monero. We also use the following terminology if the scheme satisfies the respective properties.
\begin{description}
\item[Correctly verified:] For any message $m$, $d$-dimensional secret key $\textbf{sk}$ with corresponding public key $\textbf{pk}$, and appropriately-sized matrix $\underline{\textbf{pk}} = \left\{\textbf{pk}_1, \ldots, \textbf{pk}_n\right\}$, if there exists an index $1 \leq \ell \leq n$ such that $\textbf{pk} = \textbf{pk}_\ell$, then $\texttt{Verify}(\texttt{Sign}(m, \underline{\textbf{pk}}, \textbf{sk})) = 1$.

\item[Correctly linkable:] For any messages $m$, $m^\prime$, any $d$-dimensional secret keys  $\textbf{sk}$ and $\textbf{sk}^\prime$ with equal linking keys (that is, with $\textbf{sk}_0 = \textbf{sk}^\prime_0$) and with corresponding public keys $\textbf{pk}$ and $\textbf{pk}^\prime$ respectively, any appropriately-sized pair of matrices $\underline{\textbf{pk}}$ and $\underline{\textbf{pk}}^\prime$, if $(\sigma, \mathfrak{T}) \leftarrow \texttt{Sign}(m, \underline{\textbf{pk}}, \textbf{sk})$ and $(\sigma^\prime, \mathfrak{T}^\prime) \leftarrow \texttt{Sign}(m^\prime, \underline{\textbf{pk}}^\prime, \textbf{sk}^\prime)$ and there exists a pair of indices $\ell$ and $\ell^\prime$ such that $\underline{\textbf{pk}}_\ell = \textbf{pk}$ and $\underline{\textbf{pk}}_{\ell^\prime} = \textbf{pk}^\prime$, then
$\texttt{Link}((\sigma, \mathfrak{T}), (\sigma^\prime, \mathfrak{T}^\prime))=1$.
\end{description}

Note that linkability is only considered with respect to a single component of a matrix entry. When applied to Monero, this is important since only one such entry corresponds to an output public key for double-spend detection purposes.

%In the sequel, we omit $1^\lambda$ and $\textit{par}$ from the input of algorithms for clarity unless there is risk of confusion.

\subsection{Examples}

\begin{example}\label{ex:lsag}
The LSAG signature scheme from \cite{liu2004linkable} is a $1$-LRMS. In this example, $\texttt{Setup}$ always deterministically sets $d:=1$ (so we only use the linking key and there are no auxiliary keys). $\texttt{Setup}$ selects some $G \in \mathbb{G}$ to be a group generator for the group parameters $(p, \mathbb{G}, 1, G)$, two cryptographic hash functions $\mathcal{H}^s:\left\{0,1\right\}^* \to \mathbb{Z}/p\mathbb{Z}$ and $\mathcal{H}^p:\left\{0,1\right\}^* \to \mathbb{G}$. $\texttt{Setup}$ outputs $\textit{par} = (p, \mathbb{G}, 1, G, \mathcal{H}^s, \mathcal{H}^p)$.

$\texttt{KeyGen}$ produces as output a private key $x \in \mathbb{Z}/p\mathbb{Z}$ and a public key $X = xG$. $\texttt{Sign}$ takes as input a private key $y \in \mathbb{Z}/p\mathbb{Z}$, a message $m$, and a ring $\textbf{X} = \left\{X_1, \ldots, X_n\right\}$, and produces as output either a distinguished failure symbol $\bot_{\texttt{Sign}}$ or a signature-tag pair $(\sigma, \mathfrak{T})$.

The signature scheme originally described in \cite{liu2004linkable} signs a message $m$ with a ring of keys $\textbf{X} = \left\{X_1, \ldots, X_n\right\}$ and a secret key $x$ corresponding to some $X_\ell$, using the linkability tag (key image) $\mathfrak{T} := x \mathcal{H}^p(\textbf{X})$. Unfortunately, this key image is unsuitable for use in Monero, as changing ring members will change the key image. This would allow the same key to be used twice in two different ring signatures. For use in Monero, we modify this key image to be independent of the non-signing ring members, $\mathfrak{T} := x \mathcal{H}^p(X_\ell)$. This allows these key images to be used for double-spend protection.

An LSAG signature on a message $m$ with ring $\textbf{X}$ using these key images is computed in the following way. First, the signer samples $\alpha, s_{\ell+1}, s_{\ell+2}, \ldots, s_{\ell-1} \in \mathbb{Z}/p\mathbb{Z}$ at random. Next, the signer computes basepoints $H_i = \mathcal{H}^p(X_i)$. Next, the signer computes $c_{\ell+1}  = \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid \alpha G \mid \mid \alpha H_\ell)$ and the signer computes each $c_{i+1} = \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid s_i G + c_i X_i \mid \mid s_i H_i + c_i \mathfrak{T})$ for $i = \ell+1, \ldots, \ell-1$, naturally identifying index $1$ with index $n+1$. The signer finishes by computing $s_\ell = \alpha - c_\ell x_\ell$ and publishing the signature-tag pair $(\sigma, \mathfrak{T})$ where $\sigma = (c_1, s_1, \ldots, s_n)$.

A purported LSAG signature-tag pair on a message $m$ with ring $\textbf{X}$ is verified in the following way. The verifier sets $c_1^\prime = c_1$ and computes $c_{i+1}^\prime = \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid s_i G + c_i^\prime X_i \mid \mid s_i H_i + c_i^\prime \mathfrak{T})$ for $i=1, 2, \ldots, n$. The verifier outputs $1$ when $c_{n+1}^\prime = c_1$ and $0$ otherwise. Note that all verifiers must list the keys in $\textbf{X}$ in an agreed-upon order for the above verification to work; either they should agree upon lexicographic or some other ordering.  LSAG signature-tag pairs are linked merely by comparing key images: two valid signatures with the same key image were signed with the same secret key (and, in the case of Monero, would signal an attempt to double-spend funds).
\end{example}

\begin{remark}
The key image modification in Example \ref{ex:lsag} is due to the basepoint of the key image $\mathfrak{T}$. As noted in \cite{liu2004linkable}, easy variations on key image formats are available. How or whether the security properties of LSAG signatures are retained in practical use given more flexible key image formats, while interesting, is beyond the scope of this work.
\end{remark}

\begin{example}\label{ex:mlsag}
The MLSAG signature scheme from \cite{noether2016ring} is a $2$-LRMS. In this example, $\texttt{Setup}$ always deterministically sets $d := 2$. Public keys are taken to be pairs of group elements $(X, Z) \in \mathbb{G}^2$. $\texttt{Sign}$ takes as input a private key vector $(x,z)$, a message $m$, and a matrix of public keys $\underline{\textbf{pk}} = \left\{\textbf{pk}_1, \ldots, \textbf{pk}_n\right\}$ where each $\textbf{pk}_i = (X_i, Z_i)$, each $X_i$ is the public key of a one-time transaction output, and each $Z_i$ is computed using combinations of Pedersen commitments that depend on the particular transaction type in use. %The commitments that form $Z_i$ can be adversarially selected and are not used in linking, and the secret key for $X_i$ can only be computed by the recipient except with negligible probability.

A signature-tag pair $(\sigma, \mathfrak{T})$ is computed in the following way. Two rows of random signature data are sampled, say  $\alpha, \alpha^\prime, s_{\ell + 1}, s^\prime_{\ell + 1}, s_{\ell + 2}, s^\prime_{\ell + 2}, \ldots, s_{\ell -1}, s^\prime_{\ell - 1}$  and the basepoints $H_i = \mathcal{H}^p(X_i)$ are computed from the signing keys $X_i$ of each ring member $(X_i, Z_i)$. The key image $\mathfrak{T} = x_\ell H_\ell$ is computed. The following  challenges are computed
\begin{align*}
c_{\ell + 1} =& \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid \alpha G \mid \mid \alpha H_\ell \mid \mid \alpha^\prime G^\prime) \\
c_{i+1} =& \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid s_i G + c_i X_i \mid \mid s_i H_i + c_i \mathfrak{T} \mid \mid s_i^\prime G^\prime + c_i Z_i). \end{align*}The values $s_\ell = \alpha - c_\ell x_\ell$ and $s_\ell^\prime = \alpha^\prime - c_\ell z_\ell$ are computed. The signature is set $\sigma := (c_1, s_1, s_1^\prime, \ldots, s_n, s_n^\prime)$ and the signature-tag pair is published $(\sigma, \mathfrak{T})$. Verification proceeds as one would expect, succeeding if $c_{n+1}^\prime = c_1$ after the verifier computes each $H_i$ and each challenge
\begin{align*}
c_{2}^\prime =&  \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid s_1 G + c_1 X_1 \mid \mid s_1 H_1 + c_1 \mathfrak{T} \mid \mid s_1^\prime G^\prime + c_1 Z_1) \\
c_{i+1}^\prime =&  \mathcal{H}^s\left(\textbf{X} \mid \mid m \mid \mid s_i G + c_i^\prime X_i \mid \mid s_i H_i + c_i^\prime \mathfrak{T} \mid \mid s_i^\prime G^\prime + c_i^\prime Z_i \right).
\end{align*} 
Note this scheme is not compact in the sense that doubling key dimension going from $d=2$ in Example \ref{ex:lsag} to $d=2$ results in an asymptotic doubling of signature size. 
\end{example}

\section{A compact d-LRMS scheme}

We present a multisignature variant of LSAG signatures that is more compact than the previous examples. We loosely say that a $d$-LRMS scheme is compact if its signature sizes are not proportional to $d$. We call this scheme $d$-CLSAG to be concise. We show how to apply a $2$-CLSAG for use in ring confidential transactions, and how to apply $d$-CLSAG for colored ring confidential transactions. We make remarks on efficiency for both applications. In particular, we show that our $2$-CLSAG construction is more efficient in both space and verification time than the equivalent MLSAG construction.

\subsection{Implementation}\label{sec:implem}

\begin{defn}[$d$-CLSAG]\label{def:clsag}
The following tuple $(\texttt{Setup}, \texttt{KeyGen}, \texttt{Sign}, \texttt{Verify}, \texttt{Link})$ is a compact $d$-LRMS.

\begin{itemize}
\item $\texttt{Setup}(1^\lambda, d) \to \textit{par}$. $\texttt{Setup}$ takes as input a security parameter $1^\lambda$ and a public dimension $d$. $\texttt{Setup}$ selects a prime $p$, a group $\mathbb{G}$ with prime order $p$, selects a group generator $G \in \mathbb{G}$ uniformly at random, selects $d$ cryptographic hash functions $\mathcal{H}^s_0, \ldots, \mathcal{H}^s_{d-1}$ with codomain $\mathbb{Z}/p\mathbb{Z}$, selects a cryptographic hash function $\mathcal{H}^p$ with codomain $\mathbb{G}$. $\texttt{Setup}$ outputs $\textit{par} = \left( p,\mathbb{G}, d, G, \left\{\mathcal{H}^s_j\right\}_{j=0}^{d-1}, \mathcal{H}^p\right)$.\footnote{Note that domain separation can be used here to take one $\mathcal{H}^s$ and construct each $\mathcal{H}^s_j$ by defining $\mathcal{H}^s_j(x) := \mathcal{H}^s(j \mid\mid x)$.}

\item $\texttt{KeyGen}(1^\lambda, \textit{par}) \to (\textbf{sk}, \textbf{pk})$. $\texttt{KeyGen}$ takes as input the security parameter $1^\lambda$, public parameters $\textit{par}$. $\texttt{KeyGen}$ samples $\textbf{sk} \leftarrow (\mathbb{Z}/p\mathbb{Z})^d$, which we denote $\textbf{sk} = (x, z_1, \ldots, z_{d-1})$, and computes $\textbf{pk} := \textbf{sk} \circ \textbf{G}$ for $\textbf{G} = (G, G, \ldots, G) \in \mathbb{G}^d$. $\texttt{KeyGen}$ outputs $(\textbf{sk}, \textbf{pk})$. We say $x$ is the \textit{linking key} and the remaining keys $\left\{z_j\right\}$ are the \textit{auxiliary keys}.

\item $\texttt{Sign}\left(1^\lambda, \textit{par}, (m, \underline{\textbf{pk}}, \textbf{sk})\right) \to \left\{\bot_{\texttt{Sign}}, (\sigma, \mathfrak{T})\right\}$. $\texttt{Sign}$ takes as input the security parameter $1^\lambda$, public parameters $\textit{par}$, a message $m \in \left\{0,1\right\}^*$, a matrix of public keys $\underline{\textbf{pk}} = (\textbf{pk}_1, \ldots, \textbf{pk}_n)$ where each $\textbf{pk}_i = (X_i, Z_{i,1}, \ldots, Z_{i,d-1}) \in \mathbb{G}^d$, and a secret key vector $\textbf{sk} = (x,z_1, \ldots, z_{d-1}) \in (\mathbb{Z}/p\mathbb{Z})^d$. $\texttt{Sign}$ does the following.

\begin{enumerate}
\item $\texttt{Sign}$ looks for the signing index $\ell$ such that $(x, z_1, \ldots, z_{d-1}) \circ (G, G, \ldots, G) = \textbf{pk}_\ell$. If no such index exists, $\texttt{Sign}$ outputs $\bot_{\texttt{Sign}}$ and terminates.

\item Otherwise, $\texttt{Sign}$ samples $\alpha \in \mathbb{Z}/p\mathbb{Z}$ and $\left\{s_i\right\}_{i \neq \ell} \in (\mathbb{Z}/p\mathbb{Z})^{n-1}$.

\item $\texttt{Sign}$ computes the \textit{aggregation coefficients} $\mu_X$ and $\{\mu_j\}_{j=1}^{d-1}$, the \textit{linkability tag} or \textit{key image} $\mathfrak{T}$, and auxiliary key images $\{\mathfrak{D}_j\}_{j=1}^{d-1}$:
\begin{align*}
\mathfrak{T} \leftarrow& x \mathcal{H}^p(X_\ell) & \mu_X \leftarrow& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}) \\
\{\mathfrak{D}_j\} \leftarrow&  \{z_j \mathcal{H}^p(X_\ell)\} & \mu_j \leftarrow& \mathcal{H}^s_1(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}).
\end{align*}

\item For $i = \ell, \ell+1, \ldots, \ell-1$, identifying index $n$ with index $1$ as usual, $\texttt{Sign}$ computes
\begin{align*}
L_\ell =& \alpha G & L_i =& s_i G + c_i \left(\mu_X X_i + \sum_{j=1}^{d-1} \mu_jZ_{i,j}\right)\\
R_\ell =& \alpha \mathcal{H}^p(X_\ell) & R_i =& s_i \mathcal{H}^p(X_i) + c_i \left(\mu_X \mathfrak{T} + \sum_{j=1}^{d-1} \mu_j \mathfrak{D}_j\right) \\
c_{\ell+1} =& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid m \mid \mid L_\ell \mid \mid R_\ell) & c_{i+1} =& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid m \mid \mid L_i \mid \mid R_i)
\end{align*} and lastly computes $s_\ell = \alpha - c_\ell (\mu_X x_\ell + \sum_{j=1}^{d-1} \mu_jz_{\ell,j})$.

\item $\texttt{Sign}$ sets the signature $\sigma = (c_1, s_1, \ldots, s_n, \{\mathfrak{D}_j\}_{j=1}^{d-1})$ and publishes the signature-tag pair $(\sigma, \mathfrak{T})$.
\end{enumerate}

\item $\texttt{Verify}\left(1^\lambda, \textit{par}, m, \underline{\textbf{pk}}, (\sigma, \mathfrak{T})\right) \to \left\{0,1\right\}$. $\texttt{Verify}$ takes as input the security parameter $1^\lambda$, public parameters $\textit{par}$, a message $m$, a matrix $\underline{\textbf{pk}} = ((X_i, Z_{i,1}, \ldots, Z_{i,d-1}))_{i=1}^{n}$, and a signature-tag pair $(\sigma, \mathfrak{T})$. $\texttt{Verify}$ does the follwoing.

\begin{enumerate}
\item If $n > N$, or any coordinate of any ring member is not in $\mathbb{G}$, or if $\sigma$ cannot be parsed as $(c_1, s_1, \ldots, s_n, \mathfrak{D}_1, \ldots, \mathfrak{D}_{d-1})$ for some $c_1 \in \mathbb{Z}/p\mathbb{Z}$, some $s_i \in \mathbb{Z}/p\mathbb{Z}$, and some $\mathfrak{D}_j \in \mathbb{G}$, or if $\mathfrak{T} \notin \mathbb{G}$, $\texttt{Verify}$ produces $0$ as output and terminates.

\item Otherwise, $\texttt{Verify}$ parses $(c_1, s_1, \ldots, s_n, \{\mathfrak{D}_j\}_{j=1}^{d-1}) \leftarrow \sigma$, computes each $\mathcal{H}^p(X_i)$, and compute the aggregation coefficients as above.

\item $\texttt{Verify}$ sets $c_1^\prime := c_1$ and, for $i=1, 2, \ldots, n-1$, computes the following.
\begin{align*}
L_i :=& s_i G + c_i^\prime \left(\mu_X X_i + \sum_{j=1}^{d-1} \mu_jZ_{i,j}\right) \\ 
R_i :=& s_i \mathcal{H}^p(X_i) + c_i^\prime\left(\mu_X \mathfrak{T} + \sum_{j=1}^{d-1} \mu_j \mathfrak{D}_j\right)\\
c_{i+1}^\prime :=& \mathcal{H}^s_0\left(\underline{\textbf{pk}} \mid \mid m \mid \mid L_i \mid \mid R_i\right)
\end{align*}
\item If $c_{n+1}^\prime = c_1$, $\texttt{Verify}$ produces $1$ as output. Otherwise, $\texttt{Verify}$ produces $0$ as output.
\end{enumerate}

\item $\texttt{Link}\left(1^\lambda, \textit{par}, (\sigma_1, \mathfrak{T}_1), (\sigma_2, \mathfrak{T}_2)\right) \to \left\{0,1\right\}$. $\texttt{Link}$ takes as input the security parameter $1^\lambda$, public parameters $\textit{par}$, and two signature-tag pairs $((\sigma_1, \mathfrak{T}_1), (\sigma_2, \mathfrak{T}_2))$. If $\mathfrak{T}_1 \in \mathbb{G}$ and $\mathfrak{T}_2 \in \mathbb{G}$ and $\mathfrak{T}_1 = \mathfrak{T}_2$, $\texttt{Link}$ produces $1$ as output. Otherwise, $\texttt{Link}$ produces $0$ as output.
\end{itemize}

\end{defn}

We use the usual definition of correct verification and correct linkability, both of which are straightforward to verify directly from the implementation. Later, we discuss the security of this implementation.

\begin{remark}
It may be possible to compress signatures further by  computing the coefficients $\mu_j$ without the inputs $\mathfrak{D}_j$ and publishing $\sigma = (c_1, s_1, \ldots, s_n, \sum_j \mu_j \mathfrak{D}_j)$ only, reducing signature sizes for $d > 1$ further.

The security of this variant is not proven here and is a good avenue for future work. The variant is not relevant for Monero, since $d=1$ for single-asset ring confidential transactions.
\end{remark}

\begin{remark}

Note that the signature is computed with the aggregated secret $w = \mu_X x_\ell + \sum_j \mu_j z_{\ell,j}$. This method of aggregating keys has two properties of importance.

First, under the random oracle model, the map defined by mapping $(x, z_1, \ldots, z_{d-1}) \mapsto w$ is collision resistant and anyone with knowledge of $(x_\ell, z_{\ell,1}, \ldots, z_{\ell,d-1})$ can compute the aggregated secret key $w$. More than one choice of $(x_\ell, z_{\ell,1}, \ldots, z_{\ell,d-1})$ could map to the same aggregated key, but collision resistance implies second pre-image resistance. Hence, given some $W = wG$ for an unknown aggregated secret key $w$ aggregated from some secret key $(x_\ell, z_{\ell,1}, \ldots, z_{\ell,d-1})$, an attacker has at most a negligible chance of finding a second secret key $(x_\ell^\prime, z_{\ell,1}^\prime, \ldots, z_{\ell,d-1}^\prime)$ that aggregates to the same secret $w$. This prevents the attacker from using an adversarially generated secret key that coincidentally aggregates to the same $w$ as some challenge key.

Second, under the random oracle model, the map is resistant to key cancellation. That is to say, an attacker has at most a negligible chance of selecting a secret key $(x_\ell, z_{\ell, 1}, \ldots, z_{\ell, d-1})$ with coordinates that cancel in the sum $w$; except with negligible probability, $w$ is dependent upon all bits of all coordinates of a secret key $(x, z_1, \ldots, z_{d-1})$.

\end{remark}

\subsection{Efficiency}

Consider the space and time efficiency of Definition \ref{def:clsag}. A $d$-CLSAG signature with a ring size of $n$ contains $n+1$ scalars and $d$ group elements, so this scheme is compact. In practice, signatures are broadcast with additional information such as references to the ring members. However, this is outside the scope of our definitions.

To examine the verification time complexity, let $k_s$ and $k_p$ be the time complexity of evaluating the hash-to-scalar functions $\mathcal{H}^s$ and of evaluating the hash-to-point function $\mathcal{H}^p$, respectively. Let $k^{(i)}$ be the time complexity to evaluate a scalar-point linear combination of $i$ terms; using specialized algorithms like Straus or Pippenger multiexponentiation (or others, based on $i$), such a linear combination can be evaluated much more quickly than a simple term-by-term computation. We note that it is also possible to cache multiples of points that are reused within verification for faster linear combination evaluation, but we do not differentiate this here. Using these, the time complexity of $d$-CLSAG verification is $(n+d)k_s + nk_p + 2nk^{(d+1)}$.

To compare to the current MLSAG scheme in Monero, note that $2$-CLSAG has equivalent functionality. The current Monero implementation requires $2n+1$ scalars and $1$ group element.

To determine the feasibility of implementation in Monero, we produced a test implementation using the Monero codebase and tested signing and verification for MLSAG and $2$-CLSAG on a 2.1 GHz Opteron processor. Table \ref{table:timing} shows the results for different ring sizes. In particular, we note that for ring sizes of interest to Monero (the current network-enforced size is $11$), CLSAG is uniformly faster than MLSAG. However, at very large ring sizes, MLSAG is faster due to additional computations involved in computing aggregation coefficients and key prefixing.

\begin{table}[htp]
\begin{center}
\begin{tabular}{r|ll|ll}
& \multicolumn{2}{c|}{Verify} & \multicolumn{2}{c}{Sign} \\
\hline
Ring size & MLSAG & CLSAG & MLSAG & CLSAG \\
\hline
2 & 2.4 & 2.0 & 2.3 & 2.7 \\
4 & 4.7 & 4.0 & 4.6 & 4.6 \\
8 & 9.5 & 7.8 & 9.4 & 8.5 \\
16 & 18.9 & 15.9 & 18.9 & 16.5 \\
32 & 37.8 & 32.3 & 37.8 & 33.0 \\
64 & 75.4 & 67.5 & 75.9 & 68.3 \\
128 & 150 & 147 & 151 & 148 \\
256 & 301 & 344 & 303 & 346
\end{tabular}
\end{center}
\caption{Signing and verification times (ms) for MLSAG and $2$-CLSAG}
\label{table:timing}
\end{table}

\section{Applications}

\subsection{Single-asset ring confidential transactions}\label{sec:ringct}

As mentioned above, it is possible to use $2$-CLSAG as a replacement for MLSAG signatures in Monero for equivalent functionality. Currently, Monero uses MLSAG signatures for two different transaction types: full and simple.

Full transactions are only used when spending a single input. They leverage the fact that in a balanced transaction, the difference between input and output commitments is a commitment to zero; the signer can therefore use such differences as the second component of key vectors in the signature and sign using the known secret key at the signing index.

Simple transactions are used when spending multiple inputs. Each spent input requires a separate signature, as a naive extension of full transactions presents an index linking issue. The signer first generates auxiliary commitments for each spent input using the same value but a different blinder. This means it is possible to use the difference between input and auxiliary commitments as a commitment to zero for the purpose of signing. By choosing all blinders at random except one, the signer can construct the auxiliary commitments such that the difference between auxiliary and output commitments is zero, proving balance.

Both transaction types can be used with $2$-CLSAG, since linkability is not considered for the second key component used in the transaction protocols.

\subsection{Multi-asset ring confidential transactions (MARCTs)}

It is possible to use a straightforward $d$-CLSAG construction to accommodate transactions spending $d-1$ \textit{types} or \textit{colors} of assets separately within the same transaction and signature. To do so, Monero outputs are extended to have a separate commitment to each asset type value. When spending an output, either a full or simple transaction (discussed above) is used; we simply copy the method used to compute commitment public keys in the signature to additional dimensions of the $d$-CLSAG signature, using only the commitments for a particular asset type in each. This separation ensures that the transaction balances in each asset type separately, while taking advantage of the scaling benefits of $d$-CLSAG compared to the equivalent MLSAG signature construction.

\subsubsection{Informal description of MARCT implementation}\label{ex:dualasset}

In this section, we leverage $\Pi_C^{(d)}$ for use in ring confidential transactions on $d-1$ different assets (or colors) with a pegged exchange rate between colors. We analyze the cost (in terms of weight and sync time) to the blockchain of our proposal compared to a similar proposal using $d$-MLSAG signatures. We present only the case $d=3$ in this section to represent two colors, leaving extensions for future work.

Consider the canonical example of colored currency with a fixed peg between two colors: dollars and pennies with a $100:1$ exchange rate between them. Define an exchange rate by determining some constants $\gamma_C, \gamma_D$ on $\left\{1, 2, \ldots, 2^{\xi - 1}\right\}$, (in this example, $\gamma_C = 1$ and $\gamma_D = 100$). Let $G, G^\prime$ be public group elements with unknown discrete logarithms with respect to each other where $G$ is the output from $\texttt{Setup}$ for a $d$-CLSAG.  Let $(\texttt{Prove}, \texttt{Ver})$ be a zero-knowledge sound range proving scheme, such as that described in \cite{bulletproofs}, and let $(\texttt{Com}, \texttt{Open})$ be a Pedersen commitment scheme such that $\texttt{Com}(r,v) = rG + v G^\prime$.

For the sake of this example, we define a public trading key to be a tuple $(X, C, D, P)$ where $X, C, D \in \mathbb{G}$, $C$ and $D$ are commitments and $P$ is a batched range proof from $\texttt{Prove}$ covering the values of both $C$ and $D$. We define a transaction key to be a tuple $(m, \textbf{Q}, \textbf{O}, (f_C, f_D), (\sigma, \mathfrak{T}), \textit{aux})$ where $\textbf{Q}$ is a ring of $n$ public trading keys  $\textbf{Q} = \left\{(X_i, C_i, D_i, P_i)\right\}_{i=1}^{n}$, $\textbf{O}$ is a set of $n^\prime$ output public trading keys $\textbf{O} = \left\{(X_i^\prime, C_i^\prime, D_i^\prime, P_i^\prime)\right\}_{i=1}^{n^\prime}$, $f_C$ is a plaintext list of fees to be paid from $C$, $f_D$ is a plaintext list of fees to be paid from $D$, $S=(\sigma, \mathfrak{T})$ is a CLSAG signature-tag pair.

We say a simple transaction key is valid if the following are satisfied:
\begin{itemize}
\item every input ring member $(X_i, C_i, D_i, P_i) \in \textbf{Q}$ has a valid range proof $P_i$ so $\texttt{Ver}(P_i) = 1$; and
\item every output range proof $P_k^\prime$ is valid so $\texttt{Ver}(P_k^\prime)=1$; and
\item the signature-tag pair $(\sigma, \mathfrak{T})$ passes $d$-CLSAG verification $\texttt{Verify}(m, \underline{\textbf{pk}}, (\sigma, \mathfrak{T})) = 1$ for the modified ring \[\textbf{pk} = \begin{pmatrix} X_1 & X_2 & \cdots & X_n \\ Z_1 & Z_2 & \cdots & Z_n\end{pmatrix}\] where each $Z_i = \gamma_C (C_i - f_C G^\prime - \sum_k C_k^\prime) + \gamma_D ( D_i - f_D G^\prime - \sum_k D_k^\prime)$.
\end{itemize}

As before, this CLSAG signature demonstrates knowledge of the discrete logarithm of some $x_\ell$, knowledge of the opening information for the input and output commitments, and that the opening information for the commitments balance with the fees $f_C$ and $f_D$.  After all, when the amounts in $C_\ell$ and $D_\ell$ balance with the fees $f_C$ and $f_D$ together with the sum of the amounts in each $C_k^\prime$ and $D_k^\prime$, and when the signer knows all the openers for all these commitments, the point $\gamma_C(C_\ell - f_C G^\prime - \sum_k C_k^\prime) + \gamma_D(D_\ell - f_D G^\prime - \sum_k D_k^\prime)$ will be a usual public key with basepoint $G$ whose secret key is known by the signer.

\subsubsection{Flexible pegs, coin spectra, privacy, and further extensions}

The validity of a MARCT without any exchange at all between assets is also possible, allowing for assets to be segregated.

On the other hand, different exchange coefficients $\gamma_C$ and $\gamma_D$ are certainly possible.  Just so long as there is a way for validators to come to an agreement upon exchange rate coefficients, validators can also convince themselves that transactions accordingly balance. Extending the model of simple ring confidential transactions with two colors to more than two colors is a straightforward exercise.

Further extensions with more immediate value may be possible. One open question is how to modify the above scheme to mask exchange rates. Another open question involves formalizing flexible-peg models of full colored ring confidential transactions between many colors (a spectrum?). These extensions represent fundamental building blocks for a system of smart transactions that respect user privacy.

\appendix

\section{Security: Unforgeability}

\subsection{Hardness}

Unforgeability comes from the $k$-OMDL hardness assumption.

\begin{defn}[k-OMDL problem]
Let $k \in \mathbb{N}$. We say a PPT algorithm $\texttt{A}$ is a $(t, \epsilon)$-solver of the $k$-OMDL problem if, within time at most $t$ and with probability at least $\epsilon$, $\texttt{A}$ can succeed at the following.

\begin{enumerate}
\item The challenger uses group parameters $(p, \mathbb{G}, G)$ and picks $G_1, G_2, \ldots, G_{k}, G_{k+1} \in \mathbb{G}$ (the targets) uniformly at random from $\mathbb{G}$. The challenger sends the group parameters and $\left\{G_i\right\}$ to $\texttt{A}$.

\item $\texttt{A}$ is granted access to a corruption oracle $\mathcal{CO}$ that takes as input some $G_i$ sent to $\texttt{A}$ and produces as output the discrete logarithm of $G_i$ with respect to $G$, i.e.\ some $x_i \in \mathbb{Z}/p\mathbb{Z}$ such that $G_i = x_i G$.

\item $\texttt{A}$ produces as output a sequence of $k+1$ scalars $x_1, \ldots, x_{k+1} \in \mathbb{Z}/p\mathbb{Z}$, counting as a success if:
\begin{enumerate}[(i)]
\item for each $x_i$, there exists some index $1 \leq j(i) \leq k+1$ such that $G_{j(i)} = xG$ and
\item $\texttt{A}$ made no more than $k$ queries to $\mathcal{CO}$. 
\end{enumerate}
\end{enumerate}
\end{defn}

\subsection{Defining forgeries}
We use a modified version of the definition of existential forgery with insider corruption for a ring signature by Bender, Katz, and Morselli \cite{bender}. By using linkability tags, our definition is slightly stronger; we allow forgeries to count as successful either with partially-corrupted rings or with messages that the signing oracle has signed before, just so long as neither the signature nor the linkability tag from the forgery appear as output from any oracle query in any transcript. This prevents a malicious party with the ability to persuade users to sign maliciously selected messages with maliciously selected ring members from constructing ostensibly valid, previously-unseen signature-tag pairs.

We use the following in the next definition. Let $n(-)$ be a positive polynomial. Let $\mathcal{H}^s:\left\{0,1\right\}^* \to \mathbb{Z}/p\mathbb{Z}$ be modeled as a random oracle. Let $\mathcal{CO}$ be a corruption oracle that takes as input a public key $\textbf{pk}$ and produces as output the corresponding secret key $\textbf{sk}$ and the linkability tag $\mathfrak{T}$. Let $C$ be the set of all keys in the transcript of queries made by $\texttt{A}$ to $\mathcal{CO}$. Let $T_C$ be the set of all linkability tags that appear as output from such a query. Let $\mathcal{SO}$ be a signing oracle that takes as input some $(m, \underline{\textbf{pk}}^\prime, \ell)$ such that $pk_\ell \in \underline{\textbf{pk}} \cap \underline{\textbf{pk}^\prime}$ and produces as output a signature-tag pair $(\sigma, \mathfrak{T})$ such that $\texttt{Verify}(m, \underline{\textbf{pk}}^\prime, \sigma, \mathfrak{T}) = 1$.

\begin{defn}[Existential unforgeability of linkable ring signatures with respect to insider corruption]\label{def:unf}

We say a PPT algorithm $\texttt{A}$  is a $(t, \epsilon, q_h, q_c, q_s,  n(-))$-forger of a linkable ring signature scheme if, within time at most $t$ and with at most $q_h$ oracle queries to $\mathcal{H}^s$, at most $q_c$ oracle queries to $\mathcal{CO}$, and at most $q_s$ queries to $\mathcal{SO}$, $\texttt{A}$ can succeed at the following game with probability at least $\epsilon$.
\begin{enumerate}
\item The challenger selects $\left\{(\textbf{sk}_i, \textbf{pk}_i)\right\}_{i=1}^{n(\lambda)} \leftarrow \texttt{KeyGen}(1^\lambda)$ and sends $\underline{\textbf{pk}} = \left\{\textbf{pk}_i\right\}_{i=1}^{n(\lambda)}$ to $\texttt{A}$.

\item $\texttt{A}$ is granted access to a corruption oracle $\mathcal{CO}$, random oracle $\mathcal{H}^s$, and the signing oracle $\mathcal{SO}$.

\item $\texttt{A}$ outputs a message $m$, a ring of at most $n$ public keys $\underline{\textbf{pk}}^\prime$, and a signature-tag pair $(\sigma, \mathfrak{T})$. This output is a success if $\underline{\textbf{pk}}^\prime \subseteq \underline{\textbf{pk}}$ and $\mathfrak{T} \notin T_C$ and $\sigma$ has not been output by $\mathcal{SO}$ and $\texttt{Verify}(m, \underline{\textbf{pk}}^\prime, \sigma, \mathfrak{T}) = 1$.

\end{enumerate}
\end{defn}

These success requirements ensure that (i) any ring member whose linkability tag is $\mathfrak{T}$ has not yet had its corresponding private key corrupted by $\mathcal{CO}$; and (ii) the signature itself has not been produced by the signing oracle. This allows the attacker to perhaps re-use a message $m$ and linkability tag $\mathfrak{T}$ from a previous oracle query. If the attacker can produce a new signature $\sigma^\prime$ on a message that has been signed before by the oracle then the new signature should still count as a forgery.

\subsection{The Forking Lemma} To prove that the existence of a forger implies that of a $k$-OMDL solver, we use the forking lemma. In the following, we presume the bit length $\eta$ is used to describe group elements in $\mathbb{G}$ and scalars in $\mathbb{Z}/p\mathbb{Z}$, i.e.\ $\eta = O(\left|p\right|)$.

\begin{lemma}[General Forking Lemma]\label{lem:fork}
Let $q, \eta \geq 1$. Let $\texttt{A}$ be any PPT algorithm which takes as input some $x_\texttt{A} = (x, \underline{h})$ where $\underline{h} = (h_1, \ldots, h_q)$ is a sequence of oracle query responses ($\eta$-bit strings) and returns as output $y_{\texttt{A}}$ either a distinguished failure symbol $\bot$ or a pair $(\textit{idx}, y)$ where $\text{idx} \in [q]^2$ and $y$ is some output. Let $\epsilon_{\texttt{A}}$ denote the probability that $\texttt{A}$ does not output $\bot_{\texttt{A}}$ (where this probability is taken over all random coins of $\texttt{A}$, the distribution of $x$, all choices $\underline{h}$). Let $\mathcal{F} = \mathcal{F}^{\texttt{A}}$ be the forking algorithm for $\texttt{A}$ described below. The accepting probability of $\mathcal{F}$ satisfies \[\epsilon_{\mathcal{F}} \geq \epsilon_{\texttt{A}} \left(\frac{\epsilon_{\texttt{A}}}{q} - \frac{1}{2^\eta}\right).\]
\end{lemma}

We refer the reader to \cite{bellare} for a proof of this lemma, which demonstrates that if executing some $\texttt{A}$ has non-negligible acceptance probability, then forking $\texttt{A}$ does as well. Since all queries before the $(j^*)^{th}$ query are identical in both transcripts, the input of the $(j^*)^{th}$ query is also identical. Since oracle queries $h_{j^*}^{\prime}, h_{j^*+1}^{\prime}, \ldots$ are newly sampled upon receiving the first output from $\texttt{A}$, the queries $h_{j^*} \neq h_{j^*}^\prime$ except with negligible probability. All subsequent computations in the signature that are common in both transcripts will have the same results only with negligible probability.

\subsubsection{Using a forger in the Forking Lemma}

Note that a forger according to Definition \ref{def:unf} is not directly compatible with the forking lemma; the output is some $y = (m, \textbf{pk}, \sigma, \mathfrak{T})$ and no $\textit{idx}$ is included.  However, without loss of generality, we can execute $\texttt{A}$ in a black box that extracts from the transcript of $\texttt{A}$ some $\textit{idx} = (j^*, i^*)$ in the following way.

For each query for any $c_{i+1}$ that appears in the successful forgery, there exists a corresponding index $j(i)$ that satisfies $c_{i+1} = h_{j(i)}$. The black box executing $\texttt{A}$ looks at the transcript and extracts the index pair $\textit{idx} = (i^*, j^*)$ that indicates where in the random oracle transcript we can find the very first oracle query made by $\texttt{A}$ to $\mathcal{H}^s$ for any challenge $c_{i^*+1}$ used in the successful forgery. If such a pair $(i^*, j^*)$ can be found, the algorithm wrapping $\texttt{A}$ can then output $(\textit{idx}, y)$ with only a negligible difference in advantage.

Moreover, each $c_{i+1}$ used in the signature verification is computed by $\texttt{A}$ by querying $\mathcal{H}^s$  in the transcript of $\texttt{A}$ leading to a successful forgery. In particular, the challenge could not have been guessed without making the query (except with negligible success). Indeed, a probabilistic algorithm could flip coins to guess the hash output, but this is successful with negligible probability. Of course, although the index $i^*$ may not have been decided by $\texttt{A}$ when the query was made, but by the time the forgery is complete, the index $i^*$ has been assigned.

Hence, without loss of generality, we can assume that $\texttt{A}$ has been appropriately wrapped so is compatible with the forking lemma without impacting its advantage. One algorithm $\mathcal{F}^\texttt{A}$ that works in Lemma \ref{lem:fork} works in the following way.

\begin{enumerate}
\item $\mathcal{F}$ takes as input some $x$ and $\mathcal{F}$ selects the random tape for $\texttt{A}$.
\item $\mathcal{F}$ selects some $\underline{h} = (h_1, \ldots, h_q)$ at random by flipping coins, and $\mathcal{F}$ executes $y_\texttt{A} \leftarrow \texttt{A}(x,\underline{h})$.
\item If $y_{\texttt{A}} = \bot_{\texttt{A}}$, then $\mathcal{F}$ outputs $\bot_{\mathcal{F}}$ and terminates. Otherwise, $y_{\texttt{A}} = (\textit{idx}, y)$ for some $\textit{idx}=(i^*,j^*)$ and some output $y$ and $\mathcal{F}$ selects new oracle queries $h_{j^*}^\prime, h_{j^*+1}^\prime, \ldots, h_q^\prime$, and glues the hash challenges together $\underline{h}^\prime = (h_1, \ldots, h_{j^*-1}, h_{j^*}^\prime, h_{j^*+1}^\prime, \ldots, h_q^\prime)$. 
\item If $h_{j^*} = h_{j^{*}}^\prime$, then $\mathcal{F}$ outputs $\bot_{\mathcal{F}}$ and terminates. Otherwise, $h_{j^*} \neq h_{j^{*}}^\prime$ and $\mathcal{F}$ executes $y_\texttt{A}^\prime \leftarrow \texttt{A}(x,\underline{h}^\prime)$.
\item If $y_{\texttt{A}}^\prime = \bot_{\texttt{A}}$, then $\mathcal{F}$ outputs $\bot_{\mathcal{F}}$ and terminates. Otherwise, $y_{\texttt{A}}^\prime = (\textit{idx}^{\prime}, y^\prime)$. If $\textit{idx} \neq \textit{idx}^\prime$, $\mathcal{F}$ outputs $\bot_{\mathcal{F}}$ and terminates. Otherwise, $\mathcal{F}$ outputs $(\textit{idx}, y, \underline{h}, y^\prime, \underline{h}^\prime)$.
\end{enumerate}

We note that $\mathcal{F}^{\texttt{A}}$ executed in a black box can be fed the oracle queries $\underline{h}$ and $\underline{h}^\prime$ and so these can be assumed to be output as well without loss of generality or impacting acceptance probability.

Of course, if $\texttt{A}$ runs in time at most $t$, $\mathcal{F}^{\texttt{A}}$ runs in time at most $2t+s$ where $s$ denotes the (negligible) time it takes $\mathcal{F}^{\texttt{A}}$ to select the random tape for $\texttt{A}$, select the oracle query sequences $\underline{h}$ and $\underline{h}^\prime$, and output the results.

\subsection{The Oracles}

Of course, any oracle queries made by $\texttt{A}$ must be handled by $\mathcal{F}^{\texttt{A}}$ somehow, and we have already described how $\mathcal{F}^{\texttt{A}}$ handles random oracle queries made by $\texttt{A}$: by flipping coins at random and keeping a hash table of the results to maintain consistency with future queries. The forger also has corruption oracle and signing oracle access. We assume that $\mathcal{F}^{\texttt{A}}$ is granted access to a corruption oracle (say, through the $k$-OMDL game challenger), so we only need to describe the signing oracle.

The signing oracle access granted to $\texttt{A}$ is simulated by $\mathcal{F}^{\texttt{A}}$ through backpatching in the following way. $\mathcal{F}^{\texttt{A}}$ selects $c_{\ell+1}$ at random without knowing the corresponding query to $\mathcal{H}^s$. $\mathcal{F}^{\texttt{A}}$ uses the query results $\underline{h}$ to get each $c_{i+1}$ and stores the results in a hash table for consistency in later queries. $\mathcal{F}^{\texttt{A}}$ finally computes $c_\ell$, $\mathcal{F}^{\texttt{A}}$ and can compute the group points $L_\ell, R_\ell$ such that $c_{\ell+1} = \mathcal{H}^s(\underline{\textbf{pk}} \mid \mid m \mid \mid L_\ell \mid \mid R_\ell)$. $\mathcal{F}^{\texttt{A}}$ back-patches the hash table.

\subsection{Playing k-OMDL}

We now construct a master algorithm $\texttt{M}$ that plays the $k$-OMDL game for $k=2d\cdot q_c + d-1$ that operates in the following way.
\begin{enumerate}

\item $\texttt{M}$ receives group parameters $(p, \mathbb{G}, G)$ and target group elements $G_1, \ldots, G_{k+1}$ from the $k$-OMDL challenger.

\item $\texttt{M}$ sets $\textbf{pk}_i := (G_{d(i-1) + 1}, G_{d(i-1) + 2}, \ldots, G_{di})$ for $i=1, \ldots, \frac{k+1}{d}$ and uses $\left\{\textbf{pk}_i\right\}_{i=1}^{\frac{k+1}{d}}$ as input for $\mathcal{F}^{\texttt{A}}$, responding to queries made by $\mathcal{F}^{\texttt{A}}$ for a key $\textbf{pk}_i$ by querying $\mathcal{CO}$ directly with each coordinate and responding with the result.

\item If $\mathcal{F}^{\texttt{A}}$ outputs $\bot$, so does $\texttt{M}$ and $\texttt{M}$ terminates.

\item Otherwise, $\mathcal{F}^{\texttt{A}}$ succeeds executing $\texttt{A}$ twice, each time taking no more than $q_c$ queries to corrupt $d$-dimensional keys, resulting in no more than $2\cdot d\cdot q_c$ queries to the discrete logarithm oracle $\mathcal{CO}$. $\mathcal{F}^{\texttt{A}}$ produces $(\textit{idx}, y_1, \underline{h}, y_2, \underline{h}^\prime)$ where $y_1 = (m_1, \textbf{pk}^{\prime}_1, \sigma_1, \mathfrak{T}_1)$ and $y_2 = (m_2, \textbf{pk}^{\prime}_2, \sigma_2, \mathfrak{T}_2)$ are forgeries using oracle queries $\underline{h}$ and $\underline{h}^\prime$, respectively, and $\textit{idx} = (i^*, j^*)$ as described previously. The messages and rings are identical in these forgeries because they must have been selected before the first challenge query, except with negligible probability. So $\texttt{M}$ can parse 
\begin{align*}
y_1 =& (m, \underline{\textbf{pk}}^\prime, \sigma_1, \mathfrak{T}_1) & \sigma_1 =& (c_1, s_1, \ldots, s_n, \left\{\mathfrak{D}_j\right\}_j) \\
y_2 =& (m, \underline{\textbf{pk}}^\prime, \sigma_2, \mathfrak{T}_2) & \sigma_2 =& (c_1^\prime, s_1^\prime, \ldots, s_n^\prime, \left\{\mathfrak{D}_j^\prime\right\}_j)\end{align*}

\item In the transcript of $\mathcal{F}^{\texttt{A}}$, $\texttt{M}$ finds $c_{i^*+1} = h_{j^*}$ and in the second transcript $c_{i^*+1} = h^\prime_{j^*}$ for some $h_{j^*} \neq h^\prime_{j^*}$. In both transcripts, $c_{i^*+1}$ is the response to the query $\mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid L \mid \mid R)$ for the same group elements $L, R$. Moreover, since this is the query for $c_{i^*+1}$ in both transcripts, the  $\texttt{M}$ finds that $L = s_{i^*} G + c_{i^*} W$ where $W = \mu_X X_{i^*} + \sum_j \mu_j Z_{i^*, j}$ in the first transcript and that $L = s_{i^*}^\prime G + c_{i^*}^\prime W$ in the second transcript, where $L$ and $W$ are common to both transcripts.

\item If $\mu_X = 0$ then $\texttt{M}$ outputs $\bot$ and terminates.

\item Otherwise, $\texttt{M}$ computes the discrete logarithm
$w = \frac{s_{i^*}^\prime - s_{i^*}}{(c_{i^*} - c_{i^*}^\prime)}$ without querying $\mathcal{CO}$.

\item $\texttt{M}$ makes up to $d-1$ queries to $\mathcal{CO}$ to find the discrete logarithms of the elements of any $(d-1)$-subset of $\left\{X_{i^*}, Z_{i^*, 1}, \ldots, Z_{i^*, d-1}\right\}$.

\item $\texttt{M}$ uses $w$ to solve for the final discrete logarithm.

\item $\texttt{M}$ outputs the $2 \cdot d \cdot q_c$ queries made by $\mathcal{F}^{\texttt{A}}$ and outputs the vector $(x_{i^*}, z_{i^*, 1}, \ldots, z_{i^*, d-1})$.

\end{enumerate}

Note that if $\texttt{M}$ does not terminate and output $\bot$, then $\texttt{M}$ makes up to $2\cdot d \cdot q_c$ queries to $\mathcal{CO}$ for $\mathcal{F}^{\texttt{A}}$ and makes an an additional $d-1$ queries to $\mathcal{CO}$, and yet produces as output $d \cdot (q_c + 1) > d \cdot q_c + d-1$ discrete logarithms, i.e.\ $\texttt{M}$ successfully plays the $k$-OMDL game for $k = 2\cdot d\cdot q_c + d-1$. Furthermore,  if $\texttt{M}$ already corrupted these discrete logarithms, even fewer queries could be made, tightening $k$ and making $\texttt{M}$ a more powerful solver.

Also note that, as previously mentioned, since the map $(x, z_1, \ldots, z_{d-1}) \mapsto w$ is collision resistant, $\texttt{M}$ can skip steps and guess $w$ in step $7$ only with negligible success.

We previously noted that if $\texttt{A}$ runs in time $O(t)$, $\mathcal{F}^{\texttt{A}}$ runs in time $O(2t)$. $\texttt{M}$ takes an additional  time $s$ due to: simulating oracle queries with coin flips and hash table modifications throughout the execution, constructing keys in step $2$,  making termination checks in steps $3$, $6$, parsing the transcripts in step $4$, retrieving $L$ and $W$ from the transcript in step $5$, computing the discrete logarithm $w$ in step $7$, computing the $d$-linear system of equations in step $9$.

\subsection{Security proof}

All that remains to prove the unforgeability of the $d$-CLSAG scheme from Section \ref{sec:implem} is to show that $\texttt{M}$ as described has a non-negligible acceptance probability.

\begin{theorem}
Let $d, q_h, q_c, q_s \in \mathbb{N}$  and let $(p,\mathbb{G},G)$ be some group parameters. If a $(t, \epsilon, q_h, q_c, q_s, n(-))$-forger of the $d$-CLSAG implementation in Section \ref{sec:implem} exists then a $(2t, \epsilon^\prime)$-solver of the $k$-OMDL problem in $\mathbb{G}$ exists for $k = d\cdot q_c + d - 1$ where $\epsilon^\prime \geq \epsilon\left(\frac{\epsilon}{q_c} - \frac{1}{2^\eta}\right) - p^{-1}$.
\end{theorem}

\begin{proof}
Let where $d, q_h, q_c, q_s$ satisfy the hypotheses and let $\texttt{A}$ be a $(t, \epsilon, q_h, q_c, q_s, n)$-forger of the $d$-CLSAG scheme of Section \ref{sec:implem}, let $\mathcal{F}^{\texttt{A}}$ be the forking algorithm for $\texttt{A}$, and let $\texttt{M}$ be the master algorithm previously described. $\texttt{M}$ terminates and outputs $\bot$ in steps $3$ and $6$ only; otherwise, $\texttt{M}$ succeeds at the $k$-OMDL game. Hence, if $E_3$ is the event that $\texttt{M}$ outputs $\bot$ in step $3$ and $E_6$ is the event that $\texttt{M}$ outptus $\bot$ in step $6$, then $E_3, E_6$ are disjoint and the acceptance probability for $\texttt{M}$ is $1 - \mathbb{P}(E_3 \cup E_6) =  1 - \mathbb{P}(E_3) - \mathbb{P}(E_6)$. The probability that $\texttt{M}$ outputs $\bot$ in step $6$ is the probability that the hashed coefficient $\mu_X = 0$, which occurs with probability $p^{-1}$.  $\texttt{M}$ outputs $\bot$ in step $3$ when $\mathcal{F}^{\texttt{A}}$ produces $\bot$, but the forking lemma gives us that the acceptance probability of $\mathcal{F}^\texttt{A}$ is bounded from below by $\epsilon\left(\frac{\epsilon}{q_c} - \frac{1}{2^\eta}\right)$. Hence, $\texttt{M}$ succeeds with probability at least $ \left(\epsilon\left(\frac{\epsilon}{q_c} - \frac{1}{2^\eta}\right) - p^{-1}\right)$.
\end{proof}

\section{Security: Signer ambiguity}

\subsection{Hardness}

We show our scheme is computationally signer-ambiguous if the following DDH game is hard in $\mathbb{G}$.

\begin{defn}[Decisional Diffie-Hellman]\label{ddhgame} Let $\texttt{A}$ be any computationally unbounded PPT algorithm, $(p, \mathbb{G}, G)$ and let $n \in \mathbb{N}$.
\begin{enumerate}
\item The challenger selects $(r_{i,1}, r_{i,2}, r_{i,3}) \left(\mathbb{Z}/p\mathbb{Z}\right)^3$ uniformly and independently for $i=1, \ldots, n$. The challenger computes the public keys $R_{i,1} = r_{i,1} G$, $R_{i,2} = r_{i,2}G$, $R_{i,3}^{(0)} = r_{i,1} r_{i,2} G$, $R_{i,3}^{(1)} = r_{i,3} G$.

\item The challenger selects a bit $b$ independently and uniformly from $\left\{0,1\right\}$ and sends $\left\{(R_{i,1}, R_{i,2}, R_{i,3}^{(b)})\right\}_{i=1}^{n}$ to $\texttt{A}$.

\item $\texttt{A}$ outputs a bit $b^\prime$, succeeding if $b = b^\prime$.
\end{enumerate}

Note any algorithm can flip a coin and guess correctly half the time. We say the \textit{advantage} of $\texttt{A}$ is the difference between the probability of success for $\texttt{A}$ and $1/2$. If $\texttt{A}$ can solve this with an advantage at least $\epsilon$ in time at most $t$, we say $\texttt{A}$ is a $(t,\epsilon)$-solver of the DDH problem in $\mathbb{G}$.

\end{defn}

We note that due to the random self-reducibility of the DDH game, the classic DDH game is no harder than Definition \ref{ddhgame}
\subsection{Defining signer ambiguity}

\begin{defn}\label{sigambgame} We say $\texttt{A}$ is a $(t,\epsilon,n_1,n_2)$-solver of the signer ambiguity game if it can succeed with non-negligible advantage at the following game.
\begin{enumerate}
\item The challenger selects $n_1$ secret keys $\left\{\textbf{sk}_i\right\} \subseteq (\mathbb{Z}/p\mathbb{Z})^d$, computes the corresponding public keys $\textbf{pk}_i = \textbf{sk}_i \circ \textbf{G}$, and sends $\left\{\textbf{pk}_i\right\}$ to $\texttt{A}$.

\item $\texttt{A}$ outputs an arbitrary message $m$ and a ring of $n_2$ distinct members $\underline{\textbf{pk}}^\prime \subseteq \left\{\textbf{pk}_i\right\}$.

\item The challenger selects a ring index $1 \leq \ell \leq n_2$ uniformly at random, retrieves the private key $\textbf{sk}$, and sends a valid signature-tag pair $(\sigma, \mathfrak{T}) \leftarrow \texttt{Sign}(m, \underline{\textbf{pk}}^\prime, \textbf{sk})$ to $\texttt{A}$.
\item $\texttt{A}$ outputs an index $\ell^\prime$, succeeding if $\ell = \ell^\prime$. 
\end{enumerate}
Note that a simulator in place of $\texttt{A}$ without any input can guess any index from $\left\{1, \ldots, n_2\right\}$ with coin flips, succeeding with probability  at least $1/n_2$. We define the advantage of $\texttt{A}$ as the difference in acceptance probability and $1/n_2$.
\end{defn}

Note that if the secret index $\ell$ is leaked in the signer ambiguity game, this is equivalent to leaking information about the bit $b$ used in the DDH game. Also note that the game could be generalized to allow $\texttt{A}$ repeated and adaptive access to a signing oracle, just so long as so-called \textit{ring intersection} attacks are taken into account when defining the advantage of $\texttt{A}$. However, such a generalization is equivalent to ours.

\subsection{Security proof}

If $\mathbb{G}$ satisfies the DDH hardness assumption, then the distribution of the triple $(r_1G, r_2G, r_3G)$ is computationally indistinguishable from the triple $(r_1G, r_2G, r_1r_2G)$,  where the $r_i$ are independently uniform on $\mathbb{Z}/p\mathbb{Z}$. If $\mathcal{H}^p: \left\{0,1\right\}^* \to \mathbb{G}$ is modeled as a random oracle with output that is independent of its input, the distribution of a tuple $(r_1G, r_2G, r_3G)$ is identical to the distribution of $(r_1G, \mathcal{H}^p(r_1G), r_3G)$ where $r_1, r_3$ are independently uniform on $\mathbb{Z}/p\mathbb{Z}$. Hence, under the random oracle model and assuming $\mathbb{G}$ is DDH-hard, the distribution of triples $(r_1G, \mathcal{H}^p(r_1G), r_1\mathcal{H}^p(r_1G))$ where $r_1$ is uniformly random from $\mathbb{Z}/p\mathbb{Z}$ is computationally indistinguishable from the distribution of triples $(r_1G, \mathcal{H}^p(r_1G), r_3G)$ where $r_1, r_3$ are uniformly random from $\mathbb{Z}/p\mathbb{Z}$.

Now note that a solver of the signer ambiguity game is given $X_i$ and $\mathcal{H}^p(X_i)$ for each ring member and the linkability tag $\mathfrak{T} = x_\ell \mathcal{H}^p(X_\ell)$. The solver with a non-negligible advantage at guessing $\ell$ has a non-negligible advantage in distinguishing whether a given triple $(X_i, \mathcal{H}^p(X_i), \mathfrak{T})$ satisfies $\mathfrak{T} = x_i \mathcal{H}^p(X_i)$ or not.

\begin{theorem}
If a $(t, \epsilon, n_1, n_2)$-solver of the signer-ambiguity game exists, there exists a $(t, \frac{\epsilon}{2})$-solver of the DDH game. 
\end{theorem}

\begin{proof}
We assume $\texttt{A}$ is an algorithm that can succeed at the game in Definition \ref{sigambgame} with non-negligible advantage. We construct a master algorithm $\texttt{M}$ that plays the game in Definition \ref{ddhgame} by executing $\texttt{A}$ in a black box such that $\texttt{M}$ plays the role of the challenger in Definition \ref{sigambgame}.

$\texttt{M}$ receives a set of DDH challenge tuples $\left\{(R_{i,1}, R_{i,2}, R_{i,3}^{(b)})\right\}_{i=1}^{n}$. $\texttt{M}$ keeps two internal hash tables to maintain consistency between oracle queries made to $\mathcal{H}^p$ and $\mathcal{H}^s$, and flips coins to determine hash outcomes except as specified below. $\texttt{M}$ sets $X_i := R_{i,1}$, backpatches the key image basepoints $\mathcal{H}^p(X_i) := R_{i,2}$, and sets the purported key images $\mathfrak{T}_i := R_{i,3}^{(b)}$. The algorithm selects $Z_{i,j}$ at random and sets $\textbf{pk}_i := (X_i, Z_{i,1}, \ldots, Z_{i,d-1})$. The algorithm $\texttt{M}$ then operates in the following way:
\begin{enumerate}
\item $\texttt{M}$ sends the public keys $\underline{\textbf{pk}} = \left\{\textbf{pk}_i\right\}_{i=1}^{n}$ to $\texttt{A}$.

\item $\texttt{A}$ outputs a message $m$ and a ring $\underline{\textbf{pk}}^\prime$.

\item If $\underline{\textbf{pk}}^\prime \not\subseteq \underline{\textbf{pk}}$, $\texttt{M}$ outputs $\bot$ and terminates. Otherwise, the algorithm $\texttt{M}$ can find a one-to-one correspondence between ring indices in $\underline{\textbf{pk}}^\prime$ and key indices in $\underline{\textbf{pk}}$, so that for each ring index $1 \leq \ell \leq n_2$ in $\underline{\textbf{pk}}^\prime$, there exists some key index $1 \leq i(\ell) \leq n_1$ in $\underline{\textbf{pk}}$ such that the ring member is $X_{i(\ell)} = R_{i(\ell),1}$, has key image basepoint $\mathcal{H}^p(X_{i(\ell)}) = R_{i(\ell),2}$, and has key image $R_{i(\ell),3}^b$.

\item $\texttt{M}$ simulates a signature in the following way.
\begin{enumerate}[(a)]
\item $\texttt{M}$ selects a random index $1 \leq \ell \leq n_2$, selects a random scalar $c_{\ell+1} \in \mathbb{Z}/p\mathbb{Z}$, and selects random scalars $s_1, s_2, \ldots, s_n \in \mathbb{Z}/p\mathbb{Z}$.

\item For $i=\ell+1, \ell+2, \ldots, n-1, n, 1, 2, \ldots, \ell-1$, $\texttt{M}$ computes 
\begin{align*}
L_i :=& s_iG + c_i\left(\mu_X X_i + \sum_j \mu_j Z_{i,j}\right) \\
R_i :=& s_i\mathcal{H}^p(X_i) + c_i\left(\mu_X \mathfrak{T}_{i(\ell)} + \sum_j \mu_j \mathfrak{D}_j\right)\\
c_{i+1} :=& \mathcal{H}^s\left(\underline{\textbf{pk}}^\prime \mid \mid m \mid \mid L_i \mid \mid R_i \right)
\end{align*}

\item $\texttt{M}$ computes $c_\ell$, $L_\ell$, and $R_\ell$ as above. If $\mathcal{H}^s$ has been queried before with $\left(\underline{\textbf{pk}}^\prime \mid \mid m \mid \mid L_\ell \mid \mid R_\ell \right)$, $\texttt{M}$ outputs $\bot$ and terminates. Otherwise, $\texttt{M}$ backpatches $\mathcal{H}^s\left(\underline{\textbf{pk}}^\prime \mid \mid m \mid \mid L_\ell \mid \mid R_\ell \right) \leftarrow c_{\ell+1}$.

\item $\texttt{M}$ sends to $\texttt{A}$ the signature-tag pair $\left(\sigma, \mathfrak{T}_{i(\ell)}\right)$ where $\sigma = (c_1, s_1, \ldots, s_n, \left\{\mathfrak{D}_j\right\}_j)$.

\end{enumerate}

\item $\texttt{A}$ outputs a signing index $\ell^\prime$. If $\ell = \ell^\prime$, $\texttt{M}$ outputs $b^\prime = 0$. Otherwise, $\texttt{M}$ flips a coin and outputs a bit $b^\prime$ selected uniformly at random.
\end{enumerate}

Note that $\texttt{M}$ only terminates and outputs $\bot$ if $\texttt{A}$ asks for a signature with a ring containing a key that is not a DDH challenge key or if $\mathcal{H}^s$ has been queried with $\left(\underline{\textbf{pk}}^\prime \mid \mid m \mid \mid L_\ell \mid \mid R_\ell \right)$ before step $4c$. We can assume $\texttt{A}$ never asks for a signature with a bad ring like this. Moreover, the points $L_\ell$ and $R_\ell$ are uniformly distributed, so the probability that any algorithm can guess the input for backpatching is negligible. Hence, $\texttt{M}$ carries out the game in Definition \ref{ddhgame} except with negligible probability.

The law of total probability gives us that $\mathbb{P}\left[\texttt{M}\text{ wins}\right] = \frac{1}{2}\mathbb{P}\left[1 \leftarrow \texttt{M} \mid b=1\right] + \frac{1}{2}\mathbb{P}\left[0 \leftarrow \texttt{M} \mid b=0\right]$. Moreover, the event that $1 \leftarrow \texttt{M}$ is exactly the event that $\ell^\prime \leftarrow \texttt{A}$ and $\ell^\prime \neq \ell$, and the event that $0 \leftarrow \texttt{M}$ is exactly the event that $\ell^\prime \leftarrow \texttt{A}$ and $\ell^\prime = \ell$. If $b=1$, then $\texttt{M}$ received random points, not the DDH exchange key, so the signature sent to $\texttt{A}$ consists of uniformly random points and scalars. $\texttt{A}$ can do no better than to guess the index $\ell^\prime$ uniformly at random.  So $\mathbb{P}\left[1 \leftarrow \texttt{M} \mid b=1\right] = \mathbb{P}\left[\ell^\prime \leftarrow \texttt{A}, \ell^\prime \neq \ell \mid b = 1\right] = \frac{n-1}{n}$. On the other hand, if $b = 0$, then $\texttt{M}$ received the DDH exchange key. In this case, $\texttt{A}$ has an advantage $\epsilon$ at guessing the successful index, so $\mathbb{P}\left[\ell^\prime \leftarrow \texttt{A}, \ell = \ell^\prime \mid b = 0\right] = \frac{1}{n} + \epsilon$. Hence, $\texttt{M}$ succeeds at the DDH game with probability $\frac{1}{2}\left(1-\frac{1}{n}\right) + \frac{1}{2}\left(\frac{1}{n} + \epsilon\right) = \frac{1}{2} + \frac{\epsilon}{2}$.
\end{proof}

\bibliographystyle{plain}
\bibliography{bibliography}

\end{document}

### 2019-06-03 paper/mrl.tex
Both versions of paper (MRL and IACR)

--- 2019-06-03 paper/iacr.tex
@@
-\documentclass{article}
+\documentclass{mrl}
 
@@
 \usepackage[utf8]{inputenc}
-\usepackage{authblk}
-\usepackage{amsmath,amssymb,amsthm}
-\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}
 
@@
 \title{Compact linkable ring signatures and applications}
-\author[1]{Brandon Goodell}
-\author[1]{Sarang Noether}
-\author[2]{\texttt{RandomRun}}
-\affil[1]{Monero Research Lab, \texttt{\{surae,sarang\}@getmonero.org}}
-\affil[2]{Independent researcher}
-\date{}
+\authors{Brandon Goodell\footnote{\texttt{surae.noether@protonmail.com}} and Sarang Noether\footnote{\texttt{sarang.noether@protonmail.com}} and \texttt{RandomRun}}
+\affiliations{Monero Research Lab}
+\date{\today}
+\type{RESEARCH BULLETIN}
+\ident{MRL-0011}
 
 \begin{document}
-\maketitle
 

### 2019-06-25 slides/main.tex
Slides from Monero Konferenco 2019

\documentclass[aspectratio=169]{beamer}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric}
\usepackage{amsmath,amssymb}

\setbeamertemplate{footline}[frame number]
\setbeamertemplate{navigation symbols}{}

\setbeamercolor{palette primary}{fg=black,bg=white}
\setbeamercolor{palette secondary}{fg=black,bg=white}
\setbeamercolor{structure}{fg=black,bg=white}

% title frame
\defbeamertemplate*{title page}{mytheme}[1][]
{
  \begin{tikzpicture}[remember picture,overlay]
  \filldraw[white]
    (current page.north west) --
    (current page.north east) --
    ([xshift=0cm,yshift=-2cm]current page.north east)  --
    ([xshift=0cm,yshift=-2cm]current page.north west) -- cycle
    ;

  \node[opacity=0.2] at ([xshift=-1.5cm,yshift=-1cm]current page.north east) {\includegraphics[width=15cm]{monkon}};

  \node[text=black,anchor=south west,font=\sffamily\LARGE,text width=.8\paperwidth] at ([xshift=-100pt,yshift=-1cm]current page.center)(title){\raggedright\inserttitle};

  \node[text=black,anchor=south west,font=\sffamily\small,text width=.6\paperwidth] at ([xshift=-100pt,yshift=-1.5cm]current page.center)(institute){\raggedright\insertinstitute};

  \node[text=black,font=\large\sffamily,anchor=south west] at ([xshift=30pt,yshift=0.5cm]current page.south west)(date){\insertdate};

  \node[text=black,font=\large\sffamily,anchor=south west] at ([yshift=5pt]date.north west)(author){\insertauthor};
  \end{tikzpicture}
}

% definition of the symbols used in itemize
\newcommand\mysymbol{%
  \begin{tikzpicture}[xscale=0.85]
\draw[black, thick]  circle (1.5 pt);             
  \end{tikzpicture}%
  }

% definition of the itemize templates
\defbeamertemplate*{itemize item}{mysymbol}{\small\raise0.5pt\hbox{\mysymbol}}
\defbeamertemplate*{itemize subitem}{mysymbol}{\footnotesize\raise0.5pt\hbox{\mysymbol}}
\defbeamertemplate*{itemize subsubitem}{mysymbol}{\footnotesize\raise0.5pt\hbox{\mysymbol}}

\title[Transaction efficiency then and now]{Transaction efficiency then and now}
\author{Sarang Noether, Ph.D.}
\date{23 June 2019}

\institute{Monero Konferenco}

\begin{document}

\begin{frame}[plain]
\maketitle
\end{frame}

\begin{frame}
\frametitle{Disclaimer}
\begin{columns}
\begin{column}{0.2\textwidth}
\includegraphics[width=0.9\textwidth]{monero.png}
\end{column}
\begin{column}{0.8\textwidth}
The views expressed in this presentation are solely those of the author, and do not necessarily reflect those of any other person, organization, or community. \\~\\

The author receives funding support from the Monero community.
\end{column}
\end{columns}
\end{frame}

\begin{frame}
\frametitle{What is transaction efficiency?}
\begin{columns}

\begin{column}{0.3\textwidth}
\centering
\includegraphics[width=0.4\textwidth]{icon-space.png} \\~\\
\textbf{Space} \\
Bandwidth/storage
\end{column}

\begin{column}{0.3\textwidth}
\centering
\includegraphics[width=0.4\textwidth]{icon-hourglass.png} \\~\\
\textbf{Generation time} \\
Low-capacity devices
\end{column}

\begin{column}{0.3\textwidth}
\centering
\includegraphics[width=0.4\textwidth]{icon-stopwatch.png} \\~\\
\textbf{Verification time} \\
Chain sync
\end{column}

\end{columns}
\end{frame}

\begin{frame}{Levels of optimization}
\begin{columns}
\begin{column}{0.5\textwidth}
We can optimize at difference levels:
\begin{itemize}
\item low-level cryptographic operations
\item higher-level constructions
\item protocol parameters \\~\\
\end{itemize}

We will focus on \textit{constructions} today, but all of these have effects.
\end{column}
\begin{column}{0.5\textwidth}
\centering
\includegraphics[width=0.9\textwidth]{chain-growth.pdf} \\
Chain growth over time
\end{column}
\end{columns}
\end{frame}

\begin{frame}
\begin{figure}
\begin{tikzpicture}[square/.style={regular polygon,regular polygon sides=4}]
\node [square,draw,fill=lightgray] (sig) {\begin{tabular}{c}Ring \\ signature\end{tabular}};
\node [ellipse,draw,left=60pt,at=(sig.west),above=20pt] (inputs) {Input keys};
\node [ellipse,draw,left=60pt,at=(sig.west),below=20pt] (offsets) {\begin{tabular}{c}Commitment \\ offsets\end{tabular}};
\node [rectangle,draw,right=20pt,at=(sig.east)] (image) {Key image};

\draw [->] (inputs) -- (sig);
\draw [->] (offsets) -- (sig);
\draw [->] (sig) -- (image);
\end{tikzpicture}
\end{figure}
\centering
The ring signature proves key ownership, helps demonstrate transaction balance, and asserts correct key image construction.
\end{frame}

\begin{frame}
\begin{figure}
\begin{tikzpicture}[square/.style={regular polygon,regular polygon sides=4}]
\node [circle,draw] (data) {\begin{tabular}{c}Output data \\ \hline Amount ($v$)\\ Mask ($r$)\end{tabular}};
\node [rectangle,draw,left=20pt,at=(data.west),fill=lightgray] (enc) {\begin{tabular}{c}Recipient data \\ \hline $\operatorname{Enc}(v)$ \\ $\operatorname{Enc}(r)$\end{tabular}};
\node [rectangle,draw,right=20pt,at=(data.east)] (commit) {$\operatorname{Commit}(v,r)$};
\node [rectangle,draw,below=20pt,at=(commit.south),fill=lightgray] (range) {\begin{tabular}{c}Range proof \\ $v \in [0,2^n)$\end{tabular}};

\draw [->] (data) -- (enc);
\draw [->] (data) -- (commit);
\draw [->] (commit) -- (range);
\end{tikzpicture}
\end{figure}
\centering
The output constructions communicate output data to the recipient, are used (with auxiliary commitments) to show balance, and prevent amount overflow.
\end{frame}

\begin{frame}{Construction: ring signature}
We use \textbf{MLSAG} signatures to prove ownership of spent outputs without revealing the specific output in question. This type of ring signature shows more, though.
\begin{itemize}
\item The signer controls one output among a given set
\item The key image (used to detect double-spend attempts) was generated correctly
\item The (hidden) transaction amounts balance \\~\\
\end{itemize}

These signatures scale \textit{linearly} with the ring size in space, signing time, and verify time.
\end{frame}

\begin{frame}{CLSAG: the new hotness}
We propose \textbf{CLSAG} signatures to do the same thing, but more efficiently. \\~\\

CLSAG signatures use a linear combination of output signing keys and commitment keys to provide a drop-in replacement to MLSAG signatures. \\~\\

They still scale linearly, but take up less space and are faster to sign and verify. \\~\\

Security is more formally proven.
\end{frame}

\begin{frame}{Signature size (11-ring)}
\centering
\includegraphics[width=0.7\textwidth]{sig-size.pdf}
\end{frame}

\begin{frame}{Timing (11-ring)}
\begin{columns}
\begin{column}{0.5\textwidth}
\centering
\includegraphics[width=\textwidth]{sig-sign.pdf} \\~\\
\textbf{Signing}
\end{column}
\begin{column}{0.5\textwidth}
\centering
\includegraphics[width=\textwidth]{sig-verify.pdf} \\~\\
\textbf{Verification}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{Construction: commitments}
All amounts are represented as Pedersen commitments with globally fixed base:
$$\operatorname{Commit}(v,r) \equiv \underbrace{vH}_{\text{value}} + \underbrace{rG}_{\text{mask}}$$

The recipient needs to know both $v$ and $r$ to reconstruct the commitment and later use it in a ring signature to spend the output. \\~\\

Previously, both values were encrypted using the transaction shared secret $\operatorname{H}(aR,i)$:
\begin{eqnarray*}
\operatorname{Enc}(v) &\equiv& v + \operatorname{H}(\operatorname{H}(\operatorname{H}(aR,i))) \\
\operatorname{Enc}(r) &\equiv& r + \operatorname{H}(\operatorname{H}(aR,i))
\end{eqnarray*}
\end{frame}

\begin{frame}{New hotness: being clever}
\textbf{This is wasteful}. If generated randomly, both $r$ and $\operatorname{Enc}(r)$ are uniformly distributed and known only to the sender and recipient. So why include $\operatorname{Enc}(r)$ in the transaction at all? \\~\\

\textbf{Solution}: Do not include $\operatorname{Enc}(r)$. The sender and recipient both compute $$r \equiv \operatorname{H}(``\text{commitment\_mask}",\operatorname{H}(aR,i))$$ instead, and save $32$ bytes per output. \\~\\
\end{frame}

\begin{frame}{New hotness: being clever}
\textbf{This is still wasteful}. The amount cannot be larger than $8$ bytes, but is represented as a $32$-byte scalar. \\~\\

\textbf{Solution}: Restrict the amount representation to $8$ bytes and encrypt with a length-restricted XOR operation to save $24$ bytes per output:

$$\operatorname{Enc}(v) \equiv \Big( v \oplus \operatorname{H}(``\text{amount}",\operatorname{H}(aR,i)) \Big)_{0-7}$$

The full 32-byte scalar can be recovered in the same way.
\end{frame}

\begin{frame}{Commitment data size}
\centering
\includegraphics[width=0.7\textwidth]{commit.pdf}
\end{frame}

\begin{frame}{Construction: range proofs}
Since amounts are represented as commitments and balance is proven using commitment sums and differences, amounts must be restricted (relative to scalar field size) to avoid overflow. \\~\\

We must show that for $\operatorname{Commit}(v,r)$, the value $v$ is in the range $[0,2^{64})$. \\~\\

\textbf{Strategy}: Show that $v$ can be decomposed to $64$ bits, each of which is $0$ or $1$, without revealing the value of the bits. \\~\\

\textbf{Example}: $13_{10} = 1101_2 = (1 \times 2^3) + (1 \times 2^2) + (0 \times 2^1) + (1 \times 2^0)$
\end{frame}

\begin{frame}{Old way: bitwise ring signatures}
The previous method, bitwise Borromean range proofs, used ring signatures.
\begin{itemize}
\item Construct $64$ commitments, each to a bit of $v$, with masks that sum appropriately.
\item Build a ring signature over each bit commitment to show the value is either $0$ or $1$. \\~\\
\end{itemize}

To verify:
\begin{itemize}
\item Take a weighted sum of the bit commitments (using powers of $2$) and show it recovers the full amount commitment.
\item Verify the ring signature to assert that each commitment is to $0$ or $1$. \\~\\
\end{itemize}

This scales in space and time linearly with the number of bits!
\end{frame}

\begin{frame}{Bulletproofs: the new hotness}
Bulletproofs take a different approach.
\begin{itemize}
\item Reduce the range assertion to a set of vector inner product equations.
\item Prove knowledge of vector components in zero knowledge.
\item Compress this proof using a clever folding technique. \\~\\
\end{itemize}

This achieves precisely the same goal as bitwise Borromean proofs, but scales logarithmically with the number of bits. Plus:
\begin{itemize}
\item A prover can include multiple values in the same proof, to extend the logarithmic space scaling.
\item Generation and verification are still linear in the bit length, but we can use tricks.
\item Verification of a set of proofs adds only marginal time cost! (This is \textit{batching}.)
\end{itemize}
\end{frame}

\begin{frame}{2-output verification}
\centering
\includegraphics[width=0.7\textwidth]{bp-2.pdf}
\end{frame}

\begin{frame}{16-output verification}
\centering
\includegraphics[width=0.7\textwidth]{bp-16.pdf}
\end{frame}

\begin{frame}{2-output 128-batch verification}
\centering
\includegraphics[width=0.7\textwidth]{bp-2-batch-128.pdf}
\end{frame}

\begin{frame}{Proof size}
\centering
\includegraphics[width=0.7\textwidth]{bp-size.pdf}
\end{frame}

\begin{frame}{Typical transaction}
\begin{columns}
\begin{column}{0.5\textwidth}
\centering
\includegraphics[width=\textwidth]{txn-size-2-2.pdf} \\~\\
\textbf{Transaction size}
\end{column}
\begin{column}{0.5\textwidth}
\centering
\includegraphics[width=\textwidth]{txn-time-2-2.pdf} \\~\\
\textbf{Verification time}
\end{column}
\end{columns}
\begin{center}
We save $85\%$ on space and up to $81\%$ on verification time!
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\textbf{These are not complete scaling solutions!}
\end{center}

These are incremental (but useful) improvements to slow blockchain growth and speed up new node sync time. \\~\\

\begin{itemize}
\item Sublinear fixed-decoy transaction protocols
\begin{itemize}
\item Lelantus
\item Omniring
\end{itemize}
\item Efficient full-anonymity transaction protocols
\begin{itemize}
\item Bulletproofs (poor verification scaling for circuits)
\item Older-style SNARKs (toxic; excellent space/time scaling)
\item Newer-style SNARKs (nontoxic; better scaling, but not quite there)
\end{itemize}
\item Off-chain transaction layers (requires new plumbing)
\begin{itemize}
\item Atomic swaps
\item Payment channels/networks
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Thank you!}
\textbf{GitHub}: \texttt{https://github.com/SarangNoether}
\begin{itemize}
\item \texttt{research-lab}: older research
\item \texttt{skunkworks}: newer research (work in branches) \\~\\
\end{itemize}

\textbf{GitLab}: \texttt{https://repo.getmonero.org/SarangNoether}
\end{frame}

\end{document}

### 2019-06-27 dumb25519.py
Schnorr signatures

@@ -1,0 +1,449 @@
+# Dumb25519: a stupid implementation of ed25519
+#
+# Use this code only for prototyping
+# -- putting this code into production would be dumb
+# -- assuming this code is secure would also be dumb
+
+import random
+import hashlib
+
+# curve parameters
+q = 2**255 - 19
+l = 2**252 + 27742317777372353535851937790883648493
+cofactor = 8
+
+# Internal helper methods
+def exponent(b,e,m):
+    return pow(b,e,m)
+
+def invert(x,n):
+    return exponent(x,n-2,n)
+
+def xfromy(y):
+    temp = (y*y-1) * invert(d*y*y+1,q)
+    x = exponent(temp,(q+3)/8,q)
+    if (x*x - temp) % q != 0:
+        x = (x*I) % q
+    if x % 2 != 0:
+        x = q-x
+    return x
+
+d = -121665 * invert(121666,q)
+I = exponent(2,(q-1)/4,q)
+
+class Scalar:
+    def __init__(self,x):
+        if not isinstance(x,int) and not isinstance(x,long):
+            raise TypeError
+        self.x = x % l
+
+    def invert(self):
+        if self.x == 0:
+            raise ZeroDivisionError
+        return Scalar(invert(self.x,l))
+
+    def __add__(self,y):
+        if isinstance(y,int):
+            return Scalar(self.x + y)
+        if isinstance(y,Scalar):
+            return Scalar(self.x + y.x)
+        return NotImplemented
+
+    def __sub__(self,y):
+        if isinstance(y,int):
+            return Scalar(self.x - y)
+        if isinstance(y,Scalar):
+            return Scalar(self.x - y.x)
+        return NotImplemented
+
+    def __mul__(self,y):
+        if isinstance(y,int):
+            return Scalar(self.x * y)
+        if isinstance(y,Scalar):
+            return Scalar(self.x * y.x)
+        return NotImplemented
+
+    def __div__(self,y):
+        if isinstance(y,int):
+            return Scalar(self.x / y)
+        if isinstance(y,Scalar):
+            return Scalar(self.x / y.x)
+        raise NotImplemented
+
+    def __pow__(self,y):
+        if not isinstance(y,int):
+            return NotImplemented
+        return Scalar(self.x**y)
+
+    def __eq__(self,y):
+        if isinstance(y,Scalar):
+            return self.x == y.x
+        raise TypeError
+
+    def __ne__(self,y):
[…]

### 2019-06-27 schnorr.py

@@ -1,0 +1,76 @@
+# Schnorr signatures
+from dumb25519 import *
+
+# Schnorr signature
+class Signature:
+    def __init__(self):
+        self.c = None
+        self.s = None
+
+# Generate a key pair
+# OUTPUT
+#   x: private key (Scalar)
+#   X: public key (Point)
+def gen_keys():
+    x = random_scalar()
+    X = x*G
+    return x,X
+
+# Generate a Schnorr signature
+#
+# INPUT
+#   m: message (any hashable data type)
+#   x: private key (Scalar)
+# OUTPUT
+#   sig: Schnorr signature (Signature)
+def sign(m,x):
+    try:
+        hash_to_scalar(m)
+    except:
+        raise TypeError('Cannot hash message!')
+
+    if not isinstance(x,Scalar):
+        raise TypeError('Private key must be a Scalar!')
+
+    # Nonce must be nonzero
+    alpha = Scalar(0)
+    while alpha == Scalar(0):
+        alpha = random_scalar()
+
+    # Construct signature
+    sig = Signature()
+    sig.c = hash_to_scalar(m, alpha*G)
+    sig.s = alpha - x*sig.c
+    return sig
+
+# Verify a Schnorr signature
+#
+# INPUT
+#   m: message (any hashable data type)
+#   X: public key (Point)
+#   sig: Schnorr signature (Signature)
+# OUTPUT
+#   True/False: whether the signature is valid
+def verify(m,X,sig):
+    try:
+        hash_to_scalar(m)
+    except:
+        raise TypeError('Cannot hash message!')
+
+    if not isinstance(X,Point):
+        raise TypeError('Public key must be a Point!')
+
+    if not isinstance(sig,Signature):
+        raise TypeError('Signature must be a Signature!')
+    if not isinstance(sig.c,Scalar) or not isinstance(sig.s,Scalar):
+        raise TypeError('Signature components must be Scalars!')
+
+    # Verify the signature
+    c = hash_to_scalar(m, sig.s*G + sig.c*X)
+    return c == sig.c
+
+# Run simple tests
+x,X = gen_keys()
+m = 'Test message'
+assert verify(m,X,sign(m,x)) == True
+assert verify('Evil message',X,sign(m,x)) == False

### 2019-06-27 commit.py
Pedersen commitments

@@ -1,0 +1,37 @@
+# Pedersen commitments and algebra
+from dumb25519 import *
+import schnorr
+
+H = hash_to_point('H')
+
+# Construct a Pedersen commitment
+#
+# INPUT
+#   v: value (Scalar)
+#   r: mask (Scalar)
+# OUTPUT
+#   C: commitment (Point)
+def commit(v,r):
+    return r*G + v*H
+
+# Generate a Schnorr signature on the difference of two commitments
+# This shows the prover knows the discrete log of this difference,
+#   and therefore that the commitments are to the same value
+v = random_scalar() # common value
+r = random_scalar() # masks
+s = random_scalar()
+
+C = commit(v,r) # commitments
+D = commit(v,s)
+
+m = hash_to_scalar(C,D) # message is the public information
+
+# Generate a valid signature
+sig = schnorr.sign(m,r-s)
+assert schnorr.verify(m,C-D,sig) == True
+
+# Gnerate an invalid signature
+E = commit(random_scalar(),s)
+m = hash_to_scalar(C,E)
+sig = schnorr.sign(m,r-s)
+assert schnorr.verify(m,C-E,sig) == False

### 2019-07-19 rct3/dumb25519.py
Initial work on spend transaction

@@ -299,6 +299,9 @@ class ScalarVector:
             return self.scalars[i]
         return ScalarVector(self.scalars[i])
 
+    def __setitem__(self,key,value):
+        self.scalars[key] = value
+
     def append(self,item):
         if not isinstance(item,Scalar):
             raise TypeError
@@ -390,8 +393,8 @@ Z = Point(0,1)
 # multiexponention operation using simplified Pippenger
 def multiexp(*data):
     if len(data) == 1:
-        scalars = [datum[1] for datum in data[0]]
-        points = [datum[0] for datum in data[0]]
+        scalars = ScalarVector([datum[1] for datum in data[0]])
+        points = PointVector([datum[0] for datum in data[0]])
     else:
         scalars = data[0]
         points = data[1]

### 2019-07-19 rct3/pybullet.py

@@ -1,0 +1,342 @@
+import dumb25519
+from dumb25519 import Scalar, Point, ScalarVector, PointVector, random_scalar, random_point, hash_to_scalar, hash_to_point
+
+cache = '' # rolling transcript hash
+inv8 = Scalar(8).invert()
+
+# Add to a transcript hash
+def mash(s):
+    global cache
+    cache = hash_to_scalar(cache,s)
+
+# Clear the transcript hash
+def clear_cache():
+    global cache
+    cache = ''
+
+# Turn a scalar into a vector of bit scalars
+# s: Scalar
+# N: int; number of bits
+#
+# returns: ScalarVector
+def scalar_to_bits(s,N):
+    result = []
+    for i in range(N-1,-1,-1):
+        if s/Scalar(2**i) == Scalar(0):
+            result.append(Scalar(0))
+        else:
+            result.append(Scalar(1))
+            s -= Scalar(2**i)
+    return ScalarVector(list(reversed(result)))
+
+# Generate a vector of powers of a scalar
+# s: Scalar
+# l: int; number of powers to include
+#
+# returns: ScalarVector
+def exp_scalar(s,l):
+    return ScalarVector([s**i for i in range(l)])
+
+# Sum the powers of a scalar
+# s: Scalar
+# l: int; number of powers to include
+#
+# returns: Scalar; s^0+s^1+...+s^(l-1)
+def sum_scalar(s,l):
+    if not l & (l-1) == 0:
+        raise ValueError('We need l to be a power of 2!')
+
+    if l == 0:
+        return Scalar(0)
+    if l == 1:
+        return Scalar(1)
+
+    r = Scalar(1) + s
+    while l > 2:
+        s = s*s
+        r += s*r
+        l /= 2
+    return r
+
+# Perform an inner-product proof round
+# G,H: PointVector
+# U: Point
+# a,b: ScalarVector
+#
+# returns: G',H',U,a',b',L,R
+def inner_product(data):
+    G,H,U,a,b,L,R = data
+
+    n = len(G)
+    if n == 1:
+        return [a[0],b[0]]
+
+    n /= 2
+    cL = a[:n]**b[n:]
+    cR = a[n:]**b[:n]
+    L = (G[n:]*a[:n] + H[:n]*b[n:] + U*cL)*inv8
+    R = (G[:n]*a[n:] + H[n:]*b[:n] + U*cR)*inv8
+
[…]

### 2019-07-19 rct3/spend.py

@@ -1,0 +1,193 @@
+# RCT3 spend algorithm
+
+from dumb25519 import *
+from random import randrange
+
+RING = 8 # ring size
+
+# Generators
+Gc = hash_to_point('Gc')
+Hc = hash_to_point('Hc')
+U = hash_to_point('U')
+G0 = hash_to_point('G0')
+Hi = []
+for i in range(RING):
+    Hi.append(hash_to_point('Hi',i))
+
+k = randrange(RING) # signing index
+a = random_scalar() # input value
+kappa = random_scalar() # input mask
+delta = random_scalar() # input offset
+
+# Set ring and commitments
+print 'Preparing ring with',RING,'members...'
+pk = []
+C_in = []
+for i in range(RING):
+    pk.append(random_point())
+    C_in.append(random_point())
+
+sk = random_scalar() # signing key
+pk[k] = sk*G
+C_in[k] = a*Hc + kappa*Gc # input commitment
+C1 = C_in[k] - delta*Gc # offset commitment
+
+# Key image
+U1 = sk.invert()*U
+
+# Final ring
+Y = []
+temp = repr(pk) + repr(C_in) + repr(C1)
+d1 = hash_to_scalar(1,temp)
+d2 = hash_to_scalar(2,temp)
+for i in range(RING):
+    Y.append(pk[i] + d1*(C_in[i]-C1) + d2*G0)
+
+# Check spend index construction
+print 'Checking ring...'
+assert Y[k] == sk*G + (d1*delta)*Gc + d2*G0
+
+# Prepare signer index
+print 'Proving...'
+bL = ScalarVector([Scalar(0)]*RING)
+bL[k] = Scalar(1)
+bR = ScalarVector([])
+for i in range(RING):
+    bR.append(bL[i] - Scalar(1))
+
+# Point generation
+H = hash_to_point(repr(Y))
+alpha = random_scalar()
+beta = random_scalar()
+p = random_scalar()
+r_a = random_scalar()
+r_sk = random_scalar()
+r_d = random_scalar()
+sL = ScalarVector([])
+sR = ScalarVector([])
+for i in range(RING):
+    sL.append(random_scalar())
+    sR.append(random_scalar())
+
+# Commit 1
+B = alpha*H
+A = beta*H
[…]

### 2019-07-19 rct3/transaction.py

@@ -1,0 +1,208 @@
+# Basic transaction flow
+
+from common import *
+from dumb25519 import *
+import elgamal
+import signature
+import pybullet
+
+class Coin:
+    # Generate a new coin
+    # INPUTS
+    #   v: coin value
+    #   X1,X2: destination address
+    #   r: transaction private key
+    #   i: index
+    # DATA
+    #   P: coin public key
+    #   R: recovery public key
+    #   C: value commitment
+    #   enc_v: encrypted value
+    #   i: index in transaction
+    #   p: coin private key (after recovery)
+    #   v: coin value (after recovery)
+    def __init__(self,v,X1,X2,r,i):
+        # Sanity checks
+        if not isinstance(v,Scalar):
+            raise TypeError('Invalid coin value!')
+        if v > Scalar(2)**BITS - 1:
+            raise ValueError('Value is out of range!')
+        if not isinstance(X1,Point) or not isinstance(X2,Point):
+            raise TypeError('Invalid destination address!')
+        if not isinstance(r,Scalar):
+            raise TypeError('Invalid recovery private key!')
+
+        # Deterministic commitment mask
+        mask = hash_to_scalar('mask',hash_to_scalar(r*X2,i))
+
+        # Coin data
+        self.P = X1 + hash_to_scalar(r*X2,i)*G
+        self.R = r*G
+        self.C = com(v,mask)
+        self.enc_v = elgamal.encrypt(v,self.P)
+        self.i = i
+        self.p = None
+        self.v = None
+        self.mask = mask # private data
+
+    # Recover a coin's private data
+    # INPUTS
+    #   x1,x2: private address
+    # OUTPUTS
+    #   p: coin private key
+    #   v: coin value
+    def recover(self,x1,x2):
+        # Attempt to recover the coin private key
+        p = x1 + hash_to_scalar(x2*self.R,self.i)
+        if not p*G == self.P:
+            raise ValueError('Failed to recover coin!')
+
+        # Recover the coin value
+        v = elgamal.decrypt(self.enc_v,p)
+
+        # Confirm the commitment is valid
+        if not com(v,hash_to_scalar('mask',hash_to_scalar(x2*self.R,self.i))) == self.C:
+            raise ValueError('Coin commitment does not match!')
+
+        self.p = p
+        self.v = v
+
+    def __repr__(self):
+        r = '<Coin> '
[…]

### 2019-07-19 transaction.py

@@ -1,120 +1,0 @@
-# Basic transaction flow
-
-from common import *
-from dumb25519 import *
-import elgamal
-import signature
-
-class Coin:
-    # Mint a coin
-    # INPUTS
-    #   v: coin value
-    #   X1,X2: destination address
-    #   r: transaction private key
-    #   i: index
-    def __init__(self,v,X1,X2,r,i):
-        # Ensure the value is in range
-        if v > Scalar(2)**BITS - 1:
-            raise ValueError('Value is out of range!')
-
-        # Deterministic commitment mask
-        mask = hash_to_scalar('mask',hash_to_scalar(r*X2,i))
-
-        self.P = X1 + hash_to_scalar(r*X2,i)*G # coin public key
-        self.R = r*G # recovery public key
-        self.C = com(v,mask) # coin commitment
-        self.enc_v = elgamal.encrypt(v,self.P) # encrypted coin value
-        self.i = i # index
-
-    # Recover a coin
-    # INPUTS
-    #   x1,x2: private address
-    # OUTPUTS
-    #   p: coin private key
-    #   v: coin value
-    def recover(self,x1,x2):
-        # Attempt to recover the coin private key
-        p = x1 + hash_to_scalar(x2*self.R,self.i)
-        if not p*G == self.P:
-            raise ValueError('Failed to recover coin!')
-
-        # Recover the coin value
-        v = elgamal.decrypt(self.enc_v,p)
-
-        # Confirm the commitment is valid
-        if not com(v,hash_to_scalar('mask',hash_to_scalar(x2*self.R,self.i))) == self.C:
-            raise ValueError('Coin commitment does not match!')
-
-        return p,v
-
-    def __repr__(self):
-        r = '<Coin> '
-        r += 'P:' + repr(self.P) + '|'
-        r += 'R:' + repr(self.R) + '|'
-        r += 'C:' + repr(self.C) + '|'
-        r += 'enc_v:' + repr(self.enc_v) + '|'
-        r += 'i:' + repr(self.i)
-        return r
-
-
-# The result of a mint operation
-class MintTransaction:
-    # Mint a coin
-    #
-    # INPUTS
-    #  v: coin value
-    #  X1,X2: destination address
-    def __init__(self,v,X1,X2):
-        r = random_scalar() # recovery private key
-
-        self.coin = Coin(v,X1,X2,r,1) # minted coin
-        self.v = v # plaintext coin value
-
[…]

### 2019-07-20 workshop.tex
Workshop handout

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

\title{Crypto Playtime}
\author{Sarang Noether, Ph.D.}
\date{Monero Research Lab}

\begin{document}

\maketitle

Welcome! This workshop will guide you through simple cryptographic constructions using Python. These constructions are common in applied cryptography, and are similar to those used in Monero. Feel free to play around and learn, but please \textbf{do not use this library or the tools presented here for production code}. The library and tools have not been externally reviewed for security, and are intended only for basic algorithm prototyping and education.

\section{The \texttt{dumb25519} library}
The \texttt{dumb25519} library is a Python library that encapsulates basic elliptic curve cryptography similar to that used by Monero. Note that its representation of things like keys and hash functions, while mathematically sound, are not directly compatible with those used in the Monero codebase. The goal here is stupid simplicity. Find the library here:
\begin{center}
\url{https://github.com/SarangNoether/skunkworks/tree/curves/dumb25519}
\end{center}
Your Python 2.7-compatible installation will need the \texttt{random} and \texttt{hashlib} packages available to it.

The library is a basic implementation of the \texttt{ed25519} twisted Edwards elliptic curve used by Monero and other projects. Fortunately, you don't need to know the details of how the curve works in order to build things with it (but there are plenty of great resources on this if you're curious). Most of the functionality is abstracted away by \texttt{dumb25519}.

\subsection{Keys, points, and scalars}
We typically care about private and public keys for basic cryptographic constructions. Private keys are represented as a modular integer; that is, a non-negative integer restricted by a particular range that depends on the curve. For \texttt{ed25519}, that number (called $l$ in the code) is around $2^{252}$. This wraps around, so you can keep incrementing such a private key modular integer, and it will eventually wrap to zero.

Public keys, on the other hand, are typically represented as a point on the elliptic curve defined by the \texttt{ed25519} scheme. You can think of this (roughly) as a point on the $x$-$y$ plans on a complex-looking curve. In order to give our keys the expected structure, we need a ``starting point" or \textit{basepoint} on the curve. Any point will do, but the \texttt{ed25519} scheme defines one point in particular, called $G$. It's just a point that everyone agrees was chosen non-suspiciously, and is a public parameter of the curve scheme.

If my private key is the modular integer $x$, then my public key is defined to be $X = xG$. That's right, you can multiply an integer by a curve point, and you get another curve point! There's a geometric definition for how this arises, but the library abstracts it away for you.

You can also add curve points together, or subtract them. And this plays nicely with these modular integers (we call them \textit{scalars} too): $$X + X + X = 3X$$
Note that you can't multiply or divide points. Sorry, not defined.

There is a special point on the curve that we'll call the \textit{zero point} and denote by $Z$. It's not the number $0$ (curve points are points, not numbers), but a specific point. It has the property that it behaves like zero:
\begin{eqnarray*}
X + Z &=& X \\
X - X &=& Z \\
0X &=& Z
\end{eqnarray*}
We usually try to use lowercase letters to represent scalars, and uppercase letters to represent points. This helps us keep track of what's a number and what's a point on the curve.

The reason we define private and public key pairs using this simple multiplication method is that the operation only works in one direction. If I hand you a private key (scalar), you can easily multiply it by the basepoint and generate the public key (point). But if I hand you an arbitrary public key (point), it's considered not possible to easily find the private key (scalar) that corresponds to it.

\subsection{Data types}
The \texttt{dumb25519} library has Scalar and Point types that handle all of the functionality described above. It also defines the basepoint $G$ and the zero point $Z$ for you. They have particular $x$-$y$ coordinates that you can look up in the library code if you're curious.

You can generate a Scalar with the corresponding integer representation directly. You typically don't do this with Points, since they usually come from Scalar multiplication. You can also use \texttt{random\_scalar()} and \texttt{random\_point()} to generate them randomly for you, if you don't have particular values in mind.

Algebra and arithmetic work basically like you might expect:

\begin{verbatim}
from dumb25519 import *

# Generate a key pair
x = random_scalar()
X = x*G

# Test some basic arithmetic
P = random_point()
Q = random_point()
assert P + Q == Q + P # addition is commutative
assert P - P == Z # the zero point
assert P + P == Scalar(2)*P
assert Z - Q == Scalar(-1)*Q
\end{verbatim}

\subsection{Hashing}
It's very common in cryptographic applications to generate a fixed-length digest of a chunk of data. It should be easy to generate this digest, but very hard to invert and find out what data originally went in. This process is called \textit{hashing} the data, and the technique to do it is to use a \textit{hash function}. A hash function takes in whatever data you want and outputs some fixed-length representation.

For our purposes, we either want to hash data and get a Scalar, or hash data and get a Point. The \texttt{dumb25519} library supports both, and you can pass in essentially whatever data you need:

\begin{verbatim}
from dumb25519 import *

y = hash_to_scalar('arbitrary','data','here')

P = hash_to_point(G)
Q = hash_to_point(y,P,'test message',12345,random_scalar())
\end{verbatim}
You can go pretty crazy with hashing.

\section{Challenge: Schnorr signature}
For this challenge, we'll implement the popular Schnorr signature scheme. The idea is to take a message and sign it with a private key, such that anyone who knows the corresponding public key can verify the signature. Without knowing the private key, it isn't possible to forge a signature. Monero uses a variant of Schnorr signatures as its ring signature construction.

To start, suppose you have a message $m$ that you wish to sign. This can be any hashable data type. Assume also that you have generated a private and public key in the usual way: the private key is a random Scalar $x$, and the public key is the Point $X = xG$ (where $G$ is the known basepoint).

\subsection{Signing}
To sign the message $m$ with private key $x$, do the following:
\begin{enumerate}
\item Select a random nonzero Scalar $a$.
\item Compute the Scalar $c = H(m, aG)$ (where $H$ is a hash-to-scalar function).
\item Compute the Scalar $s = a - cx$.
\end{enumerate}
The resulting signature is the Scalar pair $(c,s)$.

\subsection{Verifying}
To verify a signature $(c,s)$ on a message $m$ with public key $X$, do the following:
\begin{enumerate}
\item Compute the Scalar $d = H(m, sG+cX)$.
\item Confirm that $d = c$.
\end{enumerate}

Observe why the signature works. The second component of the hash function simplifies, if it was generated correctly:
\begin{eqnarray*}
sG + cX &=& (a - cx)G + cX \\
&=& aG - c(xG) + cX \\
&=& aG - cX + cX \\
&=& aG + Z \\
&=& aG
\end{eqnarray*}
And, of course, $aG$ is what originally went into the hash function when signing!

\subsection{Code}
Use the \texttt{dumb25519} library to write a Schnorr signature implementation. The implementation should produce signatures on arbitrary messages using a specified private key, and verify signatures. If time permits, write a basic test suite.

\section{Challenge: Pedersen commitment}
For this challenge, we'll implement a particular application of Pedersen commitments. Pedersen commitments are a simple way to publicly ``commit" to a secret value, and later confirm that the value is what you claimed. They have many useful applications; in Monero, they are used to hide amounts and prove transaction balance. Note that if you are handed a commitment, it looks like a random Point; you cannot undo the commitment to figure out the value.

\subsection{Commit and reveal}
Everyone first needs to agree on two Points, $G$ and $H$. We usually use the standard curve basepoint $G$ and a hash-to-point result for $H$. (There are particular requirements on these Points, but for now we'll just say that they need to be ``effectively random" from each other.)

To publicly commit to a secret Scalar value $v$, do the following:
\begin{enumerate}
\item Choose a random Scalar $m$ (called the \textit{mask}).
\item Compute the Point $C = vH + mG$.
\end{enumerate}
The commitment is the point $C$.

You can later show that you had committed to $v$ easily. Simply reveal $v$ and $m$, and anyone can reconstruct $C$.

\subsection{Proving the same value}
Suppose we want to do something different. Namely, I want to generate two Pedersen commitments to the same value and publicly prove this, but without revealing the secret value $v$. This is similar to what happens in Monero, where we want to prove that transaction inputs and outputs are the same, but not reveal the amount itself.

It isn't enough to publicly look at the commitments and check that they are equal. If different masks are used (which should be the case!) with the same value, the resulting Points will look entirely random. Instead, we'll do something clever that involves the Schnorr work we did earlier.

To generate commitments to a value $v$ and prove this, do the following:
\begin{enumerate}
\item Choose random masks $m$ and $n$.
\item Compute the Pedersen commitments $C = vH + mG$ and $D = vH + nG$.
\item Compute the message $m = H(C,D)$, where $H$ is a hash-to-scalar function.
\item Generate a Schnorr signature on $m$; the private key should be the difference between masks $m-n$.
\end{enumerate}
Notice the cleverness here. The difference in commitments is $C-D = vH + mG - vH - nG = (m-n)G$. Because the values are the same, the result is the Point $(m-n)G$, which is a public key! The private key is $m-n$, which we can use in the Schnorr signature. Notice that we never reveal either of the masks $m$ or $n$ here; if we did, it may be possible for an attacker to brute-force the value $v$, which is not desirable. Further, notice that if the same value $v$ were not used in both commitments, we would not be able to identify the single public key in $C-D$.

To publicly verify that a given Schnorr signature is valid for commitments $C$ and $D$, do the following:
\begin{enumerate}
\item Compute the message $m = H(C,D)$.
\item Verify the Schnorr signature on $m$ using the public key $C-D$.
\end{enumerate}
This publicly convinces the verifier that $C$ and $D$ are commitments to the same value, but does not reveal anything about the value itself!

\subsection{Code}
Use the \texttt{dumb25519} library to write an implementation of this proving scheme. Given a value $v$, the code should produce commitments to $v$ and generate the proper Schnorr signature. It should also permit verification that two commitments are to the same value by verifying the Schnorr signature. Feel free to use your earlier Schnorr code to do this! If time permits, write a basic test suite.

\section{Other fun challenges}
Monero Research Lab researchers sometimes use the \texttt{dumb25519} library for easy initial prototyping of new ideas before investing time and effort in production code; it's a good way to check complex algebra for errors, and to iterate rapidly on new ideas. There are plenty of other cryptographic schemes you could implement. Here are two ideas:
\begin{itemize}
\item Look up details on the ElGamal encryption scheme, and implement encryption and decryption routines.
\item Look up details on Monero's MLSAG and CLSAG signature schemes, which are signer-ambiguous linkable variants of Schnorr signatures; implement signing and verifying.
\item If two Schnorr signatures are produced on different messages using the same private key and the same random value $a$, it is possible to trivially recover the private key. Write a tool that tests whether this has occurred when presented with two Schnorr signatures.
\end{itemize}

\end{document}

### 2019-07-22 rct3/common.py
Basic spend operation added to transaction flow

@@ -1,17 +1,24 @@
 # Common constants and such
 
-import dumb25519
+from dumb25519 import *
+
+# Protocol constants
+BITS = 4 # range bit length
+RING = 4 # anonymity set size
 
 # Fixed generators
-G = dumb25519.G
-H = dumb25519.hash_to_point('H')
-
-# Range bit length
-BITS = 4
+H = hash_to_point('H')
+Gc = hash_to_point('Gc') # commitment generator
+Hc = hash_to_point('Hc') # commitment generator
+U = hash_to_point('U')
+G0 = hash_to_point('G0')
+Hi = []
+for i in range(RING):
+    Hi.append(hash_to_point('Hi',i))
 
 # Pedersen commitment
 # INPUT
 #   v: value
 #   a: mask
 def com(v,a):
-    return v*H + a*G
+    return v*Hc + a*Gc

### 2019-07-22 rct3/spend.py

@@ -1,193 +1,246 @@
-# RCT3 spend algorithm
-
 from dumb25519 import *
-from random import randrange
+from common import *
 
-RING = 8 # ring size
+# Spend proof
+class SpendProof:
+    def __init__(self):
+        self.A = None
+        self.B = None
+        self.S1 = None
+        self.S2 = None
+        self.S3 = None
+        self.T1 = None
+        self.T2 = None
+        self.tau_x = None
+        self.mu = None
+        self.z_a = None
+        self.z_sk = None
+        self.z_d = None
+        self.l = None
+        self.r = None
+        self.t = None
+        self.P = None
+        self.U1 = None
 
-# Generators
-Gc = hash_to_point('Gc')
-Hc = hash_to_point('Hc')
-U = hash_to_point('U')
-G0 = hash_to_point('G0')
-Hi = []
-for i in range(RING):
-    Hi.append(hash_to_point('Hi',i))
-
-k = randrange(RING) # signing index
-a = random_scalar() # input value
-kappa = random_scalar() # input mask
-delta = random_scalar() # input offset
-
-# Set ring and commitments
-print 'Preparing ring with',RING,'members...'
-pk = []
-C_in = []
-for i in range(RING):
-    pk.append(random_point())
-    C_in.append(random_point())
-
-sk = random_scalar() # signing key
-pk[k] = sk*G
-C_in[k] = a*Hc + kappa*Gc # input commitment
-C1 = C_in[k] - delta*Gc # offset commitment
-
-# Key image
-U1 = sk.invert()*U
-
-# Final ring
-Y = []
-temp = repr(pk) + repr(C_in) + repr(C1)
-d1 = hash_to_scalar(1,temp)
-d2 = hash_to_scalar(2,temp)
-for i in range(RING):
-    Y.append(pk[i] + d1*(C_in[i]-C1) + d2*G0)
-
-# Check spend index construction
-print 'Checking ring...'
-assert Y[k] == sk*G + (d1*delta)*Gc + d2*G0
-
-# Prepare signer index
-print 'Proving...'
-bL = ScalarVector([Scalar(0)]*RING)
-bL[k] = Scalar(1)
-bR = ScalarVector([])
-for i in range(RING):
[…]

### 2019-07-22 rct3/transaction.py

@@ -5,6 +5,7 @@ from dumb25519 import *
 import elgamal
 import signature
 import pybullet
+import spend
 
 class Coin:
     # Generate a new coin
@@ -103,11 +104,11 @@ class MintTransaction:
 
         # Prove the committed value is valid
         mask = hash_to_scalar('mask',hash_to_scalar(r*X2,1))
-        self.proof = signature.sign(hash_to_scalar(self.coin),mask,G)
+        self.proof = signature.sign(hash_to_scalar(self.coin),mask,Gc)
 
     # Verify the mint operation
     def verify(self):
-        signature.verify(hash_to_scalar(self.coin),self.coin.C-self.v*H,self.proof,G)
+        signature.verify(hash_to_scalar(self.coin),self.coin.C-self.v*Hc,self.proof,Gc)
 
     # Recover the minted coin
     #
@@ -126,9 +127,11 @@ class SpendTransaction:
     #   dest: list of destination addresses (each a list)
     #   v: list of output coin values
     # DATA
-    #   coins: output coins
+    #   coins_in: input coins
+    #   coins_out: output coins
+    #   C1: commitment offset
     #   range: aggregate range proof
-    #   spend: spend proof
+    #   spend_proof: spend proof
     #   bal_c: balance proof c
     #   bal_z: balance proof z
     def __init__(self,coins,l,dest,v):
@@ -141,33 +144,38 @@ class SpendTransaction:
             raise ValueError('No output coins specified!')
         if not len(dest) == len(v):
             raise TypeError('Destination/value mismatch!')
+        
+        self.coins_in = coins
 
         # Generate output coins
-        self.coins = []
+        self.coins_out = []
         r = [] # output coin masks
         for i in range(len(dest)):
             r.append(random_scalar())
-            self.coins.append(Coin(v[i],dest[i][0],dest[i][1],r[i],i))
+            self.coins_out.append(Coin(v[i],dest[i][0],dest[i][1],r[i],i))
 
         # Generate range proof
-        self.range = pybullet.prove([[v[i],self.coins[i].mask] for i in range(len(dest))],BITS)
+        self.range = pybullet.prove([[v[i],self.coins_out[i].mask] for i in range(len(dest))],BITS)
 
         # Offset input coin
         delta = random_scalar()
-        C1 = coins[l].C - delta*G
[…]

### 2019-07-22 rct3/transaction.py
Updated spend operation to support multiple inputs, balance verification, and range verification

@@ -122,60 +122,91 @@ class SpendTransaction:
     # Spend a coin
     #
     # INPUTS
-    #   coins: list of coins (spend and decoys)
-    #   l: spend index (corresponding coin must be recovered)
+    #   coins: list of coins (spends and decoys)
+    #   l: spend indices (corresponding coins must be recovered)
     #   dest: list of destination addresses (each a list)
     #   v: list of output coin values
     # DATA
     #   coins_in: input coins
     #   coins_out: output coins
-    #   C1: commitment offset
-    #   range: aggregate range proof
-    #   spend_proof: spend proof
+    #   C1: commitment offsets
+    #   range_proof: aggregate range proof
+    #   spend_proofs: spend proofs
     #   bal_c: balance proof c
     #   bal_z: balance proof z
-    def __init__(self,coins,l,dest,v):
+    def __init__(self,coins_in,l,dest,v):
         # Sanity checks
-        if not l < len(coins) or not l >= 0:
-            raise IndexError('Spent coin index out of bounds!')
-        if coins[l].p is None:
-            raise ValueError('Spent coin is not recovered!')
+        for i in l:
+            if not i < len(coins_in) or not i >= 0:
+                raise IndexError('Spent coin index out of bounds!')
+            if coins_in[i].p is None:
+                raise ValueError('Spent coin is not recovered!')
         if len(dest) == 0:
             raise ValueError('No output coins specified!')
         if not len(dest) == len(v):
             raise TypeError('Destination/value mismatch!')
         
-        self.coins_in = coins
-
         # Generate output coins
-        self.coins_out = []
+        coins_out = []
         r = [] # output coin masks
         for i in range(len(dest)):
             r.append(random_scalar())
-            self.coins_out.append(Coin(v[i],dest[i][0],dest[i][1],r[i],i))
+            coins_out.append(Coin(v[i],dest[i][0],dest[i][1],r[i],i))
 
         # Generate range proof
-        self.range = pybullet.prove([[v[i],self.coins_out[i].mask] for i in range(len(dest))],BITS)
[…]

### 2019-07-23 rct3/pybullet.py
Updated range proof generators

@@ -1,5 +1,6 @@
 import dumb25519
 from dumb25519 import Scalar, Point, ScalarVector, PointVector, random_scalar, random_point, hash_to_scalar, hash_to_point
+from common import *
 
 cache = '' # rolling transcript hash
 inv8 = Scalar(8).invert()
@@ -99,8 +100,6 @@ def prove(data,N):
     M = len(data)
 
     # curve points
-    G = dumb25519.G
-    H = hash_to_point('pybullet H')
     Gi = PointVector([hash_to_point('pybullet Gi ' + str(i)) for i in range(M*N)])
     Hi = PointVector([hash_to_point('pybullet Hi ' + str(i)) for i in range(M*N)])
 
@@ -108,7 +107,7 @@ def prove(data,N):
     V = PointVector([])
     aL = ScalarVector([])
     for v,gamma in data:
-        V.append((H*v + G*gamma)*inv8)
+        V.append(com(v,gamma)*inv8)
         mash(V[-1])
         aL.extend(scalar_to_bits(v,N))
 
@@ -118,12 +117,12 @@ def prove(data,N):
         aR.append(bit-Scalar(1))
 
     alpha = random_scalar()
-    A = (Gi*aL + Hi*aR + G*alpha)*inv8
+    A = (Gi*aL + Hi*aR + Gc*alpha)*inv8
 
     sL = ScalarVector([random_scalar()]*(M*N))
     sR = ScalarVector([random_scalar()]*(M*N))
     rho = random_scalar()
-    S = (Gi*sL + Hi*sR + G*rho)*inv8
+    S = (Gi*sL + Hi*sR + Gc*rho)*inv8
 
     # get challenges
     mash(A)
@@ -160,8 +159,8 @@ def prove(data,N):
 
     tau1 = random_scalar()
     tau2 = random_scalar()
-    T1 = (H*t1 + G*tau1)*inv8
-    T2 = (H*t2 + G*tau2)*inv8
+    T1 = com(t1,tau1)*inv8
+    T2 = com(t2,tau2)*inv8
 
     mash(T1)
     mash(T2)
@@ -186,7 +185,7 @@ def prove(data,N):
     R = PointVector([])
    
     # initial inner product inputs
-    data_ip = [Gi,PointVector([Hi[i]*(y_inv**i) for i in range(len(Hi))]),H*x_ip,l,r,None,None]
+    data_ip = [Gi,PointVector([Hi[i]*(y_inv**i) for i in range(len(Hi))]),Hc*x_ip,l,r,None,None]
[…]

### 2019-07-23 rct3/spend.py
Minor verification speedup

@@ -231,11 +231,11 @@ def verify(proof,pk,C_in,C1):
     data.append([proof.B,Scalar(1)])
     data.append([proof.A,w])
     data.append([proof.S2,x])
+    data.append([G0,-Scalar(RING)*z*d2])
     for i in range(RING):
         data.append([pk[i],-z])
         data.append([C_in[i],-z*d1])
         data.append([C1,z*d1])
-        data.append([G0,-z*d2])
         data.append([Hi[i],(w*z*y**i + z**2)*(y.invert()**i)])
     for i in range(len(data)):
         data[i][1] *= w3

### 2019-07-24 pybullet/pybullet.py
Updated comments

@@ -39,11 +39,9 @@ def decomp(val,size):
     return r
 
 # Perform an inner-product proof round
-# G,H: PointVector
-# U: Point
-# a,b: ScalarVector
 #
-# returns: G',H',U,a',b',L,R,aa,bb,P
+# INPUTS
+#   data: round data (InnerProductRound)
 def inner_product(data):
     n = len(data.G)
     if n == 1:

### 2019-07-24 pybullet/pybullet.py
Code restructuring and more robust Fiat-Shamir transcript

@@ -1,24 +1,52 @@
 import dumb25519
 from dumb25519 import Scalar, Point, ScalarVector, PointVector, random_scalar, random_point, hash_to_scalar, hash_to_point
+import transcript
 
-cache = '' # rolling transcript hash
 inv8 = Scalar(8).invert()
 
-# Add to a transcript hash
-def mash(s):
-    global cache
-    cache = hash_to_scalar(cache,s)
+# Proof structure
+class Bulletproof:
+    def __init__(self,V,A,S,T1,T2,taux,mu,L,R,a,b,t):
+        self.V = V
+        self.A = A
+        self.S = S
+        self.T1 = T1
+        self.T2 = T2
+        self.taux = taux
+        self.mu = mu
+        self.L = L
+        self.R = R
+        self.a = a
+        self.b = b
+        self.t = t
 
-# Clear the transcript hash
-def clear_cache():
-    global cache
-    cache = ''
+# Data for a round of the inner product argument
+class InnerProductRound:
+    def __init__(self,G,H,U,a,b,tr):
+        # Common data
+        self.G = G
+        self.H = H
+        self.U = U
+        self.done = False
+
+        # Prover data
+        self.a = a
+        self.b = b
+
+        # Verifier data (appended lists)
+        self.L = PointVector([])
+        self.R = PointVector([])
+
+        # Transcript
+        self.tr = tr
 
 # Turn a scalar into a vector of bit scalars
-# s: Scalar
-# N: int; number of bits
 #
-# returns: ScalarVector
+# INPUTS
+#   s: (Scalar)
+#   N: number of bits (int)
+# OUTPUTS
+#   ScalarVector
 def scalar_to_bits(s,N):
     result = []
     for i in range(N-1,-1,-1):
@@ -30,18 +58,22 @@ def scalar_to_bits(s,N):
     return ScalarVector(list(reversed(result)))
 
 # Generate a vector of powers of a scalar
-# s: Scalar
-# l: int; number of powers to include
 #
-# returns: ScalarVector
+# INPUTS
+#   s: (Scalar)
+#   l: number of powers to include (int)
+# OUTPUTS
+#   ScalarVector
 def exp_scalar(s,l):
     return ScalarVector([s**i for i in range(l)])
 
 # Sum the powers of a scalar
-# s: Scalar
[…]

### 2019-07-24 rct3/pybullet.py
Range proof library update

@@ -1,25 +1,53 @@
 import dumb25519
 from dumb25519 import Scalar, Point, ScalarVector, PointVector, random_scalar, random_point, hash_to_scalar, hash_to_point
 from common import *
+import transcript
 
-cache = '' # rolling transcript hash
 inv8 = Scalar(8).invert()
 
-# Add to a transcript hash
-def mash(s):
-    global cache
-    cache = hash_to_scalar(cache,s)
+# Proof structure
+class Bulletproof:
+    def __init__(self,V,A,S,T1,T2,taux,mu,L,R,a,b,t):
+        self.V = V
+        self.A = A
+        self.S = S
+        self.T1 = T1
+        self.T2 = T2
+        self.taux = taux
+        self.mu = mu
+        self.L = L
+        self.R = R
+        self.a = a
+        self.b = b
+        self.t = t
 
-# Clear the transcript hash
-def clear_cache():
-    global cache
-    cache = ''
+# Data for a round of the inner product argument
+class InnerProductRound:
+    def __init__(self,G,H,U,a,b,tr):
+        # Common data
+        self.G = G
+        self.H = H
+        self.U = U
+        self.done = False
+
+        # Prover data
+        self.a = a
+        self.b = b
+
+        # Verifier data (appended lists)
+        self.L = PointVector([])
+        self.R = PointVector([])
+
+        # Transcript
+        self.tr = tr
 
 # Turn a scalar into a vector of bit scalars
-# s: Scalar
-# N: int; number of bits
 #
-# returns: ScalarVector
+# INPUTS
+#   s: (Scalar)
+#   N: number of bits (int)
+# OUTPUTS
+#   ScalarVector
 def scalar_to_bits(s,N):
     result = []
     for i in range(N-1,-1,-1):
@@ -31,18 +59,22 @@ def scalar_to_bits(s,N):
     return ScalarVector(list(reversed(result)))
 
 # Generate a vector of powers of a scalar
-# s: Scalar
-# l: int; number of powers to include
 #
-# returns: ScalarVector
+# INPUTS
+#   s: (Scalar)
+#   l: number of powers to include (int)
+# OUTPUTS
+#   ScalarVector
 def exp_scalar(s,l):
     return ScalarVector([s**i for i in range(l)])
 
 # Sum the powers of a scalar
-# s: Scalar
[…]

### 2019-07-24 pybullet/transcript.py
Transcript requires a prefix

@@ -3,8 +3,8 @@
 from dumb25519 import *
 
 class Transcript:
-    # Initialize the transcript, optionally with a fixed prefix
-    def __init__(self,prefix=None):
+    # Initialize the transcript
+    def __init__(self,prefix):
         self.state = hash_to_scalar(prefix)
 
     # Update the transcript with public data

### 2019-07-26 dumb25519/test.py
Hex encoding and decoding

@@ -3,6 +3,38 @@
 from dumb25519 import *
 import unittest
 
+class TestEncoding(unittest.TestCase):
+    def test_G(self):
+        self.assertEqual(repr(G),'5866666666666666666666666666666666666666666666666666666666666666')
+        self.assertEqual(Point('5866666666666666666666666666666666666666666666666666666666666666'),G)
+
+    def test_Z(self):
+        self.assertEqual(repr(Z),'0100000000000000000000000000000000000000000000000000000000000000')
+        self.assertEqual(Point('0100000000000000000000000000000000000000000000000000000000000000'),Z)
+
+    def test_0(self):
+        self.assertEqual(repr(Scalar(0)),'0000000000000000000000000000000000000000000000000000000000000000')
+        self.assertEqual(Scalar('0000000000000000000000000000000000000000000000000000000000000000'),Scalar(0))
+
+    def test_1(self):
+        self.assertEqual(repr(Scalar(1)),'0100000000000000000000000000000000000000000000000000000000000000')
+        self.assertEqual(Scalar('0100000000000000000000000000000000000000000000000000000000000000'),Scalar(1))
+
+    def test_8(self):
+        eight = Scalar('0800000000000000000000000000000000000000000000000000000000000000')
+        inv_8 = Scalar('792fdce229e50661d0da1c7db39dd30700000000000000000000000000000006')
+        self.assertEqual(eight*inv_8,Scalar(1))
+
+    def test_keys(self):
+        tests = []
+        tests.append(['1ad5f2d49b9a9aff87a178e34dd676b92560ce1c17ef581101403d86d3e0420a','2c173a515d472f4088f3716bb4ae7ded9c8a116811767028b41ac11189d52930'])
+        tests.append(['925ca4f809e42f9adb719c0561681d529d579cbb800c88485606df0f69f86c0a','c1cae3aedde97856d20b3a1a475ea14fc6726ec365d084019e62cb45e6881b46'])
+        tests.append(['ec683df871ccdb1c6b0bb0f8170db4bce5f54e6f66946c05b32c2a6c510d2807','16d3b58656c049dcdd7fa53d6d6c4d9be6420498095d3eceffd568fe612fa488'])
+
+        for test in tests:
+            self.assertEqual(Scalar(test[0])*G,Point(test[1]))
+            self.assertEqual(repr(Scalar(test[0])*G),test[1])
+
 class TestPoint(unittest.TestCase):
[…]

### 2019-07-26 hashes/dumb25519.py
Curve library update

@@ -6,11 +6,13 @@
 
 import random
 import hashlib
+import binascii
 
 # curve parameters
 q = 2**255 - 19
 l = 2**252 + 27742317777372353535851937790883648493
 cofactor = 8
+b = 256 # bit representation
 
 # Internal helper methods
 def exponent(b,e,m):
@@ -28,14 +30,26 @@ def xfromy(y):
         x = q-x
     return x
 
+def bit(h,i):
+    return (ord(h[i/8]) >> (i%8)) & 1
+
 d = -121665 * invert(121666,q)
 I = exponent(2,(q-1)/4,q)
 
 class Scalar:
     def __init__(self,x):
-        if not isinstance(x,int) and not isinstance(x,long):
+        # Generated from an integer value
+        if isinstance(x,int) or isinstance(x,long):
+            self.x = x % l
+        # Generated from a hex representation
+        elif isinstance(x,str):
+            try:
+                x = binascii.unhexlify(x)
+                self.x = sum(2**i * bit(x,i) for i in range(0,b)) % l
+            except:
+                raise TypeError
+        else:
             raise TypeError
-        self.x = x % l
 
     def invert(self):
         if self.x == 0:
@@ -106,7 +120,8 @@ class Scalar:
         raise TypeError
 
     def __repr__(self):
-        return '<Scalar> x:'+str(self.x)
+        bits = [(self.x >> i) & 1 for i in range(b)]
+        return binascii.hexlify(''.join([chr(sum([bits[i*8+j] << j for j in range(8)])) for i in range(b/8)]))
 
     def __int__(self):
         return self.x
@@ -122,13 +137,20 @@ class Scalar:
         return Scalar(-self.x)
 
 class Point:
-    def __init__(self,x,y):
-        if not isinstance(x,long) and not isinstance(x,int):
+    def __init__(self,x,y=None):
+        # Generated from integer values
+        if (isinstance(x,long) or isinstance(x,int)) and (isinstance(y,long) or isinstance(y,int)) and y is not None:
+            self.x = x
+            self.y = y
+        # Generated from a hex representation
+        elif isinstance(x,str) and y is None:
+            x = binascii.unhexlify(x)
+            self.y = sum(2**i * bit(x,i) for i in range(0,b-1))
+            self.x = xfromy(self.y)
+            if self.x & 1 != bit(x,b-1):
+                self.x = q - self.x
+        else:
             raise TypeError
[…]

### 2019-07-26 image/clsag.py

@@ -1,139 +1,0 @@
-# Mixed CLSAG: Compressed Linkable Spontaneous Anonymous Group signatures
-# https://github.com/monero-project/research-lab/issues/52
-#
-# For a ring with members of the form (P_i,C_i) such that (P_l,C_l) = (p*G,z*G)
-# for some index l, generates a linkable ring signature on a message such that
-# any public key is equiprobable as corresponding to the signing key.
-#
-# Two valid signatures containing the same key image were signed with the same
-# private key, regardless of the other ring members used in the signature.
-
-import dumb25519
-from dumb25519 import hash_to_scalar, hash_to_point, random_scalar, G
-
-# Constants
-TYPE_LEGACY = 0
-TYPE_NEW = 1
-H = hash_to_point('clsag H')
-
-# CLSAG signature
-class Signature:
-    h0 = None
-    s = None
-    I = None
-    D = None
-
-# Generate a CLSAG signature
-# INPUTS
-#   M: message
-#   p: private key
-#   P: public key vector
-#   t: key type vector
-#   z: commitment private key
-#   C: commitment vector
-#   index: if set, bypass key index check (testing only)
-# RETURNS
-#   sig: Signature
-# RAISES
-#   IndexError if index is not set and private keys are invalid
-def sign(M,p,P,t,z,C,index=None):
-    n = len(P) # ring size
-
-    # Recover the private key index
-    l = None
-    if index is not None:
-        l = index
-    else:
-        for i in range(n):
-            if P[i] == G*p and C[i] == G*z:
-                l = i
-                break
-        if l is None:
-            raise IndexError('Private keys must correspond to public keys!')
-
-    # Construct key images
-    if t[l] == TYPE_LEGACY:
-        I = hash_to_point(P[l])*p
-        D = hash_to_point(P[l])*z
-    else:
-        I = H*p
-        D = H*z
-
-    # Now generate the signature
-    mu_P = hash_to_scalar(0,P,I,C,D)
-    mu_C = hash_to_scalar(1,P,I,C,D)
-    h = [None]*n
-    alpha = random_scalar()
-    s = [random_scalar()]*n
-
-    # Private index
[…]

### 2019-07-26 image/dumb25519.py

@@ -1,449 +1,0 @@
-# Dumb25519: a stupid implementation of ed25519
-#
-# Use this code only for prototyping
-# -- putting this code into production would be dumb
-# -- assuming this code is secure would also be dumb
-
-import random
-import hashlib
-
-# curve parameters
-q = 2**255 - 19
-l = 2**252 + 27742317777372353535851937790883648493
-cofactor = 8
-
-# Internal helper methods
-def exponent(b,e,m):
-    return pow(b,e,m)
-
-def invert(x,n):
-    return exponent(x,n-2,n)
-
-def xfromy(y):
-    temp = (y*y-1) * invert(d*y*y+1,q)
-    x = exponent(temp,(q+3)/8,q)
-    if (x*x - temp) % q != 0:
-        x = (x*I) % q
-    if x % 2 != 0:
-        x = q-x
-    return x
-
-d = -121665 * invert(121666,q)
-I = exponent(2,(q-1)/4,q)
-
-class Scalar:
-    def __init__(self,x):
-        if not isinstance(x,int) and not isinstance(x,long):
-            raise TypeError
-        self.x = x % l
-
-    def invert(self):
-        if self.x == 0:
-            raise ZeroDivisionError
-        return Scalar(invert(self.x,l))
-
-    def __add__(self,y):
-        if isinstance(y,int):
-            return Scalar(self.x + y)
-        if isinstance(y,Scalar):
-            return Scalar(self.x + y.x)
-        return NotImplemented
-
-    def __sub__(self,y):
-        if isinstance(y,int):
-            return Scalar(self.x - y)
-        if isinstance(y,Scalar):
-            return Scalar(self.x - y.x)
-        return NotImplemented
-
-    def __mul__(self,y):
-        if isinstance(y,int):
-            return Scalar(self.x * y)
-        if isinstance(y,Scalar):
-            return Scalar(self.x * y.x)
-        return NotImplemented
-
-    def __div__(self,y):
-        if isinstance(y,int):
-            return Scalar(self.x / y)
-        if isinstance(y,Scalar):
-            return Scalar(self.x / y.x)
-        raise NotImplemented
-
-    def __pow__(self,y):
-        if not isinstance(y,int):
-            return NotImplemented
-        return Scalar(self.x**y)
-
-    def __eq__(self,y):
-        if isinstance(y,Scalar):
-            return self.x == y.x
-        raise TypeError
-
-    def __ne__(self,y):
[…]

### 2019-07-26 image/test.py

@@ -1,314 +1,0 @@
-# Basic test suite for CLSAG
-
-import dumb25519
-from dumb25519 import *
-import clsag
-from clsag import *
-import unittest
-
-class TestValidSignatures(unittest.TestCase):
-    def test_n_1(self):
-        p = random_scalar()
-        P = [G*p]
-        t = [TYPE_NEW]
-        z = random_scalar()
-        C = [G*z]
-        M = 'Test message'
-        
-        sig = sign(M,p,P,t,z,C)
-        verify(M,P,t,C,sig)
-
-    def test_n_2_l_0(self):
-        p = random_scalar()
-        P = [G*p,random_point()]
-        t = [TYPE_NEW,TYPE_NEW]
-        z = random_scalar()
-        C = [G*z,random_point()]
-        M = 'Test message'
-        
-        sig = sign(M,p,P,t,z,C)
-        verify(M,P,t,C,sig)
-
-    def test_n_2_l_0_mixed(self):
-        p = random_scalar()
-        P = [G*p,random_point()]
-        t = [TYPE_LEGACY,TYPE_NEW]
-        z = random_scalar()
-        C = [G*z,random_point()]
-        M = 'Test message'
-        
-        sig = sign(M,p,P,t,z,C)
-        verify(M,P,t,C,sig)
-
-    def test_n_2_l_0_mixed_2(self):
-        p = random_scalar()
-        P = [G*p,random_point()]
-        t = [TYPE_NEW,TYPE_LEGACY]
-        z = random_scalar()
-        C = [G*z,random_point()]
-        M = 'Test message'
-        
-        sig = sign(M,p,P,t,z,C)
-        verify(M,P,t,C,sig)
-
-    def test_n_2_l_1(self):
-        p = random_scalar()
-        P = [random_point(),G*p]
-        t = [TYPE_NEW,TYPE_NEW]
-        z = random_scalar()
-        C = [random_point(),G*z]
-        M = 'Test message'
-        
-        sig = sign(M,p,P,t,z,C)
-        verify(M,P,t,C,sig)
-
-    def test_n_2_l_1_mixed(self):
-        p = random_scalar()
-        P = [random_point(),G*p]
-        t = [TYPE_LEGACY,TYPE_NEW]
-        z = random_scalar()
-        C = [random_point(),G*z]
-        M = 'Test message'
-        
-        sig = sign(M,p,P,t,z,C)
-        verify(M,P,t,C,sig)
-
-    def test_n_2_l_1_mixed_2(self):
-        p = random_scalar()
[…]

### 2019-07-26 pybullet/dumb25519.py
Curve library update

@@ -6,11 +6,13 @@
 
 import random
 import hashlib
+import binascii
 
 # curve parameters
 q = 2**255 - 19
 l = 2**252 + 27742317777372353535851937790883648493
 cofactor = 8
+b = 256 # bit representation
 
 # Internal helper methods
 def exponent(b,e,m):
@@ -28,14 +30,26 @@ def xfromy(y):
         x = q-x
     return x
 
+def bit(h,i):
+    return (ord(h[i/8]) >> (i%8)) & 1
+
 d = -121665 * invert(121666,q)
 I = exponent(2,(q-1)/4,q)
 
 class Scalar:
     def __init__(self,x):
-        if not isinstance(x,int) and not isinstance(x,long):
+        # Generated from an integer value
+        if isinstance(x,int) or isinstance(x,long):
+            self.x = x % l
+        # Generated from a hex representation
+        elif isinstance(x,str):
+            try:
+                x = binascii.unhexlify(x)
+                self.x = sum(2**i * bit(x,i) for i in range(0,b)) % l
+            except:
+                raise TypeError
+        else:
             raise TypeError
-        self.x = x % l
 
     def invert(self):
         if self.x == 0:
@@ -106,7 +120,8 @@ class Scalar:
         raise TypeError
 
     def __repr__(self):
-        return '<Scalar> x:'+str(self.x)
+        bits = [(self.x >> i) & 1 for i in range(b)]
+        return binascii.hexlify(''.join([chr(sum([bits[i*8+j] << j for j in range(8)])) for i in range(b/8)]))
 
     def __int__(self):
         return self.x
@@ -122,13 +137,20 @@ class Scalar:
         return Scalar(-self.x)
 
 class Point:
-    def __init__(self,x,y):
-        if not isinstance(x,long) and not isinstance(x,int):
+    def __init__(self,x,y=None):
+        # Generated from integer values
+        if (isinstance(x,long) or isinstance(x,int)) and (isinstance(y,long) or isinstance(y,int)) and y is not None:
+            self.x = x
+            self.y = y
+        # Generated from a hex representation
+        elif isinstance(x,str) and y is None:
+            x = binascii.unhexlify(x)
+            self.y = sum(2**i * bit(x,i) for i in range(0,b-1))
+            self.x = xfromy(self.y)
+            if self.x & 1 != bit(x,b-1):
+                self.x = q - self.x
+        else:
             raise TypeError
[…]

### 2019-07-26 pybullet/pybullet.py

@@ -1,5 +1,10 @@
 import dumb25519
 from dumb25519 import Scalar, Point, ScalarVector, PointVector, random_scalar, random_point, hash_to_scalar, hash_to_point
+import random
+
+# Set random seed
+def set_seed(seed):
+    random.seed(seed)
 
 cache = '' # rolling transcript hash
 inv8 = Scalar(8).invert()
@@ -157,7 +162,7 @@ def inner_product(data):
 # returns: ProofA object
 def prove_A(v,gamma,k,seed=None):
     if seed is not None:
-        dumb25519.set_seed(seed)
+        set_seed(seed)
 
     # internal state
     state = PlayerState()
@@ -210,7 +215,7 @@ def prove_A(v,gamma,k,seed=None):
 # returns: ProofB object
 def prove_B(state,y,z,seed=None):
     if seed is not None:
-        dumb25519.set_seed(seed)
+        set_seed(seed)
 
     # check for bad challenges
     if y == Scalar(0) or z == Scalar(0):
@@ -270,7 +275,7 @@ def prove_B(state,y,z,seed=None):
 # returns: ProofC object
 def prove_C(state,x,seed=None):
     if seed is not None:
-        dumb25519.set_seed(seed)
+        set_seed(seed)
 
     # check for bad challenge
     if x == Scalar(0):

### 2019-07-26 pybullet/test.py

@@ -258,7 +258,7 @@ class TestKnownProofs(unittest.TestCase):
         gamma = Scalar(23579) # abitrary commitment blinder
         pybullet.N = 2
 
-        dumb25519.set_seed(seed)
+        pybullet.set_seed(seed)
         alpha = random_scalar()
         sL = ScalarVector([random_scalar()]*pybullet.N)
         sR = ScalarVector([random_scalar()]*pybullet.N)
@@ -279,7 +279,7 @@ class TestKnownProofs(unittest.TestCase):
 
         # B-proof
         seed = 2 # arbitrary
-        dumb25519.set_seed(seed)
+        pybullet.set_seed(seed)
         y = Scalar(8675309) # arbitrary nonzero challenge
         z = Scalar(3141592) # arbitrary nonzero challenge
 
@@ -302,7 +302,7 @@ class TestKnownProofs(unittest.TestCase):
 
         # C-proof
         seed = 3 # arbitrary
-        dumb25519.set_seed(seed)
+        pybullet.set_seed(seed)
         x = Scalar(2718281) # arbitrary nonzero challenge
 
         taux = tau2*x**2 + tau1*x + z**2*gamma

### 2019-07-26 paper/iacr.tex
Updates to CLSAG paper

@@
 
-\item[Correctly linkable:] For any messages $m$, $m^\prime$, any $d$-dimensional secret keys  $\textbf{sk}$ and $\textbf{sk}^\prime$ with equal linking keys (that is, with $\textbf{sk}_0 = \textbf{sk}^\prime_0$) and with corresponding public keys $\textbf{pk}$ and $\textbf{pk}^\prime$ respectively, any appropriately-sized pair of matrices $\underline{\textbf{pk}}$ and $\underline{\textbf{pk}}^\prime$, if $(\sigma, \mathfrak{T}) \leftarrow \texttt{Sign}(m, \underline{\textbf{pk}}, \textbf{sk})$ and $(\sigma^\prime, \mathfrak{T}^\prime) \leftarrow \texttt{Sign}(m^\prime, \underline{\textbf{pk}}^\prime, \textbf{sk}^\prime)$ and there exists a pair of indices $\ell$ and $\ell^\prime$ such that $\underline{\textbf{pk}}_\ell = \textbf{pk}$ and $\underline{\textbf{pk}}_{\ell^\prime} = \textbf{pk}^\prime$, then
+\item[Correctly linkable:] For any messages $m$, $m^\prime$, any $d$-dimensional secret keys  $\textbf{sk}$ and $\textbf{sk}^\prime$ with equal linking keys (that is, with $\textbf{sk}_0 = \textbf{sk}^\prime_0$) and with corresponding public keys $\textbf{pk}$ and $\textbf{pk}^\prime$ respectively, any appropriately-sized pair of matrices $\underline{\textbf{pk}}$ and $\underline{\textbf{pk}}^\prime$, if $(\sigma, \mathfrak{T}) \leftarrow \texttt{Sign}(m, \underline{\textbf{pk}}, \textbf{sk})$ and $(\sigma^\prime, \mathfrak{T}^\prime) \leftarrow \texttt{Sign}(m^\prime, \underline{\textbf{pk}}^\prime, \textbf{sk}^\prime)$ such that $\underline{\textbf{pk}}_\ell = \textbf{pk}$ and $\underline{\textbf{pk}}_{\ell^\prime} = \textbf{pk}^\prime$, then
 $\texttt{Link}((\sigma, \mathfrak{T}), (\sigma^\prime, \mathfrak{T}^\prime))=1$.
@@
 \mathfrak{T} \leftarrow& x \mathcal{H}^p(X_\ell) & \mu_X \leftarrow& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}) \\
-\{\mathfrak{D}_j\} \leftarrow&  \{z_j \mathcal{H}^p(X_\ell)\} & \mu_j \leftarrow& \mathcal{H}^s_1(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}).
+\{\mathfrak{D}_j\} \leftarrow&  \{z_j \mathcal{H}^p(X_\ell)\} & \mu_j \leftarrow& \mathcal{H}^s_j(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}).
 \end{align*}
@@
 Let $\mathcal{H}^s:\left\{0,1\right\}^* \to \mathbb{Z}/p\mathbb{Z}$ be modeled as a random oracle.
-Let $\mathcal{CO}$ be a corruption oracle that takes as input a public key $\textbf{pk}$ and produces as output the corresponding secret key $\textbf{sk}$ and the linkability tag $\mathfrak{T}$.
+Let $\mathcal{CO}$ be a corruption oracle that takes as input a public key $\textbf{pk}$ from the list of challenge keys and produces as output the corresponding secret key $\textbf{sk}$ and the linkability tag $\mathfrak{T}$.
 Let $C$ be the set of all keys in the transcript of queries made by $\texttt{A}$ to $\mathcal{CO}$.
 Let $T_C$ be the set of all linkability tags that appear as output from such a query.
-Let $\mathcal{SO}$ be a signing oracle that takes as input some $(m, \underline{\textbf{pk}}^\prime, \ell)$ such that $pk_\ell \in \underline{\textbf{pk}} \cap \underline{\textbf{pk}^\prime}$ and produces as output a signature-tag pair $(\sigma, \mathfrak{T})$ such that $\texttt{Verify}(m, \underline{\textbf{pk}}^\prime, \sigma, \mathfrak{T}) = 1$.
+Let $\mathcal{SO}$ be a signing oracle that takes as input some $(m, \underline{\textbf{pk}}^\prime, \ell)$ such that $\underline{\textbf{pk}^\prime}$ is a matrix of challenge key vectors (i.e.\ each column is in $\textbf{pk}$) and produces as output a signature-tag pair $(\sigma, \mathfrak{T})$ such that $\texttt{Verify}(m, \underline{\textbf{pk}}^\prime, \sigma, \mathfrak{T}) = 1$ and $\mathfrak{T}$ is the linkability tag for the $\ell^{th}$ key in $\underline{\textbf{pk}}^\prime$.
 
@@
 If the attacker can produce a new signature $\sigma^\prime$ on a message that has been signed before by the oracle then the new signature should still count as a forgery.
+
+\begin{remark}
+Note that if the corruption oracle merely acted by computing arbitrary discrete logarithms, then an adversary could do the following: take some target $\textbf{pk}$ from the challenge set, apply a permutation to the coordinates of $\textbf{pk}$, pass the permuted key through $\mathcal{CO}$, obtain the discrete logarithm of the first (signing) key of $\textbf{pk}$, compute the linkability tag for this signing key, and lastly produce a signature using $\texttt{Sign}$.
+
+Such a signature would pass validation and not be described as a forgery according to our definition.
+Our definition avoids this problem by requiring the corruption oracle only be queried with challenge keys.
+This way, a corruption oracle can be simulated for the black box execution of $\texttt{A}$.
+\end{remark}
 
@@
 
-\begin{defn}[Decisional Diffie-Hellman]\label{ddhgame} Let $\texttt{A}$ be any computationally unbounded PPT algorithm, $(p, \mathbb{G}, G)$ and let $n \in \mathbb{N}$.
+\begin{defn}[Decisional Diffie-Hellman]\label{ddhgame} Let $\texttt{A}$ be any PPT algorithm, $(p, \mathbb{G}, G)$ and let $n \in \mathbb{N}$.
 \begin{enumerate}

### 2019-07-29 rct3/common.py
Initial work on inner product argument

@@ -12,6 +12,7 @@ Gc = hash_to_point('Gc') # commitment generator
 Hc = hash_to_point('Hc') # commitment generator
 U = hash_to_point('U')
 G0 = hash_to_point('G0')
+G_ip = hash_to_point('G_ip')
 Hi = []
 for i in range(RING):
     Hi.append(hash_to_point('Hi',i))
@@ -22,3 +23,12 @@ for i in range(RING):
 #   a: mask
 def com(v,a):
     return v*Hc + a*Gc
+
+# Determine if a value is a power of 2
+#
+# INPUTS
+#   x: value (int)
+# OUTPUTS
+#   True if x is a power of 2
+def power2(x):
+    return x > 0 and (x & (x-1)) == 0

### 2019-07-29 rct3/dumb25519.py

@@ -6,11 +6,13 @@
 
 import random
 import hashlib
+import binascii
 
 # curve parameters
 q = 2**255 - 19
 l = 2**252 + 27742317777372353535851937790883648493
 cofactor = 8
+b = 256 # bit representation
 
 # Internal helper methods
 def exponent(b,e,m):
@@ -28,14 +30,26 @@ def xfromy(y):
         x = q-x
     return x
 
+def bit(h,i):
+    return (ord(h[i/8]) >> (i%8)) & 1
+
 d = -121665 * invert(121666,q)
 I = exponent(2,(q-1)/4,q)
 
 class Scalar:
     def __init__(self,x):
-        if not isinstance(x,int) and not isinstance(x,long):
+        # Generated from an integer value
+        if isinstance(x,int) or isinstance(x,long):
+            self.x = x % l
+        # Generated from a hex representation
+        elif isinstance(x,str):
+            try:
+                x = binascii.unhexlify(x)
+                self.x = sum(2**i * bit(x,i) for i in range(0,b)) % l
+            except:
+                raise TypeError
+        else:
             raise TypeError
-        self.x = x % l
 
     def invert(self):
         if self.x == 0:
@@ -106,7 +120,8 @@ class Scalar:
         raise TypeError
 
     def __repr__(self):
-        return '<Scalar> x:'+str(self.x)
+        bits = [(self.x >> i) & 1 for i in range(b)]
+        return binascii.hexlify(''.join([chr(sum([bits[i*8+j] << j for j in range(8)])) for i in range(b/8)]))
 
     def __int__(self):
         return self.x
@@ -122,13 +137,20 @@ class Scalar:
         return Scalar(-self.x)
 
 class Point:
-    def __init__(self,x,y):
-        if not isinstance(x,long) and not isinstance(x,int):
+    def __init__(self,x,y=None):
+        # Generated from integer values
+        if (isinstance(x,long) or isinstance(x,int)) and (isinstance(y,long) or isinstance(y,int)) and y is not None:
+            self.x = x
+            self.y = y
+        # Generated from a hex representation
+        elif isinstance(x,str) and y is None:
+            x = binascii.unhexlify(x)
+            self.y = sum(2**i * bit(x,i) for i in range(0,b-1))
+            self.x = xfromy(self.y)
+            if self.x & 1 != bit(x,b-1):
+                self.x = q - self.x
+        else:
             raise TypeError
[…]

### 2019-07-29 rct3/pybullet.py

@@ -211,9 +211,6 @@ def prove(data,N):
     tr.update(t)
     x_ip = tr.challenge()
 
-    L = PointVector([])
-    R = PointVector([])
-   
     # initial inner product inputs
     data = InnerProductRound(Gi,PointVector([Hi[i]*(y_inv**i) for i in range(len(Hi))]),Hc*x_ip,l,r,tr)
     while True:

### 2019-07-29 rct3/spend.py

@@ -17,11 +17,60 @@ class SpendProof:
         self.z_a = None
         self.z_sk = None
         self.z_d = None
-        self.l = None
-        self.r = None
+        self.L = None
+        self.R = None
+        self.a = None
+        self.b = None
         self.t = None
-        self.P = None
         self.U1 = None
+
+# Data for a round of the inner product argument
+class InnerProductRound:
+    def __init__(self,G,H,U,a,b,tr):
+        # Common data
+        self.G = G
+        self.H = H
+        self.U = U
+        self.done = False
+
+        # Prover data
+        self.a = a
+        self.b = b
+
+        # Verifier data (appended lists)
+        self.L = PointVector([])
+        self.R = PointVector([])
+
+        # Transcript
+        self.tr = tr
+
+# Perform an inner-product proof round
+#
+# INPUTS
+#   data: round data (InnerProductRound)
+def inner_product(data):
+    n = len(data.G)
+    if n == 1:
+        data.done = True
+        data.a = data.a[0]
+        data.b = data.b[0]
+        return
+
+    n /= 2
+    cL = data.a[:n]**data.b[n:]
+    cR = data.a[n:]**data.b[:n]
+    data.L.append(data.G[n:]*data.a[:n] + data.H[:n]*data.b[n:] + data.U*cL)
+    data.R.append(data.G[:n]*data.a[n:] + data.H[n:]*data.b[:n] + data.U*cR)
+
+    data.tr.update(data.L[-1])
+    data.tr.update(data.R[-1])
+    x = data.tr.challenge()
+
+    data.G = (data.G[:n]*x.invert())*(data.G[n:]*x)
+    data.H = (data.H[:n]*x)*(data.H[n:]*x.invert())
+
+    data.a = data.a[:n]*x + data.a[n:]*x.invert()
+    data.b = data.b[:n]*x.invert() + data.b[n:]*x
 
 # Generate a spend proof
 #
@@ -39,6 +88,8 @@ def prove(pk,C_in,k,a,kappa,delta,sk):
     # Sanity checks
     if not len(pk) == RING or not len(C_in) == RING:
         raise IndexError('Bad input ring size!')
+    if not power2(RING):
+        raise IndexError('Bad input ring size!')
 
     # Begin transcript
[…]

### 2019-09-24 paper/mrl.tex
Updates to CLSAG paper

--- 2019-06-03 paper/mrl.tex
@@
 \newtheorem{example}{Example}[section]
-\newtheorem{defn}{Definition}[section]
-\newtheorem{assu}{Assumption}[section]
+\newtheorem{definition}{Definition}[section]
 
 \title{Compact linkable ring signatures and applications}
-\authors{Brandon Goodell\footnote{\texttt{surae.noether@protonmail.com}} and Sarang Noether\footnote{\texttt{sarang.noether@protonmail.com}} and \texttt{RandomRun}}
-\affiliations{Monero Research Lab}
+\authors{Brandon Goodell\footnote{\texttt{surae.noether@protonmail.com}} and Sarang Noether\footnote{\texttt{sarang.noether@protonmail.com}} and Arthur Blue\footnote{\texttt{randomrun@protonmail.com}}}
+\affiliations{Monero Research Lab, independent researcher}
 \date{\today}
@@
 \begin{abstract}
-We describe an efficient linkable ring signature scheme, compact linkable spontaneous anonymous group (CLSAG) signatures, for use in confidential transactions.
-Compared to the existing signature scheme used in Monero, CLSAG signatures are both smaller and more efficient to generate and verify for ring sizes of interest.
-We generalize the construction and show how it can be used to produce signatures with coins of different type in the same transaction.
+We introduce an efficient linkable ring multisignature construction, \textit{compact linkable spontaneous anonymous group} (CLSAG) signatures.
+These admit $d$-dimensional keys with a specified linking coordinate but do not have signature sizes directly proportional to $d$.
+Compared to existing constructions used for signer-ambiguous confidential transactions without trusted setup, CLSAG signatures are smaller and more efficient in terms of both proving and verification time.
+CLSAG signatures also satisfy some rigorous security definitions: unforgeability depends upon the $k$-OMDL hardness assumption, linkability depends on unforgeability as well as the collision resistance of key aggregation, and signer-ambiguity depends on the DDH assumption.
+We demonstrate an application for CLSAG signatures for use in transacting multiple assets over ring signature-based transaction protocols.
 \end{abstract}
@@
 \section{Introduction}
-Ring signatures are used in Monero to provide transaction signer ambiguity.
-Originally, a simple Schnorr-like linkable ring signature \cite{liu2004linkable} was used that included previous one-time output public keys as possible signers.
-Later, the addition of Pedersen commitments to hide amounts necessitated a generalization to the signature \cite{noether2016ring} in order to prove transaction balance without revealing the signer.
+First introduced in \cite{rivest} in the RSA setting and in \cite{liu} in the discrete logarithm setting, ring signatures permit a non-interactive signature on behalf of a set of public keys rather than a single public key.
+Ring signatures see myriad applications ranging from lightweight anonymous authentication as in \cite{yang2015lightweight} to transaction protocols like Monero in \cite{noether} and CryptoNote in \cite{van2013cryptonote}.
+A verifier is assured that the signer knows the private key of at least one of these public keys, which are called ring members.
+Ring signatures are \textit{signer-ambiguous} by nature because the verifier does not learn additional information from the signature about which key is the signer.
+We stress that methods of practical analysis such as those of  \cite{moser2018empirical,quesnelle2017linkability} can exploit metadata in real-life applications of signer-ambiguous protocols to reduce ambiguity.
 
-The current ring signature construction used in Monero, MLSAG signatures, scale linearly with the number of ring members included in the signature.
-In particular, they require the inclusion of two scalars per ring member.
+Group signature constructions preceding \cite{rivest,liu} require some degree of interactivity, a fixed set of participants, a trusted group manager (or some other trusted setup), or hardness assumptions not based on the discrete logarithm problem.
+Since \cite{rivest}, ring signatures have enjoyed many improvements, expansions, and modifications.
+An incomplete list of examples includes: ring signatures are constructed in the bilinear pairing setting in \cite{zhang2002id}, key structures are generalized in \cite{abe20021}, security definitions are improved in \cite{bender}, signature size is improved in \cite{fujisaki2011sub,gu2018constant}, and traceability is introduced in \cite{fujisaki2007traceable}.
 
-We note that the MLSAG signature scheme, while general enough to permit linking across multiple sets of input keys, is in practice used as a hybrid approach to a linkable ring signature.
-Indeed, each signature input consists of two keys: the first is a standard one-time output public key, and the second is a key computed using the associated Pedersen commitments.
-Linkability is only used for the first key, to ensure that double-spending does not occur.
+Linkable ring signatures were first introduced in \cite{liu}; in the context of distributed ledgers like Monero, linkable ring signatures are the basis for signer-ambiguous transaction authentication.
+Linkable ring signatures guarantee that two signatures with the same ring on arbitrary messages can be publicly linked if signed using the same key.
+An implementation is presented in \cite{liu} in the discrete logarithm setting; that implementation functions for similar reasons as Schnorr signatures in \cite{schnorr1991efficient}.
 
-This construction is flexible.
-For example, the format can be used for usual ring confidential transactions or could be modified to describe \textit{colored ring confidential transactions} with multiple so-called coin colors, allowing users to transact with multiple assets simultaneously.
+The key images in \cite{liu} are unsuitable for applications where signatures must be linked key-by-key, not ring-by-ring (such as for ``double-signing'' protection in a setting where users generate new keys over time and select \textit{ad hoc} ring members).
+Resistance to double-spend attempts is ensured using key images as described in \cite{van2013cryptonote}.
+More recent work of \cite{noether} extends the approach of \cite{liu} to enable a signer-ambiguous confidential transaction model with \textit{ad hoc} ring member selection.
+In \cite{noether}, transaction amounts are replaced with Pedersen commitments to amounts together with range proofs.
+Signatures are constructed from key vectors including differences of amount commitments as one of the keys.
+However, the proofs in \cite{noether} are informal and not based on rigorous security models.
+
+Alternatives to ring signatures like more general zero-knowledge proving systems typically require a trusted party to honestly perform a setup process (as in \cite{groth,ben2014succinct,groth2018updatable}) or lack practical efficiency for large circuits (as in \cite{bulletproofs}), meaning that such systems may not be appropriate for distributed ledger applications.
+However, more recent approaches such as \cite{bowehalo,hoffmann2019efficient} show both improvements to the trust requirement as well as improvements in efficiency.
 
 \subsection{Our contribution}
+We first introduce a formal definition of $d$-dimensional linkable ring signatures.
+We present an implementation of a new signature scheme, $d$-CLSAG signatures.
+These have $d$-dimensional keys and are \textit{compact} linkable spontaneous anonymous group signatures in the sense that signature size scales with the \textit{sum} of ring size and the dimension $d$.
+Equivalent MLSAG signatures of \cite{noether} produce signatures that scale with the product of ring size and $d$ rather than the sum.
+Size efficiency comes from an aggregation of keys across components, similar to the approach from \cite{maxwell2018simple,qian2010non}, resulting in $d$-CLSAG signatures that are about half the size of \cite{noether}, and can be generated and verified more quickly.
 
-In this work, we introduce a $d$-dimensional linkable ring multisignature ($d$-LRMS) scheme suitable for use in a colored ring confidential transaction scheme with $d$ colors.
-Our scheme is \textit{compact} in the sense that signature size scales with the sum of ring size and the dimension $d$; that is, increasing $d$ yields the same additional number of signature elements, regardless of the ring size.
-We prove our scheme is unforgeable up to the hardness of the $k$-one-more discrete logarithm problem.
+We present linkable ring signatures and some examples in Section \ref{sec:lrs-and-exs}.
+We present a compact $d$-LRS scheme we call $d$-CLSAG in Section \ref{sec:themainthing} and measure efficiency.
+We present an informal description of a transaction protocol for confidentially transacting multiple asset types simultaneously, which we call a \textit{multi-asset ring confidential transaction} or MARCT in Section \ref{sec:marct}.
+We reserve discussion of security for the appendix, where we make a new definition for unforgeability in linkable ring signatures that takes into account both insider corruption and forgeries from partially-corrupted rings.
+We prove that $d$-CLSAG signatures are unforgeable up to the hardness of the $k$-one-more discrete logarithm ($k$-OMDL) problem under this definition in the random oracle model in Appendix \ref{app:unf}.
+We also make some comments on signer ambiguity and linkability in Appendix \ref{app:link-and-sa}.
 
-We call our signature scheme $d$-dimensional compact linkable spontaneous anonymous group ($d$-CLSAG) signatures.
-We demonstrate how to use this scheme for ring confidential transactions in Monero by replacing multi-layered linkable spontaneous anonymous group (MLSAG) signatures with $d$-CLSAG signatures.
-The resulting scheme is more efficient in both signature size and verification time than current Monero transaction structures, and can be seamlessly integrated into the Monero transaction protocol.
-
-\section{Notation}
-
-In this document, we denote algorithms with typefont majuscule English letters like $\texttt{A}$, $\texttt{B}$, or $\texttt{O}$, or typefont names like $\texttt{Setup}$, $\texttt{KeyGen}$, and so on.
+\subsection{Notation}\label{sec:notation}
+We denote algorithms with typefont majuscule English letters like $\texttt{A}$, $\texttt{B}$, or $\texttt{O}$, or typefont names like $\texttt{Setup}$, $\texttt{KeyGen}$, and so on.
+For any prime $p$, denote the field with $p$ elements as $\mathbb{F}_p := \mathbb{Z}/p\mathbb{Z}$, and denote the non-zero elements as $\mathbb{F}_p^*$.
 
 Group parameters are denoted as a tuple $(p, \mathbb{G}, d, G)$ where $\mathbb{G}$ is an elliptic curve group with prime order $p$, $d$ is a dimension, and $G$ is a generator of $\mathbb{G}$.
-We denote integers, bits, indices, and scalars in $\mathbb{Z}/p\mathbb{Z}$ with minuscule English letters $x, y, z, b, c, i, j, k$, etc.\ and we denote group elements with majuscule English letters, $G, X, W$, and so on.
-We use miniscule Greek letters like $\sigma$ to describe signatures and majuscule calligraphic Latin letters like $\mathfrak{T}$ when describing linkability tags.
+We denote integers, bits, indices, and scalars in $\mathbb{F}_p$ with minuscule English letters $x, y, z, b, c, i, j, k$, etc.\ and we denote group elements with majuscule English letters, $G, X, W$, and so on.
+We use miniscule Greek letters like $\sigma$ to describe signatures and majuscule calligraphic Latin letters like $\mathfrak{T}$ when describing key images.
+
+For these group parameters, the secret key space is $\mathbb{F}_p^*$ and the public key space is $\mathbb{G}$.
+For any non-zero secret key $\textit{sk} \in \mathbb{F}_p^*$, the corresponding public key $\textit{pk}$ is computed from the generator $G$ through exponentiation in $\mathbb{G}$ as usual.
+However, we use notation for a module over the field $\mathbb{Z}_p$ to maintain consistency with, say \cite{van2013cryptonote} and \cite{noether}.
 
@@
 We distinguish oracles with calligraphic font, e.g.\ $\mathcal{CO}$ denotes a corruption oracle, $\mathcal{SO}$ denotes a signing oracle.
-If the codomain of a random oracle is the field of scalars $\mathbb{Z}/p\mathbb{Z}$, we denote this $\mathcal{H}^s$ (hash-to-scalar).
+If the codomain of a random oracle is the field of scalars $\mathbb{F}_p$, we denote this $\mathcal{H}^s$ (hash-to-scalar).
 If the codomain is $\mathbb{G}$, we denote this $\mathcal{H}^p$ (hash-to-point).
 
-\section{Linkable ring multisignatures}
+\section{Linkable ring multisignatures}\label{sec:lrs-and-exs}
+In this section, we recall linkable ring signature (LRS) schemes, definitions of correctness in verification and linkability, and we provide two examples.
 
-In this section, we recall linkable ring signature (LRS) schemes, we modify the definition to account for $d$-dimensional keys for linkable ring multisignature (LRMS) schemes, and we provide two examples.
-We emphasize that our description does not present multisignatures as computed between mutually untrusted parties.
-We use the term to mean a $d$-of-$d$ threshold multisignature with all keys controlled by the same signer; in particular, we have none of the communication steps necessary for computing a multisignature.
-
-\subsection{LRS and LRMS schemes}
-
-\begin{defn}[LRS]\label{def:lrs}
-A \textit{linkable ring signature scheme} is a tuple $(\texttt{Setup}, \texttt{KeyGen}, \texttt{Sign}, \texttt{Verify}, \texttt{Link})$ satisfying the following. 
+\subsection{LRS schemes}
+\begin{definition}[LRS]\label{def:lrs}
+A \textit{linkable ring signature scheme} is a tuple $\left(\texttt{Setup}, \texttt{KeyGen}, \right. \allowbreak \left. \texttt{Sign}, \texttt{Verify}, \texttt{Link}\right)$ satisfying the following. 
 \begin{itemize}
@@
 
-\item $\texttt{Sign}\left(1^\lambda, \textit{par}, (m, \textbf{pk}, sk)\right) \to \left\{\bot_{\texttt{Sign}}, (\sigma, \mathfrak{T})\right\}$.
+\item $\texttt{Sign}\left(1^\lambda, \textit{par}, (m, \textbf{pk}, sk)\right) \to \left\{\bot_{\texttt{Sign}}, \sigma \right\}$.
 $\texttt{Sign}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, an arbitrary message $m \in \left\{0,1\right\}^*$, an ad hoc \textit{ring} of public keys $\textbf{pk} = \left\{pk_1, \ldots, pk_n\right\}$, and a secret key $sk$.
-$\texttt{Sign}$ produces as output either a distinguished failure symbol $\textit{out} = \bot_{\texttt{Sign}}$ or a signature-tag pair $\textit{out} = (\sigma, \mathfrak{T})$.
+$\texttt{Sign}$ produces as output either a distinguished failure symbol $\textit{out} = \bot_{\texttt{Sign}}$ or a signature $\textit{out} = \sigma$.
 
-\item $\texttt{Verify}\left(1^\lambda, \textit{par}, (m, \textbf{pk}, (\sigma, \mathfrak{T}))\right) \to \left\{0,1\right\}$.
-$\texttt{Verify}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, a message $m$, a ring of public keys $\textbf{pk}$, and a signature-tag pair $(\sigma, \mathfrak{T})$.
-$\texttt{Verify}$ produces as output a bit $b \in \left\{0,1\right\}$.
+\item $\texttt{Verify}\left(1^\lambda, \textit{par}, (m, \textbf{pk}, \sigma)\right) \to \left\{0,1\right\}$.
+$\texttt{Verify}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, a message $m$, a ring of public keys $\textbf{pk}$, and a signature $\sigma$.
+$\texttt{Verify}$ produces as output a bit $b \in \left\{0,1\right\}$; $0$ indicates the signature is not verified, and $1$ indicates the signature is verified.
 
-\item $\texttt{Link}\left(1^\lambda, \textit{par}, (\sigma, \mathfrak{T}), (\sigma^\prime, \mathfrak{T}^\prime)\right)$.
-$\texttt{Link}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, and a pair of signature-tag pairs $(\sigma, \mathfrak{T}), (\sigma^\prime, \mathfrak{T}^\prime)$.
-$\texttt{Link}$ produces as output a bit $b \in \left\{0,1\right\}$.
+\item $\texttt{Link}\left(1^\lambda, \textit{par}, (m, \textbf{pk}, \sigma), (m^\prime, \textbf{pk}^\prime, \sigma^\prime)\right)$.
+$\texttt{Link}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, and a pair of tuples $(m, \textbf{pk}, \sigma), (m^\prime, \textbf{pk}^\prime, \sigma^\prime)$ for messages $m, m^\prime$, rings $\textbf{pk}$, $\textbf{pk}^\prime$, and ring signatures $\sigma, \sigma^\prime$.
+$\texttt{Link}$ produces as output a bit $b \in \left\{0,1\right\}$; $0$ indicates the signatures are not linked or invalid, and $1$ indicates the signatures are valid and linked.\footnote{This is the opposite of the conventions in, say, \cite{tsang2004separable}, which outputs $0$ to indicate two signatures are linked (\textit{i.e.}\ rejected) and outputs $1$ to indicate two signatures are not linked (\textit{i.e.}\ accepted).}
 \end{itemize}
-\end{defn}
+\end{definition}
 
-We extend this to a scheme with $d$-dimensional keys.
+In the sequel, we implicitly assume all algorithms in a LRS take $1^\lambda$ as input, and all algorithms (except $\texttt{Setup}$) takes $\textit{par}$ as input.
+We suppress this notation in the sequel.
+For example, we write $\textit{par} \leftarrow \texttt{Setup}$ instead of $\textit{par} \leftarrow \texttt{Setup}(1^\lambda)$ and $\sigma \leftarrow \texttt{Sign}(m, \textbf{pk}, \textit{sk})$ instead of $\sigma \leftarrow \texttt{Sign}(1^\lambda, \textit{par}, m, \textbf{pk}, \textit{sk})$.
 
-\begin{defn}[$d$-LRMS]
-A \textit{$d$-dimensional linkable ring multisignature scheme} is a tuple of algorithms $(\texttt{Setup}, \texttt{KeyGen}, \texttt{Sign}, \texttt{Verify}, \texttt{Link})$ satisfying the following. 
+Note the dimension of keys in Definition \ref{def:lrs} is not specified.
+If the keys from $\texttt{KeyGen}$ have dimension $d > 1$, we instead say the LRS is a $d$-LRS and use the vector notation introduced in Section \ref{sec:notation} representing keys in boldface (\textit{e.g.}\ \textbf{pk} instead of \textit{pk}) and rings in underlined boldface ($\underline{\textbf{pk}}$ instead of $\textbf{pk}$).
+We always assume the first coordinate of a secret key is the \textit{linking coordinate}, and linkability depends only on the linking coordinate of the signing key vector.
+For ring confidential transactions, this is important since only one such entry corresponds to an output public key for double-spend detection purposes and the rest of the keys could have been adversarially generated.
+
+\begin{definition}[Correctly verified]
+Let $m$ be any message, $\textit{sk}$ be any secret key with corresponding public key $\textit{pk}$, and let $\textbf{pk}$ be a multiset of public keys $\textbf{pk} = \left\{\textit{pk}_1, \ldots, \textit{pk}_n\right\}$.
+If there exists an index $1 \leq \ell \leq n$ satisfying $\textit{pk} = \textit{pk}_\ell$, then \[\texttt{Verify}(m, \textbf{pk}, \texttt{Sign}(m, \textbf{pk}, \textit{sk})) = 1.\]
+\end{definition}
+Soundness in verification is the property of unforgeability. See Appendix \ref{app:unf}.
+
+\begin{definition}[Correctly linkable]
+Let $m, m^\prime$ be any messages, $\textit{sk}, \textit{sk}^\prime$ be any secret keys with corresponding public keys $\textit{pk}$, $\textit{pk}^\prime$.
+Let $\textbf{pk}$, $\textbf{pk}^\prime$ be multisets of public keys with indices $\ell, \ell^\prime$, respectively, such that $\textbf{pk}_\ell = \textit{pk}$ and $\textbf{pk}^\prime_{\ell^\prime} = \textit{pk}^\prime$.
+Let $\textit{sk}, \textit{sk}^\prime$ be the respective private keys for $\textit{pk}, \textit{pk}^\prime$ with respective linking coordinates $\textit{sk}_0$ and $\textit{sk}^\prime_0$.
+Correct linkability means being both \textit{positively} and \textit{negatively} linkable, in the following sense.
 \begin{itemize}
-\item $\texttt{Setup}(1^\lambda) \to \textit{par}$. $\texttt{Setup}$ works as described in \ref{def:lrs}.
+\item \textbf{Positively linkable:} If the linking coordinates satisfy $\textit{sk}_0 = \textit{sk}^\prime_0$, then \[\textit{Link}((m, \textbf{pk}, \texttt{Sign}(m, \textbf{pk}, sk)), (m^\prime, \textbf{pk}^\prime, \texttt{Sign}(m^\prime, \textbf{pk}^\prime, sk^\prime)))=1\] except with negligible probability.
 
-\item $\texttt{KeyGen}(1^\lambda, \textit{par}) \to (\textbf{sk}, \textbf{pk})$.
-$\texttt{KeyGen}$ takes as input a security parameter $1^\lambda$ and public parameters $\textit{par}$.
-$\texttt{KeyGen}$ produces as output a private-public keypair $(\textbf{sk}, \textbf{pk})$ where each key is a $d$-dimensional vector.
-We refer to the first coordinate of each of these keys as the \textit{linking key} and the $d-1$ remaining coordinates (if there are any) are the \textit{auxiliary keys}.
+\item \textbf{Negatively linkable:} If the linking coordinates satisfy $\textit{sk}_0 \neq \textit{sk}^\prime_0$, then \[\textit{Link}((m, \textbf{pk}, \texttt{Sign}(m, \textbf{pk}, sk)), (m^\prime, \textbf{pk}^\prime, \texttt{Sign}(m^\prime, \textbf{pk}^\prime, sk^\prime)))=0\] except with negligible probability.
+\end{itemize}
+\end{definition}
 
-\item $\texttt{Sign}\left(1^\lambda, \textit{par}, (m, \underline{\textbf{pk}}, \textbf{sk})\right) \to \left\{\bot_{\texttt{Sign}}, (\sigma, \mathfrak{T})\right\}$.
-$\texttt{Sign}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, a message $m$, a vector of public keys $\underline{\textbf{pk}} = \left\{\textbf{pk}_1, \ldots, \textbf{pk}_n\right\}$ where each $\textbf{pk}_i$ is a $d$-dimensional public key, and a $d$-dimensional secret key $\textbf{sk}$.
-$\texttt{Sign}$ produces as output either a distinguished failure symbol $\bot_{\texttt{Sign}}$ or a signature-tag pair $(\sigma, \mathfrak{T})$.
-
-\item $\texttt{Verify}\left(1^\lambda, \textit{par}, (m, \underline{\textbf{pk}}, (\sigma, \mathfrak{T}))\right) \rightarrow \left\{0,1\right\}$.
-$\texttt{Verify}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, a message $m$, a matrix of public keys $\underline{\textbf{pk}}$, and a signature-tag pair $(\sigma, \mathfrak{T})$.
-$\texttt{Verify}$ produces as output a bit $b \in \left\{0,1\right\}$.
-
-\item  $\texttt{Link}\left(1^\lambda, \textit{par}, (\sigma, \mathfrak{T}), (\sigma^\prime, \mathfrak{T}^\prime)\right)$. $\texttt{Link}$ works as described in \ref{def:lrs}.
-\end{itemize}
-\end{defn}
-
-We refer to the linkability tag as the \textit{key image} for consistency with terminology in Monero. We also use the following terminology if the scheme satisfies the respective properties.
-\begin{description}
-\item[Correctly verified:] For any message $m$, $d$-dimensional secret key $\textbf{sk}$ with corresponding public key $\textbf{pk}$, and appropriately-sized matrix $\underline{\textbf{pk}} = \left\{\textbf{pk}_1, \ldots, \textbf{pk}_n\right\}$, if there exists an index $1 \leq \ell \leq n$ such that $\textbf{pk} = \textbf{pk}_\ell$, then $\texttt{Verify}(\texttt{Sign}(m, \underline{\textbf{pk}}, \textbf{sk})) = 1$.
-
-\item[Correctly linkable:] For any messages $m$, $m^\prime$, any $d$-dimensional secret keys  $\textbf{sk}$ and $\textbf{sk}^\prime$ with equal linking keys (that is, with $\textbf{sk}_0 = \textbf{sk}^\prime_0$) and with corresponding public keys $\textbf{pk}$ and $\textbf{pk}^\prime$ respectively, any appropriately-sized pair of matrices $\underline{\textbf{pk}}$ and $\underline{\textbf{pk}}^\prime$, if $(\sigma, \mathfrak{T}) \leftarrow \texttt{Sign}(m, \underline{\textbf{pk}}, \textbf{sk})$ and $(\sigma^\prime, \mathfrak{T}^\prime) \leftarrow \texttt{Sign}(m^\prime, \underline{\textbf{pk}}^\prime, \textbf{sk}^\prime)$ and there exists a pair of indices $\ell$ and $\ell^\prime$ such that $\underline{\textbf{pk}}_\ell = \textbf{pk}$ and $\underline{\textbf{pk}}_{\ell^\prime} = \textbf{pk}^\prime$, then
-$\texttt{Link}((\sigma, \mathfrak{T}), (\sigma^\prime, \mathfrak{T}^\prime))=1$.
-\end{description}
-
-Note that linkability is only considered with respect to a single component of a matrix entry.
-When applied to Monero, this is important since only one such entry corresponds to an output public key for double-spend detection purposes.
-
-%In the sequel, we omit $1^\lambda$ and $\textit{par}$ from the input of algorithms for clarity unless there is risk of confusion.
+Soundness in linkability means informally that an adversarial algorithm can only produce tuples $y=(m, \textbf{pk}, \sigma)$ and $y^\prime =(m^\prime, \textbf{pk}^\prime, \sigma^\prime)$ such that $\texttt{Link}(y, y^\prime)=1$ by computing $\sigma$, $\sigma^\prime$ from $\texttt{Sign}$ using secret keys $\textit{sk}, \textit{sk}^\prime$ with matching linking coordinates.
+See Appendix \ref{app:link-and-sa}.
 
 \subsection{Examples}
+In the following examples, all verifiers must list the keys in $\textbf{pk}$ in an agreed-upon order for the above verification to work; either they should agree upon lexicographic or some other ordering.
+Linking occurs merely by comparing key images: two valid signatures with the same key image were signed with the same secret key (and, in transaction applications, would signal an attempt to double-spend funds).
 
 \begin{example}\label{ex:lsag}
-The LSAG signature scheme from \cite{liu2004linkable} is a $1$-LRMS.
-In this example, $\texttt{Setup}$ always deterministically sets $d:=1$ (so we only use the linking key and there are no auxiliary keys).
-$\texttt{Setup}$ selects some $G \in \mathbb{G}$ to be a group generator for the group parameters $(p, \mathbb{G}, 1, G)$, two cryptographic hash functions $\mathcal{H}^s:\left\{0,1\right\}^* \to \mathbb{Z}/p\mathbb{Z}$ and $\mathcal{H}^p:\left\{0,1\right\}^* \to \mathbb{G}$.
-$\texttt{Setup}$ outputs $\textit{par} = (p, \mathbb{G}, 1, G, \mathcal{H}^s, \mathcal{H}^p)$.
+The signature scheme of \cite{liu} is an LRS; we present the key image variant from \cite{van2013cryptonote} with a key image appropriate for linking signatures key-by-key.
+The signature scheme originally described in \cite{liu} signs a message $m$ with a ring of keys $\textbf{pk} = \left\{\textit{pk}_1, \ldots, \textit{pk}_n\right\}$ and a secret index-key pair $(\ell, \textit{sk})$ corresponding to some $\textit{pk}_\ell$, using the key image $\mathfrak{T} := \textit{sk} \cdot \mathcal{H}^p(\textbf{pk})$.
 
-$\texttt{KeyGen}$ produces as output a private key $x \in \mathbb{Z}/p\mathbb{Z}$ and a public key $X = xG$.
-$\texttt{Sign}$ takes as input a private key $y \in \mathbb{Z}/p\mathbb{Z}$, a message $m$, and a ring $\textbf{X} = \left\{X_1, \ldots, X_n\right\}$, and produces as output either a distinguished failure symbol $\bot_{\texttt{Sign}}$ or a signature-tag pair $(\sigma, \mathfrak{T})$.
+Unfortunately, this key image is unsuitable for transaction applications, as changing ring members will change the key image, allowing the same key to sign twice.
+For use in a transaction protocol and following \cite{van2013cryptonote}, we modify this key image from that of \cite{liu} to be $\mathfrak{T} := \textit{sk} \cdot  \mathcal{H}^p(\textit{pk}_\ell)$, which is independent of the non-signing ring members.
+This allows these key images to be used for double-spend protection, as discussed previously.
 
-The signature scheme originally described in \cite{liu2004linkable} signs a message $m$ with a ring of keys $\textbf{X} = \left\{X_1, \ldots, X_n\right\}$ and a secret key $x$ corresponding to some $X_\ell$, using the linkability tag (key image) $\mathfrak{T} := x \mathcal{H}^p(\textbf{X})$.
-Unfortunately, this key image is unsuitable for use in Monero, as changing ring members will change the key image.
-This would allow the same key to be used twice in two different ring signatures.
-For use in Monero, we modify this key image to be independent of the non-signing ring members, $\mathfrak{T} := x \mathcal{H}^p(X_\ell)$.
-This allows these key images to be used for double-spend protection.
+$\texttt{Setup}$ always deterministically sets $d:=1$ so we only use the linking key and there are no auxiliary keys.
+$\texttt{Setup}$ selects a generator $G \in \mathbb{G}$ to be a group generator for the group parameters $(p, \mathbb{G}, d, G)$, two cryptographic hash functions $\mathcal{H}^s:\left\{0,1\right\}^* \to \mathbb{F}_p$ and $\mathcal{H}^p:\left\{0,1\right\}^* \to \mathbb{G}$.
+$\texttt{Setup}$ outputs $\textit{par} = (p, \mathbb{G}, d, G, \mathcal{H}^s, \mathcal{H}^p)$.
 
-An LSAG signature on a message $m$ with ring $\textbf{X}$ using these key images is computed in the following way.
-First, the signer samples $\alpha, s_{\ell+1}, s_{\ell+2}, \ldots, s_{\ell-1} \in \mathbb{Z}/p\mathbb{Z}$ at random.
-Next, the signer computes basepoints $H_i = \mathcal{H}^p(X_i)$.
-Next, the signer computes $c_{\ell+1}  = \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid \alpha G \mid \mid \alpha H_\ell)$ and the signer computes each $c_{i+1} = \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid s_i G + c_i X_i \mid \mid s_i H_i + c_i \mathfrak{T})$ for $i = \ell+1, \ldots, \ell-1$, naturally identifying index $1$ with index $n+1$.
-The signer finishes by computing $s_\ell = \alpha - c_\ell x_\ell$ and publishing the signature-tag pair $(\sigma, \mathfrak{T})$ where $\sigma = (c_1, s_1, \ldots, s_n)$.
+$\texttt{KeyGen}$ produces as output a secret key $\textit{sk} \in \mathbb{F}_p^*$ and the corresponding public key $\texttt{pk} = \textit{sk}\cdot G\in \mathbb{G}$.
 
-A purported LSAG signature-tag pair on a message $m$ with ring $\textbf{X}$ is verified in the following way.
-The verifier sets $c_1^\prime = c_1$ and computes $c_{i+1}^\prime = \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid s_i G + c_i^\prime X_i \mid \mid s_i H_i + c_i^\prime \mathfrak{T})$ for $i=1, 2, \ldots, n$.
+$\texttt{Sign}$ takes as input a (non-zero) private key $\textit{sk} \in \mathbb{F}_p^*$, a message $m$, a ring $\textbf{pk} = \left\{\textit{pk}_1, \ldots, \textit{pk}_n\right\}$, and produces as output either a distinguished failure symbol $\bot_{\texttt{Sign}}$ or a signature $\sigma$, computed as follows.
+First, the signer samples $\alpha, s_{\ell+1}, s_{\ell+2}, \ldots, s_{\ell-1} \in \mathbb{F}_p$ at random.
+Next, the signer computes basepoints $H_i = \mathcal{H}^p(\textit{pk}_i)$ and the key image $\mathfrak{T} = \textit{sk} \cdot \mathcal{H}^p(\textit{pk}_\ell)$, the first challenge $$c_{\ell+1}  = \mathcal{H}^s(\textbf{pk} \mid \mid m \mid \mid \alpha G \mid \mid \alpha H_\ell)$$ and each subsequent challenge $$c_{i+1} = \mathcal{H}^s(\textbf{pk} \mid \mid m \mid \mid s_i G + c_i \cdot \textit{pk}_i \mid \mid s_i H_i + c_i \mathfrak{T})$$ for $i = \ell+1, \ldots, \ell-1$, naturally identifying index $1$ with index $n+1$.
+The signer finishes by computing $s_\ell = \alpha - c_\ell \cdot \textit{sk}$ and publishing the signature $\sigma$ where $\sigma = (c_1, s_1, \ldots, s_n, \mathfrak{T})$.
+
+$\texttt{Verify}$ takes as input a message $m$, a ring $\textbf{pk}$, and a purported signature $\sigma^\prime$.
+$\texttt{Verify}$ parses the signature $(c_1, s_1, \ldots, s_n, \mathfrak{T}) \leftarrow \sigma$.
+If $c_1 \notin \mathbb{F}_p$ or any $s_i \notin \mathbb{F}_p$ or $\mathfrak{T} \notin \mathbb{G}$, then $\texttt{Verify}$ outputs $0$.
+Otherwise, the verifier computes $H_i := \mathcal{H}^p(X_i)$ for each ring member, sets $c_1^\prime := c_1$, and computes the challenges $$c_{i+1}^\prime = \mathcal{H}^s(\textbf{pk} \mid \mid m \mid \mid s_i G + c_i^\prime \cdot \textit{pk}_i \mid \mid s_i H_i + c_i^\prime \mathfrak{T})$$ for $i=1, 2, \ldots, n$.
 The verifier outputs $1$ when $c_{n+1}^\prime = c_1$ and $0$ otherwise.
-Note that all verifiers must list the keys in $\textbf{X}$ in an agreed-upon order for the above verification to work; either they should agree upon lexicographic or some other ordering.
-LSAG signature-tag pairs are linked merely by comparing key images: two valid signatures with the same key image were signed with the same secret key (and, in the case of Monero, would signal an attempt to double-spend funds).
+
+$\texttt{Link}$ checks the validity of both signatures.
+If both are valid, $\texttt{Link}$ parses the key images $\mathfrak{T}$ and $\mathfrak{T}^\prime$.
+If either are not in $\mathbb{G}$, the linker outputs $0$ and terminates.
+Otherwise, the linker outputs $1$ when $\mathfrak{T} = \mathfrak{T}^\prime$ and $0$ otherwise.
 \end{example}
@@
 The key image modification in Example \ref{ex:lsag} is due to the basepoint of the key image $\mathfrak{T}$.
-As noted in \cite{liu2004linkable}, easy variations on key image formats are available.
+As noted in \cite{liu}, variations on key image formats may be desirable.
 How or whether the security properties of LSAG signatures are retained in practical use given more flexible key image formats, while interesting, is beyond the scope of this work.
@@
 \begin{example}\label{ex:mlsag}
-The MLSAG signature scheme from \cite{noether2016ring} is a $2$-LRMS.
-In this example, $\texttt{Setup}$ always deterministically sets $d := 2$.
-Public keys are taken to be pairs of group elements $(X, Z) \in \mathbb{G}^2$.
-$\texttt{Sign}$ takes as input a private key vector $(x,z)$, a message $m$, and a matrix of public keys $\underline{\textbf{pk}} = \left\{\textbf{pk}_1, \ldots, \textbf{pk}_n\right\}$ where each $\textbf{pk}_i = (X_i, Z_i)$, each $X_i$ is the public key of a one-time transaction output, and each $Z_i$ is computed using combinations of Pedersen commitments that depend on the particular transaction type in use.
-%The commitments that form $Z_i$ can be adversarially selected and are not used in linking, and the secret key for $X_i$ can only be computed by the recipient except with negligible probability.
+This example extends the LRS of the previous example to a so-called MLSAG scheme \cite{noether}, which is a $2$-LRS for use in signer-ambiguous confidential transactions.
+$\texttt{Setup}$ always deterministically sets $d := 2$, so we use one linking key and one auxiliary key, but otherwise works as before.
 
-A signature-tag pair $(\sigma, \mathfrak{T})$ is computed in the following way.
-Two rows of random signature data are sampled, say  $\alpha, \alpha^\prime, s_{\ell + 1}, s^\prime_{\ell + 1}, s_{\ell + 2}, s^\prime_{\ell + 2}, \ldots, s_{\ell -1}, s^\prime_{\ell - 1}$  and the basepoints $H_i = \mathcal{H}^p(X_i)$ are computed from the signing keys $X_i$ of each ring member $(X_i, Z_i)$.
-The key image $\mathfrak{T} = x_\ell H_\ell$ is computed.
-The following  challenges are computed
-\begin{align*}
-c_{\ell + 1} =& \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid \alpha G \mid \mid \alpha H_\ell \mid \mid \alpha^\prime G^\prime) \\
-c_{i+1} =& \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid s_i G + c_i X_i \mid \mid s_i H_i + c_i \mathfrak{T} \mid \mid s_i^\prime G^\prime + c_i Z_i).
-\end{align*}The values $s_\ell = \alpha - c_\ell x_\ell$ and $s_\ell^\prime = \alpha^\prime - c_\ell z_\ell$ are computed.
-The signature is set $\sigma := (c_1, s_1, s_1^\prime, \ldots, s_n, s_n^\prime)$ and the signature-tag pair is published $(\sigma, \mathfrak{T})$.
-Verification proceeds as one would expect, succeeding if $c_{n+1}^\prime = c_1$ after the verifier computes each $H_i$ and each challenge
-\begin{align*}
-c_{2}^\prime =&  \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid s_1 G + c_1 X_1 \mid \mid s_1 H_1 + c_1 \mathfrak{T} \mid \mid s_1^\prime G^\prime + c_1 Z_1) \\
-c_{i+1}^\prime =&  \mathcal{H}^s\left(\textbf{X} \mid \mid m \mid \mid s_i G + c_i^\prime X_i \mid \mid s_i H_i + c_i^\prime \mathfrak{T} \mid \mid s_i^\prime G^\prime + c_i^\prime Z_i \right).
-\end{align*} 
-Note this scheme is not compact in the sense that doubling key dimension going from $d=2$ in Example \ref{ex:lsag} to $d=2$ results in an asymptotic doubling of signature size. 
+$\texttt{KeyGen}$ produces as output a secret key $\textbf{sk} = (x, z) \in \mathbb{F}_p^* \times \mathbb{F}_p^*$ and the corresponding public key  $\textbf{pk} := \textbf{sk} \circ \textbf{G} = (xG, zG) \in \mathbb{G}^2$ where $\textbf{G} = (G, G) \in \mathbb{G}^2$.
+The key $x$ is the linking key.
+The auxiliary key $z$ is a blinder that opens a Pedersen commitment to zero demonstrating transaction balance in ring confidential transactions in the style of \cite{noether}.
+
+$\texttt{Sign}$ takes as input a (non-zero) private key $\textbf{sk} \in \mathbb{F}_p^* \times \mathbb{F}_p^*$, a message $m$, a ring $\underline{\textbf{pk}} \in \mathbb{G}^{2 \times n}$, and produces as output either a distinguished failure symbol $\bot_{\texttt{Sign}}$ or a signature $\sigma$, computed as follows.
+First, the signer samples rows of signature data  $\alpha, \alpha^\prime, s_{\ell + 1}, s^\prime_{\ell + 1}, s_{\ell + 2}, s^\prime_{\ell + 2}, \ldots, s_{\ell -1}, s^\prime_{\ell - 1} \in \mathbb{F}_p$ at random.
+Next, the signer computes the basepoints $H_i = \mathcal{H}^p(X_i)$ from the linking keys $X_i$ of each ring member $\textbf{pk}_i = (X_i, Z_i)$.
+The linking key image $\mathfrak{T} = x H_\ell$ is computed from the linking key.
+An auxiliary key image with the same basepoint but discrete logarithm $z_\ell$ is computed, $\mathfrak{D} = z_\ell H_\ell$.
+The signer computes the challenges
+$$c_{\ell + 1} = \mathcal{H}^s(\textbf{pk} \mid \mid m \mid \mid \alpha G \mid \mid \alpha H_\ell \mid \mid \alpha^\prime G \mid \mid \alpha^\prime H_\ell)$$
+and
+$$c_{i+1} = \mathcal{H}^s(\textbf{pk} \mid \mid m \mid \mid s_i G + c_i X_i \mid \mid s_i H_i + c_i \mathfrak{T} \mid \mid s_i^\prime G + c_i Z_i \mid \mid s_i^\prime H_i + c_i \mathfrak{D}).$$
+The values $s_\ell = \alpha - c_\ell x_\ell$ and $s_\ell^\prime = \alpha^\prime - c_\ell z_\ell$ are computed.
+The signature is set $\sigma := (c_1, s_1, s_1^\prime, \ldots, s_n, s_n^\prime, \mathfrak{T}, \mathfrak{D})$ and is output.
+
+$\texttt{Verify}$ takes as input a message $m$, a ring $\underline{\textbf{pk}}$, and a signature $\sigma$.
+The verifier parses the signature $(c_1, s_1, s_1^\prime, \ldots, s_n, s_n^\prime, \mathfrak{T}, \mathfrak{D}) \leftarrow \sigma$.
+If this is not possible, or $c_1 \notin \mathbb{F}_p$, or any $s_i$ or $s_i^\prime \notin \mathbb{F}_p$, or if $\mathfrak{T} \notin \mathbb{G}$, then the verifier outputs $0$.
+Otherwise, the verifier parses $(\textbf{pk}_1, \ldots, \textbf{pk}_{n^\prime}) \leftarrow \underline{\textbf{pk}}$.
+If any $\textbf{pk}_i \notin \mathbb{G}^2$, or if $n \neq n^\prime$, the verifier outputs $0$.
+Otherwise, the verifier parses each $\textbf{pk}_i$ as $(X_i, Z_i)$, computes each $H_i = \mathcal{H}^p(X_i)$, sets $c_1^\prime := c_1$, and computes the challenges $$c_{i+1}^\prime = \mathcal{H}^s(\textbf{pk} \mid \mid m \mid \mid s_i G + c_i^\prime X_i \mid \mid s_i H_i + c_i^\prime \mathfrak{T} \mid \mid s_i^\prime G + c_i^\prime Z_i \mid \mid s_i^\prime H_i + c_i^\prime \mathfrak{D})$$ for $i=1, 2, \ldots, n$.
+The verifier outputs $1$ when $c_{n+1}^\prime = c_1$ and $0$ otherwise.
+
+Lastly, $\texttt{Link}$ works as before, by checking key images.
 \end{example}
 
-\section{A compact d-LRMS scheme}
-
-We present a multisignature variant of LSAG signatures that is more compact than the previous examples.
-We loosely say that a $d$-LRMS scheme is compact if its signature sizes are not proportional to $d$.
-We call this scheme $d$-CLSAG to be concise.
-We show how to apply a $2$-CLSAG for use in ring confidential transactions, and how to apply $d$-CLSAG for colored ring confidential transactions.
-We make remarks on efficiency for both applications.
-In particular, we show that our $2$-CLSAG construction is more efficient in both space and verification time than the equivalent MLSAG construction.
+\section{A compact d-LRS scheme}\label{sec:themainthing}
+We informally say that a $d$-LRS scheme is \textit{compact} or \textit{concise} if signature sizes are not directly proportional to $d$.
+We present a multisignature variant of LSAG signatures that is asymptotically more compact than the previous examples.
+We call this scheme $d$-CLSAG.
+We take a look at efficiency for usage in ring confidential transactions by comparing $2$-CLSAG signatures against equivalent MLSAG signatures.
 
 \subsection{Implementation}\label{sec:implem}
-
-\begin{defn}[$d$-CLSAG]\label{def:clsag}
-The following tuple $(\texttt{Setup}, \texttt{KeyGen}, \texttt{Sign}, \texttt{Verify}, \texttt{Link})$ is a compact $d$-LRMS.
+\begin{definition}[$d$-CLSAG]\label{def:clsag}
+The tuple $(\texttt{Setup}, \texttt{KeyGen}, \texttt{Sign}, \texttt{Verify}, \allowbreak \texttt{Link})$ satisfying the following is a $d$-CLSAG signature scheme.
 
 \begin{itemize}
-\item $\texttt{Setup}(1^\lambda, d) \to \textit{par}$.
-$\texttt{Setup}$ takes as input a security parameter $1^\lambda$ and a public dimension $d$.
-$\texttt{Setup}$ selects a prime $p$, a group $\mathbb{G}$ with prime order $p$, selects a group generator $G \in \mathbb{G}$ uniformly at random, selects $d$ cryptographic hash functions $\mathcal{H}^s_0, \ldots, \mathcal{H}^s_{d-1}$ with codomain $\mathbb{Z}/p\mathbb{Z}$, selects a cryptographic hash function $\mathcal{H}^p$ with codomain $\mathbb{G}$.
-$\texttt{Setup}$ outputs $\textit{par} = \left( p,\mathbb{G}, d, G, \left\{\mathcal{H}^s_j\right\}_{j=0}^{d-1}, \mathcal{H}^p\right)$.\footnote{Note that domain separation can be used here to take one $\mathcal{H}^s$ and construct each $\mathcal{H}^s_j$ by defining $\mathcal{H}^s_j(x) := \mathcal{H}^s(j \mid\mid x)$.}
+\item $\texttt{Setup} \to \textit{par}$.
+$\texttt{Setup}$ selects a prime $p$, a group $\mathbb{G}$ with prime order $p$, selects a group generator $G \in \mathbb{G}$ uniformly at random, selects $d$ cryptographic hash functions $\mathcal{H}^s_0, \ldots, \mathcal{H}^s_{d-1}$ with codomain $\mathbb{F}_p$, selects a cryptographic hash function $\mathcal{H}^p$ with codomain $\mathbb{G}$.
+$\texttt{Setup}$ outputs the group parameter tuple and the hash functions, $\textit{par} := \left(p,\mathbb{G}, d, G, \left\{\mathcal{H}^s_j\right\}_{j=0}^{d-1}, \mathcal{H}^p\right)$.\footnote{Note that domain separation can be used here to take one $\mathcal{H}^s$ and construct each $\mathcal{H}^s_j$ by defining $\mathcal{H}^s_j(x) := \mathcal{H}^s(j \mid\mid x)$.}
 
-\item $\texttt{KeyGen}(1^\lambda, \textit{par}) \to (\textbf{sk}, \textbf{pk})$.
-$\texttt{KeyGen}$ takes as input the security parameter $1^\lambda$, public parameters $\textit{par}$.
-$\texttt{KeyGen}$ samples $\textbf{sk} \leftarrow (\mathbb{Z}/p\mathbb{Z})^d$, which we denote $\textbf{sk} = (x, z_1, \ldots, z_{d-1})$, and computes $\textbf{pk} := \textbf{sk} \circ \textbf{G}$ for $\textbf{G} = (G, G, \ldots, G) \in \mathbb{G}^d$.
+\item $\texttt{KeyGen} \to (\textbf{sk}, \textbf{pk})$. When queried for a new key, $\texttt{KeyGen}$ samples a fresh secret key and computes the associated public key:
+\begin{align*}
+\textbf{sk} =& (x, z_1, \ldots, z_{d-1}) \leftarrow (\mathbb{F}_p^*)^d\\
+\textbf{pk} :=& \textbf{sk} \circ \textbf{G} = (X, Z_1, \ldots, Z_{d-1}) \in \mathbb{G}^d
+\end{align*} where $\textbf{G} = (G, \ldots, G) \in \mathbb{G}^d$.
 $\texttt{KeyGen}$ outputs $(\textbf{sk}, \textbf{pk})$.
@@
 
-\item $\texttt{Sign}\left(1^\lambda, \textit{par}, (m, \underline{\textbf{pk}}, \textbf{sk})\right) \to \left\{\bot_{\texttt{Sign}}, (\sigma, \mathfrak{T})\right\}$.
-$\texttt{Sign}$ takes as input the security parameter $1^\lambda$, public parameters $\textit{par}$, a message $m \in \left\{0,1\right\}^*$, a matrix of public keys $\underline{\textbf{pk}} = (\textbf{pk}_1, \ldots, \textbf{pk}_n)$ where each $\textbf{pk}_i = (X_i, Z_{i,1}, \ldots, Z_{i,d-1}) \in \mathbb{G}^d$, and a secret key vector $\textbf{sk} = (x,z_1, \ldots, z_{d-1}) \in (\mathbb{Z}/p\mathbb{Z})^d$.
+\item $\texttt{Sign}\left(m, \underline{\textbf{pk}}, \textbf{sk}\right) \to \left\{\bot_{\texttt{Sign}}, \sigma\right\}$.
+$\texttt{Sign}$ takes as input a message $m \in \left\{0,1\right\}^*$, a ring  $\underline{\textbf{pk}} = (\textbf{pk}_1, \ldots, \textbf{pk}_n)$ for ring members $\textbf{pk}_i = (X_i, Z_{i,1}, \ldots, Z_{i,d-1}) \in \mathbb{G}^d$, and a secret key $\textbf{sk} = (x,z_1, \ldots, z_{d-1}) \in (\mathbb{F}_p^*)^d$.
 $\texttt{Sign}$ does the following.
@@
 \begin{enumerate}
-\item $\texttt{Sign}$ looks for the signing index $\ell$ such that $(x, z_1, \ldots, z_{d-1}) \circ (G, G, \ldots, G) = \textbf{pk}_\ell$.
-If no such index exists, $\texttt{Sign}$ outputs $\bot_{\texttt{Sign}}$ and terminates.
+\item If $\underline{\textbf{pk}} \notin \mathbb{G}^{d\times n}$ for some $n$, $\texttt{Sign}$ outputs $\bot_{\texttt{Sign}}$ and terminates.
 
-\item Otherwise, $\texttt{Sign}$ samples $\alpha \in \mathbb{Z}/p\mathbb{Z}$ and $\left\{s_i\right\}_{i \neq \ell} \in (\mathbb{Z}/p\mathbb{Z})^{n-1}$.
+\item Otherwise, $\texttt{Sign}$ parses\footnote{Note that this parsing always succeeds if $\texttt{Sign}$ does not fail in the previous step.} $\underline{\textbf{pk}}$ to obtain each $\textbf{pk}_i$.
+If the public key associated with the input $\textbf{sk}$ is not a ring member in $\underline{\textbf{pk}}$, then $\texttt{Sign}$ outputs $\bot_{\texttt{Sign}}$ and terminate.
 
-\item $\texttt{Sign}$ computes the \textit{aggregation coefficients} $\mu_X$ and $\{\mu_j\}_{j=1}^{d-1}$, the \textit{linkability tag} or \textit{key image} $\mathfrak{T}$, and auxiliary key images $\{\mathfrak{D}_j\}_{j=1}^{d-1}$:
+\item Otherwise, $\texttt{Sign}$ finds the signing index $\ell$ such that $\textbf{pk}_\ell = \textbf{sk} \circ (G, \ldots, G)$.
+$\texttt{Sign}$ samples $\alpha \in \mathbb{F}_p$, samples $\left\{s_i\right\}_{i \neq \ell} \in (\mathbb{F}_p)^{n-1}$, and computes the points $H_i = \mathcal{H}^p(X_i)$ for each $i$.
+$\texttt{Sign}$ computes the \textit{aggregation coefficients} $\mu_X$ and $\{\mu_j\}_{j=1}^{d-1}$, the key image $\mathfrak{T}$, the auxiliary key images $\{\mathfrak{D}_j\}_{j=1}^{d-1}$, the aggregated public keys and their key images:
 \begin{align*}
-\mathfrak{T} \leftarrow& x \mathcal{H}^p(X_\ell) & \mu_X \leftarrow& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}) \\
-\{\mathfrak{D}_j\} \leftarrow&  \{z_j \mathcal{H}^p(X_\ell)\} & \mu_j \leftarrow& \mathcal{H}^s_1(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}).
-\end{align*}
+\mathfrak{T} :=& x H_\ell & \{\mathfrak{D}_j\} :=&  \{z_j H_\ell\} \\
+\mu_X :=& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}) 
+ & \mu_j :=& \mathcal{H}^s_j(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}) \\
+ W_i :=& \mu_X X_i + \sum_{j=1}^{d-1} \mu_j Z_{i,j} & \mathfrak{W} :=& \mu_X \mathfrak{T} + \sum_{j=1}^{d-1} \mu_j \mathfrak{D}_j
+ \end{align*} and the aggregated secret key $w_\ell :=  \mu_X x + \sum_{j=1}^{d-1} \mu_j z_j$.
+For $i = \ell, \ell+1, \ldots, \ell-1$, (and by identifying index $n+1$ with index $1$), $\texttt{Sign}$ computes
+\begin{align*}
+L_\ell =& \alpha G & R_\ell =& \alpha H_\ell & c_{\ell+1} =& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid m \mid \mid L_\ell \mid \mid R_\ell) \\ 
+L_i =& s_i G + c_i W_i & R_i =& s_i H_i + c_i \mathfrak{W}  
+ & c_{i+1} =& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid m \mid \mid L_i \mid \mid R_i)
+\end{align*} and lastly computes $s_\ell = \alpha - c_\ell w_\ell$.
 
-\item For $i = \ell, \ell+1, \ldots, \ell-1$, identifying index $n$ with index $1$ as usual, $\texttt{Sign}$ computes
-\begin{align*}
-L_\ell =& \alpha G & L_i =& s_i G + c_i \left(\mu_X X_i + \sum_{j=1}^{d-1} \mu_jZ_{i,j}\right)\\
-R_\ell =& \alpha \mathcal{H}^p(X_\ell) & R_i =& s_i \mathcal{H}^p(X_i) + c_i \left(\mu_X \mathfrak{T} + \sum_{j=1}^{d-1} \mu_j \mathfrak{D}_j\right) \\
-c_{\ell+1} =& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid m \mid \mid L_\ell \mid \mid R_\ell) & c_{i+1} =& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid m \mid \mid L_i \mid \mid R_i)
-\end{align*} and lastly computes $s_\ell = \alpha - c_\ell (\mu_X x_\ell + \sum_{j=1}^{d-1} \mu_jz_{\ell,j})$.
-
-\item $\texttt{Sign}$ sets the signature $\sigma = (c_1, s_1, \ldots, s_n, \{\mathfrak{D}_j\}_{j=1}^{d-1})$ and publishes the signature-tag pair $(\sigma, \mathfrak{T})$.
+\item $\texttt{Sign}$ sets the signature $\sigma = (c_1, s_1, \ldots, s_n, \mathfrak{T}, \{\mathfrak{D}_j\}_{j=1}^{d-1})$ and publishes the signature $\sigma$.
 \end{enumerate}
 
-\item $\texttt{Verify}\left(1^\lambda, \textit{par}, m, \underline{\textbf{pk}}, (\sigma, \mathfrak{T})\right) \to \left\{0,1\right\}$.
-$\texttt{Verify}$ takes as input the security parameter $1^\lambda$, public parameters $\textit{par}$, a message $m$, a matrix $\underline{\textbf{pk}} = ((X_i, Z_{i,1}, \ldots, Z_{i,d-1}))_{i=1}^{n}$, and a signature-tag pair $(\sigma, \mathfrak{T})$.
-$\texttt{Verify}$ does the follwoing.
+\item $\texttt{Verify}\left(m, \underline{\textbf{pk}}, \sigma\right) \to \left\{0,1\right\}$.
+$\texttt{Verify}$ takes as input a message $m$, a matrix $\underline{\textbf{pk}} = (\textbf{pk}_1, \ldots, \textbf{pk}_n)$, and a signature $\sigma$.
 
 \begin{enumerate}
-\item If $n > N$, or any coordinate of any ring member is not in $\mathbb{G}$, or if $\sigma$ cannot be parsed as $(c_1, s_1, \ldots, s_n, \mathfrak{D}_1, \ldots, \mathfrak{D}_{d-1})$ for some $c_1 \in \mathbb{Z}/p\mathbb{Z}$, some $s_i \in \mathbb{Z}/p\mathbb{Z}$, and some $\mathfrak{D}_j \in \mathbb{G}$, or if $\mathfrak{T} \notin \mathbb{G}$, $\texttt{Verify}$ produces $0$ as output and terminates.
+\item If $\underline{\textbf{pk}} \notin \mathbb{G}^{d \times n}$ for some $n$, or if $\sigma \notin \mathbb{F}_p^{n^\prime+1} \times \mathbb{G}^d$ for some $n^\prime$, $\texttt{Verify}$ outputs $0$ and terminates.
+Otherwise, if $n^\prime \neq n$, $\texttt{Verify}$ outputs $0$ and terminates.
 
-\item Otherwise, $\texttt{Verify}$ parses $(c_1, s_1, \ldots, s_n, \{\mathfrak{D}_j\}_{j=1}^{d-1}) \leftarrow \sigma$, computes each $\mathcal{H}^p(X_i)$, and compute the aggregation coefficients as above.
+\item $\texttt{Verify}$ parses\footnote{This parsing is always successful if the previous step does not terminate $\texttt{Verify}$.} $(\textbf{pk}_1, \ldots, \textbf{pk}_n) \leftarrow \underline{\textbf{pk}}$ for keys $\textbf{pk}_i \in \mathbb{G}^d$ for $i=1, \ldots, n$, and parses each public key $(X_i, Z_{i, 1}, \ldots, Z_{i, d-1}) \leftarrow \textbf{pk}_i$.
+$\texttt{Verify}$ also parses $(c_1, s_1, \ldots, s_n, \mathfrak{T}, \mathfrak{D}_1, \ldots, \mathfrak{D}_{d - 1}) \leftarrow \sigma$.
+$\texttt{Verify}$ computes each $H_i = \mathcal{H}^p(X_i)$, computes the aggregation coefficients, and computes aggregated public keys and their images:
+\begin{align*}
+\mu_X := & \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}) & \mu_j := & \mathcal{H}^s_j(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1})\\
+W_i :=& \mu_X X_i + \sum_{j=1}^{d-1} \mu_j Z_{i,j} & \mathfrak{W} :=& \mu_X \mathfrak{T} + \sum_{j=1}^{d-1} \mu_j \mathfrak{D}_j 
+\end{align*}
 
@@
 \begin{align*}
-L_i :=& s_i G + c_i^\prime \left(\mu_X X_i + \sum_{j=1}^{d-1} \mu_jZ_{i,j}\right) \\ 
-R_i :=& s_i \mathcal{H}^p(X_i) + c_i^\prime\left(\mu_X \mathfrak{T} + \sum_{j=1}^{d-1} \mu_j \mathfrak{D}_j\right)\\
+L_i :=& s_i G + c_i^\prime W_i, &
+R_i :=& s_i H_i + c_i^\prime\mathfrak{W}, &
 c_{i+1}^\prime :=& \mathcal{H}^s_0\left(\underline{\textbf{pk}} \mid \mid m \mid \mid L_i \mid \mid R_i\right)
 \end{align*}
-\item If $c_{n+1}^\prime = c_1$, $\texttt{Verify}$ produces $1$ as output. Otherwise, $\texttt{Verify}$ produces $0$ as output.
+\item If $c_{n+1}^\prime = c_1$, $\texttt{Verify}$ outputs $1$, and otherwise outputs $0$.
 \end{enumerate}
 
-\item $\texttt{Link}\left(1^\lambda, \textit{par}, (\sigma_1, \mathfrak{T}_1), (\sigma_2, \mathfrak{T}_2)\right) \to \left\{0,1\right\}$.
-$\texttt{Link}$ takes as input the security parameter $1^\lambda$, public parameters $\textit{par}$, and two signature-tag pairs $((\sigma_1, \mathfrak{T}_1), (\sigma_2, \mathfrak{T}_2))$.
-If $\mathfrak{T}_1 \in \mathbb{G}$ and $\mathfrak{T}_2 \in \mathbb{G}$ and $\mathfrak{T}_1 = \mathfrak{T}_2$, $\texttt{Link}$ produces $1$ as output.
-Otherwise, $\texttt{Link}$ produces $0$ as output.
+\item $\texttt{Link}\left((m, \underline{\textbf{pk}}, \sigma), (m^\prime, \underline{\textbf{pk}}^\prime, \sigma^\prime)\right) \to \left\{0,1\right\}$.
+$\texttt{Link}$ takes as input two message-ring-signature triples.
+\begin{enumerate}
+\item If $\texttt{Verify}(m, \underline{\textbf{pk}}, \sigma) = 0$ or $\texttt{Verify}(m^\prime, \underline{\textbf{pk}}^\prime, \sigma^\prime) = 0$, $\texttt{Link}$ outputs $0$ and terminates.
+
+\item Otherwise, $\texttt{Link}$ parses\footnote{As before with $\texttt{Verify}$, this parsing is always successful if the previous step does not terminate $\texttt{Link}$.} the signatures to obtain
+\begin{align*}
+(c_1, s_1, \ldots, s_n, \mathfrak{T}, \mathfrak{D}_1, \ldots, \mathfrak{D}_{d-1}) \leftarrow&  \sigma\text{ and}\\
+(c_1^\prime, s_1^\prime, \ldots, s_n^\prime, \mathfrak{T}^\prime, \mathfrak{D}_1^\prime, \ldots, \mathfrak{D}_{d-1}^\prime) \leftarrow& \sigma^\prime.
+\end{align*} $\texttt{Link}$ outputs $1$ if $\mathfrak{T} = \mathfrak{T}^\prime$ and $0$ otherwise.
+\end{enumerate}
 \end{itemize}
+\end{definition}
 
-\end{defn}
-
-We use the usual definition of correct verification and correct linkability, both of which are straightforward to verify directly from the implementation.
 Later, we discuss the security of this implementation.
 
-\begin{remark}
-It may be possible to compress signatures further by  computing the coefficients $\mu_j$ without the inputs $\mathfrak{D}_j$ and publishing $\sigma = (c_1, s_1, \ldots, s_n, \sum_j \mu_j \mathfrak{D}_j)$ only, reducing signature sizes for $d > 1$ further.
+\subsection{Efficiency}
+Consider the space and time efficiency of Definition \ref{def:clsag}. We disregard additional information broadcast alongside the signature, such as descriptions of the ring members.
 
-The security of this variant is not proven here and is a good avenue for future work. The variant is not relevant for Monero, since $d=1$ for single-asset ring confidential transactions.
-\end{remark}
+A $d$-CLSAG signature with a ring size of $n$ contains $n+1$ scalars and $d$ group elements, so this scheme is compact; signature size is $k_s(n+1) + k_p d$ where $k_s$ describes the size of scalar field elements and $k_p$ describes the size of points on the curve.
 
-\begin{remark}
-
-Note that the signature is computed with the aggregated secret $w = \mu_X x_\ell + \sum_j \mu_j z_{\ell,j}$. This method of aggregating keys has two properties of importance.
-
-First, under the random oracle model, the map defined by mapping $(x, z_1, \ldots, z_{d-1}) \mapsto w$ is collision resistant and anyone with knowledge of $(x_\ell, z_{\ell,1}, \ldots, z_{\ell,d-1})$ can compute the aggregated secret key $w$.
-More than one choice of $(x_\ell, z_{\ell,1}, \ldots, z_{\ell,d-1})$ could map to the same aggregated key, but collision resistance implies second pre-image resistance.
-Hence, given some $W = wG$ for an unknown aggregated secret key $w$ aggregated from some secret key $(x_\ell, z_{\ell,1}, \ldots, z_{\ell,d-1})$, an attacker has at most a negligible chance of finding a second secret key $(x_\ell^\prime, z_{\ell,1}^\prime, \ldots, z_{\ell,d-1}^\prime)$ that aggregates to the same secret $w$.
-This prevents the attacker from using an adversarially generated secret key that coincidentally aggregates to the same $w$ as some challenge key.
-
-Second, under the random oracle model, the map is resistant to key cancellation.
-That is to say, an attacker has at most a negligible chance of selecting a secret key $(x_\ell, z_{\ell, 1}, \ldots, z_{\ell, d-1})$ with coordinates that cancel in the sum $w$; except with negligible probability, $w$ is dependent upon all bits of all coordinates of a secret key $(x, z_1, \ldots, z_{d-1})$.
-
-\end{remark}
-
-\subsection{Efficiency}
-
-Consider the space and time efficiency of Definition \ref{def:clsag}.
-A $d$-CLSAG signature with a ring size of $n$ contains $n+1$ scalars and $d$ group elements, so this scheme is compact.
-In practice, signatures are broadcast with additional information such as references to the ring members.
-However, this is outside the scope of our definitions.
-
-To examine the verification time complexity, let $k_s$ and $k_p$ be the time complexity of evaluating the hash-to-scalar functions $\mathcal{H}^s$ and of evaluating the hash-to-point function $\mathcal{H}^p$, respectively.
-Let $k^{(i)}$ be the time complexity to evaluate a scalar-point linear combination of $i$ terms; using specialized algorithms like Straus or Pippenger multiexponentiation (or others, based on $i$), such a linear combination can be evaluated much more quickly than a simple term-by-term computation.
+To examine the verification time complexity, instead let $k_s$ and $k_p$ be the time complexity of evaluating the hash-to-scalar functions $\mathcal{H}^s$ and of evaluating the hash-to-point function $\mathcal{H}^p$, respectively.
+Let $k^{(i)}$ be the time complexity to evaluate a scalar-point linear combination of $i$ terms; using specialized algorithms like Straus \cite{straus} or Pippenger \cite{pippenger} multiexponentiation (or others, based on $i$), such a linear combination can be evaluated much more quickly than a simple term-by-term computation.
 We note that it is also possible to cache multiples of points that are reused within verification for faster linear combination evaluation, but we do not differentiate this here.
@@
 
-To compare to the current MLSAG scheme in Monero, note that $2$-CLSAG has equivalent functionality. The current Monero implementation requires $2n+1$ scalars and $1$ group element.
+To compare to the efficiency of an MLSAG implementation, note that $2$-CLSAG has equivalent functionality to an MLSAG signature (which is a $2$-LRS).
+An MLSAG signature used in this way requires $2n+1$ scalars and $1$ group element.
 
-To determine the feasibility of implementation in Monero, we produced a test implementation using the Monero codebase and tested signing and verification for MLSAG and $2$-CLSAG on a 2.1 GHz Opteron processor.
+We produced a test implementation in C++ and tested signing and verification for MLSAG and $2$-CLSAG on a 2.1 GHz Opteron processor.
 Table \ref{table:timing} shows the results for different ring sizes.
-In particular, we note that for ring sizes of interest to Monero (the current network-enforced size is $11$), CLSAG is uniformly faster than MLSAG.
+In particular, we note that for smaller anonymity sizes, CLSAG is uniformly faster than MLSAG.
 However, at very large ring sizes, MLSAG is faster due to additional computations involved in computing aggregation coefficients and key prefixing.
@@
 \hline
-Ring size & MLSAG & CLSAG & MLSAG & CLSAG \\
+Anonymity set & MLSAG & CLSAG & MLSAG & CLSAG \\
 \hline
@@
 \section{Applications}
-
 \subsection{Single-asset ring confidential transactions}\label{sec:ringct}
-
-As mentioned above, it is possible to use $2$-CLSAG as a replacement for MLSAG signatures in Monero for equivalent functionality.
-Currently, Monero uses MLSAG signatures for two different transaction types: full and simple.
+As mentioned above, it is possible to use $2$-CLSAG as a replacement for MLSAG signatures in  ledger applications (like Monero) for equivalent functionality.
+For example, Monero currently uses MLSAG signatures for two different transaction types: full and simple.
 
@@
 
-Both transaction types can be used with $2$-CLSAG, since linkability is not considered for the second key component used in the transaction protocols.
+Both transaction types can be constructed with $2$-CLSAG signatures since linkability is not considered for the second key component used in the transaction protocols.
 
-\subsection{Multi-asset ring confidential transactions (MARCTs)}
-
+\subsection{Multi-asset ring confidential transactions (MARCTs)}\label{sec:marct}
 It is possible to use a straightforward $d$-CLSAG construction to accommodate transactions spending $d-1$ \textit{types} or \textit{colors} of assets separately within the same transaction and signature.
-To do so, Monero outputs are extended to have a separate commitment to each asset type value.
+To do so, transaction outputs are extended to have a separate commitment to each asset type value.
 When spending an output, either a full or simple transaction (discussed above) is used; we simply copy the method used to compute commitment public keys in the signature to additional dimensions of the $d$-CLSAG signature, using only the commitments for a particular asset type in each.
@@
 
-\subsubsection{Informal description of MARCT implementation}\label{ex:dualasset}
-
-In this section, we leverage $\Pi_C^{(d)}$ for use in ring confidential transactions on $d-1$ different assets (or colors) with a pegged exchange rate between colors.
-We analyze the cost (in terms of weight and sync time) to the blockchain of our proposal compared to a similar proposal using $d$-MLSAG signatures.
-We present only the case $d=3$ in this section to represent two colors, leaving extensions for future work.
-
-Consider the canonical example of colored currency with a fixed peg between two colors: dollars and pennies with a $100:1$ exchange rate between them.
-Define an exchange rate by determining some constants $\gamma_C, \gamma_D$ on $\left\{1, 2, \ldots, 2^{\xi - 1}\right\}$, (in this example, $\gamma_C = 1$ and $\gamma_D = 100$).
-Let $G, G^\prime$ be public group elements with unknown discrete logarithms with respect to each other where $G$ is the output from $\texttt{Setup}$ for a $d$-CLSAG.
+\subsection{Informal description of MARCTs with unmixable colors}
+We informally describe an example of MARCTs with two unmixable colors using $3$-CLSAG.
 Let $(\texttt{Prove}, \texttt{Ver})$ be a zero-knowledge sound range proving scheme, such as that described in \cite{bulletproofs}, and let $(\texttt{Com}, \texttt{Open})$ be a Pedersen commitment scheme such that $\texttt{Com}(r,v) = rG + v G^\prime$.
 
-For the sake of this example, we define a public trading key to be a tuple $(X, C, D, P)$ where $X, C, D \in \mathbb{G}$, $C$ and $D$ are commitments and $P$ is a batched range proof from $\texttt{Prove}$ covering the values of both $C$ and $D$.
-We define a transaction key to be a tuple $(m, \textbf{Q}, \textbf{O}, (f_C, f_D), (\sigma, \mathfrak{T}), \textit{aux})$ where $\textbf{Q}$ is a ring of $n$ public trading keys  $\textbf{Q} = \left\{(X_i, C_i, D_i, P_i)\right\}_{i=1}^{n}$, $\textbf{O}$ is a set of $n^\prime$ output public trading keys $\textbf{O} = \left\{(X_i^\prime, C_i^\prime, D_i^\prime, P_i^\prime)\right\}_{i=1}^{n^\prime}$, $f_C$ is a plaintext list of fees to be paid from $C$, $f_D$ is a plaintext list of fees to be paid from $D$, $S=(\sigma, \mathfrak{T})$ is a CLSAG signature-tag pair.
+For the sake of this example, we define a public trading key to be a tuple $(X, C, D, P)$ where $X, C, D \in \mathbb{G}$, $C$ and $D$ are amount commitments and $P$ is a batched range proof from $\texttt{Prove}$ covering the values of both $C$ and $D$.
+Here, $C$ and $D$ play the role of the $Z_j$ points, and $P$ is additional data required for the transaction protocol.
 
+We define a transaction key to be a tuple $(m, \textbf{Q}, \textbf{O}, (f_C, f_D), \sigma, \textit{aux})$ where $\textbf{Q}$ is a ring of $n$ public trading keys  $\textbf{Q} = \left\{(X_i, C_i, D_i, P_i)\right\}_{i=1}^{n}$, $\textbf{O}$ is a set of $n^\prime$ output public trading keys $\textbf{O} = \left\{(X_i^\prime, C_i^\prime, D_i^\prime, P_i^\prime)\right\}_{i=1}^{n^\prime}$, $f_C$ is a plaintext list of fees to be paid from $C$, $f_D$ is a plaintext list of fees to be paid from $D$, and $\sigma$ is a $3$-CLSAG signature.
+We say a transaction key is valid if the following are satisfied:
+\begin{itemize}
+\item every input ring member $(X_i, C_i, D_i, P_i) \in \textbf{Q}$ has a valid range proof $P_i$ so $\texttt{Ver}(P_i) = 1$; and
+\item every output range proof $P_k^\prime$ is valid so $\texttt{Ver}(P_k^\prime)=1$; and
+\item for the ring \[\textbf{pk} = \begin{pmatrix} X_1 & X_2 & \cdots & X_n \\ Z_1 & Z_2 & \cdots & Z_n \\ Z_1^\prime & Z_2^\prime & \cdots & Z_n^\prime\end{pmatrix}\] where each $Z_i = C_i - f_C G^\prime - \sum_k C_k^\prime$ and each $Z_i^\prime = D_i - f_D G^\prime - \sum_k D_k^\prime$,  $\texttt{Verify}(m, \underline{\textbf{pk}}, \sigma) = 1$.
+\end{itemize}
+
+This $3$-CLSAG signature demonstrates knowledge of the discrete logarithm of some $x_\ell$, knowledge of the opening information for the input and output commitments, and that the transaction amounts balance  with the fees $f_C$ and $f_D$.
+After all, when the amounts in $C_\ell$ and $D_\ell$ balance with the fees $f_C$ and $f_D$ together with the sum of the amounts in each $C_k^\prime$ and $D_k^\prime$, and when the signer knows all the openers for all these commitments, $Z_\ell$ and $Z_\ell^\prime$ can be regarded as usual public keys with basepoint $G$ whose secret key is known by the signer.
+
+Unfortunately, this model does not allow for exchanging amounts of the first color with amounts of the second color.
+In the next section, we present another toy model that allows for transferring between colors at a fixed/pegged exchange rate.
+
+\subsubsection{Informal description of MARCTs with a fixed exchange rate}\label{ex:dualasset}
+We modify the previous example to use a $2$-CLSAG.
+Consider the canonical example of colored currency with a fixed peg between two colors: dollars and pennies with a $100:1$ exchange rate between them.
+Define an exchange rate by determining a constant $\xi$ and some constants $\gamma_C, \gamma_D$ on $\left\{1, 2, \ldots, 2^{\xi - 1}\right\}$, (in this example, $\gamma_C = 1$ and $\gamma_D = 100$).
+
+As before, we define a public trading key to be a tuple $(X, C, D, P)$ and a transaction key to be a tuple $(m, \textbf{Q}, \textbf{O}, (f_C, f_D), \sigma, \textit{aux})$.
+We interpret these identically as in the previous step, except using $2$-CLSAG signatures instead of $3$-CLSAG signatures, and of course we compute them differently.
 We say a simple transaction key is valid if the following are satisfied:
@@
 \item every output range proof $P_k^\prime$ is valid so $\texttt{Ver}(P_k^\prime)=1$; and
-\item the signature-tag pair $(\sigma, \mathfrak{T})$ passes $d$-CLSAG verification $\texttt{Verify}(m, \underline{\textbf{pk}}, (\sigma, \mathfrak{T})) = 1$ for the modified ring \[\textbf{pk} = \begin{pmatrix} X_1 & X_2 & \cdots & X_n \\ Z_1 & Z_2 & \cdots & Z_n\end{pmatrix}\] where each $Z_i = \gamma_C (C_i - f_C G^\prime - \sum_k C_k^\prime) + \gamma_D ( D_i - f_D G^\prime - \sum_k D_k^\prime)$.
+\item for the modified ring \[\textbf{pk} = \begin{pmatrix} X_1 & X_2 & \cdots & X_n \\ Z_1 & Z_2 & \cdots & Z_n\end{pmatrix}\] where each $Z_i = \gamma_C (C_i - f_C G^\prime - \sum_k C_k^\prime) + \gamma_D ( D_i - f_D G^\prime - \sum_k D_k^\prime)$, the signature $\sigma$ passes the $2$-CLSAG verification, $\texttt{Verify}(m, \underline{\textbf{pk}}, \sigma) = 1$ .
 \end{itemize}
 
-As before, this CLSAG signature demonstrates knowledge of the discrete logarithm of some $x_\ell$, knowledge of the opening information for the input and output commitments, and that the opening information for the commitments balance with the fees $f_C$ and $f_D$.
-After all, when the amounts in $C_\ell$ and $D_\ell$ balance with the fees $f_C$ and $f_D$ together with the sum of the amounts in each $C_k^\prime$ and $D_k^\prime$, and when the signer knows all the openers for all these commitments, the point $\gamma_C(C_\ell - f_C G^\prime - \sum_k C_k^\prime) + \gamma_D(D_\ell - f_D G^\prime - \sum_k D_k^\prime)$ will be a usual public key with basepoint $G$ whose secret key is known by the signer.
-
-\subsubsection{Flexible pegs, coin spectra, privacy, and further extensions}
-
-The validity of a MARCT without any exchange at all between assets is also possible, allowing for assets to be segregated.
-
-On the other hand, different exchange coefficients $\gamma_C$ and $\gamma_D$ are certainly possible.
-Just so long as there is a way for validators to come to an agreement upon exchange rate coefficients, validators can also convince themselves that transactions accordingly balance.
-Extending the model of simple ring confidential transactions with two colors to more than two colors is a straightforward exercise.
-
-Further extensions with more immediate value may be possible.
-One open question is how to modify the above scheme to mask exchange rates.
-Another open question involves formalizing flexible-peg models of full colored ring confidential transactions between many colors (a spectrum?).
-These extensions represent fundamental building blocks for a system of smart transactions that respect user privacy.
+Unlike the previous example, this example allows for the fixed exchange rate between colors determined by $\gamma_C$ and $\gamma_D$.
 
@@
 
-\section{Security: Unforgeability}
+\section{Security: Unforgeability}\label{app:unf}
+We prove the unforgeability of our implementation in Definition \ref{def:clsag}.
+A good forgery game should grant the adversary the power to persuade otherwise honest users to hand over their keys (modeled by a corruption oracle) or sign adversarially selected messages with adversarially selected rings (modeled by a signing oracle), and our algorithm is based on the random oracle model.
+Of course, any oracle queries made by a forgery algorithm $\texttt{A}$ being run in a black box must be handled by whatever algorithm is executing $\texttt{A}$, so we describe how these are simulated in Section \ref{app:oracles}.
 
-\subsection{Hardness}
-
+\subsection{Hardness Assumption}
 Unforgeability comes from the $k$-OMDL hardness assumption.
 
-\begin{defn}[k-OMDL problem]
+\begin{definition}[k-OMDL problem]
 Let $k \in \mathbb{N}$.
@@
 \begin{enumerate}
-\item The challenger uses group parameters $(p, \mathbb{G}, G)$ and picks $G_1, G_2, \ldots, G_{k}, G_{k+1} \in \mathbb{G}$ (the targets) uniformly at random from $\mathbb{G}$.
+\item The challenger uses group parameters $(p, \mathbb{G}, G)$ and picks group elements $G_1, G_2, \ldots, G_{k}, G_{k+1} \in \mathbb{G}$ (the targets) uniformly at random from $\mathbb{G}$.
 The challenger sends the group parameters and $\left\{G_i\right\}$ to $\texttt{A}$.
 
-\item $\texttt{A}$ is granted access to a corruption oracle $\mathcal{CO}$ that takes as input some $G_i$ sent to $\texttt{A}$ and produces as output the discrete logarithm of $G_i$ with respect to $G$, i.e.\ some $x_i \in \mathbb{Z}/p\mathbb{Z}$ such that $G_i = x_i G$.
+\item $\texttt{A}$ is granted access to a corruption oracle $\mathcal{CO}$ that takes as input some $G_i$ sent to $\texttt{A}$ and produces as output the discrete logarithm of $G_i$ with respect to $G$, \textit{i.e.}\ some $x_i \in \mathbb{F}_p^*$ such that $G_i = x_i G$.
 
-\item $\texttt{A}$ produces as output a sequence of $k+1$ scalars $x_1, \ldots, x_{k+1} \in \mathbb{Z}/p\mathbb{Z}$, counting as a success if:
+\item $\texttt{A}$ produces as output a sequence of $k+1$ scalars $x_1, \ldots, x_{k+1} \in \mathbb{F}_p^*$, counting as a success if:
 \begin{enumerate}[(i)]
-\item for each $x_i$, there exists some index $1 \leq j(i) \leq k+1$ such that $G_{j(i)} = xG$ and
+\item for each $x_i$, there exists some index $1 \leq j(i) \leq k+1$ such that $G_{j(i)} = x_iG$ and
 \item $\texttt{A}$ made no more than $k$ queries to $\mathcal{CO}$. 
@@
 \end{enumerate}
-\end{defn}
+\end{definition}
+
+\subsection{The Oracles}\label{app:oracles}
+Random oracle queries made by $\texttt{A}$ are handled by looking to a random tape $\textbf{h}$ available to the simulator to generate hashes for new queries made to the oracle $\mathcal{H}^s$.
+These are stored in a hash table for consistency in later queries.
+We assume whatever algorithm is executing $\texttt{A}$ in a black box has pre-generated a set of private-public key pairs for use in simulating a corruption oracle $\mathcal{CO}$ for $\texttt{A}$.
+This leaves only the signing oracle, which is simulated through back-patching in the following way.
+
+The simulator reserves the next random oracle query on the random tape $\textbf{h}$ to select $c_{\ell+1}$ for back-patching.
+The random signature data $\alpha$ and $\left\{s_i\right\}_{i \neq \ell}$ are sampled as usual, and each challenge $c_{i+1}$ for $i \neq \ell$ is simulated from $\textbf{h}$ as described before and stored in a hash table.
+After all challenges are computed, the simulator compute the group points $L_\ell, R_\ell$, and back-patches their hash table to force $\mathcal{H}^s(\underline{\textbf{pk}} \mid \mid m \mid \mid L_\ell \mid \mid R_\ell) \leftarrow c_{\ell+1}$.
 
@@
 We use a modified version of the definition of existential forgery with insider corruption for a ring signature by Bender, Katz, and Morselli \cite{bender}.
-By using linkability tags, our definition is slightly stronger; we allow forgeries to count as successful either with partially-corrupted rings or with messages that the signing oracle has signed before, just so long as neither the signature nor the linkability tag from the forgery appear as output from any oracle query in any transcript.
-This prevents a malicious party with the ability to persuade users to sign maliciously selected messages with maliciously selected ring members from constructing ostensibly valid, previously-unseen signature-tag pairs.
+In contrast with the definition of unforgeability with respect to insider corruption in \cite{bender}, our modification allows for a forger to succeed at the forgery game with partially corrupted rings.
 
-We use the following in the next definition.
 Let $n(-)$ be a positive polynomial.
-Let $\mathcal{H}^s:\left\{0,1\right\}^* \to \mathbb{Z}/p\mathbb{Z}$ be modeled as a random oracle.
-Let $\mathcal{CO}$ be a corruption oracle that takes as input a public key $\textbf{pk}$ and produces as output the corresponding secret key $\textbf{sk}$ and the linkability tag $\mathfrak{T}$.
-Let $C$ be the set of all keys in the transcript of queries made by $\texttt{A}$ to $\mathcal{CO}$.
-Let $T_C$ be the set of all linkability tags that appear as output from such a query.
-Let $\mathcal{SO}$ be a signing oracle that takes as input some $(m, \underline{\textbf{pk}}^\prime, \ell)$ such that $pk_\ell \in \underline{\textbf{pk}} \cap \underline{\textbf{pk}^\prime}$ and produces as output a signature-tag pair $(\sigma, \mathfrak{T})$ such that $\texttt{Verify}(m, \underline{\textbf{pk}}^\prime, \sigma, \mathfrak{T}) = 1$.
+Let $\mathcal{H}^s:\left\{0,1\right\}^* \to \mathbb{F}_p$ be modeled as a random oracle.
+Let $\mathcal{CO}$ be a corruption oracle that takes as input a public key $\textbf{pk}$ from the list of challenge keys and produces as output the corresponding secret key $\textbf{sk}$ and the key image $\mathfrak{T}$.
+Let $\mathcal{SO}$ be a signing oracle that takes as input some $(m, \underline{\textbf{pk}}^\prime, \ell)$ such that $\underline{\textbf{pk}^\prime}$ is a matrix of challenge key vectors (\textit{i.e.}\ each column is in $\textbf{pk}$) and produces as output a signature $\sigma$ such that $\texttt{Verify}(m, \underline{\textbf{pk}}^\prime, \sigma) = 1$ and such that the key image $\mathfrak{T} \in \sigma$ is the key image for the $\ell^{th}$ key in $\underline{\textbf{pk}}^\prime$.
 
-\begin{defn}[Existential unforgeability of linkable ring signatures with respect to insider corruption]\label{def:unf}
+\begin{definition}[Existential unforgeability of linkable ring signatures with respect to insider corruption]\label{def:unf}
 
@@
 \begin{enumerate}
-\item The challenger selects $\left\{(\textbf{sk}_i, \textbf{pk}_i)\right\}_{i=1}^{n(\lambda)} \leftarrow \texttt{KeyGen}(1^\lambda)$ and sends $\underline{\textbf{pk}} = \left\{\textbf{pk}_i\right\}_{i=1}^{n(\lambda)}$ to $\texttt{A}$.
+\item Challenge keys $\left\{(\textbf{sk}_i, \textbf{pk}_i)\right\}_{i=1}^{n(\lambda)} \leftarrow \texttt{KeyGen}(1^\lambda)$ are selected and the public keys $\underline{\textbf{pk}} = \left\{\textbf{pk}_i\right\}_{i=1}^{n(\lambda)}$ are sent to $\texttt{A}$.
 
@@
 
-\item $\texttt{A}$ outputs a message $m$, a ring of at most $n$ public keys $\underline{\textbf{pk}}^\prime$, and a signature-tag pair $(\sigma, \mathfrak{T})$.
-This output is a success if $\underline{\textbf{pk}}^\prime \subseteq \underline{\textbf{pk}}$ and $\mathfrak{T} \notin T_C$ and $\sigma$ has not been output by $\mathcal{SO}$ and $\texttt{Verify}(m, \underline{\textbf{pk}}^\prime, \sigma, \mathfrak{T}) = 1$.
+\item $\texttt{A}$ outputs a message $m$, a ring of at most $n$ public keys $\underline{\textbf{pk}}^\prime$, and a signature $\sigma$. This output is a success if
+\begin{enumerate}
+\item $\sigma$ is not output from any query made to $\mathcal{SO}$; and
+\item the key image $\mathfrak{T}$ does not correspond to a corrupted ring member; and
+\item $\texttt{Verify}(m, \underline{\textbf{pk}}^\prime, \sigma) = 1$.
+\end{enumerate}
+\end{enumerate}
+\end{definition}
 
-\end{enumerate}
-\end{defn}
+A forgery challenger can play the forgery game of Definition \ref{def:unf} with $\texttt{A}$ in a black box, can simulate $\mathcal{SO}$ and $\mathcal{CO}$, and can check whether the purported forgeries by $\texttt{A}$ are successful; the challenger simply keeps a history of all oracle queries, and computes key images of corrupted keys to check.
 
-These success requirements ensure that (i) any ring member whose linkability tag is $\mathfrak{T}$ has not yet had its corresponding private key corrupted by $\mathcal{CO}$; and (ii) the signature itself has not been produced by the signing oracle.
-This allows the attacker to perhaps re-use a message $m$ and linkability tag $\mathfrak{T}$ from a previous oracle query.
-If the attacker can produce a new signature $\sigma^\prime$ on a message that has been signed before by the oracle then the new signature should still count as a forgery.
+This definition allows the attacker to attempt a successful forgery by re-using messages, rings, or indices from previous $\mathcal{SO}$ queries (but not by reusing queries \textit{per totum}).
+It also allows key images that are unrelated to the ring members and it allows key images  found in previous $\mathcal{SO}$ queries.
+Hence, proving the implementation of Definition \ref{def:clsag} unforgeable under this definition implies these attempts will fail.
+A forger gains no advantage by re-using messages (or rings or indices) that have already been used in $\mathcal{SO}$.
+The forger gains no advantage by including key images that are unrelated to the ring members, or by using the key images from $\mathcal{SO}$ queries.
 
-\subsection{The Forking Lemma} To prove that the existence of a forger implies that of a $k$-OMDL solver, we use the forking lemma.
-In the following, we presume the bit length $\eta$ is used to describe group elements in $\mathbb{G}$ and scalars in $\mathbb{Z}/p\mathbb{Z}$, i.e.\ $\eta = O(\left|p\right|)$.
+Moreover, consider some $(m, \underline{\textbf{pk}}^\prime, \sigma)$ output by an alleged forger $\texttt{A}$.
+If the scheme is unforgeable, one of the above conditions must fail.
+If the signature passes verification, one of the first two conditions must fail, so any valid signature must violate one of these first two conditions.
+If the first condition is violated, the forger is merely attempting to pass off an oracle signature or some previously computed signature as their own.
+If the second condition is violated, then $\mathfrak{T}$ corresponds to a corrupted ring member (in which case $\texttt{A}$ knows the key) or corresponds to none of the ring members.
+
+That is to say: if $\texttt{A}$ produces a valid signature, then either $\texttt{A}$ knows the key or the key image does not correspond to a ring member.
+
+Moreover, presume that $\texttt{A}$ produces a message $m$, a ring $\underline{\textbf{pk}}$, and a signature $\sigma$ that passes verification, and yet such that the key image $\mathfrak{T} \in \sigma$ does not correspond to any ring member.
+Under the random oracle model, $\texttt{A}$ cannot simultaneously satisfy the verification equations
+\begin{align*}
+c_{2} =& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid m \mid \mid s_1 G + c_1 W_1 \mid \mid s_1 H_1 + c_1 \mathfrak{W}) \\
+\vdots & \\
+c_{n} =& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid m \mid \mid s_{n-1} G + c_{n-1} W_{n-1} \mid \mid s_{n-1} H_{n-1} + c_{n-1} \mathfrak{W}) \\
+c_{1} =& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid m \mid \mid s_{n} G + c_{n} W_{n} \mid \mid s_{n} H_{n} + c_{n} \mathfrak{W}) 
+\end{align*}
+except with negligible probability, because the discrete logarithm of $\mathfrak{W}$ cannot be written as $x_i \mathcal{H}^p(X_i)$ for any $i$.
+We conclude that $\texttt{A}$ must have known the discrete logarithm of the signing key to produce this signature.
+
+\begin{remark}
+Note that if the corruption oracle merely acted by computing arbitrary discrete logarithms, then an adversary could do the following: take some target $\textbf{pk}$ from the challenge set, apply a permutation to the coordinates of $\textbf{pk}$, pass the permuted key through $\mathcal{CO}$, obtain the discrete logarithm of the first (signing) key of $\textbf{pk}$, compute the key image for this signing key, and lastly produce a signature using $\texttt{Sign}$.
+For example, to find the discrete logarithm of the linking key in $\textbf{pk} = (A, B)$, the adversary may query $\mathcal{CO}$ with $(B, A)$, bypassing our definition.
+
+Such a signature would pass validation and not be described as a forgery according to our definition.
+Our definition avoids this problem by requiring the corruption oracle only be queried with challenge keys.
+This has the added benefit that it is possible to simulate the corruption oracle for a the black box execution of $\texttt{A}$.
+\end{remark}
+
+\subsection{The Forking Lemma}
+To prove that the existence of a forger implies that of a $k$-OMDL solver, we use the forking lemma.
+In the following, we presume the bit length $\eta$ is used to describe group elements in $\mathbb{G}$ and scalars in $\mathbb{F}_p$, \textit{i.e.}\ $\eta = O(\left|p\right|)$.
 
@@
 Let $q, \eta \geq 1$.
-Let $\texttt{A}$ be any PPT algorithm which takes as input some $x_\texttt{A} = (x, \underline{h})$ where $\underline{h} = (h_1, \ldots, h_q)$ is a sequence of oracle query responses ($\eta$-bit strings) and returns as output $y_{\texttt{A}}$ either a distinguished failure symbol $\bot$ or a pair $(\textit{idx}, y)$ where $\text{idx} \in [q]^2$ and $y$ is some output.
-Let $\epsilon_{\texttt{A}}$ denote the probability that $\texttt{A}$ does not output $\bot_{\texttt{A}}$ (where this probability is taken over all random coins of $\texttt{A}$, the distribution of $x$, all choices $\underline{h}$).
+Let $\texttt{A}$ be any PPT algorithm which takes as input some $x_\texttt{A} = (x, \textbf{h})$ where $\textbf{h} = (h_1, \ldots, h_q)$ is a sequence of oracle query responses ($\eta$-bit strings) and returns as output $y_{\texttt{A}}$ either a distinguished failure symbol $\bot$ or a pair $(\textit{idx}, y)$ where $\text{idx} \in [q]^2$ and $y$ is some output.
+Let $\epsilon_{\texttt{A}}$ denote the probability that $\texttt{A}$ does not output $\bot_{\texttt{A}}$ (where this probability is taken over all random coins of $\texttt{A}$, the distribution of $x$, all choices $\textbf{h}$).
 Let $\mathcal{F} = \mathcal{F}^{\texttt{A}}$ be the forking algorithm for $\texttt{A}$ described below.
@@
 
-We refer the reader to \cite{bellare} for a proof of this lemma, which demonstrates that if executing some $\texttt{A}$ has non-negligible acceptance probability, then forking $\texttt{A}$ does as well.
+We describe the general forking algorithm below, and refer the reader to \cite{bellare} for a proof of this lemma, which demonstrates that if executing some $\texttt{A}$ has non-negligible acceptance probability, then forking $\texttt{A}$ does as well.
 Since all queries before the $(j^*)^{th}$ query are identical in both transcripts, the input of the $(j^*)^{th}$ query is also identical.
@@
 
-\subsubsection{Using a forger in the Forking Lemma}
+\subsubsection{Using a forger in the Forking Lemma}\label{subsubsec:using-forger}
 
-Note that a forger according to Definition \ref{def:unf} is not directly compatible with the forking lemma; the output is some $y = (m, \textbf{pk}, \sigma, \mathfrak{T})$ and no $\textit{idx}$ is included.
-However, without loss of generality, we can execute $\texttt{A}$ in a black box that extracts from the transcript of $\texttt{A}$ some $\textit{idx} = (j^*, i^*)$ in the following way.
+Note that a forger according to Definition \ref{def:unf} is not directly compatible with the forking lemma; the output is some $y = (m, \textbf{pk}, \sigma)$ and no $\textit{idx}$ is included.
+However, without loss of generality, we can execute $\texttt{A}$ in a black box that extracts from the transcript of $\texttt{A}$ some $\textit{idx} = (i^*, j^*)$ for $j^* = j(i^*)$ in the following way.
 
 For each query for any $c_{i+1}$ that appears in the successful forgery, there exists a corresponding index $j(i)$ that satisfies $c_{i+1} = h_{j(i)}$.
-The black box executing $\texttt{A}$ looks at the transcript and extracts the index pair $\textit{idx} = (i^*, j^*)$ that indicates where in the random oracle transcript we can find the very first oracle query made by $\texttt{A}$ to $\mathcal{H}^s$ for any challenge $c_{i^*+1}$ used in the successful forgery.
-If such a pair $(i^*, j^*)$ can be found, the algorithm wrapping $\texttt{A}$ can then output $(\textit{idx}, y)$ with only a negligible difference in advantage.
+The black box executing $\texttt{A}$ looks at the transcript and extracts the index pair $\textit{idx} = (i^*, j^*)$ that indicates where in the random oracle transcript we can find the very first oracle query made by $\texttt{A}$ to $\mathcal{H}^s$ for some challenge used in signature verification \[c_{i^*+1} = \mathcal{H}^s_0\left(\underline{\textbf{pk}} \mid \mid m \mid \mid L_{i^*} \mid \mid R_{i^*}\right)\] used in the successful forgery.
+Such a pair $(i^*, j^*)$ can be found by merely inspecting the transcript, so the algorithm wrapping $\texttt{A}$ can output $(\textit{idx}, y)$ without harming its advantage.
 
-Moreover, each $c_{i+1}$ used in the signature verification is computed by $\texttt{A}$ by querying $\mathcal{H}^s$  in the transcript of $\texttt{A}$ leading to a successful forgery.
-In particular, the challenge could not have been guessed without making the query (except with negligible success).
-Indeed, a probabilistic algorithm could flip coins to guess the hash output, but this is successful with negligible probability.
-Of course, although the index $i^*$ may not have been decided by $\texttt{A}$ when the query was made, but by the time the forgery is complete, the index $i^*$ has been assigned.
+Without loss of generality, we can assume that $\texttt{A}$ has been appropriately wrapped so is compatible with the forking lemma without impacting its advantage.
 
-Hence, without loss of generality, we can assume that $\texttt{A}$ has been appropriately wrapped so is compatible with the forking lemma without impacting its advantage.
-One algorithm $\mathcal{F}^\texttt{A}$ that works in Lemma \ref{lem:fork} works in the following way.
+Forking the forger at this query preserves the input to the query $(\underline{\textbf{pk}}, m, L_{i^*}, R_{i^*})$ but does not preserve the challenge $c_{i^*+1}$.
+Moreover, each $c_{i+1}$ used in the signature verification is computed by $\texttt{A}$ by querying $\mathcal{H}^s$  in the transcript of $\texttt{A}$ leading to a successful forgery; the outputs of these queries cannot be guessed except with negligible probability, and so the oracle must have actually been queried  (see, for example, \cite{liu}).
+Of course, although the index $i^*$ may not have been decided by $\texttt{A}$ when the query was made, but the index $i^*$ is assigned before the end of the transcript.
+
+That is to say, a forked forger presents two forgeries with the same ring, message, and $\textit{idx}$ except with negligible probability, with the pair of points $L_{i^*}, R_{i^*}$ common in both transcripts.
+
+A forking algorithm $\mathcal{F}^\texttt{A}$ satisfying Lemma \ref{lem:fork} works in the following way.
 
@@
 \item $\mathcal{F}$ takes as input some $x$ and $\mathcal{F}$ selects the random tape for $\texttt{A}$.
-\item $\mathcal{F}$ selects some $\underline{h} = (h_1, \ldots, h_q)$ at random by flipping coins, and $\mathcal{F}$ executes $y_\texttt{A} \leftarrow \texttt{A}(x,\underline{h})$.
+\item $\mathcal{F}$ selects some $\textbf{h} = (h_1, \ldots, h_q)$ at random by flipping coins, and $\mathcal{F}$ executes $y_\texttt{A} \leftarrow \texttt{A}(x,\textbf{h})$.
 \item If $y_{\texttt{A}} = \bot_{\texttt{A}}$, then $\mathcal{F}$ outputs $\bot_{\mathcal{F}}$ and terminates.
-Otherwise, $y_{\texttt{A}} = (\textit{idx}, y)$ for some $\textit{idx}=(i^*,j^*)$ and some output $y$ and $\mathcal{F}$ selects new oracle queries $h_{j^*}^\prime, h_{j^*+1}^\prime, \ldots, h_q^\prime$, and glues the hash challenges together $\underline{h}^\prime = (h_1, \ldots, h_{j^*-1}, h_{j^*}^\prime, h_{j^*+1}^\prime, \ldots, h_q^\prime)$.
+Otherwise, $y_{\texttt{A}} = (\textit{idx}, y)$ for some $\textit{idx}=(i^*,j^*)$ and some output $y$ and $\mathcal{F}$ selects new oracle queries $h_{j^*}^\prime, h_{j^*+1}^\prime, \ldots, h_q^\prime$, and glues the hash challenges together: $$\textbf{h}^\prime = (h_1, \ldots, h_{j^*-1}, h_{j^*}^\prime, h_{j^*+1}^\prime, \ldots, h_q^\prime)$$
 \item If $h_{j^*} = h_{j^{*}}^\prime$, then $\mathcal{F}$ outputs $\bot_{\mathcal{F}}$ and terminates.
-Otherwise, $h_{j^*} \neq h_{j^{*}}^\prime$ and $\mathcal{F}$ executes $y_\texttt{A}^\prime \leftarrow \texttt{A}(x,\underline{h}^\prime)$.
+Otherwise, $h_{j^*} \neq h_{j^{*}}^\prime$ and $\mathcal{F}$ executes $y_\texttt{A}^\prime \leftarrow \texttt{A}(x,\textbf{h}^\prime)$.
 \item If $y_{\texttt{A}}^\prime = \bot_{\texttt{A}}$, then $\mathcal{F}$ outputs $\bot_{\mathcal{F}}$ and terminates.
@@
 If $\textit{idx} \neq \textit{idx}^\prime$, $\mathcal{F}$ outputs $\bot_{\mathcal{F}}$ and terminates.
-Otherwise, $\mathcal{F}$ outputs $(\textit{idx}, y, \underline{h}, y^\prime, \underline{h}^\prime)$.
+Otherwise, $\mathcal{F}$ outputs the tuple $(\textit{idx}, y, \textbf{h}, y^\prime, \textbf{h}^\prime)$.
 \end{enumerate}
 
-We note that $\mathcal{F}^{\texttt{A}}$ executed in a black box can be fed the oracle queries $\underline{h}$ and $\underline{h}^\prime$ and so these can be assumed to be output as well without loss of generality or impacting acceptance probability.
-
-Of course, if $\texttt{A}$ runs in time at most $t$, $\mathcal{F}^{\texttt{A}}$ runs in time at most $2t+s$ where $s$ denotes the (negligible) time it takes $\mathcal{F}^{\texttt{A}}$ to select the random tape for $\texttt{A}$, select the oracle query sequences $\underline{h}$ and $\underline{h}^\prime$, and output the results.
-
-\subsection{The Oracles}
-
-Of course, any oracle queries made by $\texttt{A}$ must be handled by $\mathcal{F}^{\texttt{A}}$ somehow, and we have already described how $\mathcal{F}^{\texttt{A}}$ handles random oracle queries made by $\texttt{A}$: by flipping coins at random and keeping a hash table of the results to maintain consistency with future queries.
-The forger also has corruption oracle and signing oracle access.
-We assume that $\mathcal{F}^{\texttt{A}}$ is granted access to a corruption oracle (say, through the $k$-OMDL game challenger), so we only need to describe the signing oracle.
-
-The signing oracle access granted to $\texttt{A}$ is simulated by $\mathcal{F}^{\texttt{A}}$ through backpatching in the following way.
-$\mathcal{F}^{\texttt{A}}$ selects $c_{\ell+1}$ at random without knowing the corresponding query to $\mathcal{H}^s$.
-$\mathcal{F}^{\texttt{A}}$ uses the query results $\underline{h}$ to get each $c_{i+1}$ and stores the results in a hash table for consistency in later queries.
-$\mathcal{F}^{\texttt{A}}$ finally computes $c_\ell$, $\mathcal{F}^{\texttt{A}}$ and can compute the group points $L_\ell, R_\ell$ such that $c_{\ell+1} = \mathcal{H}^s(\underline{\textbf{pk}} \mid \mid m \mid \mid L_\ell \mid \mid R_\ell)$.
-$\mathcal{F}^{\texttt{A}}$ back-patches the hash table.
+We note that $\mathcal{F}^{\texttt{A}}$ executed in a black box can be fed the oracle queries $\textbf{h}$ and $\textbf{h}^\prime$ and so these can be assumed to be output as well without loss of generality or impacting acceptance probability.
+Of course, if $\texttt{A}$ runs in time at most $t$, $\mathcal{F}^{\texttt{A}}$ runs in time at most $2t+s$ where $s$ denotes the time it takes $\mathcal{F}^{\texttt{A}}$ to select the random tape for $\texttt{A}$, select the oracle query sequences $\textbf{h}$ and $\textbf{h}^\prime$, perform lookups in hash tables to maintain oracle query consistency, and outputting the results.
+These times are all negligible, so $\mathcal{F}^{\texttt{A}}$ runs in $O(2t)$ time.
 
 \subsection{Playing k-OMDL}
-
 We now construct a master algorithm $\texttt{M}$ that plays the $k$-OMDL game for $k=2d\cdot q_c + d-1$ that operates in the following way.
+Recall that $\texttt{M}$ is granted access to up to $k$ queries at a discrete logarithm oracle.
 \begin{enumerate}
@@
 
-\item $\texttt{M}$ sets $\textbf{pk}_i := (G_{d(i-1) + 1}, G_{d(i-1) + 2}, \ldots, G_{di})$ for $i=1, \ldots, \frac{k+1}{d}$ and uses $\left\{\textbf{pk}_i\right\}_{i=1}^{\frac{k+1}{d}}$ as input for $\mathcal{F}^{\texttt{A}}$, responding to queries made by $\mathcal{F}^{\texttt{A}}$ for a key $\textbf{pk}_i$ by querying $\mathcal{CO}$ directly with each coordinate and responding with the result.
+\item $\texttt{M}$ blocks $(G_1, \ldots, G_{k+1})$ into $d$-length blocks and reserve them for public keys using the following equations.
+\begin{align*}
+\textbf{pk}_1 =& (G_1, \ldots, G_d) \\
+\textbf{pk}_2 =& (G_{d+1}, \ldots, G_{2d}) \\
+\vdots & \\
+\textbf{pk}_{2q_c + 1} =& (G_{2q_c d+1}, \ldots, G_{k+1}) 
+\end{align*}  $\texttt{M}$ uses $\left\{\textbf{pk}_i\right\}_{i=1}^{2q_c + 1}$ as input for $\mathcal{F}^{\texttt{A}}$, responding to corruption oracle queries made by $\mathcal{F}^{\texttt{A}}$ for a key $\textbf{pk}_i$ by querying $\mathcal{CO}$ directly with each coordinate and responding with the result.
+Denote $X_i := G_{(i-1)d + 1}$ and $Z_{i,j} := G_{(i-1)d + 1 + j}$ for consistency with our earlier notation.
 
 \item If $\mathcal{F}^{\texttt{A}}$ outputs $\bot$, so does $\texttt{M}$ and $\texttt{M}$ terminates.
+Otherwise, $\mathcal{F}^{\texttt{A}}$ succeeds executing $\texttt{A}$ twice, each time taking no more than $q_c$ queries to corrupt $d$-dimensional keys, resulting in no more than $2\cdot d\cdot q_c$ queries to the discrete logarithm oracle $\mathcal{CO}$.
+$\mathcal{F}^{\texttt{A}}$ produces $(\textit{idx}, y, \textbf{h}, y^\prime, \textbf{h}^\prime)$ where $y = (m, \underline{\textbf{pk}}, \sigma)$ and $y^\prime = (m, \underline{\textbf{pk}}, \sigma^\prime)$ are forgeries using oracle queries $\textbf{h}$ and $\textbf{h}^\prime$, respectively, and $\textit{idx} = (i^*, j^*)$ as described  in Section \ref{subsubsec:using-forger}.
 
-\item Otherwise, $\mathcal{F}^{\texttt{A}}$ succeeds executing $\texttt{A}$ twice, each time taking no more than $q_c$ queries to corrupt $d$-dimensional keys, resulting in no more than $2\cdot d\cdot q_c$ queries to the discrete logarithm oracle $\mathcal{CO}$.
-$\mathcal{F}^{\texttt{A}}$ produces $(\textit{idx}, y_1, \underline{h}, y_2, \underline{h}^\prime)$ where $y_1 = (m_1, \textbf{pk}^{\prime}_1, \sigma_1, \mathfrak{T}_1)$ and $y_2 = (m_2, \textbf{pk}^{\prime}_2, \sigma_2, \mathfrak{T}_2)$ are forgeries using oracle queries $\underline{h}$ and $\underline{h}^\prime$, respectively, and $\textit{idx} = (i^*, j^*)$ as described previously.
-The messages and rings are identical in these forgeries because they must have been selected before the first challenge query, except with negligible probability.
-So $\texttt{M}$ can parse
+The messages and rings are identical in these forgeries because they must have been selected before the first challenge query, except with negligible probability. So $\texttt{M}$ can parse 
 \begin{align*}
-y_1 =& (m, \underline{\textbf{pk}}^\prime, \sigma_1, \mathfrak{T}_1) & \sigma_1 =& (c_1, s_1, \ldots, s_n, \left\{\mathfrak{D}_j\right\}_j) \\
-y_2 =& (m, \underline{\textbf{pk}}^\prime, \sigma_2, \mathfrak{T}_2) & \sigma_2 =& (c_1^\prime, s_1^\prime, \ldots, s_n^\prime, \left\{\mathfrak{D}_j^\prime\right\}_j)\end{align*}
+y =& (m, \underline{\textbf{pk}}, \sigma) & \sigma =& (c_1, s_1, \ldots, s_n, \mathfrak{T}, \left\{\mathfrak{D}_j\right\}_j) \\
+y^\prime =& (m, \underline{\textbf{pk}}, \sigma^\prime) & \sigma^\prime =& (c_1^\prime, s_1^\prime, \ldots, s_n^\prime, \mathfrak{T}^\prime, \left\{\mathfrak{D}_j^\prime\right\}_j)\end{align*} except with negligible probability (in which case $\texttt{M}$ outputs $\bot_{\texttt{M}}$ and terminates).
 
-\item In the transcript of $\mathcal{F}^{\texttt{A}}$, $\texttt{M}$ finds $c_{i^*+1} = h_{j^*}$ and in the second transcript $c_{i^*+1} = h^\prime_{j^*}$ for some $h_{j^*} \neq h^\prime_{j^*}$.
-In both transcripts, $c_{i^*+1}$ is the response to the query $\mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid L \mid \mid R)$ for the same group elements $L, R$.
-Moreover, since this is the query for $c_{i^*+1}$ in both transcripts, the  $\texttt{M}$ finds that $L = s_{i^*} G + c_{i^*} W$ where $W = \mu_X X_{i^*} + \sum_j \mu_j Z_{i^*, j}$ in the first transcript and that $L = s_{i^*}^\prime G + c_{i^*}^\prime W$ in the second transcript, where $L$ and $W$ are common to both transcripts.
+\item In the transcript of $\mathcal{F}^{\texttt{A}}$, $\texttt{M}$ can find $c_{i^*+1} = \textbf{h}_{j^*}$ and in the second transcript $c_{i^*+1} = \textbf{h}^\prime_{j^*}$ for some $\textbf{h}_{j^*} \neq \textbf{h}^\prime_{j^*}$, except with negligible probability (in which case $\texttt{M}$ outputs $\bot_{\texttt{M}}$ and terminates).
 
-\item If $\mu_X = 0$ then $\texttt{M}$ outputs $\bot$ and terminates.
+\item $\texttt{M}$ parses the random oracle transcript to find the query yielding the signature challenge  $c_{i^*+1} \leftarrow \mathcal{H}^s(\underline{\textbf{pk}} \mid \mid m \mid \mid L_{i^*} \mid \mid R_{i^*})$.
+Both transcripts match until this line, and the oracle responses stored in $c_{i^*+1}$ in these transcripts don't match (i.e.\ $\textbf{h}_{j^*} \neq \textbf{h}^\prime_{j^*}$ except with negligible probability).
+The algorithm  $\texttt{M}$ parses the first transcript to look for constants $s_{i^*}, c_{i^*}$ and the group point $W = \mu_X X_{i^*} + \sum_j \mu_j Z_{i^*, j}$ such that $L_{i^*} = s_{i^*} G + c_{i^*} W$.
+From the second transcript, and with the same $L_{i^*}$ and $W$, $\texttt{M}$ parses to find constants $s_{i^*}^\prime, c_{i^*}^\prime$ such that $L_{i^*} = s_{i^*}^\prime G + c_{i^*}^\prime W$.
 
-\item Otherwise, $\texttt{M}$ computes the discrete logarithm
-$w = \frac{s_{i^*}^\prime - s_{i^*}}{(c_{i^*} - c_{i^*}^\prime)}$ without querying $\mathcal{CO}$.
+\item If $\mu_X = 0$ then $\texttt{M}$ outputs $\bot$ and terminates. Otherwise, $\texttt{M}$ computes the discrete logarithm
+$$w = \frac{s_{i^*}^\prime - s_{i^*}}{c_{i^*} - c_{i^*}^\prime}$$ without querying $\mathcal{CO}$.
 
@@
 
-\item $\texttt{M}$ outputs the $2 \cdot d \cdot q_c$ queries made by $\mathcal{F}^{\texttt{A}}$ and outputs the vector $(x_{i^*}, z_{i^*, 1}, \ldots, z_{i^*, d-1})$.
-
+\item $\texttt{M}$ outputs the $2 \cdot d \cdot q_c$ corruptions queries and the $d$-vector $(x_{i^*}, z_{i^*, 1}, \ldots, z_{i^*, d-1})$, totaling $k+1$ discrete logarithms.
 \end{enumerate}
 
-Note that if $\texttt{M}$ does not terminate and output $\bot$, then $\texttt{M}$ makes up to $2\cdot d \cdot q_c$ queries to $\mathcal{CO}$ for $\mathcal{F}^{\texttt{A}}$ and makes an an additional $d-1$ queries to $\mathcal{CO}$, and yet produces as output $d \cdot (q_c + 1) > d \cdot q_c + d-1$ discrete logarithms, i.e.\ $\texttt{M}$ successfully plays the $k$-OMDL game for $k = 2\cdot d\cdot q_c + d-1$.
+Note that if $\texttt{M}$ does not terminate and output $\bot$, then $\texttt{M}$ makes up to $2\cdot d \cdot q_c$ queries to $\mathcal{CO}$ for $\mathcal{F}^{\texttt{A}}$ and makes an an additional $d-1$ queries to $\mathcal{CO}$, and yet produces as output $d \cdot (q_c + 1) > d \cdot q_c + d-1$ discrete logarithms, \textit{i.e.}\ $\texttt{M}$ successfully plays the $k$-OMDL game for $k = 2\cdot d\cdot q_c + d-1$.
 Furthermore,  if $\texttt{M}$ already corrupted these discrete logarithms, even fewer queries could be made, tightening $k$ and making $\texttt{M}$ a more powerful solver.
@@
 
-We previously noted that if $\texttt{A}$ runs in time $O(t)$, $\mathcal{F}^{\texttt{A}}$ runs in time $O(2t)$.
-$\texttt{M}$ takes an additional  time $s$ due to: simulating oracle queries with coin flips and hash table modifications throughout the execution, constructing keys in step $2$,  making termination checks in steps $3$, $6$, parsing the transcripts in step $4$, retrieving $L$ and $W$ from the transcript in step $5$, computing the discrete logarithm $w$ in step $7$, computing the $d$-linear system of equations in step $9$.
+Recall that $\mathcal{F}^{\texttt{A}}$ takes time $O(2t)$ to execute.
+$\texttt{M}$ executes $\texttt{F}^{\texttt{A}}$ and then performs parsing of transcripts and some additional computations, so $\texttt{M}$ takes time $O(2t+s^\prime)$ for some $s^\prime$ due to parsing and processing transcript data.
 
-\subsection{Security proof}
+The additional time $s^\prime$ is due to: 
+\begin{itemize}
+\item Lookup time in a hash table for each $\mathcal{CO}$ query, each random oracle query, and each extraction of a value from the random tapes $\textbf{h}$, $\textbf{h}^\prime$ by $\mathcal{F}^{\texttt{A}}$ throughout the transcript.
+\item Parsing and constructing keys in step $2$.
+\item Parsing purported forgeries in step $3$.
+\item Parsing transcripts and computing multi-exponentiations to verify equations in step $5$.
+\item Computing the discrete logarithm $w$ using field arithmetic in Step $6$.
+\item Computing the discrete logarithm of the challenge key using field arithmetic in step $8$.
+\item Outputting the results.
+\end{itemize}
+All of these are negligible, so $\texttt{M}$ also takes time $O(2t)$.
 
+\subsection{Proof}
 All that remains to prove the unforgeability of the $d$-CLSAG scheme from Section \ref{sec:implem} is to show that $\texttt{M}$ as described has a non-negligible acceptance probability.
@@
 $\texttt{M}$ terminates and outputs $\bot$ in steps $3$ and $6$ only; otherwise, $\texttt{M}$ succeeds at the $k$-OMDL game.
-Hence, if $E_3$ is the event that $\texttt{M}$ outputs $\bot$ in step $3$ and $E_6$ is the event that $\texttt{M}$ outptus $\bot$ in step $6$, then $E_3, E_6$ are disjoint and the acceptance probability for $\texttt{M}$ is $1 - \mathbb{P}(E_3 \cup E_6) =  1 - \mathbb{P}(E_3) - \mathbb{P}(E_6)$.
+Hence, if $E_3$ is the event that $\texttt{M}$ outputs $\bot$ in step $3$ and $E_6$ is the event that $\texttt{M}$ outputs $\bot$ in step $6$, then $E_3, E_6$ are disjoint and the acceptance probability for $\texttt{M}$ is $1 - \mathbb{P}(E_3 \cup E_6) =  1 - \mathbb{P}(E_3) - \mathbb{P}(E_6)$.
 The probability that $\texttt{M}$ outputs $\bot$ in step $6$ is the probability that the hashed coefficient $\mu_X = 0$, which occurs with probability $p^{-1}$.
@@
 
-\section{Security: Signer ambiguity}
+Note that, as a corollary, we can conclude that if a signature passes verification, then the key image corresponds to one of the ring members except with negligible probability.
+Indeed, these signatures soundly prove knowledge of the discrete logarithm of the signing key as well as equality of the discrete logarithm with the signing key and the key image, so constructing a signature that convinces the verifier of one but not the other succeeds with at most negligible probability.
 
-\subsection{Hardness}
+\section{Security: Definitions other than unforgeability}\label{app:link-and-sa}
+\subsection{Linkability}
+Correctness in linkability for the implementation of Definition \ref{def:clsag} is easily verified.
+We consider soundness in linkability.
+Soundness relies upon the collision resistance of the map from a secret key to the key image $\mathfrak{T}$ and unforgeability (which, in turn, relies on the $k$-OMDL hardness assumption).
+\begin{description}
+\item[Soundly linkable:]  We say Definition \ref{def:clsag} is \textit{soundly linkable} or \textit{non-slanderable} if it is infeasible for an algorithm to produce messages $m$, $m^\prime$, signatures $\sigma, \sigma^\prime$, rings $\underline{\textbf{pk}}$, $\underline{\textbf{pk}}^\prime$, and indices $\ell, \ell^\prime$ such that  the key image $\mathfrak{T} \in \sigma$ corresponds to the $\ell^{th}$ member of $\underline{\textbf{pk}}$, the key image $\mathfrak{T}^\prime \in \sigma^\prime$ corresponds to the $(\ell^\prime)^{th}$ member of $\underline{\textbf{pk}}^\prime$, the linking coordinate of $\textbf{pk}_\ell$ does not equal the linking coordinate of $\textbf{pk}^\prime_{\ell^\prime}$,  and $\texttt{Link}((m, \underline{\textbf{pk}}, \sigma), (m^\prime, \underline{\textbf{pk}}^\prime, \sigma^\prime))=1$.
+\end{description}
+
+Assume an algorithm attempts to slander and generates a pair of tuples $(m, \underline{\textbf{pk}}, \sigma)$ and  $(m^\prime, \underline{\textbf{pk}}^\prime, \sigma^\prime)$ such that $\texttt{Link}((m, \underline{\textbf{pk}}, \sigma), (m^\prime, \underline{\textbf{pk}}^\prime, \sigma^\prime)) = 1$.
+Since $\texttt{Link}$ outputs $1$, both signatures pass verification and the key image $\mathfrak{T}$ is the same in both signatures, $\mathfrak{T} = \mathfrak{T}^\prime$.
+Since both signatures pass verification and Definition \ref{def:clsag} is unforgeable, the slanderer has, except with negligible probability, computed the signatures $\texttt{Sign}$, \textit{i.e.}\ $\sigma \leftarrow \texttt{Sign}(m, \underline{\textbf{pk}}, \textbf{sk})$ and $\sigma^\prime \leftarrow \texttt{Sign}(m^\prime, \underline{\textbf{pk}}^\prime, \textbf{sk}^\prime)$.
+
+Since the map from $\textbf{sk}$ to the key image $\mathfrak{T}$ is collision-resistant, this implies that the linking coordinates are equal, $\textbf{sk}_0 = \textbf{sk}^\prime_0$, except with negligible probability, so no one is slandered.
+
+\subsection{Signer ambiguity}
+\subsubsection{Hardness}
 
@@
 
-\begin{defn}[Decisional Diffie-Hellman]\label{ddhgame} Let $\texttt{A}$ be any computationally unbounded PPT algorithm, $(p, \mathbb{G}, G)$ and let $n \in \mathbb{N}$.
+\begin{definition}[Decisional Diffie-Hellman]\label{ddhgame} Let $\texttt{A}$ be any PPT algorithm, $(p, \mathbb{G}, G)$ and let $n \in \mathbb{N}$.
 \begin{enumerate}
-\item The challenger selects $(r_{i,1}, r_{i,2}, r_{i,3}) \left(\mathbb{Z}/p\mathbb{Z}\right)^3$ uniformly and independently for $i=1, \ldots, n$.
+\item The challenger selects $(r_{i,1}, r_{i,2}, r_{i,3}) \in \left(\mathbb{F}_p\right)^3$ uniformly and independently for $i=1, \ldots, n$.
 The challenger computes the public keys $R_{i,1} = r_{i,1} G$, $R_{i,2} = r_{i,2}G$, $R_{i,3}^{(0)} = r_{i,1} r_{i,2} G$, $R_{i,3}^{(1)} = r_{i,3} G$.
@@
 If $\texttt{A}$ can solve this with an advantage at least $\epsilon$ in time at most $t$, we say $\texttt{A}$ is a $(t,\epsilon)$-solver of the DDH problem in $\mathbb{G}$.
+\end{definition}
 
-\end{defn}
+We note that due to the random self-reducibility of the DDH game, in the sense that solving one instance of the problem has complexity no worse than solving a sequence of random instances of the problem, the classic DDH game is no harder than Definition \ref{ddhgame}.
 
-We note that due to the random self-reducibility of the DDH game, the classic DDH game is no harder than Definition \ref{ddhgame}
-\subsection{Defining signer ambiguity}
-
-\begin{defn}\label{sigambgame} We say $\texttt{A}$ is a $(t,\epsilon,n_1,n_2)$-solver of the signer ambiguity game if it can succeed with non-negligible advantage at the following game.
+\begin{definition}[Signer Ambiguity]\label{sigambgame} We say $\texttt{A}$ is a $(t,\epsilon,n_1,n_2)$-solver of the signer ambiguity game if it can succeed with non-negligible advantage at the following game.
 \begin{enumerate}
-\item The challenger selects $n_1$ secret keys $\left\{\textbf{sk}_i\right\} \subseteq (\mathbb{Z}/p\mathbb{Z})^d$, computes the corresponding public keys $\textbf{pk}_i = \textbf{sk}_i \circ \textbf{G}$, and sends $\left\{\textbf{pk}_i\right\}$ to $\texttt{A}$.
+\item The challenger selects $n_1$ secret keys $\left\{\textbf{sk}_i\right\} \subseteq (\mathbb{F}_p^*)^d$, computes the corresponding public keys $\textbf{pk}_i = \textbf{sk}_i \circ \textbf{G}$, and sends $\left\{\textbf{pk}_i\right\}$ to $\texttt{A}$.
 
@@
 
-\item The challenger selects a ring index $1 \leq \ell \leq n_2$ uniformly at random, retrieves the private key $\textbf{sk}$, and sends a valid signature-tag pair $(\sigma, \mathfrak{T}) \leftarrow \texttt{Sign}(m, \underline{\textbf{pk}}^\prime, \textbf{sk})$ to $\texttt{A}$.
+\item The challenger selects a ring index $1 \leq \ell \leq n_2$ uniformly at random, retrieves the private key $\textbf{sk}$, and sends a valid signature $\sigma \leftarrow \texttt{Sign}(m, \underline{\textbf{pk}}^\prime, \textbf{sk})$ to $\texttt{A}$.
 \item $\texttt{A}$ outputs an index $\ell^\prime$, succeeding if $\ell = \ell^\prime$. 
@@
 We define the advantage of $\texttt{A}$ as the difference in acceptance probability and $1/n_2$.
-\end{defn}
+\end{definition}
 
@@
 
-\subsection{Security proof}
+\subsubsection{Proof of Signer Ambiguity}
+If $\mathbb{G}$ satisfies the DDH hardness assumption, then the distribution of the triple $(r_1G, r_2G, r_3G)$ is computationally indistinguishable from the triple $(r_1G, r_2G, r_1r_2G)$,  where the $r_i$ are independently uniform on $\mathbb{F}_p$.
+If $\mathcal{H}^p: \left\{0,1\right\}^* \to \mathbb{G}$ is modeled as a random oracle with output that is independent of its input, the distribution of a tuple $(r_1G, r_2G, r_3G)$ is identical to the distribution of $(r_1G, \mathcal{H}^p(r_1G), r_3G)$ where $r_1, r_3$ are independently uniform on $\mathbb{F}_p$.
+Hence, under the random oracle model and assuming $\mathbb{G}$ is DDH-hard, the distribution of triples $(r_1G, \mathcal{H}^p(r_1G), r_1\mathcal{H}^p(r_1G))$ where $r_1$ is uniformly random from $\mathbb{F}_p$ is computationally indistinguishable from the distribution of triples $(r_1G, \mathcal{H}^p(r_1G), r_3G)$ where $r_1, r_3$ are uniformly random from $\mathbb{F}_p$.
 
-If $\mathbb{G}$ satisfies the DDH hardness assumption, then the distribution of the triple $(r_1G, r_2G, r_3G)$ is computationally indistinguishable from the triple $(r_1G, r_2G, r_1r_2G)$,  where the $r_i$ are independently uniform on $\mathbb{Z}/p\mathbb{Z}$.
-If $\mathcal{H}^p: \left\{0,1\right\}^* \to \mathbb{G}$ is modeled as a random oracle with output that is independent of its input, the distribution of a tuple $(r_1G, r_2G, r_3G)$ is identical to the distribution of $(r_1G, \mathcal{H}^p(r_1G), r_3G)$ where $r_1, r_3$ are independently uniform on $\mathbb{Z}/p\mathbb{Z}$.
-Hence, under the random oracle model and assuming $\mathbb{G}$ is DDH-hard, the distribution of triples $(r_1G, \mathcal{H}^p(r_1G), r_1\mathcal{H}^p(r_1G))$ where $r_1$ is uniformly random from $\mathbb{Z}/p\mathbb{Z}$ is computationally indistinguishable from the distribution of triples $(r_1G, \mathcal{H}^p(r_1G), r_3G)$ where $r_1, r_3$ are uniformly random from $\mathbb{Z}/p\mathbb{Z}$.
-
-Now note that a solver of the signer ambiguity game is given $X_i$ and $\mathcal{H}^p(X_i)$ for each ring member and the linkability tag $\mathfrak{T} = x_\ell \mathcal{H}^p(X_\ell)$.
+Now note that a solver of the signer ambiguity game is given $X_i$ and $\mathcal{H}^p(X_i)$ for each ring member and the key image $\mathfrak{T} = x_\ell \mathcal{H}^p(X_\ell)$.
 The solver with a non-negligible advantage at guessing $\ell$ has a non-negligible advantage in distinguishing whether a given triple $(X_i, \mathcal{H}^p(X_i), \mathfrak{T})$ satisfies $\mathfrak{T} = x_i \mathcal{H}^p(X_i)$ or not.
@@
 \begin{enumerate}[(a)]
-\item $\texttt{M}$ selects a random index $1 \leq \ell \leq n_2$, selects a random scalar $c_{\ell+1} \in \mathbb{Z}/p\mathbb{Z}$, and selects random scalars $s_1, s_2, \ldots, s_n \in \mathbb{Z}/p\mathbb{Z}$.
+\item $\texttt{M}$ selects a random index $1 \leq \ell \leq n_2$, selects a random scalar $c_{\ell+1} \in \mathbb{F}_p$, and selects random scalars $s_1, s_2, \ldots, s_n \in \mathbb{F}_p$.
 
@@
 
-\item $\texttt{M}$ sends to $\texttt{A}$ the signature-tag pair $\left(\sigma, \mathfrak{T}_{i(\ell)}\right)$ where $\sigma = (c_1, s_1, \ldots, s_n, \left\{\mathfrak{D}_j\right\}_j)$.
-
+\item $\texttt{M}$ sends to $\texttt{A}$ the signature $\left(\sigma, \mathfrak{T}_{i(\ell)}\right)$ where the signature $\sigma = (c_1, s_1, \ldots, s_n, \left\{\mathfrak{D}_j\right\}_j)$.
 \end{enumerate}

### 2019-09-27 rct3/common.py
Incomplete work on updated spend proof

@@ -4,18 +4,12 @@ from dumb25519 import *
 
 # Protocol constants
 BITS = 4 # range bit length
-RING = 4 # anonymity set size
 
 # Fixed generators
-H = hash_to_point('H')
 Gc = hash_to_point('Gc') # commitment generator
 Hc = hash_to_point('Hc') # commitment generator
 U = hash_to_point('U')
-G0 = hash_to_point('G0')
 G_ip = hash_to_point('G_ip')
-Hi = []
-for i in range(RING):
-    Hi.append(hash_to_point('Hi',i))
 
 # Pedersen commitment
 # INPUT

### 2019-09-27 rct3/spend.py

@@ -1,12 +1,14 @@
 from dumb25519 import *
 from common import *
+from random import sample
 import transcript
 
 # Spend proof
 class SpendProof:
     def __init__(self):
+        self.B1 = None
+        self.B2 = None
         self.A = None
-        self.B = None
         self.S1 = None
         self.S2 = None
         self.S3 = None
@@ -14,15 +16,16 @@ class SpendProof:
         self.T2 = None
         self.tau_x = None
         self.mu = None
-        self.z_a = None
-        self.z_sk = None
+        self.z_a1 = None
+        self.z_a2 = None
+        self.z_sk = None # list
         self.z_d = None
-        self.L = None
-        self.R = None
+        self.L = None # list
+        self.R = None # list
         self.a = None
         self.b = None
         self.t = None
-        self.U1 = None
+        self.U = None # list (key images)
         self.P = None
 
 # Data for a round of the inner product argument
@@ -73,101 +76,134 @@ def inner_product(data):
     data.a = data.a[:n]*x + data.a[n:]*x.invert()
     data.b = data.b[:n]*x.invert() + data.b[n:]*x
 
-# Generate a spend proof
+# Generate a spend proof for multiple inputs
 #
 # INPUTS
-#   pk: list of public keys (Points)
-#   C_in: list of corresponding input commitments (Points)
-#   k: signing index (int)
-#   a: input amount (Scalar)
-#   kappa: input mask (Scalar)
-#   delta: input offset (Scalar)
-#   sk: secret key (Scalar)
+#   pk: list of public keys (Point list)
+#   C_in: list of input commitments (Point list)
+#   k: signing indices (int list)
+#   a: input amounts (Scalar list)
+#   kappa: input masks (Scalar list)
+#   sk: secret keys (Scalar list)
+#   delta: difference of input and output masks (Scalar)
 # OUTPUTS
 #   proof: spend proof
-def prove(pk,C_in,k,a,kappa,delta,sk):
+def prove(pk,C_in,k,a,kappa,sk,delta):
+    M = len(k) # number of spends
+
     # Sanity checks
[…]

### 2019-09-27 rct3/common.py
Updated transaction flow

@@ -4,6 +4,7 @@ from dumb25519 import *
 
 # Protocol constants
 BITS = 4 # range bit length
+RING = 4 # anonymity set size
 
 # Fixed generators
 Gc = hash_to_point('Gc') # commitment generator
@@ -13,10 +14,10 @@ G_ip = hash_to_point('G_ip')
 
 # Pedersen commitment
 # INPUT
-#   v: value
-#   a: mask
-def com(v,a):
-    return v*Hc + a*Gc
+#   a: amount
+#   m: mask
+def com(a,m):
+    return a*Hc + m*Gc
 
 # Determine if a value is a power of 2
 #

### 2019-09-27 rct3/spend.py

@@ -464,45 +464,3 @@ def verify(proof,pk,C_in,C_out):
 
     if not multiexp(check) == Z:
         raise ArithmeticError('Failed verification!')
-
-# NOTE: debug only
-M = 2
-RING = 8 # overrides common.py
-k = sample(range(RING),M) # spend indices
-N = 3 # number of outputs
-
-# Output keys
-P = [random_point() for _ in range(RING)]
-p = [random_scalar() for _ in range(M)]
-
-# Commitment keys
-C_in = [random_point() for _ in range(RING)]
-v_in = [random_scalar() for _ in range(M)]
-m_in = [random_scalar() for _ in range(M)]
-
-# Construct public keys from private keys
-for i in range(M):
-    P[k[i]] = p[i]*G
-    C_in[k[i]] = com(v_in[i],m_in[i])
-
-# Output commitments
-C_out = []
-v_out = [random_scalar() for _ in range(N)]
-m_out = [random_scalar() for _ in range(N)]
-v_out[-1] = Scalar(0)
-delta = Scalar(0)
-for i in range(M):
-    v_out[-1] += v_in[i]
-    delta += m_in[i]
-for i in range(N-1):
-    v_out[-1] -= v_out[i]
-    delta -= m_out[i]
-    C_out.append(com(v_out[i],m_out[i]))
-delta -= m_out[-1]
-C_out.append(com(v_out[-1],m_out[-1]))
-
-print 'Proving...'
-proof = prove(P,C_in,k,v_in,m_in,p,delta)
-print 'Verifying...'
-verify(proof,P,C_in,C_out)
-print 'Passed!'

### 2019-09-27 rct3/test.py

@@ -119,7 +119,7 @@ class MintTransaction:
 
 # The result of a spend transaction
 class SpendTransaction:
-    # Spend a coin
+    # Spend coins
     #
     # INPUTS
     #   coins: list of coins (spends and decoys)
@@ -130,11 +130,8 @@ class SpendTransaction:
     # DATA
     #   coins_in: input coins
     #   coins_out: output coins
-    #   C1: commitment offsets
     #   range_proof: aggregate range proof
-    #   spend_proofs: spend proofs
-    #   bal_c: balance proof c
-    #   bal_z: balance proof z
+    #   spend_proof: aggregate spend proof
     #   f: fee
     def __init__(self,coins_in,l,dest,v,f):
         # Sanity checks
@@ -158,52 +155,26 @@ class SpendTransaction:
         # Generate range proof
         range_proof = pybullet.prove([[v[i],coins_out[i].mask] for i in range(len(dest))],BITS)
 
-        # Offset input coins
-        delta = []
-        C1 = []
-        for i in range(len(l)):
-            delta.append(random_scalar())
-            C1.append(coins_in[l[i]].C - delta[i]*Gc)
-
-        # Generate balance proof
+        # Generate balance proof secret, accounting for fee
         d = Scalar(0)
+        for i in range(len(l)):
+            d += coins_in[l[i]].mask
         for i in range(len(coins_out)):
-            d += coins_out[i].mask
-        for i in range(len(l)):
-            d -= (coins_in[l[i]].mask - delta[i])
-        r1 = random_scalar()
-        bal_c = hash_to_scalar(r1*Gc,coins_out,coins_in,f)
-        bal_z = r1 + d*bal_c
+            d -= coins_out[i].mask
 
-        # Generate spend proofs
-        spend_proofs = []
-        for i in range(len(l)):
-            spend_proofs.append(spend.prove([coin.P for coin in coins_in],[coin.C for coin in coins_in],l[i],coins_in[l[i]].v,coins_in[l[i]].mask,delta[i],coins_in[l[i]].p))
+        # Generate spend proof
+        spend_proof = spend.prove([coin.P for coin in coins_in],[coin.C for coin in coins_in],l,[coins_in[l[i]].v for i in range(len(l))],[coins_in[l[i]].mask for i in range(len(l))],[coins_in[l[i]].p for i in range(len(l))],d)
 
         self.coins_in = coins_in
         self.coins_out = coins_out
-        self.C1 = C1
[…]

### 2019-10-18 triptych/test.py
Better test structure

@@ -1,0 +1,56 @@
+import triptych
+import unittest
+import dumb25519
+from dumb25519 import random_scalar, random_point, Scalar
+import random
+
+G = dumb25519.G
+H = dumb25519.hash_to_point('H')
+
+# Given a list of linking tags, determine if there are any duplicates
+# NOTE: this scales poorly
+#
+# INPUT
+#   tags: list of linking tags (Point list)
+# OUTPUT
+#   boolean: True if a duplicate exists, False otherwise
+def double_spend(tags):
+    return len(tags) != len(set(tags))
+
+
+class TestValidProofs(unittest.TestCase):
+    def test_valid_prove_verify(self):
+        print ''
+
+        for m in [1,2]: # ring size 2,4
+            for spends in range(1,min(3,2**m)+1):
+                for outs in [1,2,3]:
+                    print 'Test parameters (m spends outs):',m,spends,outs
+                    l = random.sample(range(2**m),spends) # spend indices
+                    r = [random_scalar() for _ in range(spends)] # signing keys
+                    s = [random_scalar() for _ in range(spends)] # input commitment blinders
+                    a = [random_scalar() for _ in range(spends)] # input commitment amounts
+                    t = [random_scalar() for _ in range(outs)] # output commitment blinders
+                    b = [random_scalar() for _ in range(outs)] # output commitment amounts
+
+                    # Balance amounts
+                    b[0] = Scalar(0)
+                    for i in range(len(a)):
+                        b[0] += a[i]
+                    for i in range(1,len(b)):
+                        b[0] -= b[i]
+
+                    # Set keys and commitments
+                    M = [random_point() for _ in range(2**m)] # possible signing keys
+                    P = [random_point() for _ in range(2**m)] # corresponding commitments
+                    Q = []
+                    for i in range(outs): # output commitments
+                        Q.append(t[i]*G + b[i]*H)
+                    for i in range(spends): # spend commitments
+                        M[l[i]] = r[i]*G
+                        P[l[i]] = s[i]*G + a[i]*H
+
+                    # Run test
+                    self.assertTrue(triptych.verify(M,P,Q,triptych.prove(M,P,Q,l,r,s,t,a,b,m),m))
+
+unittest.TextTestRunner(verbosity=2,failfast=True).run(unittest.TestLoader().loadTestsFromTestCase(TestValidProofs))

### 2019-10-18 triptych/triptych.py

@@ -329,44 +329,3 @@ def verify(M,P,Q,proof,m):
         raise ArithmeticError('Failed balance check!')
 
     return True
-
-
-#
-# Basic test
-#
-
-# Parameters
-m = 3 # ring size is 2**m
-spends = 2 # number of spent inputs
-outs = 2 # number of generated outputs
-
-# Set up the test
-l = random.sample(range(2**m),spends) # spend indices
-r = [random_scalar() for _ in range(spends)] # signing keys
-s = [random_scalar() for _ in range(spends)] # input commitment blinders
-a = [random_scalar() for _ in range(spends)] # input commitment amounts
-t = [random_scalar() for _ in range(outs)] # output commitment blinders
-b = [random_scalar() for _ in range(outs)] # output commitment amounts
-
-# Ensure output amounts balance input amounts
-b[0] = Scalar(0)
-for i in range(len(a)):
-    b[0] += a[i]
-for i in range(1,len(b)):
-    b[0] -= b[i]
-
-# Set all keys and commitments
-M = [random_point() for _ in range(2**m)] # possible signing keys
-P = [random_point() for _ in range(2**m)] # corresponding commitments
-Q = []
-for i in range(outs): # output commitments
-    Q.append(t[i]*G + b[i]*H)
-for i in range(spends): # spend commitments
-    M[l[i]] = r[i]*G
-    P[l[i]] = s[i]*G + a[i]*H
-
-# Run test
-print 'Proving...'
-proof = prove(M,P,Q,l,r,s,t,a,b,m)
-print 'Verifying...'
-verify(M,P,Q,proof,m)

### 2019-10-21 paper/main.tex
Paper with algorithms and correctness proof

\documentclass[draft]{article}
\usepackage[top=1.0in,bottom=1.0in,left=0.5in,right=0.5in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

\title{Triptych}
\author{Sarang Noether and Arthur Blue}
\date{\today}

\newcommand{\G}{\mathbb{G}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\hs}{\mathsf{H}}
\newcommand{\hp}{\mathcal{H}}
\newcommand{\com}{\operatorname{Com}}

\newcommand{\sumi}{\sum_{i=0}^{n-1}}
\newcommand{\sumj}{\sum_{j=0}^{m-1}}
\newcommand{\sumk}{\sum_{k=0}^{N-1}}
\newcommand{\sumu}{\sum_{u=0}^{w-1}}

\begin{document}

\maketitle

\textbf{NOTE:} This document is a work in progress and is \textit{extremely} incomplete.

\section{Introduction}
This document describes the Triptych transaction protocol\footnote{\url{https://github.com/SarangNoether/skunkworks/tree/triptych}}. Triptych uses a modification to a one-of-many commitment to zero proving construction by Bootle \textit{et al.} \cite{bootle} that itself is a generalization of earlier work by Groth and Kohlweiss \cite{groth}. It extends these approaches in two ways. First, we show how to generalize the proof to show knowledge of the openings of multiple commitments in a single list; this necessitates the addition of linking tags to ensure uniqueness of the opened commitments. Second, we show how to leverage the same proof to show general openings of commitments not necessarily to zero via a summation protocol. The use of these components in a single proof is much more efficient than an equivalent construction using multiple proofs.

Taken together, these generalizations permit a useful application as a transaction protocol. If output public keys are considered as commitments to zero with Pedersen blinders set to the corresponding private keys, and each such public key comes equipped with a separate commitment to the output's amount, we can use a single Triptych proof to permit the spending of multiple outputs while detecting double-spending attempts and showing transaction balance without leaking amount or signer information.

Triptych proofs are logarithmic in size with the number of possible signers, are efficient to verify using a single multiscalar multiplication operation, and can use delayed batch verification of arbitrary proofs for further efficiency gains.

\subsection{Warning}
There is currently no security model established for Triptych, and no proofs of security (except for correctness). This document currently serves only to describe the construction and its algorithms. It should not be considered secure or safe for use without extensive additional formalization and analysis. This is very early research that is still under active development.

\section{Algorithms}
Let $\G$ be a cyclic group in which the discrete logarithm problem is hard, and let $\F$ be its scalar field. Let $\hs$ be a cryptographic hash function mapping arbitrary input to $\F$. Let $\hp$ be a cryptographic hash function mapping arbitrary input to $\G$. Assume that any point of the form $G_i$ or $H_i$ (possibly with multiple indices) is a generator of $\G$ whose discrete logarithm relationship with all other such points is unknown; in the case of elliptic curve groups, using an indexed $\hp$ operation is appropriate for these generators. Let $G, H$ be distinguished generators used for Pedersen commitments.

Assume that previously-generated transaction outputs are constructed as Pedersen commitments to zero, such that an output is of the form $M \equiv rG$. We do not consider here the method by which output keys are generated, but assume this is offloaded to another protocol. Each output comes equipped with an amount commitment $P \equiv sG + aH$, where $a$ is the amount and $s$ a blinding factor.

A user of the protocol wishes to spend $w$ distinct outputs $\{M_u\}_{u=0}^{w-1}$ for which it knows the corresponding private keys, and generate $T$ new outputs such that the amounts balance between input and output commitments. Further, it wishes to demonstrate to other users of the protocol that none of the $w$ outputs has been previously spent in another transaction.

To obscure the set $\{M_i\}$ being spent in the transaction, the user includes a number of other outputs in the list, for which it does not necessarily know the private keys. Note this is a non-interactive process that does not require the participation of the owners of the other outputs.

Suppose the user has such a list of $N$ outputs, randomly shuffled such that for $0 \leq u < w$, the quantity $0 \leq l^{(u)} < N$ represents the index of an output to be spent. Note that the mapping $u \mapsto l^{(u)}$ is one-to-one. We assume that $N = n^m$ for some $n,m$. In practice this is not a practical concern, since it is always possible to include additional outputs to the set. The user generates $T$ new outputs whose associated amount commitments are $\{Q_j\}_{j=0}^{T-1}$, and such that the input and output amounts balance between spent input commitments and newly-generated output commitments.

\subsection{Notation}
For a three-dimensional tensor $f \equiv (f_{i,j,k}) \subset \F^3$ and blinding factor $r \in \F$, define the Pedersen tensor commitment $$\com(f,r) \equiv rH + \sum_{i,j,k} f_{i,j,k} G_{i,j,k}$$ using fixed independent generators as described above. Operations on tensors are assumed to be performed componentwise. The ordering of elements of $f$ is assumed to be known and canonical.

For integers or scalars $i,j$, the Kronecker delta function $\delta(i,j)$ evaluates to $1$ if $i=j$ and $0$ otherwise, where the output is taken to be in the appropriate set.

We sometimes use index subscript notation of the form $i_j$ to indicate the $j$ digit of $i$, where such a decomposition of $i$ is taken base $n$ with padded length $m$. That is, for $n=2$, this indexes a binary decomposition. This notation will be specified explicitly where confusion may occur.

\subsection{Prover}
The prover algorithm accepts the following:
\begin{itemize}
\item a set of outputs $\{M_k\}_{k=0}^{N-1} \subset \G$
\item a set of corresponding amount commitments $\{P_k\}_{k=0}^{N-1} \subset \G$
\item a set of private keys $\{r^{(u)}\}_{u=0}^{w-1} \subset \F$
\item a set of commitment amounts and blinding factors $\{(s^{(u)},a_u)\}_{u=0}^{w-1} \subset \F^2$
\item a set $\{l^{(u)}\}_{u=0}^{w-1} \subset \F$ such that:
\begin{itemize}
\item each $M_{l^{(u)}} = r^{(u)}G$ has its private key known to the prover
\item each $P_{l^{(u)}} = s^{(u)}G + a_uH$ has its amount and blinding factor known to the prover
\end{itemize}
\item a set of new amount commitments $\{Q_j\}_{j=0}^{T-1} \subset \G$
\item a set of commitment amounts and blinding factors $\{(t_j,b_j)\}_{j=0}^{T-1} \subset \F^2$ such that:
\begin{itemize}
\item each $Q_j = t_jG + b_jH$ has its amount and blinding factor known to the prover
\item $\sum_{u=0}^{w-1} a_j - \sum_{j=0}^{T-1} b_j = 0$
\end{itemize}
\end{itemize}

The prover then performs these steps:
\begin{itemize}
\item Define $\left\{J^{(u)}\right\}_{u=0}^{w-1} \subset \G$ such that $J^{(u)} \equiv (r^{(u)})^{-1}\hp(M_{l_u})$.
\item Select random $r_A \in \F$ and $\left\{a^{(u)}_{j,i}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1} \subset \F^3$. Define $A \equiv \com(a,r_A)$.
\item Define $\left\{\sigma^{(u)}_{j,i}\right\}_{i,j,u=0}^{n-1,j-1,w-1} \subset \F^3$ such that $\sigma^{(u)}_{j,i} \equiv \delta\left(l^{(u)}_j,i\right)$ (using our decomposition notation), and choose random $r_B \in \F$. Define $B \equiv \com(\sigma,r_B)$.
\item Select random $r_C \in \F$, and define $C \equiv \com(a(1-2\sigma), r_C)$.
\item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
\item Select random $\left\{\rho^{(u)}_j\right\}_{j,u=0}^{m-1,w-1} \subset \F^2$.
\item For each $0 \leq u < w$, define coefficients $\left\{p^{(u)}_{k,j}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p^{(u)}_k(x) \equiv \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} = \delta\left(l^{(u)},k\right)x^m + \sumj p^{(u)}_{k,j}x^j$$ (using our decomposition notation). Then define $p_{k,j} \equiv \sumu p^{(u)}_{k,j}$ and $p_k(x) \equiv \sumu p^{(u)}_k(x)$ accordingly.
\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}M_k + \sumu \rho^{(u)}_jG$$
\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv \sumk p_{k,j}\hp(M_k) + \sumu \rho^{(u)}_jJ^{(u)}$$
\item Define $\{Z_j\}_{j=0}^{m-1} \subset \G$ such that: $$Z_j \equiv \sumk p_{k,j}P_k + \sumu \rho^{(u)}_jG$$
\item Define the Fiat-Shamir transcript challenge $x \in \F$ computed using all public parameters and these elements (with set notation dropped for brevity): $$M,P,Q,J,A,B,C,D,X,Y,Z$$
\item Define $\left\{f^{(u)}_{j,i}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1}$ such that $f^{(u)}_{j,i} \equiv \sigma^{(u)}_{j,i}x + a^{(u)}_{j,i}$.
\item Define $z_A \equiv r_A + xr_B$ and $z_C \equiv xr_C + r_D$.
\item Define $\left\{z^{(u)}_R\right\}_{u=0}^{w-1} \subset \F$ such that: $$z^{(u)}_R \equiv r^{(u)}x^m - \sumj \rho^{(u)}_jx^j$$
\item Define: $$z_S \equiv x^m\left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right) - \sumj \left(x^j \sumu \rho^{(u)}_j\right)$$
\end{itemize}

The proof consists of these elements (with set notation dropped for brevity):
$$J,A,B,C,D,X,Y,Z,f,z_A,z_C,z_R,z_S$$
A proof consists of $3m + w + 4$ elements of $\G$, and $w\left[ m(n-1) + 1 \right] + 3$ elements of $\F$.

\subsection{Verifier}
The verifier accepts the following:
\begin{itemize}
\item a set of outputs $\{M_k\}_{k=0}^{N-1}$
\item a set of corresponding amount commitments $\{P_k\}_{k=0}^{N-1}$
\item a proof generated by a prover
\end{itemize}

All prover-supplied elements are checked to ensure their membership in the proper set (either the scalar field $\F$ or the group $\G$, as appropriate). The verifier uses the public parameters and proof elements to construct the Fiat-Shamir transcript challenge $x$, and then performs these steps:
\begin{itemize}
\item Ensure that each $J^{(u)}$ is unique for $0 \leq u < w$. Reject otherwise.
\item For all $0 \leq u < w$ and $0 \leq j < m$, set: $$f^{(u)}_{j,0} \equiv x - \sum_{i=1}^{n-1} f^{(u)}_{j,i}$$
\item{($A/B$ check)} Check that $\com(f,z_A) = A + xB$ and reject otherwise.
\item{($C/D$ check)} Check that $\com(f(x-f),z_C) = xC + D$ and reject otherwise.
\item{($X$ check)} Check that $$\sumk M_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jX_j - \sumu z^{(u)}_RG = 0$$ and reject otherwise.
\item{($Y$ check)} Check that $$\sumk \hp(M_k) \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} = 0$$ and reject otherwise.
\item{($Z$ check)} Check that $$\sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jZ_j - x^m\sum_{j=0}^{T-1} Q_j - z_SG = 0$$ and reject otherwise.
\end{itemize}

\section{Security}
We are interested initially to know whether the Triptych proving system is correct.

\subsection{Correctness}
To show that a correct proof will always be accepted by an honest verifier, we examine each verifier check separately.

The $A/B$ check passes using the identity $$\sumi \sigma^{(u)}_{j,i} = 1$$ for all $0 \leq j < m$ and $0 \leq u < w$.

The $C/D$ check passes similarly, using the identity $$\left(\sigma^{(u)}_{j,i}\right)^2 = \sigma^{(u)}_{j,i}$$ for all $0 \leq j < m$ and $0 \leq u < w$.

To show the correctness of the $X$ check:
\begin{eqnarray*}
&& \sumk M_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jX_j - \sumu z^{(u)}_RG \\
&=& \sumk M_k p_k(x) - \sumj x^j \left( \sumk p_{k,j}M_k + \sumu \rho^{(u)}_jG \right) - \sumu z^{(u)}_RG \\
&=& \sumk M_k \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jG - \sumu z^{(u)}_RG \\
&=& \sumk M_k \left[ \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_jG - \sumu\left[ r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right]G \\
&=& x^m\sumu r^{(u)}G - \sumj x^j \sumu \rho^{(u)}_jG - x^m\sumu r^{(u)}G + \sumj x^j \sumu \rho^{(u)}_jG \\
&=& 0
\end{eqnarray*}

The $Y$-check proceeds similarly, but with more irritating algebra:
\begin{eqnarray*}
&& \sumk \hp(M_k) \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} \\
&=& \sumk \hp(M_k) p_k(x) - \sumj x^j \left( \sumk p_{k,j}\hp(M_k) + \sumu \rho^{(u)}_jJ^{(u)} \right) - \sumu z^{(u)}_RJ^{(u)} \\
&=& \sumk \hp(M_k) \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jJ^{(u)} - \sumu z^{(u)}_RJ^{(u)} \\
&=& \sumk \hp(M_k) \left[ \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) - \sumu\left[ r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right](r^{(u)})^{-1}\hp(M_{l^{(u)}}) \\
&=& x^m\sumu \hp(M_{l^{(u)}}) - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) - x^m\sumu \hp(M_{l^{(u)}}) + \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) \\
&=& 0
\end{eqnarray*}

Finally, the $Z$-check:
\begin{eqnarray*}
&& \sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jZ_j - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
&=& \sumk P_k p_k(x) - \sumj x^j \left( \sumk p_{k,j}P_k + \sumu \rho^{(u)}_jG \right) - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
&=& \sumk P_k \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jG - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
&=& x^m\sumu (s^{(u)}G + a_uH) - \sumj x^j \sumu \rho^{(u)}_jG - x^m\sum_{j=0}^{T-1} (t_jG + b_jH) - x^m\left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right)G + \sumj x^j \sumu \rho^{(u)}_jG \\
&=& \left( \sumu a_u - \sum_{j=0}^{T-1} b_j \right)H \\
&=& 0
\end{eqnarray*}

\section{Optimizations}
We note that all verifier checks can be reduced to multiscalar multiplications yielding the identity element in $\G$, and that the tensor commitment $A/B$ and $C/D$ checks have the same number of elements if the parameters $n,m,u$ are assumed to be fixed. This means the verifier can verify all such commitments (whether part of the same proof or not) by combining scalars across common generators using a set of verifier-selected random weighting factors. This combination of commitments may be similarly weight-combined with the $X,Y,Z$ checks. The end result is that a collection of arbitrary proofs may be verified using a single multiscalar multiplication operation, with common generators reused as they appear.

Several algorithms exist for evaluating multiscalar multiplications more efficiently than a straightforward multiply-then-add arrangement, reducing the overall time complexity of a multiscalar multiplication with $N$ terms as low as $O(N/\log(N))$, such as the Straus \cite{straus} and Pippenger \cite{pippenger} families of algorithms.

Further, note that newly-generated output commitments must come equipped with range proofs demonstrating that amounts lie within a range sufficiently below $|\G|$ to avoid overflow. The Bulletproofs range proof construction is particularly efficient for this purpose \cite{bulletproofs}. It too supports delayed batch verification of the same type discussed here, offering additional optimizations. In particular, combining the fixed generators from the Bulletproofs public parameters with the fixed generators in Triptych can further reduce the time complexity of verification. The size of Bulletproofs range proofs is logarithmic in the product of the number of bits in the range and the number of outputs generated.

\bibliographystyle{plain}
\bibliography{main}

\end{document}

### 2019-10-22 triptych/triptych.py
Better input checks

@@ -53,7 +53,6 @@ def com_tensor(v,r):
 
 # Decompose a value with given base and size
 def decompose(val,base,size,t=int):
-    temp_val = val # for reconstruction testing
     r = []
     for i in range(size-1,-1,-1):
         slot = base**i
@@ -99,27 +98,32 @@ def convolve(x,y,size=None):
 #  l: list of indices such that each M[l[i]] is a commitment to zero
 #  r: list of Pedersen blinders for all M[l[i]]
 #  s: list of Pedersen blinders for all P[l[i]]
-#  t: list of Pedersen blinders for all Q[l[i]]
+#  t: list of Pedersen blinders for all Q[i]
 #  a: list of Pedersen values for all P[l[i]]
-#  b: list of Pedersen values for all Q[l[i]]
+#  b: list of Pedersen values for all Q[i]
 #  m: dimension such that len(M) == 2**m
 # RETURNS
 #  proof structure
 def prove(M,P,Q,l,r,s,t,a,b,m):
     n = 2 # binary decomposition
 
-    # Size check
+    # Commitment list size check
     if not len(M) == n**m or not len(P) == n**m:
-        raise IndexError('Bad size decomposition!')
+        raise IndexError('Input size mismatch!')
+    if not len(l) == len(r) or not len(l) == len(s) or not len(l) == len(a):
+        raise IndexError('Input size mismatch!')
+    if not len(Q) == len(t) or not len(Q) == len(b):
+        raise IndexError('Output size mismatch!')
     N = len(M)
 
     # Reconstruct the known commitments
-    if not len(l) == len(r) or not len(l) == len(s):
-        raise IndexError('Index/blinder size mismatch!')
     w = len(l)
     for i in range(w):
-        if not M[l[i]] == r[i]*G:
-            raise ValueError('Bad commitment blinder!')
+        if not M[l[i]] == r[i]*G or not P[l[i]] == s[i]*G + a[i]*H:
+            raise ValueError('Bad input commitment!')
+    for j in range(len(Q)):
+        if not Q[j] == t[j]*G + b[j]*H:
+            raise ValueError('Bad output commitment!')
 
     # Construct key images
     J = []

### 2019-10-23 paper/main.tex
Paper line endings
SHVZK proof and corresponding algorithm update

@@
 \subsection{Warning}
-There is currently no security model established for Triptych, and no proofs of security (except for correctness).
+There is currently no security model established for Triptych, and incomplete proofs of security.
 This document currently serves only to describe the construction and its algorithms.
@@
 \subsection{Notation}
-For a three-dimensional tensor $f \equiv (f_{i,j,k}) \subset \F^3$ and blinding factor $r \in \F$, define the Pedersen tensor commitment $$\com(f,r) \equiv rH + \sum_{i,j,k} f_{i,j,k} G_{i,j,k}$$ using fixed independent generators as described above.
+For a three-dimensional tensor $f \equiv (f_{i,j,k}) \subset \F$ and blinding factor $r \in \F$, define the Pedersen tensor commitment $$\com(f,r) \equiv rH + \sum_{i,j,k} f_{i,j,k} G_{i,j,k}$$ using fixed independent generators as described above.
 Operations on tensors are assumed to be performed componentwise.
@@
 \item a set of private keys $\{r^{(u)}\}_{u=0}^{w-1} \subset \F$
-\item a set of commitment amounts and blinding factors $\{(s^{(u)},a_u)\}_{u=0}^{w-1} \subset \F^2$
+\item a set of commitment amounts and blinding factors $\{(s^{(u)},a_u)\}_{u=0}^{w-1} \subset \F$
 \item a set $\{l^{(u)}\}_{u=0}^{w-1} \subset \F$ such that:
@@
 \item a set of new amount commitments $\{Q_j\}_{j=0}^{T-1} \subset \G$
-\item a set of commitment amounts and blinding factors $\{(t_j,b_j)\}_{j=0}^{T-1} \subset \F^2$ such that:
+\item a set of commitment amounts and blinding factors $\{(t_j,b_j)\}_{j=0}^{T-1} \subset \F$ such that:
 \begin{itemize}
@@
 \item Define $\left\{J^{(u)}\right\}_{u=0}^{w-1} \subset \G$ such that $J^{(u)} \equiv (r^{(u)})^{-1}\hp(M_{l_u})$.
-\item Select random $r_A \in \F$ and $\left\{a^{(u)}_{j,i}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1} \subset \F^3$. Define $A \equiv \com(a,r_A)$.
-\item Define $\left\{\sigma^{(u)}_{j,i}\right\}_{i,j,u=0}^{n-1,j-1,w-1} \subset \F^3$ such that $\sigma^{(u)}_{j,i} \equiv \delta\left(l^{(u)}_j,i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
+\item Select random $r_A \in \F$ and $\left\{a^{(u)}_{j,i}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1} \subset \F$.
+Define $A \equiv \com(a,r_A)$.
+\item Define $\left\{\sigma^{(u)}_{j,i}\right\}_{i,j,u=0}^{n-1,j-1,w-1} \subset \F$ such that $\sigma^{(u)}_{j,i} \equiv \delta\left(l^{(u)}_j,i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
 Define $B \equiv \com(\sigma,r_B)$.
@@
 \item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
-\item Select random $\left\{\rho^{(u)}_j\right\}_{j,u=0}^{m-1,w-1} \subset \F^2$.
+\item Select random $\left\{\rho^{(u)}_j\right\}_{j,u=0}^{m-1,w-1}, \left\{\overline{\rho}^{(u)}_j\right\}_{j,u=0}^{m-1,w-1} \subset \F$.
 \item For each $0 \leq u < w$, define coefficients $\left\{p^{(u)}_{k,j}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p^{(u)}_k(x) \equiv \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} = \delta\left(l^{(u)},k\right)x^m + \sumj p^{(u)}_{k,j}x^j$$ (using our decomposition notation).
@@
 \item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv \sumk p_{k,j}\hp(M_k) + \sumu \rho^{(u)}_jJ^{(u)}$$
-\item Define $\{Z_j\}_{j=0}^{m-1} \subset \G$ such that: $$Z_j \equiv \sumk p_{k,j}P_k + \sumu \rho^{(u)}_jG$$
+\item Define $\{Z_j\}_{j=0}^{m-1} \subset \G$ such that: $$Z_j \equiv \sumk p_{k,j}P_k + \sumu \overline{\rho}^{(u)}_jG$$
 \item Define the Fiat-Shamir transcript challenge $x \in \F$ computed using all public parameters and these elements (with set notation dropped for brevity): $$M,P,Q,J,A,B,C,D,X,Y,Z$$
@@
 \item Define $\left\{z^{(u)}_R\right\}_{u=0}^{w-1} \subset \F$ such that: $$z^{(u)}_R \equiv r^{(u)}x^m - \sumj \rho^{(u)}_jx^j$$
-\item Define: $$z_S \equiv x^m\left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right) - \sumj \left(x^j \sumu \rho^{(u)}_j\right)$$
+\item Define: $$z_S \equiv x^m\left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right) - \sumj \left(x^j \sumu \overline{\rho}^{(u)}_j\right)$$
 \end{itemize}
@@
 \begin{itemize}
-\item Ensure that each $J^{(u)}$ is unique for $0 \leq u < w$. Reject otherwise.
+\item Ensure that each $J^{(u)}$ is unique for $0 \leq u < w$.
+Reject otherwise.
 \item For all $0 \leq u < w$ and $0 \leq j < m$, set: $$f^{(u)}_{j,0} \equiv x - \sum_{i=1}^{n-1} f^{(u)}_{j,i}$$
@@
 \section{Security}
-We are interested initially to know whether the Triptych proving system is correct.
+We are interested initially to show that Triptych proving system is perfectly complete, special honest verifier zero-knowledge, and special sound.
+Note that being special honest verifier zero-knowledge implies that the construction is also witness-indistinguishable \cite{cramer}.
 
-\subsection{Correctness}
-To show that a correct proof will always be accepted by an honest verifier, we examine each verifier check separately.
+\subsection{Perfect completeness}
+To show that a valid proof will always be accepted by an honest verifier, we examine each verifier check separately.
 
-The $A/B$ check passes using the identity $$\sumi \sigma^{(u)}_{j,i} = 1$$ for all $0 \leq j < m$ and $0 \leq u < w$.
+The $A/B$ check succeeds on a valid proof using the identity $$\sumi \sigma^{(u)}_{j,i} = 1$$ for all $0 \leq j < m$ and $0 \leq u < w$.
 
-The $C/D$ check passes similarly, using the identity $$\left(\sigma^{(u)}_{j,i}\right)^2 = \sigma^{(u)}_{j,i}$$ for all $0 \leq j < m$ and $0 \leq u < w$.
+The $C/D$ check succeeds similarly, using the identity $$\left(\sigma^{(u)}_{j,i}\right)^2 = \sigma^{(u)}_{j,i}$$ for all $0 \leq j < m$ and $0 \leq u < w$.
 
@@
 && \sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jZ_j - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
-&=& \sumk P_k p_k(x) - \sumj x^j \left( \sumk p_{k,j}P_k + \sumu \rho^{(u)}_jG \right) - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
-&=& \sumk P_k \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jG - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
-&=& x^m\sumu (s^{(u)}G + a_uH) - \sumj x^j \sumu \rho^{(u)}_jG - x^m\sum_{j=0}^{T-1} (t_jG + b_jH) - x^m\left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right)G + \sumj x^j \sumu \rho^{(u)}_jG \\
+&=& \sumk P_k p_k(x) - \sumj x^j \left( \sumk p_{k,j}P_k + \sumu \overline{\rho}^{(u)}_jG \right) - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
+&=& \sumk P_k \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \overline{\rho}^{(u)}_jG - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
+&=& x^m\sumu (s^{(u)}G + a_uH) - \sumj x^j \sumu \overline{\rho}^{(u)}_jG - x^m\sum_{j=0}^{T-1} (t_jG + b_jH) - x^m\left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right)G + \sumj x^j \sumu \overline{\rho}^{(u)}_jG \\
 &=& \left( \sumu a_u - \sum_{j=0}^{T-1} b_j \right)H \\
@@
 \end{eqnarray*}
+
+\subsection{Special honest verifier zero-knowledge}
+We construct a special honest verifier zero-knowledge simulator that, given a random verifier challenge $x$, can construct a proof transcript with identical distribution to a valid proof.
+
+First, observe that the simulator presented in the proof of Lemma 1 in \cite{bootle} translates nearly identically to our setting, since we can flatten tensor commitments to a matrix structure with the required sum property.
+If the simulator chooses $B \in \G$ randomly, the cited lemma assures us a valid simulation of the proof elements $A,C,D,z_A,z_C,\{f^{(u)}_{j,i \neq 0}\}$; we may compute each $f^{(u)}_{j,0}$ from here.
+Further, in a valid proof, $B$ is independent and uniformly distributed as well.
+
+The decisional Diffie-Hellman assumption implies that the elements $\{X_j\}_{j=1}^{m-1}, \{Y_j\}_{j=1}^{m-1}, \{Z_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof, so the simulator may choose these randomly.
+The verification checks require that $X_0,Y_0,Z_0$ be uniquely determined by the other elements in the corresponding sets in both real proofs and by the simulator.
+
+Finally, the elements $\{z^{(u)}_R\}_{u=0}^{w-1}$ and $z_S$ are independent and uniformly distributed in valid proofs given random $x$, so the simulator may choose them randomly.
+Hence the construction is special honest verifier zero-knowledge.
 

### 2019-10-23 triptych/triptych.py

@@ -1,5 +1,4 @@
 # Proof-of-concept implementation of https://github.com/monero-project/research-lab/issues/56
-# This version proves knowledge of one or more commitments to zero in a list, with key images and amount commitments
 
 from dumb25519 import hash_to_point, random_scalar, Scalar, hash_to_scalar, G, random_point, Z
 import dumb25519
@@ -193,16 +192,17 @@ def prove(M,P,Q,l,r,s,t,a,b,m):
     X = [dumb25519.Z for _ in range(m)]
     Y = [dumb25519.Z for _ in range(m)]
     Z = [dumb25519.Z for _ in range(m)]
-    rho = [[random_scalar() for _ in range(m)] for _ in range(w)]
+    rho_R = [[random_scalar() for _ in range(m)] for _ in range(w)]
+    rho_S = [[random_scalar() for _ in range(m)] for _ in range(w)]
     for j in range(m):
         for i in range(N):
             X[j] += M[i]*p[0][i][j]
             Y[j] += hash_to_point(M[i])*p[0][i][j]
             Z[j] += P[i]*p[0][i][j]
         for u in range(w):
-            X[j] += rho[u][j]*G
-            Y[j] += rho[u][j]*J[u]
-            Z[j] += rho[u][j]*G
+            X[j] += rho_R[u][j]*G
+            Y[j] += rho_R[u][j]*J[u]
+            Z[j] += rho_S[u][j]*G
 
     # Partial proof
     proof = Proof()
@@ -233,8 +233,8 @@ def prove(M,P,Q,l,r,s,t,a,b,m):
         zS += s[u]*x**m
     for j in range(m):
         for u in range(w):
-            zR[u] -= rho[u][j]*x**j
-            zS -= rho[u][j]*x**j
+            zR[u] -= rho_R[u][j]*x**j
+            zS -= rho_S[u][j]*x**j
     for i in range(len(t)):
         zS -= t[i]*x**m
 

### 2019-10-23 paper/main.tex
Aggregation coefficients for soundness proof

@@
 Then define $p_{k,j} \equiv \sumu p^{(u)}_{k,j}$ and $p_k(x) \equiv \sumu p^{(u)}_k(x)$ accordingly.
-\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}M_k + \sumu \rho^{(u)}_jG$$
-\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv \sumk p_{k,j}\hp(M_k) + \sumu \rho^{(u)}_jJ^{(u)}$$
+\item Define aggregation coefficients $\{\mu_k\}_{k=0}^{N-1}$ using a $k$-indexed $\hs$ operation, containing all public parameters and proof elements.
+\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}\mu_kM_k + \sumu \rho^{(u)}_jG$$
+\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv \sumk p_{k,j}\mu_k\hp(M_k) + \sumu \rho^{(u)}_jJ^{(u)}$$
 \item Define $\{Z_j\}_{j=0}^{m-1} \subset \G$ such that: $$Z_j \equiv \sumk p_{k,j}P_k + \sumu \overline{\rho}^{(u)}_jG$$
@@
 \item Define $z_A \equiv r_A + xr_B$ and $z_C \equiv xr_C + r_D$.
-\item Define $\left\{z^{(u)}_R\right\}_{u=0}^{w-1} \subset \F$ such that: $$z^{(u)}_R \equiv r^{(u)}x^m - \sumj \rho^{(u)}_jx^j$$
+\item Define $\left\{z^{(u)}_R\right\}_{u=0}^{w-1} \subset \F$ such that: $$z^{(u)}_R \equiv \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j$$
 \item Define: $$z_S \equiv x^m\left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right) - \sumj \left(x^j \sumu \overline{\rho}^{(u)}_j\right)$$
@@
 All prover-supplied elements are checked to ensure their membership in the proper set (either the scalar field $\F$ or the group $\G$, as appropriate).
-The verifier uses the public parameters and proof elements to construct the Fiat-Shamir transcript challenge $x$, and then performs these steps:
+The verifier uses the public parameters and proof elements to construct the Fiat-Shamir transcript challenge $x$ and aggregation coefficients $\{\mu_k\}_{k=0}^{N-1}$, and then performs these steps:
 \begin{itemize}
@@
 \item{($C/D$ check)} Check that $\com(f(x-f),z_C) = xC + D$ and reject otherwise.
-\item{($X$ check)} Check that $$\sumk M_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jX_j - \sumu z^{(u)}_RG = 0$$ and reject otherwise.
-\item{($Y$ check)} Check that $$\sumk \hp(M_k) \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} = 0$$ and reject otherwise.
+\item{($X$ check)} Check that $$\sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jX_j - \sumu z^{(u)}_RG = 0$$ and reject otherwise.
+\item{($Y$ check)} Check that $$\sumk \mu_k\hp(M_k) \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} = 0$$ and reject otherwise.
 \item{($Z$ check)} Check that $$\sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jZ_j - x^m\sum_{j=0}^{T-1} Q_j - z_SG = 0$$ and reject otherwise.
@@
 \begin{eqnarray*}
-&& \sumk M_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jX_j - \sumu z^{(u)}_RG \\
-&=& \sumk M_k p_k(x) - \sumj x^j \left( \sumk p_{k,j}M_k + \sumu \rho^{(u)}_jG \right) - \sumu z^{(u)}_RG \\
-&=& \sumk M_k \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jG - \sumu z^{(u)}_RG \\
-&=& \sumk M_k \left[ \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_jG - \sumu\left[ r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right]G \\
-&=& x^m\sumu r^{(u)}G - \sumj x^j \sumu \rho^{(u)}_jG - x^m\sumu r^{(u)}G + \sumj x^j \sumu \rho^{(u)}_jG \\
+&& \sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jX_j - \sumu z^{(u)}_RG \\
+&=& \sumk \mu_kM_k p_k(x) - \sumj x^j \left( \sumk p_{k,j}\mu_kM_k + \sumu \rho^{(u)}_jG \right) - \sumu z^{(u)}_RG \\
+&=& \sumk \mu_kM_k \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jG - \sumu z^{(u)}_RG \\
+&=& \sumk \mu_kM_k \left[ \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_jG - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right]G \\
+&=& x^m\sumu \mu_{l^{(u)}}r^{(u)}G - \sumj x^j \sumu \rho^{(u)}_jG - x^m\sumu \mu_{l^{(u)}}r^{(u)}G + \sumj x^j \sumu \rho^{(u)}_jG \\
 &=& 0
@@
 \begin{eqnarray*}
-&& \sumk \hp(M_k) \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} \\
-&=& \sumk \hp(M_k) p_k(x) - \sumj x^j \left( \sumk p_{k,j}\hp(M_k) + \sumu \rho^{(u)}_jJ^{(u)} \right) - \sumu z^{(u)}_RJ^{(u)} \\
-&=& \sumk \hp(M_k) \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jJ^{(u)} - \sumu z^{(u)}_RJ^{(u)} \\
-&=& \sumk \hp(M_k) \left[ \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) - \sumu\left[ r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right](r^{(u)})^{-1}\hp(M_{l^{(u)}}) \\
-&=& x^m\sumu \hp(M_{l^{(u)}}) - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) - x^m\sumu \hp(M_{l^{(u)}}) + \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) \\
+&& \sumk \mu_k\hp(M_k) \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu_k\hp(M_k) p_k(x) - \sumj x^j \left( \sumk p_{k,j}\mu_k\hp(M_k) + \sumu \rho^{(u)}_jJ^{(u)} \right) - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu_k\hp(M_k) \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jJ^{(u)} - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu_k\hp(M_k) \left[ \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right](r^{(u)})^{-1}\hp(M_{l^{(u)}}) \\
+&=& x^m\sumu \mu_{l^{(u)}}\hp(M_{l^{(u)}}) - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) - x^m\sumu \mu_{l^{(u)}}\hp(M_{l^{(u)}}) + \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) \\
 &=& 0

### 2019-10-23 triptych/triptych.py

@@ -94,12 +94,12 @@ def convolve(x,y,size=None):
 #  M: public key list
 #  P: input commitment list
 #  Q: output commitment list
-#  l: list of indices such that each M[l[i]] is a commitment to zero
-#  r: list of Pedersen blinders for all M[l[i]]
-#  s: list of Pedersen blinders for all P[l[i]]
-#  t: list of Pedersen blinders for all Q[i]
-#  a: list of Pedersen values for all P[l[i]]
-#  b: list of Pedersen values for all Q[i]
+#  l: list of indices such that each M[l[u]] is a commitment to zero
+#  r: list of Pedersen blinders for all M[l[u]]
+#  s: list of Pedersen blinders for all P[l[u]]
+#  t: list of Pedersen blinders for all Q[j]
+#  a: list of Pedersen values for all P[l[u]]
+#  b: list of Pedersen values for all Q[j]
 #  m: dimension such that len(M) == 2**m
 # RETURNS
 #  proof structure
@@ -117,8 +117,8 @@ def prove(M,P,Q,l,r,s,t,a,b,m):
 
     # Reconstruct the known commitments
     w = len(l)
-    for i in range(w):
-        if not M[l[i]] == r[i]*G or not P[l[i]] == s[i]*G + a[i]*H:
+    for u in range(w):
+        if not M[l[u]] == r[u]*G or not P[l[u]] == s[u]*G + a[u]*H:
             raise ValueError('Bad input commitment!')
     for j in range(len(Q)):
         if not Q[j] == t[j]*G + b[j]*H:
@@ -126,8 +126,8 @@ def prove(M,P,Q,l,r,s,t,a,b,m):
 
     # Construct key images
     J = []
-    for i in range(w):
-        J.append(r[i].invert()*hash_to_point(M[l[i]]))
+    for u in range(w):
+        J.append(r[u].invert()*hash_to_point(M[l[u]]))
 
     # Prepare matrices and corresponding blinders
     rA = random_scalar()
@@ -192,12 +192,13 @@ def prove(M,P,Q,l,r,s,t,a,b,m):
     X = [dumb25519.Z for _ in range(m)]
     Y = [dumb25519.Z for _ in range(m)]
     Z = [dumb25519.Z for _ in range(m)]
+    mu = [hash_to_scalar(i,M,P,Q,J,A,B,C,D) for i in range(N)] # aggregation coefficients
[…]

### 2019-10-25 paper/main.tex
Incomplete special-soundness proof

@@
 \subsection{Notation}
-For a three-dimensional tensor $f \equiv (f_{i,j,k}) \subset \F$ and blinding factor $r \in \F$, define the Pedersen tensor commitment $$\com(f,r) \equiv rH + \sum_{i,j,k} f_{i,j,k} G_{i,j,k}$$ using fixed independent generators as described above.
+For a three-dimensional tensor $f \equiv (f_{i,j,k}) \subset \F$ and blinding factor $r \in \F$, define the Pedersen tensor commitment
+$$\com(f,r) \equiv rH + \sum_{i,j,k} f_{i,j,k} G_{i,j,k}$$
+using fixed independent generators as described above.
 Operations on tensors are assumed to be performed componentwise.
@@
 
-We sometimes use index subscript notation of the form $i_j$ to indicate the $j$ digit of $i$, where such a decomposition of $i$ is taken base $n$ with padded length $m$.
-That is, for $n=2$, this indexes a binary decomposition.
+We sometimes use index subscript notation of the form $i_j$ to indicate the $j$ digit of $i$, where such a decomposition of $i$ is taken base $n$ with padded length $m$:
+$$\sum_{j=0}^m i_j n^j = i$$
 This notation will be specified explicitly where confusion may occur.
@@
 \item a set of commitment amounts and blinding factors $\{(s^{(u)},a_u)\}_{u=0}^{w-1} \subset \F$
-\item a set $\{l^{(u)}\}_{u=0}^{w-1} \subset \F$ such that:
+\item a set of linking tags $\left\{J^{(u)}\right\}_{u=0}^{w-1} \subset \G$
+\item a set $\{l^{(u)}\}_{u=0}^{w-1} \subset \F$
 \begin{itemize}
@@
 \item each $P_{l^{(u)}} = s^{(u)}G + a_uH$ has its amount and blinding factor known to the prover
+\item each $J^{(u)} = (r^{(u)})^{-1}\hp(M_{l_u})$
 \end{itemize}
@@
 \begin{itemize}
-\item Define $\left\{J^{(u)}\right\}_{u=0}^{w-1} \subset \G$ such that $J^{(u)} \equiv (r^{(u)})^{-1}\hp(M_{l_u})$.
 \item Select random $r_A \in \F$ and $\left\{a^{(u)}_{j,i}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1} \subset \F$.
@@
 The proof consists of these elements (with set notation dropped for brevity):
-$$J,A,B,C,D,X,Y,Z,f,z_A,z_C,z_R,z_S$$
+$$A,B,C,D,X,Y,Z,f,z_A,z_C,z_R,z_S$$
 A proof consists of $3m + w + 4$ elements of $\G$, and $w\left[ m(n-1) + 1 \right] + 3$ elements of $\F$.
@@
 \item a set of corresponding amount commitments $\{P_k\}_{k=0}^{N-1}$
+\item a set of linking tags $\{J^{(u)}\}_{u=0}^{w-1}$
 \item a proof generated by a prover
@@
 
+Proofs follow similarly to those in \cite{bootle}.
+
 \subsection{Perfect completeness}
@@
 &=& \sumk \mu_kM_k \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jG - \sumu z^{(u)}_RG \\
-&=& \sumk \mu_kM_k \left[ \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_jG - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right]G \\
+&=& \sumk \mu_kM_k \left[ x^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_jG - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right]G \\
 &=& x^m\sumu \mu_{l^{(u)}}r^{(u)}G - \sumj x^j \sumu \rho^{(u)}_jG - x^m\sumu \mu_{l^{(u)}}r^{(u)}G + \sumj x^j \sumu \rho^{(u)}_jG \\
@@
 &=& \sumk \mu_k\hp(M_k) \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jJ^{(u)} - \sumu z^{(u)}_RJ^{(u)} \\
-&=& \sumk \mu_k\hp(M_k) \left[ \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right](r^{(u)})^{-1}\hp(M_{l^{(u)}}) \\
+&=& \sumk \mu_k\hp(M_k) \left[ x^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right](r^{(u)})^{-1}\hp(M_{l^{(u)}}) \\
 &=& x^m\sumu \mu_{l^{(u)}}\hp(M_{l^{(u)}}) - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) - x^m\sumu \mu_{l^{(u)}}\hp(M_{l^{(u)}}) + \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) \\
@@
 
+\subsection{Special soundness}
+We claim that the protocol is $(m+1)$-special sound, where $m > 1$.
+To show this, we construct an extractor that, given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness.
+In particular, we produce a modified witness for the following relation that is based on the information presented in the prover algorithm:
+\begin{multline*}
+\left\{ \{M_k\}_{k=0}^{N-1},\{P_k\}_{k=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, r, y \right) : r = \sum_{u=0}^{w-1} \hs(l^{(u)},M,P,Q)r^{(u)} \text{ and } \right.
+\\
+\left.
+M_{l^{(u)}} = r_uG \; \forall \: u \in [0,w) \text{ and } r^{(u)}J^{(u)} = \hp(M_{l^{(u)}}) \; \forall \: u \in [0,w) \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \right\}
+\end{multline*}
+
+Collision resistance of $\hs$ means that, with high probability, knowledge of $r$ is equivalent to knowledge of $\{r^{(u)}\}$.
+The combination of the discrete logarithm problem on $\G$ and the collision-resistance of $\hp$ allows for double-spend enforcement using the linking tags $\{J^{(u)}\}$.
+The binding property of Pedersen commitments ensures that, for properly constructed commitments, knowledge of $y$ implies that the sum of values of input commitments $\{P_{l^{(u)}}\}$ balances the sum of output commitments $\{Q_j\}$.
+We may assume here that such commitments are correctly constructed, as this is shown by range proofs outside the scope of the proving system.
+
+Suppose that for a given statement, we have a set of $(m+1)$ distinct verifier challenges $\{x_e\}_{e=0}^m$ corresponding to distinct valid responses of this form:
+$$\left\{ \{{}_ef^{(u)}_{j,i}\}, \{{}_ez^{(u)}_R\}, {}_ez_S \right\}_{e=0}^m$$
+From the $3$-special soundness in \cite{bootle} and $m > 1$ we have valid extractions $\{\sigma^{(u)}_{j,i}\}_{u=0}^{w-1}$ and $\{a^{(u)}_{j,i}\}_{u=0}^{w-1}$, and the Pedersen binding property ensures that (with high probability) we have:
+$${}_ef^{(u)}_{j,i} = \sigma^{(u)}_{j,i}x_e + a^{(u)}_{j,i} \; \forall \: e \in [0,m]$$
+Using the extracted values, compute
+$$p_k(x) \equiv \sum_{u=0}^{w-1}\left[ \prod_{j=0}^{m-1} \left( \sigma^{(u)}_{j,k}x + a^{(u)}_{j,k} \right) \right]$$
+for all $k \in [0,N)$.
+
+We have seen that $p_k$ is of degree $m$ only when $k \in \{l^{(u)}\}_{u=0}^{w-1}$.
+Hence there exist coefficients $\{\overline{X}_j,\overline{Y}_j,\overline{Z}_j\}_{j=0}^{m-1}$, computed uniquely from the statement and extracted values, such that the verification equations are of the following form:
+\begin{eqnarray*}
+x^m \sumu \mu_{l^{(u)}}M_{l^{(u)}} + \sumj x^j\overline{X}_j &=& \left( \sumu z^{(u)}_R \right)G \\
+x^m \sumu \mu_{l^{(u)}}\hp(M_{l^{(u)}}) + \sumj x^j\overline{Y}_j &=& \sumu z^{(u)}_RJ^{(u)} \\
+x^m \sumu P_{l^{(u)}} + \sumj x^j\overline{Z}_j - x^m \sum_{j=0}^{T-1} Q_j &=& z_SG
+\end{eqnarray*}
+
+Construct a Vandermonde matrix $V$ where the $e$ row is the vector $(1,x_e,\ldots,x^m_e)$.
+Since all $x_e$ are distinct, the rows of $V$ span $\F^{m+1}$; hence there exist weights $\{\theta_e\}_{e=0}^m$ such that the resulting linear combination of rows produces the vector $(0,\ldots,0,1)$.
+That is, $\sum_{e=0}^m \theta_ex^j = \delta(j,m)$.
+
+For each verification equation, we can therefore build a linear combination over $e$. For the $X$-check:
+$$\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sum_{e=0}^m \theta_ex_e^m \left( \sumu \mu_{l^{(u)}} M_{l^{(u)}} \right) + \sum_{e=0}^m \theta_e \left( \sumj x_e^j \overline{X}_j \right) = \left[ \sum_{e=0}^m \theta_e \left( \sumu {}_ez^{(u)}_R \right) \right]G$$
+The rightmost bracketed double sum is therefore, with high probability, equal to $r = \mu_{l^{(u)}} r^{(u)}$.
+
+The $Z$-check proceeds similarly:
+$$\sumu P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = \sum_{e=0}^m \theta_ex_e^m \left( \sumu P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j \right) + \sum_{e=0}^m \theta_e \left( \sumj x_e^j \overline{Z}_j \right) = \left( \sum_{e=0}^m \theta_e {}_ez_S  \right)G$$
+Hence we have $y \equiv \sum_{e=0}^m \theta_e {}_ez_S$.
+
+Unfortunately, the same technique does not appear to apply for the $Y$-check. Doing so obtains the following:
+$$\sumu \mu_{l^{(u)}} \hp(M_{l^{(u)}}) = \sum_{e=0}^m \theta_ex_e^m \left( \sumu \mu_{l^{(u)}} \hp(M_{l^{(u)}}) \right) + \sum_{e=0}^m \theta_e \left( \sumj x_e^j \overline{Y}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) J^{(u)}$$
+It is unclear how to associate this with the required witness extraction.
+
+\textbf{Therefore, the special-soundness proof is incomplete!}
+
 \section{Optimizations}

### 2019-10-28 pybullet/pybullet.py
More efficient prover polynomial coefficient computation

@@ -167,16 +167,14 @@ def prove(data,N):
     l0 = aL - ScalarVector([z]*(M*N))
     l1 = sL
 
-    # ugly sum
+    # for polynomial coefficients
     zeros_twos = []
-    for i in range (M*N):
-        zeros_twos.append(Scalar(0))
-        for j in range(1,M+1):
-            temp = Scalar(0)
-            if i >= (j-1)*N and i < j*N:
-                temp = Scalar(2)**(i-(j-1)*N)
-            zeros_twos[-1] += temp*(z**(1+j))
-    
+    z_cache = z**2
+    for j in range(M):
+        for i in range(N):
+            zeros_twos.append(z_cache*2**i)
+        z_cache *= z
+
     # more polynomial coefficients
     r0 = aR + ScalarVector([z]*(M*N))
     r0 = r0*exp_scalar(y,M*N)

### 2019-10-28 lelantus/pybullet.py
Library update

@@ -159,15 +159,13 @@ def prove(data,N):
     l0 = aL - ScalarVector([z]*(M*N))
     l1 = sL
 
-    # ugly sum
+    # for polynomial coefficients
     zeros_twos = []
-    for i in range (M*N):
-        zeros_twos.append(Scalar(0))
-        for j in range(1,M+1):
-            temp = Scalar(0)
-            if i >= (j-1)*N and i < j*N:
-                temp = Scalar(2)**(i-(j-1)*N)
-            zeros_twos[-1] += temp*(z**(1+j))
+    z_cache = z**2
+    for j in range(M):
+        for i in range(N):
+            zeros_twos.append(z_cache*2**i)
+        z_cache *= z
     
     # more polynomial coefficients
     r0 = aR + ScalarVector([z]*(M*N))

### 2019-10-28 rct3/pybullet.py
Library update

@@ -166,15 +166,13 @@ def prove(data,N):
     l0 = aL - ScalarVector([z]*(M*N))
     l1 = sL
 
-    # ugly sum
+    # for polynomial coefficients
     zeros_twos = []
-    for i in range (M*N):
-        zeros_twos.append(Scalar(0))
-        for j in range(1,M+1):
-            temp = Scalar(0)
-            if i >= (j-1)*N and i < j*N:
-                temp = Scalar(2)**(i-(j-1)*N)
-            zeros_twos[-1] += temp*(z**(1+j))
+    z_cache = z**2
+    for j in range(M):
+        for i in range(N):
+            zeros_twos.append(z_cache*2**i)
+        z_cache *= z
     
     # more polynomial coefficients
     r0 = aR + ScalarVector([z]*(M*N))

### 2019-11-18 triptych/test.py
Updated linking tag format

@@ -7,17 +7,6 @@ import random
 G = dumb25519.G
 H = dumb25519.hash_to_point('H')
 
-# Given a list of linking tags, determine if there are any duplicates
-# NOTE: this scales poorly
-#
-# INPUT
-#   tags: list of linking tags (Point list)
-# OUTPUT
-#   boolean: True if a duplicate exists, False otherwise
-def double_spend(tags):
-    return len(tags) != len(set(tags))
-
-
 class TestValidProofs(unittest.TestCase):
     def test_valid_prove_verify(self):
         print ''

### 2019-11-18 triptych/triptych.py

@@ -5,6 +5,7 @@ import dumb25519
 import random
 
 H = hash_to_point('H')
+U = hash_to_point('U')
 
 # Proof structure
 class Proof:
@@ -127,7 +128,7 @@ def prove(M,P,Q,l,r,s,t,a,b,m):
     # Construct key images
     J = []
     for u in range(w):
-        J.append(r[u].invert()*hash_to_point(M[l[u]]))
+        J.append(r[u].invert()*U)
 
     # Prepare matrices and corresponding blinders
     rA = random_scalar()
@@ -198,7 +199,7 @@ def prove(M,P,Q,l,r,s,t,a,b,m):
     for j in range(m):
         for i in range(N):
             X[j] += M[i]*p[0][i][j]*mu[i]
-            Y[j] += hash_to_point(M[i])*p[0][i][j]*mu[i]
+            Y[j] += U*p[0][i][j]*mu[i]
             Z[j] += P[i]*p[0][i][j]
         for u in range(w):
             X[j] += rho_R[u][j]*G
@@ -313,7 +314,7 @@ def verify(M,P,Q,proof,m):
                 t[u] *= f[u][j][decomp_i[j]]
         for u in range(w):
             RX += M[i]*t[u]*mu[i]
-            RY += hash_to_point(M[i])*t[u]*mu[i]
+            RY += U*t[u]*mu[i]
             RZ += P[i]*t[u]
 
     for j in range(m):

### 2019-11-18 paper/main.tex
Paper updates

@@
 
-\title{Triptych}
-\author{Sarang Noether and Arthur Blue}
+\title{Triptych: multiple inputs}
+\author{Sarang Noether}
 \date{\today}
@@
 \newcommand{\F}{\mathbb{F}}
+\newcommand{\N}{\mathbb{N}}
 \newcommand{\hs}{\mathsf{H}}
@@
 Assume that any point of the form $G_i$ or $H_i$ (possibly with multiple indices) is a generator of $\G$ whose discrete logarithm relationship with all other such points is unknown; in the case of elliptic curve groups, using an indexed $\hp$ operation is appropriate for these generators.
-Let $G, H$ be distinguished generators used for Pedersen commitments.
+Let $G, H$ be distinguished generators of $\G$ used for Pedersen commitments.
+Let $U$ be a distinguished generator of $\G$.
 
@@
 \item a set of linking tags $\left\{J^{(u)}\right\}_{u=0}^{w-1} \subset \G$
-\item a set $\{l^{(u)}\}_{u=0}^{w-1} \subset \F$
+\item a set $\{l^{(u)}\}_{u=0}^{w-1} \subset \N$
 \begin{itemize}
@@
 \item each $P_{l^{(u)}} = s^{(u)}G + a_uH$ has its amount and blinding factor known to the prover
-\item each $J^{(u)} = (r^{(u)})^{-1}\hp(M_{l_u})$
+\item each $J^{(u)} = (r^{(u)})^{-1}U$
 \end{itemize}
@@
 \item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}\mu_kM_k + \sumu \rho^{(u)}_jG$$
-\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv \sumk p_{k,j}\mu_k\hp(M_k) + \sumu \rho^{(u)}_jJ^{(u)}$$
+\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv \sumk p_{k,j}\mu_kU + \sumu \rho^{(u)}_jJ^{(u)}$$
 \item Define $\{Z_j\}_{j=0}^{m-1} \subset \G$ such that: $$Z_j \equiv \sumk p_{k,j}P_k + \sumu \overline{\rho}^{(u)}_jG$$
@@
 \item{($X$ check)} Check that $$\sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jX_j - \sumu z^{(u)}_RG = 0$$ and reject otherwise.
-\item{($Y$ check)} Check that $$\sumk \mu_k\hp(M_k) \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} = 0$$ and reject otherwise.
+\item{($Y$ check)} Check that $$\sumk \mu_kU \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} = 0$$ and reject otherwise.
 \item{($Z$ check)} Check that $$\sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jZ_j - x^m\sum_{j=0}^{T-1} Q_j - z_SG = 0$$ and reject otherwise.
@@
 \begin{eqnarray*}
-&& \sumk \mu_k\hp(M_k) \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} \\
-&=& \sumk \mu_k\hp(M_k) p_k(x) - \sumj x^j \left( \sumk p_{k,j}\mu_k\hp(M_k) + \sumu \rho^{(u)}_jJ^{(u)} \right) - \sumu z^{(u)}_RJ^{(u)} \\
-&=& \sumk \mu_k\hp(M_k) \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jJ^{(u)} - \sumu z^{(u)}_RJ^{(u)} \\
-&=& \sumk \mu_k\hp(M_k) \left[ x^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right](r^{(u)})^{-1}\hp(M_{l^{(u)}}) \\
-&=& x^m\sumu \mu_{l^{(u)}}\hp(M_{l^{(u)}}) - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) - x^m\sumu \mu_{l^{(u)}}\hp(M_{l^{(u)}}) + \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}\hp(M_{l^{(u)}}) \\
+&& \sumk \mu_kU \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu_kU p_k(x) - \sumj x^j \left( \sumk p_{k,j}\mu_kU + \sumu \rho^{(u)}_jJ^{(u)} \right) - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu_kU \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jJ^{(u)} - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu_kU \left[ x^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right](r^{(u)})^{-1}U \\
+&=& x^m\sumu \mu_{l^{(u)}}U - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - x^m\sumu \mu_{l^{(u)}}U + \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U \\
 &=& 0
@@
 
+%The decisional Diffie-Hellman assumption implies that the elements {Xj} and {Yj} are independent and uniformly distributed in a valid proof" should be changed to "The selection of random \rho values and the computation of each \mu_k and H(M_k) under the random oracle model imply that X, Y, and Z are statistically uniform and independent..." or something like that.
+DDH is a worse
 The decisional Diffie-Hellman assumption implies that the elements $\{X_j\}_{j=1}^{m-1}, \{Y_j\}_{j=1}^{m-1}, \{Z_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof, so the simulator may choose these randomly.
@@
 \\
-\left.
-M_{l^{(u)}} = r_uG \; \forall \: u \in [0,w) \text{ and } r^{(u)}J^{(u)} = \hp(M_{l^{(u)}}) \; \forall \: u \in [0,w) \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \right\}
+\left. M_{l^{(u)}} = r_uG \; \forall \: u \in [0,w) \text{ and } r^{(u)}J^{(u)} = U \; \forall \: u \in [0,w) \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \right\}
 \end{multline*}
 
+% Since H is a random oracle, knowledge of r implies knowledge of {r^u} except with negligible probability
 Collision resistance of $\hs$ means that, with high probability, knowledge of $r$ is equivalent to knowledge of $\{r^{(u)}\}$.
+%  it's DL hardness on G together with the random oracle model
 The combination of the discrete logarithm problem on $\G$ and the collision-resistance of $\hp$ allows for double-spend enforcement using the linking tags $\{J^{(u)}\}$.
@@
 x^m \sumu \mu_{l^{(u)}}M_{l^{(u)}} + \sumj x^j\overline{X}_j &=& \left( \sumu z^{(u)}_R \right)G \\
-x^m \sumu \mu_{l^{(u)}}\hp(M_{l^{(u)}}) + \sumj x^j\overline{Y}_j &=& \sumu z^{(u)}_RJ^{(u)} \\
+x^m \sumu \mu_{l^{(u)}}U + \sumj x^j\overline{Y}_j &=& \sumu z^{(u)}_RJ^{(u)} \\
 x^m \sumu P_{l^{(u)}} + \sumj x^j\overline{Z}_j - x^m \sum_{j=0}^{T-1} Q_j &=& z_SG
@@
 Since all $x_e$ are distinct, the rows of $V$ span $\F^{m+1}$; hence there exist weights $\{\theta_e\}_{e=0}^m$ such that the resulting linear combination of rows produces the vector $(0,\ldots,0,1)$.
-That is, $\sum_{e=0}^m \theta_ex^j = \delta(j,m)$.
+That is, $\sum_{e=0}^m \theta_ex_e^j = \delta(j,m)$.
 
 For each verification equation, we can therefore build a linear combination over $e$. For the $X$-check:
-$$\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sum_{e=0}^m \theta_ex_e^m \left( \sumu \mu_{l^{(u)}} M_{l^{(u)}} \right) + \sum_{e=0}^m \theta_e \left( \sumj x_e^j \overline{X}_j \right) = \left[ \sum_{e=0}^m \theta_e \left( \sumu {}_ez^{(u)}_R \right) \right]G$$
-The rightmost bracketed double sum is therefore, with high probability, equal to $r = \mu_{l^{(u)}} r^{(u)}$.
+$$\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sum_{e=0}^m \theta_ex_e^m \left( \sumu \mu_{l^{(u)}} M_{l^{(u)}} \right) + \sum_{e=0}^m \theta_e \left( \sumj x_e^j \overline{X}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) G$$
+The rightmost double sum of scalars is therefore, with high probability, equal to $r = \mu_{l^{(u)}} r^{(u)}$.
+
+\textbf{OPEN QUESTION:} Does it necessarily follow that $\sum_{e=0}^m \theta_e {}_ez^{(u)}_R = \mu_{l^{(u)}} r^{(u)}$ for each $u$?
 
@@
 Unfortunately, the same technique does not appear to apply for the $Y$-check. Doing so obtains the following:
-$$\sumu \mu_{l^{(u)}} \hp(M_{l^{(u)}}) = \sum_{e=0}^m \theta_ex_e^m \left( \sumu \mu_{l^{(u)}} \hp(M_{l^{(u)}}) \right) + \sum_{e=0}^m \theta_e \left( \sumj x_e^j \overline{Y}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) J^{(u)}$$
+$$\sumu \mu_{l^{(u)}} U = \sum_{e=0}^m \theta_ex_e^m \left( \sumu \mu_{l^{(u)}} U \right) + \sum_{e=0}^m \theta_e \left( \sumj x_e^j \overline{Y}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) J^{(u)}$$
 It is unclear how to associate this with the required witness extraction.
 
-\textbf{Therefore, the special-soundness proof is incomplete!}
+\textbf{OPEN QUESTION:} Does the witness extraction from the previous open question imply that each linking tag satisfies the required relation?
 

### 2019-11-18 triptych-single/test.py
Code and tests for single-signer proving

@@ -1,0 +1,29 @@
+import triptych
+import unittest
+import dumb25519
+from dumb25519 import random_scalar, random_point, Scalar
+import random
+
+G = dumb25519.G
+H = dumb25519.hash_to_point('H')
+
+class TestValidProofs(unittest.TestCase):
+    def test_valid_prove_verify(self):
+        print ''
+
+        for m in [1,2]: # ring size 2,4
+            print 'Test parameter (m):',m
+            l = random.randrange(2**m) # spend index
+            r = random_scalar() # signing key
+            s = random_scalar() # commitment key
+
+            # Set keys and commitments
+            M = [random_point() for _ in range(2**m)] # possible signing keys
+            P = [random_point() for _ in range(2**m)] # corresponding commitments
+            M[l] = r*G
+            P[l] = s*G
+
+            # Run test
+            self.assertTrue(triptych.verify(M,P,triptych.prove(M,P,l,r,s,m),m))
+
+unittest.TextTestRunner(verbosity=2,failfast=True).run(unittest.TestLoader().loadTestsFromTestCase(TestValidProofs))

### 2019-11-18 triptych-single/triptych.py

@@ -1,0 +1,287 @@
+# Proof-of-concept implementation of https://github.com/monero-project/research-lab/issues/56
+
+from dumb25519 import hash_to_point, random_scalar, Scalar, hash_to_scalar, G, random_point, Z
+import dumb25519
+import random
+
+H = hash_to_point('H')
+U = hash_to_point('U')
+
+# Proof structure
+class Proof:
+    def __init__(self):
+        self.J = None # key images
+        self.A = None
+        self.B = None
+        self.C = None
+        self.D = None
+        self.X = None # for signing key
+        self.Y = None # for key image
+        self.Z = None # for amount
+        self.f = None
+        self.zA = None
+        self.zC = None
+        self.zR = None # for signing key and key image
+        self.zS = None # for amount
+
+    def __repr__(self):
+        temp = '<TriptychProof> '
+        temp += 'J:'+repr(self.J)+'|'
+        temp += 'A:'+repr(self.A)+'|'
+        temp += 'B:'+repr(self.B)+'|'
+        temp += 'C:'+repr(self.C)+'|'
+        temp += 'D:'+repr(self.D)+'|'
+        temp += 'X:'+repr(self.X)+'|'
+        temp += 'Y:'+repr(self.Y)+'|'
+        temp += 'Z:'+repr(self.Z)+'|'
+        temp += 'f:'+repr(self.f)+'|'
+        temp += 'zA:'+repr(self.zA)+'|'
+        temp += 'zC:'+repr(self.zC)+'|'
+        temp += 'zR:'+repr(self.zR)+'|'
+        temp += 'zS:'+repr(self.zS)
+        return temp
+
+# Pedersen matrix commitment
+def com_matrix(v,r):
+    C = dumb25519.Z
+    for i in range(len(v)):
+        for j in range(len(v[0])):
+            C += hash_to_point('Gi',i,j)*v[i][j]
+    C += r*H
+    return C
+
+# Decompose a value with given base and size
+def decompose(val,base,size,t=int):
+    r = []
+    for i in range(size-1,-1,-1):
+        slot = base**i
+        r.append(int(val/slot))
+        val -= slot*r[-1]
+    r = list(reversed(r))
+
+    # Return int list or Scalar list
+    if t == int:
+        return r
+
+    s = []
+    for i in r:
[…]

### 2019-11-20 triptych-single/triptych.py
Single-signer key aggregation

@@ -10,35 +10,33 @@ U = hash_to_point('U')
 # Proof structure
 class Proof:
     def __init__(self):
-        self.J = None # key images
+        self.J = None # key image
+        self.K = None
         self.A = None
         self.B = None
         self.C = None
         self.D = None
-        self.X = None # for signing key
+        self.X = None # for signing keys
         self.Y = None # for key image
-        self.Z = None # for amount
         self.f = None
         self.zA = None
         self.zC = None
-        self.zR = None # for signing key and key image
-        self.zS = None # for amount
+        self.z = None
 
     def __repr__(self):
         temp = '<TriptychProof> '
         temp += 'J:'+repr(self.J)+'|'
+        temp += 'K:'+repr(self.K)+'|'
         temp += 'A:'+repr(self.A)+'|'
         temp += 'B:'+repr(self.B)+'|'
         temp += 'C:'+repr(self.C)+'|'
         temp += 'D:'+repr(self.D)+'|'
         temp += 'X:'+repr(self.X)+'|'
         temp += 'Y:'+repr(self.Y)+'|'
-        temp += 'Z:'+repr(self.Z)+'|'
         temp += 'f:'+repr(self.f)+'|'
         temp += 'zA:'+repr(self.zA)+'|'
         temp += 'zC:'+repr(self.zC)+'|'
-        temp += 'zR:'+repr(self.zR)+'|'
-        temp += 'zS:'+repr(self.zS)
+        temp += 'z:'+repr(self.z)
         return temp
 
 # Pedersen matrix commitment
@@ -113,6 +111,7 @@ def prove(M,P,l,r,s,m):
 
     # Construct key image
     J = r.invert()*U
+    K = s*J
 
     # Prepare matrices and corresponding blinders
     rA = random_scalar()
@@ -162,31 +161,28 @@ def prove(M,P,l,r,s,m):
     # Generate proof values
     X = [dumb25519.Z for _ in range(m)]
     Y = [dumb25519.Z for _ in range(m)]
-    Z = [dumb25519.Z for _ in range(m)]
-    rho_R = [random_scalar() for _ in range(m)]
-    rho_S = [random_scalar() for _ in range(m)]
+    rho = [random_scalar() for _ in range(m)]
[…]

### 2020-01-03 paper/iacr.tex
Paper updates

--- 2019-06-03 paper/iacr.tex
@@
-\documentclass{article}
+\documentclass[draft]{article} % TODO: remove draft
+\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}
+\usepackage{amsmath,amssymb,amsthm,amsfonts}
+\usepackage[utf8]{inputenc}
+\usepackage{hyperref}
+\usepackage{graphicx}
 
-\usepackage{enumerate}
-\usepackage[utf8]{inputenc}
-\usepackage{authblk}
-\usepackage{amsmath,amssymb,amsthm}
-\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}
+% TODO remove
+\usepackage{lineno}
+\linenumbers
 
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
+\title{Triptych: logarithmic-sized linkable ring signatures with applications}
+\author{Sarang Noether \\ Monero Research Lab \\ \texttt{sarang.noether@protonmail.com}}
+\date{\today}
+
+\newcommand{\G}{\mathbb{G}}
+\newcommand{\F}{\mathbb{F}}
+\newcommand{\com}{\operatorname{Com}}
+\newcommand{\hs}{\mathcal{H}}
+\newcommand{\hp}{\mathbb{H}}
+
+\newcommand{\A}{\mathcal{A}}
+
+\newcommand{\sumi}{\sum_{i=0}^{n-1}}
+\newcommand{\sumj}{\sum_{j=0}^{m-1}}
+\newcommand{\sumk}{\sum_{k=0}^{N-1}}
+
+\newtheorem{theorem}{Theorem}
 \theoremstyle{definition}
-\newtheorem{remark}{Remark}[section]
-\newtheorem{example}{Example}[section]
-\newtheorem{defn}{Definition}[section]
-\newtheorem{assu}{Assumption}[section]
-
-\title{Compact linkable ring signatures and applications}
-\author[1]{Brandon Goodell}
-\author[1]{Sarang Noether}
-\author[2]{\texttt{RandomRun}}
-\affil[1]{Monero Research Lab, \texttt{\{surae,sarang\}@getmonero.org}}
-\affil[2]{Independent researcher}
-\date{}
+\newtheorem{definition}{Definition}
 
 \begin{document}
+
 \maketitle
@@
 \begin{abstract}
-We describe an efficient linkable ring signature scheme, compact linkable spontaneous anonymous group (CLSAG) signatures, for use in confidential transactions.
-Compared to the existing signature scheme used in Monero, CLSAG signatures are both smaller and more efficient to generate and verify for ring sizes of interest.
-We generalize the construction and show how it can be used to produce signatures with coins of different type in the same transaction.
+Ring signatures are a common construction used to provide signer ambiguity among a non-interactive set of public keys specified at the time of signing.
+Unlike early approaches where signature size is linear in the size of the signer anonymity set, current optimal solutions either require centralized trusted setups or produce signatures logarithmic in size.
+However, few also provide linkability, a property used to determine whether the signer of a message has signed any previous message, possibly with restrictions on the anonymity set choice.
+Here we introduce Triptych, a family of linkable ring signatures without trusted setup that is based on generalizations of zero-knowledge proofs of knowledge of commitment openings to zero.
+We demonstrate applications of Triptych in signer-ambiguous transaction protocols by extending the construction to openings of parallel commitments in independent anonymity sets.
+Signatures are logarithmic in the anonymity set size and, while verification complexity is linear, collections of proofs can be efficiently verified in batches.
+We show that for anonymity set sizes practical for use in distributed protocols, Triptych offers competitive performance with a straightforward construction.
 \end{abstract}
@@
 \section{Introduction}
-Ring signatures are used in Monero to provide transaction signer ambiguity.
-Originally, a simple Schnorr-like linkable ring signature \cite{liu2004linkable} was used that included previous one-time output public keys as possible signers.
-Later, the addition of Pedersen commitments to hide amounts necessitated a generalization to the signature \cite{noether2016ring} in order to prove transaction balance without revealing the signer.
+First introduced in \cite{rivest} with respect to RSA groups, ring signatures permit the signing of messages using public key sets not fixed in advance, without the need of a trusted group manager.
+Earlier constructions lacked such flexibility, requiring either centralized key setup or the establishment of fixed signing sets.
+Later work \cite{bender} established more robust security models for unforgeability and anonymity, capturing realistic threat models where an adversary is permitted to corrupt keys, convince honest signers to include malicious anonymity set members, or obtain signatures in advance.
 
-The current ring signature construction used in Monero, MLSAG signatures, scale linearly with the number of ring members included in the signature.
-In particular, they require the inclusion of two scalars per ring member.
+Since a ring signature has an anonymity set of public keys, one of which is the true signer, the detection of signing by the same key requires an additional property, linkability.
+A linkable ring signature \cite{lsag} enables verifiers to determine whether the (unknown) signer of a message has signed other messages.
+Such a construction was proposed for election applications, where it is necessary to ensure that votes are anonymous, but voters are permitted to vote only once on a particular issue.
+The construction in \cite{lsag}, with a hash-trapdoor structure similar to that of \cite{schnorr}, is of particular interest due to potential flexibility in linking; while its linking is limited to signer-selected but unchanging signer anonymity sets, it permits linking on a per-issue basis.
+Additional recent work in \cite{backes} introduces the property of linkable anonymity, using sets of signatures and establishing restrictions on key corruption.
+Other related interesting properties like traceability \cite{fs,f} imply stronger capabilities, where an attempt to sign two messages with the same key permits verifiers to identify the signer.
 
-We note that the MLSAG signature scheme, while general enough to permit linking across multiple sets of input keys, is in practice used as a hybrid approach to a linkable ring signature.
-Indeed, each signature input consists of two keys: the first is a standard one-time output public key, and the second is a key computed using the associated Pedersen commitments.
-Linkability is only used for the first key, to ensure that double-spending does not occur.
+Linkable ring signatures have seen particular applications in signer-ambiguous transaction protocols.
+In such an application, transactions are authorized by a ring signature whose signing anonymity set consists of previously-generated transaction outputs.
+A signature demonstrates that the signer controls the private key of one such output without revealing which is the signer, and linkability is used to assure verifiers that output has not been used in another signature (signifying a double-spend attempt).
 
-This construction is flexible.
-For example, the format can be used for usual ring confidential transactions or could be modified to describe \textit{colored ring confidential transactions} with multiple so-called coin colors, allowing users to transact with multiple assets simultaneously.
+A practical consideration for the use of linkable ring signatures in transaction protocols is how signature size and verification time scale with the size of the anonymity set.
+In common applied constructions like \cite{mlsag,clsag}, signature size and verification time scale linearly with the size of the signing ambiguity set; since such signatures are typically included in a public distributed data structure like a blockchain, there is a balance between the size of the anonymity set and the requirements for storage and verification.
+Recent protocol work in this area mitigates the size restriction.
+For example, in \cite{rct3}, the authors introduce a confidential transaction protocol based on a proving system whose size scales logarithmically with the anonymity set size, and which includes a method for demonstrating amount balance; amount commitment range proving is offloaded to other constructions like \cite{bulletproofs}.
+In \cite{omniring}, the authors use a more general proving technique to accomplish a similar goal; however, the protocol offers further size benefits by integrating commitment range proofs into the proof structure directly, taking advantage of the logarithmic proof size.
+
+Other signer-ambiguous transaction protocols not based on linkable ring signatures offer more competitive performance.
+For example, protocols like \cite{zcash} produce maximal theoretical signer ambiguity through the use of zero-knowledge Merkle proofs (among others) that offer extremely small proofs with low verification time, but at the cost of a trusted structured setup process that arises from the underlying proving system \cite{groth16}.
+Like this work, \cite{lelantus} is a transaction protocol also based on \cite{groth}; however, it is intended to operate on commitments similar to those used in \cite{zerocoin} but with the inclusion of amounts, and has limitations on addressing and sender tracing.
 
 \subsection{Our contribution}
+We produce two instantiations of a linkable ring signature, which we call Triptych.
+The constructions are a linkable generalization of Groth's one-of-many commitment-to-zero proving system \cite{groth}, with optimizations from Bootle \cite{bootle} applied for improvements to proof size and verification complexity.
+In one version of Triptych, the prover shows that it knows the opening of a commitment to zero within a commitment list, and also that it has constructed a linking tag using the same opening, enabling linkability.
+We then modify Groth's ring signature definitions to include linkability and a related property, non-frameability.
 
-In this work, we introduce a $d$-dimensional linkable ring multisignature ($d$-LRMS) scheme suitable for use in a colored ring confidential transaction scheme with $d$ colors.
-Our scheme is \textit{compact} in the sense that signature size scales with the sum of ring size and the dimension $d$; that is, increasing $d$ yields the same additional number of signature elements, regardless of the ring size.
-We prove our scheme is unforgeable up to the hardness of the $k$-one-more discrete logarithm problem.
+In the second version of Triptych, we further generalize to include a parallel list of commitments.
+Here, the prover proceeds as before to show its knowledge of an opening to a commitment in one list, as well as the construction of the linking tag.
+However, the proof also shows that the prover knows an opening of a commitment at the same position in the second commitment list.
+This construction has immediate application; in some signer-ambiguous confidential transaction protocols, transaction inputs are commitments to zero, for which the signer shows it knows the opening.
+Each commitment comes equipped with another commitment to the amount of the input; by offsetting these commitments homomorphically and carefully choosing commitment randomness, the prover can show that a particular transaction balances.
 
-We call our signature scheme $d$-dimensional compact linkable spontaneous anonymous group ($d$-CLSAG) signatures.
-We demonstrate how to use this scheme for ring confidential transactions in Monero by replacing multi-layered linkable spontaneous anonymous group (MLSAG) signatures with $d$-CLSAG signatures.
-The resulting scheme is more efficient in both signature size and verification time than current Monero transaction structures, and can be seamlessly integrated into the Monero transaction protocol.
+We show that Triptych produces signatures with competitive performance to other modern linkable ring signatures for limited anonymity set sizes.
+We note that similar constructions also require linear verification time, meaning that the size of anonymity set used in practice is likely to be limited for performance reasons.
 
-\section{Notation}
+\section{Preliminaries}
+\subsection{Public parameters}
+Let $\G$ be a cyclic group in which the discrete logarithm problem is hard, and let $\F$ be the scalar field of $\G$.
+Let $\hs: \{0,1\}^* \to \F$ be a cryptographic hash function.
+Let $G$ and $H$ be generators of $\G$ with unknown discrete logarithm relationship.
+Let $N = n^m$ be a size parameter, where $n > 1$ and $m > 1$.
+Let $\{G_{j,i}\}_{j,i=0}^{m-1,n-1}$ be a set of generators of $\G$ with unknown discrete logarithm relationship to each other, to $G$, and to $H$.
+Let $U$ be a generator of $\G$.
+Note that all generators may be produced using public randomness; for example, the use of a suitable hash function with domain separation may be appropriate.
+All such public parameters are assumed to comprise a global reference string known to all players; in particular, we exclude them from algorithm definitions and Fiat-Shamir transcript hashes for readability.
 
-In this document, we denote algorithms with typefont majuscule English letters like $\texttt{A}$, $\texttt{B}$, or $\texttt{O}$, or typefont names like $\texttt{Setup}$, $\texttt{KeyGen}$, and so on.
+\subsection{Pedersen commitment}
+Let $\com$ be a homomorphic commitment scheme that is perfectly hiding and computationally binding.
+In this work, we assume use of the Pedersen commitment scheme: for $x,r \in \F$, define $\com(x,r) \equiv xG + rH$ to be the commitment of the value $x$ with randomness $r$.
+This can be trivially extended to support matrix values; for $\{x_{j,i}\},r \in \F$, define $\com(x,r) \equiv rH + \sum_{j,i} x_{j,i}G_{j,i}$.
+Note in particular that Pedersen matrix commitments are similarly homomorphic.
 
-Group parameters are denoted as a tuple $(p, \mathbb{G}, d, G)$ where $\mathbb{G}$ is an elliptic curve group with prime order $p$, $d$ is a dimension, and $G$ is a generator of $\mathbb{G}$.
-We denote integers, bits, indices, and scalars in $\mathbb{Z}/p\mathbb{Z}$ with minuscule English letters $x, y, z, b, c, i, j, k$, etc.\ and we denote group elements with majuscule English letters, $G, X, W$, and so on.
-We use miniscule Greek letters like $\sigma$ to describe signatures and majuscule calligraphic Latin letters like $\mathfrak{T}$ when describing linkability tags.
+\subsection{Other notation}
+For integers or field elements $i,j$, the Kronecker delta function $\delta(i,j)$ evaluates to $1$ if $i=j$ and $0$ otherwise, where the output is taken to be in the appropriate set.
 
-We denote column vectors in boldface, e.g.\ $(x_1, \ldots, x_d)^\top = \textbf{x}$, and matrices in underlined boldface, e.g.\ $((x_{1,1}, x_{1,2}, \ldots, x_{1,n}), \ldots, (x_{d,1}, \ldots, x_{d,n})) = (\textbf{x}_1, \textbf{x}_2, \ldots, \textbf{x}_n) = \underline{\textbf{x}}$ is a $d\times n$ matrix.
-We denote the Hadamard product of two vectors with $\circ$, so for any $\textbf{x} = (x_1, x_2, \ldots, x_d) = (x_i)_{i=1}^{d}$, and for any $\textbf{y} = (y_i)_{i=1}^{d}$, we denote the sequence $(x_i \cdot y_i)_{i=1}^{d}$ with $\textbf{x} \circ \textbf{y}$.
-We denote bitwise concatenation with the symbol $\mid \mid$.
+We sometimes use index subscript notation of the form $i_j$ to indicate the $j$ digit of $i$, where such a decomposition of $i$ is taken base $n$ with padded length $m$:
+$$\sum_{j=0}^m i_j n^j = i$$
+This notation will be specified explicitly where confusion may occur.
 
-We distinguish oracles with calligraphic font, e.g.\ $\mathcal{CO}$ denotes a corruption oracle, $\mathcal{SO}$ denotes a signing oracle.
-If the codomain of a random oracle is the field of scalars $\mathbb{Z}/p\mathbb{Z}$, we denote this $\mathcal{H}^s$ (hash-to-scalar).
-If the codomain is $\mathbb{G}$, we denote this $\mathcal{H}^p$ (hash-to-point).
+\section{Protocol: linkable one-of-many commitment}
+We wish to build a linkable ring signature construction, where a signer who knows the opening of a commitment may sign messages using an anonymity set containing other commitments for which the signer does not know openings.
+Included with the proof of knowledge, the signer also provides a linking tag that is the image of the signing commitment's opening under a verifiable pseudorandom function, using the method of \cite{dodis} that has previously appeared in \cite{omniring,rct3}.
+Part of the soundness of the proving system relies on the proper construction of this linking tag.
+Upon receipt, a verifier can check whether the linking tag has previously appeared in any other valid proof; if it has not, injectivity assures the verifier that no other signature has been produced by the (unknown) signer.
 
-\section{Linkable ring multisignatures}
+More specifically, we modify the construction of Bootle \cite{bootle}, which itself is a generalization of a construction by Groth \cite{groth}.
+We produce a sigma protocol for the following relation:
+$$\mathcal{R}_{\text{link}} = \left\{ \{M_i\}_{i=0}^{N-1} \subset \G, J \in \G ; (l \in \mathbb{Z},r \in \F) : M_l = rG \text{ and } U = rJ \right\}$$
+Figures \ref{fig:link} and \ref{fig:link_2} describe the protocol.
 
-In this section, we recall linkable ring signature (LRS) schemes, we modify the definition to account for $d$-dimensional keys for linkable ring multisignature (LRMS) schemes, and we provide two examples.
-We emphasize that our description does not present multisignatures as computed between mutually untrusted parties.
-We use the term to mean a $d$-of-$d$ threshold multisignature with all keys controlled by the same signer; in particular, we have none of the communication steps necessary for computing a multisignature.
-
-\subsection{LRS and LRMS schemes}
-
-\begin{defn}[LRS]\label{def:lrs}
-A \textit{linkable ring signature scheme} is a tuple $(\texttt{Setup}, \texttt{KeyGen}, \texttt{Sign}, \texttt{Verify}, \texttt{Link})$ satisfying the following. 
+\begin{figure}[htbp]
+\centering
+\fbox{\begin{minipage}{0.95\textwidth}
+$\underline{\mathcal{P}_{\text{link}}(\{M_i\},J;(l,r)):}$
 \begin{itemize}
-\item $\texttt{Setup}(1^\lambda) \to \textit{par}$. $\texttt{Setup}$ takes as input a security parameter $1^\lambda$, produces some public parameters $\textit{par}$.
-
-\item $\texttt{KeyGen}(1^\lambda, \textit{par}) \to (sk, pk)$.
-$\texttt{KeyGen}$ takes as input a security parameter $1^\lambda$ and public parameters $\textit{par}$.
-$\texttt{KeyGen}$ produces as output a private-public keypair $(sk, pk)$.
-
-\item $\texttt{Sign}\left(1^\lambda, \textit{par}, (m, \textbf{pk}, sk)\right) \to \left\{\bot_{\texttt{Sign}}, (\sigma, \mathfrak{T})\right\}$.
-$\texttt{Sign}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, an arbitrary message $m \in \left\{0,1\right\}^*$, an ad hoc \textit{ring} of public keys $\textbf{pk} = \left\{pk_1, \ldots, pk_n\right\}$, and a secret key $sk$.
-$\texttt{Sign}$ produces as output either a distinguished failure symbol $\textit{out} = \bot_{\texttt{Sign}}$ or a signature-tag pair $\textit{out} = (\sigma, \mathfrak{T})$.
-
-\item $\texttt{Verify}\left(1^\lambda, \textit{par}, (m, \textbf{pk}, (\sigma, \mathfrak{T}))\right) \to \left\{0,1\right\}$.
-$\texttt{Verify}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, a message $m$, a ring of public keys $\textbf{pk}$, and a signature-tag pair $(\sigma, \mathfrak{T})$.
-$\texttt{Verify}$ produces as output a bit $b \in \left\{0,1\right\}$.
-
-\item $\texttt{Link}\left(1^\lambda, \textit{par}, (\sigma, \mathfrak{T}), (\sigma^\prime, \mathfrak{T}^\prime)\right)$.
-$\texttt{Link}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, and a pair of signature-tag pairs $(\sigma, \mathfrak{T}), (\sigma^\prime, \mathfrak{T}^\prime)$.
-$\texttt{Link}$ produces as output a bit $b \in \left\{0,1\right\}$.
-\end{itemize}
-\end{defn}
-
-We extend this to a scheme with $d$-dimensional keys.
-
-\begin{defn}[$d$-LRMS]
-A \textit{$d$-dimensional linkable ring multisignature scheme} is a tuple of algorithms $(\texttt{Setup}, \texttt{KeyGen}, \texttt{Sign}, \texttt{Verify}, \texttt{Link})$ satisfying the following. 
-\begin{itemize}
-\item $\texttt{Setup}(1^\lambda) \to \textit{par}$. $\texttt{Setup}$ works as described in \ref{def:lrs}.
-
-\item $\texttt{KeyGen}(1^\lambda, \textit{par}) \to (\textbf{sk}, \textbf{pk})$.
-$\texttt{KeyGen}$ takes as input a security parameter $1^\lambda$ and public parameters $\textit{par}$.
-$\texttt{KeyGen}$ produces as output a private-public keypair $(\textbf{sk}, \textbf{pk})$ where each key is a $d$-dimensional vector.
-We refer to the first coordinate of each of these keys as the \textit{linking key} and the $d-1$ remaining coordinates (if there are any) are the \textit{auxiliary keys}.
-
-\item $\texttt{Sign}\left(1^\lambda, \textit{par}, (m, \underline{\textbf{pk}}, \textbf{sk})\right) \to \left\{\bot_{\texttt{Sign}}, (\sigma, \mathfrak{T})\right\}$.
-$\texttt{Sign}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, a message $m$, a vector of public keys $\underline{\textbf{pk}} = \left\{\textbf{pk}_1, \ldots, \textbf{pk}_n\right\}$ where each $\textbf{pk}_i$ is a $d$-dimensional public key, and a $d$-dimensional secret key $\textbf{sk}$.
-$\texttt{Sign}$ produces as output either a distinguished failure symbol $\bot_{\texttt{Sign}}$ or a signature-tag pair $(\sigma, \mathfrak{T})$.
-
-\item $\texttt{Verify}\left(1^\lambda, \textit{par}, (m, \underline{\textbf{pk}}, (\sigma, \mathfrak{T}))\right) \rightarrow \left\{0,1\right\}$.
-$\texttt{Verify}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, a message $m$, a matrix of public keys $\underline{\textbf{pk}}$, and a signature-tag pair $(\sigma, \mathfrak{T})$.
-$\texttt{Verify}$ produces as output a bit $b \in \left\{0,1\right\}$.
-
-\item  $\texttt{Link}\left(1^\lambda, \textit{par}, (\sigma, \mathfrak{T}), (\sigma^\prime, \mathfrak{T}^\prime)\right)$. $\texttt{Link}$ works as described in \ref{def:lrs}.
-\end{itemize}
-\end{defn}
-
-We refer to the linkability tag as the \textit{key image} for consistency with terminology in Monero. We also use the following terminology if the scheme satisfies the respective properties.
-\begin{description}
-\item[Correctly verified:] For any message $m$, $d$-dimensional secret key $\textbf{sk}$ with corresponding public key $\textbf{pk}$, and appropriately-sized matrix $\underline{\textbf{pk}} = \left\{\textbf{pk}_1, \ldots, \textbf{pk}_n\right\}$, if there exists an index $1 \leq \ell \leq n$ such that $\textbf{pk} = \textbf{pk}_\ell$, then $\texttt{Verify}(\texttt{Sign}(m, \underline{\textbf{pk}}, \textbf{sk})) = 1$.
-
-\item[Correctly linkable:] For any messages $m$, $m^\prime$, any $d$-dimensional secret keys  $\textbf{sk}$ and $\textbf{sk}^\prime$ with equal linking keys (that is, with $\textbf{sk}_0 = \textbf{sk}^\prime_0$) and with corresponding public keys $\textbf{pk}$ and $\textbf{pk}^\prime$ respectively, any appropriately-sized pair of matrices $\underline{\textbf{pk}}$ and $\underline{\textbf{pk}}^\prime$, if $(\sigma, \mathfrak{T}) \leftarrow \texttt{Sign}(m, \underline{\textbf{pk}}, \textbf{sk})$ and $(\sigma^\prime, \mathfrak{T}^\prime) \leftarrow \texttt{Sign}(m^\prime, \underline{\textbf{pk}}^\prime, \textbf{sk}^\prime)$ and there exists a pair of indices $\ell$ and $\ell^\prime$ such that $\underline{\textbf{pk}}_\ell = \textbf{pk}$ and $\underline{\textbf{pk}}_{\ell^\prime} = \textbf{pk}^\prime$, then
-$\texttt{Link}((\sigma, \mathfrak{T}), (\sigma^\prime, \mathfrak{T}^\prime))=1$.
-\end{description}
-
-Note that linkability is only considered with respect to a single component of a matrix entry.
-When applied to Monero, this is important since only one such entry corresponds to an output public key for double-spend detection purposes.
-
-%In the sequel, we omit $1^\lambda$ and $\textit{par}$ from the input of algorithms for clarity unless there is risk of confusion.
-
-\subsection{Examples}
-
-\begin{example}\label{ex:lsag}
-The LSAG signature scheme from \cite{liu2004linkable} is a $1$-LRMS.
-In this example, $\texttt{Setup}$ always deterministically sets $d:=1$ (so we only use the linking key and there are no auxiliary keys).
-$\texttt{Setup}$ selects some $G \in \mathbb{G}$ to be a group generator for the group parameters $(p, \mathbb{G}, 1, G)$, two cryptographic hash functions $\mathcal{H}^s:\left\{0,1\right\}^* \to \mathbb{Z}/p\mathbb{Z}$ and $\mathcal{H}^p:\left\{0,1\right\}^* \to \mathbb{G}$.
-$\texttt{Setup}$ outputs $\textit{par} = (p, \mathbb{G}, 1, G, \mathcal{H}^s, \mathcal{H}^p)$.
-
-$\texttt{KeyGen}$ produces as output a private key $x \in \mathbb{Z}/p\mathbb{Z}$ and a public key $X = xG$.
-$\texttt{Sign}$ takes as input a private key $y \in \mathbb{Z}/p\mathbb{Z}$, a message $m$, and a ring $\textbf{X} = \left\{X_1, \ldots, X_n\right\}$, and produces as output either a distinguished failure symbol $\bot_{\texttt{Sign}}$ or a signature-tag pair $(\sigma, \mathfrak{T})$.
-
-The signature scheme originally described in \cite{liu2004linkable} signs a message $m$ with a ring of keys $\textbf{X} = \left\{X_1, \ldots, X_n\right\}$ and a secret key $x$ corresponding to some $X_\ell$, using the linkability tag (key image) $\mathfrak{T} := x \mathcal{H}^p(\textbf{X})$.
-Unfortunately, this key image is unsuitable for use in Monero, as changing ring members will change the key image.
-This would allow the same key to be used twice in two different ring signatures.
-For use in Monero, we modify this key image to be independent of the non-signing ring members, $\mathfrak{T} := x \mathcal{H}^p(X_\ell)$.
-This allows these key images to be used for double-spend protection.
-
-An LSAG signature on a message $m$ with ring $\textbf{X}$ using these key images is computed in the following way.
-First, the signer samples $\alpha, s_{\ell+1}, s_{\ell+2}, \ldots, s_{\ell-1} \in \mathbb{Z}/p\mathbb{Z}$ at random.
-Next, the signer computes basepoints $H_i = \mathcal{H}^p(X_i)$.
-Next, the signer computes $c_{\ell+1}  = \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid \alpha G \mid \mid \alpha H_\ell)$ and the signer computes each $c_{i+1} = \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid s_i G + c_i X_i \mid \mid s_i H_i + c_i \mathfrak{T})$ for $i = \ell+1, \ldots, \ell-1$, naturally identifying index $1$ with index $n+1$.
-The signer finishes by computing $s_\ell = \alpha - c_\ell x_\ell$ and publishing the signature-tag pair $(\sigma, \mathfrak{T})$ where $\sigma = (c_1, s_1, \ldots, s_n)$.
-
-A purported LSAG signature-tag pair on a message $m$ with ring $\textbf{X}$ is verified in the following way.
-The verifier sets $c_1^\prime = c_1$ and computes $c_{i+1}^\prime = \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid s_i G + c_i^\prime X_i \mid \mid s_i H_i + c_i^\prime \mathfrak{T})$ for $i=1, 2, \ldots, n$.
-The verifier outputs $1$ when $c_{n+1}^\prime = c_1$ and $0$ otherwise.
-Note that all verifiers must list the keys in $\textbf{X}$ in an agreed-upon order for the above verification to work; either they should agree upon lexicographic or some other ordering.
-LSAG signature-tag pairs are linked merely by comparing key images: two valid signatures with the same key image were signed with the same secret key (and, in the case of Monero, would signal an attempt to double-spend funds).
-\end{example}
-
-\begin{remark}
-The key image modification in Example \ref{ex:lsag} is due to the basepoint of the key image $\mathfrak{T}$.
-As noted in \cite{liu2004linkable}, easy variations on key image formats are available.
-How or whether the security properties of LSAG signatures are retained in practical use given more flexible key image formats, while interesting, is beyond the scope of this work.
-\end{remark}
-
-\begin{example}\label{ex:mlsag}
-The MLSAG signature scheme from \cite{noether2016ring} is a $2$-LRMS.
-In this example, $\texttt{Setup}$ always deterministically sets $d := 2$.
-Public keys are taken to be pairs of group elements $(X, Z) \in \mathbb{G}^2$.
-$\texttt{Sign}$ takes as input a private key vector $(x,z)$, a message $m$, and a matrix of public keys $\underline{\textbf{pk}} = \left\{\textbf{pk}_1, \ldots, \textbf{pk}_n\right\}$ where each $\textbf{pk}_i = (X_i, Z_i)$, each $X_i$ is the public key of a one-time transaction output, and each $Z_i$ is computed using combinations of Pedersen commitments that depend on the particular transaction type in use.
-%The commitments that form $Z_i$ can be adversarially selected and are not used in linking, and the secret key for $X_i$ can only be computed by the recipient except with negligible probability.
-
-A signature-tag pair $(\sigma, \mathfrak{T})$ is computed in the following way.
-Two rows of random signature data are sampled, say  $\alpha, \alpha^\prime, s_{\ell + 1}, s^\prime_{\ell + 1}, s_{\ell + 2}, s^\prime_{\ell + 2}, \ldots, s_{\ell -1}, s^\prime_{\ell - 1}$  and the basepoints $H_i = \mathcal{H}^p(X_i)$ are computed from the signing keys $X_i$ of each ring member $(X_i, Z_i)$.
-The key image $\mathfrak{T} = x_\ell H_\ell$ is computed.
-The following  challenges are computed
-\begin{align*}
-c_{\ell + 1} =& \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid \alpha G \mid \mid \alpha H_\ell \mid \mid \alpha^\prime G^\prime) \\
-c_{i+1} =& \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid s_i G + c_i X_i \mid \mid s_i H_i + c_i \mathfrak{T} \mid \mid s_i^\prime G^\prime + c_i Z_i).
-\end{align*}The values $s_\ell = \alpha - c_\ell x_\ell$ and $s_\ell^\prime = \alpha^\prime - c_\ell z_\ell$ are computed.
-The signature is set $\sigma := (c_1, s_1, s_1^\prime, \ldots, s_n, s_n^\prime)$ and the signature-tag pair is published $(\sigma, \mathfrak{T})$.
-Verification proceeds as one would expect, succeeding if $c_{n+1}^\prime = c_1$ after the verifier computes each $H_i$ and each challenge
-\begin{align*}
-c_{2}^\prime =&  \mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid s_1 G + c_1 X_1 \mid \mid s_1 H_1 + c_1 \mathfrak{T} \mid \mid s_1^\prime G^\prime + c_1 Z_1) \\
-c_{i+1}^\prime =&  \mathcal{H}^s\left(\textbf{X} \mid \mid m \mid \mid s_i G + c_i^\prime X_i \mid \mid s_i H_i + c_i^\prime \mathfrak{T} \mid \mid s_i^\prime G^\prime + c_i^\prime Z_i \right).
-\end{align*} 
-Note this scheme is not compact in the sense that doubling key dimension going from $d=2$ in Example \ref{ex:lsag} to $d=2$ results in an asymptotic doubling of signature size. 
-\end{example}
-
-\section{A compact d-LRMS scheme}
-
-We present a multisignature variant of LSAG signatures that is more compact than the previous examples.
-We loosely say that a $d$-LRMS scheme is compact if its signature sizes are not proportional to $d$.
-We call this scheme $d$-CLSAG to be concise.
-We show how to apply a $2$-CLSAG for use in ring confidential transactions, and how to apply $d$-CLSAG for colored ring confidential transactions.
-We make remarks on efficiency for both applications.
-In particular, we show that our $2$-CLSAG construction is more efficient in both space and verification time than the equivalent MLSAG construction.
-
-\subsection{Implementation}\label{sec:implem}
-
-\begin{defn}[$d$-CLSAG]\label{def:clsag}
-The following tuple $(\texttt{Setup}, \texttt{KeyGen}, \texttt{Sign}, \texttt{Verify}, \texttt{Link})$ is a compact $d$-LRMS.
-
-\begin{itemize}
-\item $\texttt{Setup}(1^\lambda, d) \to \textit{par}$.
-$\texttt{Setup}$ takes as input a security parameter $1^\lambda$ and a public dimension $d$.
-$\texttt{Setup}$ selects a prime $p$, a group $\mathbb{G}$ with prime order $p$, selects a group generator $G \in \mathbb{G}$ uniformly at random, selects $d$ cryptographic hash functions $\mathcal{H}^s_0, \ldots, \mathcal{H}^s_{d-1}$ with codomain $\mathbb{Z}/p\mathbb{Z}$, selects a cryptographic hash function $\mathcal{H}^p$ with codomain $\mathbb{G}$.
-$\texttt{Setup}$ outputs $\textit{par} = \left( p,\mathbb{G}, d, G, \left\{\mathcal{H}^s_j\right\}_{j=0}^{d-1}, \mathcal{H}^p\right)$.\footnote{Note that domain separation can be used here to take one $\mathcal{H}^s$ and construct each $\mathcal{H}^s_j$ by defining $\mathcal{H}^s_j(x) := \mathcal{H}^s(j \mid\mid x)$.}
-
-\item $\texttt{KeyGen}(1^\lambda, \textit{par}) \to (\textbf{sk}, \textbf{pk})$.
-$\texttt{KeyGen}$ takes as input the security parameter $1^\lambda$, public parameters $\textit{par}$.
-$\texttt{KeyGen}$ samples $\textbf{sk} \leftarrow (\mathbb{Z}/p\mathbb{Z})^d$, which we denote $\textbf{sk} = (x, z_1, \ldots, z_{d-1})$, and computes $\textbf{pk} := \textbf{sk} \circ \textbf{G}$ for $\textbf{G} = (G, G, \ldots, G) \in \mathbb{G}^d$.
-$\texttt{KeyGen}$ outputs $(\textbf{sk}, \textbf{pk})$.
-We say $x$ is the \textit{linking key} and the remaining keys $\left\{z_j\right\}$ are the \textit{auxiliary keys}.
-
-\item $\texttt{Sign}\left(1^\lambda, \textit{par}, (m, \underline{\textbf{pk}}, \textbf{sk})\right) \to \left\{\bot_{\texttt{Sign}}, (\sigma, \mathfrak{T})\right\}$.
-$\texttt{Sign}$ takes as input the security parameter $1^\lambda$, public parameters $\textit{par}$, a message $m \in \left\{0,1\right\}^*$, a matrix of public keys $\underline{\textbf{pk}} = (\textbf{pk}_1, \ldots, \textbf{pk}_n)$ where each $\textbf{pk}_i = (X_i, Z_{i,1}, \ldots, Z_{i,d-1}) \in \mathbb{G}^d$, and a secret key vector $\textbf{sk} = (x,z_1, \ldots, z_{d-1}) \in (\mathbb{Z}/p\mathbb{Z})^d$.
-$\texttt{Sign}$ does the following.
-
-\begin{enumerate}
-\item $\texttt{Sign}$ looks for the signing index $\ell$ such that $(x, z_1, \ldots, z_{d-1}) \circ (G, G, \ldots, G) = \textbf{pk}_\ell$.
-If no such index exists, $\texttt{Sign}$ outputs $\bot_{\texttt{Sign}}$ and terminates.
-
-\item Otherwise, $\texttt{Sign}$ samples $\alpha \in \mathbb{Z}/p\mathbb{Z}$ and $\left\{s_i\right\}_{i \neq \ell} \in (\mathbb{Z}/p\mathbb{Z})^{n-1}$.
-
-\item $\texttt{Sign}$ computes the \textit{aggregation coefficients} $\mu_X$ and $\{\mu_j\}_{j=1}^{d-1}$, the \textit{linkability tag} or \textit{key image} $\mathfrak{T}$, and auxiliary key images $\{\mathfrak{D}_j\}_{j=1}^{d-1}$:
-\begin{align*}
-\mathfrak{T} \leftarrow& x \mathcal{H}^p(X_\ell) & \mu_X \leftarrow& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}) \\
-\{\mathfrak{D}_j\} \leftarrow&  \{z_j \mathcal{H}^p(X_\ell)\} & \mu_j \leftarrow& \mathcal{H}^s_1(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}).
-\end{align*}
-
-\item For $i = \ell, \ell+1, \ldots, \ell-1$, identifying index $n$ with index $1$ as usual, $\texttt{Sign}$ computes
-\begin{align*}
-L_\ell =& \alpha G & L_i =& s_i G + c_i \left(\mu_X X_i + \sum_{j=1}^{d-1} \mu_jZ_{i,j}\right)\\
-R_\ell =& \alpha \mathcal{H}^p(X_\ell) & R_i =& s_i \mathcal{H}^p(X_i) + c_i \left(\mu_X \mathfrak{T} + \sum_{j=1}^{d-1} \mu_j \mathfrak{D}_j\right) \\
-c_{\ell+1} =& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid m \mid \mid L_\ell \mid \mid R_\ell) & c_{i+1} =& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid m \mid \mid L_i \mid \mid R_i)
-\end{align*} and lastly computes $s_\ell = \alpha - c_\ell (\mu_X x_\ell + \sum_{j=1}^{d-1} \mu_jz_{\ell,j})$.
-
-\item $\texttt{Sign}$ sets the signature $\sigma = (c_1, s_1, \ldots, s_n, \{\mathfrak{D}_j\}_{j=1}^{d-1})$ and publishes the signature-tag pair $(\sigma, \mathfrak{T})$.
-\end{enumerate}
-
-\item $\texttt{Verify}\left(1^\lambda, \textit{par}, m, \underline{\textbf{pk}}, (\sigma, \mathfrak{T})\right) \to \left\{0,1\right\}$.
-$\texttt{Verify}$ takes as input the security parameter $1^\lambda$, public parameters $\textit{par}$, a message $m$, a matrix $\underline{\textbf{pk}} = ((X_i, Z_{i,1}, \ldots, Z_{i,d-1}))_{i=1}^{n}$, and a signature-tag pair $(\sigma, \mathfrak{T})$.
-$\texttt{Verify}$ does the follwoing.
-
-\begin{enumerate}
-\item If $n > N$, or any coordinate of any ring member is not in $\mathbb{G}$, or if $\sigma$ cannot be parsed as $(c_1, s_1, \ldots, s_n, \mathfrak{D}_1, \ldots, \mathfrak{D}_{d-1})$ for some $c_1 \in \mathbb{Z}/p\mathbb{Z}$, some $s_i \in \mathbb{Z}/p\mathbb{Z}$, and some $\mathfrak{D}_j \in \mathbb{G}$, or if $\mathfrak{T} \notin \mathbb{G}$, $\texttt{Verify}$ produces $0$ as output and terminates.
-
-\item Otherwise, $\texttt{Verify}$ parses $(c_1, s_1, \ldots, s_n, \{\mathfrak{D}_j\}_{j=1}^{d-1}) \leftarrow \sigma$, computes each $\mathcal{H}^p(X_i)$, and compute the aggregation coefficients as above.
-
-\item $\texttt{Verify}$ sets $c_1^\prime := c_1$ and, for $i=1, 2, \ldots, n-1$, computes the following.
-\begin{align*}
-L_i :=& s_i G + c_i^\prime \left(\mu_X X_i + \sum_{j=1}^{d-1} \mu_jZ_{i,j}\right) \\ 
-R_i :=& s_i \mathcal{H}^p(X_i) + c_i^\prime\left(\mu_X \mathfrak{T} + \sum_{j=1}^{d-1} \mu_j \mathfrak{D}_j\right)\\
-c_{i+1}^\prime :=& \mathcal{H}^s_0\left(\underline{\textbf{pk}} \mid \mid m \mid \mid L_i \mid \mid R_i\right)
-\end{align*}
-\item If $c_{n+1}^\prime = c_1$, $\texttt{Verify}$ produces $1$ as output. Otherwise, $\texttt{Verify}$ produces $0$ as output.
-\end{enumerate}
-
-\item $\texttt{Link}\left(1^\lambda, \textit{par}, (\sigma_1, \mathfrak{T}_1), (\sigma_2, \mathfrak{T}_2)\right) \to \left\{0,1\right\}$.
-$\texttt{Link}$ takes as input the security parameter $1^\lambda$, public parameters $\textit{par}$, and two signature-tag pairs $((\sigma_1, \mathfrak{T}_1), (\sigma_2, \mathfrak{T}_2))$.
-If $\mathfrak{T}_1 \in \mathbb{G}$ and $\mathfrak{T}_2 \in \mathbb{G}$ and $\mathfrak{T}_1 = \mathfrak{T}_2$, $\texttt{Link}$ produces $1$ as output.
-Otherwise, $\texttt{Link}$ produces $0$ as output.
+\item Select random $r_A \in \F$ and $\left\{a_{j,i}\right\}_{i=1,j=0}^{n-1,m-1} \subset \F$.
+Define $A \equiv \com(a,r_A)$.
+\item Define $\left\{\sigma_{j,i}\right\}_{i,j=0}^{n-1,j-1} \subset \F$ such that $\sigma_{j,i} \equiv \delta\left(l_j,i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
+Define $B \equiv \com(\sigma,r_B)$.
+\item Select random $r_C \in \F$, and define $C \equiv \com(a(1-2\sigma), r_C)$.
+\item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
+\item Define coefficients $\left\{p_{k,j}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p_k(x) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}x + a_{j,k} \right) = \delta\left(l,k\right)x^m + \sumj p_{k,j}x^j$$ for all $k \in [0,N)$ (using our decomposition notation).
+\item Select random $\left\{\rho_j\right\}_{j=0}^{m-1} \subset \F$.
+\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}M_k + \rho_jG$$
+\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv U \sumk p_{k,j}+ \rho_jJ$$
 \end{itemize}
 
-\end{defn}
+$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
+$A,B,C,D,\{X_j\},\{Y_j\}$ \\
 
-We use the usual definition of correct verification and correct linkability, both of which are straightforward to verify directly from the implementation.
-Later, we discuss the security of this implementation.
+$\underline{\mathcal{V} \to \mathcal{P}:}$ \\
+$\xi \in \{0,1\}^*$ \\
 
-\begin{remark}
-It may be possible to compress signatures further by  computing the coefficients $\mu_j$ without the inputs $\mathfrak{D}_j$ and publishing $\sigma = (c_1, s_1, \ldots, s_n, \sum_j \mu_j \mathfrak{D}_j)$ only, reducing signature sizes for $d > 1$ further.
-
-The security of this variant is not proven here and is a good avenue for future work. The variant is not relevant for Monero, since $d=1$ for single-asset ring confidential transactions.
-\end{remark}
-
-\begin{remark}
-
-Note that the signature is computed with the aggregated secret $w = \mu_X x_\ell + \sum_j \mu_j z_{\ell,j}$. This method of aggregating keys has two properties of importance.
-
-First, under the random oracle model, the map defined by mapping $(x, z_1, \ldots, z_{d-1}) \mapsto w$ is collision resistant and anyone with knowledge of $(x_\ell, z_{\ell,1}, \ldots, z_{\ell,d-1})$ can compute the aggregated secret key $w$.
-More than one choice of $(x_\ell, z_{\ell,1}, \ldots, z_{\ell,d-1})$ could map to the same aggregated key, but collision resistance implies second pre-image resistance.
-Hence, given some $W = wG$ for an unknown aggregated secret key $w$ aggregated from some secret key $(x_\ell, z_{\ell,1}, \ldots, z_{\ell,d-1})$, an attacker has at most a negligible chance of finding a second secret key $(x_\ell^\prime, z_{\ell,1}^\prime, \ldots, z_{\ell,d-1}^\prime)$ that aggregates to the same secret $w$.
-This prevents the attacker from using an adversarially generated secret key that coincidentally aggregates to the same $w$ as some challenge key.
-
-Second, under the random oracle model, the map is resistant to key cancellation.
-That is to say, an attacker has at most a negligible chance of selecting a secret key $(x_\ell, z_{\ell, 1}, \ldots, z_{\ell, d-1})$ with coordinates that cancel in the sum $w$; except with negligible probability, $w$ is dependent upon all bits of all coordinates of a secret key $(x, z_1, \ldots, z_{d-1})$.
-
-\end{remark}
-
-\subsection{Efficiency}
-
-Consider the space and time efficiency of Definition \ref{def:clsag}.
-A $d$-CLSAG signature with a ring size of $n$ contains $n+1$ scalars and $d$ group elements, so this scheme is compact.
-In practice, signatures are broadcast with additional information such as references to the ring members.
-However, this is outside the scope of our definitions.
-
-To examine the verification time complexity, let $k_s$ and $k_p$ be the time complexity of evaluating the hash-to-scalar functions $\mathcal{H}^s$ and of evaluating the hash-to-point function $\mathcal{H}^p$, respectively.
-Let $k^{(i)}$ be the time complexity to evaluate a scalar-point linear combination of $i$ terms; using specialized algorithms like Straus or Pippenger multiexponentiation (or others, based on $i$), such a linear combination can be evaluated much more quickly than a simple term-by-term computation.
-We note that it is also possible to cache multiples of points that are reused within verification for faster linear combination evaluation, but we do not differentiate this here.
-Using these, the time complexity of $d$-CLSAG verification is $(n+d)k_s + nk_p + 2nk^{(d+1)}$.
-
-To compare to the current MLSAG scheme in Monero, note that $2$-CLSAG has equivalent functionality. The current Monero implementation requires $2n+1$ scalars and $1$ group element.
-
-To determine the feasibility of implementation in Monero, we produced a test implementation using the Monero codebase and tested signing and verification for MLSAG and $2$-CLSAG on a 2.1 GHz Opteron processor.
-Table \ref{table:timing} shows the results for different ring sizes.
-In particular, we note that for ring sizes of interest to Monero (the current network-enforced size is $11$), CLSAG is uniformly faster than MLSAG.
-However, at very large ring sizes, MLSAG is faster due to additional computations involved in computing aggregation coefficients and key prefixing.
-
-\begin{table}[htp]
-\begin{center}
-\begin{tabular}{r|ll|ll}
-& \multicolumn{2}{c|}{Verify} & \multicolumn{2}{c}{Sign} \\
-\hline
-Ring size & MLSAG & CLSAG & MLSAG & CLSAG \\
-\hline
-2 & 2.4 & 2.0 & 2.3 & 2.7 \\
-4 & 4.7 & 4.0 & 4.6 & 4.6 \\
-8 & 9.5 & 7.8 & 9.4 & 8.5 \\
-16 & 18.9 & 15.9 & 18.9 & 16.5 \\
-32 & 37.8 & 32.3 & 37.8 & 33.0 \\
-64 & 75.4 & 67.5 & 75.9 & 68.3 \\
-128 & 150 & 147 & 151 & 148 \\
-256 & 301 & 344 & 303 & 346
-\end{tabular}
-\end{center}
-\caption{Signing and verification times (ms) for MLSAG and $2$-CLSAG}
-\label{table:timing}
-\end{table}
-
-\section{Applications}
-
-\subsection{Single-asset ring confidential transactions}\label{sec:ringct}
-
-As mentioned above, it is possible to use $2$-CLSAG as a replacement for MLSAG signatures in Monero for equivalent functionality.
-Currently, Monero uses MLSAG signatures for two different transaction types: full and simple.
-
-Full transactions are only used when spending a single input.
-They leverage the fact that in a balanced transaction, the difference between input and output commitments is a commitment to zero; the signer can therefore use such differences as the second component of key vectors in the signature and sign using the known secret key at the signing index.
-
-Simple transactions are used when spending multiple inputs.
-Each spent input requires a separate signature, as a naive extension of full transactions presents an index linking issue.
-The signer first generates auxiliary commitments for each spent input using the same value but a different blinder.
-This means it is possible to use the difference between input and auxiliary commitments as a commitment to zero for the purpose of signing.
-By choosing all blinders at random except one, the signer can construct the auxiliary commitments such that the difference between auxiliary and output commitments is zero, proving balance.
-
-Both transaction types can be used with $2$-CLSAG, since linkability is not considered for the second key component used in the transaction protocols.
-
-\subsection{Multi-asset ring confidential transactions (MARCTs)}
-
-It is possible to use a straightforward $d$-CLSAG construction to accommodate transactions spending $d-1$ \textit{types} or \textit{colors} of assets separately within the same transaction and signature.
-To do so, Monero outputs are extended to have a separate commitment to each asset type value.
-When spending an output, either a full or simple transaction (discussed above) is used; we simply copy the method used to compute commitment public keys in the signature to additional dimensions of the $d$-CLSAG signature, using only the commitments for a particular asset type in each.
-This separation ensures that the transaction balances in each asset type separately, while taking advantage of the scaling benefits of $d$-CLSAG compared to the equivalent MLSAG signature construction.
-
-\subsubsection{Informal description of MARCT implementation}\label{ex:dualasset}
-
-In this section, we leverage $\Pi_C^{(d)}$ for use in ring confidential transactions on $d-1$ different assets (or colors) with a pegged exchange rate between colors.
-We analyze the cost (in terms of weight and sync time) to the blockchain of our proposal compared to a similar proposal using $d$-MLSAG signatures.
-We present only the case $d=3$ in this section to represent two colors, leaving extensions for future work.
-
-Consider the canonical example of colored currency with a fixed peg between two colors: dollars and pennies with a $100:1$ exchange rate between them.
-Define an exchange rate by determining some constants $\gamma_C, \gamma_D$ on $\left\{1, 2, \ldots, 2^{\xi - 1}\right\}$, (in this example, $\gamma_C = 1$ and $\gamma_D = 100$).
-Let $G, G^\prime$ be public group elements with unknown discrete logarithms with respect to each other where $G$ is the output from $\texttt{Setup}$ for a $d$-CLSAG.
-Let $(\texttt{Prove}, \texttt{Ver})$ be a zero-knowledge sound range proving scheme, such as that described in \cite{bulletproofs}, and let $(\texttt{Com}, \texttt{Open})$ be a Pedersen commitment scheme such that $\texttt{Com}(r,v) = rG + v G^\prime$.
-
-For the sake of this example, we define a public trading key to be a tuple $(X, C, D, P)$ where $X, C, D \in \mathbb{G}$, $C$ and $D$ are commitments and $P$ is a batched range proof from $\texttt{Prove}$ covering the values of both $C$ and $D$.
-We define a transaction key to be a tuple $(m, \textbf{Q}, \textbf{O}, (f_C, f_D), (\sigma, \mathfrak{T}), \textit{aux})$ where $\textbf{Q}$ is a ring of $n$ public trading keys  $\textbf{Q} = \left\{(X_i, C_i, D_i, P_i)\right\}_{i=1}^{n}$, $\textbf{O}$ is a set of $n^\prime$ output public trading keys $\textbf{O} = \left\{(X_i^\prime, C_i^\prime, D_i^\prime, P_i^\prime)\right\}_{i=1}^{n^\prime}$, $f_C$ is a plaintext list of fees to be paid from $C$, $f_D$ is a plaintext list of fees to be paid from $D$, $S=(\sigma, \mathfrak{T})$ is a CLSAG signature-tag pair.
-
-We say a simple transaction key is valid if the following are satisfied:
+$\underline{\mathcal{P}(\xi):}$
 \begin{itemize}
-\item every input ring member $(X_i, C_i, D_i, P_i) \in \textbf{Q}$ has a valid range proof $P_i$ so $\texttt{Ver}(P_i) = 1$; and
-\item every output range proof $P_k^\prime$ is valid so $\texttt{Ver}(P_k^\prime)=1$; and
-\item the signature-tag pair $(\sigma, \mathfrak{T})$ passes $d$-CLSAG verification $\texttt{Verify}(m, \underline{\textbf{pk}}, (\sigma, \mathfrak{T})) = 1$ for the modified ring \[\textbf{pk} = \begin{pmatrix} X_1 & X_2 & \cdots & X_n \\ Z_1 & Z_2 & \cdots & Z_n\end{pmatrix}\] where each $Z_i = \gamma_C (C_i - f_C G^\prime - \sum_k C_k^\prime) + \gamma_D ( D_i - f_D G^\prime - \sum_k D_k^\prime)$.
+\item Define $\left\{f_{j,i}\right\}_{i=1,j}^{n-1,m-1}$ such that $f_{j,i} \equiv \sigma_{j,i}\xi + a_{j,i}$.
+\item Define $z_A \equiv r_A + \xi r_B$ and $z_C \equiv \xi r_C + r_D$.
+\item Define $z \equiv r \xi^m - \sumj \rho_j \xi^j$.
 \end{itemize}
 
-As before, this CLSAG signature demonstrates knowledge of the discrete logarithm of some $x_\ell$, knowledge of the opening information for the input and output commitments, and that the opening information for the commitments balance with the fees $f_C$ and $f_D$.
-After all, when the amounts in $C_\ell$ and $D_\ell$ balance with the fees $f_C$ and $f_D$ together with the sum of the amounts in each $C_k^\prime$ and $D_k^\prime$, and when the signer knows all the openers for all these commitments, the point $\gamma_C(C_\ell - f_C G^\prime - \sum_k C_k^\prime) + \gamma_D(D_\ell - f_D G^\prime - \sum_k D_k^\prime)$ will be a usual public key with basepoint $G$ whose secret key is known by the signer.
+$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
+$\{f_{j,i}\}_{j=0,i=1}^{m-1,n-1},z_A,z_C,z$
+\end{minipage}}
+\caption{Sigma protocol for $\mathcal{R}_{\text{link}}$}
+\label{fig:link}
+\end{figure}
 
-\subsubsection{Flexible pegs, coin spectra, privacy, and further extensions}
+\begin{figure}[htbp]
+\centering
+\fbox{\begin{minipage}{0.95\textwidth}
+$\underline{\mathcal{V}_{\text{link}}(\{M_i\},J):}$
+\begin{itemize}
+\item For $0 \leq j < m$, let $f_{j,0} \equiv \xi - \sum_{i=1}^{n-1} f_{j,i}$.
+\item Accept if and only if:
+\begin{eqnarray}
+A + \xi B &=& \com(f,z_A) \label{eqn:ab} \\
+\xi C + D &=& \com(f(\xi-f),z_C) \label{eqn:cd} \\
+\sumk M_k \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG &=& 0 \label{eqn:x} \\
+U \sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ &=& 0 \label{eqn:y}
+\end{eqnarray}
+\end{itemize}
+\end{minipage}}
+\caption{Sigma protocol for $\mathcal{R}_{\text{link}}$ (continued)}
+\label{fig:link_2}
+\end{figure}
 
-The validity of a MARCT without any exchange at all between assets is also possible, allowing for assets to be segregated.
+Observe that this protocol can be made non-interactive using the Fiat-Shamir heuristic, where the verifier challenge is produced using a collision-resistant hash function (modeling a random oracle) and the proof transcript \cite{fiatshamir}.
 
-On the other hand, different exchange coefficients $\gamma_C$ and $\gamma_D$ are certainly possible.
-Just so long as there is a way for validators to come to an agreement upon exchange rate coefficients, validators can also convince themselves that transactions accordingly balance.
-Extending the model of simple ring confidential transactions with two colors to more than two colors is a straightforward exercise.
-
-Further extensions with more immediate value may be possible.
-One open question is how to modify the above scheme to mask exchange rates.
-Another open question involves formalizing flexible-peg models of full colored ring confidential transactions between many colors (a spectrum?).
-These extensions represent fundamental building blocks for a system of smart transactions that respect user privacy.
-
-\appendix
-
-\section{Security: Unforgeability}
-
-\subsection{Hardness}
-
-Unforgeability comes from the $k$-OMDL hardness assumption.
-
-\begin{defn}[k-OMDL problem]
-Let $k \in \mathbb{N}$.
-We say a PPT algorithm $\texttt{A}$ is a $(t, \epsilon)$-solver of the $k$-OMDL problem if, within time at most $t$ and with probability at least $\epsilon$, $\texttt{A}$ can succeed at the following.
-
-\begin{enumerate}
-\item The challenger uses group parameters $(p, \mathbb{G}, G)$ and picks $G_1, G_2, \ldots, G_{k}, G_{k+1} \in \mathbb{G}$ (the targets) uniformly at random from $\mathbb{G}$.
-The challenger sends the group parameters and $\left\{G_i\right\}$ to $\texttt{A}$.
-
-\item $\texttt{A}$ is granted access to a corruption oracle $\mathcal{CO}$ that takes as input some $G_i$ sent to $\texttt{A}$ and produces as output the discrete logarithm of $G_i$ with respect to $G$, i.e.\ some $x_i \in \mathbb{Z}/p\mathbb{Z}$ such that $G_i = x_i G$.
-
-\item $\texttt{A}$ produces as output a sequence of $k+1$ scalars $x_1, \ldots, x_{k+1} \in \mathbb{Z}/p\mathbb{Z}$, counting as a success if:
-\begin{enumerate}[(i)]
-\item for each $x_i$, there exists some index $1 \leq j(i) \leq k+1$ such that $G_{j(i)} = xG$ and
-\item $\texttt{A}$ made no more than $k$ queries to $\mathcal{CO}$. 
-\end{enumerate}
-\end{enumerate}
-\end{defn}
-
-\subsection{Defining forgeries}
-We use a modified version of the definition of existential forgery with insider corruption for a ring signature by Bender, Katz, and Morselli \cite{bender}.
-By using linkability tags, our definition is slightly stronger; we allow forgeries to count as successful either with partially-corrupted rings or with messages that the signing oracle has signed before, just so long as neither the signature nor the linkability tag from the forgery appear as output from any oracle query in any transcript.
-This prevents a malicious party with the ability to persuade users to sign maliciously selected messages with maliciously selected ring members from constructing ostensibly valid, previously-unseen signature-tag pairs.
-
-We use the following in the next definition.
-Let $n(-)$ be a positive polynomial.
-Let $\mathcal{H}^s:\left\{0,1\right\}^* \to \mathbb{Z}/p\mathbb{Z}$ be modeled as a random oracle.
-Let $\mathcal{CO}$ be a corruption oracle that takes as input a public key $\textbf{pk}$ and produces as output the corresponding secret key $\textbf{sk}$ and the linkability tag $\mathfrak{T}$.
-Let $C$ be the set of all keys in the transcript of queries made by $\texttt{A}$ to $\mathcal{CO}$.
-Let $T_C$ be the set of all linkability tags that appear as output from such a query.
-Let $\mathcal{SO}$ be a signing oracle that takes as input some $(m, \underline{\textbf{pk}}^\prime, \ell)$ such that $pk_\ell \in \underline{\textbf{pk}} \cap \underline{\textbf{pk}^\prime}$ and produces as output a signature-tag pair $(\sigma, \mathfrak{T})$ such that $\texttt{Verify}(m, \underline{\textbf{pk}}^\prime, \sigma, \mathfrak{T}) = 1$.
-
-\begin{defn}[Existential unforgeability of linkable ring signatures with respect to insider corruption]\label{def:unf}
-
-We say a PPT algorithm $\texttt{A}$  is a $(t, \epsilon, q_h, q_c, q_s,  n(-))$-forger of a linkable ring signature scheme if, within time at most $t$ and with at most $q_h$ oracle queries to $\mathcal{H}^s$, at most $q_c$ oracle queries to $\mathcal{CO}$, and at most $q_s$ queries to $\mathcal{SO}$, $\texttt{A}$ can succeed at the following game with probability at least $\epsilon$.
-\begin{enumerate}
-\item The challenger selects $\left\{(\textbf{sk}_i, \textbf{pk}_i)\right\}_{i=1}^{n(\lambda)} \leftarrow \texttt{KeyGen}(1^\lambda)$ and sends $\underline{\textbf{pk}} = \left\{\textbf{pk}_i\right\}_{i=1}^{n(\lambda)}$ to $\texttt{A}$.
-
-\item $\texttt{A}$ is granted access to a corruption oracle $\mathcal{CO}$, random oracle $\mathcal{H}^s$, and the signing oracle $\mathcal{SO}$.
-
-\item $\texttt{A}$ outputs a message $m$, a ring of at most $n$ public keys $\underline{\textbf{pk}}^\prime$, and a signature-tag pair $(\sigma, \mathfrak{T})$.
-This output is a success if $\underline{\textbf{pk}}^\prime \subseteq \underline{\textbf{pk}}$ and $\mathfrak{T} \notin T_C$ and $\sigma$ has not been output by $\mathcal{SO}$ and $\texttt{Verify}(m, \underline{\textbf{pk}}^\prime, \sigma, \mathfrak{T}) = 1$.
-
-\end{enumerate}
-\end{defn}
-
-These success requirements ensure that (i) any ring member whose linkability tag is $\mathfrak{T}$ has not yet had its corresponding private key corrupted by $\mathcal{CO}$; and (ii) the signature itself has not been produced by the signing oracle.
-This allows the attacker to perhaps re-use a message $m$ and linkability tag $\mathfrak{T}$ from a previous oracle query.
-If the attacker can produce a new signature $\sigma^\prime$ on a message that has been signed before by the oracle then the new signature should still count as a forgery.
-
-\subsection{The Forking Lemma} To prove that the existence of a forger implies that of a $k$-OMDL solver, we use the forking lemma.
-In the following, we presume the bit length $\eta$ is used to describe group elements in $\mathbb{G}$ and scalars in $\mathbb{Z}/p\mathbb{Z}$, i.e.\ $\eta = O(\left|p\right|)$.
-
-\begin{lemma}[General Forking Lemma]\label{lem:fork}
-Let $q, \eta \geq 1$.
-Let $\texttt{A}$ be any PPT algorithm which takes as input some $x_\texttt{A} = (x, \underline{h})$ where $\underline{h} = (h_1, \ldots, h_q)$ is a sequence of oracle query responses ($\eta$-bit strings) and returns as output $y_{\texttt{A}}$ either a distinguished failure symbol $\bot$ or a pair $(\textit{idx}, y)$ where $\text{idx} \in [q]^2$ and $y$ is some output.
-Let $\epsilon_{\texttt{A}}$ denote the probability that $\texttt{A}$ does not output $\bot_{\texttt{A}}$ (where this probability is taken over all random coins of $\texttt{A}$, the distribution of $x$, all choices $\underline{h}$).
-Let $\mathcal{F} = \mathcal{F}^{\texttt{A}}$ be the forking algorithm for $\texttt{A}$ described below.
-The accepting probability of $\mathcal{F}$ satisfies \[\epsilon_{\mathcal{F}} \geq \epsilon_{\texttt{A}} \left(\frac{\epsilon_{\texttt{A}}}{q} - \frac{1}{2^\eta}\right).\]
-\end{lemma}
-
-We refer the reader to \cite{bellare} for a proof of this lemma, which demonstrates that if executing some $\texttt{A}$ has non-negligible acceptance probability, then forking $\texttt{A}$ does as well.
-Since all queries before the $(j^*)^{th}$ query are identical in both transcripts, the input of the $(j^*)^{th}$ query is also identical.
-Since oracle queries $h_{j^*}^{\prime}, h_{j^*+1}^{\prime}, \ldots$ are newly sampled upon receiving the first output from $\texttt{A}$, the queries $h_{j^*} \neq h_{j^*}^\prime$ except with negligible probability.
-All subsequent computations in the signature that are common in both transcripts will have the same results only with negligible probability.
-
-\subsubsection{Using a forger in the Forking Lemma}
-
-Note that a forger according to Definition \ref{def:unf} is not directly compatible with the forking lemma; the output is some $y = (m, \textbf{pk}, \sigma, \mathfrak{T})$ and no $\textit{idx}$ is included.
-However, without loss of generality, we can execute $\texttt{A}$ in a black box that extracts from the transcript of $\texttt{A}$ some $\textit{idx} = (j^*, i^*)$ in the following way.
-
-For each query for any $c_{i+1}$ that appears in the successful forgery, there exists a corresponding index $j(i)$ that satisfies $c_{i+1} = h_{j(i)}$.
-The black box executing $\texttt{A}$ looks at the transcript and extracts the index pair $\textit{idx} = (i^*, j^*)$ that indicates where in the random oracle transcript we can find the very first oracle query made by $\texttt{A}$ to $\mathcal{H}^s$ for any challenge $c_{i^*+1}$ used in the successful forgery.
-If such a pair $(i^*, j^*)$ can be found, the algorithm wrapping $\texttt{A}$ can then output $(\textit{idx}, y)$ with only a negligible difference in advantage.
-
-Moreover, each $c_{i+1}$ used in the signature verification is computed by $\texttt{A}$ by querying $\mathcal{H}^s$  in the transcript of $\texttt{A}$ leading to a successful forgery.
-In particular, the challenge could not have been guessed without making the query (except with negligible success).
-Indeed, a probabilistic algorithm could flip coins to guess the hash output, but this is successful with negligible probability.
-Of course, although the index $i^*$ may not have been decided by $\texttt{A}$ when the query was made, but by the time the forgery is complete, the index $i^*$ has been assigned.
-
-Hence, without loss of generality, we can assume that $\texttt{A}$ has been appropriately wrapped so is compatible with the forking lemma without impacting its advantage.
-One algorithm $\mathcal{F}^\texttt{A}$ that works in Lemma \ref{lem:fork} works in the following way.
-
-\begin{enumerate}
-\item $\mathcal{F}$ takes as input some $x$ and $\mathcal{F}$ selects the random tape for $\texttt{A}$.
-\item $\mathcal{F}$ selects some $\underline{h} = (h_1, \ldots, h_q)$ at random by flipping coins, and $\mathcal{F}$ executes $y_\texttt{A} \leftarrow \texttt{A}(x,\underline{h})$.
-\item If $y_{\texttt{A}} = \bot_{\texttt{A}}$, then $\mathcal{F}$ outputs $\bot_{\mathcal{F}}$ and terminates.
-Otherwise, $y_{\texttt{A}} = (\textit{idx}, y)$ for some $\textit{idx}=(i^*,j^*)$ and some output $y$ and $\mathcal{F}$ selects new oracle queries $h_{j^*}^\prime, h_{j^*+1}^\prime, \ldots, h_q^\prime$, and glues the hash challenges together $\underline{h}^\prime = (h_1, \ldots, h_{j^*-1}, h_{j^*}^\prime, h_{j^*+1}^\prime, \ldots, h_q^\prime)$.
-\item If $h_{j^*} = h_{j^{*}}^\prime$, then $\mathcal{F}$ outputs $\bot_{\mathcal{F}}$ and terminates.
-Otherwise, $h_{j^*} \neq h_{j^{*}}^\prime$ and $\mathcal{F}$ executes $y_\texttt{A}^\prime \leftarrow \texttt{A}(x,\underline{h}^\prime)$.
-\item If $y_{\texttt{A}}^\prime = \bot_{\texttt{A}}$, then $\mathcal{F}$ outputs $\bot_{\mathcal{F}}$ and terminates.
-Otherwise, $y_{\texttt{A}}^\prime = (\textit{idx}^{\prime}, y^\prime)$.
-If $\textit{idx} \neq \textit{idx}^\prime$, $\mathcal{F}$ outputs $\bot_{\mathcal{F}}$ and terminates.
-Otherwise, $\mathcal{F}$ outputs $(\textit{idx}, y, \underline{h}, y^\prime, \underline{h}^\prime)$.
-\end{enumerate}
-
-We note that $\mathcal{F}^{\texttt{A}}$ executed in a black box can be fed the oracle queries $\underline{h}$ and $\underline{h}^\prime$ and so these can be assumed to be output as well without loss of generality or impacting acceptance probability.
-
-Of course, if $\texttt{A}$ runs in time at most $t$, $\mathcal{F}^{\texttt{A}}$ runs in time at most $2t+s$ where $s$ denotes the (negligible) time it takes $\mathcal{F}^{\texttt{A}}$ to select the random tape for $\texttt{A}$, select the oracle query sequences $\underline{h}$ and $\underline{h}^\prime$, and output the results.
-
-\subsection{The Oracles}
-
-Of course, any oracle queries made by $\texttt{A}$ must be handled by $\mathcal{F}^{\texttt{A}}$ somehow, and we have already described how $\mathcal{F}^{\texttt{A}}$ handles random oracle queries made by $\texttt{A}$: by flipping coins at random and keeping a hash table of the results to maintain consistency with future queries.
-The forger also has corruption oracle and signing oracle access.
-We assume that $\mathcal{F}^{\texttt{A}}$ is granted access to a corruption oracle (say, through the $k$-OMDL game challenger), so we only need to describe the signing oracle.
-
-The signing oracle access granted to $\texttt{A}$ is simulated by $\mathcal{F}^{\texttt{A}}$ through backpatching in the following way.
-$\mathcal{F}^{\texttt{A}}$ selects $c_{\ell+1}$ at random without knowing the corresponding query to $\mathcal{H}^s$.
-$\mathcal{F}^{\texttt{A}}$ uses the query results $\underline{h}$ to get each $c_{i+1}$ and stores the results in a hash table for consistency in later queries.
-$\mathcal{F}^{\texttt{A}}$ finally computes $c_\ell$, $\mathcal{F}^{\texttt{A}}$ and can compute the group points $L_\ell, R_\ell$ such that $c_{\ell+1} = \mathcal{H}^s(\underline{\textbf{pk}} \mid \mid m \mid \mid L_\ell \mid \mid R_\ell)$.
-$\mathcal{F}^{\texttt{A}}$ back-patches the hash table.
-
-\subsection{Playing k-OMDL}
-
-We now construct a master algorithm $\texttt{M}$ that plays the $k$-OMDL game for $k=2d\cdot q_c + d-1$ that operates in the following way.
-\begin{enumerate}
-
-\item $\texttt{M}$ receives group parameters $(p, \mathbb{G}, G)$ and target group elements $G_1, \ldots, G_{k+1}$ from the $k$-OMDL challenger.
-
-\item $\texttt{M}$ sets $\textbf{pk}_i := (G_{d(i-1) + 1}, G_{d(i-1) + 2}, \ldots, G_{di})$ for $i=1, \ldots, \frac{k+1}{d}$ and uses $\left\{\textbf{pk}_i\right\}_{i=1}^{\frac{k+1}{d}}$ as input for $\mathcal{F}^{\texttt{A}}$, responding to queries made by $\mathcal{F}^{\texttt{A}}$ for a key $\textbf{pk}_i$ by querying $\mathcal{CO}$ directly with each coordinate and responding with the result.
-
-\item If $\mathcal{F}^{\texttt{A}}$ outputs $\bot$, so does $\texttt{M}$ and $\texttt{M}$ terminates.
-
-\item Otherwise, $\mathcal{F}^{\texttt{A}}$ succeeds executing $\texttt{A}$ twice, each time taking no more than $q_c$ queries to corrupt $d$-dimensional keys, resulting in no more than $2\cdot d\cdot q_c$ queries to the discrete logarithm oracle $\mathcal{CO}$.
-$\mathcal{F}^{\texttt{A}}$ produces $(\textit{idx}, y_1, \underline{h}, y_2, \underline{h}^\prime)$ where $y_1 = (m_1, \textbf{pk}^{\prime}_1, \sigma_1, \mathfrak{T}_1)$ and $y_2 = (m_2, \textbf{pk}^{\prime}_2, \sigma_2, \mathfrak{T}_2)$ are forgeries using oracle queries $\underline{h}$ and $\underline{h}^\prime$, respectively, and $\textit{idx} = (i^*, j^*)$ as described previously.
-The messages and rings are identical in these forgeries because they must have been selected before the first challenge query, except with negligible probability.
-So $\texttt{M}$ can parse
-\begin{align*}
-y_1 =& (m, \underline{\textbf{pk}}^\prime, \sigma_1, \mathfrak{T}_1) & \sigma_1 =& (c_1, s_1, \ldots, s_n, \left\{\mathfrak{D}_j\right\}_j) \\
-y_2 =& (m, \underline{\textbf{pk}}^\prime, \sigma_2, \mathfrak{T}_2) & \sigma_2 =& (c_1^\prime, s_1^\prime, \ldots, s_n^\prime, \left\{\mathfrak{D}_j^\prime\right\}_j)\end{align*}
-
-\item In the transcript of $\mathcal{F}^{\texttt{A}}$, $\texttt{M}$ finds $c_{i^*+1} = h_{j^*}$ and in the second transcript $c_{i^*+1} = h^\prime_{j^*}$ for some $h_{j^*} \neq h^\prime_{j^*}$.
-In both transcripts, $c_{i^*+1}$ is the response to the query $\mathcal{H}^s(\textbf{X} \mid \mid m \mid \mid L \mid \mid R)$ for the same group elements $L, R$.
-Moreover, since this is the query for $c_{i^*+1}$ in both transcripts, the  $\texttt{M}$ finds that $L = s_{i^*} G + c_{i^*} W$ where $W = \mu_X X_{i^*} + \sum_j \mu_j Z_{i^*, j}$ in the first transcript and that $L = s_{i^*}^\prime G + c_{i^*}^\prime W$ in the second transcript, where $L$ and $W$ are common to both transcripts.
-
-\item If $\mu_X = 0$ then $\texttt{M}$ outputs $\bot$ and terminates.
-
-\item Otherwise, $\texttt{M}$ computes the discrete logarithm
-$w = \frac{s_{i^*}^\prime - s_{i^*}}{(c_{i^*} - c_{i^*}^\prime)}$ without querying $\mathcal{CO}$.
-
-\item $\texttt{M}$ makes up to $d-1$ queries to $\mathcal{CO}$ to find the discrete logarithms of the elements of any $(d-1)$-subset of $\left\{X_{i^*}, Z_{i^*, 1}, \ldots, Z_{i^*, d-1}\right\}$.
-
-\item $\texttt{M}$ uses $w$ to solve for the final discrete logarithm.
-
-\item $\texttt{M}$ outputs the $2 \cdot d \cdot q_c$ queries made by $\mathcal{F}^{\texttt{A}}$ and outputs the vector $(x_{i^*}, z_{i^*, 1}, \ldots, z_{i^*, d-1})$.
-
-\end{enumerate}
-
-Note that if $\texttt{M}$ does not terminate and output $\bot$, then $\texttt{M}$ makes up to $2\cdot d \cdot q_c$ queries to $\mathcal{CO}$ for $\mathcal{F}^{\texttt{A}}$ and makes an an additional $d-1$ queries to $\mathcal{CO}$, and yet produces as output $d \cdot (q_c + 1) > d \cdot q_c + d-1$ discrete logarithms, i.e.\ $\texttt{M}$ successfully plays the $k$-OMDL game for $k = 2\cdot d\cdot q_c + d-1$.
-Furthermore,  if $\texttt{M}$ already corrupted these discrete logarithms, even fewer queries could be made, tightening $k$ and making $\texttt{M}$ a more powerful solver.
-
-Also note that, as previously mentioned, since the map $(x, z_1, \ldots, z_{d-1}) \mapsto w$ is collision resistant, $\texttt{M}$ can skip steps and guess $w$ in step $7$ only with negligible success.
-
-We previously noted that if $\texttt{A}$ runs in time $O(t)$, $\mathcal{F}^{\texttt{A}}$ runs in time $O(2t)$.
-$\texttt{M}$ takes an additional  time $s$ due to: simulating oracle queries with coin flips and hash table modifications throughout the execution, constructing keys in step $2$,  making termination checks in steps $3$, $6$, parsing the transcripts in step $4$, retrieving $L$ and $W$ from the transcript in step $5$, computing the discrete logarithm $w$ in step $7$, computing the $d$-linear system of equations in step $9$.
-
-\subsection{Security proof}
-
-All that remains to prove the unforgeability of the $d$-CLSAG scheme from Section \ref{sec:implem} is to show that $\texttt{M}$ as described has a non-negligible acceptance probability.
+We will show that the sigma protocol is complete, sound, and zero-knowledge, the precise definitions of which are common and found in \cite{groth}.
+Informally, we require the protocol be:
+\begin{itemize}
+\item \textit{Perfectly complete}: Given knowledge of a witness to a statement in the proof relation, an honest prover can always convince an honest verifier of the validity of the witness.
+\item \textit{Special sound}: Given a statement in the proof relation, if a prover can answer multiple honest verifier challenges correctly, then it is possible to extract a witness for this statement.
+\item \textit{Special honest-verifier zero knowledge}: Given any statement and verifier challenge, it is possible to simulate a transcript that is accepted by an honest verifier without knowledge of a corresponding witness.
+\end{itemize}
 
 \begin{theorem}
-Let $d, q_h, q_c, q_s \in \mathbb{N}$  and let $(p,\mathbb{G},G)$ be some group parameters.
-If a $(t, \epsilon, q_h, q_c, q_s, n(-))$-forger of the $d$-CLSAG implementation in Section \ref{sec:implem} exists then a $(2t, \epsilon^\prime)$-solver of the $k$-OMDL problem in $\mathbb{G}$ exists for $k = d\cdot q_c + d - 1$ where $\epsilon^\prime \geq \epsilon\left(\frac{\epsilon}{q_c} - \frac{1}{2^\eta}\right) - p^{-1}$.
+The protocol in Figures \ref{fig:link} and \ref{fig:link_2} is perfectly complete, special honest-verifier zero knowledge, and $(m+1)$-special sound.
 \end{theorem}
@@
 \begin{proof}
-Let where $d, q_h, q_c, q_s$ satisfy the hypotheses and let $\texttt{A}$ be a $(t, \epsilon, q_h, q_c, q_s, n)$-forger of the $d$-CLSAG scheme of Section \ref{sec:implem}, let $\mathcal{F}^{\texttt{A}}$ be the forking algorithm for $\texttt{A}$, and let $\texttt{M}$ be the master algorithm previously described.
-$\texttt{M}$ terminates and outputs $\bot$ in steps $3$ and $6$ only; otherwise, $\texttt{M}$ succeeds at the $k$-OMDL game.
-Hence, if $E_3$ is the event that $\texttt{M}$ outputs $\bot$ in step $3$ and $E_6$ is the event that $\texttt{M}$ outptus $\bot$ in step $6$, then $E_3, E_6$ are disjoint and the acceptance probability for $\texttt{M}$ is $1 - \mathbb{P}(E_3 \cup E_6) =  1 - \mathbb{P}(E_3) - \mathbb{P}(E_6)$.
-The probability that $\texttt{M}$ outputs $\bot$ in step $6$ is the probability that the hashed coefficient $\mu_X = 0$, which occurs with probability $p^{-1}$.
-$\texttt{M}$ outputs $\bot$ in step $3$ when $\mathcal{F}^{\texttt{A}}$ produces $\bot$, but the forking lemma gives us that the acceptance probability of $\mathcal{F}^\texttt{A}$ is bounded from below by $\epsilon\left(\frac{\epsilon}{q_c} - \frac{1}{2^\eta}\right)$.
-Hence, $\texttt{M}$ succeeds with probability at least $ \left(\epsilon\left(\frac{\epsilon}{q_c} - \frac{1}{2^\eta}\right) - p^{-1}\right)$.
+The proof follows similarly to that of \cite{bootle}.
+
+% Completeness
+We first show perfect completeness.
+Suppose the verifier receives a proof generated by an honest prover.
+Equation \ref{eqn:ab} holds using the identity $$\sumi \sigma_{j,i} = 1$$ for all $0 \leq j < m$.
+Equation \ref{eqn:cd} follows similarly, using the identity $$\left(\sigma_{j,i}\right)^2 = \sigma_{j,i}$$ for all $0 \leq j < m$.
+To show Equation \ref{eqn:x} holds:
+\begin{eqnarray*}
+&& \sumk M_k \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG \\
+&=& \sumk M_k p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}M_k + \rho_jG \right) - zG \\
+&=& \sumk M_k \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \rho_jG - zG \\
+&=& \sumk M_k \xi^m \delta(l,k) - \sumj \xi^j \rho_jG - \left( r\xi^m - \sumj \rho_j\xi^j \right)G \\
+&=& \xi^mrG - \sumj \xi^j \rho_jG - \xi^mrG + \sumj \xi^j \rho_jG \\
+&=& 0
+\end{eqnarray*}
+Equation \ref{eqn:y} follows similarly:
+\begin{eqnarray*}
+&& U \sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ \\
+&=& U \sumk p_k(\xi) - \sumj \xi^j \left( U \sumk p_{k,j} + \rho_jJ \right) - zJ \\
+&=& U \sumk \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \rho_jJ - zJ \\
+&=& U \sumk \xi^m \delta(l,k) - \sumj \xi^j \rho_jJ - \left( r\xi^m - \sumj \rho_j\xi^j \right)J \\
+&=& \xi^mU - \sumj \xi^j \rho_jG - \xi^mrJ + \sumj \xi^j \rho_jG \\
+&=& 0
+\end{eqnarray*}
+since $J = r^{-1}U$ in a valid proof.
+Hence the protocol is perfectly complete.
+
+% SHVZK
+We next show that the protocol is special honest-verifier zero knowledge.
+To do so, we construct a simulator that, given a random verifier challenge $\xi$, can construct a proof transcript with identical distribution to a valid proof.
+
+First, observe that the simulator presented in the proof of Lemma 1 in \cite{bootle} translates identically to our setting.
+If the simulator chooses $B \in \G$ uniformly at random, the cited lemma assures us a valid simulation of the proof elements $A,C,D,z_A,z_C,\{f^{(u)}_{j,i \neq 0}\}$; we may compute each $f^{(u)}_{j,0}$ from this.
+Further, in a valid proof, $B$ is independent and uniformly distributed as well.
+
+The proof elements $\{X_j\}_{j=1}^{m-1}$ and $\{Y_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof since the set $\{\rho_j\}$ is random and the discrete logarithm problem in $\G$ is hard, so the simulator may choose these uniformly at random.
+The verification checks require that $X_0$ and $Y_0$ be uniquely determined by the other elements in the corresponding sets in both real proofs and by the simulator.
+
+Finally, $z$ is uniformly distributed in valid proofs given random $\xi$, so the simulator may choose it uniformly at random.
+Hence the construction is special honest verifier zero-knowledge.
+
+% Soundness
+It remains to show that the protocol is $(m+1)$-special sound, where $m > 1$.
+To show this, we construct an extractor that, given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness.
+
+Suppose that for a given statement, we have a set of $m+1$ distinct verifier challenges $\{\xi_e\}_{e=0}^m$ corresponding to unique valid responses of this form:
+$$\left\{ \{f^{(e)}_{j,i}\}, \{z_e\} \right\}_{e=0}^m$$
+From the $3$-special soundness in \cite{bootle} and $m > 1$ we have valid extractions $\{\sigma_{j,i}\}_{j,i=0}^{m-1,n-1}$ and $\{a_{j,i}\}_{j,i=0}^{m-1,n-1}$, and the Pedersen binding property ensures that (with high probability) we have:
+$$f^{(e)}_{j,i} = \sigma_{j,i}\xi_e + a_{j,i}$$
+for all $e \in [0,m]$.
+Using the extracted values, compute
+$$p_k(\xi) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}\xi + a_{j,k} \right)$$
+for all $k \in [0,N)$.
+Extraction of $\{\sigma_{j,i}\}_{j,i=0}^{m-1,n-1}$ immediately yields the signing index $l$.
+
+We have seen that $p_k$ is of degree $m$ only when $k = l$.
+Hence there exist coefficients $\{\overline{X}_j,\overline{Y}_j\}_{j=0}^{m-1}$, computed uniquely from the statement and extracted values, such that Equations \ref{eqn:x} and \ref{eqn:y} are of the following form:
+\begin{eqnarray*}
+\xi^m M_l + \sumj \xi^j\overline{X}_j &=& zG \\
+\xi^m U + \sumj \xi^j\overline{Y}_j &=& zJ \\
+\end{eqnarray*}
+
+Construct a Vandermonde matrix $V$ where the $e$ row is the vector $(1,\xi_e,\ldots,\xi^m_e)$.
+Since all $\xi_e$ are distinct, the rows of $V$ span $\F^{m+1}$; hence there exist weights $\{\theta_e\}_{e=0}^m$ such that the resulting linear combination of rows produces the vector $(0,\ldots,0,1)$.
+That is, $\sum_{e=0}^m \theta_e\xi_e^j = \delta(j,m)$.
+
+For each of the previous two equations, we can therefore build a linear combination over $e$.
+For the first:
+$$M_l = \sum_{e=0}^m \theta_e\xi_e^m M_l + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{X}_j \right) = \left( \sum_{e=0}^m \theta_e z_e \right) G$$
+Hence we extract $r \equiv \sum_{e=0}^m \theta_e z_e$.
+For the second:
+$$U = \sum_{e=0}^m \theta_e\xi_e^m U + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{X}_j \right) = \left( \sum_{e=0}^m \theta_e z_e \right) J$$
+This implies that $rJ = U$, as required.
+Hence the protocol is $(m+1)$-special sound, which completes the proof.
 \end{proof}
 
-\section{Security: Signer ambiguity}
+\section{Security: linkable ring signature}
+Informally, a linkable ring signature is a construction permitting signatures on messages using a signer-selected anonymity set (called a \textit{ring}) of possible signers.
+A valid signature convinces a verifier that the signer knows (at least) one of the private keys to a ring member.
+The construction is linkable if it is possible to determine whether two signatures were generated using the same private key, regardless of the ring members used.
 
-\subsection{Hardness}
+We use the security definitions in \cite{groth} as a starting point, directly adopting definitions for correctness and unforgeability that also appear in more recent work like \cite{backes}.
+However, we modify the definition of anonymity to account for linking tags, such that the adversary is required to differentiate between at least two possible honest signers that the adversary has not corrupted.
+To account for the linking properties desired in our construction, we use the clever linkability definition from \cite{backes}, which uses a set-theoretic approach.
+We use a straightforward definition for non-frameability, where the adversary produces a target signature on an honest key after receiving signing and corruption oracle access, and must then produce a new signature that links.
 
-We show our scheme is computationally signer-ambiguous if the following DDH game is hard in $\mathbb{G}$.
+More formally, a \textit{linkable ring signature} (LRS) construction is a set of algorithms \text{KeyGen}, \text{Sign}, \text{Verify}, and \text{Link} satisfying certain properties.
+A set of public parameters is assumed to be available to each algorithm.
+\begin{itemize}
+\item $\text{KeyGen}(r) \to (x,X)$: Generates a secret key $x$ and corresponding public key $X$, optionally using randomness $r$; if not specified, the secret key is sampled uniformly at random.
+\item $\text{Sign}(x,M,R) \to \sigma$: Generates a signature $\sigma$ on a message $M \in \{0,1\}^*$ with respect to the ring $R = \{X_1,\ldots,X_n\}$, provided that $x$ is a secret key corresponding to some $X_i \in R$ generated by $\text{KeyGen}$.
+\item $\text{Verify}(\sigma,M,R) \to \{0,1\}$: Verifies a signature $\sigma$ on a message $M$ with respect to the ring $R$.
+Outputs $0$ is the signature is rejected, and $1$ if accepted.
+\item $\text{Link}(\sigma,\sigma') \to \{0,1\}$: Determines if signatures $\sigma$ and $\sigma'$ were signed using the same private key.
+Outputs $0$ if the signatures were signed using different private keys, and $1$ if they were signed using the same private key.
+\end{itemize}
 
-\begin{defn}[Decisional Diffie-Hellman]\label{ddhgame} Let $\texttt{A}$ be any computationally unbounded PPT algorithm, $(p, \mathbb{G}, G)$ and let $n \in \mathbb{N}$.
-\begin{enumerate}
-\item The challenger selects $(r_{i,1}, r_{i,2}, r_{i,3}) \left(\mathbb{Z}/p\mathbb{Z}\right)^3$ uniformly and independently for $i=1, \ldots, n$.
-The challenger computes the public keys $R_{i,1} = r_{i,1} G$, $R_{i,2} = r_{i,2}G$, $R_{i,3}^{(0)} = r_{i,1} r_{i,2} G$, $R_{i,3}^{(1)} = r_{i,3} G$.
+We require that an LRS have the properties of correctness, anonymity, unforgeability, linkability, and non-frameability.
 
-\item The challenger selects a bit $b$ independently and uniformly from $\left\{0,1\right\}$ and sends $\left\{(R_{i,1}, R_{i,2}, R_{i,3}^{(b)})\right\}_{i=1}^{n}$ to $\texttt{A}$.
+Correctness requires that a signature generated honestly will always verify.
+\begin{definition}[Correctness]
+Consider this game between a challenger and a probabilistic polynomial-time adversary $\A$:
+\begin{itemize}
+\item The challenger runs $\text{KeyGen} \to (x,X)$ and supplies the keys to $\A$.
+\item The adversary $\A$ chooses a ring such that $X \in R$ and a message $M \in \{0,1\}^*$, and sends them to the challenger.
+\item The challenger signs the message with $\text{Sign}(x,M,R) \to \sigma$.
+\end{itemize}
+If $\text{Pr}[ \text{Verify}(\sigma,M,R) = 1 ] = 1$, we say that the LRS is \textit{perfectly correct}.
+\end{definition}
+Note that we do not require any ring members (except for $X$) to have been generated by $\text{KeyGen}$.
+However, distributed applications may in practice place additional restrictions on public keys used in anonymity sets.
+This allows for the possibility that $\A$ maliciously chooses ring members.
 
-\item $\texttt{A}$ outputs a bit $b^\prime$, succeeding if $b = b^\prime$.
-\end{enumerate}
+Unforgeability requires that an adversary who does not control the private key to a ring member cannot generate a valid signature on any message using that ring.
+\begin{definition}[Unforgeability]
+Consider this game between a challenger and a probabilistic polynomial-time adversary $\A$:
+\begin{itemize}
+\item The adversary $\A$ is granted access to a public-key oracle $\text{GenOracle}$ that (on the $i^\text{th}$ invocation) runs $\text{KeyGen} \to (x_i,X_i)$ and returns $X_i$ to $\A$.
+\item The adversary $\A$ is granted access to a corruption oracle $\text{CorruptOracle}(i)$ that returns $x_i$ if it corresponds to a query to $\text{GenOracle}$.
+\item The adversary $\A$ is granted access to a signing oracle $\text{SignOracle}(X,M,R)$ that runs $\text{Sign}(x,M,R) \to \sigma$ and returns $\sigma$ to $\A$, provided that $X$ corresponds to a query to $\text{GenOracle}$ and $X \in R$.
+\item Then, $\A$ outputs $(\sigma,M,R)$ such that $\text{SignOracle}$ was not queried with $(-,M,R)$, all keys in $R$ were generated by queries to $\text{GenOracle}$, and no key in $R$ was corrupted by $\text{CorruptOracle}$.
+\end{itemize}
+If $\text{Pr}[ \text{Verify}(\sigma,M,R) = 1 ] \approx 0$, we say that the LRS is $\textit{unforgeable with respect to insider corruption}$.
+\end{definition}
 
-Note any algorithm can flip a coin and guess correctly half the time.
-We say the \textit{advantage} of $\texttt{A}$ is the difference between the probability of success for $\texttt{A}$ and $1/2$.
-If $\texttt{A}$ can solve this with an advantage at least $\epsilon$ in time at most $t$, we say $\texttt{A}$ is a $(t,\epsilon)$-solver of the DDH problem in $\mathbb{G}$.
+Anonymity requires that as long as a ring contains at least two members that have not been corrupted, an adversary can do no better than guessing at determining the signer of an honest signature.
+\begin{definition}[Anonymity]
+Consider this game between a challenger and a probabilistic polynomial-time adversary $\A$:
+\begin{itemize}
+\item The adversary $\A$ is granted access to the public-key oracle $\text{GenOracle}$ and the corruption oracle $\text{CorruptOracle}$.
+\item The adversary $\A$ chooses a message $M \in \{0,1\}^*$, a ring $R$, and indices $i_0$ and $i_1$, and sends them to the challenger.
+We require that $X_{i_0},X_{i_1} \in R$ such that both keys were generated by queries to $\text{GenOracle}$, and neither key was queried to $\text{CorruptOracle}$.
+\item The challenger selects a uniformly random bit $b \in \{0,1\}$, generates the signature $\text{Sign}(x_{i_b},M,R) \to \sigma$, and sends it to $\A$.
+\item The adversary $\A$ chooses a bit $b' \in \{0,1\}$.
+\end{itemize}
+If $\text{Pr}[ b' = b ] \approx 1/2$ and $\A$ did not make any corruption queries after receiving the challenge bit, we say that the LRS is \textit{anonymous}.
+\end{definition}
+We observe that this definition permits the adversary to have corrupted or maliciously generated all but two keys in the ring.
+Some definitions allow the adversary to corrupt more keys, but we will see that this is inconsistent with our linkability construction, where an adversary in control of a ring member's private key can trivially determine if it was the signer by examining the linking tag associated to a signature.
 
-\end{defn}
+Linkability requires that an adversary be unable to produce $k+1$ non-linked signatures on a combined anonymity set of $k$ public keys.
+\begin{definition}[Linkability]
+Consider the following game between a challenger and a probabilistic polynomial-time adversary $\A$:
+\begin{itemize}
+\item For $i \in [0,k-1]$, the adversary $\A$ produces a public key $X_i$, message $M_i$, ring $R_i$, and signature $\sigma_i$.
+\item The adversary $\A$ produces another message M, ring R, and signature $\sigma$.
+\item All tuples $(X_i,M_i,R_i,\sigma_i)$ and $(M,R,\sigma)$ are sent to the challenger.
+\item The challenger checks the following:
+\begin{itemize}
+\item $\left| V \right| = k$, where $V \equiv \bigcup_{i=0}^{k-1} R_i$.
+\item Each $X_i \in V$.
+\item Each $R_i \subset V$.
+\item $\text{Verify}(\sigma_i,M_i,R_i) = 1$ for all $i$.
+\item $\text{Verify}(\sigma,M,R) = 1$.
+\item For all $i \neq j$, we have $\text{Link}(\sigma_i,\sigma_j) = \text{Link}(\sigma_i,\sigma) = 0$.
+\end{itemize}
+\item If all checks pass, $\A$ wins.
+\end{itemize}
+If $\A$ wins with only negligible probability for all $k$, we say the LRS is \textit{linkable}.
+\end{definition}
 
-We note that due to the random self-reducibility of the DDH game, the classic DDH game is no harder than Definition \ref{ddhgame}
-\subsection{Defining signer ambiguity}
+Non-frameability requires that an adversary be unable to generate a signature that links with an honest signature.
+\begin{definition}[Non-frameability]
+Consider also the following game between a challenger and a probabilistic polynomial-time adversary $\A$:
+\begin{itemize}
+\item The adversary $\A$ is granted access to the public-key oracle $\text{GenOracle}$.
+\item The adversary $\A$ is granted access to the corruption oracle $\text{CorruptOracle}$.
+\item The adversary $\A$ is granted access to the signing oracle $\text{SignOracle}$.
+\item The adversary $\A$ chooses a public key $X$ that was generated by a query to $\text{GenOracle}$, but was not presented as a query to $\text{CorruptOracle}$.
+It selects a message $M \in \{0,1\}^*$ and ring $R$ such that $X \in R$.
+It queries $\text{SignOracle}(X,M,R) \to \sigma$.
+\item The adversary $\A$ then produces a tuple $(M',R',\sigma')$ and sends $(M',R',\sigma')$ to the challenger, along with $(X,M,R,\sigma)$.
+\item If $\text{Verify}(\sigma',M',R') = 0$ or if $\sigma'$ was produced using a query to $\text{SignOracle}$, the challenger aborts.
+\end{itemize}
+If $\text{Pr}[ \text{Link}(\sigma,\sigma') = 1 \approx 0$, we say that the LRS is \textit{non-frameable}.
+\end{definition}
 
-\begin{defn}\label{sigambgame} We say $\texttt{A}$ is a $(t,\epsilon,n_1,n_2)$-solver of the signer ambiguity game if it can succeed with non-negligible advantage at the following game.
-\begin{enumerate}
-\item The challenger selects $n_1$ secret keys $\left\{\textbf{sk}_i\right\} \subseteq (\mathbb{Z}/p\mathbb{Z})^d$, computes the corresponding public keys $\textbf{pk}_i = \textbf{sk}_i \circ \textbf{G}$, and sends $\left\{\textbf{pk}_i\right\}$ to $\texttt{A}$.
+\section{Application: linkable ring signature}
+The constructions in \cite{groth,bootle} describe how to use a similar sigma protocol to construct a simple ring signature scheme.
+Using our modifications, we can easily extend this to account for linkability and non-frameability.
+We briefly show how to do so.
 
-\item $\texttt{A}$ outputs an arbitrary message $m$ and a ring of $n_2$ distinct members $\underline{\textbf{pk}}^\prime \subseteq \left\{\textbf{pk}_i\right\}$.
+\begin{figure}[htbp]
+\centering
+\fbox{\begin{minipage}{0.95\textwidth}
+    $\underline{\text{KeyGen}(r):}$
+    \begin{itemize}
+        \item If not specified, select $r \in \F$ uniformly at random.
+        \item Compute $R = rG$.
+        \item Return $(x,X) = (r,R)$.
+    \end{itemize}
 
-\item The challenger selects a ring index $1 \leq \ell \leq n_2$ uniformly at random, retrieves the private key $\textbf{sk}$, and sends a valid signature-tag pair $(\sigma, \mathfrak{T}) \leftarrow \texttt{Sign}(m, \underline{\textbf{pk}}^\prime, \textbf{sk})$ to $\texttt{A}$.
-\item $\texttt{A}$ outputs an index $\ell^\prime$, succeeding if $\ell = \ell^\prime$. 
-\end{enumerate}
-Note that a simulator in place of $\texttt{A}$ without any input can guess any index from $\left\{1, \ldots, n_2\right\}$ with coin flips, succeeding with probability  at least $1/n_2$.
-We define the advantage of $\texttt{A}$ as the difference in acceptance probability and $1/n_2$.
-\end{defn}
+    $\underline{\text{Sign}(x,M,R):}$
+    \begin{itemize}
+        \item Let $R = \{X_0,\ldots,X_{N-1}\}$ such that $X_l = x_lG$.
+        \item Compute $J \equiv x_l^{-1}U$.
+        \item Run $\mathcal{P}_{\text{link}}(R,J;(l,x_l)) \to a$ (up to the verifier challenge).
+        \item Set $\xi \equiv \hs(M,R,a)$.
+        \item Run $\mathcal{P}_{\text{link}}(\xi) \to z$ (after the verifier challenge).
+        \item Return $\sigma = (a,z,J)$.
+    \end{itemize}
 
-Note that if the secret index $\ell$ is leaked in the signer ambiguity game, this is equivalent to leaking information about the bit $b$ used in the DDH game.
-Also note that the game could be generalized to allow $\texttt{A}$ repeated and adaptive access to a signing oracle, just so long as so-called \textit{ring intersection} attacks are taken into account when defining the advantage of $\texttt{A}$.
-However, such a generalization is equivalent to ours.
+    $\underline{\text{Verify}(\sigma,M,R):}$
+    \begin{itemize}
+        \item Let $R = \{X_0,\ldots,X_{N-1}\}$ such that $X_l - x_lG$.
+        \item Let $\sigma = (a,z,J)$.
+        \item Set $\xi \equiv \hs (M,R,a)$.
+        \item Return $\mathcal{V}_{\text{link}}(R,J,a,z)$.
+    \end{itemize}
 
-\subsection{Security proof}
-
-If $\mathbb{G}$ satisfies the DDH hardness assumption, then the distribution of the triple $(r_1G, r_2G, r_3G)$ is computationally indistinguishable from the triple $(r_1G, r_2G, r_1r_2G)$,  where the $r_i$ are independently uniform on $\mathbb{Z}/p\mathbb{Z}$.
-If $\mathcal{H}^p: \left\{0,1\right\}^* \to \mathbb{G}$ is modeled as a random oracle with output that is independent of its input, the distribution of a tuple $(r_1G, r_2G, r_3G)$ is identical to the distribution of $(r_1G, \mathcal{H}^p(r_1G), r_3G)$ where $r_1, r_3$ are independently uniform on $\mathbb{Z}/p\mathbb{Z}$.
-Hence, under the random oracle model and assuming $\mathbb{G}$ is DDH-hard, the distribution of triples $(r_1G, \mathcal{H}^p(r_1G), r_1\mathcal{H}^p(r_1G))$ where $r_1$ is uniformly random from $\mathbb{Z}/p\mathbb{Z}$ is computationally indistinguishable from the distribution of triples $(r_1G, \mathcal{H}^p(r_1G), r_3G)$ where $r_1, r_3$ are uniformly random from $\mathbb{Z}/p\mathbb{Z}$.
-
-Now note that a solver of the signer ambiguity game is given $X_i$ and $\mathcal{H}^p(X_i)$ for each ring member and the linkability tag $\mathfrak{T} = x_\ell \mathcal{H}^p(X_\ell)$.
-The solver with a non-negligible advantage at guessing $\ell$ has a non-negligible advantage in distinguishing whether a given triple $(X_i, \mathcal{H}^p(X_i), \mathfrak{T})$ satisfies $\mathfrak{T} = x_i \mathcal{H}^p(X_i)$ or not.
+    $\underline{\text{Link}(\sigma,\sigma'):}$
+    \begin{itemize}
+        \item We implicitly assume that $\sigma$ and $\sigma'$ have been previously verified.
+        \item Let $\sigma = (a,z,J)$ and $\sigma' = (a',z',J')$.
+        \item If $J = J'$, return $1$.
+        Otherwise, return $0$.
+    \end{itemize}
+\end{minipage}}
+    \caption{Linkable ring signature using $\mathcal{R}_{\text{link}}$}
+    \label{fig:lrs}
+\end{figure}
 
 \begin{theorem}
-If a $(t, \epsilon, n_1, n_2)$-solver of the signer-ambiguity game exists, there exists a $(t, \frac{\epsilon}{2})$-solver of the DDH game. 
+The protocol in Figure \ref{fig:lrs} is a linkable ring signature construction.
 \end{theorem}
@@
 \begin{proof}
-We assume $\texttt{A}$ is an algorithm that can succeed at the game in Definition \ref{sigambgame} with non-negligible advantage.
-We construct a master algorithm $\texttt{M}$ that plays the game in Definition \ref{ddhgame} by executing $\texttt{A}$ in a black box such that $\texttt{M}$ plays the role of the challenger in Definition \ref{sigambgame}.
+Perfect correctness follows immediately from the perfect completeness of the proving system for $\mathcal{R}_{link}$.
 
-$\texttt{M}$ receives a set of DDH challenge tuples $\left\{(R_{i,1}, R_{i,2}, R_{i,3}^{(b)})\right\}_{i=1}^{n}$.
-$\texttt{M}$ keeps two internal hash tables to maintain consistency between oracle queries made to $\mathcal{H}^p$ and $\mathcal{H}^s$, and flips coins to determine hash outcomes except as specified below.
-$\texttt{M}$ sets $X_i := R_{i,1}$, backpatches the key image basepoints $\mathcal{H}^p(X_i) := R_{i,2}$, and sets the purported key images $\mathfrak{T}_i := R_{i,3}^{(b)}$.
-The algorithm selects $Z_{i,j}$ at random and sets $\textbf{pk}_i := (X_i, Z_{i,1}, \ldots, Z_{i,d-1})$.
-The algorithm $\texttt{M}$ then operates in the following way:
-\begin{enumerate}
-\item $\texttt{M}$ sends the public keys $\underline{\textbf{pk}} = \left\{\textbf{pk}_i\right\}_{i=1}^{n}$ to $\texttt{A}$.
+Similarly, anonymity follows since the proving system is special honest-verifier zero knowledge, and therefore witness indistinguishable \cite{cramer}.
+Any adversarial advantage in breaking anonymity must therefore arise from distinguishing either input commitments or linking tags in signatures.
+Since honestly-generated input Pedersen commitments are perfectly hiding, they are indistinguishable from elements of $\G$ selected uniformly at random; we assume by definition that at least two such commitments are present in such a signature.
+Further, honestly-generated linking tags are generated from a one-way pseudorandom function, and therefore in the random oracle model are independently uniformly distributed from other proof elements and input commitments.
 
-\item $\texttt{A}$ outputs a message $m$ and a ring $\underline{\textbf{pk}}^\prime$.
+The proof for unforgeability in \cite{groth} relies on the (special) soundness of the underlying sigma protocol; it applies directly to our modification for $\mathcal{R}_{link}$, and is not repeated here.
 
-\item If $\underline{\textbf{pk}}^\prime \not\subseteq \underline{\textbf{pk}}$, $\texttt{M}$ outputs $\bot$ and terminates.
-Otherwise, the algorithm $\texttt{M}$ can find a one-to-one correspondence between ring indices in $\underline{\textbf{pk}}^\prime$ and key indices in $\underline{\textbf{pk}}$, so that for each ring index $1 \leq \ell \leq n_2$ in $\underline{\textbf{pk}}^\prime$, there exists some key index $1 \leq i(\ell) \leq n_1$ in $\underline{\textbf{pk}}$ such that the ring member is $X_{i(\ell)} = R_{i(\ell),1}$, has key image basepoint $\mathcal{H}^p(X_{i(\ell)}) = R_{i(\ell),2}$, and has key image $R_{i(\ell),3}^b$.
+To show linkability, observe first that $\text{Link}$ simply compares linking tags, so two signatures link if and only if they share a common linking tag.
+Suppose an adversary can win the linkability game with non-negligible probability for some $k > 1$.
+Since all provided signatures verify, soundness implies extraction of a witness $x_i$ from signature $\sigma_i$ for all $i$, and of a witness $x$ from $\sigma$.
+Note that all $\{x_i\}$ and $x$ are distinct.
+If $x_i = x_j$ for $i \neq j$, then the corresponding linking tags $J_i$ and $J_j$ are such that $x_iJ_i = x_jJ_j = U$; then $J_i = J_j$, which contradicts $\text{Link}(\sigma_i,\sigma_j) = 0$.
+The same reasoning holds to show $x$ is similarly distinct.
+Soundness also implies that for all $i$, there exists $X_i \in R_i$ such that $x_iG = X_i$; similarly, there exists $X \in R$ such that $xG = X$.
+By assumption we have $$\{X_0,\ldots,X_{k-1},X\} \subset \left( \bigcup_{i=0}^{k-1} R_i \right) \cup R \subset V.$$
+However, note that $\left| \{X_0,\ldots,X_{k-1},X\} \right| = k+1$, but that $\left| V \right| = k$, a contradiction.
 
-\item $\texttt{M}$ simulates a signature in the following way.
-\begin{enumerate}[(a)]
-\item $\texttt{M}$ selects a random index $1 \leq \ell \leq n_2$, selects a random scalar $c_{\ell+1} \in \mathbb{Z}/p\mathbb{Z}$, and selects random scalars $s_1, s_2, \ldots, s_n \in \mathbb{Z}/p\mathbb{Z}$.
-
-\item For $i=\ell+1, \ell+2, \ldots, n-1, n, 1, 2, \ldots, \ell-1$, $\texttt{M}$ computes 
-\begin{align*}
-L_i :=& s_iG + c_i\left(\mu_X X_i + \sum_j \mu_j Z_{i,j}\right) \\
-R_i :=& s_i\mathcal{H}^p(X_i) + c_i\left(\mu_X \mathfrak{T}_{i(\ell)} + \sum_j \mu_j \mathfrak{D}_j\right)\\
-c_{i+1} :=& \mathcal{H}^s\left(\underline{\textbf{pk}}^\prime \mid \mid m \mid \mid L_i \mid \mid R_i \right)
-\end{align*}
-
-\item $\texttt{M}$ computes $c_\ell$, $L_\ell$, and $R_\ell$ as above.
-If $\mathcal{H}^s$ has been queried before with $\left(\underline{\textbf{pk}}^\prime \mid \mid m \mid \mid L_\ell \mid \mid R_\ell \right)$, $\texttt{M}$ outputs $\bot$ and terminates.
-Otherwise, $\texttt{M}$ backpatches $\mathcal{H}^s\left(\underline{\textbf{pk}}^\prime \mid \mid m \mid \mid L_\ell \mid \mid R_\ell \right) \leftarrow c_{\ell+1}$.
-
-\item $\texttt{M}$ sends to $\texttt{A}$ the signature-tag pair $\left(\sigma, \mathfrak{T}_{i(\ell)}\right)$ where $\sigma = (c_1, s_1, \ldots, s_n, \left\{\mathfrak{D}_j\right\}_j)$.
-
-\end{enumerate}
-
-\item $\texttt{A}$ outputs a signing index $\ell^\prime$.
-If $\ell = \ell^\prime$, $\texttt{M}$ outputs $b^\prime = 0$.
-Otherwise, $\texttt{M}$ flips a coin and outputs a bit $b^\prime$ selected uniformly at random.
-\end{enumerate}
-
-Note that $\texttt{M}$ only terminates and outputs $\bot$ if $\texttt{A}$ asks for a signature with a ring containing a key that is not a DDH challenge key or if $\mathcal{H}^s$ has been queried with $\left(\underline{\textbf{pk}}^\prime \mid \mid m \mid \mid L_\ell \mid \mid R_\ell \right)$ before step $4c$.
-We can assume $\texttt{A}$ never asks for a signature with a bad ring like this.
-Moreover, the points $L_\ell$ and $R_\ell$ are uniformly distributed, so the probability that any algorithm can guess the input for backpatching is negligible.
-Hence, $\texttt{M}$ carries out the game in Definition \ref{ddhgame} except with negligible probability.
-
-The law of total probability gives us that $\mathbb{P}\left[\texttt{M}\text{ wins}\right] = \frac{1}{2}\mathbb{P}\left[1 \leftarrow \texttt{M} \mid b=1\right] + \frac{1}{2}\mathbb{P}\left[0 \leftarrow \texttt{M} \mid b=0\right]$.
-Moreover, the event that $1 \leftarrow \texttt{M}$ is exactly the event that $\ell^\prime \leftarrow \texttt{A}$ and $\ell^\prime \neq \ell$, and the event that $0 \leftarrow \texttt{M}$ is exactly the event that $\ell^\prime \leftarrow \texttt{A}$ and $\ell^\prime = \ell$.
-If $b=1$, then $\texttt{M}$ received random points, not the DDH exchange key, so the signature sent to $\texttt{A}$ consists of uniformly random points and scalars.
-$\texttt{A}$ can do no better than to guess the index $\ell^\prime$ uniformly at random.
-So $\mathbb{P}\left[1 \leftarrow \texttt{M} \mid b=1\right] = \mathbb{P}\left[\ell^\prime \leftarrow \texttt{A}, \ell^\prime \neq \ell \mid b = 1\right] = \frac{n-1}{n}$.
-On the other hand, if $b = 0$, then $\texttt{M}$ received the DDH exchange key.
-In this case, $\texttt{A}$ has an advantage $\epsilon$ at guessing the successful index, so $\mathbb{P}\left[\ell^\prime \leftarrow \texttt{A}, \ell = \ell^\prime \mid b = 0\right] = \frac{1}{n} + \epsilon$.
-Hence, $\texttt{M}$ succeeds at the DDH game with probability $\frac{1}{2}\left(1-\frac{1}{n}\right) + \frac{1}{2}\left(\frac{1}{n} + \epsilon\right) = \frac{1}{2} + \frac{\epsilon}{2}$.
+Finally, we show non-frameability and assume an adversary has a non-negligible advantage in breaking this property.
+Because we have $\text{Verify}(\sigma',M',R') = 1$, soundness implies extraction of a witness $x' \in \F$ such that $x'G \in R'$; we also have a witness $x$ such that $xG \in R$ from the known signature $\sigma$.
+Since $\text{Link}(\sigma,\sigma') = 1$, the corresponding linking tags $J$ and $J'$ are equal by definition; hence by soundness $xJ = x'J' = U$, giving $x = x'$.
+However, the adversary did not query $\text{CorruptOracle}$ with $X$, meaning it breaks the discrete logarithm problem non-negligibly.
 \end{proof}
 
+\section{Protocol: parallel linkable one-of-many commitment}
+In this section, we describe a modification of the sigma protocol for $\mathcal{R}_{\text{link}}$ that permits us to prove knowledge of multiple commitments in separate sets at the same index position, while retaining the linking property in the first commitment set only.
+We later show how to apply such a construction to a signer-ambiguous transaction protocol that can demonstrate balance preservation.
+
+We wish to produce a sigma protocol for the following relation:
+$$\mathcal{R}_{\text{par}} = \left\{ \{M_i\}_{i=0}^{N-1} \subset \G, \{P_i\}_{i=0}^{N-1} \subset \G, J \in \G ; (l \in \mathbb{Z},r \in \F,s \in \F) : M_l = rG \text{ and } P_l = sG \text{ and } U = rJ \right\}$$
+This requires only minor modifications to the protocol for $\mathcal{R}_{\text{link}}$, so we document only the modified proof elements constructed and verified in Figure \ref{fig:par}.
+All other proof elements are generated and verified identically.
+
+\begin{figure}[htbp]
+\centering
+\fbox{\begin{minipage}{0.95\textwidth}
+$\underline{\mathcal{P}_{\text{par}}(\{M_i\},\{P_i\},J;(l,r,s)):}$
+\begin{itemize}
+\item Define $K \equiv sJ$.
+\item Define $\mu \equiv \hs(\{M_i\},\{P_i\},J,K)$.
+\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}(M_k + \mu P_k) + \rho_jG$$
+\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv (U + \mu K)\sumk p_{k,j} + \rho_jG$$
+\end{itemize}
+
+$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
+$K,\{X_j\},\{Y_j\}$ \\
+
+$\underline{\mathcal{V} \to \mathcal{P}:}$ \\
+$\xi \in \{0,1\}^*$ \\
+
+$\underline{\mathcal{P}(\xi):}$
+\begin{itemize}
+\item Define $z \equiv (r + \mu s)\xi^m - \sumj \rho_j\xi^j$.
+\end{itemize}
+
+$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
+$z$ \\
+
+$\underline{\mathcal{V}_{\text{par}}(\{M_i\},\{P_i\},J):}$
+\begin{itemize}
+\item Define $\mu \equiv \hs(\{M_i\},\{P_i\},J,K)$.
+\item Accept if and only if:
+\begin{eqnarray*}
+\sumk (M_k + \mu P_k) \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG &=& 0 \\
+(U + \mu K)\sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ &=& 0
+\end{eqnarray*}
+\end{itemize}
+\end{minipage}}
+\caption{Sigma protocol (abbreviated) for $\mathcal{R}_{\text{par}}$}
+\label{fig:par}
+\end{figure}
+
+\begin{theorem}
+The protocol in Figure \ref{fig:par} is perfectly complete, special honest-verifier zero knowledge, and $(m+1)$-special sound.
+\end{theorem}
+
+\begin{proof}
+In the random oracle model, extraction of a witness of the form $r + \mu s$ implies knowledge of both $r$ and $s$ such that $rG = M_l$ and $sG = P_l$, similarly to the key-aggregation arguments in \cite{musig}.
+The same extraction shows that $(r + \mu s)J = U + \mu K$, which implies in particular that $rJ = U$, as required.
+
+The rest of the proof follows with only trivial modifications from the proof for $\mathcal{R}_{\text{link}}$.
+\end{proof}
+
+\section{Application: signer-ambiguous transaction protocol}
+The parallel construction described in Figure \ref{fig:par} can be used in a signer-ambiguous transaction protocol.
+
+Suppose a user wishes to generate a transaction consuming $W$ previously-generated outputs and generating $T$ fresh outputs.
+The user shuffles the consumed outputs within a larger list of $N$ outputs $\{M_k\}_{k=0}^{N-1}$, such that there exist indices $\{l_u\}_{u=0}^{W-1}$ where each $M_{l_u} = r_u$ for some known private key $r_u$.
+Further, assume each $M_{l_u}$ comes equipped with an amount commitment of the form $P_{l_u} \equiv \com(a_u,s_u)$ for amount $a_u$ and mask $s_u$.
+(All other $M_k$ also come equipped with a corresponding $P_k$, but the structure of these points is not relevant here.)
+
+The user generates $W$ auxiliary commitments $P'_u \equiv \com(a_u,s'_u)$ to the same amounts, but with different masks $\{s'_u\}$ chosen uniformly at random from $\F$.
+Then, the user generates $W$ spend proofs, each using the following prover inputs for $u \in [0,W)$:
+$$\mathcal{P}_{par}(\{M_i\},\{P_i-P'_u\},r_u^{-1}U;(l_u,r_u,s_u-s'_u))$$
+
+For $j \in [0,T)$, the user generates a fresh output of the form $Q_j \equiv \com(b_j,t_j)$ for amount $b_j$ and mask $t_j$.
+The masks are chosen such that for $j \in [1,T)$, we have $t_j$ chosen uniformly at random from $\F$.
+We then choose $$t_0 \equiv \sum_{u=0}^{W-1} s_u' -\sum_{j=1}^{t-1} t_j$$ and include all $\{P'_u\}$ auxiliary commitments in the transaction.
+
+To verify such a transaction, the verifier first performs verification on each spend proof to ensure it is valid.
+Then, the verifier ensures that $$\sum_{u=0}^{W-1} P'_u - \sum_{j=0}^{T-1} Q_j = 0$$ such that the transaction balances.
+This succeeds since the commitments sum to zero if and only if the difference of input and output amounts is zero, which holds since the Pedersen commitment construction is computationally binding.
+
+\section{Efficiency}
+Triptych proofs scale logarithmically with the size of the input anonymity set; this is the best asymptotic scaling known for ring signatures that do not require a trusted setup process over non-pairing groups.
+Related protocols based on the inner-product compression method of \cite{bulletproofs} include Omniring \cite{omniring} and RingCT 3.0 \cite{omniring}.
+However, it is challenging to directly compare these protocols' efficiency.
+Omniring includes all transaction input signatures, output range proofs, and balance within a single proof structure; however, it is not possible to verify a batch of proofs more efficiently by combining common generators.
+While an early version of RingCT 3.0 used separate input, range, and balance proofs, the most recent version merges all input and balance proofs together but outsources the range proofs to an efficient construction like \cite{bulletproofs}; this comes at the cost of requiring that the number of inputs be a power of two or otherwise carefully padded.
+A more direct comparison is to CLSAG, a linear-sized linkable ring signature construction.
+
+We compare size and verification of parallel Triptych, the earlier version of RingCT 3.0 considering only the signature proof component, and CLSAG.
+For verification scaling, we account for the use of batching in Triptych and RingCT 3.0, where generators common to multiple proofs are used only once in verification.
+Further, since verification in both of these constructions reduces to checking whether several multiscalar multiplications are zero, we may apply random weighting such that verifying a batch of multiple proofs reduces to a single multiscalar multiplication.
+The use of efficient multiscalar multiplication algorithms like \cite{straus,pippenger} means that an $n$-multiscalar multiplication evaluates as $O(n/\log n)$.
+This form of batching does not apply to CLSAG, where verification consists of a sequence of hash function evaluations.
+
+Table \ref{table:size} compares proof/signature sizes and verification complexity for these constructions.
+Verification complexity is separated into the number of hash-to-$\F$ operations (denoted $\hs$), hash-to-$\G$ operations (denoted $\hp$), and $i$-multiscalar multiplication operations of size $k(i)$.
+Figure \ref{fig:size} examines size as a function of input anonymity size under the assumption that elements of both $\G$ and $\F$ occupy $32$ kB of space.
+We note that although RingCT 3.0 proofs are smaller for large $N$, Triptych proofs are smaller in the range $16 < N < 1024$, a reasonable range given practical verification times.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{r|ll|l}
+& Size ($\G$) & Size ($\F$) & Verification \\
+\hline
+CLSAG \cite{clsag} & $1$ & $N + 1$ & $(N + 2) \hs + N \hp + 2N k(3)$ \\
+RingCT 3.0 \cite{rct3} & $2\lg(N) + 8$ & $10$ & $k(4N + 2\lg(N) + 16)$ \\
+Triptych (this work) & $2\lg(N) + 5$ & $\lg(N) + 3$ & $k(2N + 4\lg(N) + 8)$
+\end{tabular}
+\caption{Proof sizes and verification complexity, for anonymity set size $N$}
+\label{table:size}
+\end{table}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\textwidth]{size.png}
+\caption{Proof sizes for input anonymity set size $N$}
+\label{fig:size}
+\end{figure}
+
+\section{Future work}
+It is possible to further extend the Triptych proving system to support proving knowledge of openings of multiple commitments within the \textit{same} anonymity set, while permitting the construction of linking tags for each such opening and demonstrating balance directly within a single proof.
+Such a construction is much more efficient than the present work when built into a transaction protocol, but the security definitions applying to such a construction are still under evaluation.
+
 \bibliographystyle{plain}
-\bibliography{bibliography}
+\bibliography{main}
 

### 2020-01-03 paper/multi.tex
Paper updates

--- 2019-11-18 paper/main.tex
@@
-\documentclass[draft]{article}
+\documentclass[draft]{article} % TODO: remove draft
 \usepackage[top=1.0in,bottom=1.0in,left=0.5in,right=0.5in]{geometry}
@@
 \usepackage{hyperref}
+
+% TODO remove
+\usepackage{lineno}
+\linenumbers
 
@@
 
+We now present a sigma protocol for the following relation:
+\begin{multline*}
+\left\{ \{M_k\}_{k=0}^{N-1},\{P_k\}_{k=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \right. \\
+\left. M_{l^{(u)}} = r^{(u)}G \; \forall \: u \in [0,w) \text{ and } r^{(u)}J^{(u)} = U \; \forall \: u \in [0,w) \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \right\}
+\end{multline*}
+
 \subsection{Prover}
@@
 \item each $Q_j = t_jG + b_jH$ has its amount and blinding factor known to the prover
-\item $\sum_{u=0}^{w-1} a_j - \sum_{j=0}^{T-1} b_j = 0$
+\item $\sum_{u=0}^{w-1} a_u - \sum_{j=0}^{T-1} b_j = 0$
 \end{itemize}
@@
 \item a set of corresponding amount commitments $\{P_k\}_{k=0}^{N-1}$
+\item a set of new amount commitments $\{Q_j\}_{j=0}^{T-1}$
 \item a set of linking tags $\{J^{(u)}\}_{u=0}^{w-1}$
@@
 
-%The decisional Diffie-Hellman assumption implies that the elements {Xj} and {Yj} are independent and uniformly distributed in a valid proof" should be changed to "The selection of random \rho values and the computation of each \mu_k and H(M_k) under the random oracle model imply that X, Y, and Z are statistically uniform and independent..." or something like that.
-DDH is a worse
-The decisional Diffie-Hellman assumption implies that the elements $\{X_j\}_{j=1}^{m-1}, \{Y_j\}_{j=1}^{m-1}, \{Z_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof, so the simulator may choose these randomly.
+Under the random oracle model, the elements $\{X_j\}_{j=1}^{m-1}, \{Y_j\}_{j=1}^{m-1}, \{Z_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof, so the simulator may choose these randomly.
 The verification checks require that $X_0,Y_0,Z_0$ be uniquely determined by the other elements in the corresponding sets in both real proofs and by the simulator.
@@
 To show this, we construct an extractor that, given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness.
-In particular, we produce a modified witness for the following relation that is based on the information presented in the prover algorithm:
+In particular, we produce a modified witness for the following relation that is based on the information presented in the prover algorithm, where we define aggregation coefficients $\mu_k$ as before:
 \begin{multline*}
-\left\{ \{M_k\}_{k=0}^{N-1},\{P_k\}_{k=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, r, y \right) : r = \sum_{u=0}^{w-1} \hs(l^{(u)},M,P,Q)r^{(u)} \text{ and } \right.
-\\
-\left. M_{l^{(u)}} = r_uG \; \forall \: u \in [0,w) \text{ and } r^{(u)}J^{(u)} = U \; \forall \: u \in [0,w) \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \right\}
+\left\{ \{M_k\}_{k=0}^{N-1},\{P_k\}_{k=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \right. \\
+\left.
+\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sumu \mu_{l^{(u)}} r^{(u)}G \text{ and } \sumu \mu_{l^{(u)}} r^{(u)}J^{(u)} = \sumu \mu_{l^{(u)}} U \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \right\}
 \end{multline*}
 
-% Since H is a random oracle, knowledge of r implies knowledge of {r^u} except with negligible probability
-Collision resistance of $\hs$ means that, with high probability, knowledge of $r$ is equivalent to knowledge of $\{r^{(u)}\}$.
-%  it's DL hardness on G together with the random oracle model
-The combination of the discrete logarithm problem on $\G$ and the collision-resistance of $\hp$ allows for double-spend enforcement using the linking tags $\{J^{(u)}\}$.
+Since aggregation coefficients are produced using a collision-resistant hash function modeling a random oracle and the discrete logarithm problem is assumed to be hard, the above sum requirements involving $\mu_k$ terms are sufficient to imply the desired witness requirements.
+Further, this allows for double-spend enforcement using the linking tags $\{J^{(u)}\}$.
 The binding property of Pedersen commitments ensures that, for properly constructed commitments, knowledge of $y$ implies that the sum of values of input commitments $\{P_{l^{(u)}}\}$ balances the sum of output commitments $\{Q_j\}$.
@@
 $$\left\{ \{{}_ef^{(u)}_{j,i}\}, \{{}_ez^{(u)}_R\}, {}_ez_S \right\}_{e=0}^m$$
-From the $3$-special soundness in \cite{bootle} and $m > 1$ we have valid extractions $\{\sigma^{(u)}_{j,i}\}_{u=0}^{w-1}$ and $\{a^{(u)}_{j,i}\}_{u=0}^{w-1}$, and the Pedersen binding property ensures that (with high probability) we have:
+From the $3$-special soundness in \cite{bootle} and $m > 1$ we have valid extractions $\{\sigma^{(u)}_{j,i}\}_{u=0}^{w-1}$ and $\{a^{(u)}_{j,i}\}_{u=0}^{w-1}$ (and the signing indices), and the Pedersen binding property ensures that (with high probability) we have:
 $${}_ef^{(u)}_{j,i} = \sigma^{(u)}_{j,i}x_e + a^{(u)}_{j,i} \; \forall \: e \in [0,m]$$
@@
 $$\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sum_{e=0}^m \theta_ex_e^m \left( \sumu \mu_{l^{(u)}} M_{l^{(u)}} \right) + \sum_{e=0}^m \theta_e \left( \sumj x_e^j \overline{X}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) G$$
-The rightmost double sum of scalars is therefore, with high probability, equal to $r = \mu_{l^{(u)}} r^{(u)}$.
+We therefore can define extractions for each $r^{(u)}$:
+$$r^{(u)} \equiv \frac{1}{\mu_{l^{(u)}}} \sum_{e=0}^m \theta_e {}_ez^{(u)}_R$$
 
-\textbf{OPEN QUESTION:} Does it necessarily follow that $\sum_{e=0}^m \theta_e {}_ez^{(u)}_R = \mu_{l^{(u)}} r^{(u)}$ for each $u$?
+Observe that the same witnesses appear in the $Y$-check:
+$$\sumu \mu_{l^{(u)}} U = \sum_{e=0}^m \theta_ex_e^m \left( \sumu \mu_{l^{(u)}} U \right) + \sum_{e=0}^m \theta_e \left( \sumj x_e^j \overline{Y}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) J^{(u)}$$
+This means the requirements on each $r^{(u)}$ are satisfied.
 
@@
 Hence we have $y \equiv \sum_{e=0}^m \theta_e {}_ez_S$.
-
-Unfortunately, the same technique does not appear to apply for the $Y$-check. Doing so obtains the following:
-$$\sumu \mu_{l^{(u)}} U = \sum_{e=0}^m \theta_ex_e^m \left( \sumu \mu_{l^{(u)}} U \right) + \sum_{e=0}^m \theta_e \left( \sumj x_e^j \overline{Y}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) J^{(u)}$$
-It is unclear how to associate this with the required witness extraction.
-
-\textbf{OPEN QUESTION:} Does the witness extraction from the previous open question imply that each linking tag satisfies the required relation?
 

### 2020-01-06 paper/iacr.tex
Paper update for IACR archive
Paper updates

@@
-\documentclass[draft]{article} % TODO: remove draft
-\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}
-\usepackage{amsmath,amssymb,amsthm,amsfonts}
-\usepackage[utf8]{inputenc}
+\documentclass[draft]{llncs} % TODO: remove draft option
+\pagestyle{headings}
+
+\usepackage{enumerate}
+\usepackage{amsmath,amssymb}
 \usepackage{hyperref}
-\usepackage{graphicx}
+\usepackage[notcite]{showkeys} % TODO: remove showkeys
+\usepackage{lineno} % TODO: remove
+\linenumbers % TODO: remove
 
-% TODO remove
-\usepackage{lineno}
-\linenumbers
-
-\title{Triptych: logarithmic-sized linkable ring signatures with applications}
-\author{Sarang Noether \\ Monero Research Lab \\ \texttt{sarang.noether@protonmail.com}}
-\date{\today}
-
-\newcommand{\G}{\mathbb{G}}
-\newcommand{\F}{\mathbb{F}}
-\newcommand{\com}{\operatorname{Com}}
-\newcommand{\hs}{\mathcal{H}}
-\newcommand{\hp}{\mathbb{H}}
-
-\newcommand{\A}{\mathcal{A}}
-
-\newcommand{\sumi}{\sum_{i=0}^{n-1}}
-\newcommand{\sumj}{\sum_{j=0}^{m-1}}
-\newcommand{\sumk}{\sum_{k=0}^{N-1}}
-
-\newtheorem{theorem}{Theorem}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
+\title{Concise Linkable Ring Signatures and Applications}
+\institute{Monero Research Lab, \email{\{surae,sarang\}@getmonero.org} \and Independent researcher, \email{randomrun@protonmail.com}}
+\author{Brandon Goodell\inst{1} \and Sarang Noether\inst{1} \and Arthur Blue\inst{2}}
 
 \begin{document}
-
 \maketitle
@@
 \begin{abstract}
-Ring signatures are a common construction used to provide signer ambiguity among a non-interactive set of public keys specified at the time of signing.
-Unlike early approaches where signature size is linear in the size of the signer anonymity set, current optimal solutions either require centralized trusted setups or produce signatures logarithmic in size.
-However, few also provide linkability, a property used to determine whether the signer of a message has signed any previous message, possibly with restrictions on the anonymity set choice.
-Here we introduce Triptych, a family of linkable ring signatures without trusted setup that is based on generalizations of zero-knowledge proofs of knowledge of commitment openings to zero.
-We demonstrate applications of Triptych in signer-ambiguous transaction protocols by extending the construction to openings of parallel commitments in independent anonymity sets.
-Signatures are logarithmic in the anonymity set size and, while verification complexity is linear, collections of proofs can be efficiently verified in batches.
-We show that for anonymity set sizes practical for use in distributed protocols, Triptych offers competitive performance with a straightforward construction.
+We describe a generalization of linkable ring signatures, $d$-linkable ring signatures ($d$-LRS).
+These admit $d$-dimensional vectors of keys with a specified linking coordinate, but do not have signature sizes linear in $d$.
+We then produce an efficient $d$-LRS construction, called \textit{concise linkable spontaneous anonymous group} signatures (CLSAG), that are smaller than existing constructions without a trusted setup used in production, and are more efficient in verification over a reasonable range of anonymity set sizes.
+Security is proven using the $k$-one more discrete logarithm and decisional Diffie-Hellman hardness assumptions to show correctness, unforgeability, linkable anonymity, linkability, and non-frameability.
+We describe direct applications to signer-ambiguous confidential transactions with single or multiple asset classes.
 \end{abstract}
@@
 \section{Introduction}
-First introduced in \cite{rivest} with respect to RSA groups, ring signatures permit the signing of messages using public key sets not fixed in advance, without the need of a trusted group manager.
-Earlier constructions lacked such flexibility, requiring either centralized key setup or the establishment of fixed signing sets.
-Later work \cite{bender} established more robust security models for unforgeability and anonymity, capturing realistic threat models where an adversary is permitted to corrupt keys, convince honest signers to include malicious anonymity set members, or obtain signatures in advance.
 
-Since a ring signature has an anonymity set of public keys, one of which is the true signer, the detection of signing by the same key requires an additional property, linkability.
-A linkable ring signature \cite{lsag} enables verifiers to determine whether the (unknown) signer of a message has signed other messages.
-Such a construction was proposed for election applications, where it is necessary to ensure that votes are anonymous, but voters are permitted to vote only once on a particular issue.
-The construction in \cite{lsag}, with a hash-trapdoor structure similar to that of \cite{schnorr}, is of particular interest due to potential flexibility in linking; while its linking is limited to signer-selected but unchanging signer anonymity sets, it permits linking on a per-issue basis.
-Additional recent work in \cite{backes} introduces the property of linkable anonymity, using sets of signatures and establishing restrictions on key corruption.
-Other related interesting properties like traceability \cite{fs,f} imply stronger capabilities, where an attempt to sign two messages with the same key permits verifiers to identify the signer.
+First introduced in \cite{rivest} in the RSA setting and in \cite{liu} in the discrete logarithm setting, ring signatures permit message signing on behalf of a set of public keys rather than a single public key.
+Ring signatures see myriad applications ranging from lightweight anonymous authentication in \cite{yang2015lightweight} to transaction protocols like Monero in \cite{noether} and CryptoNote in \cite{van2013cryptonote}.
+A verifier is assured that the signer knows the private key of at least one of these public keys, which are called ring members.
+Ring signatures are anonymous or signer-ambiguous in the sense that the verifier does not learn information from the signature about which key is the signer.
+We stress that methods of practical analysis such as those of  \cite{moser2018empirical,quesnelle2017linkability} can exploit metadata in real-life applications of anonymous authentication protocols to reduce anonymity.
 
-Linkable ring signatures have seen particular applications in signer-ambiguous transaction protocols.
-In such an application, transactions are authorized by a ring signature whose signing anonymity set consists of previously-generated transaction outputs.
-A signature demonstrates that the signer controls the private key of one such output without revealing which is the signer, and linkability is used to assure verifiers that output has not been used in another signature (signifying a double-spend attempt).
+Group signature constructions preceding \cite{rivest,liu} require some degree of interactivity, a fixed set of participants, a trusted group manager or other trusted setup, or hardness assumptions not based on the discrete logarithm problem.
+Since \cite{rivest}, ring signatures have enjoyed many improvements, extensions, and modifications.
+For example, ring signatures are constructed in the bilinear pairing setting in \cite{zhang2002id}, key structures are generalized in \cite{abe20021}, security definitions are improved in \cite{bender}, signature size is improved in \cite{fujisaki2011sub,gu2018constant}, and traceability is introduced in \cite{fujisaki2007traceable}.
 
-A practical consideration for the use of linkable ring signatures in transaction protocols is how signature size and verification time scale with the size of the anonymity set.
-In common applied constructions like \cite{mlsag,clsag}, signature size and verification time scale linearly with the size of the signing ambiguity set; since such signatures are typically included in a public distributed data structure like a blockchain, there is a balance between the size of the anonymity set and the requirements for storage and verification.
-Recent protocol work in this area mitigates the size restriction.
-For example, in \cite{rct3}, the authors introduce a confidential transaction protocol based on a proving system whose size scales logarithmically with the anonymity set size, and which includes a method for demonstrating amount balance; amount commitment range proving is offloaded to other constructions like \cite{bulletproofs}.
-In \cite{omniring}, the authors use a more general proving technique to accomplish a similar goal; however, the protocol offers further size benefits by integrating commitment range proofs into the proof structure directly, taking advantage of the logarithmic proof size.
+Linkable ring signatures were first introduced in \cite{liu}; in the context of transaction protocols, linkable ring signatures are the basis for anonymous transaction authentication.
+Linkable ring signatures guarantee that two signatures with the same ring on arbitrary messages can be publicly linked if signed using the same key.
+An implementation is presented in \cite{liu} in the discrete logarithm setting; that implementation functions for similar reasons as Schnorr signatures in \cite{schnorr1991efficient}.
 
-Other signer-ambiguous transaction protocols not based on linkable ring signatures offer more competitive performance.
-For example, protocols like \cite{zcash} produce maximal theoretical signer ambiguity through the use of zero-knowledge Merkle proofs (among others) that offer extremely small proofs with low verification time, but at the cost of a trusted structured setup process that arises from the underlying proving system \cite{groth16}.
-Like this work, \cite{lelantus} is a transaction protocol also based on \cite{groth}; however, it is intended to operate on commitments similar to those used in \cite{zerocoin} but with the inclusion of amounts, and has limitations on addressing and sender tracing.
+The signature linking tags in \cite{liu} are unsuitable for applications where signatures must be linked key-by-key, not ring-by-ring (such as for ``double-signing'' protection in a setting where users generate new keys over time and select \textit{ad hoc} ring members).
+Resistance to double-signing attempts is ensured using linking tags as described in \cite{van2013cryptonote} (therein called key images).
+More recent work of \cite{noether} extends the approach of \cite{liu} to enable an anonymous confidential transaction model with \textit{ad hoc} ring member selection.
+In \cite{noether}, transaction amounts are replaced with Pedersen commitments to amounts together with range proofs.
+Signatures are constructed from key vectors including differences of amount commitments as one of the keys.
+However, the proofs in \cite{noether} are informal and not based on rigorous security models.
+
+Alternatives to ring signatures like more general zero-knowledge proving systems typically require a trusted party to honestly perform a setup process (as in \cite{groth,ben2014succinct,groth2018updatable}) or lack practical efficiency for large circuits (as in \cite{bulletproofs}), meaning that such systems may not be appropriate for distributed ledger applications.
+However, more recent approaches such as \cite{bowehalo,hoffmann2019efficient} show both improvements to the trust requirement as well as improvements in efficiency.
 
 \subsection{Our contribution}
-We produce two instantiations of a linkable ring signature, which we call Triptych.
-The constructions are a linkable generalization of Groth's one-of-many commitment-to-zero proving system \cite{groth}, with optimizations from Bootle \cite{bootle} applied for improvements to proof size and verification complexity.
-In one version of Triptych, the prover shows that it knows the opening of a commitment to zero within a commitment list, and also that it has constructed a linking tag using the same opening, enabling linkability.
-We then modify Groth's ring signature definitions to include linkability and a related property, non-frameability.
 
-In the second version of Triptych, we further generalize to include a parallel list of commitments.
-Here, the prover proceeds as before to show its knowledge of an opening to a commitment in one list, as well as the construction of the linking tag.
-However, the proof also shows that the prover knows an opening of a commitment at the same position in the second commitment list.
-This construction has immediate application; in some signer-ambiguous confidential transaction protocols, transaction inputs are commitments to zero, for which the signer shows it knows the opening.
-Each commitment comes equipped with another commitment to the amount of the input; by offsetting these commitments homomorphically and carefully choosing commitment randomness, the prover can show that a particular transaction balances.
+We first introduce a formal definition of $d$-dimensional linkable ring signatures ($d$-LRS) as a generalization of linkable ring signatures (LRS).
+We present an implementation of a new $d$-LRS, $d$-concise linkable spontaneous anonymous group ($d$-CLSAG) signatures.
+These have $d$-dimensional keys, and signature size scales with the sum of ring size and the dimension $d$.
+Equivalent MLSAG signatures of \cite{noether} produce signatures that scale with the product of ring size and $d$ rather than the sum.
+Size efficiency comes from an aggregation of keys across key vector components, similar to the approach from \cite{maxwell2018simple,qian2010non}; this results in signatures that are about half the size of \cite{noether}, and can be generated and verified more quickly in practice.
 
-We show that Triptych produces signatures with competitive performance to other modern linkable ring signatures for limited anonymity set sizes.
-We note that similar constructions also require linear verification time, meaning that the size of anonymity set used in practice is likely to be limited for performance reasons.
+We describe linkable ring signatures, $d$-LRS constructions, and examples in Section \ref{sec:lrs}.
+We present our $d$-CLSAG construction in Section \ref{sec:construction} and discuss its efficiency.
+The security model and main results are presented in Section \ref{sec:security}.
+We produce informal descriptions of signer-ambiguous confidential transaction applications for single and multiple asset types in Section \ref{sec:applications}.
+Security proof are presented in Appendix \ref{app:proofs}.
 
-\section{Preliminaries}
-\subsection{Public parameters}
-Let $\G$ be a cyclic group in which the discrete logarithm problem is hard, and let $\F$ be the scalar field of $\G$.
-Let $\hs: \{0,1\}^* \to \F$ be a cryptographic hash function.
-Let $G$ and $H$ be generators of $\G$ with unknown discrete logarithm relationship.
-Let $N = n^m$ be a size parameter, where $n > 1$ and $m > 1$.
-Let $\{G_{j,i}\}_{j,i=0}^{m-1,n-1}$ be a set of generators of $\G$ with unknown discrete logarithm relationship to each other, to $G$, and to $H$.
-Let $U$ be a generator of $\G$.
-Note that all generators may be produced using public randomness; for example, the use of a suitable hash function with domain separation may be appropriate.
-All such public parameters are assumed to comprise a global reference string known to all players; in particular, we exclude them from algorithm definitions and Fiat-Shamir transcript hashes for readability.
+Notably, we provide a new definition for unforgeability in linkable ring signatures that takes into account both insider corruption and forgeries from partially-corrupted rings.
+We prove that $d$-CLSAG signatures are unforgeable under the hardness of the $k$-one-more discrete logarithm ($k$-OMDL) problem under this definition in the random oracle model, and show that  the properties of linkability and non-frameability follow from unforgeability.
+We show that linkable anonymity reduces to the hardness of a form of the decisional Diffie-Hellman (DDH) problem.
 
-\subsection{Pedersen commitment}
-Let $\com$ be a homomorphic commitment scheme that is perfectly hiding and computationally binding.
-In this work, we assume use of the Pedersen commitment scheme: for $x,r \in \F$, define $\com(x,r) \equiv xG + rH$ to be the commitment of the value $x$ with randomness $r$.
-This can be trivially extended to support matrix values; for $\{x_{j,i}\},r \in \F$, define $\com(x,r) \equiv rH + \sum_{j,i} x_{j,i}G_{j,i}$.
-Note in particular that Pedersen matrix commitments are similarly homomorphic.
+\subsection{Notation}\label{sec:notation}
 
-\subsection{Other notation}
-For integers or field elements $i,j$, the Kronecker delta function $\delta(i,j)$ evaluates to $1$ if $i=j$ and $0$ otherwise, where the output is taken to be in the appropriate set.
+We denote algorithms with typefont upper-case English letters like $\texttt{A}$, $\texttt{B}$, or $\texttt{O}$, or typefont names like $\texttt{Setup}$, $\texttt{KeyGen}$, and so on.
+For any prime $p$, denote the field with $p$ elements as $\mathbb{F}_p := \mathbb{Z}/p\mathbb{Z}$, and denote the non-zero elements as $\mathbb{F}_p^*$.
 
-We sometimes use index subscript notation of the form $i_j$ to indicate the $j$ digit of $i$, where such a decomposition of $i$ is taken base $n$ with padded length $m$:
-$$\sum_{j=0}^m i_j n^j = i$$
-This notation will be specified explicitly where confusion may occur.
+Group parameters are denoted as a tuple $(p, \mathbb{G}, d, G)$ where $\mathbb{G}$ is an elliptic curve group with prime order $p$, $d$ is a dimension, and $G$ is a generator of $\mathbb{G}$.
+We denote integers, bits, indices, and scalars in $\mathbb{F}_p$ with lower-case English letters $x, y, z, b, c, i, j, k$, etc.\ and we denote group elements with upper-case English letters, $G, X, W$, and so on.
+We use lower-case Greek letters like $\sigma$ to describe signatures and upper-case calligraphic Latin letters like $\mathfrak{T}$ when describing key images.
 
-\section{Protocol: linkable one-of-many commitment}
-We wish to build a linkable ring signature construction, where a signer who knows the opening of a commitment may sign messages using an anonymity set containing other commitments for which the signer does not know openings.
-Included with the proof of knowledge, the signer also provides a linking tag that is the image of the signing commitment's opening under a verifiable pseudorandom function, using the method of \cite{dodis} that has previously appeared in \cite{omniring,rct3}.
-Part of the soundness of the proving system relies on the proper construction of this linking tag.
-Upon receipt, a verifier can check whether the linking tag has previously appeared in any other valid proof; if it has not, injectivity assures the verifier that no other signature has been produced by the (unknown) signer.
+For these group parameters, the secret key space is $\mathbb{F}_p^*$ and the public key space is $\mathbb{G}$.
+For any non-zero secret key $\textit{sk} \in \mathbb{F}_p^*$, the corresponding public key $\textit{pk}$ is computed from the generator $G$ through exponentiation in $\mathbb{G}$ as usual.
+However, we use notation for a module over the field $\mathbb{Z}_p$ to maintain consistency with related work like \cite{van2013cryptonote} and \cite{noether}.
 
-More specifically, we modify the construction of Bootle \cite{bootle}, which itself is a generalization of a construction by Groth \cite{groth}.
-We produce a sigma protocol for the following relation:
-$$\mathcal{R}_{\text{link}} = \left\{ \{M_i\}_{i=0}^{N-1} \subset \G, J \in \G ; (l \in \mathbb{Z},r \in \F) : M_l = rG \text{ and } U = rJ \right\}$$
-Figures \ref{fig:link} and \ref{fig:link_2} describe the protocol.
+We denote column vectors in boldface, such as $(x_1, \ldots, x_d)^\top = \textbf{x}$, and matrices in underlined boldface, such as $((x_{1,1}, x_{1,2}, \ldots, x_{1,n}), \ldots, (x_{d,1}, \ldots, x_{d,n})) = (\textbf{x}_1, \textbf{x}_2, \ldots, \textbf{x}_n) = \underline{\textbf{x}}$ is a $d\times n$ matrix.
+We denote the Hadamard product of two vectors with $\circ$, so for any $\textbf{x} = (x_1, x_2, \ldots, x_d) = (x_i)_{i=1}^{d}$, and for any $\textbf{y} = (y_i)_{i=1}^{d}$, we denote the sequence $(x_i \cdot y_i)_{i=1}^{d}$ with $\textbf{x} \circ \textbf{y}$.
+We denote bitwise concatenation with the symbol $\mid \mid$.
 
-\begin{figure}[htbp]
-\centering
-\fbox{\begin{minipage}{0.95\textwidth}
-$\underline{\mathcal{P}_{\text{link}}(\{M_i\},J;(l,r)):}$
+We distinguish oracles with calligraphic font; $\mathcal{CO}$ denotes a corruption oracle, $\mathcal{SO}$ denotes a signing oracle, and so on.
+If the codomain of a random oracle is the field of scalars $\mathbb{F}_p$, we denote this $\mathcal{H}^s$ (hash-to-scalar).
+If the codomain is $\mathbb{G}$, we denote this $\mathcal{H}^p$ (hash-to-point).
+
+\section{Linkable and $d$-linkable ring signatures}\label{sec:lrs}
+
+In this section, we recall linkable ring signature schemes, related definitions, and relevant examples.
+
+\begin{definition}[Linkable ring signature]\label{def:lrs}
+A \textit{linkable ring signature scheme} is a tuple $\left(\texttt{Setup}, \texttt{KeyGen}, \right. \allowbreak \left. \texttt{Sign}, \texttt{Verify}, \texttt{Link}\right)$ satisfying the following.
 \begin{itemize}
-\item Select random $r_A \in \F$ and $\left\{a_{j,i}\right\}_{i=1,j=0}^{n-1,m-1} \subset \F$.
-Define $A \equiv \com(a,r_A)$.
-\item Define $\left\{\sigma_{j,i}\right\}_{i,j=0}^{n-1,j-1} \subset \F$ such that $\sigma_{j,i} \equiv \delta\left(l_j,i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
-Define $B \equiv \com(\sigma,r_B)$.
-\item Select random $r_C \in \F$, and define $C \equiv \com(a(1-2\sigma), r_C)$.
-\item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
-\item Define coefficients $\left\{p_{k,j}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p_k(x) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}x + a_{j,k} \right) = \delta\left(l,k\right)x^m + \sumj p_{k,j}x^j$$ for all $k \in [0,N)$ (using our decomposition notation).
-\item Select random $\left\{\rho_j\right\}_{j=0}^{m-1} \subset \F$.
-\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}M_k + \rho_jG$$
-\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv U \sumk p_{k,j}+ \rho_jJ$$
+\item $\texttt{Setup}(1^\lambda) \to \textit{par}$. $\texttt{Setup}$ takes as input a security parameter $1^\lambda$, produces some public parameters $\textit{par}$.
+
+\item $\texttt{KeyGen}(1^\lambda, \textit{par}) \to (sk, pk)$.
+$\texttt{KeyGen}$ takes as input a security parameter $1^\lambda$ and public parameters $\textit{par}$.
+$\texttt{KeyGen}$ produces as output a private-public keypair $(sk, pk)$.
+
+\item $\texttt{Sign}\left(1^\lambda, \textit{par}, (m, \textbf{pk}, sk)\right) \to \left\{\bot_{\texttt{Sign}}, \sigma \right\}$.
+$\texttt{Sign}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, an arbitrary message $m \in \left\{0,1\right\}^*$, an ad hoc \textit{ring} of public keys $\textbf{pk} = \left\{pk_1, \ldots, pk_n\right\}$, and a secret key $sk$.
+$\texttt{Sign}$ produces as output either a distinguished failure symbol $\textit{out} = \bot_{\texttt{Sign}}$ or a signature $\sigma$.
+
+\item $\texttt{Verify}\left(1^\lambda, \textit{par}, (m, \textbf{pk}, \sigma)\right) \to \left\{0,1\right\}$.
+$\texttt{Verify}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, a message $m$, a ring of public keys $\textbf{pk}$, and a signature $\sigma$.
+$\texttt{Verify}$ produces as output a bit $b \in \left\{0,1\right\}$; $0$ indicates the signature is not verified, and $1$ indicates the signature is verified.
+
+\item $\texttt{Link}\left(1^\lambda, \textit{par}, (m, \textbf{pk}, \sigma), (m^\prime, \textbf{pk}^\prime, \sigma^\prime)\right)$.
+$\texttt{Link}$ takes as input a security parameter $1^\lambda$, public parameters $\textit{par}$, and a pair of tuples $(m, \textbf{pk}, \sigma), (m^\prime, \textbf{pk}^\prime, \sigma^\prime)$ for messages $m, m^\prime$, rings $\textbf{pk}$, $\textbf{pk}^\prime$, and signatures $\sigma, \sigma^\prime$.
+$\texttt{Link}$ produces as output a bit $b \in \left\{0,1\right\}$; $0$ indicates the signatures are not linked or invalid, and $1$ indicates the signatures are valid and linked.\footnote{This is the opposite of the conventions in, say, \cite{tsang2004separable}, which outputs $0$ to indicate two signatures are linked (\textit{i.e.}\ rejected) and outputs $1$ to indicate two signatures are not linked (\textit{i.e.}\ accepted).}
+\end{itemize}
+\end{definition}
+
+In the sequel, we implicitly assume all algorithms in a LRS take the security parameters as input, and all algorithms (except $\texttt{Setup}$) take public parameters $\textit{par}$ as input.
+We suppress this notation in the sequel.
+For example, we write $\textit{par} \leftarrow \texttt{Setup}$ instead of $\textit{par} \leftarrow \texttt{Setup}(1^\lambda)$ and $\sigma \leftarrow \texttt{Sign}(m, \textbf{pk}, \textit{sk})$ instead of $\sigma \leftarrow \texttt{Sign}(1^\lambda, \textit{par}, m, \textbf{pk}, \textit{sk})$.
+
+Note that the vector dimension of keys in Definition \ref{def:lrs} is not specified.
+If the keys from $\texttt{KeyGen}$ have dimension $d$, we instead say the LRS is a $d$-LRS and use the vector notation introduced in Section \ref{sec:notation} representing keys in boldface (\textit{e.g.}\ \textbf{pk} instead of \textit{pk}) and rings in underlined boldface ($\underline{\textbf{pk}}$ instead of $\textbf{pk}$).
+We always assume the first coordinate of a key is the \textit{linking key}, and all other coordinates are \textit{auxiliary keys}; we will see that in practice, linkability depends only on the linking coordinate of the signing key vector.
+For applications in signer-ambiguous confidential transaction models, this is important since only one coordinate in a vector key corresponds to a public key used for double-spend detection purposes.
+
+\subsection{Examples}\label{sec:examples}
+
+In the following examples, all verifiers must list ring public keys in an agreed-upon order for verification to operate properly; in practice, it is simple to use lexicographical ordering.
+
+\begin{example}\label{ex:lsag}
+The signature scheme of \cite{liu} is an LRS (and, therefore, a $1$-LRS); we present the variant from \cite{van2013cryptonote} with a linking tag (a signature element which is used for identifying linked signatures) appropriate for linking signatures key-by-key.
+The signature scheme originally described in \cite{liu} signs a message $m$ with a ring of keys $\textbf{pk} = \left\{\textit{pk}_1, \ldots, \textit{pk}_n\right\}$ and a secret index-key pair $(\ell, \textit{sk})$ corresponding to some $\textit{pk}_\ell$, and the linking tag $\mathfrak{T} := \textit{sk} \cdot \mathcal{H}^p(\textbf{pk})$.
+
+Unfortunately, this tag construction is unsuitable for many applications, as changing ring members will change the linking tag, allowing the same key to sign twice.
+For use in applications where double-signing detection should be independent of non-signing ring members and following \cite{van2013cryptonote}, we modify the tag from that of \cite{liu} to be $\mathfrak{T} := \textit{sk} \cdot \mathcal{H}^p(\textit{pk}_\ell)$, which is independent of the non-signing ring members.
+This allows tags to be used for double-spend protection, as discussed below.
+
+$\texttt{Setup}$ always deterministically sets $d := 1$, so there are no auxiliary keys as part of key vectors.
+$\texttt{Setup}$ selects a generator $G \in \mathbb{G}$ to be a group generator for the group parameters $(p, \mathbb{G}, d, G)$, two cryptographic hash functions $\mathcal{H}^s:\left\{0,1\right\}^* \to \mathbb{F}_p$ and $\mathcal{H}^p:\left\{0,1\right\}^* \to \mathbb{G}$.
+$\texttt{Setup}$ outputs $\textit{par} = (p, \mathbb{G}, d, G, \mathcal{H}^s, \mathcal{H}^p)$.
+
+$\texttt{KeyGen}$ produces as output a secret key $\textit{sk} \in \mathbb{F}_p^*$ and the corresponding public key $\texttt{pk} = \textit{sk}\cdot G\in \mathbb{G}$.
+
+$\texttt{Sign}$ takes as input a private key $\textit{sk} \in \mathbb{F}_p^*$, a message $m$, a ring $\textbf{pk} = \left\{\textit{pk}_1, \ldots, \textit{pk}_n\right\}$, and produces as output either a distinguished failure symbol $\bot_{\texttt{Sign}}$ or a signature $\sigma$, computed as follows.
+First, the signer samples field elements $\alpha, s_{\ell+1}, s_{\ell+2}, \ldots, s_{\ell-1} \in \mathbb{F}_p$ at random.
+Next, the signer computes group elements $H_i = \mathcal{H}^p(\textit{pk}_i)$ and the linking tag $\mathfrak{T} = \textit{sk} \cdot \mathcal{H}^p(\textit{pk}_\ell)$, the first challenge $$c_{\ell+1}  = \mathcal{H}^s(\textbf{pk} \mid \mid m \mid \mid \alpha G \mid \mid \alpha H_\ell)$$ and each subsequent challenge $$c_{i+1} = \mathcal{H}^s(\textbf{pk} \mid \mid m \mid \mid s_i G + c_i \cdot \textit{pk}_i \mid \mid s_i H_i + c_i \mathfrak{T})$$ for $i = \ell+1, \ldots, \ell-1$, naturally identifying index $1$ with index $n+1$.
+The signer finishes by computing $s_\ell = \alpha - c_\ell \cdot \textit{sk}$ and publishing the signature $\sigma$ where $\sigma = (c_1, s_1, \ldots, s_n, \mathfrak{T})$.
+
+$\texttt{Verify}$ takes as input a message $m$, a ring $\textbf{pk}$, and a purported signature $\sigma^\prime$.
+$\texttt{Verify}$ parses $(c_1, s_1, \ldots, s_n, \mathfrak{T}) \leftarrow \sigma$.
+If $c_1 \notin \mathbb{F}_p$ or any $s_i \notin \mathbb{F}_p$ or $\mathfrak{T} \notin \mathbb{G}$, then $\texttt{Verify}$ outputs $0$.
+Otherwise, the verifier computes $H_i := \mathcal{H}^p(X_i)$ for each ring member, sets $c_1^\prime := c_1$, and computes the challenges $$c_{i+1}^\prime = \mathcal{H}^s(\textbf{pk} \mid \mid m \mid \mid s_i G + c_i^\prime \cdot \textit{pk}_i \mid \mid s_i H_i + c_i^\prime \mathfrak{T})$$ for $i=1, 2, \ldots, n$.
+The verifier outputs $1$ when $c_{n+1}^\prime = c_1$ and $0$ otherwise.
+
+$\texttt{Link}$ checks the validity of both signatures.
+If both are valid, $\texttt{Link}$ parses the linking tags $\mathfrak{T}$ and $\mathfrak{T}^\prime$.
+If either are not in $\mathbb{G}$, the linker outputs $0$ and terminates.
+Otherwise, the linker outputs $1$ when $\mathfrak{T} = \mathfrak{T}^\prime$ and $0$ otherwise.
+\end{example}
+
+\begin{example}\label{ex:mlsag}
+This example extends the LRS of the previous example to a so-called MLSAG scheme \cite{noether}, which is a $2$-LRS for use in signer-ambiguous confidential transactions.
+
+$\texttt{Setup}$ always deterministically sets $d := 2$, so there is one auxiliary key, but otherwise works as before.
+
+$\texttt{KeyGen}$ produces as output a secret key $\textbf{sk} = (x, z) \in \mathbb{F}_p^* \times \mathbb{F}_p^*$ and the corresponding public key  $\textbf{pk} := \textbf{sk} \circ \textbf{G} = (xG, zG) \in \mathbb{G}^2$ where $\textbf{G} = (G, G) \in \mathbb{G}^2$.
+The key $x$ is the linking key.
+The auxiliary key $z$ is a blinder that opens a Pedersen commitment to zero demonstrating transaction balance in ring confidential transactions in the style of \cite{noether}.
+
+$\texttt{Sign}$ takes as input a (non-zero) private key $\textbf{sk} \in \mathbb{F}_p^* \times \mathbb{F}_p^*$, a message $m$, a ring $\underline{\textbf{pk}} \in \mathbb{G}^{2 \times n}$, and produces as output either a distinguished failure symbol $\bot_{\texttt{Sign}}$ or a signature $\sigma$, computed as follows.
+First, the signer samples rows of signature data  $\alpha, \alpha^\prime, s_{\ell + 1}, s^\prime_{\ell + 1}, s_{\ell + 2}, s^\prime_{\ell + 2}, \ldots, s_{\ell -1}, s^\prime_{\ell - 1} \in \mathbb{F}_p$ at random.
+Next, the signer computes the group elements $H_i = \mathcal{H}^p(X_i)$ from the linking keys $X_i$ of each ring member $\textbf{pk}_i = (X_i, Z_i)$.
+The linking tag $\mathfrak{T} = x H_\ell$ is computed from the linking key.
+Another group element with the same base but discrete logarithm $z_\ell$ is computed: $\mathfrak{D} = z_\ell H_\ell$.
+The signer computes the challenges
+$$c_{\ell + 1} = \mathcal{H}^s(\textbf{pk} \mid \mid m \mid \mid \alpha G \mid \mid \alpha H_\ell \mid \mid \alpha^\prime G \mid \mid \alpha^\prime H_\ell)$$
+and
+$$c_{i+1} = \mathcal{H}^s(\textbf{pk} \mid \mid m \mid \mid s_i G + c_i X_i \mid \mid s_i H_i + c_i \mathfrak{T} \mid \mid s_i^\prime G + c_i Z_i \mid \mid s_i^\prime H_i + c_i \mathfrak{D}).$$
+The values $s_\ell = \alpha - c_\ell x_\ell$ and $s_\ell^\prime = \alpha^\prime - c_\ell z_\ell$ are computed.
+The signature is set $\sigma := (c_1, s_1, s_1^\prime, \ldots, s_n, s_n^\prime, \mathfrak{T}, \mathfrak{D})$ and is output.
+
+$\texttt{Verify}$ takes as input a message $m$, a ring $\underline{\textbf{pk}}$, and a signature $\sigma$.
+The verifier parses $(c_1, s_1, s_1^\prime, \ldots, s_n, s_n^\prime, \mathfrak{T}, \mathfrak{D}) \leftarrow \sigma$.
+If this is not possible, or $c_1 \notin \mathbb{F}_p$, or any $s_i$ or $s_i^\prime \notin \mathbb{F}_p$, or if $\mathfrak{T} \notin \mathbb{G}$, then the verifier outputs $0$.
+Otherwise, the verifier parses $(\textbf{pk}_1, \ldots, \textbf{pk}_{n^\prime}) \leftarrow \underline{\textbf{pk}}$.
+If any $\textbf{pk}_i \notin \mathbb{G}^2$, or if $n \neq n^\prime$, the verifier outputs $0$.
+Otherwise, the verifier parses each $\textbf{pk}_i$ as $(X_i, Z_i)$, computes each $H_i = \mathcal{H}^p(X_i)$, sets $c_1^\prime := c_1$, and computes the challenges $$c_{i+1}^\prime = \mathcal{H}^s(\textbf{pk} \mid \mid m \mid \mid s_i G + c_i^\prime X_i \mid \mid s_i H_i + c_i^\prime \mathfrak{T} \mid \mid s_i^\prime G + c_i^\prime Z_i \mid \mid s_i^\prime H_i + c_i^\prime \mathfrak{D})$$ for $i=1, 2, \ldots, n$.
+The verifier outputs $1$ when $c_{n+1}^\prime = c_1$ and $0$ otherwise.
+
+Lastly, $\texttt{Link}$ works as before, by comparing linking tags.
+\end{example}
+
+\section{Construction}\label{sec:construction}
+In this section, we describe $d$-CLSAG, our implementation of a concise $d$-LRS construction.
+
+\subsection{Implementation}\label{sec:implementation}
+\begin{definition}[$d$-CLSAG]\label{def:clsag}
+The tuple $(\texttt{Setup}, \texttt{KeyGen}, \texttt{Sign}, \texttt{Verify}, \allowbreak \texttt{Link})$ satisfying the following is a $d$-LRS signature scheme.
+
+\begin{itemize}
+\item $\texttt{Setup} \to \textit{par}$.
+$\texttt{Setup}$ selects a prime $p$, a group $\mathbb{G}$ with prime order $p$, selects a group generator $G \in \mathbb{G}$ uniformly at random, selects $d$ cryptographic hash functions $\mathcal{H}^s_0, \ldots, \mathcal{H}^s_{d-1}$ with codomain $\mathbb{F}_p$, selects a cryptographic hash function $\mathcal{H}^p$ with codomain $\mathbb{G}$.
+$\texttt{Setup}$ outputs the group parameter tuple and the hash functions, $\textit{par} := \left(p,\mathbb{G}, d, G, \left\{\mathcal{H}^s_j\right\}_{j=0}^{d-1}, \mathcal{H}^p\right)$.\footnote{Note that domain separation can be used here to take one $\mathcal{H}^s$ and construct each $\mathcal{H}^s_j$ by defining $\mathcal{H}^s_j(x) := \mathcal{H}^s(j \mid\mid x)$.}
+
+\item $\texttt{KeyGen} \to (\textbf{sk}, \textbf{pk})$. When queried for a new key, $\texttt{KeyGen}$ samples a fresh secret key and computes the associated public key:
+\begin{align*}
+\textbf{sk} =& (x, z_1, \ldots, z_{d-1}) \leftarrow (\mathbb{F}_p^*)^d\\
+\textbf{pk} :=& \textbf{sk} \circ \textbf{G} = (X, Z_1, \ldots, Z_{d-1}) \in \mathbb{G}^d
+\end{align*} where $\textbf{G} = (G, \ldots, G) \in \mathbb{G}^d$.
+$\texttt{KeyGen}$ outputs $(\textbf{sk}, \textbf{pk})$.
+We say $x$ is the \textit{linking key} and the remaining keys $\left\{z_j\right\}$ are the \textit{auxiliary keys}.
+
+\item $\texttt{Sign}\left(m, \underline{\textbf{pk}}, \textbf{sk}\right) \to \left\{\bot_{\texttt{Sign}}, \sigma\right\}$.
+$\texttt{Sign}$ takes as input a message $m \in \left\{0,1\right\}^*$, a ring  $\underline{\textbf{pk}} = (\textbf{pk}_1, \ldots, \textbf{pk}_n)$ for ring members $\textbf{pk}_i = (X_i, Z_{i,1}, \ldots, Z_{i,d-1}) \in \mathbb{G}^d$, and a secret key $\textbf{sk} = (x,z_1, \ldots, z_{d-1}) \in (\mathbb{F}_p^*)^d$.
+$\texttt{Sign}$ does the following.
+
+\begin{enumerate}
+\item If $\underline{\textbf{pk}} \notin \mathbb{G}^{d\times n}$ for some $n$, $\texttt{Sign}$ outputs $\bot_{\texttt{Sign}}$ and terminates.
+
+\item Otherwise, $\texttt{Sign}$ parses\footnote{Note that this parsing always succeeds if $\texttt{Sign}$ does not fail in the previous step.} $\underline{\textbf{pk}}$ to obtain each $\textbf{pk}_i$.
+If the public key associated with the input $\textbf{sk}$ is not a ring member in $\underline{\textbf{pk}}$, then $\texttt{Sign}$ outputs $\bot_{\texttt{Sign}}$ and terminate.
+
+\item Otherwise, $\texttt{Sign}$ finds the signing index $\ell$ such that $\textbf{pk}_\ell = \textbf{sk} \circ (G, \ldots, G)$.
+$\texttt{Sign}$ samples $\alpha \in \mathbb{F}_p$, samples $\left\{s_i\right\}_{i \neq \ell} \in (\mathbb{F}_p)^{n-1}$, and computes the points $H_i = \mathcal{H}^p(X_i)$ for each $i$.
+$\texttt{Sign}$ computes the \textit{aggregation coefficients} $\mu_X$ and $\{\mu_j\}_{j=1}^{d-1}$, the linking tag $\mathfrak{T}$, the auxiliary group elements $\{\mathfrak{D}_j\}_{j=1}^{d-1}$, and the aggregated public keys:
+\begin{align*}
+\mathfrak{T} :=& x H_\ell & \{\mathfrak{D}_j\} :=&  \{z_j H_\ell\} \\
+\mu_X :=& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1})
+ & \mu_j :=& \mathcal{H}^s_j(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}) \\
+ W_i :=& \mu_X X_i + \sum_{j=1}^{d-1} \mu_j Z_{i,j} & \mathfrak{W} :=& \mu_X \mathfrak{T} + \sum_{j=1}^{d-1} \mu_j \mathfrak{D}_j
+ \end{align*} and the aggregated secret key $w_\ell :=  \mu_X x + \sum_{j=1}^{d-1} \mu_j z_j$.
+For $i = \ell, \ell+1, \ldots, \ell-1$, (and by identifying index $n+1$ with index $1$), $\texttt{Sign}$ computes
+\begin{align*}
+L_\ell =& \alpha G & R_\ell =& \alpha H_\ell & c_{\ell+1} =& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid m \mid \mid L_\ell \mid \mid R_\ell) \\
+L_i =& s_i G + c_i W_i & R_i =& s_i H_i + c_i \mathfrak{W}
+ & c_{i+1} =& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid m \mid \mid L_i \mid \mid R_i)
+\end{align*} and lastly computes $s_\ell = \alpha - c_\ell w_\ell$.
+
+\item $\texttt{Sign}$ sets the signature $\sigma = (c_1, s_1, \ldots, s_n, \mathfrak{T}, \{\mathfrak{D}_j\}_{j=1}^{d-1})$ and publishes the signature $\sigma$.
+\end{enumerate}
+
+\item $\texttt{Verify}\left(m, \underline{\textbf{pk}}, \sigma\right) \to \left\{0,1\right\}$.
+$\texttt{Verify}$ takes as input a message $m$, a matrix $\underline{\textbf{pk}} = (\textbf{pk}_1, \ldots, \textbf{pk}_n)$, and a signature $\sigma$.
+\begin{enumerate}
+\item If $\underline{\textbf{pk}} \notin \mathbb{G}^{d \times n}$ for some $n$, or if $\sigma \notin \mathbb{F}_p^{n^\prime+1} \times \mathbb{G}^d$ for some $n^\prime$, $\texttt{Verify}$ outputs $0$ and terminates.
+Otherwise, if $n^\prime \neq n$, $\texttt{Verify}$ outputs $0$ and terminates.
+
+\item $\texttt{Verify}$ parses\footnote{This parsing is always successful if the previous step does not terminate $\texttt{Verify}$.} $(\textbf{pk}_1, \ldots, \textbf{pk}_n) \leftarrow \underline{\textbf{pk}}$ for keys $\textbf{pk}_i \in \mathbb{G}^d$ for $i=1, \ldots, n$, and parses each public key $(X_i, Z_{i, 1}, \ldots, Z_{i, d-1}) \leftarrow \textbf{pk}_i$.
+$\texttt{Verify}$ also parses $(c_1, s_1, \ldots, s_n, \mathfrak{T}, \mathfrak{D}_1, \ldots, \mathfrak{D}_{d - 1}) \leftarrow \sigma$.
+$\texttt{Verify}$ computes each $H_i = \mathcal{H}^p(X_i)$, computes the aggregation coefficients, and computes aggregated public keys:
+\begin{align*}
+\mu_X := & \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}) & \mu_j := & \mathcal{H}^s_j(\underline{\textbf{pk}} \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1})\\
+W_i :=& \mu_X X_i + \sum_{j=1}^{d-1} \mu_j Z_{i,j} & \mathfrak{W} :=& \mu_X \mathfrak{T} + \sum_{j=1}^{d-1} \mu_j \mathfrak{D}_j
+\end{align*}
+
+\item $\texttt{Verify}$ sets $c_1^\prime := c_1$ and, for $i=1, 2, \ldots, n-1$, computes the following.
+\begin{align*}
+L_i :=& s_i G + c_i^\prime W_i, &
+R_i :=& s_i H_i + c_i^\prime\mathfrak{W}, &
+c_{i+1}^\prime :=& \mathcal{H}^s_0\left(\underline{\textbf{pk}} \mid \mid m \mid \mid L_i \mid \mid R_i\right)
+\end{align*}
+\item If $c_{n+1}^\prime = c_1$, $\texttt{Verify}$ outputs $1$, and otherwise outputs $0$.
+\end{enumerate}
+
+\item $\texttt{Link}\left((m, \underline{\textbf{pk}}, \sigma), (m^\prime, \underline{\textbf{pk}}^\prime, \sigma^\prime)\right) \to \left\{0,1\right\}$.
+$\texttt{Link}$ takes as input two message-ring-signature triples.
+\begin{enumerate}
+\item If $\texttt{Verify}(m, \underline{\textbf{pk}}, \sigma) = 0$ or $\texttt{Verify}(m^\prime, \underline{\textbf{pk}}^\prime, \sigma^\prime) = 0$, $\texttt{Link}$ outputs $0$ and terminates.
+
+\item Otherwise, $\texttt{Link}$ parses\footnote{As before with $\texttt{Verify}$, this parsing is always successful if the previous step does not terminate $\texttt{Link}$.} the signatures to obtain
+\begin{align*}
+(c_1, s_1, \ldots, s_n, \mathfrak{T}, \mathfrak{D}_1, \ldots, \mathfrak{D}_{d-1}) \leftarrow&  \sigma\text{ and}\\
+(c_1^\prime, s_1^\prime, \ldots, s_n^\prime, \mathfrak{T}^\prime, \mathfrak{D}_1^\prime, \ldots, \mathfrak{D}_{d-1}^\prime) \leftarrow& \sigma^\prime.
+\end{align*} $\texttt{Link}$ outputs $1$ if $\mathfrak{T} = \mathfrak{T}^\prime$ and $0$ otherwise.
+\end{enumerate}
+\end{itemize}
+\end{definition}
+
+\subsection{Efficiency}\label{sec:efficiency}
+Consider the space and time efficiency of Definition \ref{def:clsag}. We disregard any additional information typically broadcast alongside the signature, such as representations of the ring members.
+
+A $d$-CLSAG signature with a ring size of $n$ contains $n+1$ field elements and $d$ group elements; signature size is $k_s(n+1) + k_p d$ where $k_s$ describes the size of field elements and $k_p$ describes the size of group elements.
+
+To examine the verification time complexity, instead let $k_s$ and $k_p$ be the time complexity of evaluating the hash-to-scalar functions $\mathcal{H}^s$ and of evaluating the hash-to-point function $\mathcal{H}^p$, respectively.
+Let $k^{(i)}$ be the time complexity to evaluate a linear combination of $i$ terms; using specialized algorithms like Straus \cite{straus} or Pippenger \cite{pippenger} multiscalar multiplication (or others, based on $i$), such a linear combination can be evaluated much more quickly than a simple term-by-term computation.
+We note that it is also possible to cache multiples of group elements that are reused within verification for faster linear combination evaluation, but we do not differentiate this here.
+Using these, the time complexity of $d$-CLSAG verification is $(n+d)k_s + nk_p + 2nk^{(d+1)}$.
+
+To compare to the efficiency of an MLSAG implementation from \cite{noether}, observe that $2$-CLSAG has equivalent functionality to an MLSAG signature (which is a $2$-LRS).
+An MLSAG signature used in this way produces $2n+1$ field elements and $1$ group element.
+
+We produced a test implementation in C++ and tested signing and verification for MLSAG and $2$-CLSAG on a 2.1 GHz Opteron processor.
+Table \ref{table:timing} shows the results for different ring sizes.
+In particular, we note that for smaller anonymity sizes, $2$-CLSAG is uniformly faster than MLSAG.
+However, at very large ring sizes, MLSAG is faster due to additional computations involved in computing aggregation coefficients and key prefixing.
+Despite this eventual inefficiency, we note that the linear space requirements generally preclude the use of very large ring sizes in practice, making $2$-CLSAG an efficient improvement over MLSAG in both space and time.
+
+\begin{table}[htp]
+\begin{center}
+\begin{tabular}{r|ll|ll}
+& \multicolumn{2}{c|}{Verify} & \multicolumn{2}{c}{Sign} \\
+\hline
+Anonymity set & MLSAG & CLSAG & MLSAG & CLSAG \\
+\hline
+2 & 2.4 & 2.0 & 2.3 & 2.7 \\
+4 & 4.7 & 4.0 & 4.6 & 4.6 \\
+8 & 9.5 & 7.8 & 9.4 & 8.5 \\
+16 & 18.9 & 15.9 & 18.9 & 16.5 \\
+32 & 37.8 & 32.3 & 37.8 & 33.0 \\
+64 & 75.4 & 67.5 & 75.9 & 68.3 \\
+128 & 150 & 147 & 151 & 148 \\
+256 & 301 & 344 & 303 & 346
+\end{tabular}
+\end{center}
+\caption{Signing and verification times (ms) for MLSAG and $2$-CLSAG}
+\label{table:timing}
+\end{table}
+
+\section{Security model}\label{sec:security}
+We now introduce the hardness assumptions and security definitions that apply to a $d$-LRS construction (and, implicitly, to an LRS construction).
+In particular, we rely on the $k$-one more discrete logarithm ($k$-OMDL) and decisional Diffie-Hellman (DDH) hardness assumptions for our definitions.
+
+\subsection{Hardness assumptions and useful results}\label{sec:assumptions}
+\begin{definition}[k-OMDL assumption]\label{def:komdl}
+Let $k \in \mathbb{N}$.
+We say a PPT algorithm $\texttt{A}$ is a $(t, \epsilon)$-solver of the $k$-OMDL problem if, within time at most $t$ and with probability at least $\epsilon$, $\texttt{A}$ can succeed at the following.
+
+\begin{enumerate}
+\item The challenger uses group parameters $(p, \mathbb{G}, G)$ and picks a collection of group elements $G_1, G_2, \ldots, G_{k}, G_{k+1} \in \mathbb{G}$ (the targets) uniformly at random from $\mathbb{G}$.
+The challenger sends the group parameters and $\left\{G_i\right\}$ to $\texttt{A}$.
+
+\item $\texttt{A}$ is granted access to a corruption oracle $\mathcal{CO}$ that takes as input some $G_i$ sent to $\texttt{A}$ and produces as output the discrete logarithm of $G_i$ with respect to $G$, \textit{i.e.}\ some $x_i \in \mathbb{F}_p^*$ such that $G_i = x_i G$.
+
+\item $\texttt{A}$ produces as output a sequence of $k+1$ scalars $x_1, \ldots, x_{k+1} \in \mathbb{F}_p^*$, counting as a success if:
+\begin{enumerate}[(i)]
+\item for each $x_i$, there exists some index $1 \leq j(i) \leq k+1$ such that $G_{j(i)} = x_iG$ and
+\item $\texttt{A}$ made no more than $k$ queries to $\mathcal{CO}$.
+\end{enumerate}
+\end{enumerate}
+\end{definition}
+
+\begin{definition}[Decisional Diffie-Hellman]\label{ddhgame} Let $\texttt{A}$ be any PPT algorithm, and $(p, \mathbb{G}, G)$ some group parameters.
+We say $\texttt{A}$ is a $(t, \epsilon, \kappa)$-solver of the Decisional Diffie-Hellman game if $\texttt{A}$ can succeed in time at most $t$ with probability at least $\epsilon$ in the following game.
+\begin{enumerate}
+\item The challenger selects $(r_{i,1}, r_{i,2}, r_{i,3}) \in \left(\mathbb{F}_p\right)^3$ uniformly and independently for $i=0, 1, ..., \kappa-1$.
+The challenger computes the public keys $R_{i,1} = r_{i,1} G$, $R_{i,2} = r_{i,2}G$, $R_{i,3}^{(0)} = r_{i,1} r_{i,2} G$, $R_{i,3}^{(1)} = r_{i,3} G$.
+
+\item The challenger selects a bit $b$ independently and uniformly from $\left\{0,1\right\}$ and sends the triples $\left\{(R_{i,1}, R_{i,2}, R_{i,3}^{(b)})\right\}_{i=0}^{\kappa - 1}$ to $\texttt{A}$.
+
+\item $\texttt{A}$ outputs a bit $b^\prime$, succeeding if $b = b^\prime$.
+\end{enumerate}
+\end{definition}
+
+To later prove that the existence of a forger implies that of a $k$-OMDL solver, we will use the forking lemma.
+In the following, we presume the bit length $\eta$ is used to describe group elements in $\mathbb{G}$ and scalars in $\mathbb{F}_p$, \textit{i.e.}\ $\eta = O(\left|p\right|)$.
+
+\begin{lemma}[General forking lemma]\label{lem:fork}
+Let $q, \eta \geq 1$.
+Let $\texttt{A}$ be any PPT algorithm which takes as input some $x_\texttt{A} = (x, \textbf{h})$ where $\textbf{h} = (h_1, \ldots, h_q)$ is a sequence of oracle query responses ($\eta$-bit strings) and returns as output $y_{\texttt{A}}$ either a distinguished failure symbol $\bot$ or a pair $(\textit{idx}, y)$ where $\text{idx} \in [q]^2$ and $y$ is some output.
+Let $\epsilon_{\texttt{A}}$ denote the probability that $\texttt{A}$ does not output $\bot_{\texttt{A}}$ (where this probability is taken over all random coins of $\texttt{A}$, the distribution of $x$, all choices $\textbf{h}$).
+Let $\mathcal{F} = \mathcal{F}^{\texttt{A}}$ be a forking algorithm for $\texttt{A}$.
+The accepting probability of $\mathcal{F}$ satisfies \[\epsilon_{\mathcal{F}} \geq \epsilon_{\texttt{A}} \left(\frac{\epsilon_{\texttt{A}}}{q} - \frac{1}{2^\eta}\right).\]
+\end{lemma}
+
+\subsection{Security definition}\label{sec:definitions}
+Correctness requires that an honest verifier will always verify an honest signature.
+
+\begin{definition}[Correctness]\label{def:correctness}
+Let $m$ be any message, and $\texttt{KeyGen} \rightarrow (\textbf{sk},\textbf{pk})$ be any key pair.
+Let $\underline{\textbf{pk}^\prime}$ be an arbitrary set of group elements in $\mathbb{G}$ containing $\textbf{pk}$.
+
+We say that a $d$-LRS construction is (perfectly) \textit{correct} if it always holds that $$\texttt{Verify}(m,\underline{\textbf{pk}^\prime},\texttt{Sign}(m,\underline{\textbf{pk}^\prime},\textbf{sk})) = 1.$$
+\end{definition}
+Note that we do not assume that all keys in the ring member set were generated from $\texttt{KeyGen}$; in practice, an honest signer may choose non-signing ring members that were generated maliciously by an adversary.
+In general, correctness is proved easily by inspection.
+
+Our definition of unforgeability captures the idea that an adversary can persuade honest users to turn over their secret keys (which we model by a corruption oracle) or to sign arbitrary messages with arbitrary rings (modeled by a signing oracle).
+We use a modified version of the definition of existential forgery with insider corruption for a ring signature by Bender, Katz, and Morselli \cite{bender}.
+In contrast with the definition in \cite{bender}, our modification allows for a forger to succeed at the forgery game with partially corrupted rings.
+
+\begin{definition}[Existential unforgeability with respect to insider corruption]\label{def:unforgeability}
+Let $n(-)$ be a positive polynomial.
+Let $\mathcal{H}^s:\left\{0,1\right\}^* \to \mathbb{F}_p$ be modeled as a random oracle.
+Let $\mathcal{CO}$ be a corruption oracle that takes as input a public key $\textbf{pk}$ from the list of challenge keys and produces as output the corresponding secret key $\textbf{sk}$.
+Let $\mathcal{SO}$ be a signing oracle that takes as input some $(m, \underline{\textbf{pk}}^\prime, \ell)$ such that $\underline{\textbf{pk}^\prime}$ is a matrix of challenge key vectors (\textit{i.e.}\ each column is in $\textbf{pk}$) and produces as output a signature $\sigma$ such that $\texttt{Verify}(m, \underline{\textbf{pk}}^\prime, \sigma) = 1$ and such that the linking tag $\mathfrak{T} \in \sigma$ is the tag corresponding to the $\ell^{th}$ key in $\underline{\textbf{pk}}^\prime$.
+
+We say a PPT algorithm $\texttt{A}$  is a $(t, \epsilon, q_h, q_c, q_s,  \kappa(-))$-forger of a $d$-LRS construction if, within time at most $t$ and with at most $q_h$ oracle queries to $\mathcal{H}^s$, at most $q_c$ oracle queries to $\mathcal{CO}$, and at most $q_s$ queries to $\mathcal{SO}$, $\texttt{A}$ can succeed at the following game with probability at least $\epsilon$.
+\begin{enumerate}
+\item Challenge keys $\left\{(\textbf{sk}_i, \textbf{pk}_i)\right\}_{i=1}^{\kappa(\lambda)} \leftarrow \texttt{KeyGen}(1^\lambda)$ are selected and the public keys $\underline{\textbf{pk}} = \left\{\textbf{pk}_i\right\}_{i=1}^{n(\lambda)}$ are sent to $\texttt{A}$.
+
+\item $\texttt{A}$ is granted access to a corruption oracle $\mathcal{CO}$, random oracle $\mathcal{H}^s$, and the signing oracle $\mathcal{SO}$.
+
+\item $\texttt{A}$ outputs a message $m$, a ring of at most $n$ public keys $\underline{\textbf{pk}}^\prime$, and a signature $\sigma$. This output is a success if
+\begin{enumerate}
+\item $\sigma$ is not output from any query made to $\mathcal{SO}$; and
+
+\item the linking tag $\mathfrak{T} \in \sigma$ does not correspond to a corrupted ring member; and
+
+\item $\texttt{Verify}(m, \underline{\textbf{pk}}^\prime, \sigma) = 1$.
+\end{enumerate}
+\end{enumerate}
+\end{definition}
+
+\begin{remark}
+Note that if the corruption oracle merely acted by computing arbitrary discrete logarithms, then an adversary could do the following: take some target $\textbf{pk}$ from the challenge set, apply a permutation to the coordinates of $\textbf{pk}$, pass the permuted key through $\mathcal{CO}$, obtain the discrete logarithm of the first (signing) key of $\textbf{pk}$, compute the key image for this signing key, and lastly produce a signature using $\texttt{Sign}$.
+For example, to find the discrete logarithm of the linking key in $\textbf{pk} = (A, B)$, the adversary may query $\mathcal{CO}$ with $(B, A)$, bypassing our definition.
+
+Such a signature would pass validation and not be described as a forgery according to our definition.
+Our definition avoids this problem by requiring the corruption oracle only be queried with challenge keys.
+This has the added benefit that it is possible to simulate the corruption oracle for a black-box execution of $\texttt{A}$.
+\end{remark}
+
+Linkability requires that an adversary cannot generate $q + 1$ non-linking signatures using only a combined $q$ possible public keys, asserting that a linking collision must exist, as in \cite{backes2019ring}.
+
+\begin{definition}[Linkability]
+We say a PPT algorithm $\texttt{A}$  is a $(t, \epsilon, q_c, \kappa(-))$-solver of the linkability game if, within time at most $t$ and with at most $q_c$ oracle queries to $\mathcal{CO}$, $\texttt{A}$ can succeed at the following game with probability at least $\epsilon$ for any $q \geq 1$.
+\begin{enumerate}
+\item Challenge keys $\left\{(\textbf{sk}_i, \textbf{pk}_i)\right\}_{i=1}^{\kappa(\lambda)} \leftarrow \texttt{KeyGen}(1^\lambda)$ are selected and the public keys $\underline{\textbf{pk}} = \left\{\textbf{pk}_i\right\}_{i=1}^{n(\lambda)}$ are sent to $\texttt{A}$.
+
+\item $\texttt{A}$ is granted access to a corruption oracle $\mathcal{CO}$.
+
+\item $\texttt{A}$ outputs tuples $\{(m_i, \underline{\textbf{pk}}_i^\prime, \sigma_i)\}_{i=1}^{q+1}$. We say $\texttt{A}$ wins if
+\begin{enumerate}
+\item for all $i$ we have $\underline{\textbf{pk}}_i^\prime \subset \underline{\textbf{pk}}$;
+\item $\left| \bigcup_{i=1}^{q+1} \underline{\textbf{pk}}_i^\prime \right| = q$;
+\item for all $i$ we have $\texttt{Verify}(m_i, \underline{\textbf{pk}}_i^\prime, \sigma_i) = 1$; and
+\item for all $i \neq j$ we have $\texttt{Link}(\sigma_i,\sigma_j) = 0$.
+\end{enumerate}
+
+\end{enumerate}
+\end{definition}
+
+Non-frameability asserts that an adversary cannot generate a signature linking to another without knowledge of a common signing private key.
+
+\begin{definition}[Non-frameability]
+We say that a given PPT algorithm $\texttt{A}$ is a $(t, \epsilon, q_c, q_s, \kappa(-))$-solver of the frameability game if, within time at most $t$, with at most $q_c$ oracle queries to $\mathcal{CO}$, and with at most $q_s$ oracle queries to $\mathcal{SO}$, $\texttt{A}$ can succeed at the following game with probability at least $\epsilon$.
+\begin{enumerate}
+\item Challenge keys $\left\{(\textbf{sk}_i, \textbf{pk}_i)\right\}_{i=1}^{\kappa(\lambda)} \leftarrow \texttt{KeyGen}(1^\lambda)$ are selected and the public keys $\underline{\textbf{pk}} = \left\{\textbf{pk}_i\right\}_{i=1}^{n(\lambda)}$ are sent to $\texttt{A}$.
+
+\item $\texttt{A}$ is granted access to a corruption oracle $\mathcal{CO}$ and a signing oracle $\mathcal{SO}$.
+
+\item $\texttt{A}$ chooses a challenger key $\textbf{pk}$ that was not queried to $\mathcal{CO}$, an arbitrary message $m$, a ring of public keys $\underline{\textbf{pk}}^* \subset \underline{\textbf{pk}}$ containing $\textbf{pk}$, and queries $\mathcal{SO}(\textbf{pk},m,\underline{\textbf{pk}}^*) \to \sigma$.
+
+\item $\texttt{A}$ outputs a tuple $(m^\prime, \underline{\textbf{pk}}^\prime, \sigma^\prime)$ such that $\underline{\textbf{pk}}^\prime \subset \underline{\textbf{pk}}$ and $\sigma^\prime$ was not the output of any query to $\mathcal{SO}$.
+We say $\texttt{A}$ wins if
+\begin{enumerate}
+\item $\texttt{Verify}(m^\prime, \underline{\textbf{pk}}^\prime, \sigma^\prime) = 1$; and
+\item $\texttt{Link}(\sigma,\sigma^\prime) = 1$.
+\end{enumerate}
+\end{enumerate}
+\end{definition}
+
+We use a modification of the definition of linkable anonymity from \cite{backes2019ring}.
+Note that our definition is strictly weaker; while the solver can provide malicious keys in rings, it is not granted access to a corruption oracle.
+However, we implicitly model the case where the adversary is able to obtain the key image corresponding to an honest user's public key: the adversary simply requests a signature on such a key (using any ring and message compatible with the signing oracle definition), and discards all output data except the key image.
+This could also be modeled as a separate oracle, but with identical results and equivalent security.
+
+\begin{definition}[Linkable anonymity]\label{linkable-anonymity-game} Let $\texttt{A}$ be any PPT algorithm.
+We say $\texttt{A}$ is a $(t, \epsilon, \kappa)$-solver of the linkable anonymity game if it can succeed in time at most $t$ with probability at least $\epsilon$ in the following game:
+
+\begin{enumerate}
+\item (Setup phase): The challenger selects secret keys $\underline{\textbf{sk}}^* = \left\{\textbf{sk}_i^*\right\}_{i=1}^{\kappa(\lambda)} \subseteq (\mathbb{F}_p^*)^d$, computes the corresponding public keys $\underline{\textbf{pk}}^* = \left\{\textbf{pk}_i^* \mid \textbf{pk}_i^* = \textbf{sk}_i^* \circ \textbf{G}\right\}_i$, selects a bit at random $\overline{b} \in \left\{0, 1\right\}$, and sends $\underline{\textbf{pk}}^*$ to $\texttt{A}$.
+
+\item (Key phase): $\texttt{A}$ outputs a pair of indices $i_0, i_1$ such that $\textbf{pk}_{i_0}^*, \textbf{pk}_{i_1}^* \in \underline{\textbf{pk}}^*$.
+The challenger interprets $\textbf{pk}_{i_0}^*, \textbf{pk}_{i_1}^*$ as the target keys.
+
+\item (Signing phase):  $\texttt{A}$ is granted access to a signing oracle $\mathcal{SO}$.
+The signing oracle $\mathcal{SO}$ takes as input a message $m \in \left\{0, 1\right\}^*$, ring $\underline{\textbf{pk}}$, and a public key $\textbf{pk} \in \underline{\textbf{pk}}$.
+The oracle $\mathcal{SO}$ then does the following.
+\begin{itemize}
+\item If $\left\{\textbf{pk}_{i_0}^*, \textbf{pk}_{i_1}^*\right\} \not\subseteq \underline{\textbf{pk}}$ or $\textbf{pk} \notin \underline{\textbf{pk}}$*, $\mathcal{SO}$ produces as output the distinguished failure symbol $\bot$.
+
+\item Otherwise, if $\textbf{pk} \notin \left\{\textbf{pk}_{i_0}^*, \textbf{pk}_{i_1}^*\right\}$, then $\mathcal{SO}$ retrieves $\textbf{sk} \in \underline{\textbf{sk}}^*$ such that $\textbf{pk} = \textbf{sk}  \circ \textbf{G}$, and outputs $\sigma \leftarrow \texttt{Sign}(m, \underline{\textbf{pk}}, \textbf{sk})$.
+
+\item Otherwise, $\textbf{pk} = \textbf{pk}_{i_c}^*$ for a bit $c$.
+The bit $c^\prime = (1-c)\overline{b} + c(1-\overline{b})$ is computed and the oracle outputs $\sigma \leftarrow \texttt{Sign}(m, \underline{\textbf{pk}}, \textbf{sk}_{i_{c^\prime}}^*)$.
 \end{itemize}
 
-$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
-$A,B,C,D,\{X_j\},\{Y_j\}$ \\
+\item (Decision phase): $\texttt{A}$ outputs a bit $\overline{b}^\prime$, succeeding if $\overline{b}^\prime = \overline{b}$.
+\end{enumerate}
+\end{definition}
 
-$\underline{\mathcal{V} \to \mathcal{P}:}$ \\
-$\xi \in \{0,1\}^*$ \\
+\subsection{Security results}\label{def:results}
+Here we present security results for the $d$-CLSAG construction in Definition \ref{def:clsag}. Proofs are included in Appendix \ref{app:proofs}.
 
-$\underline{\mathcal{P}(\xi):}$
+\begin{theorem}[Correctness]
+The $d$-CLSAG construction is perfectly correct.
+\end{theorem}
+This result follows by inspection, so we do not present a proof here.
+
+To show that $d$-CLSAG is unforgeable with respect to Definition \ref{def:unforgeability}, we prove that a solver of the unforgeability game is also a solver of the $k$-OMDL game.
+\begin{theorem}[Unforgeability]\label{thm:unforgeability}
+Let $d, q_h, q_c, q_s \in \mathbb{N}$  and let $(p,\mathbb{G},G)$ be some group parameters.
+If a $(t, \epsilon, q_h, q_c, q_s, \kappa(-))$-forger of the $d$-CLSAG construction exists, then a $(2t, \epsilon^\prime)$-solver of the $k$-OMDL problem in $\mathbb{G}$ exists for $k = d\cdot q_c + d - 1$, where $\epsilon^\prime \geq \epsilon\left(\frac{\epsilon}{q_c} - \frac{1}{2^\eta}\right) - p^{-1}$.
+\end{theorem}
+
+To show that the construction is linkable, we prove that a solver of the linkability game is also a solver of the unforgeability game.
+\begin{theorem}[Linkability]\label{thm:linkability}
+If a $(t, \epsilon, q_c, \kappa(-))$-solver of the linkability game exists for the $d$-CLSAG implementation, then a $(t, \epsilon, 0, q_c, 0, \kappa(-))$-forger exists.
+\end{theorem}
+
+Non-frameability will follow similarly.
+\begin{theorem}[Non-frameability]\label{thm:frameability}
+If there exists a $(t, \epsilon, q_c, q_s, \kappa(-))$-solver of the non-frameability for the $d$-CLSAG construction, then a $(t, \epsilon, 0, q_c, q_s, \kappa(-))$-forger exists.
+\end{theorem}
+
+To show that the construction has linkable anonymity, we prove that a solver of the linkable anonymity game is a solver of the DDH game.
+\begin{theorem}[Linkable anonymity]\label{thm:anonymity}
+If there exists a $(t, \epsilon, \kappa)$-solver of the linkable anonymity game, then a $(t^\prime, \epsilon^\prime, \kappa^\prime)$-solver of the DDH game exists.
+\end{theorem}
+
+\section{Applications}\label{sec:applications}
+
+\subsection{Single-asset ring confidential transactions}\label{sec:ringct}
+It is possible to use $2$-CLSAG as a replacement for MLSAG signatures in signer-ambiguous confidential transaction models for equivalent functionality.
+For example, the Monero protocol currently uses MLSAG signatures for two different transaction types: full and simple.
+
+Full transactions are only used when spending a single input.
+They leverage the fact that in a balanced transaction, the difference between input and output commitments is a commitment to zero; the signer can therefore use such differences as the second component of key vectors in the signature and sign using the known secret key at the signing index.
+
+Simple transactions are used when spending multiple inputs.
+Each spent input requires a separate signature, as a naive extension of full transactions presents an index linking issue.
+The signer first generates auxiliary commitments for each spent input using the same value but a different blinder.
+This means it is possible to use the difference between input and auxiliary commitments as a commitment to zero for the purpose of signing.
+By choosing all blinders at random except one, the signer can construct the auxiliary commitments such that the difference between auxiliary and output commitments is zero, proving balance.
+
+Both transaction types can be constructed with $2$-CLSAG signatures since linkability is not considered for the second key component used in the transaction protocols.
+
+\subsection{Multi-asset ring confidential transactions}\label{sec:marct}
+
+It is possible to use a straightforward $d$-CLSAG construction to accommodate transactions spending $d-1$ \textit{types} or \textit{colors} of assets separately within the same transaction and signature.
+To do so, transaction outputs are extended to have a separate commitment to each asset type value.
+When spending an output, either a full or simple transaction (discussed above) is used; we simply copy the method used to compute commitment public keys in the signature to additional dimensions of the $d$-CLSAG signature, using only the commitments for a particular asset type in each.
+This separation ensures that the transaction balances in each asset type separately, while taking advantage of the scaling benefits of $d$-CLSAG compared to the equivalent MLSAG signature construction.
+
+\subsection{Unmixable colors}\label{sec:unmixable}
+We informally describe an example of such a transaction model using two unmixable colors using $3$-CLSAG.
+Let $(\texttt{Prove}, \texttt{Ver})$ be a zero-knowledge sound range proving scheme, such as that described in \cite{bulletproofs}, and let $(\texttt{Com}, \texttt{Open})$ be a Pedersen commitment scheme such that $\texttt{Com}(r,v) = rG + v G^\prime$.
+
+For the sake of this example, we define a public trading key to be a tuple $(X, C, D, P)$ where $X, C, D \in \mathbb{G}$, $C$ and $D$ are amount commitments and $P$ is a batched range proof from $\texttt{Prove}$ covering the values of both $C$ and $D$.
+Here, $C$ and $D$ play the role of the $Z_j$ points, and $P$ is additional data required for the transaction protocol.
+
+We define a transaction key to be a tuple $(m, \textbf{Q}, \textbf{O}, (f_C, f_D), \sigma, \textit{aux})$ where $\textbf{Q}$ is a ring of $n$ public trading keys  $\textbf{Q} = \left\{(X_i, C_i, D_i, P_i)\right\}_{i=1}^{n}$, $\textbf{O}$ is a set of $n^\prime$ output public trading keys $\textbf{O} = \left\{(X_i^\prime, C_i^\prime, D_i^\prime, P_i^\prime)\right\}_{i=1}^{n^\prime}$, $f_C$ is a plaintext list of fees to be paid from $C$, $f_D$ is a plaintext list of fees to be paid from $D$, and $\sigma$ is a $3$-CLSAG signature.
+We say a transaction key is valid if the following are satisfied:
 \begin{itemize}
-\item Define $\left\{f_{j,i}\right\}_{i=1,j}^{n-1,m-1}$ such that $f_{j,i} \equiv \sigma_{j,i}\xi + a_{j,i}$.
-\item Define $z_A \equiv r_A + \xi r_B$ and $z_C \equiv \xi r_C + r_D$.
-\item Define $z \equiv r \xi^m - \sumj \rho_j \xi^j$.
+\item every input ring member $(X_i, C_i, D_i, P_i) \in \textbf{Q}$ has a valid range proof $P_i$ so $\texttt{Ver}(P_i) = 1$; and
+
+\item every output range proof $P_k^\prime$ is valid so $\texttt{Ver}(P_k^\prime)=1$; and
+
+\item for the ring \[\textbf{pk} = \begin{pmatrix} X_1 & X_2 & \cdots & X_n \\ Z_1 & Z_2 & \cdots & Z_n \\ Z_1^\prime & Z_2^\prime & \cdots & Z_n^\prime\end{pmatrix}\] where each $Z_i = C_i - f_C G^\prime - \sum_k C_k^\prime$ and each $Z_i^\prime = D_i - f_D G^\prime - \sum_k D_k^\prime$,  $\texttt{Verify}(m, \underline{\textbf{pk}}, \sigma) = 1$.
 \end{itemize}
 
-$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
-$\{f_{j,i}\}_{j=0,i=1}^{m-1,n-1},z_A,z_C,z$
-\end{minipage}}
-\caption{Sigma protocol for $\mathcal{R}_{\text{link}}$}
-\label{fig:link}
-\end{figure}
+This $3$-CLSAG signature demonstrates knowledge of the discrete logarithm of some $x_\ell$, knowledge of the opening information for the input and output commitments, and that the transaction amounts balance  with the fees $f_C$ and $f_D$.
+After all, when the amounts in $C_\ell$ and $D_\ell$ balance with the fees $f_C$ and $f_D$ together with the sum of the amounts in each $C_k^\prime$ and $D_k^\prime$, and when the signer knows all the openers for all these commitments, $Z_\ell$ and $Z_\ell^\prime$ can be regarded as usual public keys with base $G$ whose secret key is known by the signer.
 
-\begin{figure}[htbp]
-\centering
-\fbox{\begin{minipage}{0.95\textwidth}
-$\underline{\mathcal{V}_{\text{link}}(\{M_i\},J):}$
+Unfortunately, this model does not allow for exchanging amounts of the first color with amounts of the second color.
+In the next section, we present another toy model that allows for transferring between colors at a fixed/pegged exchange rate.
+
+\subsubsection{Mixable colors}\label{sec:mixable}
+We modify the previous example to use a $2$-CLSAG.
+Consider the canonical example of colored currency with a fixed peg between two colors: dollars and pennies with a $100:1$ exchange rate between them.
+Define an exchange rate by determining a constant $\xi$ and some constants $\gamma_C, \gamma_D$ on $\left\{1, 2, \ldots, 2^{\xi - 1}\right\}$, (in this example, $\gamma_C = 1$ and $\gamma_D = 100$).
+
+As before, we define a public trading key to be a tuple $(X, C, D, P)$ and a transaction key to be a tuple $(m, \textbf{Q}, \textbf{O}, (f_C, f_D), \sigma, \textit{aux})$.
+We interpret these identically as in the previous step, except using $2$-CLSAG signatures instead of $3$-CLSAG signatures, and of course we compute them differently.
+We say a simple transaction key is valid if the following are satisfied:
 \begin{itemize}
-\item For $0 \leq j < m$, let $f_{j,0} \equiv \xi - \sum_{i=1}^{n-1} f_{j,i}$.
-\item Accept if and only if:
-\begin{eqnarray}
-A + \xi B &=& \com(f,z_A) \label{eqn:ab} \\
-\xi C + D &=& \com(f(\xi-f),z_C) \label{eqn:cd} \\
-\sumk M_k \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG &=& 0 \label{eqn:x} \\
-U \sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ &=& 0 \label{eqn:y}
-\end{eqnarray}
-\end{itemize}
-\end{minipage}}
-\caption{Sigma protocol for $\mathcal{R}_{\text{link}}$ (continued)}
-\label{fig:link_2}
-\end{figure}
+\item every input ring member $(X_i, C_i, D_i, P_i) \in \textbf{Q}$ has a valid range proof $P_i$ so $\texttt{Ver}(P_i) = 1$; and
 
-Observe that this protocol can be made non-interactive using the Fiat-Shamir heuristic, where the verifier challenge is produced using a collision-resistant hash function (modeling a random oracle) and the proof transcript \cite{fiatshamir}.
+\item every output range proof $P_k^\prime$ is valid so $\texttt{Ver}(P_k^\prime)=1$; and
 
-We will show that the sigma protocol is complete, sound, and zero-knowledge, the precise definitions of which are common and found in \cite{groth}.
-Informally, we require the protocol be:
-\begin{itemize}
-\item \textit{Perfectly complete}: Given knowledge of a witness to a statement in the proof relation, an honest prover can always convince an honest verifier of the validity of the witness.
-\item \textit{Special sound}: Given a statement in the proof relation, if a prover can answer multiple honest verifier challenges correctly, then it is possible to extract a witness for this statement.
-\item \textit{Special honest-verifier zero knowledge}: Given any statement and verifier challenge, it is possible to simulate a transcript that is accepted by an honest verifier without knowledge of a corresponding witness.
+\item for the modified ring \[\textbf{pk} = \begin{pmatrix} X_1 & X_2 & \cdots & X_n \\ Z_1 & Z_2 & \cdots & Z_n\end{pmatrix}\] where each $Z_i = \gamma_C (C_i - f_C G^\prime - \sum_k C_k^\prime) + \gamma_D ( D_i - f_D G^\prime - \sum_k D_k^\prime)$, the signature $\sigma$ passes the $2$-CLSAG verification, $\texttt{Verify}(m, \underline{\textbf{pk}}, \sigma) = 1$ .
 \end{itemize}
 
-\begin{theorem}
-The protocol in Figures \ref{fig:link} and \ref{fig:link_2} is perfectly complete, special honest-verifier zero knowledge, and $(m+1)$-special sound.
-\end{theorem}
+Unlike the previous example, this example allows for the fixed exchange rate between colors determined by $\gamma_C$ and $\gamma_D$.
 
-\begin{proof}
-The proof follows similarly to that of \cite{bootle}.
+\section*{Acknowledgments}
+The authors wish to thank the anonymous reviewers of an earlier version of this paper for their comments and valuable suggestions.
 
-% Completeness
-We first show perfect completeness.
-Suppose the verifier receives a proof generated by an honest prover.
-Equation \ref{eqn:ab} holds using the identity $$\sumi \sigma_{j,i} = 1$$ for all $0 \leq j < m$.
-Equation \ref{eqn:cd} follows similarly, using the identity $$\left(\sigma_{j,i}\right)^2 = \sigma_{j,i}$$ for all $0 \leq j < m$.
-To show Equation \ref{eqn:x} holds:
-\begin{eqnarray*}
-&& \sumk M_k \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG \\
-&=& \sumk M_k p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}M_k + \rho_jG \right) - zG \\
-&=& \sumk M_k \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \rho_jG - zG \\
-&=& \sumk M_k \xi^m \delta(l,k) - \sumj \xi^j \rho_jG - \left( r\xi^m - \sumj \rho_j\xi^j \right)G \\
-&=& \xi^mrG - \sumj \xi^j \rho_jG - \xi^mrG + \sumj \xi^j \rho_jG \\
-&=& 0
-\end{eqnarray*}
-Equation \ref{eqn:y} follows similarly:
-\begin{eqnarray*}
-&& U \sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ \\
-&=& U \sumk p_k(\xi) - \sumj \xi^j \left( U \sumk p_{k,j} + \rho_jJ \right) - zJ \\
-&=& U \sumk \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \rho_jJ - zJ \\
-&=& U \sumk \xi^m \delta(l,k) - \sumj \xi^j \rho_jJ - \left( r\xi^m - \sumj \rho_j\xi^j \right)J \\
-&=& \xi^mU - \sumj \xi^j \rho_jG - \xi^mrJ + \sumj \xi^j \rho_jG \\
-&=& 0
-\end{eqnarray*}
-since $J = r^{-1}U$ in a valid proof.
-Hence the protocol is perfectly complete.
+\bibliographystyle{splncs04}
+\bibliography{bibliography}
 
-% SHVZK
-We next show that the protocol is special honest-verifier zero knowledge.
-To do so, we construct a simulator that, given a random verifier challenge $\xi$, can construct a proof transcript with identical distribution to a valid proof.
+\appendix
 
-First, observe that the simulator presented in the proof of Lemma 1 in \cite{bootle} translates identically to our setting.
-If the simulator chooses $B \in \G$ uniformly at random, the cited lemma assures us a valid simulation of the proof elements $A,C,D,z_A,z_C,\{f^{(u)}_{j,i \neq 0}\}$; we may compute each $f^{(u)}_{j,0}$ from this.
-Further, in a valid proof, $B$ is independent and uniformly distributed as well.
+\section{Security proofs}\label{app:proofs}
+We now prove the security theorems from the main text.
 
-The proof elements $\{X_j\}_{j=1}^{m-1}$ and $\{Y_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof since the set $\{\rho_j\}$ is random and the discrete logarithm problem in $\G$ is hard, so the simulator may choose these uniformly at random.
-The verification checks require that $X_0$ and $Y_0$ be uniquely determined by the other elements in the corresponding sets in both real proofs and by the simulator.
+\subsection{Unforgeability}\label{app:unforgeability}
+Before we can prove that $d$-CLSAG is unforgeable, we must describe the oracles in greater detail, and produce an algorithm consistent with the forking lemma.
 
-Finally, $z$ is uniformly distributed in valid proofs given random $\xi$, so the simulator may choose it uniformly at random.
-Hence the construction is special honest verifier zero-knowledge.
+\subsubsection{Oracles}
+Random oracle queries made by $\texttt{A}$ are handled by looking to a random tape $\textbf{h}$ available to the simulator to generate hashes for new queries made to the oracle $\mathcal{H}^s$.
+These are stored in a hash table for consistency in later queries.
+We assume whatever algorithm is executing $\texttt{A}$ in a black box has pre-generated a set of private-public key pairs for use in simulating a corruption oracle $\mathcal{CO}$ for $\texttt{A}$.
+This leaves only the signing oracle, which is simulated through back-patching in the following way.
 
-% Soundness
-It remains to show that the protocol is $(m+1)$-special sound, where $m > 1$.
-To show this, we construct an extractor that, given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness.
+The simulator reserves the next random oracle query on the random tape $\textbf{h}$ to select $c_{\ell+1}$ for back-patching.
+The random signature data $\alpha$ and $\left\{s_i\right\}_{i \neq \ell}$ are sampled as usual, and each challenge $c_{i+1}$ for $i \neq \ell$ is simulated from $\textbf{h}$ as described before and stored in a hash table.
+After all challenges are computed, the simulator compute the group points $L_\ell, R_\ell$, and back-patches their hash table to force $\mathcal{H}^s(\underline{\textbf{pk}} \mid \mid m \mid \mid L_\ell \mid \mid R_\ell) \leftarrow c_{\ell+1}$.
 
-Suppose that for a given statement, we have a set of $m+1$ distinct verifier challenges $\{\xi_e\}_{e=0}^m$ corresponding to unique valid responses of this form:
-$$\left\{ \{f^{(e)}_{j,i}\}, \{z_e\} \right\}_{e=0}^m$$
-From the $3$-special soundness in \cite{bootle} and $m > 1$ we have valid extractions $\{\sigma_{j,i}\}_{j,i=0}^{m-1,n-1}$ and $\{a_{j,i}\}_{j,i=0}^{m-1,n-1}$, and the Pedersen binding property ensures that (with high probability) we have:
-$$f^{(e)}_{j,i} = \sigma_{j,i}\xi_e + a_{j,i}$$
-for all $e \in [0,m]$.
-Using the extracted values, compute
-$$p_k(\xi) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}\xi + a_{j,k} \right)$$
-for all $k \in [0,N)$.
-Extraction of $\{\sigma_{j,i}\}_{j,i=0}^{m-1,n-1}$ immediately yields the signing index $l$.
+\subsubsection{Forgeries}
+A forgery challenger can play the unforgeability game with $\texttt{A}$ in a black box, can simulate $\mathcal{SO}$ and $\mathcal{CO}$, and can check whether the purported forgeries by $\texttt{A}$ are successful; the challenger simply keeps a history of all oracle queries, and computes key images of corrupted keys to check.
 
-We have seen that $p_k$ is of degree $m$ only when $k = l$.
-Hence there exist coefficients $\{\overline{X}_j,\overline{Y}_j\}_{j=0}^{m-1}$, computed uniquely from the statement and extracted values, such that Equations \ref{eqn:x} and \ref{eqn:y} are of the following form:
-\begin{eqnarray*}
-\xi^m M_l + \sumj \xi^j\overline{X}_j &=& zG \\
-\xi^m U + \sumj \xi^j\overline{Y}_j &=& zJ \\
-\end{eqnarray*}
+This definition allows the attacker to attempt a successful forgery by re-using messages, rings, or indices from previous $\mathcal{SO}$ queries (but not by reusing queries \textit{per totum}).
+It also allows key images that are unrelated to the ring members and it allows key images found in previous $\mathcal{SO}$ queries.
+Hence, proving the implementation of Definition \ref{def:clsag} unforgeable under this definition implies these attempts will fail.
+A forger gains no advantage by re-using messages (or rings or indices) that have already been used in $\mathcal{SO}$.
+The forger gains no advantage by including key images that are unrelated to the ring members, or by using the key images from $\mathcal{SO}$ queries.
 
-Construct a Vandermonde matrix $V$ where the $e$ row is the vector $(1,\xi_e,\ldots,\xi^m_e)$.
-Since all $\xi_e$ are distinct, the rows of $V$ span $\F^{m+1}$; hence there exist weights $\{\theta_e\}_{e=0}^m$ such that the resulting linear combination of rows produces the vector $(0,\ldots,0,1)$.
-That is, $\sum_{e=0}^m \theta_e\xi_e^j = \delta(j,m)$.
+Moreover, consider some $(m, \underline{\textbf{pk}}^\prime, \sigma)$ output by an alleged forger $\texttt{A}$.
+If the scheme is unforgeable, one of the above conditions must fail.
+If the signature passes verification, one of the first two conditions must fail, so any valid signature must violate one of these first two conditions.
+If the first condition is violated, the forger is merely attempting to pass off an oracle signature or some previously computed signature as their own.
+If the second condition is violated, then $\mathfrak{T}$ corresponds to a corrupted ring member (in which case $\texttt{A}$ knows the key) or corresponds to none of the ring members.
 
-For each of the previous two equations, we can therefore build a linear combination over $e$.
-For the first:
-$$M_l = \sum_{e=0}^m \theta_e\xi_e^m M_l + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{X}_j \right) = \left( \sum_{e=0}^m \theta_e z_e \right) G$$
-Hence we extract $r \equiv \sum_{e=0}^m \theta_e z_e$.
-For the second:
-$$U = \sum_{e=0}^m \theta_e\xi_e^m U + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{X}_j \right) = \left( \sum_{e=0}^m \theta_e z_e \right) J$$
-This implies that $rJ = U$, as required.
-Hence the protocol is $(m+1)$-special sound, which completes the proof.
+That is to say: if $\texttt{A}$ produces a valid signature, then either $\texttt{A}$ knows the key or the key image does not correspond to a ring member.
+
+Moreover, presume that $\texttt{A}$ produces a message $m$, a ring $\underline{\textbf{pk}}$, and a signature $\sigma$ that passes verification, and yet such that the key image $\mathfrak{T} \in \sigma$ does not correspond to any ring member.
+Under the random oracle model, $\texttt{A}$ cannot simultaneously satisfy the verification equations
+\begin{align*}
+c_{2} =& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid m \mid \mid s_1 G + c_1 W_1 \mid \mid s_1 H_1 + c_1 \mathfrak{W}) \\
+\vdots & \\
+c_{n} =& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid m \mid \mid s_{n-1} G + c_{n-1} W_{n-1} \mid \mid s_{n-1} H_{n-1} + c_{n-1} \mathfrak{W}) \\
+c_{1} =& \mathcal{H}^s_0(\underline{\textbf{pk}} \mid \mid m \mid \mid s_{n} G + c_{n} W_{n} \mid \mid s_{n} H_{n} + c_{n} \mathfrak{W})
+\end{align*}
+except with negligible probability, because the discrete logarithm of $\mathfrak{W}$ cannot be written as $x_i \mathcal{H}^p(X_i)$ for any $i$.
+We conclude that $\texttt{A}$ must have known the discrete logarithm of the signing key to produce this signature.
+
+\subsubsection{Forking lemma}
+We describe the necessary forking algorithm below, and refer the reader to \cite{bellare} for a proof of this lemma, which demonstrates that if executing some $\texttt{A}$ has non-negligible acceptance probability, then forking $\texttt{A}$ does as well.
+Since all queries before the $(j^*)^{th}$ query are identical in both transcripts, the input of the $(j^*)^{th}$ query is also identical.
+Since oracle queries $h_{j^*}^{\prime}, h_{j^*+1}^{\prime}, \ldots$ are newly sampled upon receiving the first output from $\texttt{A}$, the queries $h_{j^*} \neq h_{j^*}^\prime$ except with negligible probability.
+All subsequent computations in the signature that are common in both transcripts will have the same results only with negligible probability.
+Note that a forger as we have defined is not directly compatible with the forking lemma; the output is some $y = (m, \textbf{pk}, \sigma)$ and no $\textit{idx}$ is included.
+However, without loss of generality, we can execute $\texttt{A}$ in a black box that extracts from the transcript of $\texttt{A}$ some $\textit{idx} = (i^*, j^*)$ for $j^* = j(i^*)$ in the following way.
+
+For each query for any $c_{i+1}$ that appears in the successful forgery, there exists a corresponding index $j(i)$ that satisfies $c_{i+1} = h_{j(i)}$.
+The black box executing $\texttt{A}$ looks at the transcript and extracts the index pair $\textit{idx} = (i^*, j^*)$ that indicates where in the random oracle transcript we can find the very first oracle query made by $\texttt{A}$ to $\mathcal{H}^s$ for some challenge used in signature verification \[c_{i^*+1} = \mathcal{H}^s_0\left(\underline{\textbf{pk}} \mid \mid m \mid \mid L_{i^*} \mid \mid R_{i^*}\right)\] used in the successful forgery.
+Such a pair $(i^*, j^*)$ can be found by merely inspecting the transcript, so the algorithm wrapping $\texttt{A}$ can output $(\textit{idx}, y)$ without harming its advantage.
+
+Without loss of generality, we can assume that $\texttt{A}$ has been appropriately wrapped so is compatible with the forking lemma without impacting its advantage.
+
+Forking the forger preserves the input to the query $(\underline{\textbf{pk}}, m, L_{i^*}, R_{i^*})$ but does not preserve the challenge $c_{i^*+1}$.
+Moreover, each $c_{i+1}$ used in the signature verification is computed by $\texttt{A}$ by querying $\mathcal{H}^s$  in the transcript of $\texttt{A}$ leading to a successful forgery; the outputs of these queries cannot be guessed except with negligible probability, and so the oracle must have actually been queried  (see, for example, \cite{liu}).
+Of course, although the index $i^*$ may not have been decided by $\texttt{A}$ when the query was made, but the index $i^*$ is assigned before the end of the transcript.
+
+That is to say, a forked forger presents two forgeries with the same ring, message, and $\textit{idx}$ except with negligible probability, with the pair of points $L_{i^*}, R_{i^*}$ common in both transcripts.
+
+A forking algorithm $\mathcal{F}^\texttt{A}$ satisfying Lemma \ref{lem:fork} works in the following way.
+
+\begin{enumerate}
+\item $\mathcal{F}$ takes as input some $x$ and $\mathcal{F}$ selects the random tape for $\texttt{A}$.
+
+\item $\mathcal{F}$ selects some $\textbf{h} = (h_1, \ldots, h_q)$ at random by flipping coins, and $\mathcal{F}$ executes $y_\texttt{A} \leftarrow \texttt{A}(x,\textbf{h})$.
+
+\item If $y_{\texttt{A}} = \bot_{\texttt{A}}$, then $\mathcal{F}$ outputs $\bot_{\mathcal{F}}$ and terminates.
+Otherwise, $y_{\texttt{A}} = (\textit{idx}, y)$ for some $\textit{idx}=(i^*,j^*)$ and some output $y$ and $\mathcal{F}$ selects new oracle queries $h_{j^*}^\prime, h_{j^*+1}^\prime, \ldots, h_q^\prime$, and glues the hash challenges together: $$\textbf{h}^\prime = (h_1, \ldots, h_{j^*-1}, h_{j^*}^\prime, h_{j^*+1}^\prime, \ldots, h_q^\prime)$$
+
+\item If $h_{j^*} = h_{j^{*}}^\prime$, then $\mathcal{F}$ outputs $\bot_{\mathcal{F}}$ and terminates.
+Otherwise, $h_{j^*} \neq h_{j^{*}}^\prime$ and $\mathcal{F}$ executes $y_\texttt{A}^\prime \leftarrow \texttt{A}(x,\textbf{h}^\prime)$.
+
+\item If $y_{\texttt{A}}^\prime = \bot_{\texttt{A}}$, then $\mathcal{F}$ outputs $\bot_{\mathcal{F}}$ and terminates.
+Otherwise, $y_{\texttt{A}}^\prime = (\textit{idx}^{\prime}, y^\prime)$.
+If $\textit{idx} \neq \textit{idx}^\prime$, $\mathcal{F}$ outputs $\bot_{\mathcal{F}}$ and terminates.
+Otherwise, $\mathcal{F}$ outputs the tuple $(\textit{idx}, y, \textbf{h}, y^\prime, \textbf{h}^\prime)$.
+\end{enumerate}
+
+We note that $\mathcal{F}^{\texttt{A}}$ executed in a black box can be fed the oracle queries $\textbf{h}$ and $\textbf{h}^\prime$ and so these can be assumed to be output as well without loss of generality or impacting acceptance probability.
+Of course, if $\texttt{A}$ runs in time at most $t$, $\mathcal{F}^{\texttt{A}}$ runs in time at most $2t+s$ where $s$ denotes the time it takes $\mathcal{F}^{\texttt{A}}$ to select the random tape for $\texttt{A}$, select the oracle query sequences $\textbf{h}$ and $\textbf{h}^\prime$, perform lookups in hash tables to maintain oracle query consistency, and outputting the results.
+These times are all negligible, so $\mathcal{F}^{\texttt{A}}$ runs in $O(2t)$ time.
+
+We are now in a position to present the proof.
+
+\begin{proof}[Unforgeability]
+We construct a master algorithm $\texttt{M}$ that plays the $k$-OMDL game for $k=2d\cdot q_c + d-1$ that operates in the following way.
+Recall that $\texttt{M}$ is granted access to up to $k$ queries at a discrete logarithm oracle.
+\begin{enumerate}
+
+\item $\texttt{M}$ receives group parameters $(p, \mathbb{G}, G)$ and a list of target group elements $G_1, \ldots, G_{k+1}$ from the $k$-OMDL challenger.
+
+\item $\texttt{M}$ blocks $(G_1, \ldots, G_{k+1})$ into $d$-length blocks and reserve them for public keys using the following equations.
+\begin{align*}
+\textbf{pk}_1 =& (G_1, \ldots, G_d) \\
+\textbf{pk}_2 =& (G_{d+1}, \ldots, G_{2d}) \\
+\vdots & \\
+\textbf{pk}_{2q_c + 1} =& (G_{2q_c d+1}, \ldots, G_{k+1})
+\end{align*}
+
+\item $\texttt{M}$ uses $\left\{\textbf{pk}_i\right\}_{i=1}^{2q_c + 1}$ as input for $\mathcal{F}^{\texttt{A}}$, responding to corruption oracle queries made by $\mathcal{F}^{\texttt{A}}$ for a key $\textbf{pk}_i$ by querying $\mathcal{CO}$ directly with each coordinate and responding with the result.
+Denote $X_i := G_{(i-1)d + 1}$ and $Z_{i,j} := G_{(i-1)d + 1 + j}$ for consistency with our earlier notation.
+
+\item If $\mathcal{F}^{\texttt{A}}$ outputs $\bot$, so does $\texttt{M}$ and $\texttt{M}$ terminates.
+Otherwise, $\mathcal{F}^{\texttt{A}}$ succeeds executing $\texttt{A}$ twice, each time taking no more than $q_c$ queries to corrupt $d$-dimensional keys, resulting in no more than $2\cdot d\cdot q_c$ queries to the discrete logarithm oracle $\mathcal{CO}$.
+$\mathcal{F}^{\texttt{A}}$ produces $(\textit{idx}, y, \textbf{h}, y^\prime, \textbf{h}^\prime)$ where $y = (m, \underline{\textbf{pk}}, \sigma)$ and $y^\prime = (m, \underline{\textbf{pk}}, \sigma^\prime)$ are forgeries using oracle queries $\textbf{h}$ and $\textbf{h}^\prime$, respectively, and $\textit{idx} = (i^*, j^*)$ as described previously.
+
+The messages and rings are identical in these forgeries because they must have been selected before the first challenge query, except with negligible probability. So $\texttt{M}$ can parse
+\begin{align*}
+y =& (m, \underline{\textbf{pk}}, \sigma) & \sigma =& (c_1, s_1, \ldots, s_n, \mathfrak{T}, \left\{\mathfrak{D}_j\right\}_j) \\
+y^\prime =& (m, \underline{\textbf{pk}}, \sigma^\prime) & \sigma^\prime =& (c_1^\prime, s_1^\prime, \ldots, s_n^\prime, \mathfrak{T}^\prime, \left\{\mathfrak{D}_j^\prime\right\}_j)\end{align*} except with negligible probability (in which case $\texttt{M}$ outputs $\bot_{\texttt{M}}$ and terminates).
+
+\item In the transcript of $\mathcal{F}^{\texttt{A}}$, $\texttt{M}$ can find $c_{i^*+1} = \textbf{h}_{j^*}$ and in the second transcript $c_{i^*+1} = \textbf{h}^\prime_{j^*}$ for some $\textbf{h}_{j^*} \neq \textbf{h}^\prime_{j^*}$, except with negligible probability (in which case $\texttt{M}$ outputs $\bot_{\texttt{M}}$ and terminates).
+
+\item $\texttt{M}$ parses the random oracle transcript to find the query yielding the signature challenge  $c_{i^*+1} \leftarrow \mathcal{H}^s(\underline{\textbf{pk}} \mid \mid m \mid \mid L_{i^*} \mid \mid R_{i^*})$.
+Both transcripts match until this line, and the oracle responses stored in $c_{i^*+1}$ in these transcripts don't match (i.e.\ $\textbf{h}_{j^*} \neq \textbf{h}^\prime_{j^*}$ except with negligible probability).
+The algorithm  $\texttt{M}$ parses the first transcript to look for constants $s_{i^*}, c_{i^*}$ and the group point $W = \mu_X X_{i^*} + \sum_j \mu_j Z_{i^*, j}$ such that $L_{i^*} = s_{i^*} G + c_{i^*} W$.
+From the second transcript, and with the same $L_{i^*}$ and $W$, $\texttt{M}$ parses to find constants $s_{i^*}^\prime, c_{i^*}^\prime$ such that $L_{i^*} = s_{i^*}^\prime G + c_{i^*}^\prime W$.
+
+\item If $\mu_X = 0$ then $\texttt{M}$ outputs $\bot$ and terminates. Otherwise, $\texttt{M}$ computes the discrete logarithm
+$$w = \frac{s_{i^*}^\prime - s_{i^*}}{c_{i^*} - c_{i^*}^\prime}$$ without querying $\mathcal{CO}$.
+
+\item $\texttt{M}$ makes up to $d-1$ queries to $\mathcal{CO}$ to find the discrete logarithms of the elements of any $(d-1)$-subset of $\left\{X_{i^*}, Z_{i^*, 1}, \ldots, Z_{i^*, d-1}\right\}$.
+
+\item $\texttt{M}$ uses $w$ to solve for the final discrete logarithm.
+
+\item $\texttt{M}$ outputs the $2 \cdot d \cdot q_c$ corruptions queries and the $d$-dimensional vector $(x_{i^*}, z_{i^*, 1}, \ldots, z_{i^*, d-1})$, totaling $k+1$ discrete logarithms.
+\end{enumerate}
+
+Note that if $\texttt{M}$ does not terminate and output $\bot$, then $\texttt{M}$ makes up to $2\cdot d \cdot q_c$ queries to $\mathcal{CO}$ for $\mathcal{F}^{\texttt{A}}$ and makes an an additional $d-1$ queries to $\mathcal{CO}$, and yet produces as output $d \cdot (q_c + 1) > d \cdot q_c + d-1$ discrete logarithms, \textit{i.e.}\ $\texttt{M}$ successfully plays the $k$-OMDL game for $k = 2\cdot d\cdot q_c + d-1$.
+Furthermore,  if $\texttt{M}$ already corrupted these discrete logarithms, even fewer queries could be made, tightening $k$ and making $\texttt{M}$ a more powerful solver.
+
+Also note that, as previously mentioned, since the map $(x, z_1, \ldots, z_{d-1}) \mapsto w$ is collision resistant, $\texttt{M}$ can skip steps and guess $w$ in step $7$ only with negligible success.
+
+Recall that $\mathcal{F}^{\texttt{A}}$ takes time $O(2t)$ to execute.
+$\texttt{M}$ executes $\texttt{F}^{\texttt{A}}$ and then performs parsing of transcripts and some additional computations, so $\texttt{M}$ takes time $O(2t+s^\prime)$ for some $s^\prime$ due to parsing and processing transcript data.
+
+The additional time $s^\prime$ is due to:
+\begin{itemize}
+\item Lookup time in a hash table for each $\mathcal{CO}$ query, each random oracle query, and each extraction of a value from the random tapes $\textbf{h}$, $\textbf{h}^\prime$ by $\mathcal{F}^{\texttt{A}}$ throughout the transcript.
+\item Parsing and constructing keys in step $2$.
+\item Parsing purported forgeries in step $3$.
+\item Parsing transcripts and computing multi-exponentiations to verify equations in step $5$.
+\item Computing the discrete logarithm $w$ using field arithmetic in Step $6$.
+\item Computing the discrete logarithm of the challenge key using field arithmetic in step $8$.
+\item Outputting the results.
+\end{itemize}
+All of these are negligible, so $\texttt{M}$ also takes time $O(2t)$.
+
+To complete the proof using $\texttt{M}$, suppose $d, q_h, q_c, q_s$ satisfy the hypotheses and let $\texttt{A}$ be a $(t, \epsilon, q_h, q_c, q_s, \kappa)$-forger of the $d$-CLSAG scheme, and let $\mathcal{F}^{\texttt{A}}$ be the forking algorithm for $\texttt{A}$.
+$\texttt{M}$ terminates and outputs $\bot$ in steps $3$ and $6$ only; otherwise, $\texttt{M}$ succeeds at the $k$-OMDL game.
+Hence, if $E_3$ is the event that $\texttt{M}$ outputs $\bot$ in step $3$ and $E_6$ is the event that $\texttt{M}$ outputs $\bot$ in step $6$, then $E_3, E_6$ are disjoint and the acceptance probability for $\texttt{M}$ is $1 - \mathbb{P}(E_3 \cup E_6) =  1 - \mathbb{P}(E_3) - \mathbb{P}(E_6)$.
+The probability that $\texttt{M}$ outputs $\bot$ in step $6$ is the probability that the hashed coefficient $\mu_X = 0$, which occurs with probability $p^{-1}$.
+$\texttt{M}$ outputs $\bot$ in step $3$ when $\mathcal{F}^{\texttt{A}}$ produces $\bot$, but the forking lemma gives us that the acceptance probability of $\mathcal{F}^\texttt{A}$ is bounded from below by $\epsilon\left(\frac{\epsilon}{q_c} - \frac{1}{2^\eta}\right)$.
+Hence, $\texttt{M}$ succeeds with probability at least $ \left(\epsilon\left(\frac{\epsilon}{q_c} - \frac{1}{2^\eta}\right) - p^{-1}\right)$.
 \end{proof}
 
-\section{Security: linkable ring signature}
-Informally, a linkable ring signature is a construction permitting signatures on messages using a signer-selected anonymity set (called a \textit{ring}) of possible signers.
-A valid signature convinces a verifier that the signer knows (at least) one of the private keys to a ring member.
-The construction is linkable if it is possible to determine whether two signatures were generated using the same private key, regardless of the ring members used.
+\subsection{Linkability}
+We now prove linkability.
 
-We use the security definitions in \cite{groth} as a starting point, directly adopting definitions for correctness and unforgeability that also appear in more recent work like \cite{backes}.
-However, we modify the definition of anonymity to account for linking tags, such that the adversary is required to differentiate between at least two possible honest signers that the adversary has not corrupted.
-To account for the linking properties desired in our construction, we use the clever linkability definition from \cite{backes}, which uses a set-theoretic approach.
-We use a straightforward definition for non-frameability, where the adversary produces a target signature on an honest key after receiving signing and corruption oracle access, and must then produce a new signature that links.
+\begin{proof}[Linkability]
+Suppose $\texttt{A}$ is such a solver for $q \geq 1$.
+Among all tuples $\{(M_i, \underline{\textbf{pk}}_i^\prime, \sigma_i)\}_{i=1}^{q+1}$ returned by $\texttt{A}$, where $J_i \in \sigma_i$ is a signature's linking tag, we claim that there exists some $i$ such that $J_i$ does not correspond to any ring member in $\underline{\textbf{pk}}_i^\prime$.
 
-More formally, a \textit{linkable ring signature} (LRS) construction is a set of algorithms \text{KeyGen}, \text{Sign}, \text{Verify}, and \text{Link} satisfying certain properties.
-A set of public parameters is assumed to be available to each algorithm.
-\begin{itemize}
-\item $\text{KeyGen}(r) \to (x,X)$: Generates a secret key $x$ and corresponding public key $X$, optionally using randomness $r$; if not specified, the secret key is sampled uniformly at random.
-\item $\text{Sign}(x,M,R) \to \sigma$: Generates a signature $\sigma$ on a message $M \in \{0,1\}^*$ with respect to the ring $R = \{X_1,\ldots,X_n\}$, provided that $x$ is a secret key corresponding to some $X_i \in R$ generated by $\text{KeyGen}$.
-\item $\text{Verify}(\sigma,M,R) \to \{0,1\}$: Verifies a signature $\sigma$ on a message $M$ with respect to the ring $R$.
-Outputs $0$ is the signature is rejected, and $1$ if accepted.
-\item $\text{Link}(\sigma,\sigma') \to \{0,1\}$: Determines if signatures $\sigma$ and $\sigma'$ were signed using the same private key.
-Outputs $0$ if the signatures were signed using different private keys, and $1$ if they were signed using the same private key.
-\end{itemize}
+Indeed, the map from public keys to linking tags in the $d$-CLSAG construction is injective with high probability.
+If each linking tag $J_i$ (of which there are $q + 1$) corresponds to some public key in $\underline{\textbf{pk}}_i^\prime$, then there must exist at least two such tags that are equal, by the pigeonhole principle.
+But since $\texttt{Link}(\sigma_i,\sigma_j) = 0$ for all $i \neq j$, then by definition all linking tags are unique, a contradiction.
 
-We require that an LRS have the properties of correctness, anonymity, unforgeability, linkability, and non-frameability.
-
-Correctness requires that a signature generated honestly will always verify.
-\begin{definition}[Correctness]
-Consider this game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item The challenger runs $\text{KeyGen} \to (x,X)$ and supplies the keys to $\A$.
-\item The adversary $\A$ chooses a ring such that $X \in R$ and a message $M \in \{0,1\}^*$, and sends them to the challenger.
-\item The challenger signs the message with $\text{Sign}(x,M,R) \to \sigma$.
-\end{itemize}
-If $\text{Pr}[ \text{Verify}(\sigma,M,R) = 1 ] = 1$, we say that the LRS is \textit{perfectly correct}.
-\end{definition}
-Note that we do not require any ring members (except for $X$) to have been generated by $\text{KeyGen}$.
-However, distributed applications may in practice place additional restrictions on public keys used in anonymity sets.
-This allows for the possibility that $\A$ maliciously chooses ring members.
-
-Unforgeability requires that an adversary who does not control the private key to a ring member cannot generate a valid signature on any message using that ring.
-\begin{definition}[Unforgeability]
-Consider this game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item The adversary $\A$ is granted access to a public-key oracle $\text{GenOracle}$ that (on the $i^\text{th}$ invocation) runs $\text{KeyGen} \to (x_i,X_i)$ and returns $X_i$ to $\A$.
-\item The adversary $\A$ is granted access to a corruption oracle $\text{CorruptOracle}(i)$ that returns $x_i$ if it corresponds to a query to $\text{GenOracle}$.
-\item The adversary $\A$ is granted access to a signing oracle $\text{SignOracle}(X,M,R)$ that runs $\text{Sign}(x,M,R) \to \sigma$ and returns $\sigma$ to $\A$, provided that $X$ corresponds to a query to $\text{GenOracle}$ and $X \in R$.
-\item Then, $\A$ outputs $(\sigma,M,R)$ such that $\text{SignOracle}$ was not queried with $(-,M,R)$, all keys in $R$ were generated by queries to $\text{GenOracle}$, and no key in $R$ was corrupted by $\text{CorruptOracle}$.
-\end{itemize}
-If $\text{Pr}[ \text{Verify}(\sigma,M,R) = 1 ] \approx 0$, we say that the LRS is $\textit{unforgeable with respect to insider corruption}$.
-\end{definition}
-
-Anonymity requires that as long as a ring contains at least two members that have not been corrupted, an adversary can do no better than guessing at determining the signer of an honest signature.
-\begin{definition}[Anonymity]
-Consider this game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item The adversary $\A$ is granted access to the public-key oracle $\text{GenOracle}$ and the corruption oracle $\text{CorruptOracle}$.
-\item The adversary $\A$ chooses a message $M \in \{0,1\}^*$, a ring $R$, and indices $i_0$ and $i_1$, and sends them to the challenger.
-We require that $X_{i_0},X_{i_1} \in R$ such that both keys were generated by queries to $\text{GenOracle}$, and neither key was queried to $\text{CorruptOracle}$.
-\item The challenger selects a uniformly random bit $b \in \{0,1\}$, generates the signature $\text{Sign}(x_{i_b},M,R) \to \sigma$, and sends it to $\A$.
-\item The adversary $\A$ chooses a bit $b' \in \{0,1\}$.
-\end{itemize}
-If $\text{Pr}[ b' = b ] \approx 1/2$ and $\A$ did not make any corruption queries after receiving the challenge bit, we say that the LRS is \textit{anonymous}.
-\end{definition}
-We observe that this definition permits the adversary to have corrupted or maliciously generated all but two keys in the ring.
-Some definitions allow the adversary to corrupt more keys, but we will see that this is inconsistent with our linkability construction, where an adversary in control of a ring member's private key can trivially determine if it was the signer by examining the linking tag associated to a signature.
-
-Linkability requires that an adversary be unable to produce $k+1$ non-linked signatures on a combined anonymity set of $k$ public keys.
-\begin{definition}[Linkability]
-Consider the following game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item For $i \in [0,k-1]$, the adversary $\A$ produces a public key $X_i$, message $M_i$, ring $R_i$, and signature $\sigma_i$.
-\item The adversary $\A$ produces another message M, ring R, and signature $\sigma$.
-\item All tuples $(X_i,M_i,R_i,\sigma_i)$ and $(M,R,\sigma)$ are sent to the challenger.
-\item The challenger checks the following:
-\begin{itemize}
-\item $\left| V \right| = k$, where $V \equiv \bigcup_{i=0}^{k-1} R_i$.
-\item Each $X_i \in V$.
-\item Each $R_i \subset V$.
-\item $\text{Verify}(\sigma_i,M_i,R_i) = 1$ for all $i$.
-\item $\text{Verify}(\sigma,M,R) = 1$.
-\item For all $i \neq j$, we have $\text{Link}(\sigma_i,\sigma_j) = \text{Link}(\sigma_i,\sigma) = 0$.
-\end{itemize}
-\item If all checks pass, $\A$ wins.
-\end{itemize}
-If $\A$ wins with only negligible probability for all $k$, we say the LRS is \textit{linkable}.
-\end{definition}
-
-Non-frameability requires that an adversary be unable to generate a signature that links with an honest signature.
-\begin{definition}[Non-frameability]
-Consider also the following game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item The adversary $\A$ is granted access to the public-key oracle $\text{GenOracle}$.
-\item The adversary $\A$ is granted access to the corruption oracle $\text{CorruptOracle}$.
-\item The adversary $\A$ is granted access to the signing oracle $\text{SignOracle}$.
-\item The adversary $\A$ chooses a public key $X$ that was generated by a query to $\text{GenOracle}$, but was not presented as a query to $\text{CorruptOracle}$.
-It selects a message $M \in \{0,1\}^*$ and ring $R$ such that $X \in R$.
-It queries $\text{SignOracle}(X,M,R) \to \sigma$.
-\item The adversary $\A$ then produces a tuple $(M',R',\sigma')$ and sends $(M',R',\sigma')$ to the challenger, along with $(X,M,R,\sigma)$.
-\item If $\text{Verify}(\sigma',M',R') = 0$ or if $\sigma'$ was produced using a query to $\text{SignOracle}$, the challenger aborts.
-\end{itemize}
-If $\text{Pr}[ \text{Link}(\sigma,\sigma') = 1 \approx 0$, we say that the LRS is \textit{non-frameable}.
-\end{definition}
-
-\section{Application: linkable ring signature}
-The constructions in \cite{groth,bootle} describe how to use a similar sigma protocol to construct a simple ring signature scheme.
-Using our modifications, we can easily extend this to account for linkability and non-frameability.
-We briefly show how to do so.
-
-\begin{figure}[htbp]
-\centering
-\fbox{\begin{minipage}{0.95\textwidth}
-    $\underline{\text{KeyGen}(r):}$
-    \begin{itemize}
-        \item If not specified, select $r \in \F$ uniformly at random.
-        \item Compute $R = rG$.
-        \item Return $(x,X) = (r,R)$.
-    \end{itemize}
-
-    $\underline{\text{Sign}(x,M,R):}$
-    \begin{itemize}
-        \item Let $R = \{X_0,\ldots,X_{N-1}\}$ such that $X_l = x_lG$.
-        \item Compute $J \equiv x_l^{-1}U$.
-        \item Run $\mathcal{P}_{\text{link}}(R,J;(l,x_l)) \to a$ (up to the verifier challenge).
-        \item Set $\xi \equiv \hs(M,R,a)$.
-        \item Run $\mathcal{P}_{\text{link}}(\xi) \to z$ (after the verifier challenge).
-        \item Return $\sigma = (a,z,J)$.
-    \end{itemize}
-
-    $\underline{\text{Verify}(\sigma,M,R):}$
-    \begin{itemize}
-        \item Let $R = \{X_0,\ldots,X_{N-1}\}$ such that $X_l - x_lG$.
-        \item Let $\sigma = (a,z,J)$.
-        \item Set $\xi \equiv \hs (M,R,a)$.
-        \item Return $\mathcal{V}_{\text{link}}(R,J,a,z)$.
-    \end{itemize}
-
-    $\underline{\text{Link}(\sigma,\sigma'):}$
-    \begin{itemize}
-        \item We implicitly assume that $\sigma$ and $\sigma'$ have been previously verified.
-        \item Let $\sigma = (a,z,J)$ and $\sigma' = (a',z',J')$.
-        \item If $J = J'$, return $1$.
-        Otherwise, return $0$.
-    \end{itemize}
-\end{minipage}}
-    \caption{Linkable ring signature using $\mathcal{R}_{\text{link}}$}
-    \label{fig:lrs}
-\end{figure}
-
-\begin{theorem}
-The protocol in Figure \ref{fig:lrs} is a linkable ring signature construction.
-\end{theorem}
-
-\begin{proof}
-Perfect correctness follows immediately from the perfect completeness of the proving system for $\mathcal{R}_{link}$.
-
-Similarly, anonymity follows since the proving system is special honest-verifier zero knowledge, and therefore witness indistinguishable \cite{cramer}.
-Any adversarial advantage in breaking anonymity must therefore arise from distinguishing either input commitments or linking tags in signatures.
-Since honestly-generated input Pedersen commitments are perfectly hiding, they are indistinguishable from elements of $\G$ selected uniformly at random; we assume by definition that at least two such commitments are present in such a signature.
-Further, honestly-generated linking tags are generated from a one-way pseudorandom function, and therefore in the random oracle model are independently uniformly distributed from other proof elements and input commitments.
-
-The proof for unforgeability in \cite{groth} relies on the (special) soundness of the underlying sigma protocol; it applies directly to our modification for $\mathcal{R}_{link}$, and is not repeated here.
-
-To show linkability, observe first that $\text{Link}$ simply compares linking tags, so two signatures link if and only if they share a common linking tag.
-Suppose an adversary can win the linkability game with non-negligible probability for some $k > 1$.
-Since all provided signatures verify, soundness implies extraction of a witness $x_i$ from signature $\sigma_i$ for all $i$, and of a witness $x$ from $\sigma$.
-Note that all $\{x_i\}$ and $x$ are distinct.
-If $x_i = x_j$ for $i \neq j$, then the corresponding linking tags $J_i$ and $J_j$ are such that $x_iJ_i = x_jJ_j = U$; then $J_i = J_j$, which contradicts $\text{Link}(\sigma_i,\sigma_j) = 0$.
-The same reasoning holds to show $x$ is similarly distinct.
-Soundness also implies that for all $i$, there exists $X_i \in R_i$ such that $x_iG = X_i$; similarly, there exists $X \in R$ such that $xG = X$.
-By assumption we have $$\{X_0,\ldots,X_{k-1},X\} \subset \left( \bigcup_{i=0}^{k-1} R_i \right) \cup R \subset V.$$
-However, note that $\left| \{X_0,\ldots,X_{k-1},X\} \right| = k+1$, but that $\left| V \right| = k$, a contradiction.
-
-Finally, we show non-frameability and assume an adversary has a non-negligible advantage in breaking this property.
-Because we have $\text{Verify}(\sigma',M',R') = 1$, soundness implies extraction of a witness $x' \in \F$ such that $x'G \in R'$; we also have a witness $x$ such that $xG \in R$ from the known signature $\sigma$.
-Since $\text{Link}(\sigma,\sigma') = 1$, the corresponding linking tags $J$ and $J'$ are equal by definition; hence by soundness $xJ = x'J' = U$, giving $x = x'$.
-However, the adversary did not query $\text{CorruptOracle}$ with $X$, meaning it breaks the discrete logarithm problem non-negligibly.
+Therefore, there exists such an index $i$.
+But $\texttt{A}$ did not query a signing oracle to obtain $\sigma_i$ in the game, and $\texttt{Verify}(M_i, \underline{\textbf{pk}}_i^\prime, \sigma_i) = 1$; this corresponds to a forgery.
 \end{proof}
 
-\section{Protocol: parallel linkable one-of-many commitment}
-In this section, we describe a modification of the sigma protocol for $\mathcal{R}_{\text{link}}$ that permits us to prove knowledge of multiple commitments in separate sets at the same index position, while retaining the linking property in the first commitment set only.
-We later show how to apply such a construction to a signer-ambiguous transaction protocol that can demonstrate balance preservation.
+\subsection{Non-frameability}
+We show non-frameability.
 
-We wish to produce a sigma protocol for the following relation:
-$$\mathcal{R}_{\text{par}} = \left\{ \{M_i\}_{i=0}^{N-1} \subset \G, \{P_i\}_{i=0}^{N-1} \subset \G, J \in \G ; (l \in \mathbb{Z},r \in \F,s \in \F) : M_l = rG \text{ and } P_l = sG \text{ and } U = rJ \right\}$$
-This requires only minor modifications to the protocol for $\mathcal{R}_{\text{link}}$, so we document only the modified proof elements constructed and verified in Figure \ref{fig:par}.
-All other proof elements are generated and verified identically.
+\begin{proof}[Non-frameability]
+Suppose that $\texttt{A}$ is such a solver.
+Since $\texttt{Link}(\sigma,\sigma^\prime) = 1$, then by definition the corresponding linking tags $J$ and $J^\prime$ must be equal, and $J$ corresponds to the ring member $\textbf{pk}$ used in the signing oracle query that produced $\sigma$.
 
-\begin{figure}[htbp]
-\centering
-\fbox{\begin{minipage}{0.95\textwidth}
-$\underline{\mathcal{P}_{\text{par}}(\{M_i\},\{P_i\},J;(l,r,s)):}$
-\begin{itemize}
-\item Define $K \equiv sJ$.
-\item Define $\mu \equiv \hs(\{M_i\},\{P_i\},J,K)$.
-\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}(M_k + \mu P_k) + \rho_jG$$
-\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv (U + \mu K)\sumk p_{k,j} + \rho_jG$$
-\end{itemize}
-
-$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
-$K,\{X_j\},\{Y_j\}$ \\
-
-$\underline{\mathcal{V} \to \mathcal{P}:}$ \\
-$\xi \in \{0,1\}^*$ \\
-
-$\underline{\mathcal{P}(\xi):}$
-\begin{itemize}
-\item Define $z \equiv (r + \mu s)\xi^m - \sumj \rho_j\xi^j$.
-\end{itemize}
-
-$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
-$z$ \\
-
-$\underline{\mathcal{V}_{\text{par}}(\{M_i\},\{P_i\},J):}$
-\begin{itemize}
-\item Define $\mu \equiv \hs(\{M_i\},\{P_i\},J,K)$.
-\item Accept if and only if:
-\begin{eqnarray*}
-\sumk (M_k + \mu P_k) \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG &=& 0 \\
-(U + \mu K)\sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ &=& 0
-\end{eqnarray*}
-\end{itemize}
-\end{minipage}}
-\caption{Sigma protocol (abbreviated) for $\mathcal{R}_{\text{par}}$}
-\label{fig:par}
-\end{figure}
-
-\begin{theorem}
-The protocol in Figure \ref{fig:par} is perfectly complete, special honest-verifier zero knowledge, and $(m+1)$-special sound.
-\end{theorem}
-
-\begin{proof}
-In the random oracle model, extraction of a witness of the form $r + \mu s$ implies knowledge of both $r$ and $s$ such that $rG = M_l$ and $sG = P_l$, similarly to the key-aggregation arguments in \cite{musig}.
-The same extraction shows that $(r + \mu s)J = U + \mu K$, which implies in particular that $rJ = U$, as required.
-
-The rest of the proof follows with only trivial modifications from the proof for $\mathcal{R}_{\text{link}}$.
+However, no signing oracle query produced $\sigma^\prime$, and the corruption oracle was not queried on $\textbf{pk}$, so $\texttt{A}$ has produced a forgery $\sigma^\prime$.
 \end{proof}
 
-\section{Application: signer-ambiguous transaction protocol}
-The parallel construction described in Figure \ref{fig:par} can be used in a signer-ambiguous transaction protocol.
+\subsection{Linkable anonymity}
+To show that our construction has linkable anonymity, we first make observations about the DDH game.
 
-Suppose a user wishes to generate a transaction consuming $W$ previously-generated outputs and generating $T$ fresh outputs.
-The user shuffles the consumed outputs within a larger list of $N$ outputs $\{M_k\}_{k=0}^{N-1}$, such that there exist indices $\{l_u\}_{u=0}^{W-1}$ where each $M_{l_u} = r_u$ for some known private key $r_u$.
-Further, assume each $M_{l_u}$ comes equipped with an amount commitment of the form $P_{l_u} \equiv \com(a_u,s_u)$ for amount $a_u$ and mask $s_u$.
-(All other $M_k$ also come equipped with a corresponding $P_k$, but the structure of these points is not relevant here.)
+Note any algorithm can flip a coin and guess correctly half the time.
+We say the \textit{advantage} of $\texttt{A}$ is the difference between the probability of success for $\texttt{A}$ and $1/2$.
+Moreover, due to the random self-reducibility of the DDH game, a $(t, \epsilon, \kappa)$-solver of the DDH game presented implies the existence of a $(t^\prime, \epsilon^\prime, 1)$-solver, which is the usual DDH game.
 
-The user generates $W$ auxiliary commitments $P'_u \equiv \com(a_u,s'_u)$ to the same amounts, but with different masks $\{s'_u\}$ chosen uniformly at random from $\F$.
-Then, the user generates $W$ spend proofs, each using the following prover inputs for $u \in [0,W)$:
-$$\mathcal{P}_{par}(\{M_i\},\{P_i-P'_u\},r_u^{-1}U;(l_u,r_u,s_u-s'_u))$$
+\begin{remark}
+If $\mathbb{G}$ satisfies the DDH hardness assumption, then the distribution of the triple of group elements $(r_1G, r_2G, r_3G)$ is computationally indistinguishable from the triple $(r_1G, r_2G, r_1r_2G)$,  where the $r_i$ are independently uniform on $\mathbb{F}_p$.
+If $\mathcal{H}^p: \left\{0,1\right\}^* \to \mathbb{G}$ is modeled as a random oracle with output that is independent of its input, the distribution of a tuple $(r_1G, r_2G, r_3G)$ is identical to the distribution of $(r_1G, \mathcal{H}^p(r_1G), r_3G)$ where $r_1, r_3$ are independently uniform on $\mathbb{F}_p$.
+Hence, under the random oracle model and assuming $\mathbb{G}$ is DDH-hard, the distribution of triples $(r_1G, \mathcal{H}^p(r_1G), r_1\mathcal{H}^p(r_1G))$ where $r_1$ is uniformly random from $\mathbb{F}_p$ is computationally indistinguishable from the distribution of triples $(r_1G, \mathcal{H}^p(r_1G), r_3G)$ where $r_1, r_3$ are uniformly random from $\mathbb{F}_p$.
 
-For $j \in [0,T)$, the user generates a fresh output of the form $Q_j \equiv \com(b_j,t_j)$ for amount $b_j$ and mask $t_j$.
-The masks are chosen such that for $j \in [1,T)$, we have $t_j$ chosen uniformly at random from $\F$.
-We then choose $$t_0 \equiv \sum_{u=0}^{W-1} s_u' -\sum_{j=1}^{t-1} t_j$$ and include all $\{P'_u\}$ auxiliary commitments in the transaction.
+Now note that a solver of the signer ambiguity game is given $X_i$ and $\mathcal{H}^p(X_i)$ for each ring member and the key image $\mathfrak{T} = x_\ell \mathcal{H}^p(X_\ell)$.
+The solver with a non-negligible advantage at guessing $\ell$ has a non-negligible advantage in distinguishing whether a given triple $(X_i, \mathcal{H}^p(X_i), \mathfrak{T})$ satisfies $\mathfrak{T} = x_i \mathcal{H}^p(X_i)$ or not.
+\end{remark}
 
-To verify such a transaction, the verifier first performs verification on each spend proof to ensure it is valid.
-Then, the verifier ensures that $$\sum_{u=0}^{W-1} P'_u - \sum_{j=0}^{T-1} Q_j = 0$$ such that the transaction balances.
-This succeeds since the commitments sum to zero if and only if the difference of input and output amounts is zero, which holds since the Pedersen commitment construction is computationally binding.
+\begin{proof}[Linkable anonymity]
+We assume that $\texttt{A}$ is a $(t, \epsilon, \kappa)$-solver of the linkable anonymity game of Definition \ref{linkable-anonymity-game}.
+We assume that $\texttt{A}$ successfully outputs a bit before time $t$, i.e.\ $\texttt{A}$ is willing to flip a coin rather than output a distinguished failure symbol like $\bot_{\texttt{A}}$.
+We can always wrap $\texttt{A}$ in another algorithm that flips its own coin without losing generality, so this assumption is a reasonable one.
 
-\section{Efficiency}
-Triptych proofs scale logarithmically with the size of the input anonymity set; this is the best asymptotic scaling known for ring signatures that do not require a trusted setup process over non-pairing groups.
-Related protocols based on the inner-product compression method of \cite{bulletproofs} include Omniring \cite{omniring} and RingCT 3.0 \cite{omniring}.
-However, it is challenging to directly compare these protocols' efficiency.
-Omniring includes all transaction input signatures, output range proofs, and balance within a single proof structure; however, it is not possible to verify a batch of proofs more efficiently by combining common generators.
-While an early version of RingCT 3.0 used separate input, range, and balance proofs, the most recent version merges all input and balance proofs together but outsources the range proofs to an efficient construction like \cite{bulletproofs}; this comes at the cost of requiring that the number of inputs be a power of two or otherwise carefully padded.
-A more direct comparison is to CLSAG, a linear-sized linkable ring signature construction.
+We construct a master algorithm $\texttt{M}$ that runs $\texttt{A}$ as a subroutine and plays the game of Definition \ref{ddhgame}, specified as follows.
 
-We compare size and verification of parallel Triptych, the earlier version of RingCT 3.0 considering only the signature proof component, and CLSAG.
-For verification scaling, we account for the use of batching in Triptych and RingCT 3.0, where generators common to multiple proofs are used only once in verification.
-Further, since verification in both of these constructions reduces to checking whether several multiscalar multiplications are zero, we may apply random weighting such that verifying a batch of multiple proofs reduces to a single multiscalar multiplication.
-The use of efficient multiscalar multiplication algorithms like \cite{straus,pippenger} means that an $n$-multiscalar multiplication evaluates as $O(n/\log n)$.
-This form of batching does not apply to CLSAG, where verification consists of a sequence of hash function evaluations.
+\begin{enumerate}
+\item $\texttt{M}$ receives $\kappa$ DDH challenge tuples $\left\{(R_{i,1}, R_{i,2}, R_{i,3}^{(b)})\right\}_{i=0}^{\kappa - 1}$.
+$\texttt{M}$ sets $X_i := R_{i,1}$, instantiates hash tables for $\mathcal{H}^p$ and $\mathcal{H}^s$, back-patches $\mathcal{H}^p(X_i) \leftarrow R_{i,2}$, and defines $\mathfrak{T}_{i} := R_{i, 3}^{(b)}$ for each $i$.
 
-Table \ref{table:size} compares proof/signature sizes and verification complexity for these constructions.
-Verification complexity is separated into the number of hash-to-$\F$ operations (denoted $\hs$), hash-to-$\G$ operations (denoted $\hp$), and $i$-multiscalar multiplication operations of size $k(i)$.
-Figure \ref{fig:size} examines size as a function of input anonymity size under the assumption that elements of both $\G$ and $\F$ occupy $32$ kB of space.
-We note that although RingCT 3.0 proofs are smaller for large $N$, Triptych proofs are smaller in the range $16 < N < 1024$, a reasonable range given practical verification times.
+\item $\texttt{M}$ selects $z_{i,j}$ at random, sets $Z_{i,j} = z_{i,j} G$, sets $\textbf{pk}_i^* := (X_i, Z_{i,1}, \ldots, Z_{i,d-1})$, and computes the dummy challenge keys $\mathfrak{D}_j$.
+It selects a random bit $\overline{b} \in \{0,1\}$.
 
-\begin{table}[h]
-\centering
-\begin{tabular}{r|ll|l}
-& Size ($\G$) & Size ($\F$) & Verification \\
-\hline
-CLSAG \cite{clsag} & $1$ & $N + 1$ & $(N + 2) \hs + N \hp + 2N k(3)$ \\
-RingCT 3.0 \cite{rct3} & $2\lg(N) + 8$ & $10$ & $k(4N + 2\lg(N) + 16)$ \\
-Triptych (this work) & $2\lg(N) + 5$ & $\lg(N) + 3$ & $k(2N + 4\lg(N) + 8)$
-\end{tabular}
-\caption{Proof sizes and verification complexity, for anonymity set size $N$}
-\label{table:size}
-\end{table}
+\item $\texttt{M}$ executes $\texttt{A}$ as a black box using the set $\underline{\textbf{pk}}^*$ as challenge keys (and simulating appropriate oracle query responses for $\texttt{A}$ as described below).
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.6\textwidth]{size.png}
-\caption{Proof sizes for input anonymity set size $N$}
-\label{fig:size}
-\end{figure}
+\item $\texttt{A}$ outputs a bit $\overline{b}^\prime$. If $\overline{b}^\prime = \overline{b}$, then $\texttt{M}$ outputs $0$ and terminates. Otherwise, $\texttt{M}$ outputs $1$ and terminates.
 
-\section{Future work}
-It is possible to further extend the Triptych proving system to support proving knowledge of openings of multiple commitments within the \textit{same} anonymity set, while permitting the construction of linking tags for each such opening and demonstrating balance directly within a single proof.
-Such a construction is much more efficient than the present work when built into a transaction protocol, but the security definitions applying to such a construction are still under evaluation.
+\end{enumerate}
 
-\bibliographystyle{plain}
-\bibliography{main}
+The algorithm $\texttt{M}$ handles random oracle queries made by $\texttt{A}$ by flipping random coins and keeping consistency with an internal hash table.
+The algorithm $\texttt{M}$ handles signature oracle queries made by $\texttt{A}$, say $(m, \underline{\textbf{pk}}, \textbf{pk})$, by retrieving the challenge triple $(R_{i, 1}, R_{i, 2}, R_{i, 3}^{(b)})$ corresponding to each ring member and back-patching the signature as usual:
+\begin{enumerate}[(a)]
+\item $\texttt{M}$ selects a random scalars $c_{\ell^*+1}, s_1, s_2, \ldots, s_n \in \mathbb{F}_p$.
+
+\item For $\ell=\ell^*+1, \ell^*+2, \ldots, n-1, n, 1, 2, \ldots, \ell^*-1$, $\texttt{M}$ computes
+\begin{align*}
+L_\ell :=& s_\ell G + c_\ell\left(\mu_X X_{i(\ell)} + \sum_j \mu_j Z_{i(\ell),j}\right) \\
+R_\ell :=& s_\ell\mathcal{H}^p(X_{i(\ell)}) + c_\ell\left(\mu_X \mathfrak{T}_{i(\ell)} + \sum_j \mu_j \mathfrak{D}_j\right)\\
+c_{\ell+1} :=& \mathcal{H}^s\left(\underline{\textbf{pk}}^\prime \mid \mid m \mid \mid L_\ell \mid \mid R_\ell \right).
+\end{align*}
+
+\item $\texttt{M}$ computes $c_{\ell^*}$, $L_{\ell^*}$, and $R_{\ell^*}$ as above.
+If $\mathcal{H}^s$ has been queried before with $\left(\underline{\textbf{pk}}^\prime \mid \mid m \mid \mid L_{\ell^*} \mid \mid R_{\ell^*} \right)$, $\texttt{M}$ outputs $\bot$ and terminates.
+Otherwise, $\texttt{M}$ backpatches $\mathcal{H}^s\left(\underline{\textbf{pk}}^\prime \mid \mid m \mid \mid L_{\ell^*} \mid \mid R_{\ell^*} \right) \leftarrow c_{\ell^*+1}$.
+
+\item $\texttt{M}$ sends the signature $\sigma = (c_1, s_1, \ldots, s_n, \left\{\mathfrak{D}_j\right\}_j)$ and tag $R_{i, 3}^{(b)}$ to $\texttt{A}$.
+\end{enumerate}
+
+Note that $\texttt{M}$ only terminates and outputs $\bot$ if $\texttt{A}$ asks for a signature with a ring not containing the challenge points, or if $\mathcal{H}^s$ has been queried with $\left(\underline{\textbf{pk}}^\prime \mid \mid m \mid \mid L_\ell \mid \mid R_\ell \right)$ before step $4c$.
+We can assume $\texttt{A}$ never asks for a signature with a bad ring like this.
+Moreover, the points $L_\ell$ and $R_\ell$ are uniformly distributed, so the probability that any algorithm can guess the input for backpatching is negligible.
+Hence, $\texttt{M}$ carries out the game in Definition \ref{ddhgame} except with negligible probability.
+
+The law of total probability gives us that $\mathbb{P}\left[\texttt{M}\text{ wins}\right] = \frac{1}{2}\mathbb{P}\left[\texttt{M} \rightarrow 1 \mid b=1\right] + \frac{1}{2}\mathbb{P}\left[\texttt{M} \rightarrow 0 \mid b=0\right]$.
+Observe that the event $\texttt{M} \rightarrow 0$ is precisely the event that $\texttt{A} \rightarrow \overline{b}' = \overline{b}$.
+Similarly, the event $\texttt{M} \rightarrow 1$ is precisely the event that $\texttt{A} \rightarrow \overline{b}' \neq \overline{b}$.
+If $b = 1$ in the DDH game, then $\texttt{M}$ received random points instead of DDH exchange keys, so signature oracle points are random and $\texttt{A}$ has no advantage in the linkable anonymity game; hence $\mathbb{P}\left[\texttt{A} \rightarrow \overline{b}' = \overline{b} \mid b = 1\right] = \mathbb{P}\left[\texttt{A} \rightarrow \overline{b}' \neq \overline{b} \mid b = 1\right] = \frac{1}{2}$.
+However, if $b = 0$ in the DDH game, then $\texttt{M}$ received DDH exchange keys, and $\texttt{A}$ has an advantage $\epsilon$ in the linkable anonymity game; hence we can state that $\mathbb{P}\left[\texttt{A} \rightarrow \overline{b}' = \overline{b} \mid b = 0\right] = \frac{1}{2} + \epsilon$.
+Therefore:
+\begin{eqnarray*}
+\mathbb{P}\left[\texttt{M}\text{ wins}\right] &=& \frac{1}{2}\mathbb{P}\left[\texttt{M} \rightarrow 1 \mid b=1\right] + \frac{1}{2}\mathbb{P}\left[\texttt{M} \rightarrow 0 \mid b=0\right] \\
+&=& \frac{1}{2}\mathbb{P}\left[\texttt{A} \rightarrow \overline{b}' \neq \overline{b} \mid b = 1\right] + \mathbb{P}\left[\texttt{A} \rightarrow \overline{b}' = \overline{b} \mid b = 0\right] \\
+&=& \frac{1}{2}\left(\frac{1}{2}\right) + \frac{1}{2}\left(\frac{1}{2} + \epsilon\right) \\
+&=& \frac{1}{2} + \frac{\epsilon}{2}.
+\end{eqnarray*}
+This completes the proof.
+\end{proof}
 

### 2020-01-08 paper/iacr.tex
Paper update for efficiency data, narrative clarity, and typos

--- 2020-01-03 paper/iacr.tex
@@
-\documentclass[draft]{article} % TODO: remove draft
+\documentclass{article}
 \usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}
@@
 
-% TODO remove
-\usepackage{lineno}
-\linenumbers
-
 \title{Triptych: logarithmic-sized linkable ring signatures with applications}
-\author{Sarang Noether \\ Monero Research Lab \\ \texttt{sarang.noether@protonmail.com}}
+\author{Sarang Noether and Brandon Goodell \\ Monero Research Lab \\ \texttt{\{sarang,surae\}.noether@protonmail.com}}
 \date{\today}
@@
 \item \textit{Perfectly complete}: Given knowledge of a witness to a statement in the proof relation, an honest prover can always convince an honest verifier of the validity of the witness.
-\item \textit{Special sound}: Given a statement in the proof relation, if a prover can answer multiple honest verifier challenges correctly, then it is possible to extract a witness for this statement.
+\item \textit{Special sound}: Given a statement in the proof relation, if a prover can answer multiple verifier challenges correctly, then it is possible to extract a witness for this statement.
 \item \textit{Special honest-verifier zero knowledge}: Given any statement and verifier challenge, it is possible to simulate a transcript that is accepted by an honest verifier without knowledge of a corresponding witness.
@@
 The masks are chosen such that for $j \in [1,T)$, we have $t_j$ chosen uniformly at random from $\F$.
-We then choose $$t_0 \equiv \sum_{u=0}^{W-1} s_u' -\sum_{j=1}^{t-1} t_j$$ and include all $\{P'_u\}$ auxiliary commitments in the transaction.
+We then choose $$t_0 \equiv \sum_{u=0}^{W-1} s_u' -\sum_{j=1}^{T-1} t_j$$ and include all $\{P'_u\}$ auxiliary commitments in the transaction.
 
@@
 Omniring includes all transaction input signatures, output range proofs, and balance within a single proof structure; however, it is not possible to verify a batch of proofs more efficiently by combining common generators.
-While an early version of RingCT 3.0 used separate input, range, and balance proofs, the most recent version merges all input and balance proofs together but outsources the range proofs to an efficient construction like \cite{bulletproofs}; this comes at the cost of requiring that the number of inputs be a power of two or otherwise carefully padded.
-A more direct comparison is to CLSAG, a linear-sized linkable ring signature construction.
+While an early version of RingCT 3.0 used separate input, range, and balance proofs, the most recent version merges all input and balance proofs together but outsources the range proofs to an efficient construction like \cite{bulletproofs}; this comes at the cost of requiring that the number of inputs be a power of two or otherwise carefully padded (affecting verification time).
+Therefore, for the purpose of comparison we modify slightly the earlier version of RingCT 3.0 with a soundness fix applied from the updated version, ignoring the size and verification cost of non-proof elements.
+Another more direct comparison is to $2$-CLSAG, a linear-sized linkable ring signature construction \cite{clsag}.
 
-We compare size and verification of parallel Triptych, the earlier version of RingCT 3.0 considering only the signature proof component, and CLSAG.
-For verification scaling, we account for the use of batching in Triptych and RingCT 3.0, where generators common to multiple proofs are used only once in verification.
+We now show size and verification comparisons of the parallel instantiation of Triptych, the earlier (modified) version of RingCT 3.0, and $2$-CLSAG.
+For verification scaling, we also account for the use of batching in Triptych and RingCT 3.0, where generators common to multiple proofs are used only once in verification.
 Further, since verification in both of these constructions reduces to checking whether several multiscalar multiplications are zero, we may apply random weighting such that verifying a batch of multiple proofs reduces to a single multiscalar multiplication.
@@
 
-Table \ref{table:size} compares proof/signature sizes and verification complexity for these constructions.
+Table \ref{table:size} compares proof/signature sizes and verification complexity for these constructions as a function of the anonymity set size $N$ and batch size $B$.
 Verification complexity is separated into the number of hash-to-$\F$ operations (denoted $\hs$), hash-to-$\G$ operations (denoted $\hp$), and $i$-multiscalar multiplication operations of size $k(i)$.
-Figure \ref{fig:size} examines size as a function of input anonymity size under the assumption that elements of both $\G$ and $\F$ occupy $32$ kB of space.
-We note that although RingCT 3.0 proofs are smaller for large $N$, Triptych proofs are smaller in the range $16 < N < 1024$, a reasonable range given practical verification times.
+Figure \ref{fig:size} examines size as a function of input anonymity set size, under the assumption that elements of both $\G$ and $\F$ occupy $32$ kB of space.
+We note that although RingCT 3.0 proofs are slightly smaller for large $N$, Triptych proofs are smaller for $N < 512$, a limited but reasonable range given practical verification times.
+We also note that the application of Triptych in a complete transaction protocol is not directly compared to RingCT 3.0 here, as the use of non-proof/signaure auxiliary data in such a protocol may differ based on particular implementations.
 
@@
 \begin{tabular}{r|ll|l}
-& Size ($\G$) & Size ($\F$) & Verification \\
+& Size ($\G$) & Size ($\F$) & Verification (batch total) \\
 \hline
-CLSAG \cite{clsag} & $1$ & $N + 1$ & $(N + 2) \hs + N \hp + 2N k(3)$ \\
-RingCT 3.0 \cite{rct3} & $2\lg(N) + 8$ & $10$ & $k(4N + 2\lg(N) + 16)$ \\
-Triptych (this work) & $2\lg(N) + 5$ & $\lg(N) + 3$ & $k(2N + 4\lg(N) + 8)$
+CLSAG \cite{clsag} & $2$ & $N + 1$ & $B(N + 2) \hs + BN \hp + 2BN k(3)$ \\
+RingCT 3.0 \cite{rct3} & $2\lg(N) + 9$ & $9$ & $k(B[2N + 2\lg(N) + 9] + 2N + 5)$ \\
+Triptych (this work) & $2\lg(N) + 6$ & $\lg(N) + 3$ & $k(B[2N + 2\lg(N) + 2] + 2\lg(N) + 3)$
 \end{tabular}
-\caption{Proof sizes and verification complexity, for anonymity set size $N$}
+\caption{Proof sizes and verification complexity, for anonymity set size $N$ and batch size $B$}
 \label{table:size}

### 2020-01-11 dumb25519/test.py
Curve library and test update

@@ -3,382 +3,870 @@
 from dumb25519 import *
 import unittest
 
-class TestEncoding(unittest.TestCase):
-    def test_G(self):
-        self.assertEqual(repr(G),'5866666666666666666666666666666666666666666666666666666666666666')
-        self.assertEqual(Point('5866666666666666666666666666666666666666666666666666666666666666'),G)
+# Scalar class
+class TestScalar(unittest.TestCase):
+    def test_init(self):
+        # Test construction using x = 1
+        s = Scalar(int(1))
+        self.assertEqual(s,Scalar(long(1)))
+        self.assertEqual(s,Scalar('0100000000000000000000000000000000000000000000000000000000000000'))
+        self.assertEqual(s.x,int(1))
+        self.assertEqual(s.x,long(1))
 
-    def test_Z(self):
-        self.assertEqual(repr(Z),'0100000000000000000000000000000000000000000000000000000000000000')
-        self.assertEqual(Point('0100000000000000000000000000000000000000000000000000000000000000'),Z)
+        # Test construction using x = l = 0
+        s = Scalar(int(l))
+        self.assertEqual(s,Scalar(long(l)))
+        self.assertEqual(s,Scalar('0000000000000000000000000000000000000000000000000000000000000000'))
+        self.assertEqual(s.x,int(0))
+        self.assertEqual(s.x,long(0))
 
-    def test_0(self):
+        # Test invalid constructions
+        with self.assertRaises(TypeError):
+            Scalar('invalid')
+        with self.assertRaises(TypeError):
+            Scalar(None)
+
+    def test_invert(self):
+        # Test nonzero inversion
+        self.assertEqual(Scalar(1).invert(),Scalar(1))
+        self.assertEqual(Scalar(1).invert(allow_zero=True),Scalar(1))
+        self.assertEqual(Scalar(2).invert()*Scalar(2),Scalar(1))
+        self.assertEqual(Scalar(2).invert(allow_zero=True)*Scalar(2),Scalar(1))
+        
+        # Test zero inversion
+        self.assertEqual(Scalar(0).invert(allow_zero=True),Scalar(0))
+        with self.assertRaises(ZeroDivisionError):
+            Scalar(0).invert()
+
+    def test_add(self):
+        # Test valid addition
[…]

### 2020-01-11 clsag/dumb25519.py
Curve library update

@@ -8,18 +8,19 @@ import random
 import hashlib
 import binascii
 
-# curve parameters
+# Curve parameters
 q = 2**255 - 19
 l = 2**252 + 27742317777372353535851937790883648493
 cofactor = 8
-b = 256 # bit representation
+b = 256 # bit length
 
 # Internal helper methods
 def exponent(b,e,m):
     return pow(b,e,m)
 
-def invert(x,n):
-    return exponent(x,n-2,n)
+def invert(x,p):
+    # Assumes `p` is prime
+    return exponent(x,p-2,p)
 
 def xfromy(y):
     temp = (y*y-1) * invert(d*y*y+1,q)
@@ -36,6 +37,7 @@ def bit(h,i):
 d = -121665 * invert(121666,q)
 I = exponent(2,(q-1)/4,q)
 
+# An element of the main subgroup scalar field
 class Scalar:
     def __init__(self,x):
         # Generated from an integer value
@@ -51,25 +53,28 @@ class Scalar:
         else:
             raise TypeError
 
-    def invert(self):
+    # Multiplicative inversion, with an option to let 1/0 = 0 if you're into that
+    def invert(self,allow_zero=False):
         if self.x == 0:
-            raise ZeroDivisionError
+            if allow_zero:
+                return Scalar(0)
+            else:
+                raise ZeroDivisionError
         return Scalar(invert(self.x,l))
 
+    # Addition
     def __add__(self,y):
-        if isinstance(y,int):
-            return Scalar(self.x + y)
         if isinstance(y,Scalar):
             return Scalar(self.x + y.x)
         return NotImplemented
 
+    # Subtraction
     def __sub__(self,y):
-        if isinstance(y,int):
-            return Scalar(self.x - y)
         if isinstance(y,Scalar):
             return Scalar(self.x - y.x)
         return NotImplemented
 
+    # Multiplication (possibly by an integer)
     def __mul__(self,y):
         if isinstance(y,int):
             return Scalar(self.x * y)
@@ -77,71 +82,92 @@ class Scalar:
             return Scalar(self.x * y.x)
         return NotImplemented
 
-    def __div__(self,y):
+    def __rmul__(self,y):
         if isinstance(y,int):
+            return self*y
+        return NotImplemented
+
+    # Truncated division (possibly by a positive integer)
+    def __div__(self,y):
+        if isinstance(y,int) and y >= 0:
             return Scalar(self.x / y)
         if isinstance(y,Scalar):
[…]

### 2020-01-11 rct3-multi/dumb25519.py
Curve library update

@@ -8,18 +8,19 @@ import random
 import hashlib
 import binascii
 
-# curve parameters
+# Curve parameters
 q = 2**255 - 19
 l = 2**252 + 27742317777372353535851937790883648493
 cofactor = 8
-b = 256 # bit representation
+b = 256 # bit length
 
 # Internal helper methods
 def exponent(b,e,m):
     return pow(b,e,m)
 
-def invert(x,n):
-    return exponent(x,n-2,n)
+def invert(x,p):
+    # Assumes `p` is prime
+    return exponent(x,p-2,p)
 
 def xfromy(y):
     temp = (y*y-1) * invert(d*y*y+1,q)
@@ -36,6 +37,7 @@ def bit(h,i):
 d = -121665 * invert(121666,q)
 I = exponent(2,(q-1)/4,q)
 
+# An element of the main subgroup scalar field
 class Scalar:
     def __init__(self,x):
         # Generated from an integer value
@@ -51,25 +53,28 @@ class Scalar:
         else:
             raise TypeError
 
-    def invert(self):
+    # Multiplicative inversion, with an option to let 1/0 = 0 if you're into that
+    def invert(self,allow_zero=False):
         if self.x == 0:
-            raise ZeroDivisionError
+            if allow_zero:
+                return Scalar(0)
+            else:
+                raise ZeroDivisionError
         return Scalar(invert(self.x,l))
 
+    # Addition
     def __add__(self,y):
-        if isinstance(y,int):
-            return Scalar(self.x + y)
         if isinstance(y,Scalar):
             return Scalar(self.x + y.x)
         return NotImplemented
 
+    # Subtraction
     def __sub__(self,y):
-        if isinstance(y,int):
-            return Scalar(self.x - y)
         if isinstance(y,Scalar):
             return Scalar(self.x - y.x)
         return NotImplemented
 
+    # Multiplication (possibly by an integer)
     def __mul__(self,y):
         if isinstance(y,int):
             return Scalar(self.x * y)
@@ -77,71 +82,92 @@ class Scalar:
             return Scalar(self.x * y.x)
         return NotImplemented
 
-    def __div__(self,y):
+    def __rmul__(self,y):
         if isinstance(y,int):
+            return self*y
+        return NotImplemented
+
+    # Truncated division (possibly by a positive integer)
+    def __div__(self,y):
+        if isinstance(y,int) and y >= 0:
             return Scalar(self.x / y)
         if isinstance(y,Scalar):
[…]

### 2020-01-11 rct3-single/pybullet.py

@@ -106,15 +106,15 @@ def inner_product(data):
     n /= 2
     cL = data.a[:n]**data.b[n:]
     cR = data.a[n:]**data.b[:n]
-    data.L.append((data.G[n:]*data.a[:n] + data.H[:n]*data.b[n:] + data.U*cL)*inv8)
-    data.R.append((data.G[:n]*data.a[n:] + data.H[n:]*data.b[:n] + data.U*cR)*inv8)
+    data.L.append((data.G[n:]**data.a[:n] + data.H[:n]**data.b[n:] + data.U*cL)*inv8)
+    data.R.append((data.G[:n]**data.a[n:] + data.H[n:]**data.b[:n] + data.U*cR)*inv8)
 
     data.tr.update(data.L[-1])
     data.tr.update(data.R[-1])
     x = data.tr.challenge()
 
-    data.G = (data.G[:n]*x.invert())*(data.G[n:]*x)
-    data.H = (data.H[:n]*x)*(data.H[n:]*x.invert())
+    data.G = data.G[:n]*x.invert() + data.G[n:]*x
+    data.H = data.H[:n]*x + data.H[n:]*x.invert()
 
     data.a = data.a[:n]*x + data.a[n:]*x.invert()
     data.b = data.b[:n]*x.invert() + data.b[n:]*x
@@ -148,12 +148,12 @@ def prove(data,N):
         aR.append(bit-Scalar(1))
 
     alpha = random_scalar()
-    A = (Gi*aL + Hi*aR + Gc*alpha)*inv8
+    A = (Gi**aL + Hi**aR + Gc*alpha)*inv8
 
     sL = ScalarVector([random_scalar()]*(M*N))
     sR = ScalarVector([random_scalar()]*(M*N))
     rho = random_scalar()
-    S = (Gi*sL + Hi*sR + Gc*rho)*inv8
+    S = (Gi**sL + Hi**sR + Gc*rho)*inv8
 
     # get challenges
     tr.update(A)

### 2020-01-11 rct3-single/spend.py

@@ -63,15 +63,15 @@ def inner_product(data):
     n /= 2
     cL = data.a[:n]**data.b[n:]
     cR = data.a[n:]**data.b[:n]
-    data.L.append(data.G[n:]*data.a[:n] + data.H[:n]*data.b[n:] + data.U*cL)
-    data.R.append(data.G[:n]*data.a[n:] + data.H[n:]*data.b[:n] + data.U*cR)
+    data.L.append(data.G[n:]**data.a[:n] + data.H[:n]**data.b[n:] + data.U*cL)
+    data.R.append(data.G[:n]**data.a[n:] + data.H[n:]**data.b[:n] + data.U*cR)
 
     data.tr.update(data.L[-1])
     data.tr.update(data.R[-1])
     x = data.tr.challenge()
 
-    data.G = (data.G[:n]*x.invert())*(data.G[n:]*x)
-    data.H = (data.H[:n]*x)*(data.H[n:]*x.invert())
+    data.G = data.G[:n]*x.invert() + data.G[n:]*x
+    data.H = data.H[:n]*x + data.H[n:]*x.invert()
 
     data.a = data.a[:n]*x + data.a[n:]*x.invert()
     data.b = data.b[:n]*x.invert() + data.b[n:]*x

### 2020-01-11 rct3-single/test.py

@@ -26,7 +26,7 @@ class Coin:
         # Sanity checks
         if not isinstance(v,Scalar):
             raise TypeError('Invalid coin value!')
-        if v > Scalar(2)**BITS - 1:
+        if v > Scalar(2)**BITS - Scalar(1):
             raise ValueError('Value is out of range!')
         if not isinstance(X1,Point) or not isinstance(X2,Point):
             raise TypeError('Invalid destination address!')

### 2020-01-11 ipa-nozk/nozk.py
Curve library update

@@ -41,8 +41,8 @@ def inner_product(data):
     n /= 2
     cL = data.a[:n]**data.b[n:]
     cR = data.a[n:]**data.b[:n]
-    data.L.append(data.G[n:]*data.a[:n] + data.H[:n]*data.b[n:] + data.U*cL)
-    data.R.append(data.G[:n]*data.a[n:] + data.H[n:]*data.b[:n] + data.U*cR)
+    data.L.append(data.G[n:]**data.a[:n] + data.H[:n]**data.b[n:] + data.U*cL)
+    data.R.append(data.G[:n]**data.a[n:] + data.H[n:]**data.b[:n] + data.U*cR)
 
     mash(data.L[-1])
     mash(data.R[-1])
@@ -69,7 +69,7 @@ def test(a,b,N):
 
     # The compound commitment
     t = a**b
-    P = Gi*a + Hi*b + U*t
+    P = Gi**a + Hi**b + U*t
     mash(P)
     mash(t)
 

### 2020-01-11 lelantus/layer.py
Curve libary update and minor fixes

@@ -49,7 +49,7 @@ for i in range(M):
 
 # Layer-1 proof
 proof1,state = groth.prove_initial(d,l,v+masks_v[l],r+masks_r[l],n_M,m_M)
-state.x = groth.challenge([proof1])
+state.x = groth.challenge(d,[proof1])
 proof1 = groth.prove_final(proof1,state)[0] # ignore gamma return value for this test
 
 # Fiat-Shamir challenges
@@ -71,11 +71,11 @@ for i in range(M):
     mask_v += x[i]*masks_v[i]
     mask_r += x[i]*masks_r[i]
 proof2,state = groth.prove_initial([digest_d - D[i] for i in range(T)],k,mask_v,mask_r,n_T,m_T)
-state.x = groth.challenge([proof2])
+state.x = groth.challenge([digest_d - D[i] for i in range(T)],[proof2])
 proof2 = groth.prove_final(proof2,state)[0] # ignore gamma return value for this test
 
 # Verify the layer-1 proof
-groth.verify(d,proof1,n_M,m_M,groth.challenge([proof1]))
+groth.verify(d,proof1,n_M,m_M,groth.challenge(d,[proof1]))
 
 # Verify the layer-2 proof
-groth.verify([digest_d - D[i] for i in range(T)],proof2,n_T,m_T,groth.challenge([proof2]))
+groth.verify([digest_d - D[i] for i in range(T)],proof2,n_T,m_T,groth.challenge([digest_d - D[i] for i in range(T)],[proof2]))

### 2020-01-11 lelantus/pybullet.py

@@ -100,15 +100,15 @@ def inner_product(data):
     n /= 2
     cL = data.a[:n]**data.b[n:]
     cR = data.a[n:]**data.b[:n]
-    data.L.append((data.G[n:]*data.a[:n] + data.H[:n]*data.b[n:] + data.U*cL)*inv8)
-    data.R.append((data.G[:n]*data.a[n:] + data.H[n:]*data.b[:n] + data.U*cR)*inv8)
+    data.L.append((data.G[n:]**data.a[:n] + data.H[:n]**data.b[n:] + data.U*cL)*inv8)
+    data.R.append((data.G[:n]**data.a[n:] + data.H[n:]**data.b[:n] + data.U*cR)*inv8)
 
     data.tr.update(data.L[-1])
     data.tr.update(data.R[-1])
     x = data.tr.challenge()
 
-    data.G = (data.G[:n]*x.invert())*(data.G[n:]*x)
-    data.H = (data.H[:n]*x)*(data.H[n:]*x.invert())
+    data.G = data.G[:n]*x.invert() + data.G[n:]*x
+    data.H = data.H[:n]*x + data.H[n:]*x.invert()
 
     data.a = data.a[:n]*x + data.a[n:]*x.invert()
     data.b = data.b[:n]*x.invert() + data.b[n:]*x
@@ -141,12 +141,12 @@ def prove(data,N):
         aR.append(bit-Scalar(1))
 
     alpha = random_scalar()
-    A = (Gi*aL + Hi*aR + G*alpha)*inv8
+    A = (Gi**aL + Hi**aR + G*alpha)*inv8
 
     sL = ScalarVector([random_scalar()]*(M*N))
     sR = ScalarVector([random_scalar()]*(M*N))
     rho = random_scalar()
-    S = (Gi*sL + Hi*sR + G*rho)*inv8
+    S = (Gi**sL + Hi**sR + G*rho)*inv8
 
     # get challenges
     tr.update(A)

### 2020-01-11 lelantus/transaction.py

@@ -145,7 +145,7 @@ class SpendTransaction:
             spend_states.append(spend_state)
 
         # Compute aggregate Fiat-Shamir challenge
-        x = groth.challenge(self.spend_proofs)
+        x = groth.challenge(C_list,self.spend_proofs)
 
         # Complete spend proofs
         self.spend_sigs = []
@@ -208,7 +208,7 @@ class SpendTransaction:
             signature.verify(repr(self.spend_proofs[i]),self.Q[i],self.spend_sigs[i])
 
         # Verify the spend proofs
-        x = groth.challenge(self.spend_proofs)
+        x = groth.challenge(self.C_list,self.spend_proofs)
         for i in range(len(self.spend_proofs)):
             s = hash_to_scalar(self.Q[i])
             offset = groth.comm(s,Scalar(0),Scalar(0))

### 2020-01-11 pybullet/pybullet.py
Curve library update

@@ -105,15 +105,15 @@ def inner_product(data):
     n /= 2
     cL = data.a[:n]**data.b[n:]
     cR = data.a[n:]**data.b[:n]
-    data.L.append((data.G[n:]*data.a[:n] + data.H[:n]*data.b[n:] + data.U*cL)*inv8)
-    data.R.append((data.G[:n]*data.a[n:] + data.H[n:]*data.b[:n] + data.U*cR)*inv8)
+    data.L.append((data.G[n:]**data.a[:n] + data.H[:n]**data.b[n:] + data.U*cL)*inv8)
+    data.R.append((data.G[:n]**data.a[n:] + data.H[n:]**data.b[:n] + data.U*cR)*inv8)
 
     data.tr.update(data.L[-1])
     data.tr.update(data.R[-1])
     x = data.tr.challenge()
 
-    data.G = (data.G[:n]*x.invert())*(data.G[n:]*x)
-    data.H = (data.H[:n]*x)*(data.H[n:]*x.invert())
+    data.G = data.G[:n]*x.invert() + data.G[n:]*x
+    data.H = data.H[:n]*x + data.H[n:]*x.invert()
 
     data.a = data.a[:n]*x + data.a[n:]*x.invert()
     data.b = data.b[:n]*x.invert() + data.b[n:]*x
@@ -149,12 +149,12 @@ def prove(data,N):
         aR.append(bit-Scalar(1))
 
     alpha = random_scalar()
-    A = (Gi*aL + Hi*aR + G*alpha)*inv8
+    A = (Gi**aL + Hi**aR + G*alpha)*inv8
 
     sL = ScalarVector([random_scalar()]*(M*N))
     sR = ScalarVector([random_scalar()]*(M*N))
     rho = random_scalar()
-    S = (Gi*sL + Hi*sR + G*rho)*inv8
+    S = (Gi**sL + Hi**sR + G*rho)*inv8
 
     # get challenges
     tr.update(A)

### 2020-01-11 pybullet/pybullet.py
Curve library update

@@ -138,15 +138,15 @@ def inner_product(data):
     n /= 2
     cL = a[:n]**b[n:]
     cR = a[n:]**b[:n]
-    L = (G[n:]*a[:n] + H[:n]*b[n:] + U*cL)*inv8
-    R = (G[:n]*a[n:] + H[n:]*b[:n] + U*cR)*inv8
+    L = (G[n:]**a[:n] + H[:n]**b[n:] + U*cL)*inv8
+    R = (G[:n]**a[n:] + H[n:]**b[:n] + U*cR)*inv8
 
     mash(L)
     mash(R)
     x = cache
 
-    G = (G[:n]*x.invert())*(G[n:]*x)
-    H = (H[:n]*x)*(H[n:]*x.invert())
+    G = G[:n]*x.invert() + G[n:]*x
+    H = H[:n]*x + H[n:]*x.invert()
 
     a = a[:n]*x + a[n:]*x.invert()
     b = b[:n]*x.invert() + b[n:]*x
@@ -184,12 +184,12 @@ def prove_A(v,gamma,k,seed=None):
         aR.append(bit-Scalar(1))
 
     alpha = random_scalar()
-    A = (Gi*aL + Hi*aR + G*alpha)*inv8
+    A = (Gi**aL + Hi**aR + G*alpha)*inv8
 
     sL = ScalarVector([random_scalar()]*N)
     sR = ScalarVector([random_scalar()]*N)
     rho = random_scalar()
-    S = (Gi*sL + Hi*sR + G*rho)*inv8
+    S = (Gi**sL + Hi**sR + G*rho)*inv8
 
     # update state
     state.gamma = gamma

### 2020-01-11 pybullet/pybullet.py
Curve library update

@@ -60,15 +60,15 @@ def inner_product(data):
     n /= 2
     cL = data.a[:n]**data.b[n:]
     cR = data.a[n:]**data.b[:n]
-    data.L.append(data.G[n:]*data.a[:n] + data.H[:n]*data.b[n:] + data.U*cL)
-    data.R.append(data.G[:n]*data.a[n:] + data.H[n:]*data.b[:n] + data.U*cR)
+    data.L.append(data.G[n:]**data.a[:n] + data.H[:n]**data.b[n:] + data.U*cL)
+    data.R.append(data.G[:n]**data.a[n:] + data.H[n:]**data.b[:n] + data.U*cR)
 
     mash(data.L[-1])
     mash(data.R[-1])
     x = cache
 
-    data.G = (data.G[:n]*x.invert())*(data.G[n:]*x)
-    data.H = (data.H[:n]*x)*(data.H[n:]*x.invert())
+    data.G = data.G[:n]*x.invert() + data.G[n:]*x
+    data.H = data.H[:n]*x + data.H[n:]*x.invert()
 
     data.P = data.L[-1]*x**2 + data.P + data.R[-1]*x.invert()**2
 
@@ -80,7 +80,7 @@ def test(a,b,N):
     Gi = PointVector([hash_to_point('pybullet Gi ' + str(i)) for i in range(N)])
     Hi = PointVector([hash_to_point('pybullet Hi ' + str(i)) for i in range(N)])
     U = hash_to_point('pybullet U')
-    P = Gi*a + Hi*b + U*(a**b)
+    P = Gi**a + Hi**b + U*(a**b)
 
     data = InnerProductRound(Gi,Hi,U,a,b,P)
     while True:

### 2020-01-11 stringct/dumb25519.py
Curve library update

@@ -6,18 +6,21 @@
 
 import random
 import hashlib
+import binascii
 
-# curve parameters
+# Curve parameters
 q = 2**255 - 19
 l = 2**252 + 27742317777372353535851937790883648493
 cofactor = 8
+b = 256 # bit length
 
 # Internal helper methods
 def exponent(b,e,m):
     return pow(b,e,m)
 
-def invert(x,n):
-    return exponent(x,n-2,n)
+def invert(x,p):
+    # Assumes `p` is prime
+    return exponent(x,p-2,p)
 
 def xfromy(y):
     temp = (y*y-1) * invert(d*y*y+1,q)
@@ -28,34 +31,50 @@ def xfromy(y):
         x = q-x
     return x
 
+def bit(h,i):
+    return (ord(h[i/8]) >> (i%8)) & 1
+
 d = -121665 * invert(121666,q)
 I = exponent(2,(q-1)/4,q)
 
+# An element of the main subgroup scalar field
 class Scalar:
     def __init__(self,x):
-        if not isinstance(x,int) and not isinstance(x,long):
+        # Generated from an integer value
+        if isinstance(x,int) or isinstance(x,long):
+            self.x = x % l
+        # Generated from a hex representation
+        elif isinstance(x,str):
+            try:
+                x = binascii.unhexlify(x)
+                self.x = sum(2**i * bit(x,i) for i in range(0,b)) % l
+            except:
+                raise TypeError
+        else:
             raise TypeError
-        self.x = x % l
 
-    def invert(self):
+    # Multiplicative inversion, with an option to let 1/0 = 0 if you're into that
+    def invert(self,allow_zero=False):
         if self.x == 0:
-            raise ZeroDivisionError
+            if allow_zero:
+                return Scalar(0)
+            else:
+                raise ZeroDivisionError
         return Scalar(invert(self.x,l))
 
+    # Addition
     def __add__(self,y):
-        if isinstance(y,int):
-            return Scalar(self.x + y)
         if isinstance(y,Scalar):
             return Scalar(self.x + y.x)
         return NotImplemented
 
+    # Subtraction
     def __sub__(self,y):
-        if isinstance(y,int):
-            return Scalar(self.x - y)
         if isinstance(y,Scalar):
             return Scalar(self.x - y.x)
         return NotImplemented
 
+    # Multiplication (possibly by an integer)
     def __mul__(self,y):
         if isinstance(y,int):
             return Scalar(self.x * y)
@@ -63,258 +82,387 @@ class Scalar:
[…]

### 2020-01-11 paper/iacr.tex
Update paper title and abstract

--- 2020-01-06 paper/iacr.tex
@@
 \title{Concise Linkable Ring Signatures and Applications}
-\institute{Monero Research Lab, \email{\{surae,sarang\}@getmonero.org} \and Independent researcher, \email{randomrun@protonmail.com}}
+\institute{Monero Research Lab, \email{\{surae,sarang\}.noether@protonmail.com} \and Independent researcher, \email{randomrun@protonmail.com}}
 \author{Brandon Goodell\inst{1} \and Sarang Noether\inst{1} \and Arthur Blue\inst{2}}
@@
 \begin{abstract}
-We describe a generalization of linkable ring signatures, $d$-linkable ring signatures ($d$-LRS).
-These admit $d$-dimensional vectors of keys with a specified linking coordinate, but do not have signature sizes linear in $d$.
-We then produce an efficient $d$-LRS construction, called \textit{concise linkable spontaneous anonymous group} signatures (CLSAG), that are smaller than existing constructions without a trusted setup used in production, and are more efficient in verification over a reasonable range of anonymity set sizes.
-Security is proven using the $k$-one more discrete logarithm and decisional Diffie-Hellman hardness assumptions to show correctness, unforgeability, linkable anonymity, linkability, and non-frameability.
-We describe direct applications to signer-ambiguous confidential transactions with single or multiple asset classes.
+We describe and formalize a generalization of linkable ring signatures, $d$-linkable ring signatures ($d$-LRS), that admit multidimensional vectors of keys with a specified linking coordinate.
+These signatures are useful in trust-free signer-ambiguous transaction protocols and distributed ledger applications, but signature sizes for current implementations are $O(nd)$ for signer ambiguity set size $n$.
+We produce a new efficient $d$-LRS construction with signature size $O(n + d)$, producing smaller signatures that are faster to produce and verify over a reasonable range of anonymity set sizes than currently-deployed solutions.
+Security is proven using the $k$-one-more discrete logarithm and decisional Diffie-Hellman hardness assumptions to show correctness, unforgeability, linkable anonymity, linkability, and non-frameability.
+We describe useful applications to signer-ambiguous confidential transactions with single or multiple asset classes.
 \end{abstract}
@@
 We now introduce the hardness assumptions and security definitions that apply to a $d$-LRS construction (and, implicitly, to an LRS construction).
-In particular, we rely on the $k$-one more discrete logarithm ($k$-OMDL) and decisional Diffie-Hellman (DDH) hardness assumptions for our definitions.
+In particular, we rely on the $k$-one-more discrete logarithm ($k$-OMDL) and decisional Diffie-Hellman (DDH) hardness assumptions for our definitions.
 

### 2020-01-12 dumb448/dumb448.py
Curve library and test update

@@ -6,20 +6,21 @@
 
 import random
 import hashlib
+import binascii
 
-VERSION = 0.2 # to help with compatibility
-
-# curve parameters
+# Curve parameters
 q = 2**448 - 2**224 - 1
 l = 2**446 - 13818066809895115352007386748515426880336692474882178609894547503885
 cofactor = 4
+b = 456 # bit length
 
 # Internal helper methods
 def exponent(b,e,m):
     return pow(b,e,m)
 
-def invert(x,n):
-    return exponent(x,n-2,n)
+def invert(x,p):
+    # Assumes `p` is prime
+    return exponent(x,p-2,p)
 
 def xfromy(y):
     temp = (y*y-1) * invert(d*y*y-1,q)
@@ -28,33 +29,49 @@ def xfromy(y):
         x = q-x
     return x
 
+def bit(h,i):
+    return (ord(h[i/8]) >> (i%8)) & 1
+
 d = -39081
 
+# An element of the main subgroup scalar field
 class Scalar:
     def __init__(self,x):
-        if not isinstance(x,int) and not isinstance(x,long):
+        # Generated from an integer value
+        if isinstance(x,int) or isinstance(x,long):
+            self.x = x % l
+        # Generated from a hex representation
+        elif isinstance(x,str):
+            try:
+                x = binascii.unhexlify(x)
+                self.x = sum(2**i * bit(x,i) for i in range(0,b)) % l
+            except:
+                raise TypeError
+        else:
             raise TypeError
-        self.x = x % l
 
-    def invert(self):
+    # Multiplicative inversion, with an option to let 1/0 = 0 if you're into that
+    def invert(self,allow_zero=False):
         if self.x == 0:
-            raise ZeroDivisionError
+            if allow_zero:
+                return Scalar(0)
+            else:
+                raise ZeroDivisionError
         return Scalar(invert(self.x,l))
 
+    # Addition
     def __add__(self,y):
-        if isinstance(y,int):
-            return Scalar(self.x + y)
         if isinstance(y,Scalar):
             return Scalar(self.x + y.x)
         return NotImplemented
 
+    # Subtraction
     def __sub__(self,y):
-        if isinstance(y,int):
-            return Scalar(self.x - y)
         if isinstance(y,Scalar):
             return Scalar(self.x - y.x)
         return NotImplemented
 
+    # Multiplication (possibly by an integer)
     def __mul__(self,y):
         if isinstance(y,int):
             return Scalar(self.x * y)
[…]

### 2020-01-12 dumb448/test.py

@@ -3,350 +3,870 @@
 from dumb448 import *
 import unittest
 
-class TestPoint(unittest.TestCase):
-    def test_point_ops(self):
-        with self.assertRaises(TypeError):
-            Point('test',None)
-
-        self.assertEqual(Z+Z,Z)
-        self.assertEqual(G+Z,G)
-        self.assertEqual(Z+G,G)
-        self.assertEqual(G-G,Z)
-
-        self.assertFalse(Point(0,0).on_curve())
-        self.assertTrue(G.on_curve())
-        self.assertTrue(Z.on_curve())
-
+# Scalar class
 class TestScalar(unittest.TestCase):
-    def test_scalar_ops(self):
+    def test_init(self):
+        # Test construction using x = 1
+        s = Scalar(int(1))
+        self.assertEqual(s,Scalar(long(1)))
+        self.assertEqual(s,Scalar('010000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000'))
+        self.assertEqual(s.x,int(1))
+        self.assertEqual(s.x,long(1))
+
+        # Test construction using x = l = 0
+        s = Scalar(int(l))
+        self.assertEqual(s,Scalar(long(l)))
+        self.assertEqual(s,Scalar('000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000'))
+        self.assertEqual(s.x,int(0))
+        self.assertEqual(s.x,long(0))
+
+        # Test invalid constructions
+        with self.assertRaises(TypeError):
+            Scalar('invalid')
         with self.assertRaises(TypeError):
             Scalar(None)
-        with self.assertRaises(TypeError):
-            Scalar('test')
 
-        self.assertEqual(Scalar(0),Scalar(l))
-        self.assertEqual(Scalar(0)+Scalar(1),Scalar(1))
-        self.assertEqual(Scalar(0)-Scalar(1),Scalar(-1))
+    def test_invert(self):
+        # Test nonzero inversion
+        self.assertEqual(Scalar(1).invert(),Scalar(1))
+        self.assertEqual(Scalar(1).invert(allow_zero=True),Scalar(1))
+        self.assertEqual(Scalar(2).invert()*Scalar(2),Scalar(1))
+        self.assertEqual(Scalar(2).invert(allow_zero=True)*Scalar(2),Scalar(1))
+        
[…]

### 2020-01-12 lelantus/layer.py
Change hierarchical digest to multiscalar multiplication

@@ -5,15 +5,6 @@ from dumb25519 import *
 import groth
 from random import randint
 
-# Compute the digest of a list of points
-def digest(points,scalars):
-    if not len(points) == len(scalars):
-        raise IndexError('Digest requires the same number of points and exponents!')
-    R = Z
-    for i in range(len(points)):
-        R += points[i]*scalars[i]
-    return R
-
 # Total of N = M*T = (n_M**m_M)*(n_T**m_T) commitments
 n_M = 2
 m_M = 2
@@ -61,8 +52,8 @@ for i in range(M):
 # Subset digests
 D = []
 for i in range(T):
-    D.append(digest(C[i*M:(i+1)*M],x))
-digest_d = digest(d,x)
+    D.append(multiexp(x,C[i*M:(i+1)*M]))
+digest_d = multiexp(x,d)
 
 # Layer-2 proof
 mask_v = Scalar(0)

### 2020-01-12 dumb25519/test.py
Improved hex representation tests

@@ -6,17 +6,20 @@ import unittest
 # Scalar class
 class TestScalar(unittest.TestCase):
     def test_init(self):
+        # Test construction from hex representations
+        self.assertEqual(Scalar('0000000000000000000000000000000000000000000000000000000000000000'),Scalar(0))
+        self.assertEqual(Scalar('0100000000000000000000000000000000000000000000000000000000000000'),Scalar(1))
+        self.assertEqual(Scalar('ecd3f55c1a631258d69cf7a2def9de1400000000000000000000000000000010'),Scalar(l-1))
+        
         # Test construction using x = 1
         s = Scalar(int(1))
         self.assertEqual(s,Scalar(long(1)))
-        self.assertEqual(s,Scalar('0100000000000000000000000000000000000000000000000000000000000000'))
         self.assertEqual(s.x,int(1))
         self.assertEqual(s.x,long(1))
 
         # Test construction using x = l = 0
         s = Scalar(int(l))
         self.assertEqual(s,Scalar(long(l)))
-        self.assertEqual(s,Scalar('0000000000000000000000000000000000000000000000000000000000000000'))
         self.assertEqual(s.x,int(0))
         self.assertEqual(s.x,long(0))
 
@@ -250,13 +253,8 @@ class TestScalar(unittest.TestCase):
     def test_repr(self):
         # Test known representations
         self.assertEqual(repr(Scalar(0)),'0000000000000000000000000000000000000000000000000000000000000000')
-        self.assertEqual(str(Scalar(0)),'0000000000000000000000000000000000000000000000000000000000000000')
         self.assertEqual(repr(Scalar(1)),'0100000000000000000000000000000000000000000000000000000000000000')
-        self.assertEqual(str(Scalar(1)),'0100000000000000000000000000000000000000000000000000000000000000')
-
-        eight = Scalar('0800000000000000000000000000000000000000000000000000000000000000')
-        inv_8 = Scalar('792fdce229e50661d0da1c7db39dd30700000000000000000000000000000006')
-        self.assertEqual(eight*inv_8,Scalar(1))
+        self.assertEqual(repr(Scalar(l-1)),'ecd3f55c1a631258d69cf7a2def9de1400000000000000000000000000000010')
 
     def test_int(self):
         # Test ingeger reconstruction
@@ -298,9 +296,10 @@ class TestScalar(unittest.TestCase):
 # Point class
 class TestPoint(unittest.TestCase):
     def test_init(self):
-        # Test construction with known hex representations
[…]

### 2020-01-12 dumb448/test.py

@@ -6,17 +6,20 @@ import unittest
 # Scalar class
 class TestScalar(unittest.TestCase):
     def test_init(self):
+        # Test construction from hex representations
+        self.assertEqual(Scalar('000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000'),Scalar(0))
+        self.assertEqual(Scalar('010000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000'),Scalar(1))
+        self.assertEqual(Scalar('f24458ab92c27823558fc58d72c26c219036d6ae49db4ec4e923ca7cffffffffffffffffffffffffffffffffffffffffffffffffffffff3f00'),Scalar(l-1))
+
         # Test construction using x = 1
         s = Scalar(int(1))
         self.assertEqual(s,Scalar(long(1)))
-        self.assertEqual(s,Scalar('010000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000'))
         self.assertEqual(s.x,int(1))
         self.assertEqual(s.x,long(1))
 
         # Test construction using x = l = 0
         s = Scalar(int(l))
         self.assertEqual(s,Scalar(long(l)))
-        self.assertEqual(s,Scalar('000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000'))
         self.assertEqual(s.x,int(0))
         self.assertEqual(s.x,long(0))
 
@@ -250,13 +253,8 @@ class TestScalar(unittest.TestCase):
     def test_repr(self):
         # Test known representations
         self.assertEqual(repr(Scalar(0)),'000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000')
-        self.assertEqual(str(Scalar(0)),'000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000')
         self.assertEqual(repr(Scalar(1)),'010000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000')
[…]

### 2020-01-12 lelantus/transaction.py
Fix for aggregate Fiat-Shamir challenges

@@ -135,9 +135,11 @@ class SpendTransaction:
         spend_states = []
         self.Q = [] # input coin public keys
         self.spend_proofs = []
+        offsets = [] # for use in Fiat-Shamir challenge
         for i in range(len(q)):
             self.Q.append(G*q[i])
             offset = groth.comm(hash_to_scalar(self.Q[-1]),Scalar(0),Scalar(0))
+            offsets.append(offset)
             M = [C-offset for C in C_list] # one is a commitment to zero
 
             spend_proof,spend_state = groth.prove_initial(M,l[i],v_in[i],r_in[i],n,m)
@@ -145,7 +147,7 @@ class SpendTransaction:
             spend_states.append(spend_state)
 
         # Compute aggregate Fiat-Shamir challenge
-        x = groth.challenge(C_list,self.spend_proofs)
+        x = groth.challenge(C_list+offsets,self.spend_proofs)
 
         # Complete spend proofs
         self.spend_sigs = []
@@ -208,11 +210,13 @@ class SpendTransaction:
             signature.verify(repr(self.spend_proofs[i]),self.Q[i],self.spend_sigs[i])
 
         # Verify the spend proofs
-        x = groth.challenge(self.C_list,self.spend_proofs)
+        offsets = [] # for use in Fiat-Shamir challenge
         for i in range(len(self.spend_proofs)):
             s = hash_to_scalar(self.Q[i])
-            offset = groth.comm(s,Scalar(0),Scalar(0))
-            M = [C-offset for C in self.C_list]
+            offsets.append(groth.comm(s,Scalar(0),Scalar(0)))
+        x = groth.challenge(self.C_list+offsets,self.spend_proofs)
+        for i in range(len(self.spend_proofs)):
+            M = [C-offsets[i] for C in self.C_list]
             groth.verify(M,self.spend_proofs[i],n,m,x)
 
         # Verify the aggregate range proof

### 2020-01-24 triptych-3/test.py
Added timelock-compatible Triptych-3 code and test

@@ -1,0 +1,32 @@
+import triptych
+import unittest
+import dumb25519
+from dumb25519 import random_scalar, random_point, Scalar
+import random
+
+G = dumb25519.G
+H = dumb25519.hash_to_point('H')
+
+class TestValidProofs(unittest.TestCase):
+    def test_valid_prove_verify(self):
+        print ''
+
+        for m in [1,2]: # ring size 2,4
+            print 'Test parameter (m):',m
+            l = random.randrange(2**m) # spend index
+            r = random_scalar() # signing key
+            s = random_scalar() # commitment key
+            w = random_scalar() # timelock key
+
+            # Set keys and commitments
+            M = [random_point() for _ in range(2**m)] # possible signing keys
+            P = [random_point() for _ in range(2**m)] # corresponding commitments
+            T = [random_point() for _ in range(2**m)] # corresponding timelock commitments
+            M[l] = r*G
+            P[l] = s*G
+            T[l] = w*G
+
+            # Run test
+            self.assertTrue(triptych.verify(M,P,T,triptych.prove(M,P,T,l,r,s,w,m),m))
+
+unittest.TextTestRunner(verbosity=2,failfast=True).run(unittest.TestLoader().loadTestsFromTestCase(TestValidProofs))

### 2020-01-24 triptych-3/triptych.py

@@ -1,0 +1,311 @@
+# Proof-of-concept implementation of https://github.com/monero-project/research-lab/issues/56
+
+from dumb25519 import hash_to_point, random_scalar, Scalar, hash_to_scalar, G, random_point, Z
+import dumb25519
+import random
+import transcript
+
+H = hash_to_point('H')
+U = hash_to_point('U')
+
+# Proof structure
+class Proof:
+    def __init__(self):
+        self.J = None # linking tag
+        self.K = None # commitment tag
+        self.L = None # timelock tag
+        self.A = None
+        self.B = None
+        self.C = None
+        self.D = None
+        self.X = None # for signing keys
+        self.Y = None # for linking tags
+        self.f = None
+        self.zA = None
+        self.zC = None
+        self.z = None
+
+    def __repr__(self):
+        temp = '<TriptychProof> '
+        temp += 'J:'+repr(self.J)+'|'
+        temp += 'K:'+repr(self.K)+'|'
+        temp += 'L:'+repr(self.L)+'|'
+        temp += 'A:'+repr(self.A)+'|'
+        temp += 'B:'+repr(self.B)+'|'
+        temp += 'C:'+repr(self.C)+'|'
+        temp += 'D:'+repr(self.D)+'|'
+        temp += 'X:'+repr(self.X)+'|'
+        temp += 'Y:'+repr(self.Y)+'|'
+        temp += 'f:'+repr(self.f)+'|'
+        temp += 'zA:'+repr(self.zA)+'|'
+        temp += 'zC:'+repr(self.zC)+'|'
+        temp += 'z:'+repr(self.z)
+        return temp
+
+# Pedersen matrix commitment
+def com_matrix(v,r):
+    C = dumb25519.Z
+    for i in range(len(v)):
+        for j in range(len(v[0])):
+            C += hash_to_point('Gi',i,j)*v[i][j]
+    C += r*H
+    return C
+
+# Decompose a value with given base and size
+def decompose(val,base,size,t=int):
+    r = []
+    for i in range(size-1,-1,-1):
+        slot = base**i
+        r.append(int(val/slot))
+        val -= slot*r[-1]
+    r = list(reversed(r))
+
+    # Return int list or Scalar list
+    if t == int:
+        return r
+
+    s = []
+    for i in r:
[…]

### 2020-01-24 paper/iacr.tex
Paper update for multi-dimensional linkable ring signature construction

--- 2020-01-08 paper/iacr.tex
@@
 \subsection{Our contribution}
-We produce two instantiations of a linkable ring signature, which we call Triptych.
+We produce a family of linkable ring signatures, which we call Triptych.
 The constructions are a linkable generalization of Groth's one-of-many commitment-to-zero proving system \cite{groth}, with optimizations from Bootle \cite{bootle} applied for improvements to proof size and verification complexity.
-In one version of Triptych, the prover shows that it knows the opening of a commitment to zero within a commitment list, and also that it has constructed a linking tag using the same opening, enabling linkability.
+In the simplest version of Triptych, the prover shows that it knows the opening of a commitment to zero within a commitment set, and also that it has constructed a linking tag using the same opening, producing a linkable ring signature construction.
 We then modify Groth's ring signature definitions to include linkability and a related property, non-frameability.
 
-In the second version of Triptych, we further generalize to include a parallel list of commitments.
-Here, the prover proceeds as before to show its knowledge of an opening to a commitment in one list, as well as the construction of the linking tag.
-However, the proof also shows that the prover knows an opening of a commitment at the same position in the second commitment list.
+In an extension of Triptych, we include multiple independent sets of commitments.
+Here, the prover proceeds as before to show its knowledge of an opening to a commitment in one set, as well as the construction of the linking tag.
+However, the proof also shows that the prover knows an opening of a commitment at the same position in all other sets.
 This construction has immediate application; in some signer-ambiguous confidential transaction protocols, transaction inputs are commitments to zero, for which the signer shows it knows the opening.
@@
 \section{Protocol: parallel linkable one-of-many commitment}
-In this section, we describe a modification of the sigma protocol for $\mathcal{R}_{\text{link}}$ that permits us to prove knowledge of multiple commitments in separate sets at the same index position, while retaining the linking property in the first commitment set only.
+In this section, we describe a modification of the sigma protocol for $\mathcal{R}_{\text{link}}$ that permits us to prove knowledge of multiple commitments in $d > 1$ separate sets at the same index position, while retaining the linking property in the first commitment set only.
+This forms a version of Triptych with the same functionality as the $d$-linkable ring signature construction in \cite{clsag}, although the precise security model is a bit different.
 We later show how to apply such a construction to a signer-ambiguous transaction protocol that can demonstrate balance preservation.
 
-We wish to produce a sigma protocol for the following relation:
-$$\mathcal{R}_{\text{par}} = \left\{ \{M_i\}_{i=0}^{N-1} \subset \G, \{P_i\}_{i=0}^{N-1} \subset \G, J \in \G ; (l \in \mathbb{Z},r \in \F,s \in \F) : M_l = rG \text{ and } P_l = sG \text{ and } U = rJ \right\}$$
+We wish to produce a sigma protocol for the following relation, for some given vector dimension $d > 1$.
+$$\mathcal{R}_{\text{par}} = \left\{ \{M_{i,\alpha}\}_{i,\alpha=0}^{N-1,d-1} \subset \G^d, J \in G ; \left(l, \{r_\alpha\}_{\alpha=0}^{d-1}\right) : \{M_{l,\alpha} = r_\alpha G\}_{\alpha=0}^{d-1} \text{ and } U = r_0 J \right\}$$
 This requires only minor modifications to the protocol for $\mathcal{R}_{\text{link}}$, so we document only the modified proof elements constructed and verified in Figure \ref{fig:par}.
@@
 \fbox{\begin{minipage}{0.95\textwidth}
-$\underline{\mathcal{P}_{\text{par}}(\{M_i\},\{P_i\},J;(l,r,s)):}$
+$\underline{\mathcal{P}_{\text{par}}\left(\{M_{i,\alpha}\},J;\left(l,\{r_\alpha\}\right)\right):}$
 \begin{itemize}
-\item Define $K \equiv sJ$.
-\item Define $\mu \equiv \hs(\{M_i\},\{P_i\},J,K)$.
-\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}(M_k + \mu P_k) + \rho_jG$$
-\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv (U + \mu K)\sumk p_{k,j} + \rho_jG$$
+\item Define $K_\alpha \equiv r_\alpha J$ for $\alpha \in (0,d)$.
+\item Define $\mu_\alpha \equiv \hs\left(\alpha,\{M_{i,\alpha}\},J,\{K_\alpha\}\right)$ for $\alpha \in (0,d)$.
+\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}\left(M_{k,0} + \sum_{\alpha=1}^{d-1} \mu_\alpha M_{k,\alpha}\right) + \rho_jG$$
+\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv \left(U + \sum_{\alpha=1}^{d-1} \mu_\alpha K_\alpha\right)\sumk p_{k,j} + \rho_jG$$
 \end{itemize}
@@
 $\underline{\mathcal{P} \to \mathcal{V}:}$ \\
-$K,\{X_j\},\{Y_j\}$ \\
+$\{K_\alpha\},\{X_j\},\{Y_j\}$ \\
 
@@
 \begin{itemize}
-\item Define $z \equiv (r + \mu s)\xi^m - \sumj \rho_j\xi^j$.
+\item Define $z \equiv \left(r_0 + \sum_{\alpha=1}^{d-1} \mu_\alpha r_\alpha\right)\xi^m - \sumj \rho_j\xi^j$.
 \end{itemize}
@@
 
-$\underline{\mathcal{V}_{\text{par}}(\{M_i\},\{P_i\},J):}$
+$\underline{\mathcal{V}_{\text{par}}(\{M_{i,\alpha}\},J):}$
 \begin{itemize}
-\item Define $\mu \equiv \hs(\{M_i\},\{P_i\},J,K)$.
+\item Define $\mu_\alpha \equiv \hs\left(\alpha,\{M_{i,\alpha}\},J,\{K_\alpha\}\right)$ for $\alpha \in (0,d)$.
 \item Accept if and only if:
 \begin{eqnarray*}
-\sumk (M_k + \mu P_k) \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG &=& 0 \\
-(U + \mu K)\sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ &=& 0
+\sumk \left(M_{k,0} + \sum_{\alpha=1}^{d-1} \mu_\alpha M_{k,\alpha}\right) \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG &=& 0 \\
+\left(U + \sum_{\alpha=1}^{d-1} \mu_\alpha K_\alpha\right)\sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ &=& 0
 \end{eqnarray*}
@@
 \begin{proof}
-In the random oracle model, extraction of a witness of the form $r + \mu s$ implies knowledge of both $r$ and $s$ such that $rG = M_l$ and $sG = P_l$, similarly to the key-aggregation arguments in \cite{musig}.
-The same extraction shows that $(r + \mu s)J = U + \mu K$, which implies in particular that $rJ = U$, as required.
+In the random oracle model, extraction of a witness of the form $r_0 + \sum_{\alpha} \mu_\alpha r_\alpha$ implies knowledge of all $\{r_\alpha\}$ such that $r_\alpha G = M_{l,\alpha}$, similarly to the key-aggregation arguments in \cite{musig}.
+The same extraction shows that $\left(r_0 + \sum_{\alpha} \mu_\alpha r_\alpha\right)J = U + \sum_{\alpha} \mu_\alpha K_\alpha$, which implies in particular that $r_0J = U$, as required.
 
@@
 \section{Application: signer-ambiguous transaction protocol}
-The parallel construction described in Figure \ref{fig:par} can be used in a signer-ambiguous transaction protocol.
+The parallel construction described in Figure \ref{fig:par} can be used with $d = 2$ in a signer-ambiguous transaction protocol.
 
 Suppose a user wishes to generate a transaction consuming $W$ previously-generated outputs and generating $T$ fresh outputs.
-The user shuffles the consumed outputs within a larger list of $N$ outputs $\{M_k\}_{k=0}^{N-1}$, such that there exist indices $\{l_u\}_{u=0}^{W-1}$ where each $M_{l_u} = r_u$ for some known private key $r_u$.
-Further, assume each $M_{l_u}$ comes equipped with an amount commitment of the form $P_{l_u} \equiv \com(a_u,s_u)$ for amount $a_u$ and mask $s_u$.
-(All other $M_k$ also come equipped with a corresponding $P_k$, but the structure of these points is not relevant here.)
+The user shuffles the consumed outputs within a larger list of $N$ outputs $\{M_{k,0}\}_{k=0}^{N-1}$, such that there exist indices $\{l_u\}_{u=0}^{W-1}$ where each $M_{l_u,0} = r_u$ for some known private key $r_u$.
+Further, assume each $M_{l_u,0}$ comes equipped with an amount commitment of the form $M_{l_u,1} \equiv \com(a_u,s_u)$ for amount $a_u$ and mask $s_u$.
+(All other $M_{k,0}$ also come equipped with a corresponding $M_{k,1}$, but the structure of these points is not relevant here.)
 
@@
 Then, the user generates $W$ spend proofs, each using the following prover inputs for $u \in [0,W)$:
-$$\mathcal{P}_{par}(\{M_i\},\{P_i-P'_u\},r_u^{-1}U;(l_u,r_u,s_u-s'_u))$$
+$$\mathcal{P}_{par}(\{M_{i,\alpha}\},r_u^{-1}U;(l_u,\{r_u,s_u-s'_u\}))$$
 
@@
 Therefore, for the purpose of comparison we modify slightly the earlier version of RingCT 3.0 with a soundness fix applied from the updated version, ignoring the size and verification cost of non-proof elements.
-Another more direct comparison is to $2$-CLSAG, a linear-sized linkable ring signature construction \cite{clsag}.
+Another more direct comparison is to CLSAG, a linear-sized linkable ring signature construction \cite{clsag}.
 
-We now show size and verification comparisons of the parallel instantiation of Triptych, the earlier (modified) version of RingCT 3.0, and $2$-CLSAG.
+We now show size and verification comparisons of the parallel instantiation of Triptych with $d = 2$, the earlier (modified) version of RingCT 3.0, and $2$-CLSAG.
 For verification scaling, we also account for the use of batching in Triptych and RingCT 3.0, where generators common to multiple proofs are used only once in verification.

### 2020-03-08 paper-multi/iacr.tex
Added Triptych-2 paper and data files

\documentclass{article}
\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}
\usepackage{amsmath,amssymb,amsthm,amsfonts}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{graphics,graphicx}

\title{Triptych-2: efficient confidential transactions}
\author{Sarang Noether \\ Monero Research Lab \\ \texttt{sarang.noether@protonmail.com}}
\date{\today}

\newcommand{\G}{\mathbb{G}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\hs}{\mathsf{H}}
\newcommand{\hp}{\mathcal{H}}
\newcommand{\com}{\operatorname{Com}}
\newcommand{\A}{\mathcal{A}}

\newcommand{\sumi}{\sum_{i=0}^{n-1}}
\newcommand{\sumj}{\sum_{j=0}^{m-1}}
\newcommand{\sumk}{\sum_{k=0}^{N-1}}
\newcommand{\sumu}{\sum_{u=0}^{w-1}}

\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\begin{document}

\maketitle

\begin{abstract}
Confidential transactions are used in distributed digital assets to demonstrate the balance of values hidden in commitments, while retaining signer ambiguity.
In a previous paper, we describe how to use signer-ambiguous proofs of knowledge of the opening of multiple commitments to zero; these proofs can be combined to build confidential transactions, but require separate proofs when spending multiple input assets.
In this work, we extend our previous work to build Triptych-2, a proving system that uses a single proof to demonstrate transaction balance and the signing of multiple signer-ambiguous inputs at once.
While soundness depends on a novel dual discrete-logarithm hardness assumption, we use data from the Monero blockchain to show that Triptych-2 provides faster total batch verification time than other trust-free confidential transaction constructions.
\end{abstract}

\section{Introduction}
Distributed digital assets, starting with Bitcoin, rely on digital signatures to authorize transactions and transfer the spend authority of funds.
While early protocols based on the model established by Bitcoin have the advantage of simplicity, they lack desirable properties relating to privacy and indistinguishability.
In particular, the address/signature graph formed by the blockchain in such assets is trivially traceable, and the amounts a signature authorizes in a transaction are visible.

To protect users of distributed assets and permit better indistinguishability of transactions for fungibility, several methods have been proposed and deployed toward confidential transactions.
The CryptoNote protocol, an early proposal for obscuring transaction graphs, relied on linkable ring signatures on transaction outputs with denominated amounts \cite{cryptonote}
A later advancement to the RingCT protocol used Pedersen commitments to amounts associated with transaction outputs and extended a ring signature construction by Liu \text{et al.} to support parallel signatures in a matrix arrangement \cite{ringct,liu}.

More recent methods of maintaining transaction privacy use accumulators to represent a given state of transaction outputs.
Zerocoin \cite{zerocoin} relied on RSA accumulators and associated proofs to assert the validity of transactions, but amounts were fixed, the protocol used very large and inefficient proofs, transactions were limited to a simple burn-mint operation on a transparent chain, and the use of RSA groups required a trusted setup process.
Later work produced Zerocash \cite{zerocash}, which replaced RSA accumulators and related proofs with succinct proofs relating to Merkle tree accumulators, enabling arbitrary amounts and direct anonymous transfers.
However, like Zerocoin, Zerocash used a proving system requiring a trusted setup process; this was eventually used as the basis for the Zcash protocols.

Until recently, transaction protocols desiring robust signer ambiguity and flexible direct anonymous transfers of arbitrary amounts faced a tradeoff between a trust-free construction and efficiency in proof sizes and verification complexity.
Recent work in this area relies on one of two novel proving systems to build transactions that scale in size logarithmically with the size of the prover-specified anonymity set, while requiring no trusted setup.
A one-of-many commitment-to-zero proving system of Groth and Kohlweiss was used to build simple ring signatures and Zerocoin-style transactions, and was later extended to support accountable ring signatures more efficiently \cite{groth,bootle}.
This proving system forms the basis of Lelantus \cite{lelantus}, which extends the Zerocoin-style transaction model of \cite{groth} by using multiple-base Pedersen commitments to incorporate amounts alongside serial numbers; a modification to the proofs shows balance, and multiple proofs are needed for typical transactions.
However, Lelantus transactions allow a transaction sender to later identify when the recipient spends their funds; a mitigation to this solves the tracing problem, but at the cost of eliminating a useful one-time addressing construction that ensures recipient anonymity.
The same proving system in \cite{groth} is used in Triptych \cite{triptych}, a multi-dimensional linkable ring signature construction that can be used to build confidential transactions similarly to \cite{ringct}; Triptych notably supports one-time addressing and arbitrary amounts, while still requiring the use of multiple proofs for transactions spending multiple transaction outputs.
Interestingly, recent independent work extends \cite{groth} to support proofs on multiple commitments in a single list (as we also introduce below), with a particular application to Zether \cite{zether}; however, this uses a different approach than we take here, and results in larger proofs.

The Bulletproofs \cite{bulletproofs} proving system uses an inner-product compression method to build range and circuit satisfiability proofs with logarithmic size scaling.
Besides the increasingly widespread deployment for commitment range proofs, the underlying structure of Bulletproofs is used to build proving systems for confidential transactions.
Omniring \cite{omniring} uses similar methods to build transactions that demonstrate spend authorization for multiple signer-ambiguous transaction inputs within a single proof, while directly integrating range proving.
The result is very small proofs; however, verification is slower than other approaches, and requirements for unique group generators mean such proofs cannot be verified in efficient batches.
RingCT 3.0 \cite{rct3} also uses a Bulletproof-style construction.
In an early version, transactions required separate proofs for multiple inputs; however, an update incorporates a single proof for all inputs to a transaction.
Notably, this construction admits efficient batch verification of separate proofs; however, a limitation on the prover requires that transactions use a power-of-2 number of inputs that yields extremely poor scaling for larger transactions.

\subsection{Our contribution}
We extend the proving system in Triptych \cite{triptych} in two significant ways, which we call Triptych-2.
First, we enable the prover to show knowledge of multiple signing keys in a single proof simultaneously using one set of combined proof elements; unlike \cite{rct3}, our modification admits any number of transaction inputs without limitations.
Second, we show Pedersen commitment balance directly within the same proof; in particular, we show that a particular combination of input and output commitments sums to a commitment to zero.
We note that the soundness of the construction depends on a novel dual discrete-logarithm hardness assumption that we are not able to reduce to a standard hardness assumption; while we consider this novel assumption reasonable, it is untested.

Taken together, these changes produce a useful transaction protocol intended for efficient use in blockchain confidential transactions.
A transaction can sign for multiple signer-ambiguous inputs and prove that the transaction balances using a single proof, a major improvement to currently-deployed constructions that require multiple proofs and separate auxiliary Pedersen amount commitments.
Further, we use actual blockchain data from the Monero digital asset project to directly compare the size and verification time of Triptych-2 to that of Triptych and two separate RingCT 3.0 constructions from earlier work \cite{triptych,rct3,lelantus}.
We find that Triptych-2 provides superior verification performance compared to other trust-free confidential transaction constructions.

\section{Preliminaries}
\subsection{Public parameters}
Let $\G$ be a cyclic group in which the discrete logarithm problem is hard, and let $\F$ be its scalar field.
Let $\hs: \{0,1\}^* \to \F$ and $\hp: \{0,1\}^* \to \G$ be cryptographic hash functions.
Assume that any point of the form $G_i$ or $H_i$ (possibly with multiple indices) is a generator of $\G$ whose discrete logarithm relationship with all other such points is unknown.
Let $G, H$ be distinguished generators of $\G$ used for Pedersen commitments.
Let $U$ be a distinguished generator of $\G$.
Let $N = n^m$ be a positive integer.
Note that all such generators may be produced using public randomness; for example, the use of a suitable hash function with domain separation may be appropriate.
All such public parameters are assumed to comprise a global reference string known to all players; in particular, we generally exclude explicit reference to public parameters from algorithm definitions and Fiat-Shamir transcript hashes for readability.

\subsection{Tensor commitment}
Let $\com$ be an additively homomorphic commitment scheme that is perfectly hiding and (at least) computationally binding.
In this work, we assume use of a simple extension to the Pedersen commitment scheme: for $x,r \in \F$, define $\com(x,r) \equiv xG + rH$ to be the commitment of the value $x$ with randomness $r$.

For a three-dimensional tensor $f \equiv (f_{i,j,k}) \subset \F$ and blinding factor $r \in \F$, define the Pedersen tensor commitment
$$\com(f,r) \equiv rH + \sum_{i,j,k} f_{i,j,k} G_{i,j,k}$$
using fixed independent generators as described above.

Operations on tensors are assumed to be performed componentwise; for example, if $f \equiv (f_{i,j,k})$ and $g \equiv (g_{i,j,k})$ are such tensors over $\F$, then $f + g \equiv (f_{i,j,k} + g_{i,j,k})$, and so forth.

\subsection{Other notation}
For integers or field elements $i,j$, the Kronecker delta function $\delta(i,j)$ evaluates to $1$ if $i=j$ and $0$ otherwise, where the output is taken to be in the appropriate set.

We sometimes use index subscript notation of the form $i_j$ to indicate the $j$ digit of $i$, where such a decomposition of $i$ is taken base $n$ with padded length $m$:
$$\sum_{j=0}^m i_j n^j = i$$
This notation will be specified explicitly where confusion may occur.

\subsection{Sigma protocols}
For a given relation $\mathcal{R}$, a sigma protocol for $\mathcal{R}$ is an interactive challenge-response protocol between a prover and verifier, where the prover wishes to convince the verifier of the validity of an instance of the relation.

A sigma protocol is complete, sound, and zero-knowledge.
These definitions are well known and found, for example, in \cite{groth}.
Essentially, these properties are:
\begin{itemize}
\item \textit{Perfectly complete}: For a witness to a statement in $\mathcal{R}$, an honest prover always convinces an honest verifier of the validity.
\item \textit{Special sound}: Given a statement in $\mathcal{R}$, if the prover can produce valid proof transcripts in response to multiple verifier challenges, then it is possible to extract a witness for the statement from the transcripts.
\item \textit{Special honest-verifier zero knowledge}: Given a statement and verifier challenge, it is possible to produce a simulated transcript without knowledge of a corresponding valid witness.
\end{itemize}
Sigma protocols can be made non-interactive by replacing random verifier challenges with hash-based transcript challenges under the random oracle model; this approach is called the Fiat-Shamir heuristic \cite{fiat}.

\subsection{Hardness assumption}
We now define a novel cryptographic hardness assumption that is used later to show the soundness of our construction.

\begin{definition}[Dual-target discrete logarithm]
\label{def:dual}
Let $\G$ be a group where the discrete logarithm problem is hard, and let $\F$ be its scalar field.
Let $n > 0$.
Consider the following game between a challenger and a probabilistic polynomial-time player $\A$:
\begin{itemize}
\item The challenger chooses $G,H \in \G$ uniformly at random and sends both to $\A$.
\item $\A$ chooses and returns sets $\{G_i\}_{i=0}^{n-1},\{H_i\}_{i=0}^{n-1} \subset \G$ to the challenger.
\item The challenger chooses a set $\{\mu_i\}_{i=0}^{n-1} \subset \F$ uniformly at random and sends it to $\A$.
\item $\A$ chooses and returns a set $\{x_i\}_{i=0}^{n-1} \subset \F$ to the challenger.
\end{itemize}
We say that $\A$ wins the $(n,\epsilon,t)$-dual-target discrete logarithm game if, in time less than $t$ and with probability less than $\epsilon$, the following are true:
\begin{itemize}
\item $\sumi \mu_i \left( G_i - x_iG \right) = 0$
\item $\sumi \mu_i \left( H - x_iH_i \right) = 0$
\item There exists an index $0 \leq i < n$ such that either $x_iG \neq G_i$ or $x_iH_i \neq H$.
\end{itemize}
\end{definition}

\section{Proving system}
We now present a sigma protocol for the following relation:
\begin{multline*}
\mathcal{R} \equiv \Bigg\{ \{M_i\}_{i=0}^{N-1},\{P_i\}_{i=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \\
M_{l^{(u)}} = r^{(u)}G \; \forall \: u \in [0,w) \text{ and } r^{(u)}J^{(u)} = U \; \forall \: u \in [0,w) \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \Bigg\}
\end{multline*}
This captures the necessary elements for transaction authorization, which we describe later; knowledge of secret keys $\{r^{(u)}\}$ will show that the prover has signing authority for inputs to a transaction, and knowledge of the secret key $y$ to an amount commitment difference will show that the transaction balances.
Finally, comparison of the verifiable random function used to produce $\{J^{(u)}\}$ will be used to prevent attempts to sign for the same secret key without revealing the corresponding public key, which is important for signer ambiguity and double-spend protection within or between transactions.

Figures \ref{fig:sigma} and \ref{fig:sigma2} describes the prover and verifier interaction.
Next, we prove that the prover and verifer routines constitute a sigma protocol that is perfectly correct, special sound, and special honest-verifier zero knowledge.

\begin{figure}[htbp]
\centering
\fbox{\begin{minipage}{0.95\textwidth}
$\underline{\mathcal{P}:}$
\begin{itemize}
\item Select random $r_A \in \F$ and $\left\{a_{j,i}^{(u)}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1} \subset \F$.
Set $$\{a_{j,0}^{(u)}\}_{j,u=0}^{m-1,w-1} \equiv -\sum_{i=1}^{n-1} a_{j,0}^{(u)}$$ and define $A \equiv \com(a,r_A)$.
\item Define $\left\{\sigma_{j,i}^{(u)}\right\}_{i,j,u=0}^{n-1,m-1,w-1} \subset \F$ such that $\sigma_{j,i}^{(u)} \equiv \delta\left(l_j^{(u)},i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
Define $B \equiv \com(\sigma,r_B)$.
\item Select random $r_C \in \F$, and define $C \equiv \com(a(1-2\sigma), r_C)$.
\item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
\item For $0 \leq u < w$, define coefficients $\left\{p_{k,j}^{(u)}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p_k^{(u)}(x) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}^{(u)}x + a_{j,k}^{(u)} \right) = \delta\left(l^{(u)},k\right)x^m + \sumj p_{k,j}^{(u)}x^j$$ (using our decomposition notation).
Then define $p_{k,j} \equiv \sumu p_{k,j}^{(u)}$ and $p_k(x) \equiv \sumu p_k^{(u)}(x)$ accordingly.
\item Select random $\left\{\rho_j\right\}_{j,u=0}^{m-1,w-1}, \left\{\overline{\rho}_j^{(u)}\right\}_{j,u=0}^{m-1,w-1} \subset \F$.
\item Define aggregation coefficients $\{\mu_k\}_{k=0}^{N-1}$ using a $k$-indexed $\hs$ operation, containing all Fiat-Shamir transcript public parameters and proof elements.
\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}\mu_kM_k + \sumu \rho_j^{(u)}G$$
\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv U \sumk p_{k,j}\mu_k + \sumu \rho_j^{(u)}J^{(u)}$$
\item Define $\{Z_j\}_{j=0}^{m-1} \subset \G$ such that: $$Z_j \equiv \sumk p_{k,j}P_k + \sumu \overline{\rho}_j^{(u)}G$$
\end{itemize}

$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
$A,B,C,D,\{X_j\},\{Y_j\},\{Z_j\}$
\end{minipage}}
\caption{Sigma protocol for $\mathcal{R}$}
\label{fig:sigma}
\end{figure}

\begin{figure}[htbp]
\centering
\fbox{\begin{minipage}{0.95\textwidth}
$\underline{\mathcal{V} \to \mathcal{P}:}$ \\
$\xi \in \{0,1\}^*$ \\

$\underline{\mathcal{P}(\xi):}$
\begin{itemize}
\item Define $\left\{f_{j,i}^{(u)}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1}$ such that $f_{j,i}^{(u)} \equiv \sigma_{j,i}^{(u)}\xi + a_{j,i}^{(u)}$.
\item Define $z_A \equiv r_A + \xi r_B$ and $z_C \equiv \xi r_C + r_D$.
\item Define $\left\{z_R^{(u)}\right\}_{u=0}^{w-1} \subset \F$ such that: $$z_R^{(u)} \equiv \mu_{l^{(u)}}r^{(u)}\xi^m - \sumj \rho_j^{(u)}\xi^j$$
\item Define: $$z_S \equiv \xi^m \left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right) - \sumj \left( \xi^j \sumu \overline{\rho}_j^{(u)} \right)$$
\end{itemize}

$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
$\{f_{j,i}^{(u)}\}_{j=0,i=1,u=0}^{m-1,n-1,w-1},z_A,z_C,\{z_R^{(u)}\},z_S$ \\

$\underline{\mathcal{V}:}$
\begin{itemize}
\item For $0 \leq u < w$ and $0 \leq j < m$, set: $$f_{j,0}^{(u)} \equiv \xi - \sum_{i=1}^{n-1} f_{j,i}^{(u)}$$
\item Accept if and only if:
\begin{eqnarray}
A + \xi B &=& \com(f,z_A) \label{eqn:ab} \\
\xi C + D &=& \com(f(\xi-f),z_C) \label{eqn:cd} \\
\sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f_{j,k_j}^{(u)} \right) \right] - \sumj \xi^jX_j - \sumu z_R^{(u)}G &=& 0 \label{eqn:x} \\
U \sumk \mu_k \left[ \sumu \left( \prod_{j=0}^{m-1} f_{j,k_j}^{(u)} \right) \right] - \sumj \xi^jY_j - \sumu z_R^{(u)}J^{(u)} &=& 0 \label{eqn:y} \\
\sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f_{j,k_j}^{(u)} \right) \right] - \sumj \xi^jZ_j - \xi^m\sum_{j=0}^{T-1} Q_j - z_SG &=& 0 \label{eqn:z}
\end{eqnarray}
\end{itemize}
\end{minipage}}
\caption{Sigma protocol for $\mathcal{R}$ (continued)}
\label{fig:sigma2}
\end{figure}

\section{Security}
\begin{theorem}
The sigma protocol in Figures \ref{fig:sigma} and \ref{fig:sigma2} reflects the relation $\mathcal{R}$ and is perfectly correct, $(m+1)$-special sound, and special honest-verifier zero knowledge.
\end{theorem}

\begin{proof}
The proof proceeds similarly to that of \cite{triptych}.

To show the protocol is perfectly complete, suppose a verifier receives an honest proof.
Equation \ref{eqn:ab} holds from the identity $$\sumi \sigma_{j,i}^{(u)} = 1$$ for all $0 \leq j < m$ and $0 \leq u > w$.
Similarly, Equation \ref{eqn:cd} holds from the identity $$(\sigma_{j,i}^{(u)})^2 = \sigma_{j,i}^{(u)}$$ for all $0 \leq i < n$ and $0 \leq j < m$ and $0 \leq u < w$.

Next, we show that Equation \ref{eqn:x} holds:
\begin{eqnarray*}
&& \sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jX_j - \sumu z^{(u)}_RG \\
&=& \sumk \mu_kM_k p_k(x) - \sumj x^j \left( \sumk p_{k,j}\mu_kM_k + \sumu \rho^{(u)}_jG \right) - \sumu z^{(u)}_RG \\
&=& \sumk \mu_kM_k \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jG - \sumu z^{(u)}_RG \\
&=& \sumk \mu_kM_k \left[ x^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_jG - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right]G \\
&=& x^m\sumu \mu_{l^{(u)}}r^{(u)}G - \sumj x^j \sumu \rho^{(u)}_jG - x^m\sumu \mu_{l^{(u)}}r^{(u)}G + \sumj x^j \sumu \rho^{(u)}_jG \\
&=& 0
\end{eqnarray*}

Equation \ref{eqn:y} holds with similar algebra:
\begin{eqnarray*}
&& \sumk \mu_kU \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} \\
&=& \sumk \mu_kU p_k(x) - \sumj x^j \left( \sumk p_{k,j}\mu_kU + \sumu \rho^{(u)}_jJ^{(u)} \right) - \sumu z^{(u)}_RJ^{(u)} \\
&=& \sumk \mu_kU \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jJ^{(u)} - \sumu z^{(u)}_RJ^{(u)} \\
&=& \sumk \mu_kU \left[ x^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right](r^{(u)})^{-1}U \\
&=& x^m\sumu \mu_{l^{(u)}}U - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - x^m\sumu \mu_{l^{(u)}}U + \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U \\
&=& 0
\end{eqnarray*}

Finally, we show that Equation \ref{eqn:z} holds:
\begin{eqnarray*}
&& \sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jZ_j - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
&=& \sumk P_k p_k(x) - \sumj x^j \left( \sumk p_{k,j}P_k + \sumu \overline{\rho}^{(u)}_jG \right) - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
&=& \sumk P_k \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \overline{\rho}^{(u)}_jG - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
&=& x^m\sumu (s^{(u)}G + a_uH) - \sumj x^j \sumu \overline{\rho}^{(u)}_jG - x^m\sum_{j=0}^{T-1} (t_jG + b_jH) - x^m\left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right)G + \\
&& \sumj x^j \sumu \overline{\rho}^{(u)}_jG \\
&=& \left( \sumu a_u - \sum_{j=0}^{T-1} b_j \right)H \\
&=& 0
\end{eqnarray*}
Hence, the protocol is perfectly complete.

Next, we show that the sigma protocol is special honest-verifier zero knowledge.
To do so, we construct a simulator that, when given a random verifier challenge $\xi$, can construct a proof transcript with identical distribution to a valid proof.

Observe first that the simulator presented in the proof of Lemma 1 in \cite{bootle} translates nearly identically to our setting, since we can flatten tensor commitments to a matrix structure with the required sum property.
The simulator first chooses $B \in \G$ uniformly at random; then, the cited lemma assures a valid simulation of the proof elements  $A,C,D,z_A,z_C,\{f^{(u)}_{j,i \neq 0}\}$, and from this we may compute $\{f^{(u)}_{j,0}\}$.
In a valid proof, $B$ is also uniformly distributed.

The proof elements $\{X_j\}_{j=1}^{m-1},\{Y_j\}_{j=1}^{m-1}, \{Z_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof since the elements of $\{\rho_j\},\{\overline{\rho}_j\}$ are uniformly distributed and the discrete logarithm problem in $\G$ is hard; hence, the simulator chooses them uniformly at random.
Since the verification checks require that $X_0,Y_0,Z_0$ be uniquely determined by the other elements in the respective sets, they are selected by the simulator in this manner.

Finally, the elements $\{z^{(u)}_R\}_{u=0}^{w-1}$ and $z_S$ are independent and uniformly distributed in valid proofs given a random verifier challenge $\xi$, so the simulator may choose them uniformly at random.
Hence the protocol is special honest verifier zero-knowledge.

We claim that the protocol is $(m+1)$-special sound, where $m > 1$.
To show this, we construct an extractor that, when given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness for the statement.
In particular, we produce a modified witness for the following relation that is based on the information presented in the prover algorithm, where we define aggregation coefficients $\mu_k$ as before:
\begin{multline*}
\mathcal{R}' \equiv \Bigg\{ \{M_k\}_{k=0}^{N-1},\{P_k\}_{k=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \\
\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sumu \mu_{l^{(u)}} r^{(u)}G \text{ and } \sumu \mu_{l^{(u)}} r^{(u)}J^{(u)} = \sumu \mu_{l^{(u)}} U \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \Bigg\}
\end{multline*}
Observe that if we assume that the dual-target discrete logarithm problem is hard in $\G$, extraction of a witness for $\mathcal{R}'$ implies knowledge of a corresponding witness for $\mathcal{R}$; this in turn provides the desired soundness.

We now show that the sigma protocol is $(m+1)$-special sound for $m > 1$.
To do so, we will produce an extractor that, when provided a set of $m+1$ valid responses to corresponding distinct $m+1$ verifier challenges for the same statements, produces a witness satisfying the relation $\mathcal{R}'$.

Suppose that for a given statement, we have a set of $(m+1)$ distinct verifier challenges $\{\xi_e\}_{e=0}^m$ corresponding to distinct valid responses of this form:
$$\left\{ \{{}_ef^{(u)}_{j,i}\}, \{{}_ez^{(u)}_R\}, {}_ez_S \right\}_{e=0}^m$$
From the $3$-special soundness in \cite{bootle} and $m > 1$ we have valid extractions $\{\sigma^{(u)}_{j,i}\}_{u=0}^{w-1}$ and $\{a^{(u)}_{j,i}\}_{u=0}^{w-1}$, and the Pedersen binding property ensures that (with high probability) we have:
$${}_ef^{(u)}_{j,i} = \sigma^{(u)}_{j,i}\xi_e + a^{(u)}_{j,i} \; \forall \: e \in [0,m]$$
Using the extracted values, compute the polynomial
$$p_k(x) \equiv \sum_{u=0}^{w-1}\left[ \prod_{j=0}^{m-1} \left( \sigma^{(u)}_{j,k}x + a^{(u)}_{j,k} \right) \right]$$
for all $k \in [0,N)$.
Extraction of $\{\sigma^{(u)}_{j,i}\}_{u=0}^{w-1}$ immediately yields the signing index set $\{l^{(u)}\}_{u=0}^{w-1}$.

We have seen that $p_k$ is of degree $m$ only when $k \in \{l^{(u)}\}_{u=0}^{w-1}$.
Hence there exist sets of coefficients $\{\overline{X}_j,\overline{Y}_j,\overline{Z}_j\}_{j=0}^{m-1}$, computed uniquely from the statement and extracted values, such that Equations \ref{eqn:x}, \ref{eqn:y}, and \ref{eqn:z} are of the following form:
\begin{eqnarray*}
\xi^m \sumu \mu_{l^{(u)}}M_{l^{(u)}} + \sumj \xi^j\overline{X}_j &=& \left( \sumu z^{(u)}_R \right)G \\
\xi^m \sumu \mu_{l^{(u)}}U + \sumj \xi^j\overline{Y}_j &=& \sumu z^{(u)}_RJ^{(u)} \\
\xi^m \sumu P_{l^{(u)}} + \sumj \xi^j\overline{Z}_j - \xi^m \sum_{j=0}^{T-1} Q_j &=& z_SG
\end{eqnarray*}

Construct a Vandermonde matrix $V$ where the $e$ row is the vector $(1,\xi_e,\ldots,\xi^m_e)$.
Since all $\xi_e$ are distinct, the rows of $V$ span $\F^{m+1}$; hence there exist weights $\{\theta_e\}_{e=0}^m$ such that the resulting linear combination of rows produces the vector $(0,\ldots,0,1)$.
That is, $\sum_{e=0}^m \theta_e\xi_e^j = \delta(j,m)$.

For each of the previous three equations, we can therefore build a linear combination over $e$. For the first:
$$\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sum_{e=0}^m \theta_e\xi_e^m \left( \sumu \mu_{l^{(u)}} M_{l^{(u)}} \right) + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{X}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) G$$
We therefore can define extractions for each $r^{(u)}$:
$$r^{(u)} \equiv \frac{1}{\mu_{l^{(u)}}} \sum_{e=0}^m \theta_e {}_ez^{(u)}_R$$
Observe that the same witnesses appear in the second:
$$\sumu \mu_{l^{(u)}} U = \sum_{e=0}^m \theta_e\xi_e^m \left( \sumu \mu_{l^{(u)}} U \right) + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{Y}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) J^{(u)}$$
This means the requirements on each $r^{(u)}$ are satisfied. The third equation proceeds similarly.
$$\sumu P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = \sum_{e=0}^m \theta_e\xi_e^m \left( \sumu P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j \right) + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{Z}_j \right) = \left( \sum_{e=0}^m \theta_e {}_ez_S  \right)G$$
Hence we have $y \equiv \sum_{e=0}^m \theta_e {}_ez_S$.
\end{proof}

\section{Transaction model}
We now describe how to apply the sigma protocol for $\mathcal{R}$ in a confidential transaction model.
In such a model, funds are represented by so-called \textit{outputs} generated in transactions, which become inputs for later transactions.
Notably, in a \textit{confidential} transaction model, we wish to introduce ambiguity as to which transaction inputs are being consumed, as well as the corresponding values represented by them.

Outputs are constructed as Pedersen commitments to zero, such that an output is of the form $M \equiv rG$ with signing key $r$.
We do not consider here the method by which output keys are generated, but assume this is offloaded to another part of the transaction model.
Each output comes equipped with a value commitment $P \equiv sG + aH$, where $a$ is the amount and $s$ a blinding factor.

A user of the protocol forms an input anonymity set $\{M_i\}_{i=0}^{N-1}$ of outputs from previous transactions.
Of these, suppose that the set $\{l^{(u)}\}_{u=0}^{w-1}$ represents the indices of the $w$ outputs for which the user wishes to sign; that is, the user knows $\{r^{(u)}\}_{u=0}^{w-1}$ such that $r^{(u)}G = M_{l^{(u)}}$ for all $0 \leq u < w$.
To help ensure ambiguity of the signing indices, assume the user has shuffled the input anonymity set.
Each element of the anonymity set has a corresponding value commitment $\{P_i \equiv s_iG + a_iH\}_{i=0}^{N-1}$.

Further, the user generates a set of new outputs $\{Q_j\}_{j=0}^{T-1}$ produced by the transaction, with corresponding value commitments of the form $\{t_jG + b_jH\}_{j=0}^{T-1}$.
Because the transaction value must balance, the following must hold: $$\sum_{u=0}^{w-1} a_{l^{(u)}} = \sum_{j=0}^{T-1} b_j$$

These terms are used to form a statement using the relation $\mathcal{R}$.
The user generates a proof showing the validity of this statement with the corresponding secret values as a witness set; the proof demonstrates knowledge of the signing keys $\{r^{(u)}\}_{u=0}^{w-1}$, and the witness $y$ formed by the commitment differences demonstrates that the input and output values balance.
Provided the commitment scheme used for value representation is (at least computationally) binding, the user cannot produce such a value $y$ unless the values balance correctly; in our case, Pedersen commitments satisfy this requirement.

We call the set $\{J^{(u)}\}_{u=0}^{w-1}$ the \textit{linking tags} for the transaction.
Similar to their use in linkable ring signatures, they are used by the verifier to detect attempts to sign with a secret key multiple times, either within the same transaction or between multiple transactions.
The construction $J^{(u)} = (r^{(u)})^{-1}U$ is an injective one-way verifiable random function \cite{dodis} using the secret key $r^{(u)}$; if the verifier sees the same linking tag used elsewhere, it knows that the (unknown) secret key was used in another proof.
In our confidential transaction model, this corresponds to an attempt to double-spend funds that would be rejected.

Since the sigma protocol is special honest-verifier zero knowledge, it is witness indistinguishable.
Note, however, that an observer who sees an input anonymity set containing a commitment for which the observer knows the opening can trivially test linking tags using its own secret keys to determine if they were used in the proof.
Therefore, witness indistinguishability is assumed to apply among input commitments for which an observer does not know a corresponding opening.

\section{Efficiency}
Observe that all group operations involved in verification occur in multiscalar multiplication operations that must evaluate to zero; methods such as those in \cite{straus,pippenger} provide efficient evaluation of these operations.
Further, many group elements in these operations are globally-fixed generators that appear in all proofs.
As a result, verification of many separate independent proofs may be batched similarly to the method described in \cite{bulletproofs} and elsewhere, where random weighting of verification equations is performed and common generators are used only once.
The result is that a batch of independent proofs can be more efficiently verified using a single multiscalar multiplication operation, lowering the marginal cost per proof to verify.

We follow the same notation as before: $N$ is the size of the input anonymity set, $w$ is the number of signing indices, and $T$ is the number of output commitments used in the balance check.
Assuming that both elements of $\G$ and $\F$ occupy $32$ bytes of storage (as is the case for common elliptic curve groups using compressed point representations), we compare the size of proofs for RingCT 3.0 (two variants) \cite{rct3}, Triptych \cite{triptych}, and this work.
Note that we make some assumptions in order to produce fair comparisons here.
In Triptych and the original version of RingCT 3.0, certain commitment offsets are required as part of balance testing, which we consider, along with the multiple proofs needed in a transaction that wishes to sign for multiple inputs.
However, we ignore input set representation (which depends on implementation), range proofs (which are required for all protocols and not part of the proving systems), and any auxiliary data that would otherwise appear as part of transactions.
Table \ref{table:size} shows the results.

\begin{table}
\centering
\begin{tabular}{|ll|}
\hline
Protocol & Size (proof elements) \\
\hline
RingCT 3.0 (original) \cite{rct3} & $w(2 \lg N + 18) + w + 2$ \\
RingCT 3.0 (updated) \cite{rct3} & $2\lceil \lg(Nw) \rceil + w + 17$ \\
Triptych \cite{triptych} & $w(3 \lg N + 8) + w$ \\
Triptych-2 (this work) & $(w + 3)\lg N + w + 7$ \\
\hline
\end{tabular}
\caption{Proof size (in group/field elements) with varying anonymity set size $N$ and signing keys $w$}
\label{table:size}
\end{table}

We also examine the verification complexity of these protocols.
To do so, we examine the size of all multiscalar multiplication operations needed to verify one or more proofs in a transaction, along with balance proofs.
Table \ref{table:time} shows the results for various transaction parameters.

\begin{table}
\centering
\begin{tabular}{|ll|}
\hline
Protocol & Verification complexity \\
\hline
RingCT 3.0 (original) \cite{rct3} & $w(2\lg N + 11) + 4N + M + T + 7$ \\
RingCT 3.0 (updated) \cite{rct3} & $2\lceil \lg(Nw) \rceil + N(w + 3) + M + T + 13$ \\
Triptych \cite{triptych} & $(2 + 2w)\lg N + 2N + 4w + T + 2$ \\
Triptych-2 (this work) & $(3 + 2w)\lg N + 2N + M + T$ \\
\hline
\end{tabular}
\caption{Verification complexity with varying anonymity set size $N$, signing keys $w$, and outputs $T$}
\label{table:time}
\end{table}

Since each compared protocol scales differently with the transaction parameters, it is instructive to examine the overall size effects under real-world conditions.
To do this, we examine data from the Monero blockchain; in particular, for each transaction from 18 October 2018 to 14 February 2020, we extract the number of signed inputs, the number of newly-generated outputs, and the size of the anonymity set (in this analysis, it was constant).
Coinbase transactions, where new assets are generated by mining on a per-block basis, are ignored since they do not require this type of proof.
Figure \ref{fig:size} shows this data run against the values in \ref{table:size} with additional transaction auxiliary data (including range proofs and recipient-specific data) for increasing anonymity set size $N$.
Since all the protocols scale approximately linearly with $N$, overall verification time based on this parameter is an important bounding factor.

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{size.png}
\caption{Total chain growth by anonymity set size}
\label{fig:size}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{time.png}
\caption{Total verification time by anonymity set size}
\label{fig:time}
\end{figure}

While the updated RingCT 3.0 protocol from \cite{rct3} yields superior space scaling, its padding requirement that $w$ be a power of $2$ (padded to reach such a value) results in poor verification time scaling.
Comparatively, our construction results in lower overall verification complexity at the expense of overall size scaling.

\bibliographystyle{plain}
\bibliography{main}

\end{document}

### 2020-03-09 player.py
Minor change to integer type conversion

@@ -166,7 +166,7 @@ class Player:
             raise Exception('Incorrect state!')
 
         self.beta[friend.get_ident()] = random_scalar()
-        d = pow(c,self.gamma.x,friend.get_public_key().N**2)
+        d = pow(c,int(self.gamma),friend.get_public_key().N**2)
         d = (d*friend.get_public_key().encrypt(-self.beta[friend.get_ident()])) % friend.get_public_key().N**2
 
         return d

### 2020-03-12 paper-multi/iacr.tex
Updated Triptych-2 paper

@@
 
-\title{Triptych-2: efficient confidential transactions}
+\title{Triptych-2: efficient proofs for confidential transactions}
 \author{Sarang Noether \\ Monero Research Lab \\ \texttt{sarang.noether@protonmail.com}}
@@
 Confidential transactions are used in distributed digital assets to demonstrate the balance of values hidden in commitments, while retaining signer ambiguity.
-In a previous paper, we describe how to use signer-ambiguous proofs of knowledge of the opening of multiple commitments to zero; these proofs can be combined to build confidential transactions, but require separate proofs when spending multiple input assets.
-In this work, we extend our previous work to build Triptych-2, a proving system that uses a single proof to demonstrate transaction balance and the signing of multiple signer-ambiguous inputs at once.
-While soundness depends on a novel dual discrete-logarithm hardness assumption, we use data from the Monero blockchain to show that Triptych-2 provides faster total batch verification time than other trust-free confidential transaction constructions.
+Previous work describes a signer-ambiguous proof of knowledge of the opening of commitments to zero at the same index across multiple public commitment sets and the evaluation of a verifiable random function used as a linking tag, and uses this to build a linkable ring signature called Triptych that can be used as a building block for a confidential transaction model.
+In this work, we extend Triptych to build Triptych-2, a proving system that proves knowledge of openings of multiple commitments to zero within a single set, correct construction of a verifiable random function evaluated at each opening, and value balance across a separate list of commitments within a single proof.
+While soundness depends on a novel dual discrete-logarithm hardness assumption, we use data from the Monero blockchain to show that Triptych-2 can be used in a confidential transaction model to provide faster total batch verification time than other state-of-the-art constructions without a trusted setup.
 \end{abstract}
@@
 While early protocols based on the model established by Bitcoin have the advantage of simplicity, they lack desirable properties relating to privacy and indistinguishability.
-In particular, the address/signature graph formed by the blockchain in such assets is trivially traceable, and the amounts a signature authorizes in a transaction are visible.
+In particular, the address and signature graph formed by the blockchain in such assets is trivially traceable, and the amounts a signature authorizes in a transaction are visible.
 
 To protect users of distributed assets and permit better indistinguishability of transactions for fungibility, several methods have been proposed and deployed toward confidential transactions.
-The CryptoNote protocol, an early proposal for obscuring transaction graphs, relied on linkable ring signatures on transaction outputs with denominated amounts \cite{cryptonote}
-A later advancement to the RingCT protocol used Pedersen commitments to amounts associated with transaction outputs and extended a ring signature construction by Liu \text{et al.} to support parallel signatures in a matrix arrangement \cite{ringct,liu}.
+The CryptoNote protocol, an early proposal for obscuring transaction graphs, relies on linkable ring signatures on transaction outputs with denominated amounts \cite{cryptonote}; a transaction includes a separate signature for each such amount, yielding poor scaling.
+A later advancement to the RingCT protocol \cite{ringct} used Pedersen commitments to amounts associated with transaction outputs and extended a ring signature construction by Liu \text{et al.} \cite{liu} to support parallel signatures in a matrix arrangement, removing the need for denominated transaction outputs altogether.
+However, both of these constructions use linkable ring signatures that scale linearly in size with the size of the anonymity set used in each signature.
 
@@
 Until recently, transaction protocols desiring robust signer ambiguity and flexible direct anonymous transfers of arbitrary amounts faced a tradeoff between a trust-free construction and efficiency in proof sizes and verification complexity.
-Recent work in this area relies on one of two novel proving systems to build transactions that scale in size logarithmically with the size of the prover-specified anonymity set, while requiring no trusted setup.
-A one-of-many commitment-to-zero proving system of Groth and Kohlweiss was used to build simple ring signatures and Zerocoin-style transactions, and was later extended to support accountable ring signatures more efficiently \cite{groth,bootle}.
+Recent work in this area generally relies on one of two novel proving systems to build transactions that scale in size logarithmically with the size of the prover-specified anonymity set, while requiring no trusted setup.
+A one-of-many commitment-to-zero proving system of Groth and Kohlweiss \cite{groth} was used to build simple ring signatures and Zerocoin-style transactions, and was later extended to support accountable ring signatures more efficiently by Bootle \cite{bootle}.
 This proving system forms the basis of Lelantus \cite{lelantus}, which extends the Zerocoin-style transaction model of \cite{groth} by using multiple-base Pedersen commitments to incorporate amounts alongside serial numbers; a modification to the proofs shows balance, and multiple proofs are needed for typical transactions.
@@
 The same proving system in \cite{groth} is used in Triptych \cite{triptych}, a multi-dimensional linkable ring signature construction that can be used to build confidential transactions similarly to \cite{ringct}; Triptych notably supports one-time addressing and arbitrary amounts, while still requiring the use of multiple proofs for transactions spending multiple transaction outputs.
-Interestingly, recent independent work extends \cite{groth} to support proofs on multiple commitments in a single list (as we also introduce below), with a particular application to Zether \cite{zether}; however, this uses a different approach than we take here, and results in larger proofs.
+Interestingly, recent independent work extends \cite{groth} to support proofs on multiple commitments in a single list (as we also introduce below), with a particular application to Zether \cite{zether}; however, this uses a different approach than we take here, and seems to result in larger proofs.
 
 The Bulletproofs \cite{bulletproofs} proving system uses an inner-product compression method to build range and circuit satisfiability proofs with logarithmic size scaling.
-Besides the increasingly widespread deployment for commitment range proofs, the underlying structure of Bulletproofs is used to build proving systems for confidential transactions.
-Omniring \cite{omniring} uses similar methods to build transactions that demonstrate spend authorization for multiple signer-ambiguous transaction inputs within a single proof, while directly integrating range proving.
+Besides an increasingly widespread deployment for commitment range proofs, the underlying structure of Bulletproofs is used to construct more specialized proving systems for confidential transactions.
+Omniring \cite{omniring} uses this method to build transactions that demonstrate spend authorization for multiple signer-ambiguous transaction inputs within a single proof, while directly integrating range proving.
 The result is very small proofs; however, verification is slower than other approaches, and requirements for unique group generators mean such proofs cannot be verified in efficient batches.
 RingCT 3.0 \cite{rct3} also uses a Bulletproof-style construction.
-In an early version, transactions required separate proofs for multiple inputs; however, an update incorporates a single proof for all inputs to a transaction.
-Notably, this construction admits efficient batch verification of separate proofs; however, a limitation on the prover requires that transactions use a power-of-2 number of inputs that yields extremely poor scaling for larger transactions.
+In an early version, transactions required separate proofs for multiple inputs; while an update incorporates a single proof for all inputs to a transaction, it also requires that the number of inputs be padded to a power of two, which can yield poor verification complexity.
 
@@
 First, we enable the prover to show knowledge of multiple signing keys in a single proof simultaneously using one set of combined proof elements; unlike \cite{rct3}, our modification admits any number of transaction inputs without limitations.
-Second, we show Pedersen commitment balance directly within the same proof; in particular, we show that a particular combination of input and output commitments sums to a commitment to zero.
-We note that the soundness of the construction depends on a novel dual discrete-logarithm hardness assumption that we are not able to reduce to a standard hardness assumption; while we consider this novel assumption reasonable, it is untested.
+We retain the verifiable random function evaluation that produces linking tags, which are required for the detection of repeat signing with the same commitment opening across proofs.
+Second, we show Pedersen commitment value balance directly within the same proof; in particular, we show that a particular combination of input and output commitments sums to a commitment to zero.
+We note that the soundness of the resulting proving system depends on a novel dual discrete-logarithm hardness assumption that we are not able to reduce to a standard hardness assumption; while we consider this novel assumption reasonable, it is untested.
 
-Taken together, these changes produce a useful transaction protocol intended for efficient use in blockchain confidential transactions.
+Taken together, these changes have application to a transaction protocol for efficient use in blockchain confidential transactions that does not require any trusted setup process.
 A transaction can sign for multiple signer-ambiguous inputs and prove that the transaction balances using a single proof, a major improvement to currently-deployed constructions that require multiple proofs and separate auxiliary Pedersen amount commitments.
-Further, we use actual blockchain data from the Monero digital asset project to directly compare the size and verification time of Triptych-2 to that of Triptych and two separate RingCT 3.0 constructions from earlier work \cite{triptych,rct3,lelantus}.
-We find that Triptych-2 provides superior verification performance compared to other trust-free confidential transaction constructions.
+Further, we use actual blockchain data from the Monero digital asset project to directly compare the overall size and verification time of Triptych-2 to that of Triptych and two separate RingCT 3.0 constructions.
+We find that Triptych-2 provides superior verification performance compared to other trust-free confidential transaction constructions, with competitive size scaling.
 
@@
 Let $\hs: \{0,1\}^* \to \F$ and $\hp: \{0,1\}^* \to \G$ be cryptographic hash functions.
-Assume that any point of the form $G_i$ or $H_i$ (possibly with multiple indices) is a generator of $\G$ whose discrete logarithm relationship with all other such points is unknown.
-Let $G, H$ be distinguished generators of $\G$ used for Pedersen commitments.
-Let $U$ be a distinguished generator of $\G$.
-Let $N = n^m$ be a positive integer.
+Let $N = n^m$ be a positive integer, where $m > 1$ (for our construction, we will use $n = 2$.
+Assume that $G$, $H$, $U$, and any point of the form $G_i$ or $H_i$ (possibly with multiple indices) are uniformly random generators of $\G$ whose discrete logarithm relationship to each other is unknown.
 Note that all such generators may be produced using public randomness; for example, the use of a suitable hash function with domain separation may be appropriate.
@@
 Let $\com$ be an additively homomorphic commitment scheme that is perfectly hiding and (at least) computationally binding.
-In this work, we assume use of a simple extension to the Pedersen commitment scheme: for $x,r \in \F$, define $\com(x,r) \equiv xG + rH$ to be the commitment of the value $x$ with randomness $r$.
+In this work, we assume use of a simple extension to the Pedersen commitment scheme: for $x,r \in \F$, define $\com(x,r) \equiv rG + xH$ to be the commitment of the value $x$ with randomness $r$.
 
 For a three-dimensional tensor $f \equiv (f_{i,j,k}) \subset \F$ and blinding factor $r \in \F$, define the Pedersen tensor commitment
-$$\com(f,r) \equiv rH + \sum_{i,j,k} f_{i,j,k} G_{i,j,k}$$
+$$\com(f,r) \equiv rG + \sum_{i,j,k} f_{i,j,k} G_{i,j,k}$$
 using fixed independent generators as described above.
@@
 We sometimes use index subscript notation of the form $i_j$ to indicate the $j$ digit of $i$, where such a decomposition of $i$ is taken base $n$ with padded length $m$:
-$$\sum_{j=0}^m i_j n^j = i$$
+$$\sum_{j=0}^{m-1} i_j n^j = i$$
 This notation will be specified explicitly where confusion may occur.
@@
 \subsection{Sigma protocols}
-For a given relation $\mathcal{R}$, a sigma protocol for $\mathcal{R}$ is an interactive challenge-response protocol between a prover and verifier, where the prover wishes to convince the verifier of the validity of an instance of the relation.
+For a given relation $\mathcal{R}$, a sigma protocol for $\mathcal{R}$ is an interactive challenge-response protocol between a prover and verifier, where the prover wishes to convince the verifier it knows a witness corresponding to a statement in $\mathcal{R}$.
 
@@
 \item \textit{Special sound}: Given a statement in $\mathcal{R}$, if the prover can produce valid proof transcripts in response to multiple verifier challenges, then it is possible to extract a witness for the statement from the transcripts.
-\item \textit{Special honest-verifier zero knowledge}: Given a statement and verifier challenge, it is possible to produce a simulated transcript without knowledge of a corresponding valid witness.
+\item \textit{Special honest-verifier zero knowledge}: Given a statement and known verifier challenge, it is possible to produce a simulated transcript without knowledge of a corresponding valid witness.
 \end{itemize}
@@
 
-\begin{definition}[Dual-target discrete logarithm]
+\begin{definition}[Dual-target discrete logarithm problem]
 \label{def:dual}
-Let $\G$ be a group where the discrete logarithm problem is hard, and let $\F$ be its scalar field.
+Let $\G$ be a group in which the discrete logarithm problem is hard, and let $\F$ be its scalar field.
 Let $n > 0$.
@@
 \end{itemize}
-We say that $\A$ wins the $(n,\epsilon,t)$-dual-target discrete logarithm game if, in time less than $t$ and with probability less than $\epsilon$, the following are true:
+We say that $\A$ wins the $(n,\epsilon,t)$-dual-target discrete logarithm game if, in time less than $t$ and with probability at least $\epsilon$, the following are true:
 \begin{itemize}
@@
 \end{multline*}
-This captures the necessary elements for transaction authorization, which we describe later; knowledge of secret keys $\{r^{(u)}\}$ will show that the prover has signing authority for inputs to a transaction, and knowledge of the secret key $y$ to an amount commitment difference will show that the transaction balances.
-Finally, comparison of the verifiable random function used to produce $\{J^{(u)}\}$ will be used to prevent attempts to sign for the same secret key without revealing the corresponding public key, which is important for signer ambiguity and double-spend protection within or between transactions.
+This captures the necessary elements for transaction authorization, which we describe later; knowledge of signing keys $\{r^{(u)}\}$ will show that the prover has signing authority for inputs to a transaction, and knowledge of the secret key $y$ to an amount commitment difference will show that the transaction amounts balance.
+Finally, comparison of the verifiable random function used to produce $\{J^{(u)}\}$ will be used to prevent attempts to sign for the same secret key without revealing the corresponding public key, which is important for signer ambiguity and double-spend protection within or between proofs.
 
-Figures \ref{fig:sigma} and \ref{fig:sigma2} describes the prover and verifier interaction.
+Figures \ref{fig:sigma} and \ref{fig:sigma2} describe the prover and verifier interaction.
 Next, we prove that the prover and verifer routines constitute a sigma protocol that is perfectly correct, special sound, and special honest-verifier zero knowledge.
@@
 \begin{proof}
-The proof proceeds similarly to that of \cite{triptych}.
+The proof proceeds similarly to that of \cite{triptych}, which in turn follows the methods in \cite{groth,bootle}.
 
 To show the protocol is perfectly complete, suppose a verifier receives an honest proof.
+We wish to show that all verifier equations hold.
 Equation \ref{eqn:ab} holds from the identity $$\sumi \sigma_{j,i}^{(u)} = 1$$ for all $0 \leq j < m$ and $0 \leq u > w$.
@@
 
-We now show that the sigma protocol is $(m+1)$-special sound for $m > 1$.
-To do so, we will produce an extractor that, when provided a set of $m+1$ valid responses to corresponding distinct $m+1$ verifier challenges for the same statements, produces a witness satisfying the relation $\mathcal{R}'$.
-
 Suppose that for a given statement, we have a set of $(m+1)$ distinct verifier challenges $\{\xi_e\}_{e=0}^m$ corresponding to distinct valid responses of this form:
@@
 We now describe how to apply the sigma protocol for $\mathcal{R}$ in a confidential transaction model.
-In such a model, funds are represented by so-called \textit{outputs} generated in transactions, which become inputs for later transactions.
+In such a model, a transaction consumes so-called \textit{outputs} generated in previous transactions, and produces new outputs for use in later transactions.
 Notably, in a \textit{confidential} transaction model, we wish to introduce ambiguity as to which transaction inputs are being consumed, as well as the corresponding values represented by them.
 
-Outputs are constructed as Pedersen commitments to zero, such that an output is of the form $M \equiv rG$ with signing key $r$.
+Outputs are constructed as Pedersen commitments to zero, such that an output public key is of the form $M \equiv rG$ with signing key $r$.
 We do not consider here the method by which output keys are generated, but assume this is offloaded to another part of the transaction model.
@@
 
-A user of the protocol forms an input anonymity set $\{M_i\}_{i=0}^{N-1}$ of outputs from previous transactions.
+A user of the protocol forms an anonymity set $\{M_i\}_{i=0}^{N-1}$ of outputs from previous transactions.
 Of these, suppose that the set $\{l^{(u)}\}_{u=0}^{w-1}$ represents the indices of the $w$ outputs for which the user wishes to sign; that is, the user knows $\{r^{(u)}\}_{u=0}^{w-1}$ such that $r^{(u)}G = M_{l^{(u)}}$ for all $0 \leq u < w$.
-To help ensure ambiguity of the signing indices, assume the user has shuffled the input anonymity set.
+To help ensure ambiguity of the signing indices, assume the user has shuffled the anonymity set.
 Each element of the anonymity set has a corresponding value commitment $\{P_i \equiv s_iG + a_iH\}_{i=0}^{N-1}$.
 
-Further, the user generates a set of new outputs $\{Q_j\}_{j=0}^{T-1}$ produced by the transaction, with corresponding value commitments of the form $\{t_jG + b_jH\}_{j=0}^{T-1}$.
+Further, the user generates a set of new outputs produced by the transaction, with corresponding value commitments of the form $\{Q_j \equiv t_jG + b_jH\}_{j=0}^{T-1}$.
 Because the transaction value must balance, the following must hold: $$\sum_{u=0}^{w-1} a_{l^{(u)}} = \sum_{j=0}^{T-1} b_j$$
+Note that there is no anonymity set for outputs generated by the transaction.
 
@@
 
-We call the set $\{J^{(u)}\}_{u=0}^{w-1}$ the \textit{linking tags} for the transaction.
+We call the elements of the set $\{J^{(u)}\}_{u=0}^{w-1}$ the \textit{linking tags} for the transaction.
 Similar to their use in linkable ring signatures, they are used by the verifier to detect attempts to sign with a secret key multiple times, either within the same transaction or between multiple transactions.
-The construction $J^{(u)} = (r^{(u)})^{-1}U$ is an injective one-way verifiable random function \cite{dodis} using the secret key $r^{(u)}$; if the verifier sees the same linking tag used elsewhere, it knows that the (unknown) secret key was used in another proof.
-In our confidential transaction model, this corresponds to an attempt to double-spend funds that would be rejected.
+The construction $J^{(u)} = (r^{(u)})^{-1}U$ is an injective one-way verifiable random function \cite{dodis} using the secret key $r^{(u)}$; if the verifier sees the same linking tag used elsewhere, it knows that the (unknown) secret key was used again.
+In our confidential transaction model, this corresponds to an attempt to double-spend funds that would be rejected by the verifier.
 
-Since the sigma protocol is special honest-verifier zero knowledge, it is witness indistinguishable.
+Since the sigma protocol is special honest-verifier zero knowledge, it is witness indistinguishable \cite{cramer}.
 Note, however, that an observer who sees an input anonymity set containing a commitment for which the observer knows the opening can trivially test linking tags using its own secret keys to determine if they were used in the proof.
@@
 
-We follow the same notation as before: $N$ is the size of the input anonymity set, $w$ is the number of signing indices, and $T$ is the number of output commitments used in the balance check.
+We follow the same notation as before: $N = 2^m$ is the size of the input anonymity set for varying $m > 1$, $w$ is the number of signing indices, and $T$ is the number of output commitments used in the balance check.
 Assuming that both elements of $\G$ and $\F$ occupy $32$ bytes of storage (as is the case for common elliptic curve groups using compressed point representations), we compare the size of proofs for RingCT 3.0 (two variants) \cite{rct3}, Triptych \cite{triptych}, and this work.
@@
 Since each compared protocol scales differently with the transaction parameters, it is instructive to examine the overall size effects under real-world conditions.
-To do this, we examine data from the Monero blockchain; in particular, for each transaction from 18 October 2018 to 14 February 2020, we extract the number of signed inputs, the number of newly-generated outputs, and the size of the anonymity set (in this analysis, it was constant).
+To do this, we examine data from the Monero blockchain; in particular, for each transaction from 18 October 2018 to 14 February 2020, we extract the number of consumed outputs and the number of newly-generated outputs.
 Coinbase transactions, where new assets are generated by mining on a per-block basis, are ignored since they do not require this type of proof.
-Figure \ref{fig:size} shows this data run against the values in \ref{table:size} with additional transaction auxiliary data (including range proofs and recipient-specific data) for increasing anonymity set size $N$.
-Since all the protocols scale approximately linearly with $N$, overall verification time based on this parameter is an important bounding factor.
+Figure \ref{fig:size} shows this data run against the values in Table \ref{table:size} with additional transaction auxiliary data (including range proofs and recipient-specific data) for increasing anonymity set size $N$.
+Since verification complexity in all the protocols scales approximately linearly with $N$, overall verification time based on this parameter is an important bounding factor.
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{size.png}
+\includegraphics[width=0.6\textwidth]{size.png}
 \caption{Total chain growth by anonymity set size}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{time.png}
+\includegraphics[width=0.6\textwidth]{time.png}
 \caption{Total verification time by anonymity set size}
@@
 
-While the updated RingCT 3.0 protocol from \cite{rct3} yields superior space scaling, its padding requirement that $w$ be a power of $2$ (padded to reach such a value) results in poor verification time scaling.
+While the updated RingCT 3.0 protocol from \cite{rct3} yields superior space scaling, its requirement that $w$ be a power of two (padded to reach such a value) results in poor verification time scaling.
 Comparatively, our construction results in lower overall verification complexity at the expense of overall size scaling.

### 2020-03-30 paper/iacr.tex
Updated paper

--- 2020-01-08 paper/iacr.tex
@@
-\documentclass{article}
-\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}
-\usepackage{amsmath,amssymb,amsthm,amsfonts}
-\usepackage[utf8]{inputenc}
-\usepackage{hyperref}
-\usepackage{graphicx}
+\documentclass{llncs}
+\pagestyle{headings}
 
-\title{Triptych: logarithmic-sized linkable ring signatures with applications}
-\author{Sarang Noether and Brandon Goodell \\ Monero Research Lab \\ \texttt{\{sarang,surae\}.noether@protonmail.com}}
-\date{\today}
+\usepackage{enumerate}
+\usepackage{amsmath,amssymb}
 
-\newcommand{\G}{\mathbb{G}}
-\newcommand{\F}{\mathbb{F}}
-\newcommand{\com}{\operatorname{Com}}
-\newcommand{\hs}{\mathcal{H}}
-\newcommand{\hp}{\mathbb{H}}
-
-\newcommand{\A}{\mathcal{A}}
-
-\newcommand{\sumi}{\sum_{i=0}^{n-1}}
-\newcommand{\sumj}{\sum_{j=0}^{m-1}}
-\newcommand{\sumk}{\sum_{k=0}^{N-1}}
-
-\newtheorem{theorem}{Theorem}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
+\title{Concise Linkable Ring Signatures and Forgery Against Adversarial Keys}
+\institute{Monero Research Lab, \email{\{surae,sarang\}@getmonero.org} \and Independent researcher, \email{randomrun@protonmail.com}}
+\author{Brandon Goodell\inst{1} \and Sarang Noether\inst{1} \and Arthur Blue\inst{2}}
 
 \begin{document}
-
 \maketitle
@@
 \begin{abstract}
-Ring signatures are a common construction used to provide signer ambiguity among a non-interactive set of public keys specified at the time of signing.
-Unlike early approaches where signature size is linear in the size of the signer anonymity set, current optimal solutions either require centralized trusted setups or produce signatures logarithmic in size.
-However, few also provide linkability, a property used to determine whether the signer of a message has signed any previous message, possibly with restrictions on the anonymity set choice.
-Here we introduce Triptych, a family of linkable ring signatures without trusted setup that is based on generalizations of zero-knowledge proofs of knowledge of commitment openings to zero.
-We demonstrate applications of Triptych in signer-ambiguous transaction protocols by extending the construction to openings of parallel commitments in independent anonymity sets.
-Signatures are logarithmic in the anonymity set size and, while verification complexity is linear, collections of proofs can be efficiently verified in batches.
-We show that for anonymity set sizes practical for use in distributed protocols, Triptych offers competitive performance with a straightforward construction.
+We demonstrate that a version of non-slanderability is a natural definition of unforgeability for linkable ring signatures.
+We present a linkable ring signature construction with concise signatures and multi-dimensional keys that is linkably anonymous if a variation of the decisional Diffie-Hellman problem with random oracles is hard, linkable if key aggregation is a one-way function, and non-slanderable if a one-more variation of the discrete logarithm problem is hard.
+We remark on some applications in signer-ambiguous confidential transaction models without trusted setup.
 \end{abstract}
@@
 \section{Introduction}
-First introduced in \cite{rivest} with respect to RSA groups, ring signatures permit the signing of messages using public key sets not fixed in advance, without the need of a trusted group manager.
-Earlier constructions lacked such flexibility, requiring either centralized key setup or the establishment of fixed signing sets.
-Later work \cite{bender} established more robust security models for unforgeability and anonymity, capturing realistic threat models where an adversary is permitted to corrupt keys, convince honest signers to include malicious anonymity set members, or obtain signatures in advance.
 
-Since a ring signature has an anonymity set of public keys, one of which is the true signer, the detection of signing by the same key requires an additional property, linkability.
-A linkable ring signature \cite{lsag} enables verifiers to determine whether the (unknown) signer of a message has signed other messages.
-Such a construction was proposed for election applications, where it is necessary to ensure that votes are anonymous, but voters are permitted to vote only once on a particular issue.
-The construction in \cite{lsag}, with a hash-trapdoor structure similar to that of \cite{schnorr}, is of particular interest due to potential flexibility in linking; while its linking is limited to signer-selected but unchanging signer anonymity sets, it permits linking on a per-issue basis.
-Additional recent work in \cite{backes} introduces the property of linkable anonymity, using sets of signatures and establishing restrictions on key corruption.
-Other related interesting properties like traceability \cite{fs,f} imply stronger capabilities, where an attempt to sign two messages with the same key permits verifiers to identify the signer.
+First introduced in \cite{rivest} in the RSA setting and in \cite{liu2004linkable} in the discrete logarithm setting, ring signatures permit message signing on behalf of a set of public keys rather than a single public key.
+Ring signatures see myriad applications ranging from lightweight anonymous authentication in \cite{yang2015lightweight} to transaction protocols like Monero in \cite{noether2016ring} and CryptoNote in \cite{van2013cryptonote}.
+A verifier is assured that the signer knows the private key of at least one of these public keys, which are called ring members.
+Ring signatures are anonymous or signer-ambiguous in the sense that the verifier does not learn information from the signature about which key is the signer.
+We stress that methods of practical analysis such as those of  \cite{moser2018empirical,quesnelle2017linkability} can exploit metadata in real-life applications of anonymous authentication protocols to reduce anonymity.
 
-Linkable ring signatures have seen particular applications in signer-ambiguous transaction protocols.
-In such an application, transactions are authorized by a ring signature whose signing anonymity set consists of previously-generated transaction outputs.
-A signature demonstrates that the signer controls the private key of one such output without revealing which is the signer, and linkability is used to assure verifiers that output has not been used in another signature (signifying a double-spend attempt).
+Group signature constructions preceding \cite{rivest,liu2004linkable} require some degree of interactivity, a fixed set of participants, a trusted group manager or other trusted setup, or hardness assumptions not based on the discrete logarithm problem.
+Since \cite{rivest}, ring signatures have enjoyed many improvements, extensions, and modifications.
+For example, ring signatures are constructed in the bilinear pairing setting in \cite{zhang2002id}, key structures are generalized in \cite{abe20021}, security definitions are improved in \cite{bender2006ring}, signature size is improved in \cite{fujisaki2011sub,gu2018constant}, and traceability is introduced in \cite{fujisaki2007traceable}.
 
-A practical consideration for the use of linkable ring signatures in transaction protocols is how signature size and verification time scale with the size of the anonymity set.
-In common applied constructions like \cite{mlsag,clsag}, signature size and verification time scale linearly with the size of the signing ambiguity set; since such signatures are typically included in a public distributed data structure like a blockchain, there is a balance between the size of the anonymity set and the requirements for storage and verification.
-Recent protocol work in this area mitigates the size restriction.
-For example, in \cite{rct3}, the authors introduce a confidential transaction protocol based on a proving system whose size scales logarithmically with the anonymity set size, and which includes a method for demonstrating amount balance; amount commitment range proving is offloaded to other constructions like \cite{bulletproofs}.
-In \cite{omniring}, the authors use a more general proving technique to accomplish a similar goal; however, the protocol offers further size benefits by integrating commitment range proofs into the proof structure directly, taking advantage of the logarithmic proof size.
+Linkable ring signature (LRS) constructions were first introduced in \cite{liu2004linkable}; in the context of transaction protocols, linkable ring signatures are the basis for anonymous transaction authentication.
+Linkable ring signatures guarantee that two signatures with the same ring on arbitrary messages can be publicly linked if signed using the same key.
+An implementation is presented in \cite{liu2004linkable} in the discrete logarithm setting; that implementation functions for similar reasons as Schnorr signatures in \cite{schnorr1991efficient}.
 
-Other signer-ambiguous transaction protocols not based on linkable ring signatures offer more competitive performance.
-For example, protocols like \cite{zcash} produce maximal theoretical signer ambiguity through the use of zero-knowledge Merkle proofs (among others) that offer extremely small proofs with low verification time, but at the cost of a trusted structured setup process that arises from the underlying proving system \cite{groth16}.
-Like this work, \cite{lelantus} is a transaction protocol also based on \cite{groth}; however, it is intended to operate on commitments similar to those used in \cite{zerocoin} but with the inclusion of amounts, and has limitations on addressing and sender tracing.
+The signature linking tags in \cite{liu2004linkable} are unsuitable for applications where signatures must be linked key-by-key, not ring-by-ring (such as for ``double-signing'' protection in a setting where users generate new keys over time and select \textit{ad hoc} ring members).
+Resistance to double-signing attempts is ensured using linking tags as described in \cite{van2013cryptonote} (therein called key images).
+More recent work of \cite{noether2016ring} extends the approach of \cite{liu2004linkable} to enable an anonymous confidential transaction model with \textit{ad hoc} ring member selection.
+In \cite{noether2016ring}, transaction amounts are replaced with Pedersen commitments to amounts together with range proofs.
+Signatures are constructed from key vectors including differences of amount commitments as one of the keys.
+However, the proofs in \cite{noether2016ring} are informal and not based on rigorous security models.
 
-\subsection{Our contribution}
-We produce two instantiations of a linkable ring signature, which we call Triptych.
-The constructions are a linkable generalization of Groth's one-of-many commitment-to-zero proving system \cite{groth}, with optimizations from Bootle \cite{bootle} applied for improvements to proof size and verification complexity.
-In one version of Triptych, the prover shows that it knows the opening of a commitment to zero within a commitment list, and also that it has constructed a linking tag using the same opening, enabling linkability.
-We then modify Groth's ring signature definitions to include linkability and a related property, non-frameability.
+Alternatives to ring signatures like more general zero-knowledge proving systems typically require a trusted party to honestly perform a setup process (as in \cite{groth,ben2014succinct,groth2018updatable}) or lack practical efficiency for large circuits (as in \cite{bulletproofs}), meaning that such systems may not be appropriate for distributed ledger applications.
+However, more recent approaches such as \cite{hoffmann2019efficient} show both improvements to the trust requirement as well as improvements in efficiency.
 
-In the second version of Triptych, we further generalize to include a parallel list of commitments.
-Here, the prover proceeds as before to show its knowledge of an opening to a commitment in one list, as well as the construction of the linking tag.
-However, the proof also shows that the prover knows an opening of a commitment at the same position in the second commitment list.
-This construction has immediate application; in some signer-ambiguous confidential transaction protocols, transaction inputs are commitments to zero, for which the signer shows it knows the opening.
-Each commitment comes equipped with another commitment to the amount of the input; by offsetting these commitments homomorphically and carefully choosing commitment randomness, the prover can show that a particular transaction balances.
+Definitions of existential unforgeability for ring signature schemes from \cite{bender2006ring} are generally inappropriate for LRS.
+These definitions ensure that forgeries appear to be computed from uncorrupted challenge keys by restricting choices of anonymity set members and oracle queries.
+We can do better with linkability.
 
-We show that Triptych produces signatures with competitive performance to other modern linkable ring signatures for limited anonymity set sizes.
-We note that similar constructions also require linear verification time, meaning that the size of anonymity set used in practice is likely to be limited for performance reasons.
+The idea of existential unforgeability in usual digital signatures is to task an algorithm to produce any valid, non-oracle signature on any message such that the signature appears to be signed by an uncorrupted challenge key.
+The clear analogue for LRS schemes is to task an algorithm to produce any valid, non-oracle signature on any message such that the signature links to a challenge signature computed from an uncorrupted challenge key.
+Contrast this intuition with the definition of unforgeability for usual ring signatures with respect to insider corruption from \cite{bender2006ring}, which does not count a valid signature $\sigma$ with an anonymity set $Q$ as a forgery if any key in $Q$ is corrupt or not a challenge key, or a signing oracle has been queried with the same anonymity set $Q$ and message.
+This leads to two problems.
+
+The first problem is due to the disqualification of a purported forgery if there are any adversarially-selected keys or corrupted challenge keys in the anonymity set.
+Such a signature that links with an uncorrupted challenge key does not count as a forgery.
+In ring signature schemes without linkability, this restriction seems requisite to ensure that the signature appears to be signed by an uncorrupted challenge key.
+In applications like signer-ambiguous transaction protocols that use anonymity sets selected \textit{ad hoc}, anonymity set members should be assumed to be adversarially generated.
+Definitions of unforgeability should take this into account.
+
+The second problem is due to the signing oracle restriction in this definition.
+An adversary could generate a valid, non-oracle signature re-using the same message and anonymity set as some challenge signature generated by the oracle.
+A verifier who has found more than one valid non-oracle signature on the same message with the same anonymity set, under this definition, can only conclude that at least one anonymity set member signed at least one of the signatures.
+This allows a malicious Mallory-in-the-middle to collect outgoing honest signatures on some honest messages and attempt to construct clone signatures on these honest messages.
+A sender attempting to assert culpability over a signature could then be in danger of being unable to reconstruct a signature sent to some receiver.
+
+These problems seem to interfere with the spirit behind existential unforgeability with insider corruption from \cite{bender2006ring}: the signature is valid, not produced by an oracle, appears to have been computed from an uncorrupted challenge key, and yet is not considered a forgery.
+
+\subsection{Our Contribution}
+
+We relax the notion of successful forgeries to require only linking with uncorrupted challenge keys, obtaining a notion of unforgeability for linkable ring signatures that is equivalent to the definition of non-slanderability in \cite{au2006short}.
+Non-slanderability allows for adversaries who can query a signature oracle with any anonymity set, even adversarially-selected anonymity sets.
+This models an extremely persuasive adversary who can convince users to sign messages with adversarially-selected anonymity sets.
+We show that non-slanderability implies unforgeability with respect to insider corruption from \cite{bender2006ring}.
+
+We also present a Schnorr-like linkable ring signature scheme we call $d$-CLSAG that exploits key aggregation techniques to improve signature size.
+We describe an application for the $d$-CLSAG scheme in ring confidential transaction protocols, allowing transactions consisting of $d-1$ distinct assets simultaneously.
+We prove that $d$-CLSAG is linkable assuming collision resistance in key aggregation and linkably anonymous assuming the decisional Diffie-Hellman game is hard.
+Recall that Schnorr-like signature schemes do not cleanly reduce to the discrete logarithm assumption (\textit{c.f.}\ \cite{paillier2005discrete}), generally are only secure up to the (relatively flimsier) one-more hardness assumptions, and proof techniques typically exploit programmable random oracles with forking lemmata, leading to weak bounds.
+We use the general forking lemma to prove that $d$-CLSAG is non-slanderable assuming a $\kappa$-one-more variation of the discrete logarithm game is hard.
 
 \section{Preliminaries}
-\subsection{Public parameters}
-Let $\G$ be a cyclic group in which the discrete logarithm problem is hard, and let $\F$ be the scalar field of $\G$.
-Let $\hs: \{0,1\}^* \to \F$ be a cryptographic hash function.
-Let $G$ and $H$ be generators of $\G$ with unknown discrete logarithm relationship.
-Let $N = n^m$ be a size parameter, where $n > 1$ and $m > 1$.
-Let $\{G_{j,i}\}_{j,i=0}^{m-1,n-1}$ be a set of generators of $\G$ with unknown discrete logarithm relationship to each other, to $G$, and to $H$.
-Let $U$ be a generator of $\G$.
-Note that all generators may be produced using public randomness; for example, the use of a suitable hash function with domain separation may be appropriate.
-All such public parameters are assumed to comprise a global reference string known to all players; in particular, we exclude them from algorithm definitions and Fiat-Shamir transcript hashes for readability.
 
-\subsection{Pedersen commitment}
-Let $\com$ be a homomorphic commitment scheme that is perfectly hiding and computationally binding.
-In this work, we assume use of the Pedersen commitment scheme: for $x,r \in \F$, define $\com(x,r) \equiv xG + rH$ to be the commitment of the value $x$ with randomness $r$.
-This can be trivially extended to support matrix values; for $\{x_{j,i}\},r \in \F$, define $\com(x,r) \equiv rH + \sum_{j,i} x_{j,i}G_{j,i}$.
-Note in particular that Pedersen matrix commitments are similarly homomorphic.
+Let $\lambda$ be a security parameter and $1 \leq q, \eta, \kappa \in poly(\lambda)$.
+Let $\mathbb{G} = \langle G \rangle$ denote a group over a field $\mathbb{F}$ with generator $G$.
+Let $\mathcal{H}^s:\left\{0,1\right\}^* \to \mathbb{F}$ and $\mathcal{H}^p:\left\{0,1\right\}^* \to \mathbb{G}$ be two independent cryptographic hash functions under the random oracle model, \textit{i.e.}\ sampled uniformly from the set of all functions $\left\{0,1\right\}^* \to \mathbb{F}$ and $\left\{0,1\right\}^* \to \mathbb{G}$, respectively.
 
-\subsection{Other notation}
-For integers or field elements $i,j$, the Kronecker delta function $\delta(i,j)$ evaluates to $1$ if $i=j$ and $0$ otherwise, where the output is taken to be in the appropriate set.
+If there exists a function $f$ that is negligible in some parameter $\lambda$, and there exists $\lambda$-dependent events $A, B$ such that $\left|\mathbb{P}\left[A\right] - \mathbb{P}\left[B\right]\right| \leq f(\lambda)$, we denote this $\mathbb{P}\left[A\right] \approx \mathbb{P}\left[B\right]$.
+An event $A$ such that $\mathbb{P}\left[A\right] \approx 0$ is said to be negligible in $\lambda$ (or to occur with probability at most negligible in $\lambda$).
+The complement of an event $A$ is denoted $\overline{A}$.
+For a field $\mathbb{F}$, we denote the non-zero elements $\mathbb{F}^* := \mathbb{F}\setminus \left\{0\right\}$.
+For a finite set $S$, we define $S^*$ by interpreting $S$ as a list of letters that generate the free monoid $S^*$.
+For example, $\left\{0,1\right\}^*$ consists of all finite-length bitstrings.
 
-We sometimes use index subscript notation of the form $i_j$ to indicate the $j$ digit of $i$, where such a decomposition of $i$ is taken base $n$ with padded length $m$:
-$$\sum_{j=0}^m i_j n^j = i$$
-This notation will be specified explicitly where confusion may occur.
+For a set $S$, we define $\mathcal{P}(S)$ as the power set of $S$, i.e.\ the set of all subsets of $S$.
 
-\section{Protocol: linkable one-of-many commitment}
-We wish to build a linkable ring signature construction, where a signer who knows the opening of a commitment may sign messages using an anonymity set containing other commitments for which the signer does not know openings.
-Included with the proof of knowledge, the signer also provides a linking tag that is the image of the signing commitment's opening under a verifiable pseudorandom function, using the method of \cite{dodis} that has previously appeared in \cite{omniring,rct3}.
-Part of the soundness of the proving system relies on the proper construction of this linking tag.
-Upon receipt, a verifier can check whether the linking tag has previously appeared in any other valid proof; if it has not, injectivity assures the verifier that no other signature has been produced by the (unknown) signer.
+We denote vectors with bold, i.e.\ for a sequence $x_i \in \mathbb{F}$ for $i = 0, \ldots, n-1$, we denote the tuple $(x_0, \ldots, x_{n-1})$ with $\textbf{x}$.
+We denote the Hadamard product between vectors with $\textbf{x} \circ \textbf{y} = (x_i y_i)_i$.
+We begin all indices at $0$ to avoid all ambiguity.
 
-More specifically, we modify the construction of Bootle \cite{bootle}, which itself is a generalization of a construction by Groth \cite{groth}.
-We produce a sigma protocol for the following relation:
-$$\mathcal{R}_{\text{link}} = \left\{ \{M_i\}_{i=0}^{N-1} \subset \G, J \in \G ; (l \in \mathbb{Z},r \in \F) : M_l = rG \text{ and } U = rJ \right\}$$
-Figures \ref{fig:link} and \ref{fig:link_2} describe the protocol.
+\section{Definitions}
 
-\begin{figure}[htbp]
-\centering
-\fbox{\begin{minipage}{0.95\textwidth}
-$\underline{\mathcal{P}_{\text{link}}(\{M_i\},J;(l,r)):}$
+\subsection{Hardness Assumptions}\label{sec:hardness}
+
+We begin by noting that if $\left\{\mu_i\right\}_{i=0}^{d-1} \subseteq \mathbb{F}$ are selected uniformly at random, then the function $\mu: \mathbb{F}^d \to \mathbb{F}$ defined by mapping $\textbf{x} \mapsto \sum_i \mu_i x_i$ has uniformly distributed output and is collision resistant.
+We use this property when considering linkability and linkable anonymity.
+
+The following game is equivalent\footnote{A usual $\kappa$-one-more discrete logarithm solver can succeed at the game in Definition \ref{def:komdl} with the same probability and some extra time by merely summing solutions.
+A solver of the game in Definition \ref{def:komdl} can use their discrete logarithm knowledge to solve for an otherwise uncorrupted challenge key with the same probability and some extra time.} to the usual $\kappa$-one-more discrete logarithm game under the random oracle model.
+
+\begin{definition}[$\kappa$-One-More Linear Combination Discrete Logarithm]\label{def:komdl}
+
+Let $\kappa \geq 1$.
+We say any PPT algorithm $\texttt{A}$ that can succeed at the following game in time at most $t$ and with success probability at least $\epsilon$ is a $(t, \epsilon, q)$-solver of the $\kappa$-one-more discrete logarithm of linear combinations problem in $\mathbb{G}$.
+\begin{enumerate}
+\item Challenger draws $\left\{sk_i\right\}_{i=0}^{q-1} \subseteq \mathbb{F}$ at random, computes $pk_i := sk_i \cdot G$, sends $S := \left\{pk_i\right\}_{i=0}^{q-1}$ to $\texttt{A}$.
+
+\item $\texttt{A}$ is granted access to a corruption oracle $\texttt{CO}$ which takes as input a public key $pk_i \in S$ and produces as output the corresponding private key $sk_i$.
+Corrupted keys are recorded in a table $C$.
+
+\item $\texttt{A}$ outputs some $w \in \mathbb{F}\setminus \left\{0\right\}$, a sequence of field elements $\left\{h_j\right\}_{j=0}^{\kappa} \subseteq \mathbb{F} \setminus \left\{0\right\}$, and a subset of challenge keys $\left\{pk^*_j\right\}_{j=0}^{\kappa} \subseteq \left\{pk_i\right\}_{i=0}^{q-1}$, succeeding if and only if $w \cdot G = \sum_{j=0}^{\kappa} h_j \cdot pk^*_j$ and
+ $\texttt{A}$ queried $\texttt{CO}$ no more than $\kappa$ times.
+
+\end{enumerate}
+We say that the discrete logarithms of linear combinations are computationally hard to compute in $\mathbb{G}$ if any $(t, \epsilon, q)$-solver of this game has an advantage  that is $\epsilon$ negligible in $q$.
+\end{definition}
+
+For an algorithm $\texttt{A}$ that takes as input a random tape $\rho$, a sequence of random oracle queries $\textbf{h}$ and some input $inp$ and produces $(out, idx) \leftarrow \texttt{A}(\rho, \textbf{h}, inp)$ as output, the general forking algorithm works as follows.
+
+\begin{enumerate}[(1)]
+\item  Pick a random tape $\rho$ for $\texttt{A}$ and two sequences of random oracle queries $\textbf{h} = \left\{h_0, h_1, \ldots\right\}$ and $\textbf{h}^\prime = \left\{h_0^\prime, h_1^\prime, \ldots\right\}$.
+
+\item Execute $(out, idx) \leftarrow \texttt{A}(\rho, \textbf{h}, inp)$.
+
+\item Set $j := idx$ and glue the oracle queries $\textbf{h}$, $\textbf{h}^\prime$ together \[\textbf{h}^* = \left\{h_0, h_1, \ldots, h_{idx - 1}, h_{idx}^\prime, h_{idx+1}^\prime, \ldots, \right\}.\]
+
+\item Execute $(out^*, idx^*) \leftarrow \texttt{A}(\rho, \textbf{h}^*, inp)$.
+
+\item If $idx \neq idx^*$ or $h_{idx} = h_{idx}^\prime$, output $\bot$ and terminate. Otherwise, output $(out, out^\prime, idx)$.
+\end{enumerate}
+
+This algorithm is precisely the algorithm $\mathcal{F}^{\texttt{A}}$ in the following lemma.
+
+\begin{lemma}[General Forking Lemma]\label{lem:fork}
+Let $1 \leq \eta \in \text{poly}(\lambda)$.
+Let $\texttt{A}$ be any PPT algorithm which takes as input some tuple $x_\texttt{A} = (x, \textbf{h})$ where we let $\textbf{h} = (h_0, h_1, \ldots, h_{q-1})$ be a sequence of oracle query responses ($\eta$-bit strings) and returns as output $y_{\texttt{A}}$ either a distinguished failure symbol $\bot$ or a pair $(\textit{idx}, y)$ where $\text{idx} \in [q]^2$ and $y$ is some output.
+Let $\epsilon_{\texttt{A}}$ denote the probability that $\texttt{A}$ does not output $\bot_{\texttt{A}}$ (where this probability is taken over all random coins of $\texttt{A}$, the distribution of $x$, and all choices $\textbf{h}$).
+Let $\mathcal{F} = \mathcal{F}^{\texttt{A}}$ be a forking algorithm for $\texttt{A}$.
+The accepting probability of $\mathcal{F}$ satisfies $\epsilon_{\mathcal{F}} \geq \epsilon_{\texttt{A}} \left(\frac{\epsilon_{\texttt{A}}}{q} - \frac{1}{2^\eta}\right)$.
+\end{lemma}
+
+We assume that the following game, under the random oracle model, is as hard as the usual (fixed-base) decisional Diffie-Hellman game.
+
+\begin{definition}[Random Oracle Decisional Diffie-Hellman]\label{def:rom-ddh}
+
+We say any PPT algorithm $\texttt{A}$ that can succeed at the following game in time at most $t$ and with success probability at least $\epsilon$ is a $(t, \epsilon, q)$-solver of the random oracle decisional Diffie-Hellman game.
+\begin{enumerate}
+\item Challenger draws $\left\{sk_i\right\}_{i=0}^{q-1} \subseteq \mathbb{F}$ at random, computes $pk_i := sk_i \cdot G$, computes group elements $\mathfrak{T}^{(1)}_i := sk_i \cdot \mathcal{H}^p(pk_i)$, samples random group elements $\left\{\mathfrak{T}^{(0)}_i\right\}_{i=0}^{q-1} \subseteq \mathbb{G}$, computes $S^{(j)} := \left\{(pk_i, \mathfrak{T}^{(j)}_i)\right\}_{i=0}^{q-1}$ for $j \in \{0,1\}$, samples a random bit $b$, sends $S^{(b)}$ to $\texttt{A}$, and lastly grants $\mathcal{H}^p$ access to $\texttt{A}$.
+
+\item $\texttt{A}$ outputs a bit $b^\prime$, succeeding if and only if $b = b^\prime$.
+\end{enumerate}
+
+We say random oracle Diffie-Hellman points are hard to computationally distinguish from random in $\mathbb{G}$ if any $(t, \epsilon, q)$-solver of the random oracle decisional Diffie-Hellman game has an advantage $\left|\epsilon - 1/2\right|$ that is negligible in $q$, where this probability is measured over all functions $\mathcal{H}^p$.
+\end{definition}
+
+\subsection{Linkable Ring Signatures}
+
+\begin{definition}\label{def:lrs} A linkable ring signature (LRS) scheme $\Pi_{LRS}$ is a tuple of algorithms $(\texttt{SETUP}, \texttt{KEYGEN}, \texttt{SIGN}, \texttt{VERIFY}, \texttt{LINK})$ satisfying the following constraints.
 \begin{itemize}
-\item Select random $r_A \in \F$ and $\left\{a_{j,i}\right\}_{i=1,j=0}^{n-1,m-1} \subset \F$.
-Define $A \equiv \com(a,r_A)$.
-\item Define $\left\{\sigma_{j,i}\right\}_{i,j=0}^{n-1,j-1} \subset \F$ such that $\sigma_{j,i} \equiv \delta\left(l_j,i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
-Define $B \equiv \com(\sigma,r_B)$.
-\item Select random $r_C \in \F$, and define $C \equiv \com(a(1-2\sigma), r_C)$.
-\item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
-\item Define coefficients $\left\{p_{k,j}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p_k(x) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}x + a_{j,k} \right) = \delta\left(l,k\right)x^m + \sumj p_{k,j}x^j$$ for all $k \in [0,N)$ (using our decomposition notation).
-\item Select random $\left\{\rho_j\right\}_{j=0}^{m-1} \subset \F$.
-\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}M_k + \rho_jG$$
-\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv U \sumk p_{k,j}+ \rho_jJ$$
+\item $\texttt{SETUP}$ takes as input a security parameter $\lambda$ and produces as output some public setup parameters $\rho$.
+
+\item $\texttt{KEYGEN}$ takes as input $(\lambda, \rho)$ and outputs a private-public keypair $(sk, pk)$.
+
+\item $\texttt{SIGN}$ takes as input $(\lambda, \rho)$ and a triple $(m, Q, sk)$ and outputs a signature $\sigma$ or a failure symbol $\bot$.
+Here $m$ is a message, $Q$ is an anonymity set of public keys $Q = \left\{pk_0, pk_1, ..., pk_{n-1}\right\}$, and $sk$ is a private key.
+
+\item $\texttt{VERIFY}$ takes as input $(\lambda, \rho)$ and a triple $(m, Q, \sigma)$ and outputs a bit $b$.
+Here $m$ is a message, $Q$ is an anonymity set of public keys $Q = \left\{pk_0, pk_1, ..., pk_{n-1}\right\}$, and $\sigma$ is a signature.
+
+\item $\texttt{LINK}$ takes as input $(\lambda, \rho)$, a pair of triples $(m, Q, \sigma)$, $(m^*, Q^*, \sigma^*)$, and outputs a bit $b$.
+Here $m, m^*$ are messages, $Q, Q^*$ are anonymity sets of public keys, and $\sigma, \sigma^*$ are signatures.
+\end{itemize}
+We say a triple of the form $(m, Q, \sigma)$ (that is to say, a triple suitable for use as input in $\texttt{VERIFY}$ and $\texttt{LINK}$) is a \textit{signature triple}.
+We say $\Pi_{LRS}$ is a $d$-LRS if the dimension of private and public keys is $d \geq 1$ and anonymity sets can be described as $d\times n$ matrices.
+\end{definition}
+
+We assume $\rho$ includes (implicitly or explicitly) descriptions of a private key space $\mathcal{SK}$, a public key space $\mathcal{PK}$, a signature space $\mathcal{SIG}$, a map $\phi: \mathcal{SK} \to \mathcal{PK}$, and a family of hash functions $\mathcal{H}$ from which we can construct $\mathcal{H}^s$ and $\mathcal{H}^p$.
+For example, with an elliptic curve group $\mathbb{G}$ over a field $\mathbb{F}$, for two hash functions $H_s:\left\{0,1\right\}^* \to \mathbb{F}$ and $H_p:\left\{0,1\right\}^* \to \mathbb{G}$, a Schnorr-like ring signature scheme such as \cite{liu2004linkable} would pack into $\rho$ the descriptions $\mathcal{SK} = \mathbb{F}^*$, $\mathcal{PK} = \mathbb{G}$, $\mathcal{SIG} = \mathbb{F}^n$, and a generator $G \in \mathbb{G}$ (which is sufficient to specify the map $\phi: \mathbb{F}^* \to \mathbb{G}$ defined by $x \mapsto xG$).
+Note each algorithm in an LRS scheme takes $(\lambda, \rho)$ as input; in the sequel we exclude these from notation for LRS schemes, taking their use as implicit.
+
+Note we do not allow a LRS scheme to be correct if the scheme allows anonymity multisets $Q$.
+
+\begin{definition}\label{def:lrs-correct}
+Let $b\in \left\{0,1\right\}$, $sk, sk^* \in \mathcal{SK}$, let $Q$, $Q^* \subset \mathcal{PK}$ be sets, let $m, m^*, m^\prime$ be messages, let $\sigma, \sigma^*, \sigma^\prime \in \mathcal{SIG}$ be any purported signatures.
+Define the following events.
+\begin{itemize}
+\item $E_1(sk, pk)$ is the event that some $(sk, pk) \leftarrow \texttt{KEYGEN}$.
+
+\item $E_2(sk, Q)$ is the event that $\phi(sk) \in Q$.
+
+\item $E_3(m, Q, \sigma)$ is the event that $\texttt{VERIFY}(m, Q, \sigma) = 1$.
+
+\item $E_4(b, m, m^*, m^\prime, Q, Q^*, Q^\prime, \sigma, \sigma^*, \sigma^\prime)$ is the event that \[b = \texttt{LINK}((m, Q, \sigma), (m^*, Q^*, \sigma^*)) = \texttt{LINK}((m^*, Q^*, \sigma^*), (m^\prime, Q^\prime, \sigma^\prime)).\]
+
+\item $E_5(m, m^*, Q, Q^*, \sigma, \sigma^*, sk)$ is the event that \[\phi(sk) \in Q \cap Q^*\text{, }\sigma \leftarrow \texttt{SIGN}(m, Q, sk)\text{, and }\sigma^* \leftarrow \texttt{SIGN}(m^*, Q^*, sk).\]
+
+\item $E_6(m, m^*, Q, Q^*, \sigma, \sigma^*, sk, sk^*)$ is the event that  \[\sigma \leftarrow \texttt{SIGN}(m, Q, sk)\text{, }\sigma^* \leftarrow \texttt{SIGN}(m^*, Q^*, sk^*)\text{, and }sk \neq sk^*.\]
+\end{itemize}
+We say $\Pi_{LRS}$ is correct if all of the following properties hold, where these probabilities are computed over all random coins and over all choices of hash function.
+
+\begin{enumerate}[(i)]
+\item $\mathbb{P}\left[ \phi(sk) = pk \mid E_1(sk, pk) \right] \approx 1$
+
+\item $\mathbb{P}\left[ \texttt{SIGN}(m, Q, sk) = \bot \mid \overline{E_2}(sk, Q)  \right] \approx 1$
+
+\item $\mathbb{P}\left[ \texttt{VERIFY}(m, Q, \texttt{SIGN}(m, Q, sk)) = 1 \mid E_2(sk, Q) \right] \approx 1$
+
+\item $\mathbb{P}\left[\texttt{LINK}((m, Q, \sigma), (m, Q, \sigma)) = 1 \mid E_3(m, Q, \sigma)\right] \approx 1$
+
+\item ${\small \mathbb{P}\left[\texttt{LINK}((m, Q, \sigma), (m^*, Q^*, \sigma^*)) = \texttt{LINK}((m^*, Q^*, \sigma^*), (m, Q, \sigma))\right] \approx 1}$
+
+\item ${\small \mathbb{P}\left[b = \texttt{LINK}((m, Q, \sigma), (m^\prime, Q^\prime, \sigma^\prime)) \mid E_4(b, m, m^*, m^\prime, Q, Q^*, Q^\prime, \sigma, \sigma^*, \sigma^\prime)\right] \approx 1}$
+
+\item $\mathbb{P}\left[ \texttt{LINK}((m, Q, \sigma), (m^*, Q^*, \sigma^*)) = 1 \mid E_5(m, m^*, Q, Q^*, \sigma, \sigma^*, sk) \right] \approx 1$
+
+\item ${\small \mathbb{P}\left[ \texttt{LINK}((m, Q, \sigma), (m^*, Q^*, \sigma^*)) = 0 \mid E_6(m, m^*, Q, Q^*, \sigma, \sigma^*, sk, sk^*) \right] \approx 1}$
+\end{enumerate}
+\end{definition}
+
+\subsection{Linkability}
+
+We use two distinct, but related, definitions of linkability.
+The first is from \cite{au2006short}.
+This definition allows signing oracle queries with any anonymity sets $Q$ consisting of at least one challenge key (which can be simulated via backpatching).
+This definition also allows the challenger to succeed at the linkability game using signature triples $(m, Q, \sigma)$, $(m^*, Q^*, \sigma^*)$ that have semi-corrupted anonymity sets $Q, Q^*$ (just so long as the keys in $Q \cup Q^*$ have not been tampered with too severely).
+The second is from \cite{backes2019ring}, which allows the adversary total control over key selection, declaring success when they produce more unlinked ring signatures than total ring members.
+Such an adversary doesn't need key generation, corruption, or signature oracle access.
+
+\begin{definition}[ACST Linkability With an Adversarial Key]\label{def:acst-link-adv}
+We say any PPT algorithm $\texttt{A}$ that can succeed at the following game in time at most $t$ and with success probability at least $\epsilon$ is a $(t, \epsilon, q)$-solver of ACST linkability.
+
+\begin{enumerate}
+\item Challenger draws $\left\{(sk_i, pk_i)\right\}_{i=0}^{q-1}$ from $\texttt{KEYGEN}$ and sends the challenge public keys $S = \left\{pk_i\right\}_{i=0}^{q-1}$ to $\texttt{A}$.
+
+\item $\texttt{A}$ is granted \texttt{SO} and \texttt{CO} access.
+    \begin{itemize}
+    \item \texttt{CO} takes as input a public key $pk$.
+If $pk \in S$, $\texttt{CO}$ outputs the corresponding private key $sk$.
+Otherwise, $\texttt{CO}$ outputs a failure symbol, $\bot$.
+Corrupted keys are tracked in a table $C$.
+
+    \item \texttt{SO} operates as follows:
+        \begin{enumerate}[(i)]
+        \item Takes as input a message $m$, an anonymity set $Q = \left\{pk^\prime_i\right\}_{i=0}^{n-1}$, and an index $l$.
+
+        \item If $0 > l$ or $l \geq n$ or if the $pk^\prime_l \notin S$, \texttt{SO} outputs a failure symbol $\bot$.
+
+        \item Otherwise, there exists some $i$ such that $pk^\prime_l = pk_i \in S$.
+\texttt{SO} retrieves the private key $sk_i$ and outputs a valid signature triple $(m, Q, \sigma)$ such that $\sigma \leftarrow \texttt{SIGN}(m, Q, sk_i)$.
+        \end{enumerate}
     \end{itemize}
 
-$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
-$A,B,C,D,\{X_j\},\{Y_j\}$ \\
+\item $\texttt{A}$ outputs a pair of signature triples, $(m, Q, \sigma)$, $(m^*, Q^*, \sigma^*)$, succeeding if and only if all of the following conditions are satisfied.
+    \begin{enumerate}[(i)]
+        \item $\texttt{VERIFY}(m, Q, \sigma) = \texttt{VERIFY}(m^*, Q^*, \sigma^*) = 1$
+        \item $\texttt{LINK}((m, Q, \sigma), (m^*, Q^*, \sigma^*)) = 0$
+        \item $\sigma, \sigma^*$ are not output from any $\texttt{SO}$ query.
+        \item $\left|(Q \cup Q^* ) \cap (C \cup \overline{S})\right| \leq 1$
+    \end{enumerate}
+\end{enumerate}
+We say that a scheme is \textit{ACST linkable} if every PPT algorithm $\texttt{A}$ that is a $(t, \epsilon, q)$-solver ACST linkability game has a negligible acceptance probability $\epsilon$.
+\end{definition}
 
-$\underline{\mathcal{V} \to \mathcal{P}:}$ \\
-$\xi \in \{0,1\}^*$ \\
+\begin{definition}[$q$-Pigeonhole Linkability]\label{def:pig-link}
+We say any PPT algorithm $\texttt{A}$ that can succeed at outputting $q$ public keys $\left\{pk_i\right\}_{i=0}^{q-1}$ and $q + 1$ valid, unlinked signature triples $\left\{(m_j, Q_j, \sigma_j)\right\}_{j=0}^{q}$ such that $\cup_j Q_j \subseteq \left\{pk_i\right\}_{i=0}^{q-1}$ in time at most $t$ and probability at least $\epsilon$ is a $(t, \epsilon, q)$-solver of pigeonhole linkability.
+We say that a scheme is $q$-\textit{pigeonhole linkable} if every PPT algorithm $\texttt{A}$ that is a $(t, \epsilon, q)$-solver of $q$-pigeonhole linkability has a negligible acceptance probability $\epsilon$.
+\end{definition}
 
-$\underline{\mathcal{P}(\xi):}$
+These definitions are distinct.
+Pigeonhole linkability does not necessarily imply ACST linkability.
+Indeed, a successful player of the game in Definition \ref{def:acst-link-adv} may only succeed with sufficiently large rings, in which case that player may only be used to succeed at the game of Definition \ref{def:pig-link} for a sufficiently large $q$.
+Similarly, ACST linkability may not imply pigeonhole linkability.
+A player of the game in Definition \ref{def:pig-link} that requires knowledge of many private keys may be too corruption-hungry to succeed at Definition \ref{def:acst-link-adv}.
+
+For a scheme that is pigeonhole linkable, Definition \ref{def:pig-link} says nothing about an adversary that can keep signing with one key multiple times to construct new unlinked signatures, just so long as they continue to use different anonymity sets.
+
+For a scheme that is ACST linkable, a user providing honest signatures to an adversary acts like a signature oracle, so the adversary could  attempt to construct a bad/cloned signature that links to some honest one (possibly with adversarially selected ring members), only ever outputting a single signature.
+Definition \ref{def:acst-link-adv} says nothing about such an attacker.
+This attacker could stand between Alice and Bob, provide cloned signatures to the Bob ostensibly signed by Alice, fooling him.
+When Alice eventually contacts Bob without the adversary in the middle, Alice would be unable to assert culpability over the cloned signatures.
+Bob concludes that $\sigma^*$ and $\sigma$ were signed by the same private key, despite that the adversary does not know the private key that generated $\sigma$.
+
+However, Definition \ref{def:pig-link} implies Definition \ref{def:acst-link-adv} under certain circumstances.
+For one (of many) examples, if there exists a $(t, \epsilon, 1)$-solver of the game in Definition \ref{def:acst-link-adv} that produces two signature triples $(m, Q, \sigma)$, $(m^\prime, Q^\prime, \sigma^\prime)$ such that $Q = Q^\prime$ and $\left|Q\right| = 1$, then $\texttt{A}$ succeeds at Definition \ref{def:pig-link}.
+
+A more general look at the relationships between linkability definitions is beyond the scope of this work.
+Since neither definition is sufficient for our purposes alone and these definitions are distinct in general, we use both.
+
+\subsection{Unforgeability and Non-Slanderability}
+
+The idea of existential unforgeability in usual digital signatures is to task an algorithm to produce any valid, non-oracle signature on any message such that the signature appears to be signed by an uncorrupted challenge key.
+The clear analogue for LRS schemes is to task an algorithm to produce any valid, non-oracle signature on any message such that the signature links to a challenge signature computed from an uncorrupted challenge key.
+In fact, the implementation in Section \ref{sec:implementation} compares linking tags as if they were verification keys; in this sense, a forger is tasked to construct a valid signature with some verification keys to which they do not know the corresponding private key.
+We consider this to be a textbook forgery, and so we take these occurrences into account in our definition.
+
+\begin{definition}[Existential Unforgeability of Linkable Ring Signatures Against Adversarially-Selected Keys and Insider Corruption]\label{def:ex-unf}
+We say any PPT algorithm $\texttt{A}$ that can succeed at the following game in time at most $t$ and with probability at least $\epsilon$ is a $(t, \epsilon, q)$-forger.
+\begin{enumerate}
+
+\item Challenger draws $\left\{(sk_i, pk_i)\right\}_{i=0}^{q-1}$ from \texttt{KEYGEN} and sets $S := \left\{pk_i\right\}_{i=0}^{q-1}$.
+For each $0 \leq i < q$, the challenger uniformly samples secret $\emptyset \neq \widetilde{Q}_i \in \mathcal{P}\left(S\right)$, defines $Q_i := \widetilde{Q}_i \cup \left\{pk_i\right\}$, retrieves the index $l_i$ such that $pk_{i} \in Q_i \cap S$ has index $l_i$ in $Q_i$, samples secret random messages $\left\{m_i\right\}_{i=0}^{q-1}$, and computes secret challenge signatures $\sigma_i \leftarrow \texttt{SIGN}(m_i, Q_i, sk_i)$.
+Challenger sends $S$ to $\texttt{A}$.
+\item Challenger grants \texttt{SO} and \texttt{CO} access to \texttt{A}:
     \begin{itemize}
-\item Define $\left\{f_{j,i}\right\}_{i=1,j}^{n-1,m-1}$ such that $f_{j,i} \equiv \sigma_{j,i}\xi + a_{j,i}$.
-\item Define $z_A \equiv r_A + \xi r_B$ and $z_C \equiv \xi r_C + r_D$.
-\item Define $z \equiv r \xi^m - \sumj \rho_j \xi^j$.
+    \item \texttt{CO} takes as input a challenge public key $pk_i \in S$ and produces as output the corresponding private key $sk_i$, keeping a list of all corrupted public keys in an internal table $C$.
+
+    \item \texttt{SO} operates as follows:
+        \begin{enumerate}[(i)]
+        \item Takes as input a message $m$, an anonymity set $Q$, and an index $l$.
+
+        \item If the key at index $l$ in $Q$ is not a challenge public key from $S$, \texttt{SO} outputs a failure symbol $\bot$.
+
+        \item Otherwise, \texttt{SO} retrieves the index $i$ such that $pk_{i} \in Q \cap S$ has index $l$ in $Q$, retrieves the corresponding private key $sk_{i}$, and outputs a signature $\sigma \leftarrow \texttt{SIGN}(m, Q, sk_{i})$.
+        \end{enumerate}
     \end{itemize}
 
-$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
-$\{f_{j,i}\}_{j=0,i=1}^{m-1,n-1},z_A,z_C,z$
-\end{minipage}}
-\caption{Sigma protocol for $\mathcal{R}_{\text{link}}$}
-\label{fig:link}
-\end{figure}
+\item $\texttt{A}$ outputs a message $m$, a ring $Q$, a signature $\sigma$, succeeding if and only if:
+    \begin{enumerate}[(i)]
+    \item $\texttt{VERIFY}(m, Q, \sigma) = 1$,
 
-\begin{figure}[htbp]
-\centering
-\fbox{\begin{minipage}{0.95\textwidth}
-$\underline{\mathcal{V}_{\text{link}}(\{M_i\},J):}$
-\begin{itemize}
-\item For $0 \leq j < m$, let $f_{j,0} \equiv \xi - \sum_{i=1}^{n-1} f_{j,i}$.
-\item Accept if and only if:
-\begin{eqnarray}
-A + \xi B &=& \com(f,z_A) \label{eqn:ab} \\
-\xi C + D &=& \com(f(\xi-f),z_C) \label{eqn:cd} \\
-\sumk M_k \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG &=& 0 \label{eqn:x} \\
-U \sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ &=& 0 \label{eqn:y}
-\end{eqnarray}
-\end{itemize}
-\end{minipage}}
-\caption{Sigma protocol for $\mathcal{R}_{\text{link}}$ (continued)}
-\label{fig:link_2}
-\end{figure}
+    \item there does not exist a query made to $\texttt{SO}$ whose output is $\sigma$,
 
-Observe that this protocol can be made non-interactive using the Fiat-Shamir heuristic, where the verifier challenge is produced using a collision-resistant hash function (modeling a random oracle) and the proof transcript \cite{fiatshamir}.
+    \item ${\small \texttt{LINK}((m, Q, \sigma), (m_i, Q_i, \sigma_i)) = 1}$ for some  $pk_i \in S \cap Q \setminus C$.
+    \end{enumerate}
+\end{enumerate}
+Moreover, we say that a linkable ring signature scheme is \textit{unforgeable} if every $(t, \epsilon, q)$-solver of this game has a negligible acceptance probability $\epsilon$.
+\end{definition}
 
-We will show that the sigma protocol is complete, sound, and zero-knowledge, the precise definitions of which are common and found in \cite{groth}.
-Informally, we require the protocol be:
-\begin{itemize}
-\item \textit{Perfectly complete}: Given knowledge of a witness to a statement in the proof relation, an honest prover can always convince an honest verifier of the validity of the witness.
-\item \textit{Special sound}: Given a statement in the proof relation, if a prover can answer multiple verifier challenges correctly, then it is possible to extract a witness for this statement.
-\item \textit{Special honest-verifier zero knowledge}: Given any statement and verifier challenge, it is possible to simulate a transcript that is accepted by an honest verifier without knowledge of a corresponding witness.
-\end{itemize}
+\begin{remark}
+Access to a corruption oracle in this unforgeability definition is one reason security reduces (weakly) to the $\kappa$-one-more discrete logarithm problem, not the usual discrete logarithm problem: an algorithm executing a forgery algorithm in a black box cannot simulate the corruption oracle for the forgery without, itself, gaining corruption oracle access or without resorting to the generic group model.
+\end{remark}
 
-\begin{theorem}
-The protocol in Figures \ref{fig:link} and \ref{fig:link_2} is perfectly complete, special honest-verifier zero knowledge, and $(m+1)$-special sound.
+\begin{remark}
+If \texttt{A} is an algorithm that produces signatures from an LRS satisfying Definition \ref{def:ex-unf}, then (except with negligible probability), the signatures aren't forgeries, so some property 3(i)-3(iii) must be violated.
+If the signature is valid and not from an oracle query, then 3(iii) fails.
+In particular, for an LRS scheme satisfying Definition \ref{def:ex-unf}, if an algorithm produces a valid non-oracle triple $(m, Q, \sigma)$ that links to a challenge key in $Q$, then that challenge key has been corrupted.
+\end{remark}
+
+Non-slanderability is introduced in \cite{tsang2004separable}.
+This definition is refined twice in \cite{au2006short}, allowing \texttt{A} to succeed whenever it publishes any signature that links with any signature from a query $\texttt{A}$ made to $\texttt{SO}$, excepting certain conditions.
+We modify the definition from \cite{au2006short} to allow signing oracle queries with anonymity sets containing adversarially selected members.
+
+\begin{definition}[Chosen-Target Non-Slanderability Against Adversarial Keys and Insider Corruption]\label{def:acst-nonsl}
+We say any PPT algorithm $\texttt{A}$ that can succeed at the following game in time at most $t$ and with probability at least $\epsilon$ is a $(t, \epsilon, q)$-solver of non-slanderability against adversarially chosen keys.
+\begin{enumerate}
+\item Challenger draws $\left\{(sk_i, pk_i)\right\}_{i=0}^{q-1}$ from KeyGen and sends the challenge public keys $S = \left\{pk_i\right\}_{i=0}^{q-1}$ to \texttt{A}.
+
+\item A is granted \texttt{SO} and \texttt{CO} access just as in Definition \ref{def:ex-unf}.
+
+\item A outputs a triple $(m, Q, \sigma)$, succeeding if and only if:
+    \begin{enumerate}[(i)]
+    \item $\texttt{VERIFY}(m, Q, \sigma) = 1$, and
+
+    \item there does not exist a query made to $\texttt{SO}$ whose output is $\sigma$, and
+
+    \item there exists a query made to $\texttt{SO}$, say $\sigma^* \leftarrow \texttt{SO}(m^*, Q^*, l^*)$, such that
+        \begin{enumerate}[(a)]
+        \item $\texttt{LINK}((m, Q, \sigma), (m^*, Q^*, \sigma^*)) = 1$, and
+
+        \item $pk^*_{l^*} \in S \cap Q^* \cap Q \setminus C$.
+        \end{enumerate}
+    \end{enumerate}
+\end{enumerate}
+Moreover, we say that a linkable ring signature scheme is \textit{non-slanderable} if every $(t, \epsilon, q)$-solver of this game has a negligible acceptance probability $\epsilon$.
+\end{definition}
+
+\begin{theorem}[Non-Slanderability is Unforgeability]\label{thm:nonsl-implies-unf}
+A correct LRS is unforgeable under Definition \ref{def:ex-unf} if and only if it is non-slanderable under Definition \ref{def:acst-nonsl}.
 \end{theorem}
@@
 \begin{proof}
-The proof follows similarly to that of \cite{bootle}.
-
-% Completeness
-We first show perfect completeness.
-Suppose the verifier receives a proof generated by an honest prover.
-Equation \ref{eqn:ab} holds using the identity $$\sumi \sigma_{j,i} = 1$$ for all $0 \leq j < m$.
-Equation \ref{eqn:cd} follows similarly, using the identity $$\left(\sigma_{j,i}\right)^2 = \sigma_{j,i}$$ for all $0 \leq j < m$.
-To show Equation \ref{eqn:x} holds:
-\begin{eqnarray*}
-&& \sumk M_k \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG \\
-&=& \sumk M_k p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}M_k + \rho_jG \right) - zG \\
-&=& \sumk M_k \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \rho_jG - zG \\
-&=& \sumk M_k \xi^m \delta(l,k) - \sumj \xi^j \rho_jG - \left( r\xi^m - \sumj \rho_j\xi^j \right)G \\
-&=& \xi^mrG - \sumj \xi^j \rho_jG - \xi^mrG + \sumj \xi^j \rho_jG \\
-&=& 0
-\end{eqnarray*}
-Equation \ref{eqn:y} follows similarly:
-\begin{eqnarray*}
-&& U \sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ \\
-&=& U \sumk p_k(\xi) - \sumj \xi^j \left( U \sumk p_{k,j} + \rho_jJ \right) - zJ \\
-&=& U \sumk \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \rho_jJ - zJ \\
-&=& U \sumk \xi^m \delta(l,k) - \sumj \xi^j \rho_jJ - \left( r\xi^m - \sumj \rho_j\xi^j \right)J \\
-&=& \xi^mU - \sumj \xi^j \rho_jG - \xi^mrJ + \sumj \xi^j \rho_jG \\
-&=& 0
-\end{eqnarray*}
-since $J = r^{-1}U$ in a valid proof.
-Hence the protocol is perfectly complete.
-
-% SHVZK
-We next show that the protocol is special honest-verifier zero knowledge.
-To do so, we construct a simulator that, given a random verifier challenge $\xi$, can construct a proof transcript with identical distribution to a valid proof.
-
-First, observe that the simulator presented in the proof of Lemma 1 in \cite{bootle} translates identically to our setting.
-If the simulator chooses $B \in \G$ uniformly at random, the cited lemma assures us a valid simulation of the proof elements $A,C,D,z_A,z_C,\{f^{(u)}_{j,i \neq 0}\}$; we may compute each $f^{(u)}_{j,0}$ from this.
-Further, in a valid proof, $B$ is independent and uniformly distributed as well.
-
-The proof elements $\{X_j\}_{j=1}^{m-1}$ and $\{Y_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof since the set $\{\rho_j\}$ is random and the discrete logarithm problem in $\G$ is hard, so the simulator may choose these uniformly at random.
-The verification checks require that $X_0$ and $Y_0$ be uniquely determined by the other elements in the corresponding sets in both real proofs and by the simulator.
-
-Finally, $z$ is uniformly distributed in valid proofs given random $\xi$, so the simulator may choose it uniformly at random.
-Hence the construction is special honest verifier zero-knowledge.
-
-% Soundness
-It remains to show that the protocol is $(m+1)$-special sound, where $m > 1$.
-To show this, we construct an extractor that, given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness.
-
-Suppose that for a given statement, we have a set of $m+1$ distinct verifier challenges $\{\xi_e\}_{e=0}^m$ corresponding to unique valid responses of this form:
-$$\left\{ \{f^{(e)}_{j,i}\}, \{z_e\} \right\}_{e=0}^m$$
-From the $3$-special soundness in \cite{bootle} and $m > 1$ we have valid extractions $\{\sigma_{j,i}\}_{j,i=0}^{m-1,n-1}$ and $\{a_{j,i}\}_{j,i=0}^{m-1,n-1}$, and the Pedersen binding property ensures that (with high probability) we have:
-$$f^{(e)}_{j,i} = \sigma_{j,i}\xi_e + a_{j,i}$$
-for all $e \in [0,m]$.
-Using the extracted values, compute
-$$p_k(\xi) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}\xi + a_{j,k} \right)$$
-for all $k \in [0,N)$.
-Extraction of $\{\sigma_{j,i}\}_{j,i=0}^{m-1,n-1}$ immediately yields the signing index $l$.
-
-We have seen that $p_k$ is of degree $m$ only when $k = l$.
-Hence there exist coefficients $\{\overline{X}_j,\overline{Y}_j\}_{j=0}^{m-1}$, computed uniquely from the statement and extracted values, such that Equations \ref{eqn:x} and \ref{eqn:y} are of the following form:
-\begin{eqnarray*}
-\xi^m M_l + \sumj \xi^j\overline{X}_j &=& zG \\
-\xi^m U + \sumj \xi^j\overline{Y}_j &=& zJ \\
-\end{eqnarray*}
-
-Construct a Vandermonde matrix $V$ where the $e$ row is the vector $(1,\xi_e,\ldots,\xi^m_e)$.
-Since all $\xi_e$ are distinct, the rows of $V$ span $\F^{m+1}$; hence there exist weights $\{\theta_e\}_{e=0}^m$ such that the resulting linear combination of rows produces the vector $(0,\ldots,0,1)$.
-That is, $\sum_{e=0}^m \theta_e\xi_e^j = \delta(j,m)$.
-
-For each of the previous two equations, we can therefore build a linear combination over $e$.
-For the first:
-$$M_l = \sum_{e=0}^m \theta_e\xi_e^m M_l + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{X}_j \right) = \left( \sum_{e=0}^m \theta_e z_e \right) G$$
-Hence we extract $r \equiv \sum_{e=0}^m \theta_e z_e$.
-For the second:
-$$U = \sum_{e=0}^m \theta_e\xi_e^m U + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{X}_j \right) = \left( \sum_{e=0}^m \theta_e z_e \right) J$$
-This implies that $rJ = U$, as required.
-Hence the protocol is $(m+1)$-special sound, which completes the proof.
+If $\texttt{A}$ is a $(t, \epsilon, q)$-solver of the game of Definition \ref{def:ex-unf}, then $\texttt{A}$ can always be wrapped in an algorithm that executes $\texttt{A}$ in a black box and regurgitates the results, except querying the signing oracle with the linking challenge key before outputting the results of $\texttt{A}$.
+Such an algorithm succeeds at the game of Definition \ref{def:acst-nonsl} with exactly equal success probability and asymptotically equal timing as $\texttt{A}$.
+For the converse, let $\texttt{A}$ be a $(t, \epsilon, q)$-solver of the game of Definition \ref{def:acst-nonsl}.
+With probability at least $\epsilon$, $\texttt{A}$ outputs a signature triple $(m, Q, \sigma)$ such that the triple is valid and $\sigma$ is not output from any $\texttt{SO}$ query and there exists some query, say $\sigma^* \leftarrow \texttt{SO}(m^*, Q^*, pk^*_{l^*})$ in the transcript between $\texttt{A}$ and $\texttt{SO}$.
+The challenge key $pk^*_{l^*} = pk_i \in S$ for some $i$ and the signature $\sigma^*$ links with $\sigma$.
+By the transitivity of $\texttt{LINK}$, we obtain that $\sigma$ links to $\sigma_i$.
 \end{proof}
 
-\section{Security: linkable ring signature}
-Informally, a linkable ring signature is a construction permitting signatures on messages using a signer-selected anonymity set (called a \textit{ring}) of possible signers.
-A valid signature convinces a verifier that the signer knows (at least) one of the private keys to a ring member.
-The construction is linkable if it is possible to determine whether two signatures were generated using the same private key, regardless of the ring members used.
+\subsection{Linkable Anonymity}
 
-We use the security definitions in \cite{groth} as a starting point, directly adopting definitions for correctness and unforgeability that also appear in more recent work like \cite{backes}.
-However, we modify the definition of anonymity to account for linking tags, such that the adversary is required to differentiate between at least two possible honest signers that the adversary has not corrupted.
-To account for the linking properties desired in our construction, we use the clever linkability definition from \cite{backes}, which uses a set-theoretic approach.
-We use a straightforward definition for non-frameability, where the adversary produces a target signature on an honest key after receiving signing and corruption oracle access, and must then produce a new signature that links.
+We use a modification of the definition of linkable anonymity from \cite{backes2019ring}.
 
-More formally, a \textit{linkable ring signature} (LRS) construction is a set of algorithms \text{KeyGen}, \text{Sign}, \text{Verify}, and \text{Link} satisfying certain properties.
-A set of public parameters is assumed to be available to each algorithm.
+\begin{definition}[Chosen-Target Linkable Anonymity With Adversarial Keys]\label{linkable-anonymity-game}
+We say any PPT algorithm $\texttt{A}$ that can succeed at the following game in time at most $t$ and with probability at least $\epsilon$ is a $(t, \epsilon, q)$-solver of the linkable anonymity game.
+\begin{enumerate}
+\item Challenger samples a secret random bit $b \in \left\{0,1\right\}$, draws $\left\{(sk_i, pk_i)\right\}_{i=0}^{q-1}$ from $\texttt{KEYGEN}$, and sends the challenge public keys $S := \left\{pk_i\right\}_{i=0}^{q-1}$ to $\texttt{A}$.
+
+\item $\texttt{A}$ outputs a pair of indices $0 \leq i_0, i_1 < q$ such that $pk_{i_0}, pk_{i_1} \in S$, indicating the target keys.
+
+\item  $\texttt{A}$ is granted access to a signing oracle $\texttt{SO}$:
+    \begin{enumerate}[(i)]
+    \item Takes as input a message $m$, an anonymity set $Q$, and a public key $pk \in Q$.
+
+    \item If $\left\{pk_{i_0}, pk_{i_1}\right\} \not\subseteq Q$ or $pk \notin \left\{pk_{i_0}, pk_{i_1}\right\}$, then $\texttt{SO}$ outputs a valid signature $\sigma$ linked to $pk$.
+
+    \item Otherwise, $pk = pk_{i_c}$ for a bit $c$. The bit $c^\prime = (1-c)b + c(1-b)$ is computed and the oracle outputs $\sigma \leftarrow \texttt{Sign}(m, Q, sk_{i_{c^\prime}})$.
+    \end{enumerate}
+
+\item $\texttt{A}$ outputs a bit $b^\prime$, succeeding if $b^\prime = b$.
+\end{enumerate}
+Moreover, we say that a scheme is \textit{linkably anonymous} if every $(t, \epsilon, q)$-solver of the linkable anonymity game has a negligible acceptance advantage $\epsilon$ over $1/2$.
+\end{definition}
+
+\section{Construction}\label{sec:implementation}
+
+In this section, we describe $d$-CLSAG, our implementation of a concise $d$-LRS construction.
+
+\begin{definition}[$d$-CLSAG]\label{def:clsag}
+The tuple $(\texttt{Setup}, \texttt{KeyGen}, \texttt{Sign}, \texttt{Verify}, \allowbreak \texttt{Link})$ as follows is a $d$-LRS signature scheme.
+
 \begin{itemize}
-\item $\text{KeyGen}(r) \to (x,X)$: Generates a secret key $x$ and corresponding public key $X$, optionally using randomness $r$; if not specified, the secret key is sampled uniformly at random.
-\item $\text{Sign}(x,M,R) \to \sigma$: Generates a signature $\sigma$ on a message $M \in \{0,1\}^*$ with respect to the ring $R = \{X_1,\ldots,X_n\}$, provided that $x$ is a secret key corresponding to some $X_i \in R$ generated by $\text{KeyGen}$.
-\item $\text{Verify}(\sigma,M,R) \to \{0,1\}$: Verifies a signature $\sigma$ on a message $M$ with respect to the ring $R$.
-Outputs $0$ is the signature is rejected, and $1$ if accepted.
-\item $\text{Link}(\sigma,\sigma') \to \{0,1\}$: Determines if signatures $\sigma$ and $\sigma'$ were signed using the same private key.
-Outputs $0$ if the signatures were signed using different private keys, and $1$ if they were signed using the same private key.
+\item $\texttt{Setup} \to \textit{par}$.
+$\texttt{Setup}$ selects a prime $p$, a group $\mathbb{G}$ with prime order $p$, selects a group generator $G \in \mathbb{G}$ uniformly at random, selects $d$ cryptographic hash functions $\mathcal{H}^s_0, \ldots, \mathcal{H}^s_{d-1}$ with codomain $\mathbb{F}_p$, selects a cryptographic hash function $\mathcal{H}^p$ with codomain $\mathbb{G}$.
+$\texttt{Setup}$ outputs the group parameter tuple and the hash functions, $\textit{par} := \left(p,\mathbb{G}, d, G, \left\{\mathcal{H}^s_j\right\}_{j=0}^{d-1}, \mathcal{H}^p\right)$.\footnote{Note that domain separation can be used here to take one $\mathcal{H}^s$ and construct each $\mathcal{H}^s_j$ by defining $\mathcal{H}^s_j(x) := \mathcal{H}^s(j \mid\mid x)$.}
+
+\item $\texttt{KeyGen} \to (\textbf{sk}, \textbf{pk})$. When queried for a new key, $\texttt{KeyGen}$ samples a fresh secret key and computes the associated public key:
+\begin{align*}
+\textbf{sk} =& (z_0, z_1, \ldots, z_{d-1}) \leftarrow (\mathbb{F}_p^*)^d\\
+\textbf{pk} :=& \textbf{sk} \circ \textbf{G} = (Z_0, Z_1, \ldots, Z_{d-1}) \in \mathbb{G}^d
+\end{align*} where $\textbf{G} = (G, \ldots, G) \in \mathbb{G}^d$.
+$\texttt{KeyGen}$ outputs $(\textbf{sk}, \textbf{pk})$.
+We say $z_0$ is the \textit{linking key}, the remaining keys $\left\{z_j\right\}_{j=1}^{d-1}$ are the \textit{auxiliary keys}, and we denote the linking key with $x$.
+
+\item $\texttt{Sign}\left(m, Q, \textbf{sk}\right) \to \left\{\bot_{\texttt{Sign}}, \sigma\right\}$.
+$\texttt{Sign}$ takes as input a message $m \in \left\{0,1\right\}^*$, a ring  $Q = (\textbf{pk}_0, \ldots, \textbf{pk}_{n-1})$ for ring members $\textbf{pk}_i = (X_i, Z_{i,1}, \ldots, Z_{i,d-1}) \in \mathbb{G}^d$, and a secret key $\textbf{sk} = (x,z_1, \ldots, z_{d-1}) \in (\mathbb{F}_p^*)^d$.
+$\texttt{Sign}$ does the following.
+
+\begin{enumerate}
+\item If $Q \not\subseteq \mathbb{G}^{d\times n}$ for some $n$, $\texttt{Sign}$ outputs $\bot_{\texttt{Sign}}$ and terminates.
+
+\item Otherwise, $\texttt{Sign}$ parses\footnote{Note that this parsing always succeeds if $\texttt{Sign}$ does not fail in the previous step.} $Q$ to obtain each $\textbf{pk}_i$.
+If the public key associated with the input $\textbf{sk}$ is not a ring member in $Q$, then $\texttt{Sign}$ outputs $\bot_{\texttt{Sign}}$ and terminate.
+
+\item Otherwise, $\texttt{Sign}$ finds the signing index $\ell$ such that $\textbf{pk}_\ell = \textbf{sk} \circ (G, \ldots, G)$.
+$\texttt{Sign}$ samples $\alpha \in \mathbb{F}_p$, samples $\left\{s_i\right\}_{i \neq \ell} \in (\mathbb{F}_p)^{n-1}$, and computes the points $H_i = \mathcal{H}^p(X_i)$ for each $i$.
+$\texttt{Sign}$ computes the \textit{aggregation coefficients} $\mu_X$ and $\{\mu_j\}_{j=1}^{d-1}$, the linking tag $\mathfrak{T}$, the auxiliary group elements $\{\mathfrak{D}_j\}_{j=1}^{d-1}$, and the aggregated public keys:
+\begin{align*}
+\mathfrak{T} :=& x H_\ell & \{\mathfrak{D}_j\} :=&  \{z_j H_\ell\} \\
+\mu_X :=& \mathcal{H}^s_0(Q \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1})
+ & \mu_j :=& \mathcal{H}^s_j(Q \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}) \\
+ W_i :=& \mu_X X_i + \sum_{j=1}^{d-1} \mu_j Z_{i,j} & \mathfrak{W} :=& \mu_X \mathfrak{T} + \sum_{j=1}^{d-1} \mu_j \mathfrak{D}_j
+ \end{align*} and the aggregated secret key $w_\ell :=  \mu_X x + \sum_{j=1}^{d-1} \mu_j z_j$.
+For $i = \ell, \ell+1, \ldots, \ell-1$, (and by identifying index $n$ with index $0$), $\texttt{Sign}$ computes
+\begin{align*}
+L_\ell =& \alpha G & R_\ell =& \alpha H_\ell & c_{\ell+1} =& \mathcal{H}^s_0(Q \mid \mid m \mid \mid L_\ell \mid \mid R_\ell) \\
+L_i =& s_i G + c_i W_i & R_i =& s_i H_i + c_i \mathfrak{W}
+ & c_{i+1} =& \mathcal{H}^s_0(Q \mid \mid m \mid \mid L_i \mid \mid R_i)
+\end{align*} and lastly computes $s_\ell = \alpha - c_\ell w_\ell$.
+
+\item $\texttt{Sign}$ sets the signature $\sigma = (c_0, s_0, s_1, \ldots, s_{n-1}, \mathfrak{T}, \{\mathfrak{D}_j\}_{j=1}^{d-1})$ and publishes the signature $\sigma$.
+\end{enumerate}
+
+\item $\texttt{Verify}\left(m, Q, \sigma\right) \to \left\{0,1\right\}$.
+$\texttt{Verify}$ takes as input a message $m$, a matrix $Q = (\textbf{pk}_0, \ldots, \textbf{pk}_{n-1})$, and a signature $\sigma$.
+\begin{enumerate}
+\item If $Q \not\subseteq \mathbb{G}^{d \times n}$ for some $n$, or if $\sigma \notin \mathbb{F}_p^{n^\prime+1} \times \mathbb{G}^d$ for some $n^\prime$, $\texttt{Verify}$ outputs $0$ and terminates.
+Otherwise, if $n^\prime \neq n$, $\texttt{Verify}$ outputs $0$ and terminates.
+
+\item $\texttt{Verify}$ parses\footnote{This parsing is always successful if the previous step does not terminate $\texttt{Verify}$.} $(\textbf{pk}_0, \ldots, \textbf{pk}_{n-1}) \leftarrow Q$ for keys $\textbf{pk}_i \in \mathbb{G}^d$ for $i \in [0,n-1]$, and parses each public key $(X_i, Z_{i, 1}, \ldots, Z_{i, d-1}) \leftarrow \textbf{pk}_i$.
+$\texttt{Verify}$ also parses $(c_0, s_0, \ldots, s_{n-1}, \mathfrak{T}, \mathfrak{D}_1, \ldots, \mathfrak{D}_{d - 1}) \leftarrow \sigma$.
+$\texttt{Verify}$ computes each $H_i = \mathcal{H}^p(X_i)$, computes the aggregation coefficients, and computes aggregated public keys:
+\begin{align*}
+\mu_X := & \mathcal{H}^s_0(Q \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}) & \mu_j := & \mathcal{H}^s_j(Q \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1})\\
+W_i :=& \mu_X X_i + \sum_{j=1}^{d-1} \mu_j Z_{i,j} & \mathfrak{W} :=& \mu_X \mathfrak{T} + \sum_{j=1}^{d-1} \mu_j \mathfrak{D}_j
+\end{align*}
+
+\item $\texttt{Verify}$ sets $c_0^\prime := c_0$ and, for $i=1, 2, \ldots, n-1$, computes the following.
+\begin{align*}
+L_i :=& s_i G + c_i^\prime W_i, &
+R_i :=& s_i H_i + c_i^\prime\mathfrak{W}, &
+c_{i+1}^\prime :=& \mathcal{H}^s_0\left(Q \mid \mid m \mid \mid L_i \mid \mid R_i\right)
+\end{align*}
+\item If $c_{n}^\prime = c_0$, $\texttt{Verify}$ outputs $1$, and otherwise outputs $0$.
+\end{enumerate}
+
+\item $\texttt{Link}\left((m, Q, \sigma), (m^\prime, Q^\prime, \sigma^\prime)\right) \to \left\{0,1\right\}$. $\texttt{Link}$ takes as input two message-ring-signature triples.
+\begin{enumerate}
+\item If $\texttt{Verify}(m, Q, \sigma) = 0$ or $\texttt{Verify}(m^\prime, Q^\prime, \sigma^\prime) = 0$, $\texttt{Link}$ outputs $0$ and terminates.
+
+\item Otherwise, $\texttt{Link}$ parses\footnote{As before with $\texttt{Verify}$, this parsing is always successful if the previous step does not terminate $\texttt{Link}$.} the signatures to obtain the individual linking tags $(\mathfrak{T}, \left\{\mathfrak{D}_j\right\}_j), (\mathfrak{T}^\prime, \left\{\mathfrak{D}^\prime_j\right\}_j) \leftarrow \sigma, \sigma^\prime$.
+$\texttt{Link}$ outputs $1$ if $\mathfrak{W} = \mathfrak{W}^\prime$ and $0$ otherwise.
+\end{enumerate}
+\end{itemize}
+\end{definition}
+
+This implementation has \textit{full-key-oriented} linkability with linkability tags $\mathfrak{W}$: two signatures will link if they not only are signed using the same linking and auxiliary keys, but also the same ring.
+We can replace the $\texttt{Link}$ algorithm with \textit{single-key-oriented} linkability:
+\begin{itemize}
+
+\item $\texttt{Link}\left((m, Q, \sigma), (m^\prime, Q^\prime, \sigma^\prime)\right) \to \left\{0,1\right\}$. $\texttt{Link}$ takes as input two message-ring-signature triples.
+\begin{enumerate}
+\item If $\texttt{Verify}(m, Q, \sigma) = 0$ or $\texttt{Verify}(m^\prime, Q^\prime, \sigma^\prime) = 0$, $\texttt{Link}$ outputs $0$ and terminates.
+
+\item Otherwise, $\texttt{Link}$ parses\footnote{As before with $\texttt{Verify}$, this parsing is always successful if the previous step does not terminate $\texttt{Link}$.} the signatures to obtain the individual linking tags $(\mathfrak{T}, \left\{\mathfrak{D}_j\right\}_j), (\mathfrak{T}^\prime, \left\{\mathfrak{D}^\prime_j\right\}_j) \leftarrow \sigma, \sigma^\prime$.
+$\texttt{Link}$ outputs $1$ if $\mathfrak{T} = \mathfrak{T}^\prime$ and $0$ otherwise.
+\end{enumerate}
 \end{itemize}
 
-We require that an LRS have the properties of correctness, anonymity, unforgeability, linkability, and non-frameability.
+\section{Proofs of Security}
 
-Correctness requires that a signature generated honestly will always verify.
-\begin{definition}[Correctness]
-Consider this game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item The challenger runs $\text{KeyGen} \to (x,X)$ and supplies the keys to $\A$.
-\item The adversary $\A$ chooses a ring such that $X \in R$ and a message $M \in \{0,1\}^*$, and sends them to the challenger.
-\item The challenger signs the message with $\text{Sign}(x,M,R) \to \sigma$.
-\end{itemize}
-If $\text{Pr}[ \text{Verify}(\sigma,M,R) = 1 ] = 1$, we say that the LRS is \textit{perfectly correct}.
-\end{definition}
-Note that we do not require any ring members (except for $X$) to have been generated by $\text{KeyGen}$.
-However, distributed applications may in practice place additional restrictions on public keys used in anonymity sets.
-This allows for the possibility that $\A$ maliciously chooses ring members.
+The following lemma follows immediately from the random oracle model we use for $\mathcal{H}^s$.
 
-Unforgeability requires that an adversary who does not control the private key to a ring member cannot generate a valid signature on any message using that ring.
-\begin{definition}[Unforgeability]
-Consider this game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item The adversary $\A$ is granted access to a public-key oracle $\text{GenOracle}$ that (on the $i^\text{th}$ invocation) runs $\text{KeyGen} \to (x_i,X_i)$ and returns $X_i$ to $\A$.
-\item The adversary $\A$ is granted access to a corruption oracle $\text{CorruptOracle}(i)$ that returns $x_i$ if it corresponds to a query to $\text{GenOracle}$.
-\item The adversary $\A$ is granted access to a signing oracle $\text{SignOracle}(X,M,R)$ that runs $\text{Sign}(x,M,R) \to \sigma$ and returns $\sigma$ to $\A$, provided that $X$ corresponds to a query to $\text{GenOracle}$ and $X \in R$.
-\item Then, $\A$ outputs $(\sigma,M,R)$ such that $\text{SignOracle}$ was not queried with $(-,M,R)$, all keys in $R$ were generated by queries to $\text{GenOracle}$, and no key in $R$ was corrupted by $\text{CorruptOracle}$.
-\end{itemize}
-If $\text{Pr}[ \text{Verify}(\sigma,M,R) = 1 ] \approx 0$, we say that the LRS is $\textit{unforgeable with respect to insider corruption}$.
-\end{definition}
+\begin{lemma}
+For any $Q \subseteq \mathcal{PK}$, for any private key $sk = (x, \left\{z_j\right\}_j) \in Q$, the map $sk \mapsto \mu_X x + \sum_j \mu_j z_j$ where $\mu_X$, $\mu_j$ are computed as in Definition \ref{def:clsag} is a collision-resistant function.
+\end{lemma}
 
-Anonymity requires that as long as a ring contains at least two members that have not been corrupted, an adversary can do no better than guessing at determining the signer of an honest signature.
-\begin{definition}[Anonymity]
-Consider this game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item The adversary $\A$ is granted access to the public-key oracle $\text{GenOracle}$ and the corruption oracle $\text{CorruptOracle}$.
-\item The adversary $\A$ chooses a message $M \in \{0,1\}^*$, a ring $R$, and indices $i_0$ and $i_1$, and sends them to the challenger.
-We require that $X_{i_0},X_{i_1} \in R$ such that both keys were generated by queries to $\text{GenOracle}$, and neither key was queried to $\text{CorruptOracle}$.
-\item The challenger selects a uniformly random bit $b \in \{0,1\}$, generates the signature $\text{Sign}(x_{i_b},M,R) \to \sigma$, and sends it to $\A$.
-\item The adversary $\A$ chooses a bit $b' \in \{0,1\}$.
-\end{itemize}
-If $\text{Pr}[ b' = b ] \approx 1/2$ and $\A$ did not make any corruption queries after receiving the challenge bit, we say that the LRS is \textit{anonymous}.
-\end{definition}
-We observe that this definition permits the adversary to have corrupted or maliciously generated all but two keys in the ring.
-Some definitions allow the adversary to corrupt more keys, but we will see that this is inconsistent with our linkability construction, where an adversary in control of a ring member's private key can trivially determine if it was the signer by examining the linking tag associated to a signature.
+We prove $d$-CLSAG is unforgeable in Theorem \ref{thm:nonsl} by showing that if some PPT algorithm produces some valid, non-oracle triple $(m, Q, \sigma)$ that links to an anonymity set member in $Q$ (malicious or otherwise), then that algorithm can be rewound to compute the discrete logarithm of that anonymity set member.
+This theorem is standard for Schnorr-like signatures in the programmable random oracle model.
 
-Linkability requires that an adversary be unable to produce $k+1$ non-linked signatures on a combined anonymity set of $k$ public keys.
-\begin{definition}[Linkability]
-Consider the following game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item For $i \in [0,k-1]$, the adversary $\A$ produces a public key $X_i$, message $M_i$, ring $R_i$, and signature $\sigma_i$.
-\item The adversary $\A$ produces another message M, ring R, and signature $\sigma$.
-\item All tuples $(X_i,M_i,R_i,\sigma_i)$ and $(M,R,\sigma)$ are sent to the challenger.
-\item The challenger checks the following:
-\begin{itemize}
-\item $\left| V \right| = k$, where $V \equiv \bigcup_{i=0}^{k-1} R_i$.
-\item Each $X_i \in V$.
-\item Each $R_i \subset V$.
-\item $\text{Verify}(\sigma_i,M_i,R_i) = 1$ for all $i$.
-\item $\text{Verify}(\sigma,M,R) = 1$.
-\item For all $i \neq j$, we have $\text{Link}(\sigma_i,\sigma_j) = \text{Link}(\sigma_i,\sigma) = 0$.
-\end{itemize}
-\item If all checks pass, $\A$ wins.
-\end{itemize}
-If $\A$ wins with only negligible probability for all $k$, we say the LRS is \textit{linkable}.
-\end{definition}
-
-Non-frameability requires that an adversary be unable to generate a signature that links with an honest signature.
-\begin{definition}[Non-frameability]
-Consider also the following game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item The adversary $\A$ is granted access to the public-key oracle $\text{GenOracle}$.
-\item The adversary $\A$ is granted access to the corruption oracle $\text{CorruptOracle}$.
-\item The adversary $\A$ is granted access to the signing oracle $\text{SignOracle}$.
-\item The adversary $\A$ chooses a public key $X$ that was generated by a query to $\text{GenOracle}$, but was not presented as a query to $\text{CorruptOracle}$.
-It selects a message $M \in \{0,1\}^*$ and ring $R$ such that $X \in R$.
-It queries $\text{SignOracle}(X,M,R) \to \sigma$.
-\item The adversary $\A$ then produces a tuple $(M',R',\sigma')$ and sends $(M',R',\sigma')$ to the challenger, along with $(X,M,R,\sigma)$.
-\item If $\text{Verify}(\sigma',M',R') = 0$ or if $\sigma'$ was produced using a query to $\text{SignOracle}$, the challenger aborts.
-\end{itemize}
-If $\text{Pr}[ \text{Link}(\sigma,\sigma') = 1 \approx 0$, we say that the LRS is \textit{non-frameable}.
-\end{definition}
-
-\section{Application: linkable ring signature}
-The constructions in \cite{groth,bootle} describe how to use a similar sigma protocol to construct a simple ring signature scheme.
-Using our modifications, we can easily extend this to account for linkability and non-frameability.
-We briefly show how to do so.
-
-\begin{figure}[htbp]
-\centering
-\fbox{\begin{minipage}{0.95\textwidth}
-    $\underline{\text{KeyGen}(r):}$
-    \begin{itemize}
-        \item If not specified, select $r \in \F$ uniformly at random.
-        \item Compute $R = rG$.
-        \item Return $(x,X) = (r,R)$.
-    \end{itemize}
-
-    $\underline{\text{Sign}(x,M,R):}$
-    \begin{itemize}
-        \item Let $R = \{X_0,\ldots,X_{N-1}\}$ such that $X_l = x_lG$.
-        \item Compute $J \equiv x_l^{-1}U$.
-        \item Run $\mathcal{P}_{\text{link}}(R,J;(l,x_l)) \to a$ (up to the verifier challenge).
-        \item Set $\xi \equiv \hs(M,R,a)$.
-        \item Run $\mathcal{P}_{\text{link}}(\xi) \to z$ (after the verifier challenge).
-        \item Return $\sigma = (a,z,J)$.
-    \end{itemize}
-
-    $\underline{\text{Verify}(\sigma,M,R):}$
-    \begin{itemize}
-        \item Let $R = \{X_0,\ldots,X_{N-1}\}$ such that $X_l - x_lG$.
-        \item Let $\sigma = (a,z,J)$.
-        \item Set $\xi \equiv \hs (M,R,a)$.
-        \item Return $\mathcal{V}_{\text{link}}(R,J,a,z)$.
-    \end{itemize}
-
-    $\underline{\text{Link}(\sigma,\sigma'):}$
-    \begin{itemize}
-        \item We implicitly assume that $\sigma$ and $\sigma'$ have been previously verified.
-        \item Let $\sigma = (a,z,J)$ and $\sigma' = (a',z',J')$.
-        \item If $J = J'$, return $1$.
-        Otherwise, return $0$.
-    \end{itemize}
-\end{minipage}}
-    \caption{Linkable ring signature using $\mathcal{R}_{\text{link}}$}
-    \label{fig:lrs}
-\end{figure}
-
-\begin{theorem}
-The protocol in Figure \ref{fig:lrs} is a linkable ring signature construction.
+\begin{theorem}[Hardness of Discrete Logarithms of Linear Combinations Implies Unforgeability] \label{thm:nonsl}
+If a $(t, \epsilon, q)$-solver of the unforgeability exists for the scheme of Definition \ref{def:clsag} that makes $\kappa^\prime$ corruption oracle queries, then there exists a $(2(t+t_0) + t_1, \epsilon\left(\frac{\epsilon}{q} - \frac{1}{2^\eta}\right) - \mu, \lfloor \frac{q}{d}\rfloor)$-solver of the $2d\kappa^\prime$-one-more discrete logarithm of linear combinations problem in $\mathbb{G}$ for some negligible $\mu$ and some constants $t_0, t_1$.
 \end{theorem}
@@
 \begin{proof}
-Perfect correctness follows immediately from the perfect completeness of the proving system for $\mathcal{R}_{link}$.
+Assume $\texttt{A}$ is a $(t, \epsilon, q)$-solver of the non-slanderability game of Definition \ref{def:acst-nonsl}.
+We wrap $\texttt{A}$ in an algorithm $\texttt{B}$.
+The algorithm $\texttt{B}$ executes $\texttt{A}$ in a black box, handling oracle queries for $\texttt{A}$.
+Then, $\texttt{B}$ regurgitates the output of $\texttt{A}$ together with an index $idx$.
+This way, $\texttt{B}$ is suitable for use in the forking lemma.
+We wrap $\mathcal{F}^{\texttt{B}}$ in a master algorithm $\texttt{M}$ that is a $(2(t+t_0) + t_1, \epsilon\left(\frac{\epsilon}{q} - \frac{1}{2^\eta}\right) - \mu, \lfloor \frac{q}{d}\rfloor)$-solver of the $\kappa$-one-more discrete logarithm of linear combinations problem in $\mathbb{G}$.
 
-Similarly, anonymity follows since the proving system is special honest-verifier zero knowledge, and therefore witness indistinguishable \cite{cramer}.
-Any adversarial advantage in breaking anonymity must therefore arise from distinguishing either input commitments or linking tags in signatures.
-Since honestly-generated input Pedersen commitments are perfectly hiding, they are indistinguishable from elements of $\G$ selected uniformly at random; we assume by definition that at least two such commitments are present in such a signature.
-Further, honestly-generated linking tags are generated from a one-way pseudorandom function, and therefore in the random oracle model are independently uniformly distributed from other proof elements and input commitments.
+If $\texttt{A}$ produces a successful forgery, each verification query of the form $c_{\ell+1} = \mathcal{H}^s(m \mid \mid Q \mid \mid R_\ell \mid \mid L_\ell)$ occurs in the transcript between $\texttt{A}$ and the random oracle $\mathcal{H}^s$.
+Indeed, the signature triple produced by $\texttt{A}$ passes verification, so each challenge $c_{\ell+1}$, whether made with oracle queries in the transcript or not, must be matched by random oracle queries made by the verifier.
+The prover cannot guess the output of such a query before making it except with negligible probability.
+Hence, if $\texttt{A}$ outputs a valid signature, all verification challenges are computed by an actual oracle query.
+See \cite{liu2004linkable} for a formal proof of this fact.
+Since all verification challenges are found through genuine oracle queries, which are well-ordered, there exists a first $\mathcal{H}^s$ query made by $\texttt{A}$ for computing verification challenges, say $c = \mathcal{H}^s(m \mid \mid Q \mid \mid R^* \mid \mid L^*)$.
+This was not necessarily the first query made to $\mathcal{H}^s$ overall, though; say it was the $k^{th}$ query.
+Although the ring index for this query may not have been decided when this query was first issued by $\texttt{A}$, by the end of the transcript the ring index has been decided.
 
-The proof for unforgeability in \cite{groth} relies on the (special) soundness of the underlying sigma protocol; it applies directly to our modification for $\mathcal{R}_{link}$, and is not repeated here.
+We construct $\texttt{B}$ in the following way.
+We grant $\texttt{B}$ access to the same oracles as $\texttt{A}$.
+Any oracle queries made by $\texttt{A}$ are passed along by $\texttt{B}$ to the oracles.
+The responses are recorded and then passed back to $\texttt{A}$.
+The algorithm $\texttt{B}$ works by finding two indices to augment the output of $\texttt{A}$.
+First, $\texttt{B}$ finds the $\mathcal{H}^s$ query index $k$ corresponding to the first verification challenge computed by $\texttt{A}$ used in verifying the purported foergery.
+Second, $\texttt{B}$ inspects the transcript of $\texttt{A}$ to find the anonymity set index $\ell$ in the transcript such that $c = c_{\ell+1}$ and $R^* = R_\ell$ and $L^* = L_\ell$.
+Now $\texttt{B}$ outputs $idx = (k, \ell)$ along with whatever $\texttt{A}$ outputs.
+Clearly, $\texttt{B}$ makes the same number of corruption oracle queries as $\texttt{A}$.
 
-To show linkability, observe first that $\text{Link}$ simply compares linking tags, so two signatures link if and only if they share a common linking tag.
-Suppose an adversary can win the linkability game with non-negligible probability for some $k > 1$.
-Since all provided signatures verify, soundness implies extraction of a witness $x_i$ from signature $\sigma_i$ for all $i$, and of a witness $x$ from $\sigma$.
-Note that all $\{x_i\}$ and $x$ are distinct.
-If $x_i = x_j$ for $i \neq j$, then the corresponding linking tags $J_i$ and $J_j$ are such that $x_iJ_i = x_jJ_j = U$; then $J_i = J_j$, which contradicts $\text{Link}(\sigma_i,\sigma_j) = 0$.
-The same reasoning holds to show $x$ is similarly distinct.
-Soundness also implies that for all $i$, there exists $X_i \in R_i$ such that $x_iG = X_i$; similarly, there exists $X \in R$ such that $xG = X$.
-By assumption we have $$\{X_0,\ldots,X_{k-1},X\} \subset \left( \bigcup_{i=0}^{k-1} R_i \right) \cup R \subset V.$$
-However, note that $\left| \{X_0,\ldots,X_{k-1},X\} \right| = k+1$, but that $\left| V \right| = k$, a contradiction.
+Note $\texttt{B}$ succeeds whenever $\texttt{A}$ does and runs in time at most $t$ just like $\texttt{A}$, except for some additional time $t_0$ to search the transcript for $idx$.
+Since $\texttt{B}$ is suitable for use in the forking lemma, we can use $\mathcal{F}^{\texttt{B}}$ to construct $\texttt{M}$.
 
-Finally, we show non-frameability and assume an adversary has a non-negligible advantage in breaking this property.
-Because we have $\text{Verify}(\sigma',M',R') = 1$, soundness implies extraction of a witness $x' \in \F$ such that $x'G \in R'$; we also have a witness $x$ such that $xG \in R$ from the known signature $\sigma$.
-Since $\text{Link}(\sigma,\sigma') = 1$, the corresponding linking tags $J$ and $J'$ are equal by definition; hence by soundness $xJ = x'J' = U$, giving $x = x'$.
-However, the adversary did not query $\text{CorruptOracle}$ with $X$, meaning it breaks the discrete logarithm problem non-negligibly.
+The algorithm $\mathcal{F}^{\texttt{B}}$ is granted oracle access to the same oracles as $\texttt{B}$ except $\mathcal{H}^s$ and $\texttt{SO}$.
+The algorithm $\mathcal{F}^{\texttt{B}}$ simulates $\texttt{SO}$ queries made by $\texttt{B}$ by simple back-patching of $\mathcal{H}^s$ and simulates the other queries made to $\mathcal{H}^s$ queries made by $\texttt{B}$ using the random tapes $\textbf{h}, \textbf{h}^*$ as described in Section \ref{sec:hardness}.
+All other oracle queries made by $\texttt{B}$ are passed along by $\mathcal{F}^{\texttt{B}}$ to the actual oracles and handed back to $\texttt{B}$.
+
+Note that $\mathcal{F}^{\texttt{B}}$ runs in time $2(t+t_0)$ and (with probability at least $\epsilon\left(\frac{\epsilon}{q} - \frac{1}{2^\eta}\right)$) outputs a pair of valid signature triples $(m, Q, \sigma)$, $(m^\prime, Q^\prime, \sigma^\prime)$.
+The messages and anonymity sets are selected before the fork point in the transcripts, so $m=m^\prime$ and $Q=Q^\prime$.
+Moreover, $\mathcal{F}^{\texttt{B}}$ makes at most $2\kappa^\prime$ corruption queries.
+The challenges for the two transcripts are distinct since the forking algorithm outputs the failure symbol $\bot$ and terminates if the challenges for $c_{\ell + 1}$ are the same in each transcript.
+\[c_{\ell + 1} \leftarrow \mathcal{H}^s_0(m \mid \mid Q \mid \mid R_\ell \mid \mid L_\ell) \rightarrow c_{\ell+1}^\prime.\]
+
+We wrap $\mathcal{F}^{\texttt{B}}$ in an algorithm $\texttt{M}$ that plays the $\kappa$-one-more discrete logarithm game of Definition \ref{def:komdl} for $\kappa = 2\cdot d \cdot \kappa^\prime$.
+The algorithm $\texttt{M}$ has corruption oracle access and runs $\mathcal{F}^{\texttt{B}}$ in a black box, passing corruption oracle queries made by $\mathcal{F}^{\texttt{B}}$ along.
+The algorithm $\texttt{M}$ finds the following system of equations in the transcripts by inspecting the verification challenge queries
+\[R_\ell = s_\ell G + c_\ell X_\ell = s_\ell^\prime G + c_\ell^\prime X_\ell,\]
+\[L_\ell = s_\ell H_\ell + c_\ell \mathfrak{W} = s_\ell^\prime H_\ell + c_\ell^\prime \mathfrak{W}.\] This $\texttt{M}$ has enough information to compute
+\[ W_\ell = \frac{s_\ell - s_\ell^\prime}{c_\ell^\prime - c_\ell} G,  \mathfrak{W} = \frac{s_\ell - s_\ell^\prime}{c_\ell^\prime - c_\ell} H_\ell.\]
+and therefore the private key $w = \frac{s_{\ell} - s_\ell^\prime}{c_\ell^\prime - c_\ell}$. Formally, $\texttt{M}$ operates as follows.
+
+\begin{enumerate}[(1)]
+\item $\texttt{M}$ inputs the set of discrete logarithm challenge public keys $S = \left\{\widetilde{pk}_i\right\}_{i=0}^{q-1}$.
+
+\item $\texttt{M}$ partitions the challenge keys into lists of $d$ keys
+\begin{align*}
+pk_0 =&  (X_0, Z_{0, 1}, \ldots, Z_{0, d-1}) := (\widetilde{pk}_0, \ldots, \widetilde{pk}_{d-1}) \\
+pk_1 =& (X_1, Z_{1, 1}, \ldots, Z_{1, d-1}) := (\widetilde{pk}_d, \ldots, \widetilde{pk}_{2d-1}) \\
+\vdots
+\end{align*} obtaining $S := \left\{pk_i\right\}_{i=0}^{\left\lfloor \frac{q}{d}\right\rfloor}$.
+
+\item $\texttt{M}$ picks two random tapes $\textbf{h}, \textbf{h}^\prime$ to simulate oracle query responses for $\mathcal{F}^{\texttt{B}}$.
+
+\item $\texttt{M}$ executes $\mathcal{F}^{\texttt{B}}$ in a black box, using $S$ as input.
+Upon receiving a corruption query from $\mathcal{F}^{\texttt{B}}$ on some $pk_i$, $\texttt{M}$ makes a $\texttt{CO}$ query on $X_i$ and each $Z_{j,i}$, passing $sk_i$ back to $\mathcal{F}^{\texttt{B}}$.
+Each corruption query made by $\mathcal{F}^{\texttt{B}}$ consists of $d$ corruption queries made to $\texttt{CO}$ by $\texttt{M}$.
+
+\item If $\mathcal{F}^{\texttt{B}}$ fails, or if $\mathcal{F}^{\texttt{B}}$ succeeds with all zero coefficients $\mu_X$ and $\mu_j$, then $\texttt{M}$ samples a random $w \in \mathbb{F}$, samples a random subset of challenge keys $\left\{pk^*_j\right\}_j \subseteq S$, samples random coefficients $\left\{h_j\right\}_j$, outputs $w, \left\{pk^*_j\right\}_j, \left\{h_j\right\}_j$, and terminates.
+
+\item Otherwise, $\texttt{M}$ obtains two signature triples with the same message and ring, $(m, Q, \sigma), (m, Q, \sigma^\prime)$ at at least one non-zero aggregation coefficient.
+$\texttt{M}$ computes the challenge discrete logarithm $w = (c_\ell^\prime - c_\ell)^{-1}(s_\ell - s_\ell^\prime)$.
+$\texttt{M}$ outputs $w, \left\{\mu_X, \left\{\mu_j\right\}_j\right\}$, and $\left\{X_\ell, \left\{Z_{\ell, j}\right\}_j\right\}$.
+\end{enumerate}
+
+Denote with $t_1$ the time it takes for $\mathcal{M}$ to inspect the transcript, perform field operations, and process corruption queries for $\mathcal{F}^{\texttt{B}}$.
+Then the algorithm $\texttt{M}$ runs in time at most $2(t+t_0) + t_1$.
+
+To complete the proof, consider the overall success probability and timing of $\texttt{M}$.
+Since $\texttt{A}$ is a $(t, \epsilon, q)$-solver of the unforgeability game and these are successful signatures, there must be at least one query made to $\texttt{SO}$ corresponding to an uncorrupted challenge key linking to these signatures.
+In particular, $w \cdot G = W_\ell = \mu_X X_\ell + \sum_j \mu_j Z_{\ell,j}$ for some $(X_\ell, \left\{Z_{\ell, j}\right\}_j) \in Q$.
+The algorithm $\texttt{M}$ succeeds at the discrete logarithms of linear combinations game whenever $\mathcal{F}^{\texttt{B}}$ succeeds at forking $\texttt{B}$ and at least one coefficient $\mu_X$ and $\mu_j$ is non-zero; we denote the probability of obtaining any zero coefficients as $\mu$.
+We note that $\mu$ is negligible under the random oracle model.
+Thus, $\texttt{M}$ runs in time at most $2(t+t_0) + t_1$, has success probability exceeding $\epsilon\left(\frac{\epsilon}{q} - \frac{1}{2^\eta}\right) - \mu$.
 \end{proof}
 
-\section{Protocol: parallel linkable one-of-many commitment}
-In this section, we describe a modification of the sigma protocol for $\mathcal{R}_{\text{link}}$ that permits us to prove knowledge of multiple commitments in separate sets at the same index position, while retaining the linking property in the first commitment set only.
-We later show how to apply such a construction to a signer-ambiguous transaction protocol that can demonstrate balance preservation.
+The proof of Theorem \ref{thm:nonsl} demonstrates that the validity of a triple implies that the aggregated private key $w$ is the discrete logarithm of the aggregated linking tag $\mathfrak{W}$ with respect to $H_\ell$ and is also the discrete logarithm of the aggregated key $W_\ell$ with respect to $G$.
+In this way, the linking tag of a valid signature must be the linking tag corresponding to at least one ring member, except possibly with negligible probability.
 
-We wish to produce a sigma protocol for the following relation:
-$$\mathcal{R}_{\text{par}} = \left\{ \{M_i\}_{i=0}^{N-1} \subset \G, \{P_i\}_{i=0}^{N-1} \subset \G, J \in \G ; (l \in \mathbb{Z},r \in \F,s \in \F) : M_l = rG \text{ and } P_l = sG \text{ and } U = rJ \right\}$$
-This requires only minor modifications to the protocol for $\mathcal{R}_{\text{link}}$, so we document only the modified proof elements constructed and verified in Figure \ref{fig:par}.
-All other proof elements are generated and verified identically.
+\begin{theorem}[No Alien Linking Tags]\label{cor:no-aliens}
+If there exists a PPT algorithm $\texttt{A}$  that produces a valid signature triple $(m, Q, \sigma)$ with the scheme in Definition \ref{def:clsag}, then there exists a ring member in $Q$ whose aggregated key $W_\ell$ has the same discrete logarithm $w$ with respect to $G$ as $\mathfrak{W}$ has with respect to $H_\ell$, and this $w$ is known to $\texttt{A}$ (except possibly with negligible probability).
+\end{theorem}
 
-\begin{figure}[htbp]
-\centering
-\fbox{\begin{minipage}{0.95\textwidth}
-$\underline{\mathcal{P}_{\text{par}}(\{M_i\},\{P_i\},J;(l,r,s)):}$
-\begin{itemize}
-\item Define $K \equiv sJ$.
-\item Define $\mu \equiv \hs(\{M_i\},\{P_i\},J,K)$.
-\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}(M_k + \mu P_k) + \rho_jG$$
-\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv (U + \mu K)\sumk p_{k,j} + \rho_jG$$
-\end{itemize}
-
-$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
-$K,\{X_j\},\{Y_j\}$ \\
-
-$\underline{\mathcal{V} \to \mathcal{P}:}$ \\
-$\xi \in \{0,1\}^*$ \\
-
-$\underline{\mathcal{P}(\xi):}$
-\begin{itemize}
-\item Define $z \equiv (r + \mu s)\xi^m - \sumj \rho_j\xi^j$.
-\end{itemize}
-
-$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
-$z$ \\
-
-$\underline{\mathcal{V}_{\text{par}}(\{M_i\},\{P_i\},J):}$
-\begin{itemize}
-\item Define $\mu \equiv \hs(\{M_i\},\{P_i\},J,K)$.
-\item Accept if and only if:
-\begin{eqnarray*}
-\sumk (M_k + \mu P_k) \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG &=& 0 \\
-(U + \mu K)\sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ &=& 0
-\end{eqnarray*}
-\end{itemize}
-\end{minipage}}
-\caption{Sigma protocol (abbreviated) for $\mathcal{R}_{\text{par}}$}
-\label{fig:par}
-\end{figure}
-
-\begin{theorem}
-The protocol in Figure \ref{fig:par} is perfectly complete, special honest-verifier zero knowledge, and $(m+1)$-special sound.
+\begin{theorem}\label{thm:linkabilty}
+The scheme in Definition \ref{def:clsag} is linkable under Definition \ref{def:acst-link-adv} and Definition \ref{def:pig-link}.
 \end{theorem}
@@
 \begin{proof}
-In the random oracle model, extraction of a witness of the form $r + \mu s$ implies knowledge of both $r$ and $s$ such that $rG = M_l$ and $sG = P_l$, similarly to the key-aggregation arguments in \cite{musig}.
-The same extraction shows that $(r + \mu s)J = U + \mu K$, which implies in particular that $rJ = U$, as required.
+We show that valid, non-oracle signature triples from the scheme in Definition \ref{def:clsag} satisfying the corrupted key conditions in the game of Definition \ref{def:acst-link-adv} always link.
+Hence, any algorithm fails at that game except with negligible probability.
 
-The rest of the proof follows with only trivial modifications from the proof for $\mathcal{R}_{\text{link}}$.
+Assume that $\texttt{A}$,  while playing the game of ACST linkability from Definition \ref{def:acst-link-adv}, produces a pair of valid, non-oracle signature triples $(m, Q, \sigma)$, $(m^*, Q^*, \sigma^*)$ such that at most one key in $Q \cup Q^*$ is corrupted or outside of $S$.
+This algorithm can be forked and rewound as above to compute the aggregated private key used in computing each signature, say $w, w^*$.
+At most one key in $Q \cup Q^*$ is corrupted or outside of $S$.
+Since $\texttt{A}$ has knowledge of $w$, then $w$ is corrupted or outside of $S$, and likewise $w^*$ is corrupted or outside of $S$.
+Since at most one key in $Q \cup Q^*$ can be corrupted or outside of $S$, we conclude $w = w^*$.
+
+Since key aggregation is collision resistant and $wG$ is the aggregated public key for some public key $(X_\ell, \left\{Z_{\ell, j}\right\}_j) \in Q \cap Q^*$, $w$ must be aggregated from a private key $(x_\ell, \left\{z_{\ell, j}\right\}_j)$ via the collision-resistant aggregation function.
+In both the case of single-key-oriented linkability and full-key-oriented linkability, the linkability tags are therefore exactly equal.
+Hence, with probability $1$, the pair of triples $(m, Q, \sigma)$, $(m^*, Q^*, \sigma^*)$ are linked, and $\texttt{A}$ fails at ACST linkability except with negligible probability.
+
+Similarly, an algorithm that outputs $q+1$ unlinked signatures can be rewound to compute $2(q+1)$ signatures from which $q+1$ aggregated keys can be computed.
+Moreover, if these signatures are unlinked, then the $q+1$ aggregated keys are distinct, violating $q$-pigeonhole linkability.
 \end{proof}
 
-\section{Application: signer-ambiguous transaction protocol}
-The parallel construction described in Figure \ref{fig:par} can be used in a signer-ambiguous transaction protocol.
+\begin{theorem}
+The scheme in Definition \ref{def:clsag} is linkably anonymous.
+\end{theorem}
 
-Suppose a user wishes to generate a transaction consuming $W$ previously-generated outputs and generating $T$ fresh outputs.
-The user shuffles the consumed outputs within a larger list of $N$ outputs $\{M_k\}_{k=0}^{N-1}$, such that there exist indices $\{l_u\}_{u=0}^{W-1}$ where each $M_{l_u} = r_u$ for some known private key $r_u$.
-Further, assume each $M_{l_u}$ comes equipped with an amount commitment of the form $P_{l_u} \equiv \com(a_u,s_u)$ for amount $a_u$ and mask $s_u$.
-(All other $M_k$ also come equipped with a corresponding $P_k$, but the structure of these points is not relevant here.)
+\begin{proof}
+We assume $\texttt{A}$ is a $(t, \epsilon, q)$-solver of linkable anonymity that has access to the random oracles $\mathcal{H}^p$, $\mathcal{H}^s$ and a signing oracle $\texttt{SO}$.
+We construct an algorithm $\texttt{B}$ has $\mathcal{H}^p$ oracle access, executes $\texttt{A}$ as a black box, simulates $\mathcal{H}^s$ queries made by $\texttt{A}$ with coin flips, simulates $\texttt{SO}$ queries made by $\texttt{A}$ via usual back-patching, and plays the random oracle decisional Diffie-Hellman game of Definition \ref{def:rom-ddh}.
+The algorithm $\texttt{B}$ works formally as follows.
 
-The user generates $W$ auxiliary commitments $P'_u \equiv \com(a_u,s'_u)$ to the same amounts, but with different masks $\{s'_u\}$ chosen uniformly at random from $\F$.
-Then, the user generates $W$ spend proofs, each using the following prover inputs for $u \in [0,W)$:
-$$\mathcal{P}_{par}(\{M_i\},\{P_i-P'_u\},r_u^{-1}U;(l_u,r_u,s_u-s'_u))$$
+\begin{enumerate}[(1)]
+\item $\texttt{B}$ takes as input $S^{(b)} = \left\{(\widetilde{pk}_i, \widetilde{\mathfrak{T}}_i^{(b)})\right\}_{i=0}^{q-1}$.
 
-For $j \in [0,T)$, the user generates a fresh output of the form $Q_j \equiv \com(b_j,t_j)$ for amount $b_j$ and mask $t_j$.
-The masks are chosen such that for $j \in [1,T)$, we have $t_j$ chosen uniformly at random from $\F$.
-We then choose $$t_0 \equiv \sum_{u=0}^{W-1} s_u' -\sum_{j=1}^{T-1} t_j$$ and include all $\{P'_u\}$ auxiliary commitments in the transaction.
+\item $\texttt{B}$ partitions the challenge keys into lists of $d$ keys
+\begin{align*}
+pk_0 =&  (X_0, Z_{0, 1}, \ldots, Z_{0, d-1}) := (\widetilde{pk}_0, \ldots, \widetilde{pk}_{d-1}) \\
+pk_1 =& (X_1, Z_{1, 1}, \ldots, Z_{1, d-1}) := (\widetilde{pk}_d, \ldots, \widetilde{pk}_{2d-1}) \\
+\vdots
+\end{align*} obtaining $S := \left\{pk_i\right\}_{i=0}^{\left\lfloor \frac{q}{d}\right\rfloor}$.
 
-To verify such a transaction, the verifier first performs verification on each spend proof to ensure it is valid.
-Then, the verifier ensures that $$\sum_{u=0}^{W-1} P'_u - \sum_{j=0}^{T-1} Q_j = 0$$ such that the transaction balances.
-This succeeds since the commitments sum to zero if and only if the difference of input and output amounts is zero, which holds since the Pedersen commitment construction is computationally binding.
+\item $\texttt{B}$ sends $S$ to $\texttt{A}$, who outputs a piar of indices $i_0, i_1$.
 
-\section{Efficiency}
-Triptych proofs scale logarithmically with the size of the input anonymity set; this is the best asymptotic scaling known for ring signatures that do not require a trusted setup process over non-pairing groups.
-Related protocols based on the inner-product compression method of \cite{bulletproofs} include Omniring \cite{omniring} and RingCT 3.0 \cite{omniring}.
-However, it is challenging to directly compare these protocols' efficiency.
-Omniring includes all transaction input signatures, output range proofs, and balance within a single proof structure; however, it is not possible to verify a batch of proofs more efficiently by combining common generators.
-While an early version of RingCT 3.0 used separate input, range, and balance proofs, the most recent version merges all input and balance proofs together but outsources the range proofs to an efficient construction like \cite{bulletproofs}; this comes at the cost of requiring that the number of inputs be a power of two or otherwise carefully padded (affecting verification time).
-Therefore, for the purpose of comparison we modify slightly the earlier version of RingCT 3.0 with a soundness fix applied from the updated version, ignoring the size and verification cost of non-proof elements.
-Another more direct comparison is to $2$-CLSAG, a linear-sized linkable ring signature construction \cite{clsag}.
+\item $\texttt{B}$ grants $\texttt{SO}$ access to $\texttt{A}$, simulating oracle queries for non-challenge keys via back-patching and responding with honestly generated signatures for challenge keys.
 
-We now show size and verification comparisons of the parallel instantiation of Triptych, the earlier (modified) version of RingCT 3.0, and $2$-CLSAG.
-For verification scaling, we also account for the use of batching in Triptych and RingCT 3.0, where generators common to multiple proofs are used only once in verification.
-Further, since verification in both of these constructions reduces to checking whether several multiscalar multiplications are zero, we may apply random weighting such that verifying a batch of multiple proofs reduces to a single multiscalar multiplication.
-The use of efficient multiscalar multiplication algorithms like \cite{straus,pippenger} means that an $n$-multiscalar multiplication evaluates as $O(n/\log n)$.
-This form of batching does not apply to CLSAG, where verification consists of a sequence of hash function evaluations.
+\item $\texttt{A}$ outputs a bit $b^\prime$; $\texttt{B}$ outputs the same $b^\prime$.
+\end{enumerate}
 
-Table \ref{table:size} compares proof/signature sizes and verification complexity for these constructions as a function of the anonymity set size $N$ and batch size $B$.
-Verification complexity is separated into the number of hash-to-$\F$ operations (denoted $\hs$), hash-to-$\G$ operations (denoted $\hp$), and $i$-multiscalar multiplication operations of size $k(i)$.
-Figure \ref{fig:size} examines size as a function of input anonymity set size, under the assumption that elements of both $\G$ and $\F$ occupy $32$ kB of space.
-We note that although RingCT 3.0 proofs are slightly smaller for large $N$, Triptych proofs are smaller for $N < 512$, a limited but reasonable range given practical verification times.
-We also note that the application of Triptych in a complete transaction protocol is not directly compared to RingCT 3.0 here, as the use of non-proof/signaure auxiliary data in such a protocol may differ based on particular implementations.
+Note that if $\texttt{A}$ succeeds with a non-negligible advantage $\left|\epsilon - \frac{1}{2}\right|$, then $\texttt{B}$ succeeds with the same advantage.
+Moreover, $\texttt{B}$ takes only some additional time to process keys and simulate $\texttt{SO}$ queries, both of which we assume are dominated by the time it takes $\texttt{A}$ to succeed.
+\end{proof}
 
-\begin{table}[h]
-\centering
-\begin{tabular}{r|ll|l}
-& Size ($\G$) & Size ($\F$) & Verification (batch total) \\
+\section{Efficiency}\label{sec:efficiency}
+Consider the space and time efficiency of Definition \ref{def:clsag}. We disregard any additional information typically broadcast alongside the signature, such as representations of the ring members.
+
+A $d$-CLSAG signature with a ring size of $n$ contains $n+1$ field elements and $d$ group elements; signature size is $k_s(n+1) + k_p d$ where $k_s$ describes the size of field elements and $k_p$ describes the size of group elements.
+
+To examine the verification time complexity, let $t_s$ and $t_p$ be the time complexity of evaluating the hash-to-scalar functions $\mathcal{H}^s$ and of evaluating the hash-to-point function $\mathcal{H}^p$, respectively.
+Let $t^{(i)}$ be the time complexity to evaluate a linear combination of $i$ terms; using specialized algorithms for multiscalar multiplication \cite{straus1964addition,pippenger1980evaluation}, such a linear combination can be evaluated much more quickly than a simple term-by-term computation.
+We note that it is also possible to cache multiples of group elements that are reused within verification for faster linear combination evaluation, but we do not differentiate this here.
+Using these, the time complexity of $d$-CLSAG verification is $(n+d)t_s + nt_p + 2nt^{(d+1)}$.
+
+To compare to the efficiency of an MLSAG implementation from \cite{noether2016ring}, observe that $2$-CLSAG has equivalent functionality to an MLSAG signature (which is a $2$-LRS).
+An MLSAG signature used in this way produces $2n+1$ field elements and $1$ group element.
+
+We produced a test implementation in C++ and tested signing and verification for MLSAG and $2$-CLSAG on a 2.1 GHz Opteron processor.
+Table \ref{table:timing} shows the results for different ring sizes.
+In particular, we note that for smaller anonymity sizes, $2$-CLSAG is uniformly faster than MLSAG.
+However, at very large ring sizes, MLSAG is faster due to additional computations involved in computing aggregation coefficients and key prefixing.
+Despite this eventual inefficiency, we note that the linear space requirements generally preclude the use of very large ring sizes in practice, making $2$-CLSAG an efficient improvement over MLSAG in both space and time.
+
+\begin{table}[htp]
+\begin{center}
+\begin{tabular}{r|ll|ll}
+& \multicolumn{2}{c|}{Verify} & \multicolumn{2}{c}{Sign} \\
 \hline
-CLSAG \cite{clsag} & $2$ & $N + 1$ & $B(N + 2) \hs + BN \hp + 2BN k(3)$ \\
-RingCT 3.0 \cite{rct3} & $2\lg(N) + 9$ & $9$ & $k(B[2N + 2\lg(N) + 9] + 2N + 5)$ \\
-Triptych (this work) & $2\lg(N) + 6$ & $\lg(N) + 3$ & $k(B[2N + 2\lg(N) + 2] + 2\lg(N) + 3)$
+Anonymity set & MLSAG & CLSAG & MLSAG & CLSAG \\
+\hline
+2 & 2.4 & 2.0 & 2.3 & 2.7 \\
+4 & 4.7 & 4.0 & 4.6 & 4.6 \\
+8 & 9.5 & 7.8 & 9.4 & 8.5 \\
+16 & 18.9 & 15.9 & 18.9 & 16.5 \\
+32 & 37.8 & 32.3 & 37.8 & 33.0 \\
+64 & 75.4 & 67.5 & 75.9 & 68.3 \\
+128 & 150 & 147 & 151 & 148 \\
+256 & 301 & 344 & 303 & 346
 \end{tabular}
-\caption{Proof sizes and verification complexity, for anonymity set size $N$ and batch size $B$}
-\label{table:size}
+\end{center}
+\caption{Signing and verification times (ms) for MLSAG and $2$-CLSAG}
+\label{table:timing}
 \end{table}
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.6\textwidth]{size.png}
-\caption{Proof sizes for input anonymity set size $N$}
-\label{fig:size}
-\end{figure}
-
-\section{Future work}
-It is possible to further extend the Triptych proving system to support proving knowledge of openings of multiple commitments within the \textit{same} anonymity set, while permitting the construction of linking tags for each such opening and demonstrating balance directly within a single proof.
-Such a construction is much more efficient than the present work when built into a transaction protocol, but the security definitions applying to such a construction are still under evaluation.
-
-\bibliographystyle{plain}
-\bibliography{main}
+\bibliographystyle{splncs04}
+\bibliography{bibliography}
 

### 2020-04-07 paper/iacr.tex
Moved files for Arcturus to separate branch

--- 2020-01-24 paper/iacr.tex
@@
 \item Select random $r_A \in \F$ and $\left\{a_{j,i}\right\}_{i=1,j=0}^{n-1,m-1} \subset \F$.
-Define $A \equiv \com(a,r_A)$.
+Set $$\{a_{j,0}\}_{j=0}^{m-1} \equiv -\sum_{i=1}^{n-1} a_{j,i}$$ and define $A \equiv \com(a,r_A)$.
 \item Define $\left\{\sigma_{j,i}\right\}_{i,j=0}^{n-1,j-1} \subset \F$ such that $\sigma_{j,i} \equiv \delta\left(l_j,i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
@@
 We note that although RingCT 3.0 proofs are slightly smaller for large $N$, Triptych proofs are smaller for $N < 512$, a limited but reasonable range given practical verification times.
-We also note that the application of Triptych in a complete transaction protocol is not directly compared to RingCT 3.0 here, as the use of non-proof/signaure auxiliary data in such a protocol may differ based on particular implementations.
+We also note that the application of Triptych in a complete transaction protocol is not directly compared to RingCT 3.0 here, as the use of non-proof/signature auxiliary data in such a protocol may differ based on particular implementations.
 

### 2020-04-07 triptych-multi/dumb25519.py

@@ -1,604 +1,0 @@
-# Dumb25519: a stupid implementation of ed25519
-#
-# Use this code only for prototyping
-# -- putting this code into production would be dumb
-# -- assuming this code is secure would also be dumb
-
-import random
-import hashlib
-import binascii
-
-# Curve parameters
-q = 2**255 - 19
-l = 2**252 + 27742317777372353535851937790883648493
-cofactor = 8
-b = 256 # bit length
-
-# Internal helper methods
-def exponent(b,e,m):
-    return pow(b,e,m)
-
-def invert(x,p):
-    # Assumes `p` is prime
-    return exponent(x,p-2,p)
-
-def xfromy(y):
-    temp = (y*y-1) * invert(d*y*y+1,q)
-    x = exponent(temp,(q+3)/8,q)
-    if (x*x - temp) % q != 0:
-        x = (x*I) % q
-    if x % 2 != 0:
-        x = q-x
-    return x
-
-def bit(h,i):
-    return (ord(h[i/8]) >> (i%8)) & 1
-
-d = -121665 * invert(121666,q)
-I = exponent(2,(q-1)/4,q)
-
-# An element of the main subgroup scalar field
-class Scalar:
-    def __init__(self,x):
-        # Generated from an integer value
-        if isinstance(x,int) or isinstance(x,long):
-            self.x = x % l
-        # Generated from a hex representation
-        elif isinstance(x,str):
-            try:
-                x = binascii.unhexlify(x)
-                self.x = sum(2**i * bit(x,i) for i in range(0,b)) % l
-            except:
-                raise TypeError
-        else:
-            raise TypeError
-
-    # Multiplicative inversion, with an option to let 1/0 = 0 if you're into that
-    def invert(self,allow_zero=False):
-        if self.x == 0:
-            if allow_zero:
-                return Scalar(0)
-            else:
-                raise ZeroDivisionError
-        return Scalar(invert(self.x,l))
-
-    # Addition
-    def __add__(self,y):
-        if isinstance(y,Scalar):
-            return Scalar(self.x + y.x)
-        return NotImplemented
-
-    # Subtraction
-    def __sub__(self,y):
-        if isinstance(y,Scalar):
-            return Scalar(self.x - y.x)
-        return NotImplemented
-
-    # Multiplication (possibly by an integer)
-    def __mul__(self,y):
-        if isinstance(y,int):
-            return Scalar(self.x * y)
-        if isinstance(y,Scalar):
[…]

### 2020-04-07 triptych-multi/test.py

@@ -1,53 +1,0 @@
-import triptych
-import unittest
-import dumb25519
-from dumb25519 import random_scalar, random_point, Scalar
-import random
-
-G = dumb25519.G
-H = dumb25519.hash_to_point('H')
-
-class TestValidProofs(unittest.TestCase):
-    def test_valid_prove_verify(self):
-        print ''
-
-        for m in [1,2]: # ring size 2,4
-            for spends in range(1,min(3,2**m)+1):
-                for outs in [1,2,3]:
-                    print 'Test parameters (m spends outs):',m,spends,outs
-                    l = random.sample(range(2**m),spends) # spend indices
-                    r = [random_scalar() for _ in range(spends)] # signing keys
-                    s = [random_scalar() for _ in range(spends)] # input commitment blinders
-                    a = [random_scalar() for _ in range(spends)] # input commitment amounts
-                    t = [random_scalar() for _ in range(outs)] # output commitment blinders
-                    b = [random_scalar() for _ in range(outs)] # output commitment amounts
-
-                    # Balance amounts
-                    b[0] = Scalar(0)
-                    for i in range(len(a)):
-                        b[0] += a[i]
-                    for i in range(1,len(b)):
-                        b[0] -= b[i]
-
-                    # Data to hide
-                    seed = random_scalar()
-                    aux1 = random_scalar()
-                    aux2 = random_scalar()
-
-                    # Set keys and commitments
-                    M = [random_point() for _ in range(2**m)] # possible signing keys
-                    P = [random_point() for _ in range(2**m)] # corresponding commitments
-                    Q = []
-                    for i in range(outs): # output commitments
-                        Q.append(t[i]*G + b[i]*H)
-                    for i in range(spends): # spend commitments
-                        M[l[i]] = r[i]*G
-                        P[l[i]] = s[i]*G + a[i]*H
-
-                    # Run test
-                    proof = triptych.prove(M,P,Q,l,r,s,t,a,b,m,seed,aux1,aux2)
-                    aux1_,aux2_ = triptych.verify(M,P,Q,proof,m)
-                    self.assertEqual(aux1,aux1_)
-                    self.assertEqual(aux2,aux2_)
-
-unittest.TextTestRunner(verbosity=2,failfast=True).run(unittest.TestLoader().loadTestsFromTestCase(TestValidProofs))

### 2020-04-07 triptych-multi/triptych.py

@@ -1,374 +1,0 @@
-# Proof-of-concept implementation of https://github.com/monero-project/research-lab/issues/56
-
-from dumb25519 import hash_to_point, random_scalar, Scalar, hash_to_scalar, G, random_point, Z
-import dumb25519
-import random
-import transcript
-
-H = hash_to_point('H')
-U = hash_to_point('U')
-
-# Proof structure
-class Proof:
-    def __init__(self):
-        self.J = None # key images
-        self.A = None
-        self.B = None
-        self.C = None
-        self.D = None
-        self.X = None # for signing keys
-        self.Y = None # for key images
-        self.Z = None # for amounts
-        self.f = None
-        self.zA = None
-        self.zC = None
-        self.zR = None # for signing keys and key images
-        self.zS = None # for amounts
-        self.seed = None
-
-    def __repr__(self):
-        temp = '<TriptychProof> '
-        temp += 'J:'+repr(self.J)+'|'
-        temp += 'A:'+repr(self.A)+'|'
-        temp += 'B:'+repr(self.B)+'|'
-        temp += 'C:'+repr(self.C)+'|'
-        temp += 'D:'+repr(self.D)+'|'
-        temp += 'X:'+repr(self.X)+'|'
-        temp += 'Y:'+repr(self.Y)+'|'
-        temp += 'Z:'+repr(self.Z)+'|'
-        temp += 'f:'+repr(self.f)+'|'
-        temp += 'zA:'+repr(self.zA)+'|'
-        temp += 'zC:'+repr(self.zC)+'|'
-        temp += 'zR:'+repr(self.zR)+'|'
-        temp += 'zS:'+repr(self.zS)
-        return temp
-
-# Pedersen tensor commitment
-def com_tensor(v,r):
-    C = dumb25519.Z
-    for i in range(len(v)):
-        for j in range(len(v[0])):
-            for k in range(len(v[0][0])):
-                C += hash_to_point('Gi',i,j,k)*v[i][j][k]
-    C += r*H
-    return C
-
-# Decompose a value with given base and size
-def decompose(val,base,size,t=int):
-    r = []
-    for i in range(size-1,-1,-1):
-        slot = base**i
-        r.append(int(val/slot))
-        val -= slot*r[-1]
-    r = list(reversed(r))
-
-    # Return int list or Scalar list
[…]

### 2020-04-07 paper/iacr.tex
Code and paper

--- 2020-01-24 paper/iacr.tex
@@
 \usepackage{hyperref}
-\usepackage{graphicx}
+\usepackage{graphics,graphicx}
 
-\title{Triptych: logarithmic-sized linkable ring signatures with applications}
-\author{Sarang Noether and Brandon Goodell \\ Monero Research Lab \\ \texttt{\{sarang,surae\}.noether@protonmail.com}}
+\title{Arcturus: efficient proofs for confidential transactions}
+\author{Sarang Noether \\ Monero Research Lab \\ \texttt{sarang.noether@protonmail.com}}
 \date{\today}
@@
 \newcommand{\F}{\mathbb{F}}
+\newcommand{\N}{\mathbb{N}}
+\newcommand{\hs}{\mathsf{H}}
+\newcommand{\hp}{\mathcal{H}}
 \newcommand{\com}{\operatorname{Com}}
-\newcommand{\hs}{\mathcal{H}}
-\newcommand{\hp}{\mathbb{H}}
-
 \newcommand{\A}{\mathcal{A}}
@@
 \newcommand{\sumk}{\sum_{k=0}^{N-1}}
+\newcommand{\sumu}{\sum_{u=0}^{w-1}}
 
@@
 \begin{abstract}
-Ring signatures are a common construction used to provide signer ambiguity among a non-interactive set of public keys specified at the time of signing.
-Unlike early approaches where signature size is linear in the size of the signer anonymity set, current optimal solutions either require centralized trusted setups or produce signatures logarithmic in size.
-However, few also provide linkability, a property used to determine whether the signer of a message has signed any previous message, possibly with restrictions on the anonymity set choice.
-Here we introduce Triptych, a family of linkable ring signatures without trusted setup that is based on generalizations of zero-knowledge proofs of knowledge of commitment openings to zero.
-We demonstrate applications of Triptych in signer-ambiguous transaction protocols by extending the construction to openings of parallel commitments in independent anonymity sets.
-Signatures are logarithmic in the anonymity set size and, while verification complexity is linear, collections of proofs can be efficiently verified in batches.
-We show that for anonymity set sizes practical for use in distributed protocols, Triptych offers competitive performance with a straightforward construction.
+Confidential transactions are used in distributed digital assets to demonstrate the balance of values hidden in commitments, while retaining signer ambiguity.
+Previous work describes a signer-ambiguous proof of knowledge of the opening of commitments to zero at the same index across multiple public commitment sets and the evaluation of a verifiable random function used as a linking tag, and uses this to build a linkable ring signature called Triptych that can be used as a building block for a confidential transaction model.
+In this work, we extend Triptych to build Arcturus, a proving system that proves knowledge of openings of multiple commitments to zero within a single set, correct construction of a verifiable random function evaluated at each opening, and value balance across a separate list of commitments within a single proof.
+While soundness depends on a novel dual discrete-logarithm hardness assumption, we use data from the Monero blockchain to show that Arcturus can be used in a confidential transaction model to provide faster total batch verification time than other state-of-the-art constructions without a trusted setup.
 \end{abstract}
@@
 \section{Introduction}
-First introduced in \cite{rivest} with respect to RSA groups, ring signatures permit the signing of messages using public key sets not fixed in advance, without the need of a trusted group manager.
-Earlier constructions lacked such flexibility, requiring either centralized key setup or the establishment of fixed signing sets.
-Later work \cite{bender} established more robust security models for unforgeability and anonymity, capturing realistic threat models where an adversary is permitted to corrupt keys, convince honest signers to include malicious anonymity set members, or obtain signatures in advance.
+Distributed digital assets, starting with Bitcoin, rely on digital signatures to authorize transactions and transfer the spend authority of funds.
+While early protocols based on the model established by Bitcoin have the advantage of simplicity, they lack desirable properties relating to privacy and indistinguishability.
+In particular, the address and signature graph formed by the blockchain in such assets is trivially traceable, and the amounts a signature authorizes in a transaction are visible.
 
-Since a ring signature has an anonymity set of public keys, one of which is the true signer, the detection of signing by the same key requires an additional property, linkability.
-A linkable ring signature \cite{lsag} enables verifiers to determine whether the (unknown) signer of a message has signed other messages.
-Such a construction was proposed for election applications, where it is necessary to ensure that votes are anonymous, but voters are permitted to vote only once on a particular issue.
-The construction in \cite{lsag}, with a hash-trapdoor structure similar to that of \cite{schnorr}, is of particular interest due to potential flexibility in linking; while its linking is limited to signer-selected but unchanging signer anonymity sets, it permits linking on a per-issue basis.
-Additional recent work in \cite{backes} introduces the property of linkable anonymity, using sets of signatures and establishing restrictions on key corruption.
-Other related interesting properties like traceability \cite{fs,f} imply stronger capabilities, where an attempt to sign two messages with the same key permits verifiers to identify the signer.
+To protect users of distributed assets and permit better indistinguishability of transactions for fungibility, several methods have been proposed and deployed toward confidential transactions.
+The CryptoNote protocol, an early proposal for obscuring transaction graphs, relies on linkable ring signatures on transaction outputs with denominated amounts \cite{cryptonote}; a transaction includes a separate signature for each such amount, yielding poor scaling.
+A later advancement to the RingCT protocol \cite{ringct} used Pedersen commitments to amounts associated with transaction outputs and extended a ring signature construction by Liu \text{et al.} \cite{liu} to support parallel signatures in a matrix arrangement, removing the need for denominated transaction outputs altogether.
+However, both of these constructions use linkable ring signatures that scale linearly in size with the size of the anonymity set used in each signature.
 
-Linkable ring signatures have seen particular applications in signer-ambiguous transaction protocols.
-In such an application, transactions are authorized by a ring signature whose signing anonymity set consists of previously-generated transaction outputs.
-A signature demonstrates that the signer controls the private key of one such output without revealing which is the signer, and linkability is used to assure verifiers that output has not been used in another signature (signifying a double-spend attempt).
+More recent methods of maintaining transaction privacy use accumulators to represent a given state of transaction outputs.
+Zerocoin \cite{zerocoin} relied on RSA accumulators and associated proofs to assert the validity of transactions, but amounts were fixed, the protocol used very large and inefficient proofs, transactions were limited to a simple burn-mint operation on a transparent chain, and the use of RSA groups required a trusted setup process.
+Later work produced Zerocash \cite{zerocash}, which replaced RSA accumulators and related proofs with succinct proofs relating to Merkle tree accumulators, enabling arbitrary amounts and direct anonymous transfers.
+However, like Zerocoin, Zerocash used a proving system requiring a trusted setup process; this was eventually used as the basis for the Zcash protocols.
 
-A practical consideration for the use of linkable ring signatures in transaction protocols is how signature size and verification time scale with the size of the anonymity set.
-In common applied constructions like \cite{mlsag,clsag}, signature size and verification time scale linearly with the size of the signing ambiguity set; since such signatures are typically included in a public distributed data structure like a blockchain, there is a balance between the size of the anonymity set and the requirements for storage and verification.
-Recent protocol work in this area mitigates the size restriction.
-For example, in \cite{rct3}, the authors introduce a confidential transaction protocol based on a proving system whose size scales logarithmically with the anonymity set size, and which includes a method for demonstrating amount balance; amount commitment range proving is offloaded to other constructions like \cite{bulletproofs}.
-In \cite{omniring}, the authors use a more general proving technique to accomplish a similar goal; however, the protocol offers further size benefits by integrating commitment range proofs into the proof structure directly, taking advantage of the logarithmic proof size.
+Until recently, transaction protocols desiring robust signer ambiguity and flexible direct anonymous transfers of arbitrary amounts faced a tradeoff between a trust-free construction and efficiency in proof sizes and verification complexity.
+Recent work in this area generally relies on one of two novel proving systems to build transactions that scale in size logarithmically with the size of the prover-specified anonymity set, while requiring no trusted setup.
+A one-of-many commitment-to-zero proving system of Groth and Kohlweiss \cite{groth} was used to build simple ring signatures and Zerocoin-style transactions, and was later extended to support accountable ring signatures more efficiently by Bootle \cite{bootle}.
+This proving system forms the basis of Lelantus \cite{lelantus}, which extends the Zerocoin-style transaction model of \cite{groth} by using multiple-base Pedersen commitments to incorporate amounts alongside serial numbers; a modification to the proofs shows balance, and multiple proofs are needed for typical transactions.
+However, Lelantus transactions allow a transaction sender to later identify when the recipient spends their funds; a mitigation to this solves the tracing problem, but at the cost of eliminating a useful one-time addressing construction that ensures recipient anonymity.
+The same proving system in \cite{groth} is used in Triptych \cite{triptych}, a multi-dimensional linkable ring signature construction that can be used to build confidential transactions similarly to \cite{ringct}; Triptych notably supports one-time addressing and arbitrary amounts, while still requiring the use of multiple proofs for transactions spending multiple transaction outputs.
+Interestingly, recent independent work extends \cite{groth} to support proofs on multiple commitments in a single list (as we also introduce below), with a particular application to Zether \cite{zether}; however, this uses a different approach than we take here, and seems to result in larger proofs.
 
-Other signer-ambiguous transaction protocols not based on linkable ring signatures offer more competitive performance.
-For example, protocols like \cite{zcash} produce maximal theoretical signer ambiguity through the use of zero-knowledge Merkle proofs (among others) that offer extremely small proofs with low verification time, but at the cost of a trusted structured setup process that arises from the underlying proving system \cite{groth16}.
-Like this work, \cite{lelantus} is a transaction protocol also based on \cite{groth}; however, it is intended to operate on commitments similar to those used in \cite{zerocoin} but with the inclusion of amounts, and has limitations on addressing and sender tracing.
+The Bulletproofs \cite{bulletproofs} proving system uses an inner-product compression method to build range and circuit satisfiability proofs with logarithmic size scaling.
+Besides an increasingly widespread deployment for commitment range proofs, the underlying structure of Bulletproofs is used to construct more specialized proving systems for confidential transactions.
+Omniring \cite{omniring} uses this method to build transactions that demonstrate spend authorization for multiple signer-ambiguous transaction inputs within a single proof, while directly integrating range proving.
+The result is very small proofs; however, verification is slower than other approaches, and requirements for unique group generators mean such proofs cannot be verified in efficient batches.
+RingCT 3.0 \cite{rct3} also uses a Bulletproof-style construction.
+In an early version, transactions required separate proofs for multiple inputs; while an update incorporates a single proof for all inputs to a transaction, it also requires that the number of inputs be padded to a power of two, which can yield poor verification complexity.
 
 \subsection{Our contribution}
-We produce a family of linkable ring signatures, which we call Triptych.
-The constructions are a linkable generalization of Groth's one-of-many commitment-to-zero proving system \cite{groth}, with optimizations from Bootle \cite{bootle} applied for improvements to proof size and verification complexity.
-In the simplest version of Triptych, the prover shows that it knows the opening of a commitment to zero within a commitment set, and also that it has constructed a linking tag using the same opening, producing a linkable ring signature construction.
-We then modify Groth's ring signature definitions to include linkability and a related property, non-frameability.
+We extend the proving system in Triptych \cite{triptych} in two significant ways, which we call Arcturus.
+First, we enable the prover to show knowledge of multiple signing keys in a single proof simultaneously using one set of combined proof elements; unlike \cite{rct3}, our modification admits any number of transaction inputs without limitations.
+We retain the verifiable random function evaluation that produces linking tags, which are required for the detection of repeat signing with the same commitment opening across proofs.
+Second, we show Pedersen commitment value balance directly within the same proof; in particular, we show that a particular combination of input and output commitments sums to a commitment to zero.
+We note that the soundness of the resulting proving system depends on a novel dual discrete-logarithm hardness assumption that we are not able to reduce to a standard hardness assumption; while we consider this novel assumption reasonable, it is untested.
 
-In an extension of Triptych, we include multiple independent sets of commitments.
-Here, the prover proceeds as before to show its knowledge of an opening to a commitment in one set, as well as the construction of the linking tag.
-However, the proof also shows that the prover knows an opening of a commitment at the same position in all other sets.
-This construction has immediate application; in some signer-ambiguous confidential transaction protocols, transaction inputs are commitments to zero, for which the signer shows it knows the opening.
-Each commitment comes equipped with another commitment to the amount of the input; by offsetting these commitments homomorphically and carefully choosing commitment randomness, the prover can show that a particular transaction balances.
-
-We show that Triptych produces signatures with competitive performance to other modern linkable ring signatures for limited anonymity set sizes.
-We note that similar constructions also require linear verification time, meaning that the size of anonymity set used in practice is likely to be limited for performance reasons.
+Taken together, these changes have application to a transaction protocol for efficient use in blockchain confidential transactions that does not require any trusted setup process.
+A transaction can sign for multiple signer-ambiguous inputs and prove that the transaction balances using a single proof, a major improvement to currently-deployed constructions that require multiple proofs and separate auxiliary Pedersen amount commitments.
+Further, we use actual blockchain data from the Monero digital asset project to directly compare the overall size and verification time of Arcturus to that of Triptych and two separate RingCT 3.0 constructions.
+We find that Arcturus provides superior verification performance compared to other trust-free confidential transaction constructions, with competitive size scaling.
 
@@
 \subsection{Public parameters}
-Let $\G$ be a cyclic group in which the discrete logarithm problem is hard, and let $\F$ be the scalar field of $\G$.
-Let $\hs: \{0,1\}^* \to \F$ be a cryptographic hash function.
-Let $G$ and $H$ be generators of $\G$ with unknown discrete logarithm relationship.
-Let $N = n^m$ be a size parameter, where $n > 1$ and $m > 1$.
-Let $\{G_{j,i}\}_{j,i=0}^{m-1,n-1}$ be a set of generators of $\G$ with unknown discrete logarithm relationship to each other, to $G$, and to $H$.
-Let $U$ be a generator of $\G$.
-Note that all generators may be produced using public randomness; for example, the use of a suitable hash function with domain separation may be appropriate.
-All such public parameters are assumed to comprise a global reference string known to all players; in particular, we exclude them from algorithm definitions and Fiat-Shamir transcript hashes for readability.
+Let $\G$ be a cyclic group in which the discrete logarithm problem is hard, and let $\F$ be its scalar field.
+Let $\hs: \{0,1\}^* \to \F$ and $\hp: \{0,1\}^* \to \G$ be cryptographic hash functions.
+Let $N = n^m$ be a positive integer, where $m > 1$ (for our construction, we will use $n = 2$).
+Assume that $G$, $H$, $U$, and any point of the form $G_i$ or $H_i$ (possibly with multiple indices) are uniformly random generators of $\G$ whose discrete logarithm relationship to each other is unknown.
+Note that all such generators may be produced using public randomness; for example, the use of a suitable hash function with domain separation may be appropriate.
+All such public parameters are assumed to comprise a global reference string known to all players; in particular, we generally exclude explicit reference to public parameters from algorithm definitions and Fiat-Shamir transcript hashes for readability.
 
-\subsection{Pedersen commitment}
-Let $\com$ be a homomorphic commitment scheme that is perfectly hiding and computationally binding.
-In this work, we assume use of the Pedersen commitment scheme: for $x,r \in \F$, define $\com(x,r) \equiv xG + rH$ to be the commitment of the value $x$ with randomness $r$.
-This can be trivially extended to support matrix values; for $\{x_{j,i}\},r \in \F$, define $\com(x,r) \equiv rH + \sum_{j,i} x_{j,i}G_{j,i}$.
-Note in particular that Pedersen matrix commitments are similarly homomorphic.
+\subsection{Tensor commitment}
+Let $\com$ be an additively homomorphic commitment scheme that is perfectly hiding and (at least) computationally binding.
+In this work, we assume use of a simple extension to the Pedersen commitment scheme: for $x,r \in \F$, define $\com(x,r) \equiv rG + xH$ to be the commitment of the value $x$ with randomness $r$.
+
+For a three-dimensional tensor $f \equiv (f_{i,j,k}) \subset \F$ and blinding factor $r \in \F$, define the Pedersen tensor commitment
+$$\com(f,r) \equiv rG + \sum_{i,j,k} f_{i,j,k} G_{i,j,k}$$
+using fixed independent generators as described above.
+
+Operations on tensors are assumed to be performed componentwise; for example, if $f \equiv (f_{i,j,k})$ and $g \equiv (g_{i,j,k})$ are such tensors over $\F$, then $f + g \equiv (f_{i,j,k} + g_{i,j,k})$, and so forth.
 
@@
 We sometimes use index subscript notation of the form $i_j$ to indicate the $j$ digit of $i$, where such a decomposition of $i$ is taken base $n$ with padded length $m$:
-$$\sum_{j=0}^m i_j n^j = i$$
+$$\sum_{j=0}^{m-1} i_j n^j = i$$
 This notation will be specified explicitly where confusion may occur.
 
-\section{Protocol: linkable one-of-many commitment}
-We wish to build a linkable ring signature construction, where a signer who knows the opening of a commitment may sign messages using an anonymity set containing other commitments for which the signer does not know openings.
-Included with the proof of knowledge, the signer also provides a linking tag that is the image of the signing commitment's opening under a verifiable pseudorandom function, using the method of \cite{dodis} that has previously appeared in \cite{omniring,rct3}.
-Part of the soundness of the proving system relies on the proper construction of this linking tag.
-Upon receipt, a verifier can check whether the linking tag has previously appeared in any other valid proof; if it has not, injectivity assures the verifier that no other signature has been produced by the (unknown) signer.
+\subsection{Sigma protocols}
+For a given relation $\mathcal{R}$, a sigma protocol for $\mathcal{R}$ is an interactive challenge-response protocol between a prover and verifier, where the prover wishes to convince the verifier it knows a witness corresponding to a statement in $\mathcal{R}$.
 
-More specifically, we modify the construction of Bootle \cite{bootle}, which itself is a generalization of a construction by Groth \cite{groth}.
-We produce a sigma protocol for the following relation:
-$$\mathcal{R}_{\text{link}} = \left\{ \{M_i\}_{i=0}^{N-1} \subset \G, J \in \G ; (l \in \mathbb{Z},r \in \F) : M_l = rG \text{ and } U = rJ \right\}$$
-Figures \ref{fig:link} and \ref{fig:link_2} describe the protocol.
+A sigma protocol is complete, sound, and zero-knowledge.
+These definitions are well known and found, for example, in \cite{groth}.
+Essentially, these properties are:
+\begin{itemize}
+\item \textit{Perfectly complete}: For a witness to a statement in $\mathcal{R}$, an honest prover always convinces an honest verifier of the validity.
+\item \textit{Special sound}: Given a statement in $\mathcal{R}$, if the prover can produce valid proof transcripts in response to multiple verifier challenges, then it is possible to extract a witness for the statement from the transcripts.
+\item \textit{Special honest-verifier zero knowledge}: Given a statement and known verifier challenge, it is possible to produce a simulated transcript without knowledge of a corresponding valid witness.
+\end{itemize}
+Sigma protocols can be made non-interactive by replacing random verifier challenges with hash-based transcript challenges under the random oracle model; this approach is called the Fiat-Shamir heuristic \cite{fiat}.
+
+\subsection{Hardness assumption}
+We now define a novel cryptographic hardness assumption that is used later to show the soundness of our construction.
+
+\begin{definition}[Dual-target discrete logarithm problem]
+\label{def:dual}
+Let $\G$ be a group in which the discrete logarithm problem is hard, and let $\F$ be its scalar field.
+Let $n > 0$.
+Consider the following game between a challenger and a probabilistic polynomial-time player $\A$:
+\begin{itemize}
+\item The challenger chooses $G,H \in \G$ uniformly at random and sends both to $\A$.
+\item $\A$ chooses and returns sets $\{G_i\}_{i=0}^{n-1},\{H_i\}_{i=0}^{n-1} \subset \G$ to the challenger.
+\item The challenger chooses a set $\{\mu_i\}_{i=0}^{n-1} \subset \F$ uniformly at random and sends it to $\A$.
+\item $\A$ chooses and returns a set $\{x_i\}_{i=0}^{n-1} \subset \F$ to the challenger.
+\end{itemize}
+We say that $\A$ wins the $(n,\epsilon,t)$-dual-target discrete logarithm game if, in time less than $t$ and with probability at least $\epsilon$, the following are true:
+\begin{itemize}
+\item $\sumi \mu_i \left( G_i - x_iG \right) = 0$
+\item $\sumi \mu_i \left( H - x_iH_i \right) = 0$
+\item There exists an index $0 \leq i < n$ such that either $x_iG \neq G_i$ or $x_iH_i \neq H$.
+\end{itemize}
+\end{definition}
+
+\section{Proving system}
+We now present a sigma protocol for the following relation:
+\begin{multline*}
+\mathcal{R} \equiv \Bigg\{ \{M_i\}_{i=0}^{N-1},\{P_i\}_{i=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \\
+M_{l^{(u)}} = r^{(u)}G \; \forall \: u \in [0,w) \text{ and } r^{(u)}J^{(u)} = U \; \forall \: u \in [0,w) \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \Bigg\}
+\end{multline*}
+This captures the necessary elements for transaction authorization, which we describe later; knowledge of signing keys $\{r^{(u)}\}$ will show that the prover has signing authority for inputs to a transaction, and knowledge of the secret key $y$ to an amount commitment difference will show that the transaction amounts balance.
+Finally, comparison of the verifiable random function used to produce $\{J^{(u)}\}$ will be used to prevent attempts to sign for the same secret key without revealing the corresponding public key, which is important for signer ambiguity and double-spend protection within or between proofs.
+
+Figures \ref{fig:sigma} and \ref{fig:sigma2} describe the prover and verifier interaction.
+Next, we prove that the prover and verifer routines constitute a sigma protocol that is perfectly correct, special sound, and special honest-verifier zero knowledge.
 
@@
 \fbox{\begin{minipage}{0.95\textwidth}
-$\underline{\mathcal{P}_{\text{link}}(\{M_i\},J;(l,r)):}$
+$\underline{\mathcal{P}:}$
 \begin{itemize}
-\item Select random $r_A \in \F$ and $\left\{a_{j,i}\right\}_{i=1,j=0}^{n-1,m-1} \subset \F$.
-Define $A \equiv \com(a,r_A)$.
-\item Define $\left\{\sigma_{j,i}\right\}_{i,j=0}^{n-1,j-1} \subset \F$ such that $\sigma_{j,i} \equiv \delta\left(l_j,i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
+\item Select random $r_A \in \F$ and $\left\{a_{j,i}^{(u)}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1} \subset \F$.
+Set $$\{a_{j,0}^{(u)}\}_{j,u=0}^{m-1,w-1} \equiv -\sum_{i=1}^{n-1} a_{j,0}^{(u)}$$ and define $A \equiv \com(a,r_A)$.
+\item Define $\left\{\sigma_{j,i}^{(u)}\right\}_{i,j,u=0}^{n-1,m-1,w-1} \subset \F$ such that $\sigma_{j,i}^{(u)} \equiv \delta\left(l_j^{(u)},i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
 Define $B \equiv \com(\sigma,r_B)$.
@@
 \item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
-\item Define coefficients $\left\{p_{k,j}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p_k(x) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}x + a_{j,k} \right) = \delta\left(l,k\right)x^m + \sumj p_{k,j}x^j$$ for all $k \in [0,N)$ (using our decomposition notation).
-\item Select random $\left\{\rho_j\right\}_{j=0}^{m-1} \subset \F$.
-\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}M_k + \rho_jG$$
-\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv U \sumk p_{k,j}+ \rho_jJ$$
+\item For $0 \leq u < w$, define coefficients $\left\{p_{k,j}^{(u)}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p_k^{(u)}(x) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}^{(u)}x + a_{j,k}^{(u)} \right) = \delta\left(l^{(u)},k\right)x^m + \sumj p_{k,j}^{(u)}x^j$$ (using our decomposition notation).
+Then define $p_{k,j} \equiv \sumu p_{k,j}^{(u)}$ and $p_k(x) \equiv \sumu p_k^{(u)}(x)$ accordingly.
+\item Select random $\left\{\rho_j\right\}_{j,u=0}^{m-1,w-1}, \left\{\overline{\rho}_j^{(u)}\right\}_{j,u=0}^{m-1,w-1} \subset \F$.
+\item Define aggregation coefficients $\{\mu_k\}_{k=0}^{N-1}$ using a $k$-indexed $\hs$ operation, containing all Fiat-Shamir transcript public parameters and proof elements.
+\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}\mu_kM_k + \sumu \rho_j^{(u)}G$$
+\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv U \sumk p_{k,j}\mu_k + \sumu \rho_j^{(u)}J^{(u)}$$
+\item Define $\{Z_j\}_{j=0}^{m-1} \subset \G$ such that: $$Z_j \equiv \sumk p_{k,j}P_k + \sumu \overline{\rho}_j^{(u)}G$$
 \end{itemize}
@@
 $\underline{\mathcal{P} \to \mathcal{V}:}$ \\
-$A,B,C,D,\{X_j\},\{Y_j\}$ \\
+$A,B,C,D,\{X_j\},\{Y_j\},\{Z_j\}$
+\end{minipage}}
+\caption{Sigma protocol for $\mathcal{R}$}
+\label{fig:sigma}
+\end{figure}
 
+\begin{figure}[htbp]
+\centering
+\fbox{\begin{minipage}{0.95\textwidth}
 $\underline{\mathcal{V} \to \mathcal{P}:}$ \\
@@
 \begin{itemize}
-\item Define $\left\{f_{j,i}\right\}_{i=1,j}^{n-1,m-1}$ such that $f_{j,i} \equiv \sigma_{j,i}\xi + a_{j,i}$.
+\item Define $\left\{f_{j,i}^{(u)}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1}$ such that $f_{j,i}^{(u)} \equiv \sigma_{j,i}^{(u)}\xi + a_{j,i}^{(u)}$.
 \item Define $z_A \equiv r_A + \xi r_B$ and $z_C \equiv \xi r_C + r_D$.
-\item Define $z \equiv r \xi^m - \sumj \rho_j \xi^j$.
+\item Define $\left\{z_R^{(u)}\right\}_{u=0}^{w-1} \subset \F$ such that: $$z_R^{(u)} \equiv \mu_{l^{(u)}}r^{(u)}\xi^m - \sumj \rho_j^{(u)}\xi^j$$
+\item Define: $$z_S \equiv \xi^m \left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right) - \sumj \left( \xi^j \sumu \overline{\rho}_j^{(u)} \right)$$
 \end{itemize}
@@
 $\underline{\mathcal{P} \to \mathcal{V}:}$ \\
-$\{f_{j,i}\}_{j=0,i=1}^{m-1,n-1},z_A,z_C,z$
-\end{minipage}}
-\caption{Sigma protocol for $\mathcal{R}_{\text{link}}$}
-\label{fig:link}
-\end{figure}
+$\{f_{j,i}^{(u)}\}_{j=0,i=1,u=0}^{m-1,n-1,w-1},z_A,z_C,\{z_R^{(u)}\},z_S$ \\
 
-\begin{figure}[htbp]
-\centering
-\fbox{\begin{minipage}{0.95\textwidth}
-$\underline{\mathcal{V}_{\text{link}}(\{M_i\},J):}$
+$\underline{\mathcal{V}:}$
 \begin{itemize}
-\item For $0 \leq j < m$, let $f_{j,0} \equiv \xi - \sum_{i=1}^{n-1} f_{j,i}$.
+\item For $0 \leq u < w$ and $0 \leq j < m$, set: $$f_{j,0}^{(u)} \equiv \xi - \sum_{i=1}^{n-1} f_{j,i}^{(u)}$$
 \item Accept if and only if:
@@
 \xi C + D &=& \com(f(\xi-f),z_C) \label{eqn:cd} \\
-\sumk M_k \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG &=& 0 \label{eqn:x} \\
-U \sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ &=& 0 \label{eqn:y}
+\sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f_{j,k_j}^{(u)} \right) \right] - \sumj \xi^jX_j - \sumu z_R^{(u)}G &=& 0 \label{eqn:x} \\
+U \sumk \mu_k \left[ \sumu \left( \prod_{j=0}^{m-1} f_{j,k_j}^{(u)} \right) \right] - \sumj \xi^jY_j - \sumu z_R^{(u)}J^{(u)} &=& 0 \label{eqn:y} \\
+\sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f_{j,k_j}^{(u)} \right) \right] - \sumj \xi^jZ_j - \xi^m\sum_{j=0}^{T-1} Q_j - z_SG &=& 0 \label{eqn:z}
 \end{eqnarray}
@@
 \end{minipage}}
-\caption{Sigma protocol for $\mathcal{R}_{\text{link}}$ (continued)}
-\label{fig:link_2}
+\caption{Sigma protocol for $\mathcal{R}$ (continued)}
+\label{fig:sigma2}
 \end{figure}
 
-Observe that this protocol can be made non-interactive using the Fiat-Shamir heuristic, where the verifier challenge is produced using a collision-resistant hash function (modeling a random oracle) and the proof transcript \cite{fiatshamir}.
-
-We will show that the sigma protocol is complete, sound, and zero-knowledge, the precise definitions of which are common and found in \cite{groth}.
-Informally, we require the protocol be:
-\begin{itemize}
-\item \textit{Perfectly complete}: Given knowledge of a witness to a statement in the proof relation, an honest prover can always convince an honest verifier of the validity of the witness.
-\item \textit{Special sound}: Given a statement in the proof relation, if a prover can answer multiple verifier challenges correctly, then it is possible to extract a witness for this statement.
-\item \textit{Special honest-verifier zero knowledge}: Given any statement and verifier challenge, it is possible to simulate a transcript that is accepted by an honest verifier without knowledge of a corresponding witness.
-\end{itemize}
-
+\section{Security}
 \begin{theorem}
-The protocol in Figures \ref{fig:link} and \ref{fig:link_2} is perfectly complete, special honest-verifier zero knowledge, and $(m+1)$-special sound.
+The sigma protocol in Figures \ref{fig:sigma} and \ref{fig:sigma2} reflects the relation $\mathcal{R}$ and is perfectly correct, $(m+1)$-special sound, and special honest-verifier zero knowledge.
 \end{theorem}
@@
 \begin{proof}
-The proof follows similarly to that of \cite{bootle}.
+The proof proceeds similarly to that of \cite{triptych}, which in turn follows the methods in \cite{groth,bootle}.
 
-% Completeness
-We first show perfect completeness.
-Suppose the verifier receives a proof generated by an honest prover.
-Equation \ref{eqn:ab} holds using the identity $$\sumi \sigma_{j,i} = 1$$ for all $0 \leq j < m$.
-Equation \ref{eqn:cd} follows similarly, using the identity $$\left(\sigma_{j,i}\right)^2 = \sigma_{j,i}$$ for all $0 \leq j < m$.
-To show Equation \ref{eqn:x} holds:
+To show the protocol is perfectly complete, suppose a verifier receives an honest proof.
+We wish to show that all verifier equations hold.
+Equation \ref{eqn:ab} holds from the identity $$\sumi \sigma_{j,i}^{(u)} = 1$$ for all $0 \leq j < m$ and $0 \leq u > w$.
+Similarly, Equation \ref{eqn:cd} holds from the identity $$(\sigma_{j,i}^{(u)})^2 = \sigma_{j,i}^{(u)}$$ for all $0 \leq i < n$ and $0 \leq j < m$ and $0 \leq u < w$.
+
+Next, we show that Equation \ref{eqn:x} holds:
 \begin{eqnarray*}
-&& \sumk M_k \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG \\
-&=& \sumk M_k p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}M_k + \rho_jG \right) - zG \\
-&=& \sumk M_k \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \rho_jG - zG \\
-&=& \sumk M_k \xi^m \delta(l,k) - \sumj \xi^j \rho_jG - \left( r\xi^m - \sumj \rho_j\xi^j \right)G \\
-&=& \xi^mrG - \sumj \xi^j \rho_jG - \xi^mrG + \sumj \xi^j \rho_jG \\
+&& \sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jX_j - \sumu z^{(u)}_RG \\
+&=& \sumk \mu_kM_k p_k(x) - \sumj x^j \left( \sumk p_{k,j}\mu_kM_k + \sumu \rho^{(u)}_jG \right) - \sumu z^{(u)}_RG \\
+&=& \sumk \mu_kM_k \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jG - \sumu z^{(u)}_RG \\
+&=& \sumk \mu_kM_k \left[ x^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_jG - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right]G \\
+&=& x^m\sumu \mu_{l^{(u)}}r^{(u)}G - \sumj x^j \sumu \rho^{(u)}_jG - x^m\sumu \mu_{l^{(u)}}r^{(u)}G + \sumj x^j \sumu \rho^{(u)}_jG \\
 &=& 0
 \end{eqnarray*}
-Equation \ref{eqn:y} follows similarly:
+
+Equation \ref{eqn:y} holds with similar algebra:
 \begin{eqnarray*}
-&& U \sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ \\
-&=& U \sumk p_k(\xi) - \sumj \xi^j \left( U \sumk p_{k,j} + \rho_jJ \right) - zJ \\
-&=& U \sumk \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \rho_jJ - zJ \\
-&=& U \sumk \xi^m \delta(l,k) - \sumj \xi^j \rho_jJ - \left( r\xi^m - \sumj \rho_j\xi^j \right)J \\
-&=& \xi^mU - \sumj \xi^j \rho_jG - \xi^mrJ + \sumj \xi^j \rho_jG \\
+&& \sumk \mu_kU \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu_kU p_k(x) - \sumj x^j \left( \sumk p_{k,j}\mu_kU + \sumu \rho^{(u)}_jJ^{(u)} \right) - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu_kU \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jJ^{(u)} - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu_kU \left[ x^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right](r^{(u)})^{-1}U \\
+&=& x^m\sumu \mu_{l^{(u)}}U - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - x^m\sumu \mu_{l^{(u)}}U + \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U \\
 &=& 0
 \end{eqnarray*}
-since $J = r^{-1}U$ in a valid proof.
-Hence the protocol is perfectly complete.
 
-% SHVZK
-We next show that the protocol is special honest-verifier zero knowledge.
-To do so, we construct a simulator that, given a random verifier challenge $\xi$, can construct a proof transcript with identical distribution to a valid proof.
+Finally, we show that Equation \ref{eqn:z} holds:
+\begin{eqnarray*}
+&& \sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jZ_j - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
+&=& \sumk P_k p_k(x) - \sumj x^j \left( \sumk p_{k,j}P_k + \sumu \overline{\rho}^{(u)}_jG \right) - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
+&=& \sumk P_k \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \overline{\rho}^{(u)}_jG - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
+&=& x^m\sumu (s^{(u)}G + a_uH) - \sumj x^j \sumu \overline{\rho}^{(u)}_jG - x^m\sum_{j=0}^{T-1} (t_jG + b_jH) - x^m\left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right)G + \\
+&& \sumj x^j \sumu \overline{\rho}^{(u)}_jG \\
+&=& \left( \sumu a_u - \sum_{j=0}^{T-1} b_j \right)H \\
+&=& 0
+\end{eqnarray*}
+Hence, the protocol is perfectly complete.
 
-First, observe that the simulator presented in the proof of Lemma 1 in \cite{bootle} translates identically to our setting.
-If the simulator chooses $B \in \G$ uniformly at random, the cited lemma assures us a valid simulation of the proof elements $A,C,D,z_A,z_C,\{f^{(u)}_{j,i \neq 0}\}$; we may compute each $f^{(u)}_{j,0}$ from this.
-Further, in a valid proof, $B$ is independent and uniformly distributed as well.
+Next, we show that the sigma protocol is special honest-verifier zero knowledge.
+To do so, we construct a simulator that, when given a random verifier challenge $\xi$, can construct a proof transcript with identical distribution to a valid proof.
 
-The proof elements $\{X_j\}_{j=1}^{m-1}$ and $\{Y_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof since the set $\{\rho_j\}$ is random and the discrete logarithm problem in $\G$ is hard, so the simulator may choose these uniformly at random.
-The verification checks require that $X_0$ and $Y_0$ be uniquely determined by the other elements in the corresponding sets in both real proofs and by the simulator.
+Observe first that the simulator presented in the proof of Lemma 1 in \cite{bootle} translates nearly identically to our setting, since we can flatten tensor commitments to a matrix structure with the required sum property.
+The simulator first chooses $B \in \G$ uniformly at random; then, the cited lemma assures a valid simulation of the proof elements  $A,C,D,z_A,z_C,\{f^{(u)}_{j,i \neq 0}\}$, and from this we may compute $\{f^{(u)}_{j,0}\}$.
+In a valid proof, $B$ is also uniformly distributed.
 
-Finally, $z$ is uniformly distributed in valid proofs given random $\xi$, so the simulator may choose it uniformly at random.
-Hence the construction is special honest verifier zero-knowledge.
+The proof elements $\{X_j\}_{j=1}^{m-1},\{Y_j\}_{j=1}^{m-1}, \{Z_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof since the elements of $\{\rho_j\},\{\overline{\rho}_j\}$ are uniformly distributed and the discrete logarithm problem in $\G$ is hard; hence, the simulator chooses them uniformly at random.
+Since the verification checks require that $X_0,Y_0,Z_0$ be uniquely determined by the other elements in the respective sets, they are selected by the simulator in this manner.
 
-% Soundness
-It remains to show that the protocol is $(m+1)$-special sound, where $m > 1$.
-To show this, we construct an extractor that, given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness.
+Finally, the elements $\{z^{(u)}_R\}_{u=0}^{w-1}$ and $z_S$ are independent and uniformly distributed in valid proofs given a random verifier challenge $\xi$, so the simulator may choose them uniformly at random.
+Hence the protocol is special honest verifier zero-knowledge.
 
-Suppose that for a given statement, we have a set of $m+1$ distinct verifier challenges $\{\xi_e\}_{e=0}^m$ corresponding to unique valid responses of this form:
-$$\left\{ \{f^{(e)}_{j,i}\}, \{z_e\} \right\}_{e=0}^m$$
-From the $3$-special soundness in \cite{bootle} and $m > 1$ we have valid extractions $\{\sigma_{j,i}\}_{j,i=0}^{m-1,n-1}$ and $\{a_{j,i}\}_{j,i=0}^{m-1,n-1}$, and the Pedersen binding property ensures that (with high probability) we have:
-$$f^{(e)}_{j,i} = \sigma_{j,i}\xi_e + a_{j,i}$$
-for all $e \in [0,m]$.
-Using the extracted values, compute
-$$p_k(\xi) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}\xi + a_{j,k} \right)$$
+We claim that the protocol is $(m+1)$-special sound, where $m > 1$.
+To show this, we construct an extractor that, when given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness for the statement.
+In particular, we produce a modified witness for the following relation that is based on the information presented in the prover algorithm, where we define aggregation coefficients $\mu_k$ as before:
+\begin{multline*}
+\mathcal{R}' \equiv \Bigg\{ \{M_k\}_{k=0}^{N-1},\{P_k\}_{k=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \\
+\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sumu \mu_{l^{(u)}} r^{(u)}G \text{ and } \sumu \mu_{l^{(u)}} r^{(u)}J^{(u)} = \sumu \mu_{l^{(u)}} U \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \Bigg\}
+\end{multline*}
+Observe that if we assume that the dual-target discrete logarithm problem is hard in $\G$, extraction of a witness for $\mathcal{R}'$ implies knowledge of a corresponding witness for $\mathcal{R}$; this in turn provides the desired soundness.
+
+Suppose that for a given statement, we have a set of $(m+1)$ distinct verifier challenges $\{\xi_e\}_{e=0}^m$ corresponding to distinct valid responses of this form:
+$$\left\{ \{{}_ef^{(u)}_{j,i}\}, \{{}_ez^{(u)}_R\}, {}_ez_S \right\}_{e=0}^m$$
+From the $3$-special soundness in \cite{bootle} and $m > 1$ we have valid extractions $\{\sigma^{(u)}_{j,i}\}_{u=0}^{w-1}$ and $\{a^{(u)}_{j,i}\}_{u=0}^{w-1}$, and the Pedersen binding property ensures that (with high probability) we have:
+$${}_ef^{(u)}_{j,i} = \sigma^{(u)}_{j,i}\xi_e + a^{(u)}_{j,i} \; \forall \: e \in [0,m]$$
+Using the extracted values, compute the polynomial
+$$p_k(x) \equiv \sum_{u=0}^{w-1}\left[ \prod_{j=0}^{m-1} \left( \sigma^{(u)}_{j,k}x + a^{(u)}_{j,k} \right) \right]$$
 for all $k \in [0,N)$.
-Extraction of $\{\sigma_{j,i}\}_{j,i=0}^{m-1,n-1}$ immediately yields the signing index $l$.
+Extraction of $\{\sigma^{(u)}_{j,i}\}_{u=0}^{w-1}$ immediately yields the signing index set $\{l^{(u)}\}_{u=0}^{w-1}$.
 
-We have seen that $p_k$ is of degree $m$ only when $k = l$.
-Hence there exist coefficients $\{\overline{X}_j,\overline{Y}_j\}_{j=0}^{m-1}$, computed uniquely from the statement and extracted values, such that Equations \ref{eqn:x} and \ref{eqn:y} are of the following form:
+We have seen that $p_k$ is of degree $m$ only when $k \in \{l^{(u)}\}_{u=0}^{w-1}$.
+Hence there exist sets of coefficients $\{\overline{X}_j,\overline{Y}_j,\overline{Z}_j\}_{j=0}^{m-1}$, computed uniquely from the statement and extracted values, such that Equations \ref{eqn:x}, \ref{eqn:y}, and \ref{eqn:z} are of the following form:
 \begin{eqnarray*}
-\xi^m M_l + \sumj \xi^j\overline{X}_j &=& zG \\
-\xi^m U + \sumj \xi^j\overline{Y}_j &=& zJ \\
+\xi^m \sumu \mu_{l^{(u)}}M_{l^{(u)}} + \sumj \xi^j\overline{X}_j &=& \left( \sumu z^{(u)}_R \right)G \\
+\xi^m \sumu \mu_{l^{(u)}}U + \sumj \xi^j\overline{Y}_j &=& \sumu z^{(u)}_RJ^{(u)} \\
+\xi^m \sumu P_{l^{(u)}} + \sumj \xi^j\overline{Z}_j - \xi^m \sum_{j=0}^{T-1} Q_j &=& z_SG
 \end{eqnarray*}
@@
 
-For each of the previous two equations, we can therefore build a linear combination over $e$.
-For the first:
-$$M_l = \sum_{e=0}^m \theta_e\xi_e^m M_l + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{X}_j \right) = \left( \sum_{e=0}^m \theta_e z_e \right) G$$
-Hence we extract $r \equiv \sum_{e=0}^m \theta_e z_e$.
-For the second:
-$$U = \sum_{e=0}^m \theta_e\xi_e^m U + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{X}_j \right) = \left( \sum_{e=0}^m \theta_e z_e \right) J$$
-This implies that $rJ = U$, as required.
-Hence the protocol is $(m+1)$-special sound, which completes the proof.
+For each of the previous three equations, we can therefore build a linear combination over $e$. For the first:
+$$\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sum_{e=0}^m \theta_e\xi_e^m \left( \sumu \mu_{l^{(u)}} M_{l^{(u)}} \right) + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{X}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) G$$
+We therefore can define extractions for each $r^{(u)}$:
+$$r^{(u)} \equiv \frac{1}{\mu_{l^{(u)}}} \sum_{e=0}^m \theta_e {}_ez^{(u)}_R$$
+Observe that the same witnesses appear in the second:
+$$\sumu \mu_{l^{(u)}} U = \sum_{e=0}^m \theta_e\xi_e^m \left( \sumu \mu_{l^{(u)}} U \right) + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{Y}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) J^{(u)}$$
+This means the requirements on each $r^{(u)}$ are satisfied. The third equation proceeds similarly.
+$$\sumu P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = \sum_{e=0}^m \theta_e\xi_e^m \left( \sumu P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j \right) + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{Z}_j \right) = \left( \sum_{e=0}^m \theta_e {}_ez_S  \right)G$$
+Hence we have $y \equiv \sum_{e=0}^m \theta_e {}_ez_S$.
 \end{proof}
 
-\section{Security: linkable ring signature}
-Informally, a linkable ring signature is a construction permitting signatures on messages using a signer-selected anonymity set (called a \textit{ring}) of possible signers.
-A valid signature convinces a verifier that the signer knows (at least) one of the private keys to a ring member.
-The construction is linkable if it is possible to determine whether two signatures were generated using the same private key, regardless of the ring members used.
+\section{Transaction model}
+We now describe how to apply the sigma protocol for $\mathcal{R}$ in a confidential transaction model.
+In such a model, a transaction consumes so-called \textit{outputs} generated in previous transactions, and produces new outputs for use in later transactions.
+Notably, in a \textit{confidential} transaction model, we wish to introduce ambiguity as to which transaction inputs are being consumed, as well as the corresponding values represented by them.
 
-We use the security definitions in \cite{groth} as a starting point, directly adopting definitions for correctness and unforgeability that also appear in more recent work like \cite{backes}.
-However, we modify the definition of anonymity to account for linking tags, such that the adversary is required to differentiate between at least two possible honest signers that the adversary has not corrupted.
-To account for the linking properties desired in our construction, we use the clever linkability definition from \cite{backes}, which uses a set-theoretic approach.
-We use a straightforward definition for non-frameability, where the adversary produces a target signature on an honest key after receiving signing and corruption oracle access, and must then produce a new signature that links.
+Outputs are constructed as Pedersen commitments to zero, such that an output public key is of the form $M \equiv rG$ with signing key $r$.
+We do not consider here the method by which output keys are generated, but assume this is offloaded to another part of the transaction model.
+Each output comes equipped with a value commitment $P \equiv sG + aH$, where $a$ is the amount and $s$ a blinding factor.
 
-More formally, a \textit{linkable ring signature} (LRS) construction is a set of algorithms \text{KeyGen}, \text{Sign}, \text{Verify}, and \text{Link} satisfying certain properties.
-A set of public parameters is assumed to be available to each algorithm.
-\begin{itemize}
-\item $\text{KeyGen}(r) \to (x,X)$: Generates a secret key $x$ and corresponding public key $X$, optionally using randomness $r$; if not specified, the secret key is sampled uniformly at random.
-\item $\text{Sign}(x,M,R) \to \sigma$: Generates a signature $\sigma$ on a message $M \in \{0,1\}^*$ with respect to the ring $R = \{X_1,\ldots,X_n\}$, provided that $x$ is a secret key corresponding to some $X_i \in R$ generated by $\text{KeyGen}$.
-\item $\text{Verify}(\sigma,M,R) \to \{0,1\}$: Verifies a signature $\sigma$ on a message $M$ with respect to the ring $R$.
-Outputs $0$ is the signature is rejected, and $1$ if accepted.
-\item $\text{Link}(\sigma,\sigma') \to \{0,1\}$: Determines if signatures $\sigma$ and $\sigma'$ were signed using the same private key.
-Outputs $0$ if the signatures were signed using different private keys, and $1$ if they were signed using the same private key.
-\end{itemize}
+A user of the protocol forms an anonymity set $\{M_i\}_{i=0}^{N-1}$ of outputs from previous transactions.
+Of these, suppose that the set $\{l^{(u)}\}_{u=0}^{w-1}$ represents the indices of the $w$ outputs for which the user wishes to sign; that is, the user knows $\{r^{(u)}\}_{u=0}^{w-1}$ such that $r^{(u)}G = M_{l^{(u)}}$ for all $0 \leq u < w$.
+To help ensure ambiguity of the signing indices, assume the user has shuffled the anonymity set.
+Each element of the anonymity set has a corresponding value commitment $\{P_i \equiv s_iG + a_iH\}_{i=0}^{N-1}$.
 
-We require that an LRS have the properties of correctness, anonymity, unforgeability, linkability, and non-frameability.
+Further, the user generates a set of new outputs produced by the transaction, with corresponding value commitments of the form $\{Q_j \equiv t_jG + b_jH\}_{j=0}^{T-1}$.
+Because the transaction value must balance, the following must hold: $$\sum_{u=0}^{w-1} a_{l^{(u)}} = \sum_{j=0}^{T-1} b_j$$
+Note that there is no anonymity set for outputs generated by the transaction.
 
-Correctness requires that a signature generated honestly will always verify.
-\begin{definition}[Correctness]
-Consider this game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item The challenger runs $\text{KeyGen} \to (x,X)$ and supplies the keys to $\A$.
-\item The adversary $\A$ chooses a ring such that $X \in R$ and a message $M \in \{0,1\}^*$, and sends them to the challenger.
-\item The challenger signs the message with $\text{Sign}(x,M,R) \to \sigma$.
-\end{itemize}
-If $\text{Pr}[ \text{Verify}(\sigma,M,R) = 1 ] = 1$, we say that the LRS is \textit{perfectly correct}.
-\end{definition}
-Note that we do not require any ring members (except for $X$) to have been generated by $\text{KeyGen}$.
-However, distributed applications may in practice place additional restrictions on public keys used in anonymity sets.
-This allows for the possibility that $\A$ maliciously chooses ring members.
+These terms are used to form a statement using the relation $\mathcal{R}$.
+The user generates a proof showing the validity of this statement with the corresponding secret values as a witness set; the proof demonstrates knowledge of the signing keys $\{r^{(u)}\}_{u=0}^{w-1}$, and the witness $y$ formed by the commitment differences demonstrates that the input and output values balance.
+Provided the commitment scheme used for value representation is (at least computationally) binding, the user cannot produce such a value $y$ unless the values balance correctly; in our case, Pedersen commitments satisfy this requirement.
 
-Unforgeability requires that an adversary who does not control the private key to a ring member cannot generate a valid signature on any message using that ring.
-\begin{definition}[Unforgeability]
-Consider this game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item The adversary $\A$ is granted access to a public-key oracle $\text{GenOracle}$ that (on the $i^\text{th}$ invocation) runs $\text{KeyGen} \to (x_i,X_i)$ and returns $X_i$ to $\A$.
-\item The adversary $\A$ is granted access to a corruption oracle $\text{CorruptOracle}(i)$ that returns $x_i$ if it corresponds to a query to $\text{GenOracle}$.
-\item The adversary $\A$ is granted access to a signing oracle $\text{SignOracle}(X,M,R)$ that runs $\text{Sign}(x,M,R) \to \sigma$ and returns $\sigma$ to $\A$, provided that $X$ corresponds to a query to $\text{GenOracle}$ and $X \in R$.
-\item Then, $\A$ outputs $(\sigma,M,R)$ such that $\text{SignOracle}$ was not queried with $(-,M,R)$, all keys in $R$ were generated by queries to $\text{GenOracle}$, and no key in $R$ was corrupted by $\text{CorruptOracle}$.
-\end{itemize}
-If $\text{Pr}[ \text{Verify}(\sigma,M,R) = 1 ] \approx 0$, we say that the LRS is $\textit{unforgeable with respect to insider corruption}$.
-\end{definition}
+We call the elements of the set $\{J^{(u)}\}_{u=0}^{w-1}$ the \textit{linking tags} for the transaction.
+Similar to their use in linkable ring signatures, they are used by the verifier to detect attempts to sign with a secret key multiple times, either within the same transaction or between multiple transactions.
+The construction $J^{(u)} = (r^{(u)})^{-1}U$ is an injective one-way verifiable random function \cite{dodis} using the secret key $r^{(u)}$; if the verifier sees the same linking tag used elsewhere, it knows that the (unknown) secret key was used again.
+In our confidential transaction model, this corresponds to an attempt to double-spend funds that would be rejected by the verifier.
 
-Anonymity requires that as long as a ring contains at least two members that have not been corrupted, an adversary can do no better than guessing at determining the signer of an honest signature.
-\begin{definition}[Anonymity]
-Consider this game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item The adversary $\A$ is granted access to the public-key oracle $\text{GenOracle}$ and the corruption oracle $\text{CorruptOracle}$.
-\item The adversary $\A$ chooses a message $M \in \{0,1\}^*$, a ring $R$, and indices $i_0$ and $i_1$, and sends them to the challenger.
-We require that $X_{i_0},X_{i_1} \in R$ such that both keys were generated by queries to $\text{GenOracle}$, and neither key was queried to $\text{CorruptOracle}$.
-\item The challenger selects a uniformly random bit $b \in \{0,1\}$, generates the signature $\text{Sign}(x_{i_b},M,R) \to \sigma$, and sends it to $\A$.
-\item The adversary $\A$ chooses a bit $b' \in \{0,1\}$.
-\end{itemize}
-If $\text{Pr}[ b' = b ] \approx 1/2$ and $\A$ did not make any corruption queries after receiving the challenge bit, we say that the LRS is \textit{anonymous}.
-\end{definition}
-We observe that this definition permits the adversary to have corrupted or maliciously generated all but two keys in the ring.
-Some definitions allow the adversary to corrupt more keys, but we will see that this is inconsistent with our linkability construction, where an adversary in control of a ring member's private key can trivially determine if it was the signer by examining the linking tag associated to a signature.
-
-Linkability requires that an adversary be unable to produce $k+1$ non-linked signatures on a combined anonymity set of $k$ public keys.
-\begin{definition}[Linkability]
-Consider the following game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item For $i \in [0,k-1]$, the adversary $\A$ produces a public key $X_i$, message $M_i$, ring $R_i$, and signature $\sigma_i$.
-\item The adversary $\A$ produces another message M, ring R, and signature $\sigma$.
-\item All tuples $(X_i,M_i,R_i,\sigma_i)$ and $(M,R,\sigma)$ are sent to the challenger.
-\item The challenger checks the following:
-\begin{itemize}
-\item $\left| V \right| = k$, where $V \equiv \bigcup_{i=0}^{k-1} R_i$.
-\item Each $X_i \in V$.
-\item Each $R_i \subset V$.
-\item $\text{Verify}(\sigma_i,M_i,R_i) = 1$ for all $i$.
-\item $\text{Verify}(\sigma,M,R) = 1$.
-\item For all $i \neq j$, we have $\text{Link}(\sigma_i,\sigma_j) = \text{Link}(\sigma_i,\sigma) = 0$.
-\end{itemize}
-\item If all checks pass, $\A$ wins.
-\end{itemize}
-If $\A$ wins with only negligible probability for all $k$, we say the LRS is \textit{linkable}.
-\end{definition}
-
-Non-frameability requires that an adversary be unable to generate a signature that links with an honest signature.
-\begin{definition}[Non-frameability]
-Consider also the following game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item The adversary $\A$ is granted access to the public-key oracle $\text{GenOracle}$.
-\item The adversary $\A$ is granted access to the corruption oracle $\text{CorruptOracle}$.
-\item The adversary $\A$ is granted access to the signing oracle $\text{SignOracle}$.
-\item The adversary $\A$ chooses a public key $X$ that was generated by a query to $\text{GenOracle}$, but was not presented as a query to $\text{CorruptOracle}$.
-It selects a message $M \in \{0,1\}^*$ and ring $R$ such that $X \in R$.
-It queries $\text{SignOracle}(X,M,R) \to \sigma$.
-\item The adversary $\A$ then produces a tuple $(M',R',\sigma')$ and sends $(M',R',\sigma')$ to the challenger, along with $(X,M,R,\sigma)$.
-\item If $\text{Verify}(\sigma',M',R') = 0$ or if $\sigma'$ was produced using a query to $\text{SignOracle}$, the challenger aborts.
-\end{itemize}
-If $\text{Pr}[ \text{Link}(\sigma,\sigma') = 1 \approx 0$, we say that the LRS is \textit{non-frameable}.
-\end{definition}
-
-\section{Application: linkable ring signature}
-The constructions in \cite{groth,bootle} describe how to use a similar sigma protocol to construct a simple ring signature scheme.
-Using our modifications, we can easily extend this to account for linkability and non-frameability.
-We briefly show how to do so.
-
-\begin{figure}[htbp]
-\centering
-\fbox{\begin{minipage}{0.95\textwidth}
-    $\underline{\text{KeyGen}(r):}$
-    \begin{itemize}
-        \item If not specified, select $r \in \F$ uniformly at random.
-        \item Compute $R = rG$.
-        \item Return $(x,X) = (r,R)$.
-    \end{itemize}
-
-    $\underline{\text{Sign}(x,M,R):}$
-    \begin{itemize}
-        \item Let $R = \{X_0,\ldots,X_{N-1}\}$ such that $X_l = x_lG$.
-        \item Compute $J \equiv x_l^{-1}U$.
-        \item Run $\mathcal{P}_{\text{link}}(R,J;(l,x_l)) \to a$ (up to the verifier challenge).
-        \item Set $\xi \equiv \hs(M,R,a)$.
-        \item Run $\mathcal{P}_{\text{link}}(\xi) \to z$ (after the verifier challenge).
-        \item Return $\sigma = (a,z,J)$.
-    \end{itemize}
-
-    $\underline{\text{Verify}(\sigma,M,R):}$
-    \begin{itemize}
-        \item Let $R = \{X_0,\ldots,X_{N-1}\}$ such that $X_l - x_lG$.
-        \item Let $\sigma = (a,z,J)$.
-        \item Set $\xi \equiv \hs (M,R,a)$.
-        \item Return $\mathcal{V}_{\text{link}}(R,J,a,z)$.
-    \end{itemize}
-
-    $\underline{\text{Link}(\sigma,\sigma'):}$
-    \begin{itemize}
-        \item We implicitly assume that $\sigma$ and $\sigma'$ have been previously verified.
-        \item Let $\sigma = (a,z,J)$ and $\sigma' = (a',z',J')$.
-        \item If $J = J'$, return $1$.
-        Otherwise, return $0$.
-    \end{itemize}
-\end{minipage}}
-    \caption{Linkable ring signature using $\mathcal{R}_{\text{link}}$}
-    \label{fig:lrs}
-\end{figure}
-
-\begin{theorem}
-The protocol in Figure \ref{fig:lrs} is a linkable ring signature construction.
-\end{theorem}
-
-\begin{proof}
-Perfect correctness follows immediately from the perfect completeness of the proving system for $\mathcal{R}_{link}$.
-
-Similarly, anonymity follows since the proving system is special honest-verifier zero knowledge, and therefore witness indistinguishable \cite{cramer}.
-Any adversarial advantage in breaking anonymity must therefore arise from distinguishing either input commitments or linking tags in signatures.
-Since honestly-generated input Pedersen commitments are perfectly hiding, they are indistinguishable from elements of $\G$ selected uniformly at random; we assume by definition that at least two such commitments are present in such a signature.
-Further, honestly-generated linking tags are generated from a one-way pseudorandom function, and therefore in the random oracle model are independently uniformly distributed from other proof elements and input commitments.
-
-The proof for unforgeability in \cite{groth} relies on the (special) soundness of the underlying sigma protocol; it applies directly to our modification for $\mathcal{R}_{link}$, and is not repeated here.
-
-To show linkability, observe first that $\text{Link}$ simply compares linking tags, so two signatures link if and only if they share a common linking tag.
-Suppose an adversary can win the linkability game with non-negligible probability for some $k > 1$.
-Since all provided signatures verify, soundness implies extraction of a witness $x_i$ from signature $\sigma_i$ for all $i$, and of a witness $x$ from $\sigma$.
-Note that all $\{x_i\}$ and $x$ are distinct.
-If $x_i = x_j$ for $i \neq j$, then the corresponding linking tags $J_i$ and $J_j$ are such that $x_iJ_i = x_jJ_j = U$; then $J_i = J_j$, which contradicts $\text{Link}(\sigma_i,\sigma_j) = 0$.
-The same reasoning holds to show $x$ is similarly distinct.
-Soundness also implies that for all $i$, there exists $X_i \in R_i$ such that $x_iG = X_i$; similarly, there exists $X \in R$ such that $xG = X$.
-By assumption we have $$\{X_0,\ldots,X_{k-1},X\} \subset \left( \bigcup_{i=0}^{k-1} R_i \right) \cup R \subset V.$$
-However, note that $\left| \{X_0,\ldots,X_{k-1},X\} \right| = k+1$, but that $\left| V \right| = k$, a contradiction.
-
-Finally, we show non-frameability and assume an adversary has a non-negligible advantage in breaking this property.
-Because we have $\text{Verify}(\sigma',M',R') = 1$, soundness implies extraction of a witness $x' \in \F$ such that $x'G \in R'$; we also have a witness $x$ such that $xG \in R$ from the known signature $\sigma$.
-Since $\text{Link}(\sigma,\sigma') = 1$, the corresponding linking tags $J$ and $J'$ are equal by definition; hence by soundness $xJ = x'J' = U$, giving $x = x'$.
-However, the adversary did not query $\text{CorruptOracle}$ with $X$, meaning it breaks the discrete logarithm problem non-negligibly.
-\end{proof}
-
-\section{Protocol: parallel linkable one-of-many commitment}
-In this section, we describe a modification of the sigma protocol for $\mathcal{R}_{\text{link}}$ that permits us to prove knowledge of multiple commitments in $d > 1$ separate sets at the same index position, while retaining the linking property in the first commitment set only.
-This forms a version of Triptych with the same functionality as the $d$-linkable ring signature construction in \cite{clsag}, although the precise security model is a bit different.
-We later show how to apply such a construction to a signer-ambiguous transaction protocol that can demonstrate balance preservation.
-
-We wish to produce a sigma protocol for the following relation, for some given vector dimension $d > 1$.
-$$\mathcal{R}_{\text{par}} = \left\{ \{M_{i,\alpha}\}_{i,\alpha=0}^{N-1,d-1} \subset \G^d, J \in G ; \left(l, \{r_\alpha\}_{\alpha=0}^{d-1}\right) : \{M_{l,\alpha} = r_\alpha G\}_{\alpha=0}^{d-1} \text{ and } U = r_0 J \right\}$$
-This requires only minor modifications to the protocol for $\mathcal{R}_{\text{link}}$, so we document only the modified proof elements constructed and verified in Figure \ref{fig:par}.
-All other proof elements are generated and verified identically.
-
-\begin{figure}[htbp]
-\centering
-\fbox{\begin{minipage}{0.95\textwidth}
-$\underline{\mathcal{P}_{\text{par}}\left(\{M_{i,\alpha}\},J;\left(l,\{r_\alpha\}\right)\right):}$
-\begin{itemize}
-\item Define $K_\alpha \equiv r_\alpha J$ for $\alpha \in (0,d)$.
-\item Define $\mu_\alpha \equiv \hs\left(\alpha,\{M_{i,\alpha}\},J,\{K_\alpha\}\right)$ for $\alpha \in (0,d)$.
-\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}\left(M_{k,0} + \sum_{\alpha=1}^{d-1} \mu_\alpha M_{k,\alpha}\right) + \rho_jG$$
-\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv \left(U + \sum_{\alpha=1}^{d-1} \mu_\alpha K_\alpha\right)\sumk p_{k,j} + \rho_jG$$
-\end{itemize}
-
-$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
-$\{K_\alpha\},\{X_j\},\{Y_j\}$ \\
-
-$\underline{\mathcal{V} \to \mathcal{P}:}$ \\
-$\xi \in \{0,1\}^*$ \\
-
-$\underline{\mathcal{P}(\xi):}$
-\begin{itemize}
-\item Define $z \equiv \left(r_0 + \sum_{\alpha=1}^{d-1} \mu_\alpha r_\alpha\right)\xi^m - \sumj \rho_j\xi^j$.
-\end{itemize}
-
-$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
-$z$ \\
-
-$\underline{\mathcal{V}_{\text{par}}(\{M_{i,\alpha}\},J):}$
-\begin{itemize}
-\item Define $\mu_\alpha \equiv \hs\left(\alpha,\{M_{i,\alpha}\},J,\{K_\alpha\}\right)$ for $\alpha \in (0,d)$.
-\item Accept if and only if:
-\begin{eqnarray*}
-\sumk \left(M_{k,0} + \sum_{\alpha=1}^{d-1} \mu_\alpha M_{k,\alpha}\right) \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG &=& 0 \\
-\left(U + \sum_{\alpha=1}^{d-1} \mu_\alpha K_\alpha\right)\sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ &=& 0
-\end{eqnarray*}
-\end{itemize}
-\end{minipage}}
-\caption{Sigma protocol (abbreviated) for $\mathcal{R}_{\text{par}}$}
-\label{fig:par}
-\end{figure}
-
-\begin{theorem}
-The protocol in Figure \ref{fig:par} is perfectly complete, special honest-verifier zero knowledge, and $(m+1)$-special sound.
-\end{theorem}
-
-\begin{proof}
-In the random oracle model, extraction of a witness of the form $r_0 + \sum_{\alpha} \mu_\alpha r_\alpha$ implies knowledge of all $\{r_\alpha\}$ such that $r_\alpha G = M_{l,\alpha}$, similarly to the key-aggregation arguments in \cite{musig}.
-The same extraction shows that $\left(r_0 + \sum_{\alpha} \mu_\alpha r_\alpha\right)J = U + \sum_{\alpha} \mu_\alpha K_\alpha$, which implies in particular that $r_0J = U$, as required.
-
-The rest of the proof follows with only trivial modifications from the proof for $\mathcal{R}_{\text{link}}$.
-\end{proof}
-
-\section{Application: signer-ambiguous transaction protocol}
-The parallel construction described in Figure \ref{fig:par} can be used with $d = 2$ in a signer-ambiguous transaction protocol.
-
-Suppose a user wishes to generate a transaction consuming $W$ previously-generated outputs and generating $T$ fresh outputs.
-The user shuffles the consumed outputs within a larger list of $N$ outputs $\{M_{k,0}\}_{k=0}^{N-1}$, such that there exist indices $\{l_u\}_{u=0}^{W-1}$ where each $M_{l_u,0} = r_u$ for some known private key $r_u$.
-Further, assume each $M_{l_u,0}$ comes equipped with an amount commitment of the form $M_{l_u,1} \equiv \com(a_u,s_u)$ for amount $a_u$ and mask $s_u$.
-(All other $M_{k,0}$ also come equipped with a corresponding $M_{k,1}$, but the structure of these points is not relevant here.)
-
-The user generates $W$ auxiliary commitments $P'_u \equiv \com(a_u,s'_u)$ to the same amounts, but with different masks $\{s'_u\}$ chosen uniformly at random from $\F$.
-Then, the user generates $W$ spend proofs, each using the following prover inputs for $u \in [0,W)$:
-$$\mathcal{P}_{par}(\{M_{i,\alpha}\},r_u^{-1}U;(l_u,\{r_u,s_u-s'_u\}))$$
-
-For $j \in [0,T)$, the user generates a fresh output of the form $Q_j \equiv \com(b_j,t_j)$ for amount $b_j$ and mask $t_j$.
-The masks are chosen such that for $j \in [1,T)$, we have $t_j$ chosen uniformly at random from $\F$.
-We then choose $$t_0 \equiv \sum_{u=0}^{W-1} s_u' -\sum_{j=1}^{T-1} t_j$$ and include all $\{P'_u\}$ auxiliary commitments in the transaction.
-
-To verify such a transaction, the verifier first performs verification on each spend proof to ensure it is valid.
-Then, the verifier ensures that $$\sum_{u=0}^{W-1} P'_u - \sum_{j=0}^{T-1} Q_j = 0$$ such that the transaction balances.
-This succeeds since the commitments sum to zero if and only if the difference of input and output amounts is zero, which holds since the Pedersen commitment construction is computationally binding.
+Since the sigma protocol is special honest-verifier zero knowledge, it is witness indistinguishable \cite{cramer}.
+Note, however, that an observer who sees an input anonymity set containing a commitment for which the observer knows the opening can trivially test linking tags using its own secret keys to determine if they were used in the proof.
+Therefore, witness indistinguishability is assumed to apply among input commitments for which an observer does not know a corresponding opening.
 
 \section{Efficiency}
-Triptych proofs scale logarithmically with the size of the input anonymity set; this is the best asymptotic scaling known for ring signatures that do not require a trusted setup process over non-pairing groups.
-Related protocols based on the inner-product compression method of \cite{bulletproofs} include Omniring \cite{omniring} and RingCT 3.0 \cite{omniring}.
-However, it is challenging to directly compare these protocols' efficiency.
-Omniring includes all transaction input signatures, output range proofs, and balance within a single proof structure; however, it is not possible to verify a batch of proofs more efficiently by combining common generators.
-While an early version of RingCT 3.0 used separate input, range, and balance proofs, the most recent version merges all input and balance proofs together but outsources the range proofs to an efficient construction like \cite{bulletproofs}; this comes at the cost of requiring that the number of inputs be a power of two or otherwise carefully padded (affecting verification time).
-Therefore, for the purpose of comparison we modify slightly the earlier version of RingCT 3.0 with a soundness fix applied from the updated version, ignoring the size and verification cost of non-proof elements.
-Another more direct comparison is to CLSAG, a linear-sized linkable ring signature construction \cite{clsag}.
+Observe that all group operations involved in verification occur in multiscalar multiplication operations that must evaluate to zero; methods such as those in \cite{straus,pippenger} provide efficient evaluation of these operations.
+Further, many group elements in these operations are globally-fixed generators that appear in all proofs.
+As a result, verification of many separate independent proofs may be batched similarly to the method described in \cite{bulletproofs} and elsewhere, where random weighting of verification equations is performed and common generators are used only once.
+The result is that a batch of independent proofs can be more efficiently verified using a single multiscalar multiplication operation, lowering the marginal cost per proof to verify.
 
-We now show size and verification comparisons of the parallel instantiation of Triptych with $d = 2$, the earlier (modified) version of RingCT 3.0, and $2$-CLSAG.
-For verification scaling, we also account for the use of batching in Triptych and RingCT 3.0, where generators common to multiple proofs are used only once in verification.
-Further, since verification in both of these constructions reduces to checking whether several multiscalar multiplications are zero, we may apply random weighting such that verifying a batch of multiple proofs reduces to a single multiscalar multiplication.
-The use of efficient multiscalar multiplication algorithms like \cite{straus,pippenger} means that an $n$-multiscalar multiplication evaluates as $O(n/\log n)$.
-This form of batching does not apply to CLSAG, where verification consists of a sequence of hash function evaluations.
+We follow the same notation as before: $N = 2^m$ is the size of the input anonymity set for varying $m > 1$, $w$ is the number of signing indices, and $T$ is the number of output commitments used in the balance check.
+Assuming that both elements of $\G$ and $\F$ occupy $32$ bytes of storage (as is the case for common elliptic curve groups using compressed point representations), we compare the size of proofs for RingCT 3.0 (two variants) \cite{rct3}, Triptych \cite{triptych}, and this work.
+Note that we make some assumptions in order to produce fair comparisons here.
+In Triptych and the original version of RingCT 3.0, certain commitment offsets are required as part of balance testing, which we consider, along with the multiple proofs needed in a transaction that wishes to sign for multiple inputs.
+However, we ignore input set representation (which depends on implementation), range proofs (which are required for all protocols and not part of the proving systems), and any auxiliary data that would otherwise appear as part of transactions.
+Table \ref{table:size} shows the results.
 
-Table \ref{table:size} compares proof/signature sizes and verification complexity for these constructions as a function of the anonymity set size $N$ and batch size $B$.
-Verification complexity is separated into the number of hash-to-$\F$ operations (denoted $\hs$), hash-to-$\G$ operations (denoted $\hp$), and $i$-multiscalar multiplication operations of size $k(i)$.
-Figure \ref{fig:size} examines size as a function of input anonymity set size, under the assumption that elements of both $\G$ and $\F$ occupy $32$ kB of space.
-We note that although RingCT 3.0 proofs are slightly smaller for large $N$, Triptych proofs are smaller for $N < 512$, a limited but reasonable range given practical verification times.
-We also note that the application of Triptych in a complete transaction protocol is not directly compared to RingCT 3.0 here, as the use of non-proof/signaure auxiliary data in such a protocol may differ based on particular implementations.
-
-\begin{table}[h]
+\begin{table}
 \centering
-\begin{tabular}{r|ll|l}
-& Size ($\G$) & Size ($\F$) & Verification (batch total) \\
+\begin{tabular}{|ll|}
 \hline
-CLSAG \cite{clsag} & $2$ & $N + 1$ & $B(N + 2) \hs + BN \hp + 2BN k(3)$ \\
-RingCT 3.0 \cite{rct3} & $2\lg(N) + 9$ & $9$ & $k(B[2N + 2\lg(N) + 9] + 2N + 5)$ \\
-Triptych (this work) & $2\lg(N) + 6$ & $\lg(N) + 3$ & $k(B[2N + 2\lg(N) + 2] + 2\lg(N) + 3)$
+Protocol & Size (proof elements) \\
+\hline
+RingCT 3.0 (original) \cite{rct3} & $w(2 \lg N + 18) + w + 2$ \\
+RingCT 3.0 (updated) \cite{rct3} & $2\lceil \lg(Nw) \rceil + w + 17$ \\
+Triptych \cite{triptych} & $w(3 \lg N + 8) + w$ \\
+Arcturus (this work) & $(w + 3)\lg N + w + 7$ \\
+\hline
 \end{tabular}
-\caption{Proof sizes and verification complexity, for anonymity set size $N$ and batch size $B$}
+\caption{Proof size (in group/field elements) with varying anonymity set size $N$ and signing keys $w$}
 \label{table:size}
@@
 
-\begin{figure}[h]
+We also examine the verification complexity of these protocols.
+To do so, we examine the size of all multiscalar multiplication operations needed to verify one or more proofs in a transaction, along with balance proofs.
+Table \ref{table:time} shows the results for various transaction parameters.
+
+\begin{table}
+\centering
+\begin{tabular}{|ll|}
+\hline
+Protocol & Verification complexity \\
+\hline
+RingCT 3.0 (original) \cite{rct3} & $w(2\lg N + 11) + 4N + M + T + 7$ \\
+RingCT 3.0 (updated) \cite{rct3} & $2\lceil \lg(Nw) \rceil + N(w + 3) + M + T + 13$ \\
+Triptych \cite{triptych} & $(2 + 2w)\lg N + 2N + 4w + T + 2$ \\
+Arcturus (this work) & $(3 + 2w)\lg N + 2N + M + T$ \\
+\hline
+\end{tabular}
+\caption{Verification complexity with varying anonymity set size $N$, signing keys $w$, and outputs $T$}
+\label{table:time}
+\end{table}
+
+Since each compared protocol scales differently with the transaction parameters, it is instructive to examine the overall size effects under real-world conditions.
+To do this, we examine data from the Monero blockchain; in particular, for each transaction from 18 October 2018 to 14 February 2020, we extract the number of consumed outputs and the number of newly-generated outputs.
+Coinbase transactions, where new assets are generated by mining on a per-block basis, are ignored since they do not require this type of proof.
+Figure \ref{fig:size} shows this data run against the values in Table \ref{table:size} with additional transaction auxiliary data (including range proofs and recipient-specific data) for increasing anonymity set size $N$.
+Since verification complexity in all the protocols scales approximately linearly with $N$, overall verification time based on this parameter is an important bounding factor.
+
+\begin{figure}
 \centering
 \includegraphics[width=0.6\textwidth]{size.png}
-\caption{Proof sizes for input anonymity set size $N$}
+\caption{Total chain growth by anonymity set size}
 \label{fig:size}
@@
 
-\section{Future work}
-It is possible to further extend the Triptych proving system to support proving knowledge of openings of multiple commitments within the \textit{same} anonymity set, while permitting the construction of linking tags for each such opening and demonstrating balance directly within a single proof.
-Such a construction is much more efficient than the present work when built into a transaction protocol, but the security definitions applying to such a construction are still under evaluation.
+\begin{figure}
+\centering
+\includegraphics[width=0.6\textwidth]{time.png}
+\caption{Total verification time by anonymity set size}
+\label{fig:time}
+\end{figure}
+
+While the updated RingCT 3.0 protocol from \cite{rct3} yields superior space scaling, its requirement that $w$ be a power of two (padded to reach such a value) results in poor verification time scaling.
+Comparatively, our construction results in lower overall verification complexity at the expense of overall size scaling.
 

### 2020-04-07 arcturus/arcturus.py

@@ -1,0 +1,374 @@
+# Proof-of-concept implementation of https://github.com/monero-project/research-lab/issues/56
+
+from dumb25519 import hash_to_point, random_scalar, Scalar, hash_to_scalar, G, random_point, Z
+import dumb25519
+import random
+import transcript
+
+H = hash_to_point('H')
+U = hash_to_point('U')
+
+# Proof structure
+class Proof:
+    def __init__(self):
+        self.J = None # key images
+        self.A = None
+        self.B = None
+        self.C = None
+        self.D = None
+        self.X = None # for signing keys
+        self.Y = None # for key images
+        self.Z = None # for amounts
+        self.f = None
+        self.zA = None
+        self.zC = None
+        self.zR = None # for signing keys and key images
+        self.zS = None # for amounts
+        self.seed = None
+
+    def __repr__(self):
+        temp = '<ArcturusProof> '
+        temp += 'J:'+repr(self.J)+'|'
+        temp += 'A:'+repr(self.A)+'|'
+        temp += 'B:'+repr(self.B)+'|'
+        temp += 'C:'+repr(self.C)+'|'
+        temp += 'D:'+repr(self.D)+'|'
+        temp += 'X:'+repr(self.X)+'|'
+        temp += 'Y:'+repr(self.Y)+'|'
+        temp += 'Z:'+repr(self.Z)+'|'
+        temp += 'f:'+repr(self.f)+'|'
+        temp += 'zA:'+repr(self.zA)+'|'
+        temp += 'zC:'+repr(self.zC)+'|'
+        temp += 'zR:'+repr(self.zR)+'|'
+        temp += 'zS:'+repr(self.zS)
+        return temp
+
+# Pedersen tensor commitment
+def com_tensor(v,r):
+    C = dumb25519.Z
+    for i in range(len(v)):
+        for j in range(len(v[0])):
+            for k in range(len(v[0][0])):
+                C += hash_to_point('Gi',i,j,k)*v[i][j][k]
+    C += r*H
+    return C
+
+# Decompose a value with given base and size
+def decompose(val,base,size,t=int):
+    r = []
+    for i in range(size-1,-1,-1):
+        slot = base**i
+        r.append(int(val/slot))
+        val -= slot*r[-1]
+    r = list(reversed(r))
+
+    # Return int list or Scalar list
[…]

### 2020-04-07 arcturus/test.py

@@ -1,0 +1,53 @@
+import arcturus
+import unittest
+import dumb25519
+from dumb25519 import random_scalar, random_point, Scalar
+import random
+
+G = dumb25519.G
+H = dumb25519.hash_to_point('H')
+
+class TestValidProofs(unittest.TestCase):
+    def test_valid_prove_verify(self):
+        print ''
+
+        for m in [1,2]: # ring size 2,4
+            for spends in range(1,min(3,2**m)+1):
+                for outs in [1,2,3]:
+                    print 'Test parameters (m spends outs):',m,spends,outs
+                    l = random.sample(range(2**m),spends) # spend indices
+                    r = [random_scalar() for _ in range(spends)] # signing keys
+                    s = [random_scalar() for _ in range(spends)] # input commitment blinders
+                    a = [random_scalar() for _ in range(spends)] # input commitment amounts
+                    t = [random_scalar() for _ in range(outs)] # output commitment blinders
+                    b = [random_scalar() for _ in range(outs)] # output commitment amounts
+
+                    # Balance amounts
+                    b[0] = Scalar(0)
+                    for i in range(len(a)):
+                        b[0] += a[i]
+                    for i in range(1,len(b)):
+                        b[0] -= b[i]
+
+                    # Data to hide
+                    seed = random_scalar()
+                    aux1 = random_scalar()
+                    aux2 = random_scalar()
+
+                    # Set keys and commitments
+                    M = [random_point() for _ in range(2**m)] # possible signing keys
+                    P = [random_point() for _ in range(2**m)] # corresponding commitments
+                    Q = []
+                    for i in range(outs): # output commitments
+                        Q.append(t[i]*G + b[i]*H)
+                    for i in range(spends): # spend commitments
+                        M[l[i]] = r[i]*G
+                        P[l[i]] = s[i]*G + a[i]*H
+
+                    # Run test
+                    proof = arcturus.prove(M,P,Q,l,r,s,t,a,b,m,seed,aux1,aux2)
+                    aux1_,aux2_ = arcturus.verify(M,P,Q,proof,m)
+                    self.assertEqual(aux1,aux1_)
+                    self.assertEqual(aux2,aux2_)
+
+unittest.TextTestRunner(verbosity=2,failfast=True).run(unittest.TestLoader().loadTestsFromTestCase(TestValidProofs))

### 2020-04-07 arcturus/transcript.py

@@ -1,0 +1,21 @@
+# Transcript challenge handling
+
+from dumb25519 import *
+
+class Transcript:
+    # Initialize the transcript
+    def __init__(self,prefix):
+        self.state = hash_to_scalar(prefix)
+
+    # Update the transcript with public data
+    def update(self,data=None):
+        if data is None:
+            self.state = hash_to_scalar(self.state)
+        else:
+            self.state = hash_to_scalar(self.state,data)
+
+    # Retrieve a challenge scalar and update the state
+    def challenge(self):
+        x = self.state
+        self.update() # ensures fresh challenges
+        return x

### 2020-04-07 estimate.py
Updated for Arcturus

@@ -31,8 +31,8 @@ BATCH = args.batch_size # 0 is per block, otherwise fixed number of transactions
 data = open(args.data_file,'r') # data file
 
 # Size and time data
-size = {'triptych-single':0, 'triptych-multi':0, 'rct3-single':0, 'rct3-multi':0, 'clsag':0, 'mlsag':0} # in group/field elements
-time = {'triptych-single':0, 'triptych-multi':0, 'rct3-single':0, 'rct3-multi':0} # in linear combination counts
+size = {'triptych':0, 'arcturus':0, 'rct3-single':0, 'rct3-multi':0, 'clsag':0, 'mlsag':0} # in group/field elements
+time = {'triptych':0, 'arcturus':0, 'rct3-single':0, 'rct3-multi':0} # in linear combination counts
 actual_size = 0 # real chain growth (in bytes)
 
 # Cache data
@@ -45,8 +45,8 @@ for i in range(1,16+1):
 def timing(i):
     return float(7572-398)/(190000-10000)*(i-10000)+398
 
-# Single-input Triptych
-def triptych_single(M,T):
+# Triptych
+def triptych(M,T):
     total = 0
     total += M*(3*_logN + 8) # spend proofs
     total += M # input key images
@@ -58,7 +58,7 @@ def triptych_single(M,T):
     total += T # transaction keys
     total += 1 # payment ID
     return total
-def batch_triptych_single(batch):
+def batch_triptych(batch):
     sum_M = sum([datum[0] for datum in batch]) # M_1 + M_2 + ... + M_B
     sum_T = sum([datum[1] for datum in batch]) # T_1 + T_2 + ... + T_B
     max_T = max([datum[1] for datum in batch]) # max(T_1, ..., T_B)
@@ -70,8 +70,8 @@ def batch_triptych_single(batch):
     total += 4*B + sum_T + 2*sum([math.log2(64*datum[1]) for datum in batch]) + 128*max_T + 2 # range proofs
     return total
 
-# Multi-input Triptych
-def triptych_multi(M,T):
+# Arcturus
+def arcturus(M,T):
     total = 0
     total += _logN*(M + 3) + M + 7 # spend proof
     total += M # input key images
@@ -82,7 +82,7 @@ def triptych_multi(M,T):
     total += T # transaction keys
     total += 1 # payment ID
     return total
-def batch_triptych_multi(batch):
+def batch_arcturus(batch):
     sum_M = sum([datum[0] for datum in batch]) # M_1 + M_2 + ... + M_B
[…]

### 2020-04-07 paper/iacr.tex
Paper notation fixes

@@
 \begin{eqnarray*}
-&& \sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jX_j - \sumu z^{(u)}_RG \\
-&=& \sumk \mu_kM_k p_k(x) - \sumj x^j \left( \sumk p_{k,j}\mu_kM_k + \sumu \rho^{(u)}_jG \right) - \sumu z^{(u)}_RG \\
-&=& \sumk \mu_kM_k \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jG - \sumu z^{(u)}_RG \\
-&=& \sumk \mu_kM_k \left[ x^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_jG - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right]G \\
-&=& x^m\sumu \mu_{l^{(u)}}r^{(u)}G - \sumj x^j \sumu \rho^{(u)}_jG - x^m\sumu \mu_{l^{(u)}}r^{(u)}G + \sumj x^j \sumu \rho^{(u)}_jG \\
+&& \sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj \xi^jX_j - \sumu z^{(u)}_RG \\
+&=& \sumk \mu_kM_k p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}\mu_kM_k + \sumu \rho^{(u)}_jG \right) - \sumu z^{(u)}_RG \\
+&=& \sumk \mu_kM_k \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \sumu \rho^{(u)}_jG - \sumu z^{(u)}_RG \\
+&=& \sumk \mu_kM_k \left[ \xi^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj \xi^j \sumu \rho^{(u)}_jG - \sumu\left[ \mu_{l^{(u)}}r^{(u)}\xi^m - \sumj \rho^{(u)}_j\xi^j \right]G \\
+&=& \xi^m\sumu \mu_{l^{(u)}}r^{(u)}G - \sumj \xi^j \sumu \rho^{(u)}_jG - \xi^m\sumu \mu_{l^{(u)}}r^{(u)}G + \sumj \xi^j \sumu \rho^{(u)}_jG \\
 &=& 0
@@
 \begin{eqnarray*}
-&& \sumk \mu_kU \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} \\
-&=& \sumk \mu_kU p_k(x) - \sumj x^j \left( \sumk p_{k,j}\mu_kU + \sumu \rho^{(u)}_jJ^{(u)} \right) - \sumu z^{(u)}_RJ^{(u)} \\
-&=& \sumk \mu_kU \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jJ^{(u)} - \sumu z^{(u)}_RJ^{(u)} \\
-&=& \sumk \mu_kU \left[ x^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right](r^{(u)})^{-1}U \\
-&=& x^m\sumu \mu_{l^{(u)}}U - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - x^m\sumu \mu_{l^{(u)}}U + \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U \\
+&& \sumk \mu_kU \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj \xi^jY_j - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu_kU p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}\mu_kU + \sumu \rho^{(u)}_jJ^{(u)} \right) - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu_kU \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \sumu \rho^{(u)}_jJ^{(u)} - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu_kU \left[ \xi^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj \xi^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - \sumu\left[ \mu_{l^{(u)}}r^{(u)}\xi^m - \sumj \rho^{(u)}_j\xi^j \right](r^{(u)})^{-1}U \\
+&=& x^m\sumu \mu_{l^{(u)}}U - \sumj \xi^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - \xi^m\sumu \mu_{l^{(u)}}U + \sumj \xi^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U \\
 &=& 0
@@
 \begin{eqnarray*}
-&& \sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jZ_j - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
-&=& \sumk P_k p_k(x) - \sumj x^j \left( \sumk p_{k,j}P_k + \sumu \overline{\rho}^{(u)}_jG \right) - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
-&=& \sumk P_k \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \overline{\rho}^{(u)}_jG - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
-&=& x^m\sumu (s^{(u)}G + a_uH) - \sumj x^j \sumu \overline{\rho}^{(u)}_jG - x^m\sum_{j=0}^{T-1} (t_jG + b_jH) - x^m\left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right)G + \\
-&& \sumj x^j \sumu \overline{\rho}^{(u)}_jG \\
+&& \sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj \xi^jZ_j - \xi^m\sum_{j=0}^{T-1} Q_j - z_SG \\
+&=& \sumk P_k p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}P_k + \sumu \overline{\rho}^{(u)}_jG \right) - \xi^m\sum_{j=0}^{T-1} Q_j - z_SG \\
+&=& \sumk P_k \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \sumu \overline{\rho}^{(u)}_jG - \xi^m\sum_{j=0}^{T-1} Q_j - z_SG \\
+&=& \xi^m\sumu (s^{(u)}G + a_uH) - \sumj \xi^j \sumu \overline{\rho}^{(u)}_jG - \xi^m\sum_{j=0}^{T-1} (t_jG + b_jH) - \xi^m\left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right)G + \\
+&& \sumj \xi^j \sumu \overline{\rho}^{(u)}_jG \\
 &=& \left( \sumu a_u - \sum_{j=0}^{T-1} b_j \right)H \\

### 2020-04-08 triptych/test.py
Simplified convolution

@@ -11,7 +11,7 @@ class TestValidProofs(unittest.TestCase):
     def test_valid_prove_verify(self):
         print ''
 
-        for m in [1,2]: # ring size 2,4
+        for m in [2,3]: # ring size 4,8
             print 'Test parameter (m):',m
             l = random.randrange(2**m) # spend index
             r = random_scalar() # signing key

### 2020-04-08 triptych/triptych.py

@@ -74,17 +74,15 @@ def delta(x,y):
         return Scalar(1)
     return Scalar(0)
 
-# Compute a convolution
-def convolve(x,y,size=None):
-    r = [Scalar(0)]*(len(x)+len(y))
+# Compute a convolution with a degree-one polynomial
+def convolve(x,y):
+    if not len(y) == 2:
+        raise ValueError('Convolution requires a degree-one polynomial!')
+
+    r = [Scalar(0)]*(len(x)+1)
     for i in range(len(x)):
         for j in range(len(y)):
             r[i+j] += x[i]*y[j]
-
-    # Pad with zeros
-    if size is not None and size > len(r):
-        for i in range(size-len(r)):
-            r.append(Scalar(0))
 
     return r
 
@@ -156,13 +154,13 @@ def prove(M,P,l,r,s,m,seed=None,aux1=Scalar(0),aux2=Scalar(0)):
     D = com_matrix(a_sq,rD)
 
     # Compute p coefficients
-    p = [[Scalar(0) for _ in range(m)] for _ in range(N)]
+    p = [[] for _ in range(N)]
     for k in range(N):
         decomp_k = decompose(k,n,m)
         p[k] = [a[0][decomp_k[0]],delta(decomp_l[0],decomp_k[0])]
         
         for j in range(1,m):
-            p[k] = convolve(p[k],[a[j][decomp_k[j]],delta(decomp_l[j],decomp_k[j])],m)
+            p[k] = convolve(p[k],[a[j][decomp_k[j]],delta(decomp_l[j],decomp_k[j])])
 
     # Generate proof values
     X = [dumb25519.Z for _ in range(m)]
@@ -230,6 +228,9 @@ def prove(M,P,l,r,s,m,seed=None,aux1=Scalar(0),aux2=Scalar(0)):
 # RETURNS
 #  auxiliary data if the proof is valid
 def verify(M,P,proof,m):
+    if not m > 1:
+        raise ValueError('Must have m > 1!')
+
     n = 2
     N = n**m
     tr = transcript.Transcript('Triptych single-input')

### 2020-04-08 arcturus/arcturus.py
Simplified convolution

@@ -77,17 +77,15 @@ def delta(x,y):
         return Scalar(1)
     return Scalar(0)
 
-# Compute a convolution
-def convolve(x,y,size=None):
-    r = [Scalar(0)]*(len(x)+len(y))
+# Compute a convolution with a degree-one polynomial
+def convolve(x,y):
+    if not len(y) == 2:
+        raise ValueError('Convolution requires a degree-one polynomial!')
+
+    r = [Scalar(0)]*(len(x)+1)
     for i in range(len(x)):
         for j in range(len(y)):
             r[i+j] += x[i]*y[j]
-
-    # Pad with zeros
-    if size is not None and size > len(r):
-        for i in range(size-len(r)):
-            r.append(Scalar(0))
 
     return r
 
@@ -180,7 +178,7 @@ def prove(M,P,Q,l,r,s,t,a,b,m,seed=None,aux1=Scalar(0),aux2=Scalar(0)):
     D = com_tensor(a_sq,rD)
 
     # Compute p coefficients
-    p = [[[Scalar(0) for _ in range(m)] for _ in range(N)] for _ in range(w)]
+    p = [[[] for _ in range(N)] for _ in range(w)]
     for k in range(N):
         decomp_k = decompose(k,n,m)
         for u in range(w):
@@ -188,7 +186,7 @@ def prove(M,P,Q,l,r,s,t,a,b,m,seed=None,aux1=Scalar(0),aux2=Scalar(0)):
         
         for j in range(1,m):
             for u in range(w):
-                p[u][k] = convolve(p[u][k],[a[u][j][decomp_k[j]],delta(decomp_l[u][j],decomp_k[j])],m)
+                p[u][k] = convolve(p[u][k],[a[u][j][decomp_k[j]],delta(decomp_l[u][j],decomp_k[j])])
 
         # Combine to single coefficients in p[0]
         for j in range(m):
@@ -278,6 +276,9 @@ def prove(M,P,Q,l,r,s,t,a,b,m,seed=None,aux1=Scalar(0),aux2=Scalar(0)):
 # RETURNS
 #  auxiliary data if the proof is valid
 def verify(M,P,Q,proof,m):
+    if not m > 1:
+        raise ValueError('Must have m > 1!')
+
     n = 2
     N = n**m
     tr = transcript.Transcript('Arcturus')

### 2020-04-08 arcturus/test.py

@@ -11,7 +11,7 @@ class TestValidProofs(unittest.TestCase):
     def test_valid_prove_verify(self):
         print ''
 
-        for m in [1,2]: # ring size 2,4
+        for m in [2,3]: # ring size 4,8
             for spends in range(1,min(3,2**m)+1):
                 for outs in [1,2,3]:
                     print 'Test parameters (m spends outs):',m,spends,outs

### 2020-05-17 paper/iacr.tex
Fix typo in paper

--- 2020-04-07 paper/iacr.tex
@@
 Verification complexity is separated into the number of hash-to-$\F$ operations (denoted $\hs$), hash-to-$\G$ operations (denoted $\hp$), and $i$-multiscalar multiplication operations of size $k(i)$.
-Figure \ref{fig:size} examines size as a function of input anonymity set size, under the assumption that elements of both $\G$ and $\F$ occupy $32$ kB of space.
+Figure \ref{fig:size} examines size as a function of input anonymity set size, under the assumption that elements of both $\G$ and $\F$ occupy $32$ bytes of space.
 We note that although RingCT 3.0 proofs are slightly smaller for large $N$, Triptych proofs are smaller for $N < 512$, a limited but reasonable range given practical verification times.

### 2020-05-18 cschnorr.py
Double-key Schnorr signature examples

@@ -1,0 +1,72 @@
+# Double-key compact Schnorr signature
+
+from dumb25519 import *
+
+domain = 'double compact Schnorr signature' # hash domain separator
+domain_aggregate = 'double compact Schnorr signature aggregator' # key aggregator separator
+
+class DoubleCompactSchnorr:
+    def __init__(self):
+        self.c = None
+        self.s = None
+
+# Generate a double-key compact signature
+# INPUT:
+#   m: message
+#   p1,P1: first key pair
+#   p2,P2: second key pair
+# OUTPUT:
+#   sig: DoubleCompactSchnorr
+def sign(m,p1,P1,p2,P2):
+    if not isinstance(p1,Scalar) or not isinstance(P1,Point) or not isinstance(p2,Scalar) or not isinstance(P2,Point):
+        raise TypeError('Bad input data type!')
+    if not p1*G == P1 or not p2*G == P2:
+        raise ValueError('Bad key!')
+    try:
+        hash_to_scalar(m)
+    except:
+        raise TypeError('Unable to hash message!')
+
+    k = random_scalar()
+    mu = hash_to_scalar(domain_aggregate,m,P1,P2)
+
+    sig = DoubleCompactSchnorr()
+    sig.c = hash_to_scalar(domain,m,P1,P2,k*G)
+    sig.s = k - (p1 + mu*p2)*sig.c
+    
+    return sig
+
+# Verify a double-key compact signature
+# INPUT:
+#   m: message
+#   P1,P2: public keys
+#   sig: DoubleCompactSchnorr
+# OUTPUT:
+#   True if valid
+#   False if invalid
+def verify(m,P1,P2,sig):
+    if not isinstance(P1,Point) or not isinstance(P2,Point) or not isinstance(sig,DoubleCompactSchnorr):
+        raise TypeError('Bad input data type!')
+    try:
+        hash_to_scalar(m)
+    except:
+        raise TypeError('Unable to hash message!')
+    if sig.s == Scalar(0):
+        raise ValueError('Unexpected zero value in signature!')
+    
+    mu = hash_to_scalar(domain_aggregate,m,P1,P2)
+    if hash_to_scalar(domain,m,P1,P2,sig.s*G + sig.c*(P1 + mu*P2)) == sig.c:
+        return True
+    return False
+
+# Run a random test
+print 'Running random test...'
+p1 = random_scalar()
+P1 = p1*G
+p2 = random_scalar()
[…]

### 2020-05-18 dumb25519/test.py

@@ -1,866 +1,0 @@
-# Test suite for dumb25519
-
-from dumb25519 import *
-import unittest
-
-# Scalar class
-class TestScalar(unittest.TestCase):
-    def test_init(self):
-        # Test construction from hex representations
-        self.assertEqual(Scalar('0000000000000000000000000000000000000000000000000000000000000000'),Scalar(0))
-        self.assertEqual(Scalar('0100000000000000000000000000000000000000000000000000000000000000'),Scalar(1))
-        self.assertEqual(Scalar('ecd3f55c1a631258d69cf7a2def9de1400000000000000000000000000000010'),Scalar(l-1))
-        
-        # Test construction using x = 1
-        s = Scalar(int(1))
-        self.assertEqual(s,Scalar(long(1)))
-        self.assertEqual(s.x,int(1))
-        self.assertEqual(s.x,long(1))
-
-        # Test construction using x = l = 0
-        s = Scalar(int(l))
-        self.assertEqual(s,Scalar(long(l)))
-        self.assertEqual(s.x,int(0))
-        self.assertEqual(s.x,long(0))
-
-        # Test invalid constructions
-        with self.assertRaises(TypeError):
-            Scalar('invalid')
-        with self.assertRaises(TypeError):
-            Scalar(None)
-
-    def test_invert(self):
-        # Test nonzero inversion
-        self.assertEqual(Scalar(1).invert(),Scalar(1))
-        self.assertEqual(Scalar(1).invert(allow_zero=True),Scalar(1))
-        self.assertEqual(Scalar(2).invert()*Scalar(2),Scalar(1))
-        self.assertEqual(Scalar(2).invert(allow_zero=True)*Scalar(2),Scalar(1))
-        
-        # Test zero inversion
-        self.assertEqual(Scalar(0).invert(allow_zero=True),Scalar(0))
-        with self.assertRaises(ZeroDivisionError):
-            Scalar(0).invert()
-
-    def test_add(self):
-        # Test valid addition
-        self.assertEqual(Scalar(0) + Scalar(1),Scalar(1))
-        self.assertEqual(Scalar(1) + Scalar(1),Scalar(2))
-        self.assertEqual(Scalar(l - 1) + Scalar(1),Scalar(0))
-        self.assertEqual(Scalar(1) + Scalar(-1),Scalar(0))
-
-        # Test invalid addition
-        with self.assertRaises(TypeError):
[…]

### 2020-05-18 dumb448/dumb448.py

@@ -1,601 +1,0 @@
-# Dumb448: a stupid implementation of ed448
-#
-# Use this code only for prototyping
-# -- putting this code into production would be dumb
-# -- assuming this code is secure would also be dumb
-
-import random
-import hashlib
-import binascii
-
-# Curve parameters
-q = 2**448 - 2**224 - 1
-l = 2**446 - 13818066809895115352007386748515426880336692474882178609894547503885
-cofactor = 4
-b = 456 # bit length
-
-# Internal helper methods
-def exponent(b,e,m):
-    return pow(b,e,m)
-
-def invert(x,p):
-    # Assumes `p` is prime
-    return exponent(x,p-2,p)
-
-def xfromy(y):
-    temp = (y*y-1) * invert(d*y*y-1,q)
-    x = exponent(temp,(q+1)/4,q)
-    if x % 2 != 0:
-        x = q-x
-    return x
-
-def bit(h,i):
-    return (ord(h[i/8]) >> (i%8)) & 1
-
-d = -39081
-
-# An element of the main subgroup scalar field
-class Scalar:
-    def __init__(self,x):
-        # Generated from an integer value
-        if isinstance(x,int) or isinstance(x,long):
-            self.x = x % l
-        # Generated from a hex representation
-        elif isinstance(x,str):
-            try:
-                x = binascii.unhexlify(x)
-                self.x = sum(2**i * bit(x,i) for i in range(0,b)) % l
-            except:
-                raise TypeError
-        else:
-            raise TypeError
-
-    # Multiplicative inversion, with an option to let 1/0 = 0 if you're into that
-    def invert(self,allow_zero=False):
-        if self.x == 0:
-            if allow_zero:
-                return Scalar(0)
-            else:
-                raise ZeroDivisionError
-        return Scalar(invert(self.x,l))
-
-    # Addition
-    def __add__(self,y):
-        if isinstance(y,Scalar):
-            return Scalar(self.x + y.x)
-        return NotImplemented
-
-    # Subtraction
-    def __sub__(self,y):
-        if isinstance(y,Scalar):
-            return Scalar(self.x - y.x)
-        return NotImplemented
-
-    # Multiplication (possibly by an integer)
-    def __mul__(self,y):
-        if isinstance(y,int):
-            return Scalar(self.x * y)
-        if isinstance(y,Scalar):
-            return Scalar(self.x * y.x)
-        return NotImplemented
-
-    def __rmul__(self,y):
-        if isinstance(y,int):
-            return self*y
-        return NotImplemented
-
[…]

### 2020-05-18 dumb448/test.py

@@ -1,870 +1,0 @@
-# Test suite for dumb448
-
-from dumb448 import *
-import unittest
-
-# Scalar class
-class TestScalar(unittest.TestCase):
-    def test_init(self):
-        # Test construction from hex representations
-        self.assertEqual(Scalar('000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000'),Scalar(0))
-        self.assertEqual(Scalar('010000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000000'),Scalar(1))
-        self.assertEqual(Scalar('f24458ab92c27823558fc58d72c26c219036d6ae49db4ec4e923ca7cffffffffffffffffffffffffffffffffffffffffffffffffffffff3f00'),Scalar(l-1))
-
-        # Test construction using x = 1
-        s = Scalar(int(1))
-        self.assertEqual(s,Scalar(long(1)))
-        self.assertEqual(s.x,int(1))
-        self.assertEqual(s.x,long(1))
-
-        # Test construction using x = l = 0
-        s = Scalar(int(l))
-        self.assertEqual(s,Scalar(long(l)))
-        self.assertEqual(s.x,int(0))
-        self.assertEqual(s.x,long(0))
-
-        # Test invalid constructions
-        with self.assertRaises(TypeError):
-            Scalar('invalid')
-        with self.assertRaises(TypeError):
-            Scalar(None)
-
-    def test_invert(self):
-        # Test nonzero inversion
-        self.assertEqual(Scalar(1).invert(),Scalar(1))
-        self.assertEqual(Scalar(1).invert(allow_zero=True),Scalar(1))
-        self.assertEqual(Scalar(2).invert()*Scalar(2),Scalar(1))
-        self.assertEqual(Scalar(2).invert(allow_zero=True)*Scalar(2),Scalar(1))
-        
-        # Test zero inversion
-        self.assertEqual(Scalar(0).invert(allow_zero=True),Scalar(0))
-        with self.assertRaises(ZeroDivisionError):
-            Scalar(0).invert()
-
-    def test_add(self):
-        # Test valid addition
-        self.assertEqual(Scalar(0) + Scalar(1),Scalar(1))
-        self.assertEqual(Scalar(1) + Scalar(1),Scalar(2))
[…]

### 2020-05-18 multiexp/ed25519.py

@@ -1,86 +1,0 @@
-import random
-
-# curve parameters
-b = 256
-q = 2**255 - 19
-l = 2**252 + 27742317777372353535851937790883648493
-
-# op counts
-counts = {}
-
-def reset():
-    counts['add'] = 0
-    counts['multiply'] = 0
-    
-# compute b^e mod m
-#def exponent(b,e,m):
-#    if e == 0:
-#        return 1
-#    temp = exponent(b,e/2,m)**2 % m
-#    if e & 1:
-#        temp = (temp*b) % m
-#    return temp
-def exponent(b,e,m):
-    return pow(b,e,m)
-
-# compute x^(-1) mod m
-def invert(x):
-    return exponent(x,q-2,q)
-
-# useful constants
-d = -121665 * invert(121666)
-I = exponent(2,(q-1)/4,q)
-
-# given a y value, recover the x value on the curve
-def xfromy(y):
-    temp = (y*y-1) * invert(d*y*y+1)
-    x = exponent(temp,(q+3)/8,q)
-    if (x*x - temp) % q != 0:
-        x = (x*I) % q
-    if x % 2 != 0:
-        x = q-x
-    return x
-
-# common basepoint (requires earlier function)
-Gy = 4*invert(5)
-Gx = xfromy(Gy)
-G = [Gx % q, Gy % q]
-
-# zero point
-Z = [0,1]
-
-# add P+Q
-def _add(P,Q):
-    x1 = P[0]
-    y1 = P[1]
-    x2 = Q[0]
-    y2 = Q[1]
-    x3 = (x1*y2+x2*y1) * invert(1+d*x1*x2*y1*y2)
-    y3 = (y1*y2+x1*x2) * invert(1-d*x1*x2*y1*y2)
-    return [x3 % q, y3 % q]
-
-def add(P,Q):
-    counts['add'] += 1
-    return _add(P,Q)
-
-# scalar multiply a*P
-def _multiply(a,P):
-    if a == 0:
-        return [0,1]
-    Q = _multiply(a/2,P)
-    Q = _add(Q,Q)
-    if a & 1:
-        Q = _add(Q,P)
-    return Q
-
-def multiply(a,P):
-    counts['multiply'] += 1
-    return _multiply(a,P)
-
-# generate a random scalar
-def random_scalar():
-    return random.randrange(0,l)
-
-# generate a random multiple of the basepoint
-def random_point():
-    return _multiply(random_scalar(),G)

### 2020-05-18 multiexp/multiexp.py

@@ -1,287 +1,0 @@
-# Each test computes an expression of the form a1*P1 + ... + an*Pn
-# - each ai is a scalar
-# - each Pi is a curve point
-
-import ed25519
-import heapq
-from copy import deepcopy
-from time import clock
-import cPickle
-
-MIN_POINTS = 2 # size of first trial
-MAX_POINTS = 64 # size of last trial
-
-# use individual operations
-def basic(data):
-    result = ed25519.Z # zero point
-    for datum in data:
-        result = ed25519.add(result,ed25519.multiply(datum[0],datum[1]))
-    return result
-
-# use Bos-Coster with linear search
-def boscoster(data):
-    while True:
-        index1 = 0
-        for i in range(len(data)):
-            if data[i][0] > data[index1][0]:
-                index1 = i
-        index2 = 0
-        if index2 == index1:
-            index2 = 1
-        for i in range(len(data)):
-            if i != index1:
-                if data[i][0] > data[index2][0]:
-                    index2 = i
-        if data[index2][0] == 0:
-            return ed25519.multiply(data[index1][0],data[index1][1])
-        data[index2][1] = ed25519.add(data[index2][1],data[index1][1])
-        data[index1][0] = (data[index1][0] - data[index2][0]) % ed25519.l # scalar subtraction
-
-# use Bos-Coster with linear search and pathological input fix
-def boscoster_robust(data):
-    while True:
-        index1 = 0
-        for i in range(len(data)):
-            if data[i][0] > data[index1][0]:
-                index1 = i
-        index2 = 0
-        if index2 == index1:
-            index2 = 1
-        for i in range(len(data)):
-            if i != index1:
-                if data[i][0] > data[index2][0]:
-                    index2 = i
-        if data[index2][0] == 0:
-            return ed25519.multiply(data[index1][0],data[index1][1])
-
-        # handle pathological inputs where s1 > 2s2
-        # replace (s1,P1) with (s1/2,2*P1)
-        while data[index1][0] > 2*data[index2][0]:
-            # if s1 is odd, add (1,P1) at the end of the heap
-            if (data[index1][0] % 2) == 1:
-                data.append([1,data[index1][1]])
-            data[index1][0] = long(data[index1][0]/2)
-            data[index1][1] = ed25519.add(data[index1][1],data[index1][1])
-
[…]

### 2020-05-18 schnorr.py

@@ -1,0 +1,72 @@
+# Double-key Schnorr signature
+
+from dumb25519 import *
+
+domain = 'double Schnorr signature' # hash domain separator
+
+class DoubleSchnorr:
+    def __init__(self):
+        self.c = None
+        self.s1 = None
+        self.s2 = None
+
+# Generate a double-key signature
+# INPUT:
+#   m: message
+#   p1,P1: first key pair
+#   p2,P2: second key pair
+# OUTPUT:
+#   sig: DoubleSchnorr
+def sign(m,p1,P1,p2,P2):
+    if not isinstance(p1,Scalar) or not isinstance(P1,Point) or not isinstance(p2,Scalar) or not isinstance(P2,Point):
+        raise TypeError('Bad input data type!')
+    if not p1*G == P1 or not p2*G == P2:
+        raise ValueError('Bad key!')
+    try:
+        hash_to_scalar(m)
+    except:
+        raise TypeError('Unable to hash message!')
+
+    k1 = random_scalar()
+    k2 = random_scalar()
+
+    sig = DoubleSchnorr()
+    sig.c = hash_to_scalar(domain,m,P1,P2,k1*G,k2*G)
+    sig.s1 = k1 - p1*sig.c
+    sig.s2 = k2 - p2*sig.c
+    
+    return sig
+
+# Verify a double-key signature
+# INPUT:
+#   m: message
+#   P1,P2: public keys
+#   sig: DoubleSchnorr
+# OUTPUT:
+#   True if valid
+#   False if invalid
+def verify(m,P1,P2,sig):
+    if not isinstance(P1,Point) or not isinstance(P2,Point) or not isinstance(sig,DoubleSchnorr):
+        raise TypeError('Bad input data type!')
+    try:
+        hash_to_scalar(m)
+    except:
+        raise TypeError('Unable to hash message!')
+    if sig.s1 == Scalar(0) or sig.s2 == Scalar(0):
+        raise ValueError('Unexpected zero value in signature!')
+    
+    if hash_to_scalar(domain,m,P1,P2,sig.s1*G + sig.c*P1,sig.s2*G + sig.c*P2) == sig.c:
+        return True
+    return False
+
+# Run a random test
+print 'Running random test...'
+p1 = random_scalar()
+P1 = p1*G
+p2 = random_scalar()
+P2 = p2*G
+m = random_scalar() # or any hashable data type
+
[…]

### 2020-07-03 paper/iacr.tex
Updated paper

--- 2020-04-07 paper/iacr.tex
@@
-\documentclass{article}
-\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}
-\usepackage{amsmath,amssymb,amsthm,amsfonts}
-\usepackage[utf8]{inputenc}
-\usepackage{hyperref}
-\usepackage{graphics,graphicx}
+\documentclass{llncs}
+\pagestyle{headings}
 
-\title{Arcturus: efficient proofs for confidential transactions}
-\author{Sarang Noether \\ Monero Research Lab \\ \texttt{sarang.noether@protonmail.com}}
-\date{\today}
+\usepackage{enumerate}
+\usepackage{amsmath,amssymb}
 
-\newcommand{\G}{\mathbb{G}}
-\newcommand{\F}{\mathbb{F}}
-\newcommand{\N}{\mathbb{N}}
-\newcommand{\hs}{\mathsf{H}}
-\newcommand{\hp}{\mathcal{H}}
-\newcommand{\com}{\operatorname{Com}}
-\newcommand{\A}{\mathcal{A}}
+\newcommand{\A}{\texttt{A}}
+\newcommand{\B}{\texttt{B}}
+\newcommand{\F}{\texttt{F}_p}
+\newcommand{\G}{\texttt{G}}
+\newcommand{\Hp}{\mathcal{H}^p}
+\newcommand{\Hs}{\mathcal{H}^s}
+\newcommand{\prob}{\mathbb{P}}
 
-\newcommand{\sumi}{\sum_{i=0}^{n-1}}
-\newcommand{\sumj}{\sum_{j=0}^{m-1}}
-\newcommand{\sumk}{\sum_{k=0}^{N-1}}
-\newcommand{\sumu}{\sum_{u=0}^{w-1}}
-
-\newtheorem{theorem}{Theorem}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
+\title{Concise Linkable Ring Signatures and Forgery Against Adversarial Keys}
+\institute{Monero Research Lab, \email{\{surae,sarang\}@getmonero.org} \and Independent researcher, \email{randomrun@protonmail.com}}
+\author{Brandon Goodell\inst{1} \and Sarang Noether\inst{1} \and Arthur Blue\inst{2}}
 
 \begin{document}
-
 \maketitle
@@
 \begin{abstract}
-Confidential transactions are used in distributed digital assets to demonstrate the balance of values hidden in commitments, while retaining signer ambiguity.
-Previous work describes a signer-ambiguous proof of knowledge of the opening of commitments to zero at the same index across multiple public commitment sets and the evaluation of a verifiable random function used as a linking tag, and uses this to build a linkable ring signature called Triptych that can be used as a building block for a confidential transaction model.
-In this work, we extend Triptych to build Arcturus, a proving system that proves knowledge of openings of multiple commitments to zero within a single set, correct construction of a verifiable random function evaluated at each opening, and value balance across a separate list of commitments within a single proof.
-While soundness depends on a novel dual discrete-logarithm hardness assumption, we use data from the Monero blockchain to show that Arcturus can be used in a confidential transaction model to provide faster total batch verification time than other state-of-the-art constructions without a trusted setup.
+We demonstrate that a version of non-slanderability is a natural definition of unforgeability for linkable ring signatures.
+We present a linkable ring signature construction with concise signatures and multi-dimensional keys that is linkably anonymous if a variation of the decisional Diffie-Hellman problem with random oracles is hard, linkable if key aggregation is a one-way function, and non-slanderable if a one-more variation of the discrete logarithm problem is hard.
+We remark on some applications in signer-ambiguous confidential transaction models without trusted setup.
 \end{abstract}
@@
 \section{Introduction}
-Distributed digital assets, starting with Bitcoin, rely on digital signatures to authorize transactions and transfer the spend authority of funds.
-While early protocols based on the model established by Bitcoin have the advantage of simplicity, they lack desirable properties relating to privacy and indistinguishability.
-In particular, the address and signature graph formed by the blockchain in such assets is trivially traceable, and the amounts a signature authorizes in a transaction are visible.
 
-To protect users of distributed assets and permit better indistinguishability of transactions for fungibility, several methods have been proposed and deployed toward confidential transactions.
-The CryptoNote protocol, an early proposal for obscuring transaction graphs, relies on linkable ring signatures on transaction outputs with denominated amounts \cite{cryptonote}; a transaction includes a separate signature for each such amount, yielding poor scaling.
-A later advancement to the RingCT protocol \cite{ringct} used Pedersen commitments to amounts associated with transaction outputs and extended a ring signature construction by Liu \text{et al.} \cite{liu} to support parallel signatures in a matrix arrangement, removing the need for denominated transaction outputs altogether.
-However, both of these constructions use linkable ring signatures that scale linearly in size with the size of the anonymity set used in each signature.
+First introduced in \cite{rivest} in the RSA setting and in \cite{liu2004linkable} in the discrete logarithm setting, ring signatures permit message signing on behalf of a set of public keys rather than a single public key.
+Ring signatures see myriad applications ranging from lightweight anonymous authentication in \cite{yang2015lightweight} to transaction protocols like Monero in \cite{noether2016ring} and CryptoNote in \cite{van2013cryptonote}.
+A verifier is assured that the signer knows the private key of at least one of these public keys, which are called ring members.
+Ring signatures are anonymous or signer-ambiguous in the sense that the verifier does not learn information from the signature about which key is the signer.
+We stress that methods of practical analysis such as those of  \cite{moser2018empirical,quesnelle2017linkability} can exploit metadata in real-life applications of anonymous authentication protocols to reduce anonymity.
 
-More recent methods of maintaining transaction privacy use accumulators to represent a given state of transaction outputs.
-Zerocoin \cite{zerocoin} relied on RSA accumulators and associated proofs to assert the validity of transactions, but amounts were fixed, the protocol used very large and inefficient proofs, transactions were limited to a simple burn-mint operation on a transparent chain, and the use of RSA groups required a trusted setup process.
-Later work produced Zerocash \cite{zerocash}, which replaced RSA accumulators and related proofs with succinct proofs relating to Merkle tree accumulators, enabling arbitrary amounts and direct anonymous transfers.
-However, like Zerocoin, Zerocash used a proving system requiring a trusted setup process; this was eventually used as the basis for the Zcash protocols.
+Group signature constructions preceding \cite{rivest,liu2004linkable} require some degree of interactivity, a fixed set of participants, a trusted group manager or other trusted setup, or hardness assumptions not based on the discrete logarithm problem.
+Since \cite{rivest}, ring signatures have enjoyed many improvements, extensions, and modifications.
+For example, ring signatures are constructed in the bilinear pairing setting in \cite{zhang2002id}, key structures are generalized in \cite{abe20021}, security definitions are improved in \cite{bender2006ring}, signature size is improved in \cite{fujisaki2011sub,gu2018constant}, and traceability is introduced in \cite{fujisaki2007traceable}.
 
-Until recently, transaction protocols desiring robust signer ambiguity and flexible direct anonymous transfers of arbitrary amounts faced a tradeoff between a trust-free construction and efficiency in proof sizes and verification complexity.
-Recent work in this area generally relies on one of two novel proving systems to build transactions that scale in size logarithmically with the size of the prover-specified anonymity set, while requiring no trusted setup.
-A one-of-many commitment-to-zero proving system of Groth and Kohlweiss \cite{groth} was used to build simple ring signatures and Zerocoin-style transactions, and was later extended to support accountable ring signatures more efficiently by Bootle \cite{bootle}.
-This proving system forms the basis of Lelantus \cite{lelantus}, which extends the Zerocoin-style transaction model of \cite{groth} by using multiple-base Pedersen commitments to incorporate amounts alongside serial numbers; a modification to the proofs shows balance, and multiple proofs are needed for typical transactions.
-However, Lelantus transactions allow a transaction sender to later identify when the recipient spends their funds; a mitigation to this solves the tracing problem, but at the cost of eliminating a useful one-time addressing construction that ensures recipient anonymity.
-The same proving system in \cite{groth} is used in Triptych \cite{triptych}, a multi-dimensional linkable ring signature construction that can be used to build confidential transactions similarly to \cite{ringct}; Triptych notably supports one-time addressing and arbitrary amounts, while still requiring the use of multiple proofs for transactions spending multiple transaction outputs.
-Interestingly, recent independent work extends \cite{groth} to support proofs on multiple commitments in a single list (as we also introduce below), with a particular application to Zether \cite{zether}; however, this uses a different approach than we take here, and seems to result in larger proofs.
+Linkable ring signature (LRS) constructions were first introduced in \cite{liu2004linkable}; in the context of transaction protocols, linkable ring signatures are the basis for anonymous transaction authentication.
+Linkable ring signatures guarantee that two signatures with the same ring on arbitrary messages can be publicly linked if signed using the same key.
+An implementation is presented in \cite{liu2004linkable} in the discrete logarithm setting; that implementation functions for similar reasons as Schnorr signatures in \cite{schnorr1991efficient}.
 
-The Bulletproofs \cite{bulletproofs} proving system uses an inner-product compression method to build range and circuit satisfiability proofs with logarithmic size scaling.
-Besides an increasingly widespread deployment for commitment range proofs, the underlying structure of Bulletproofs is used to construct more specialized proving systems for confidential transactions.
-Omniring \cite{omniring} uses this method to build transactions that demonstrate spend authorization for multiple signer-ambiguous transaction inputs within a single proof, while directly integrating range proving.
-The result is very small proofs; however, verification is slower than other approaches, and requirements for unique group generators mean such proofs cannot be verified in efficient batches.
-RingCT 3.0 \cite{rct3} also uses a Bulletproof-style construction.
-In an early version, transactions required separate proofs for multiple inputs; while an update incorporates a single proof for all inputs to a transaction, it also requires that the number of inputs be padded to a power of two, which can yield poor verification complexity.
+The signature linking tags in \cite{liu2004linkable} are unsuitable for applications where signatures must be linked key-by-key, not ring-by-ring (such as for ``double-signing'' protection in a setting where users generate new keys over time and select \textit{ad hoc} ring members).
+Resistance to double-signing attempts is ensured using linking tags as described in \cite{van2013cryptonote} (therein called key images).
+More recent work of \cite{noether2016ring} extends the approach of \cite{liu2004linkable} to enable an anonymous confidential transaction model with \textit{ad hoc} ring member selection.
+In \cite{noether2016ring}, transaction amounts are replaced with Pedersen commitments to amounts together with range proofs.
+Signatures are constructed from key vectors including differences of amount commitments as one of the keys.
+However, the proofs in \cite{noether2016ring} are informal and not based on rigorous security models.
 
-\subsection{Our contribution}
-We extend the proving system in Triptych \cite{triptych} in two significant ways, which we call Arcturus.
-First, we enable the prover to show knowledge of multiple signing keys in a single proof simultaneously using one set of combined proof elements; unlike \cite{rct3}, our modification admits any number of transaction inputs without limitations.
-We retain the verifiable random function evaluation that produces linking tags, which are required for the detection of repeat signing with the same commitment opening across proofs.
-Second, we show Pedersen commitment value balance directly within the same proof; in particular, we show that a particular combination of input and output commitments sums to a commitment to zero.
-We note that the soundness of the resulting proving system depends on a novel dual discrete-logarithm hardness assumption that we are not able to reduce to a standard hardness assumption; while we consider this novel assumption reasonable, it is untested.
+Alternatives to ring signatures like more general zero-knowledge proving systems typically require a trusted party to honestly perform a setup process (as in \cite{groth,ben2014succinct,groth2018updatable}) or lack practical efficiency for large circuits (as in \cite{bulletproofs}), meaning that such systems may not be appropriate for distributed ledger applications.
+However, more recent approaches such as \cite{hoffmann2019efficient} show both improvements to the trust requirement as well as improvements in efficiency.
 
-Taken together, these changes have application to a transaction protocol for efficient use in blockchain confidential transactions that does not require any trusted setup process.
-A transaction can sign for multiple signer-ambiguous inputs and prove that the transaction balances using a single proof, a major improvement to currently-deployed constructions that require multiple proofs and separate auxiliary Pedersen amount commitments.
-Further, we use actual blockchain data from the Monero digital asset project to directly compare the overall size and verification time of Arcturus to that of Triptych and two separate RingCT 3.0 constructions.
-We find that Arcturus provides superior verification performance compared to other trust-free confidential transaction constructions, with competitive size scaling.
+Definitions of existential unforgeability for ring signature schemes from \cite{bender2006ring} are generally inappropriate for LRS.
+These definitions ensure that forgeries appear to be computed from uncorrupted challenge keys by restricting choices of anonymity set members and oracle queries.
+We can do better with linkability.
+
+The idea of existential unforgeability in usual digital signatures is to task an algorithm to produce any valid, non-oracle signature on any message such that the signature appears to be signed by an uncorrupted challenge key.
+The clear analogue for LRS schemes is to task an algorithm to produce any valid, non-oracle signature on any message such that the signature links to a challenge signature computed from an uncorrupted challenge key.
+Contrast this intuition with the definition of unforgeability for usual ring signatures with respect to insider corruption from \cite{bender2006ring}, which does not count a valid signature $\sigma$ with an anonymity set $Q$ as a forgery if any key in $Q$ is corrupt or not a challenge key, or a signing oracle has been queried with the same anonymity set $Q$ and message.
+This leads to two problems.
+
+The first problem is due to the disqualification of a purported forgery if there are any adversarially-selected keys or corrupted challenge keys in the anonymity set.
+Such a signature that links with an uncorrupted challenge key does not count as a forgery.
+In ring signature schemes without linkability, this restriction seems requisite to ensure that the signature appears to be signed by an uncorrupted challenge key.
+In applications like signer-ambiguous transaction protocols that use anonymity sets selected \textit{ad hoc}, anonymity set members should be assumed to be adversarially generated.
+Definitions of unforgeability should take this into account.
+
+The second problem is due to the signing oracle restriction in this definition.
+An adversary could generate a valid, non-oracle signature re-using the same message and anonymity set as some challenge signature generated by the oracle.
+A verifier who has found more than one valid non-oracle signature on the same message with the same anonymity set, under this definition, can only conclude that at least one anonymity set member signed at least one of the signatures.
+This allows a malicious Mallory-in-the-middle to collect outgoing honest signatures on some honest messages and attempt to construct clone signatures on these honest messages.
+A sender attempting to assert culpability over a signature could then be in danger of being unable to reconstruct a signature sent to some receiver.
+
+These problems seem to interfere with the spirit behind existential unforgeability with insider corruption from \cite{bender2006ring}: the signature is valid, not produced by an oracle, appears to have been computed from an uncorrupted challenge key, and yet is not considered a forgery.
+
+\subsection{Our Contribution}
+
+We relax the notion of successful forgeries to require only linking with uncorrupted challenge keys, obtaining a notion of unforgeability for linkable ring signatures that is equivalent to the definition of non-slanderability in \cite{au2006short}.
+Non-slanderability allows for adversaries who can query a signature oracle with any anonymity set, even adversarially-selected anonymity sets.
+This models an extremely persuasive adversary who can convince users to sign messages with adversarially-selected anonymity sets.
+We show that non-slanderability implies unforgeability with respect to insider corruption from \cite{bender2006ring}.
+
+We also present a Schnorr-like linkable ring signature scheme we call $d$-CLSAG that exploits key aggregation techniques to improve signature size.
+We describe an application for the $d$-CLSAG scheme in ring confidential transaction protocols, allowing transactions consisting of $d-1$ distinct assets simultaneously.
+We prove that $d$-CLSAG is linkable assuming collision resistance in key aggregation and linkably anonymous assuming a variant of the decisional Diffie-Hellman game is hard.
+Recall that Schnorr-like signature schemes do not cleanly reduce to the discrete logarithm assumption (\textit{c.f.}\ \cite{paillier2005discrete}), generally are only secure up to the (relatively flimsier) one-more hardness assumptions, and proof techniques typically exploit programmable random oracles with forking lemmata, leading to weak bounds.
+We use the general forking lemma to prove that $d$-CLSAG is non-slanderable assuming a $\kappa$-one-more variation of the discrete logarithm game is hard.
 
 \section{Preliminaries}
-\subsection{Public parameters}
-Let $\G$ be a cyclic group in which the discrete logarithm problem is hard, and let $\F$ be its scalar field.
-Let $\hs: \{0,1\}^* \to \F$ and $\hp: \{0,1\}^* \to \G$ be cryptographic hash functions.
-Let $N = n^m$ be a positive integer, where $m > 1$ (for our construction, we will use $n = 2$).
-Assume that $G$, $H$, $U$, and any point of the form $G_i$ or $H_i$ (possibly with multiple indices) are uniformly random generators of $\G$ whose discrete logarithm relationship to each other is unknown.
-Note that all such generators may be produced using public randomness; for example, the use of a suitable hash function with domain separation may be appropriate.
-All such public parameters are assumed to comprise a global reference string known to all players; in particular, we generally exclude explicit reference to public parameters from algorithm definitions and Fiat-Shamir transcript hashes for readability.
 
-\subsection{Tensor commitment}
-Let $\com$ be an additively homomorphic commitment scheme that is perfectly hiding and (at least) computationally binding.
-In this work, we assume use of a simple extension to the Pedersen commitment scheme: for $x,r \in \F$, define $\com(x,r) \equiv rG + xH$ to be the commitment of the value $x$ with randomness $r$.
+Let $\lambda$ be a security parameter and $1 \leq q, \eta, \kappa \in poly(\lambda)$.
+Let $\G = \langle G \rangle$ denote a finite cyclic group over a finite field $\F$ for some prime $p$, with group generator $G$.
+Let $\Hs:\left\{0,1\right\}^* \to \F$ and $\Hp:\left\{0,1\right\}^* \to \G$ be two independent cryptographic hash functions modeled as random oracles.
 
-For a three-dimensional tensor $f \equiv (f_{i,j,k}) \subset \F$ and blinding factor $r \in \F$, define the Pedersen tensor commitment
-$$\com(f,r) \equiv rG + \sum_{i,j,k} f_{i,j,k} G_{i,j,k}$$
-using fixed independent generators as described above.
+If there exists a function $f$ that is negligible in some parameter $\lambda$, and there exists $\lambda$-dependent events $A, B$ such that $\left|\prob\left[A\right] - \prob\left[B\right]\right| \leq f(\lambda)$, we denote this $\prob\left[A\right] \approx \prob\left[B\right]$.
+An event $A$ such that $\prob\left[A\right] \approx 0$ is said to be negligible in $\lambda$ (or to occur with probability at most negligible in $\lambda$).
+The complement of an event $A$ is denoted $\overline{A}$.
+For the field $\F$, we denote the non-zero elements $\F^* := \F\setminus \left\{0\right\}$.
+For a finite set $S$, we define $S^*$ by interpreting $S$ as a list of letters that generate the free monoid $S^*$.
+For example, $\left\{0,1\right\}^*$ consists of all finite-length bitstrings.
 
-Operations on tensors are assumed to be performed componentwise; for example, if $f \equiv (f_{i,j,k})$ and $g \equiv (g_{i,j,k})$ are such tensors over $\F$, then $f + g \equiv (f_{i,j,k} + g_{i,j,k})$, and so forth.
+For a set $S$, we define $\mathcal{P}(S)$ as the power set of $S$, i.e.\ the set of all subsets of $S$.
 
-\subsection{Other notation}
-For integers or field elements $i,j$, the Kronecker delta function $\delta(i,j)$ evaluates to $1$ if $i=j$ and $0$ otherwise, where the output is taken to be in the appropriate set.
+We denote vectors with bold, i.e.\ for a sequence $x_i \in \F$ for $i = 0, \ldots, n-1$, we denote the tuple $(x_0, \ldots, x_{n-1})$ with $\textbf{x}$.
+We denote the Hadamard product between vectors with $\textbf{x} \circ \textbf{y} = (x_i y_i)_i$.
+We begin all indices at $0$ to avoid all ambiguity.
+We use the notation $[n]$ to mean the set $\{0,\ldots,n-1\}$.
 
-We sometimes use index subscript notation of the form $i_j$ to indicate the $j$ digit of $i$, where such a decomposition of $i$ is taken base $n$ with padded length $m$:
-$$\sum_{j=0}^{m-1} i_j n^j = i$$
-This notation will be specified explicitly where confusion may occur.
+\section{Definitions}
 
-\subsection{Sigma protocols}
-For a given relation $\mathcal{R}$, a sigma protocol for $\mathcal{R}$ is an interactive challenge-response protocol between a prover and verifier, where the prover wishes to convince the verifier it knows a witness corresponding to a statement in $\mathcal{R}$.
+\subsection{Hardness Assumptions}\label{sec:hardness}
 
-A sigma protocol is complete, sound, and zero-knowledge.
-These definitions are well known and found, for example, in \cite{groth}.
-Essentially, these properties are:
+We begin by noting that if $\left\{\mu_i: \F^d \to \F\right\}_{i=0}^{d-1}$ are functions selected uniformly at random, then the composite function $\mu: \F^d \to \F$ defined by mapping $\textbf{x} \mapsto \sum_i \mu_i(\textbf{x}) x_i$ has uniformly distributed output and is a collision- and preimage-resistant function.
+We use this property later when considering linkability and linkable anonymity.
+
+The following game is equivalent\footnote{A usual $\kappa$-one-more discrete logarithm solver can succeed at the game in Definition \ref{def:komdl} with the same probability and some extra time by merely summing solutions.
+A solver of the game in Definition \ref{def:komdl} can use their discrete logarithm knowledge to solve for an otherwise uncorrupted challenge key with the same probability and some extra time.} to the usual $\kappa$-one-more discrete logarithm game under the random oracle model.
+
+\begin{definition}[$\kappa$-One-More Linear Combination Discrete Logarithm]\label{def:komdl}
+
+Let $\kappa \geq 1$.
+We say any PPT algorithm $\A$ that can succeed at the following game in time at most $t$ and with success probability at least $\epsilon$ is a $(t, \epsilon, q)$-solver of the $\kappa$-one-more discrete logarithm of linear combinations problem in $\G$ (where $k < q$).
+\begin{enumerate}
+\item Challenger draws $\left\{sk_i\right\}_{i=0}^{q-1} \subseteq \F$ at random, computes $pk_i := sk_i \cdot G$, sends $S := \left\{pk_i\right\}_{i=0}^{q-1}$ to $\A$.
+
+\item $\A$ is granted access to a corruption oracle $\texttt{CO}$ which takes as input a public key $pk_i \in S$ and produces as output the corresponding private key $sk_i$.
+Corrupted keys are recorded in a table $C$.
+
+\item $\A$ outputs some $w \in \F^*$, a sequence of field elements $\left\{h_j\right\}_{j=0}^{\kappa} \subseteq \F \setminus \left\{0\right\}$, and a subset of challenger keys $\left\{pk^*_j\right\}_{j=0}^{\kappa} \subseteq \left\{pk_i\right\}_{i=0}^{q-1}$, succeeding if and only if $w \cdot G = \sum_{j=0}^{\kappa} h_j \cdot pk^*_j$ and
+ $\A$ queried $\texttt{CO}$ no more than $\kappa$ times.
+
+\end{enumerate}
+We say that the discrete logarithms of linear combinations are computationally hard to compute in $\G$ if any $(t, \epsilon, q)$-solver of this game has an advantage  that is $\epsilon$ negligible in $q$.
+\end{definition}
+
+For an algorithm $\A$ that takes as input a random tape $\rho$, a sequence of random oracle queries $\textbf{h}$ and some input $inp$ and produces $(out, idx) \leftarrow \A(\rho, \textbf{h}, inp)$ as output, the general forking algorithm works as follows.
+
+\begin{enumerate}[(1)]
+\item  Pick a random tape $\rho$ for $\A$ and two sequences of random oracle queries $\textbf{h} = \left\{h_0, h_1, \ldots\right\}$ and $\textbf{h}^\prime = \left\{h_0^\prime, h_1^\prime, \ldots\right\}$.
+
+\item Execute $(out, idx) \leftarrow \A(\rho, \textbf{h}, inp)$.
+
+\item Set $j := idx$ and glue the oracle queries $\textbf{h}$, $\textbf{h}^\prime$ together \[\textbf{h}^* = \left\{h_0, h_1, \ldots, h_{idx - 1}, h_{idx}^\prime, h_{idx+1}^\prime, \ldots, \right\}.\]
+
+\item Execute $(out^*, idx^*) \leftarrow \A(\rho, \textbf{h}^*, inp)$.
+
+\item If $idx \neq idx^*$ or $h_{idx} = h_{idx}^\prime$, output $\bot$ and terminate. Otherwise, output $(out, out^\prime, idx)$.
+\end{enumerate}
+
+This algorithm is precisely the algorithm $\mathcal{F}^{\A}$ in the following lemma.
+
+\begin{lemma}[General Forking Lemma]\label{lem:fork}
+Let $1 \leq \eta \in \text{poly}(\lambda)$.
+Let $\A$ be any PPT algorithm which takes as input some tuple $x_\A = (x, \textbf{h})$ where we let $\textbf{h} = (h_0, h_1, \ldots, h_{q-1})$ be a sequence of oracle query responses ($\eta$-bit strings) and returns as output $y_{\A}$ either a distinguished failure symbol $\bot$ or a pair $(\textit{idx}, y)$ where $\text{idx} \in [q]^2$ and $y$ is some output.
+Let $\epsilon_{\A}$ denote the probability that $\A$ does not output $\bot_{\A}$ (where this probability is taken over all random coins of $\A$, the distribution of $x$, and all choices $\textbf{h}$).
+Let $\mathcal{F} = \mathcal{F}^{\A}$ be a forking algorithm for $\A$.
+The accepting probability of $\mathcal{F}$ satisfies $\epsilon_{\mathcal{F}} \geq \epsilon_{\A} \left(\frac{\epsilon_{\A}}{q} - \frac{1}{2^\eta}\right)$.
+\end{lemma}
+
+We use the next game to relate the classic decisional Diffie-Hellman hardness assumption to a random oracle construction that will be useful later when introducing a definition of linkable anonymity.
+Detailed properties of this type of construction relating to pseudorandomness and invertibility are formalized and discussed further in \cite{omniring}.
+
+\begin{definition}[Random Oracle Decisional Diffie-Hellman]\label{def:rom-ddh}
+We say any PPT algorithm $\A$ that can succeed at the following game in time at most $t$ with advantage least $\epsilon > 0$ over random chance is a $(t,\epsilon,q)$-solver of the random oracle decisional Diffie-Hellman game.
 \begin{itemize}
-\item \textit{Perfectly complete}: For a witness to a statement in $\mathcal{R}$, an honest prover always convinces an honest verifier of the validity.
-\item \textit{Special sound}: Given a statement in $\mathcal{R}$, if the prover can produce valid proof transcripts in response to multiple verifier challenges, then it is possible to extract a witness for the statement from the transcripts.
-\item \textit{Special honest-verifier zero knowledge}: Given a statement and known verifier challenge, it is possible to produce a simulated transcript without knowledge of a corresponding valid witness.
+\item The challenger chooses a bit $b \in \{0,1\}$ uniformly at random.
+\item If $b = 0$, then the challenger chooses $\{r_i\}_{i=0}^{q-1}$ from $\F$ uniformly at random, sets $$S := \{(R_i,R_i',R_i'')\}_{i=0}^{q-1} = \{(r_iG,\Hp(r_iG),r_i\Hp(r_iG))\}_{i=0}^{q-1},$$ and sends $S$ to $\A$.
+\item If instead $b = 1$, then the challenger chooses $\{(r_i,r_i'')\}_{i=0}^{q-1}$ from $\F^2$ uniformly at random, sets $$S := \{(R_i,R_i',R_i'')\}_{i=0}^{q-1} = \{(r_iG,\Hp(r_iG),r_i''G)\}_{i=0}^{q-1},$$ and sends $S$ to $\A$.
+\item $\A$ is granted access to the random oracle $\Hp$.
+\item $\A$ returns a bit $b' \in \{0,1\}$; we say $\A$ succeeds if and only if $b' = b$.
 \end{itemize}
-Sigma protocols can be made non-interactive by replacing random verifier challenges with hash-based transcript challenges under the random oracle model; this approach is called the Fiat-Shamir heuristic \cite{fiat}.
+We say that random oracle Diffie-Hellman group elements are hard to distinguish from random in $\G$ if any $(t,\epsilon,q)$-solver of this game has negligible advantage $\epsilon$.
+\end{definition}
 
-\subsection{Hardness assumption}
-We now define a novel cryptographic hardness assumption that is used later to show the soundness of our construction.
+\begin{remark}
+We assume that if the classic decisional Diffie-Hellman (DDH) game is hard in $\G$, then so is the RO-DDH game.
+Indeed, recall that DDH asks an adversary to distinguish between distributions of tuples of the form $(rG,r'G,rr'G)$ and $(rG,r'G,r''G)$.
+If DDH is hard in $\G$, then distributions of tuples of these forms are indistinguishable.
+Since $\Hp$ is a random oracle whose output is independent of input, then distributions of tuples of the form $(rG,\Hp(rG),r''G)$ and $(rG,r'G,r''G)$ are identical.
+Similarly, distributions of tuples of the form $(rG,\Hp(rG),r\Hp(rG))$ and $(rG,\Hp(rG),r''G)$ are identical.
+Finally, random self-reducibility of the classic DDH game means that solving one instance of the problem has complexity no worse than solving a sequence of random instances of the problem.
+\end{remark}
 
-\begin{definition}[Dual-target discrete logarithm problem]
-\label{def:dual}
-Let $\G$ be a group in which the discrete logarithm problem is hard, and let $\F$ be its scalar field.
-Let $n > 0$.
-Consider the following game between a challenger and a probabilistic polynomial-time player $\A$:
+\subsection{Linkable Ring Signatures}
+
+\begin{definition}\label{def:lrs} A linkable ring signature (LRS) scheme $\Pi_{LRS}$ is a tuple of PPT algorithms $(\texttt{SETUP}, \texttt{KEYGEN}, \texttt{SIGN}, \texttt{VERIFY}, \texttt{LINK})$ satisfying the following set of constraints:
 \begin{itemize}
-\item The challenger chooses $G,H \in \G$ uniformly at random and sends both to $\A$.
-\item $\A$ chooses and returns sets $\{G_i\}_{i=0}^{n-1},\{H_i\}_{i=0}^{n-1} \subset \G$ to the challenger.
-\item The challenger chooses a set $\{\mu_i\}_{i=0}^{n-1} \subset \F$ uniformly at random and sends it to $\A$.
-\item $\A$ chooses and returns a set $\{x_i\}_{i=0}^{n-1} \subset \F$ to the challenger.
+\item $\texttt{SETUP}$ takes as input a security parameter $\lambda$ and produces as output some public setup parameters $\rho$.
+
+\item $\texttt{KEYGEN}$ is a randomized; it takes as input $(\lambda, \rho)$ and outputs a private-public keypair $(sk, pk)$.
+
+\item $\texttt{SIGN}$ is randomized; it takes as input $(\lambda, \rho)$ and a triple $(m, Q, sk)$ and outputs a signature $\sigma$ or a failure symbol $\bot$.
+Here $m$ is a message, $Q$ is an anonymity set of public keys $Q = \left\{pk_0, pk_1, ..., pk_{n-1}\right\}$, and $sk$ is a private key.
+
+\item $\texttt{VERIFY}$ takes as input $(\lambda, \rho)$ and a triple $(m, Q, \sigma)$ and outputs a bit $b$.
+Here $m$ is a message, $Q$ is an anonymity set of public keys $Q = \left\{pk_0, pk_1, ..., pk_{n-1}\right\}$, and $\sigma$ is a signature.
+
+\item $\texttt{LINK}$ takes as input $(\lambda, \rho)$, a pair of triples $(m, Q, \sigma)$, $(m^*, Q^*, \sigma^*)$, and outputs a bit $b$.
+Here $m, m^*$ are messages, $Q, Q^*$ are anonymity sets of public keys, and $\sigma, \sigma^*$ are signatures.
 \end{itemize}
-We say that $\A$ wins the $(n,\epsilon,t)$-dual-target discrete logarithm game if, in time less than $t$ and with probability at least $\epsilon$, the following are true:
+We say a triple of the form $(m, Q, \sigma)$ (that is to say, a triple suitable for use as input in $\texttt{VERIFY}$ and $\texttt{LINK}$) is a \textit{signature triple}.
+We say $\Pi_{LRS}$ is a $d$-LRS if the dimension of private and public keys is $d \geq 1$ and anonymity sets can be described as $d\times n$ matrices.
+\end{definition}
+
+For use in a later concrete instantiation, we assume $\rho$ may include (implicitly or explicitly) descriptions of a private key space $\mathcal{SK}$, a public key space $\mathcal{PK}$, a signature space $\mathcal{SIG}$, a map $\phi: \mathcal{SK} \to \mathcal{PK}$, and a family of hash functions (modeled as random oracles) $\mathcal{H}$ from which we can draw $\Hs$ and $\Hp$.
+For example, with a finite cyclic group $\G$ over a finite field $\F$, for two hash functions $H^s:\left\{0,1\right\}^* \to \F$ and $H^p:\left\{0,1\right\}^* \to \G$, a Schnorr-like ring signature scheme such as \cite{liu2004linkable} would pack into $\rho$ the descriptions $\mathcal{SK} = \F^*$, $\mathcal{PK} = \G$, $\mathcal{SIG} = \F^n$, and a generator $G \in \G$ (which is sufficient to specify the one-way map $\phi: \F^* \to \G$ defined by $x \mapsto xG$).
+Note each algorithm in an LRS scheme takes $(\lambda, \rho)$ as input; in the sequel we exclude these from notation for LRS schemes, taking their use as implicit.
+
+Note we do not allow a LRS scheme to be correct if the scheme allows anonymity multisets $Q$.
+
+\begin{definition}\label{def:lrs-correct}
+Let $b\in \left\{0,1\right\}$, $sk, sk^* \in \mathcal{SK}$, let $Q$, $Q^* \subset \mathcal{PK}$ be sets, let $m, m^*, m^\prime$ be messages, let $\sigma, \sigma^*, \sigma^\prime \in \mathcal{SIG}$ be any purported signatures.
+Define the following events.
 \begin{itemize}
-\item $\sumi \mu_i \left( G_i - x_iG \right) = 0$
-\item $\sumi \mu_i \left( H - x_iH_i \right) = 0$
-\item There exists an index $0 \leq i < n$ such that either $x_iG \neq G_i$ or $x_iH_i \neq H$.
+\item $E_1(sk, pk)$ is the event that some $(sk, pk) \leftarrow \texttt{KEYGEN}$.
+
+\item $E_2(sk, Q)$ is the event that $\phi(sk) \in Q$.
+
+\item $E_3(m, Q, \sigma)$ is the event that $\texttt{VERIFY}(m, Q, \sigma) = 1$.
+
+\item $E_4(b, m, m^*, m^\prime, Q, Q^*, Q^\prime, \sigma, \sigma^*, \sigma^\prime)$ is the event that \[b = \texttt{LINK}((m, Q, \sigma), (m^*, Q^*, \sigma^*)) = \texttt{LINK}((m^*, Q^*, \sigma^*), (m^\prime, Q^\prime, \sigma^\prime)).\]
+
+\item $E_5(m, m^*, Q, Q^*, \sigma, \sigma^*, sk)$ is the event that \[\phi(sk) \in Q \cap Q^*\text{, }\sigma \leftarrow \texttt{SIGN}(m, Q, sk)\text{, and }\sigma^* \leftarrow \texttt{SIGN}(m^*, Q^*, sk).\]
+
+\item $E_6(m, m^*, Q, Q^*, \sigma, \sigma^*, sk, sk^*)$ is the event that  \[\sigma \leftarrow \texttt{SIGN}(m, Q, sk)\text{, }\sigma^* \leftarrow \texttt{SIGN}(m^*, Q^*, sk^*)\text{, and }sk \neq sk^*.\]
+\end{itemize}
+We say $\Pi_{LRS}$ is correct if all of the following properties hold, where these probabilities are computed over all random coins and over all choices of hash function.
+
+\begin{enumerate}[(i)]
+\item Valid keys map properly: $$\prob\left[ \phi(sk) = pk \mid E_1(sk, pk) \right] \approx 1$$
+
+\item Signing fails with a key not contained in the ring: $$\prob\left[ \texttt{SIGN}(m, Q, sk) = \bot \mid \overline{E_2}(sk, Q)  \right] \approx 1$$
+
+\item Verification succeeds with a valid signature: $$\prob\left[ \texttt{VERIFY}(m, Q, \texttt{SIGN}(m, Q, sk)) = 1 \mid E_2(sk, Q) \right] \approx 1$$
+
+\item A valid signature links to itself: $$\prob\left[\texttt{LINK}((m, Q, \sigma), (m, Q, \sigma)) = 1 \mid E_3(m, Q, \sigma)\right] \approx 1$$
+
+\item Linking is commutative: $${\small \prob\left[\texttt{LINK}((m, Q, \sigma), (m^*, Q^*, \sigma^*)) = \texttt{LINK}((m^*, Q^*, \sigma^*), (m, Q, \sigma))\right] \approx 1}$$
+
+\item Linking is transitive: $${\small \prob\left[b = \texttt{LINK}((m, Q, \sigma), (m^\prime, Q^\prime, \sigma^\prime)) \mid E_4(b, m, m^*, m^\prime, Q, Q^*, Q^\prime, \sigma, \sigma^*, \sigma^\prime)\right] \approx 1}$$
+
+\item Reuse of a signing key implies linking: $$\prob\left[ \texttt{LINK}((m, Q, \sigma), (m^*, Q^*, \sigma^*)) = 1 \mid E_5(m, m^*, Q, Q^*, \sigma, \sigma^*, sk) \right] \approx 1$$
+
+\item Use of distinct signing keys implies no linking: $${\small \prob\left[ \texttt{LINK}((m, Q, \sigma), (m^*, Q^*, \sigma^*)) = 0 \mid E_6(m, m^*, Q, Q^*, \sigma, \sigma^*, sk, sk^*) \right] \approx 1}$$
+\end{enumerate}
+\end{definition}
+
+\subsection{Linkability}
+
+We use two distinct, but related, definitions of linkability.
+The first is Definition 5 from \cite{au2006short}, which we term \textit{ACST linkability} (after the authors' initials).
+This definition allows signing oracle queries with any anonymity sets $Q$ consisting of at least one challenge key (which can be simulated via backpatching).
+This definition also allows the challenger to succeed at the linkability game using signature triples $(m, Q, \sigma)$, $(m^*, Q^*, \sigma^*)$ that have semi-corrupted anonymity sets $Q, Q^*$ (just so long as the keys in $Q \cup Q^*$ have not been tampered with too severely).
+The second is Definition 8 from \cite{backes2019ring}, we we term \textit{pigeonhole linkability} after its similarity to the pigeonhole principle.
+This definition allows the adversary total control over key selection, declaring success when they produce more unlinked ring signatures than total ring members.
+Such an adversary doesn't need key generation, corruption, or signature oracle access.
+
+\begin{definition}[ACST Linkability With an Adversarial Key]\label{def:acst-link-adv}
+We say any PPT algorithm $\A$ that can succeed at the following game in time at most $t$ and with success probability at least $\epsilon$ is a $(t, \epsilon, q)$-solver of ACST linkability.
+
+\begin{enumerate}
+\item Challenger draws $\left\{(sk_i, pk_i)\right\}_{i=0}^{q-1}$ from $\texttt{KEYGEN}$ and sends the challenge public keys $S = \left\{pk_i\right\}_{i=0}^{q-1}$ to $\A$.
+
+\item $\A$ is granted \texttt{SO} and \texttt{CO} access.
+    \begin{itemize}
+    \item \texttt{CO} takes as input a public key $pk$.
+If $pk \in S$, $\texttt{CO}$ outputs the corresponding private key $sk$.
+Otherwise, $\texttt{CO}$ outputs a failure symbol, $\bot$.
+Corrupted keys are tracked in a table $C$.
+
+    \item \texttt{SO} operates as follows:
+        \begin{enumerate}[(i)]
+        \item Takes as input a message $m$, an anonymity set $Q = \left\{pk^\prime_i\right\}_{i=0}^{n-1}$, and an index $l$. (Note that we do not specifically require $Q \subset S$ here.)
+
+        \item If $0 > l$ or $l \geq n$ or if $pk^\prime_l \notin S$, \texttt{SO} outputs a failure symbol $\bot$.
+
+        \item Otherwise, there exists some $i$ such that $pk^\prime_l = pk_i \in S$.
+\texttt{SO} retrieves the private key $sk_i$ and outputs a valid signature triple $(m, Q, \sigma)$ such that $\sigma \leftarrow \texttt{SIGN}(m, Q, sk_i)$.
+        \end{enumerate}
+    \end{itemize}
+
+\item $\A$ outputs a pair of signature triples, $(m, Q, \sigma)$, $(m^*, Q^*, \sigma^*)$, succeeding if and only if all of the following conditions are satisfied.
+(Note that we do not specifically require $Q \subset S$ or $Q^* \subset S$ here.)
+    \begin{enumerate}[(i)]
+        \item $\texttt{VERIFY}(m, Q, \sigma) = \texttt{VERIFY}(m^*, Q^*, \sigma^*) = 1$
+        \item $\texttt{LINK}((m, Q, \sigma), (m^*, Q^*, \sigma^*)) = 0$
+        \item $\sigma, \sigma^*$ are not output from any $\texttt{SO}$ query.
+        \item $\left|(Q \cup Q^* ) \cap (C \cup \overline{S})\right| \leq 1$
+    \end{enumerate}
+\end{enumerate}
+We say that a scheme is \textit{ACST linkable} if every PPT algorithm $\A$ that is a $(t, \epsilon, q)$-solver ACST linkability game has a negligible acceptance probability $\epsilon$.
+\end{definition}
+
+\begin{definition}[$q$-Pigeonhole Linkability]\label{def:pig-link}
+We say any PPT algorithm $\A$ that can succeed at outputting $q$ public keys $\left\{pk_i\right\}_{i=0}^{q-1}$ and $q + 1$ valid, unlinked signature triples $\left\{(m_j, Q_j, \sigma_j)\right\}_{j=0}^{q}$ such that $\cup_j Q_j \subseteq \left\{pk_i\right\}_{i=0}^{q-1}$ in time at most $t$ and probability at least $\epsilon$ is a $(t, \epsilon, q)$-solver of pigeonhole linkability.
+We say that a scheme is $q$-\textit{pigeonhole linkable} if every PPT algorithm $\A$ that is a $(t, \epsilon, q)$-solver of $q$-pigeonhole linkability has a negligible acceptance probability $\epsilon$.
+(Note that the adversary is not granted signing or corruption oracle access here.)
+\end{definition}
+
+These definitions are distinct.
+Pigeonhole linkability does not necessarily imply ACST linkability.
+Indeed, a successful player of the game in Definition \ref{def:acst-link-adv} may only succeed with sufficiently large rings, in which case that player may only be used to succeed at the game of Definition \ref{def:pig-link} for a sufficiently large $q$.
+Similarly, ACST linkability may not imply pigeonhole linkability.
+A player of the game in Definition \ref{def:pig-link} that requires knowledge of many private keys may be too corruption-hungry to succeed at Definition \ref{def:acst-link-adv}.
+
+For a scheme that is pigeonhole linkable, Definition \ref{def:pig-link} says nothing about an adversary that can keep signing with one key multiple times to construct new unlinked signatures, just so long as they continue to use different anonymity sets.
+
+For a scheme that is ACST linkable, a user providing honest signatures to an adversary acts like a signature oracle, so the adversary could  attempt to construct a bad/cloned signature that links to some honest one (possibly with adversarially selected ring members), only ever outputting a single signature.
+Definition \ref{def:acst-link-adv} says nothing about such an attacker.
+This attacker could stand between Alice and Bob, provide cloned signatures to the Bob ostensibly signed by Alice, fooling him.
+When Alice eventually contacts Bob without the adversary in the middle, Alice would be unable to assert culpability over the cloned signatures.
+Bob concludes that $\sigma^*$ and $\sigma$ were signed by the same private key, despite that the adversary does not know the private key that generated $\sigma$.
+
+However, Definition \ref{def:pig-link} implies Definition \ref{def:acst-link-adv} under certain circumstances.
+For one (of many) examples, if there exists a $(t, \epsilon, 1)$-solver of the game in Definition \ref{def:acst-link-adv} that produces two signature triples $(m, Q, \sigma)$, $(m^\prime, Q^\prime, \sigma^\prime)$ such that $Q = Q^\prime$ and $\left|Q\right| = 1$, then $\A$ succeeds at Definition \ref{def:pig-link}.
+
+A more general look at the relationships between linkability definitions is beyond the scope of this work.
+Since neither definition is sufficient for our purposes alone and these definitions are distinct in general, we use both.
+
+\subsection{Unforgeability and Non-Slanderability}
+
+The idea of existential unforgeability in usual digital signatures is to task an algorithm to produce any valid, non-oracle signature on any message such that the signature appears to be signed by an uncorrupted challenge key.
+The clear analogue for LRS schemes is to task an algorithm to produce any valid, non-oracle signature on any message such that the signature links to a challenge signature computed from an uncorrupted challenge key.
+In fact, the implementation in Section \ref{sec:implementation} compares linking tags as if they were verification keys; in this sense, a forger is tasked to construct a valid signature with some verification keys to which they do not know the corresponding private key.
+We consider this to be a textbook forgery, and so we take these occurrences into account in our definition.
+Unlike the definitions for unforgeability used in \cite{au2006short} and \cite{backes2019ring}, linking is explicitly taken into account and the adversary is permitted to use corrupted keys.
+We later relate this definition to that of non-slanderability.
+
+\begin{definition}[Existential Unforgeability of Linkable Ring Signatures Against Adversarially-Selected Keys and Insider Corruption]\label{def:ex-unf}
+We say any PPT algorithm $\A$ that can succeed at the following game in time at most $t$ and with probability at least $\epsilon$ is a $(t, \epsilon, q)$-forger.
+\begin{enumerate}
+
+\item Challenger draws $\left\{(sk_i, pk_i)\right\}_{i=0}^{q-1}$ from \texttt{KEYGEN} and sets $S := \left\{pk_i\right\}_{i=0}^{q-1}$.
+For each $0 \leq i < q$, the challenger uniformly samples secret $\emptyset \neq \widetilde{Q}_i \in \mathcal{P}\left(S\right)$, defines $Q_i := \widetilde{Q}_i \cup \left\{pk_i\right\}$, retrieves the index $l_i$ such that $pk_{i} \in Q_i \cap S$ has index $l_i$ in $Q_i$, samples secret random messages $\left\{m_i\right\}_{i=0}^{q-1}$, and computes secret challenge signatures $\sigma_i \leftarrow \texttt{SIGN}(m_i, Q_i, sk_i)$.
+Challenger sends $S$ to $\A$.
+\item Challenger grants \texttt{SO} and \texttt{CO} access to \A:
+    \begin{itemize}
+    \item \texttt{CO} takes as input a challenge public key $pk_i \in S$ and produces as output the corresponding private key $sk_i$, keeping a list of all corrupted public keys in an internal table $C$.
+
+    \item \texttt{SO} operates as follows:
+        \begin{enumerate}[(i)]
+        \item Takes as input a message $m$, an anonymity set $Q$, and an index $l$.
+
+        \item If the key at index $l$ in $Q$ is not a challenge public key from $S$, \texttt{SO} outputs a failure symbol $\bot$.
+
+        \item Otherwise, \texttt{SO} retrieves the index $i$ such that $pk_{i} \in Q \cap S$ has index $l$ in $Q$, retrieves the corresponding private key $sk_{i}$, and outputs a signature $\sigma \leftarrow \texttt{SIGN}(m, Q, sk_{i})$.
+        \end{enumerate}
+    \end{itemize}
+
+\item $\A$ outputs a message $m$, a ring $Q$, a signature $\sigma$, succeeding if and only if:
+    \begin{enumerate}[(i)]
+    \item $\texttt{VERIFY}(m, Q, \sigma) = 1$,
+
+    \item there does not exist a query made to $\texttt{SO}$ whose output is $\sigma$,
+
+    \item there exists $i \in [0,q)$ such that ${\small \texttt{LINK}((m, Q, \sigma), (m_i, Q_i, \sigma_i)) = 1}$ and $pk_i \in S \cap Q \setminus C$.
+    \end{enumerate}
+\end{enumerate}
+Moreover, we say that a linkable ring signature scheme is \textit{unforgeable} if every $(t, \epsilon, q)$-solver of this game has a negligible acceptance probability $\epsilon$.
+\end{definition}
+
+\begin{remark}
+Access to a corruption oracle in this unforgeability definition is one reason security reduces (weakly) to the $\kappa$-one-more discrete logarithm problem, not the usual discrete logarithm problem: an algorithm executing a forgery algorithm in a black box cannot simulate the corruption oracle for the forgery without, itself, gaining corruption oracle access or without resorting to the generic group model.
+\end{remark}
+
+\begin{remark}
+If \A is an algorithm that produces signatures from an LRS satisfying Definition \ref{def:ex-unf}, then (except with negligible probability), the signatures aren't forgeries, so some property 3(i)-3(iii) must be violated.
+If the signature is valid and not from an oracle query, then 3(iii) fails.
+In particular, for an LRS scheme satisfying Definition \ref{def:ex-unf}, if an algorithm produces a valid non-oracle triple $(m, Q, \sigma)$ that links to a challenge key in $Q$, then that challenge key has been corrupted.
+\end{remark}
+
+Non-slanderability is introduced in \cite{tsang2004separable}.
+This definition is refined twice in \cite{au2006short}, allowing \A to succeed whenever it publishes any signature that links with any signature from a query $\A$ made to $\texttt{SO}$, excepting certain conditions.
+We modify the definition from \cite{au2006short} to allow signing oracle queries with anonymity sets containing adversarially selected members.
+
+\begin{definition}[Chosen-Target Non-Slanderability Against Adversarial Keys and Insider Corruption]\label{def:acst-nonsl}
+We say any PPT algorithm $\A$ that can succeed at the following game in time at most $t$ and with probability at least $\epsilon$ is a $(t, \epsilon, q)$-solver of non-slanderability against adversarially chosen keys.
+\begin{enumerate}
+\item Challenger draws $\left\{(sk_i, pk_i)\right\}_{i=0}^{q-1}$ from $\texttt{KEYGEN}$ and sends the challenge public keys $S = \left\{pk_i\right\}_{i=0}^{q-1}$ to \A.
+
+\item A is granted \texttt{SO} and \texttt{CO} access just as in Definition \ref{def:ex-unf}.
+
+\item A outputs a triple $(m, Q, \sigma)$, succeeding if and only if:
+    \begin{enumerate}[(i)]
+    \item $\texttt{VERIFY}(m, Q, \sigma) = 1$, and
+
+    \item there does not exist a query made to $\texttt{SO}$ whose output is $\sigma$, and
+
+    \item there exists a query made to $\texttt{SO}$, say $\sigma^* \leftarrow \texttt{SO}(m^*, Q^*, l^*)$, such that
+        \begin{enumerate}[(a)]
+        \item $\texttt{LINK}((m, Q, \sigma), (m^*, Q^*, \sigma^*)) = 1$, and
+
+        \item $pk^*_{l^*} \in S \cap Q^* \cap Q \setminus C$.
+        \end{enumerate}
+    \end{enumerate}
+\end{enumerate}
+Moreover, we say that a linkable ring signature scheme is \textit{non-slanderable} if every $(t, \epsilon, q)$-solver of this game has a negligible acceptance probability $\epsilon$.
+\end{definition}
+
+\begin{theorem}[Non-Slanderability is Unforgeability]\label{thm:nonsl-implies-unf}
+A correct LRS is unforgeable under Definition \ref{def:ex-unf} if and only if it is non-slanderable under Definition \ref{def:acst-nonsl}.
+\end{theorem}
+
+\begin{proof}
+    Let $\A$ be a $(t,\epsilon,q)$-solver of the unforgeability game of Definition \ref{def:ex-unf}.
+We show how to construct an algorithm $\B$ that executes $\A$ in a black box and is a solver of the non-slanderability game of Definition \ref{def:acst-nonsl}.
+Observe that the signing and corruption oracles are identical in both definitions, so such queries may be seamlessly passed between players, as we describe below.
+Formally, $\B$ operates in the following manner:
+    \begin{itemize}
+        \item $\B$ receives a set of public keys $S = \{pk_i\}_{i=0}^{q-1}$ from its challenger.
+It samples messages and rings (in the manner of Definition \ref{def:ex-unf}) and generates a set of tuples $\{(m_i,Q_i,\sigma_i)\}_{i=0}^{q-1}$ by queries of the form $\texttt{SO}(m_i,Q_i,l_i) \to \sigma_i$, where each $l_i$ is the index of $pk_i$ in $Q_i$.
+It passes the public key set $S$ to $\A$
+        \item $\B$ accepts $\texttt{SO}$ and $\texttt{CO}$ oracle queries from $\A$, passes them to its challenger, and returns the results to $\A$.
+        \item $\A$ returns a tuple $(m,Q,\sigma)$ satisfying the conditions in Definition \ref{def:ex-unf}.
+        \item $\B$ outputs $(m,Q,\sigma)$.
+    \end{itemize}
+    Since $\A$ is a solver of the unforgeability game, then with advantage $\epsilon$ there exists an index $i \in [0,q)$ such that $$\texttt{LINK}((m,Q,\sigma),(m_i,Q_i,\sigma_i)) = 1$$ and $pk_i \in S \cap Q \setminus C$.
+Further, $\B$ obtained $\sigma_i$ by an oracle query $\texttt{SO}(m_i,Q_i,l_i)$, so by construction $pk_i \in Q_i$ as well.
+Since $\B$ uses additional time $t'$ for its initial $q$ signing oracle queries and transcript lookup and has identical advantage $\epsilon$ as $\A$ does, we have constructed a $(t+t',\epsilon,q)$-solver of the non-slanderability game of Definition \ref{def:acst-nonsl}.
+
+    We now show the converse of the statement, and assume that $\A$ is a $(t,\epsilon,q)$-solver of the non-slanderability game of Definition \ref{def:acst-nonsl}.
+We will construct an algorithm $\B$ that executes $\A$ in a black box and is a solver of the unforgeability game of Definition \ref{def:ex-unf}.
+    \begin{itemize}
+        \item $\B$ receives a set of public keys $S = \{pk_i\}_{i=0}^{q-1}$ from its challenger. It passes the public key set $S$ to $\A$
+        \item $\B$ accepts $\texttt{SO}$ and $\texttt{CO}$ oracle queries from $\A$, passes them to its challenger, and returns the results to $\A$.
+        \item $\A$ returns a tuple $(m,Q,\sigma)$ satisfying the conditions in Definition \ref{def:acst-nonsl}.
+        \item $\B$ outputs $(m,Q,\sigma)$.
+    \end{itemize}
+    Since $\A$ is a solver of the non-slanderability game, then with advantage $\epsilon$ there exists a signing oracle query $\texttt{SO}(m^*,Q^*,l^*) \to \sigma^*$ such that $$\texttt{LINK}((m,Q,\sigma),(m^*,Q^*,\sigma^*)) = 1$$ and $pk_{l^*}^* \in S \cap Q^* \cap Q \setminus C$.
+But since $pk_{l^*}^* = pk_i \in S$ for some index $i \in [0,q)$, the unforgeability challenger produced a valid signature $\sigma_i$ on some message $m_i$ and ring $Q_i$ where $pk_i \in Q_i$.
+Hence it must be the case that $$\texttt{LINK}((m^*,Q^*,\sigma^*),(m_i,Q_i,\sigma_i)) = 1$$ and, by transitivity, it follows that $$\texttt{LINK}((m,Q,\sigma),(m_i,Q_i,\sigma_i)) = 1$$ as well.
+We therefore have shown that $\B$ is a $(t,\epsilon,q)$-solver of the unforgeability game, which completes the proof.
+\end{proof}
+
+\subsection{Linkable Anonymity}
+
+We use a modification of the definition of linkable anonymity from \cite{backes2019ring}.
+The definition we present here differs from \cite{backes2019ring} in that it does not grant the adversary access to a subset of corrupted keys prior to giving it access to a signing oracle; this is necessary for a later reduction to the hardness problem presented in Definition \ref{def:rom-ddh}.
+
+\begin{definition}[Chosen-Target Linkable Anonymity With Adversarial Keys]\label{linkable-anonymity-game}
+We say any PPT algorithm $\A$ that can succeed at the following game in time at most $t$ and with advantage at least $\epsilon$ is a $(t, \epsilon, q)$-solver of the linkable anonymity game.
+\begin{enumerate}
+\item Challenger samples a secret random bit $b \in \left\{0,1\right\}$, draws $\left\{(sk_i, pk_i)\right\}_{i=0}^{q-1}$ from $\texttt{KEYGEN}$, and sends the challenge public keys $S := \left\{pk_i\right\}_{i=0}^{q-1}$ to $\A$.
+
+\item $\A$ outputs a pair of indices $0 \leq i_0, i_1 < q$ such that $pk_{i_0}, pk_{i_1} \in S$, indicating the target keys.
+
+\item  $\A$ is granted access to a signing oracle $\texttt{SO}$ (which notably differs from the signing oracle used in earlier definitions):
+    \begin{enumerate}[(i)]
+    \item Takes as input a message $m$, an anonymity set $Q$, and a public key $pk \in Q$.
+
+    \item If $\left\{pk_{i_0}, pk_{i_1}\right\} \not\subseteq Q$ or $pk \notin \left\{pk_{i_0}, pk_{i_1}\right\}$, then $\texttt{SO}$ outputs a valid signature $\sigma$ linked to $pk$.
+
+    \item Otherwise, $pk = pk_{i_c}$ for a bit $c$.
+The bit $c^\prime = (1-c)b + c(1-b)$ is computed and the oracle outputs $\sigma \leftarrow \texttt{Sign}(m, Q, sk_{i_{c^\prime}})$.
+(That is, $c' = c \oplus b$.)
+    \end{enumerate}
+
+\item $\A$ outputs a bit $b^\prime$, succeeding if $b^\prime = b$.
+\end{enumerate}
+Moreover, we say that a scheme is \textit{linkably anonymous} if every $(t, \epsilon, q)$-solver of the linkable anonymity game has a negligible acceptance advantage $\epsilon$ over $1/2$.
+\end{definition}
+
+\section{Construction}\label{sec:implementation}
+
+In this section, we describe $d$-CLSAG, our implementation of a concise $d$-LRS construction.
+
+\begin{definition}[$d$-CLSAG]\label{def:clsag}
+The tuple $(\texttt{Setup}, \texttt{KeyGen}, \texttt{Sign}, \texttt{Verify}, \allowbreak \texttt{Link})$ as follows is a $d$-LRS signature scheme.
+
+\begin{itemize}
+\item $\texttt{Setup} \to \textit{par}$.
+First, $\texttt{Setup}$ selects a prime $p$, a group $\G$ with prime order $p$, selects a group generator $G \in \G$ uniformly at random, selects $d$ cryptographic hash functions $\Hs_0, \ldots, \Hs_{d-1}$ (modeled as random oracles) with codomain $\F$, selects a cryptographic hash function $\Hp$ with codomain $\G$.
+Then, $\texttt{Setup}$ outputs the group parameter tuple and the hash functions, $\textit{par} := \left(p,\G, d, G, \left\{\Hs_j\right\}_{j=0}^{d-1}, \Hp\right)$.\footnote{Note that domain separation can be used here to take one $\Hs$ and construct each $\Hs_j$ by defining $\Hs_j(x) := \Hs(j \mid\mid x)$.}
+
+\item $\texttt{KeyGen} \to (\textbf{sk}, \textbf{pk})$. When queried for a new key, $\texttt{KeyGen}$ samples a fresh secret key and computes the associated public key:
+\begin{align*}
+\textbf{sk} =& (z_0, z_1, \ldots, z_{d-1}) \leftarrow (\F^*)^d\\
+\textbf{pk} :=& \textbf{sk} \circ \textbf{G} = (Z_0, Z_1, \ldots, Z_{d-1}) \in \G^d
+\end{align*} where $\textbf{G} = (G, \ldots, G) \in \G^d$.
+$\texttt{KeyGen}$ outputs $(\textbf{sk}, \textbf{pk})$.
+We say $z_0$ is the \textit{linking key}, the remaining keys $\left\{z_j\right\}_{j=1}^{d-1}$ are the \textit{auxiliary keys}, and we denote the linking key with $x$.
+
+\item $\texttt{Sign}\left(m, Q, \textbf{sk}\right) \to \left\{\bot_{\texttt{Sign}}, \sigma\right\}$.
+$\texttt{Sign}$ takes as input a message $m \in \left\{0,1\right\}^*$, a ring  $Q = (\textbf{pk}_0, \ldots, \textbf{pk}_{n-1})$ for ring members $\textbf{pk}_i = (X_i, Z_{i,1}, \ldots, Z_{i,d-1}) \in \G^d$, and a secret key $\textbf{sk} = (x,z_1, \ldots, z_{d-1}) \in (\F^*)^d$.
+$\texttt{Sign}$ does the following.
+
+\begin{enumerate}
+\item If $Q \not\subseteq \G^{d\times n}$ for some $n$, $\texttt{Sign}$ outputs $\bot_{\texttt{Sign}}$ and terminates.
+
+\item Otherwise, $\texttt{Sign}$ parses\footnote{Note that this parsing always succeeds if $\texttt{Sign}$ does not fail in the previous step.} $Q$ to obtain each $\textbf{pk}_i$.
+If the public key associated with the input $\textbf{sk}$ is not a ring member in $Q$, then $\texttt{Sign}$ outputs $\bot_{\texttt{Sign}}$ and terminate.
+
+\item Otherwise, $\texttt{Sign}$ finds the signing index $\ell$ such that $\textbf{pk}_\ell = \textbf{sk} \circ (G, \ldots, G)$.
+$\texttt{Sign}$ samples $\alpha \in \F$ uniformly at random, samples $\left\{s_i\right\}_{i \neq \ell} \in (\F)^{n-1}$ uniformly at random, and computes the group elements $H_i = \Hp(X_i)$ for each $i$.
+$\texttt{Sign}$ computes the \textit{aggregation coefficients} $\mu_X$ and $\{\mu_j\}_{j=1}^{d-1}$, the linking tag $\mathfrak{T}$, the auxiliary group elements $\{\mathfrak{D}_j\}_{j=1}^{d-1}$, and the aggregated public keys:
+\begin{align*}
+\mathfrak{T} :=& x H_\ell & \{\mathfrak{D}_j\} :=&  \{z_j H_\ell\} \\
+\mu_X :=& \Hs_0(Q \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1})
+ & \mu_j :=& \Hs_j(Q \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}) \\
+ W_i :=& \mu_X X_i + \sum_{j=1}^{d-1} \mu_j Z_{i,j} & \mathfrak{W} :=& \mu_X \mathfrak{T} + \sum_{j=1}^{d-1} \mu_j \mathfrak{D}_j
+ \end{align*} and the aggregated secret key $w_\ell :=  \mu_X x + \sum_{j=1}^{d-1} \mu_j z_j$. For $i = \ell, \ell+1, \ldots, \ell-1$, (operating modulo $n$), $\texttt{Sign}$ computes
+\begin{align*}
+L_\ell =& \alpha G & R_\ell =& \alpha H_\ell & c_{\ell+1} =& \Hs_0(Q \mid \mid m \mid \mid L_\ell \mid \mid R_\ell) \\
+L_i =& s_i G + c_i W_i & R_i =& s_i H_i + c_i \mathfrak{W}
+ & c_{i+1} =& \Hs_0(Q \mid \mid m \mid \mid L_i \mid \mid R_i)
+\end{align*} and lastly computes $s_\ell = \alpha - c_\ell w_\ell$.
+
+\item $\texttt{Sign}$ returns the signature $\sigma = (c_0, s_0, s_1, \ldots, s_{n-1}, \mathfrak{T}, \{\mathfrak{D}_j\}_{j=1}^{d-1})$.
+\end{enumerate}
+
+\item $\texttt{Verify}\left(m, Q, \sigma\right) \to \left\{0,1\right\}$.
+$\texttt{Verify}$ takes as input a message $m$, a matrix $Q = (\textbf{pk}_0, \ldots, \textbf{pk}_{n-1})$, and a signature $\sigma$.
+\begin{enumerate}
+\item If $Q \not\subseteq \G^{d \times n}$ for some $n$, or if $\sigma \notin \F^{n^\prime+1} \times \G^d$ for some $n^\prime$, $\texttt{Verify}$ outputs $0$ and terminates.
+Otherwise, if $n^\prime \neq n$, $\texttt{Verify}$ outputs $0$ and terminates.
+
+\item $\texttt{Verify}$ parses\footnote{This parsing is always successful if the previous step does not terminate $\texttt{Verify}$.} $(\textbf{pk}_0, \ldots, \textbf{pk}_{n-1}) \leftarrow Q$ for keys $\textbf{pk}_i \in \G^d$ for $i \in [0,n-1]$, and parses each public key $(X_i, Z_{i, 1}, \ldots, Z_{i, d-1}) \leftarrow \textbf{pk}_i$.
+$\texttt{Verify}$ also parses $(c_0, s_0, \ldots, s_{n-1}, \mathfrak{T}, \mathfrak{D}_1, \ldots, \mathfrak{D}_{d - 1}) \leftarrow \sigma$.
+$\texttt{Verify}$ computes each $H_i = \Hp(X_i)$, computes the aggregation coefficients, and computes aggregated public keys:
+\begin{align*}
+\mu_X := & \Hs_0(Q \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1}) & \mu_j := & \Hs_j(Q \mid \mid \mathfrak{T} \mid \mid \{\mathfrak{D}_j\}_{j=1}^{d-1})\\
+W_i :=& \mu_X X_i + \sum_{j=1}^{d-1} \mu_j Z_{i,j} & \mathfrak{W} :=& \mu_X \mathfrak{T} + \sum_{j=1}^{d-1} \mu_j \mathfrak{D}_j
+\end{align*}
+
+\item $\texttt{Verify}$ sets $c_0^\prime := c_0$ and, for $i=1, 2, \ldots, n-1$, computes the following.
+\begin{align*}
+L_i :=& s_i G + c_i^\prime W_i, &
+R_i :=& s_i H_i + c_i^\prime\mathfrak{W}, &
+c_{i+1}^\prime :=& \Hs_0\left(Q \mid \mid m \mid \mid L_i \mid \mid R_i\right)
+\end{align*}
+\item If $c_{n}^\prime = c_0$, $\texttt{Verify}$ outputs $1$, and otherwise outputs $0$.
+\end{enumerate}
+
+\item $\texttt{Link}\left((m, Q, \sigma), (m^\prime, Q^\prime, \sigma^\prime)\right) \to \left\{0,1\right\}$. $\texttt{Link}$ takes as input two message-ring-signature triples.
+\begin{enumerate}
+\item If $\texttt{Verify}(m, Q, \sigma) = 0$ or $\texttt{Verify}(m^\prime, Q^\prime, \sigma^\prime) = 0$, $\texttt{Link}$ outputs $0$ and terminates.
+
+\item Otherwise, $\texttt{Link}$ parses\footnote{As before with $\texttt{Verify}$, this parsing is always successful if the previous step does not terminate $\texttt{Link}$.} the signatures to obtain the individual linking tags $(\mathfrak{T}, \left\{\mathfrak{D}_j\right\}_j), (\mathfrak{T}^\prime, \left\{\mathfrak{D}^\prime_j\right\}_j) \leftarrow \sigma, \sigma^\prime$.
+$\texttt{Link}$ outputs $1$ if $\mathfrak{W} = \mathfrak{W}^\prime$ and $0$ otherwise.
+\end{enumerate}
 \end{itemize}
@@
 
-\section{Proving system}
-We now present a sigma protocol for the following relation:
-\begin{multline*}
-\mathcal{R} \equiv \Bigg\{ \{M_i\}_{i=0}^{N-1},\{P_i\}_{i=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \\
-M_{l^{(u)}} = r^{(u)}G \; \forall \: u \in [0,w) \text{ and } r^{(u)}J^{(u)} = U \; \forall \: u \in [0,w) \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \Bigg\}
-\end{multline*}
-This captures the necessary elements for transaction authorization, which we describe later; knowledge of signing keys $\{r^{(u)}\}$ will show that the prover has signing authority for inputs to a transaction, and knowledge of the secret key $y$ to an amount commitment difference will show that the transaction amounts balance.
-Finally, comparison of the verifiable random function used to produce $\{J^{(u)}\}$ will be used to prevent attempts to sign for the same secret key without revealing the corresponding public key, which is important for signer ambiguity and double-spend protection within or between proofs.
+This implementation has \textit{full-key-oriented} linkability with linkability tags $\mathfrak{W}$: two signatures will link if they not only are signed using the same linking and auxiliary keys, but also the same ring.
+We can replace the $\texttt{Link}$ algorithm with \textit{single-key-oriented} linkability:
+\begin{itemize}
 
-Figures \ref{fig:sigma} and \ref{fig:sigma2} describe the prover and verifier interaction.
-Next, we prove that the prover and verifer routines constitute a sigma protocol that is perfectly correct, special sound, and special honest-verifier zero knowledge.
+\item $\texttt{Link}\left((m, Q, \sigma), (m^\prime, Q^\prime, \sigma^\prime)\right) \to \left\{0,1\right\}$. $\texttt{Link}$ takes as input two message-ring-signature triples.
+\begin{enumerate}
+\item If $\texttt{Verify}(m, Q, \sigma) = 0$ or $\texttt{Verify}(m^\prime, Q^\prime, \sigma^\prime) = 0$, $\texttt{Link}$ outputs $0$ and terminates.
 
-\begin{figure}[htbp]
-\centering
-\fbox{\begin{minipage}{0.95\textwidth}
-$\underline{\mathcal{P}:}$
-\begin{itemize}
-\item Select random $r_A \in \F$ and $\left\{a_{j,i}^{(u)}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1} \subset \F$.
-Set $$\{a_{j,0}^{(u)}\}_{j,u=0}^{m-1,w-1} \equiv -\sum_{i=1}^{n-1} a_{j,0}^{(u)}$$ and define $A \equiv \com(a,r_A)$.
-\item Define $\left\{\sigma_{j,i}^{(u)}\right\}_{i,j,u=0}^{n-1,m-1,w-1} \subset \F$ such that $\sigma_{j,i}^{(u)} \equiv \delta\left(l_j^{(u)},i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
-Define $B \equiv \com(\sigma,r_B)$.
-\item Select random $r_C \in \F$, and define $C \equiv \com(a(1-2\sigma), r_C)$.
-\item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
-\item For $0 \leq u < w$, define coefficients $\left\{p_{k,j}^{(u)}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p_k^{(u)}(x) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}^{(u)}x + a_{j,k}^{(u)} \right) = \delta\left(l^{(u)},k\right)x^m + \sumj p_{k,j}^{(u)}x^j$$ (using our decomposition notation).
-Then define $p_{k,j} \equiv \sumu p_{k,j}^{(u)}$ and $p_k(x) \equiv \sumu p_k^{(u)}(x)$ accordingly.
-\item Select random $\left\{\rho_j\right\}_{j,u=0}^{m-1,w-1}, \left\{\overline{\rho}_j^{(u)}\right\}_{j,u=0}^{m-1,w-1} \subset \F$.
-\item Define aggregation coefficients $\{\mu_k\}_{k=0}^{N-1}$ using a $k$-indexed $\hs$ operation, containing all Fiat-Shamir transcript public parameters and proof elements.
-\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}\mu_kM_k + \sumu \rho_j^{(u)}G$$
-\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv U \sumk p_{k,j}\mu_k + \sumu \rho_j^{(u)}J^{(u)}$$
-\item Define $\{Z_j\}_{j=0}^{m-1} \subset \G$ such that: $$Z_j \equiv \sumk p_{k,j}P_k + \sumu \overline{\rho}_j^{(u)}G$$
+\item Otherwise, $\texttt{Link}$ parses\footnote{As before with $\texttt{Verify}$, this parsing is always successful if the previous step does not terminate $\texttt{Link}$.} the signatures to obtain the individual linking tags $(\mathfrak{T}, \left\{\mathfrak{D}_j\right\}_j), (\mathfrak{T}^\prime, \left\{\mathfrak{D}^\prime_j\right\}_j) \leftarrow \sigma, \sigma^\prime$.
+$\texttt{Link}$ outputs $1$ if $\mathfrak{T} = \mathfrak{T}^\prime$ and $0$ otherwise.
+\end{enumerate}
 \end{itemize}
 
-$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
-$A,B,C,D,\{X_j\},\{Y_j\},\{Z_j\}$
-\end{minipage}}
-\caption{Sigma protocol for $\mathcal{R}$}
-\label{fig:sigma}
-\end{figure}
+\section{Proofs of Security}
 
-\begin{figure}[htbp]
-\centering
-\fbox{\begin{minipage}{0.95\textwidth}
-$\underline{\mathcal{V} \to \mathcal{P}:}$ \\
-$\xi \in \{0,1\}^*$ \\
+The following lemma follows immediately from the random oracle model we use for $\Hs$.
 
-$\underline{\mathcal{P}(\xi):}$
-\begin{itemize}
-\item Define $\left\{f_{j,i}^{(u)}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1}$ such that $f_{j,i}^{(u)} \equiv \sigma_{j,i}^{(u)}\xi + a_{j,i}^{(u)}$.
-\item Define $z_A \equiv r_A + \xi r_B$ and $z_C \equiv \xi r_C + r_D$.
-\item Define $\left\{z_R^{(u)}\right\}_{u=0}^{w-1} \subset \F$ such that: $$z_R^{(u)} \equiv \mu_{l^{(u)}}r^{(u)}\xi^m - \sumj \rho_j^{(u)}\xi^j$$
-\item Define: $$z_S \equiv \xi^m \left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right) - \sumj \left( \xi^j \sumu \overline{\rho}_j^{(u)} \right)$$
-\end{itemize}
+\begin{lemma}
+For any $Q \subseteq \mathcal{PK}$, for any private key $sk = (x, \left\{z_j\right\}_j) \in Q$, the map $sk \mapsto \mu_X x + \sum_j \mu_j z_j$ where $\mu_X$, $\mu_j$ are computed as in Definition \ref{def:clsag} is a collision-resistant function.
+\end{lemma}
 
-$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
-$\{f_{j,i}^{(u)}\}_{j=0,i=1,u=0}^{m-1,n-1,w-1},z_A,z_C,\{z_R^{(u)}\},z_S$ \\
+We prove $d$-CLSAG is unforgeable in Theorem \ref{thm:nonsl} by showing that if some PPT algorithm produces some valid, non-oracle triple $(m, Q, \sigma)$ that links to an anonymity set member in $Q$ (malicious or otherwise), then that algorithm can be rewound to compute the discrete logarithm of that anonymity set member.
+This theorem is standard for Schnorr-like signatures in the programmable random oracle model.
 
-$\underline{\mathcal{V}:}$
-\begin{itemize}
-\item For $0 \leq u < w$ and $0 \leq j < m$, set: $$f_{j,0}^{(u)} \equiv \xi - \sum_{i=1}^{n-1} f_{j,i}^{(u)}$$
-\item Accept if and only if:
-\begin{eqnarray}
-A + \xi B &=& \com(f,z_A) \label{eqn:ab} \\
-\xi C + D &=& \com(f(\xi-f),z_C) \label{eqn:cd} \\
-\sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f_{j,k_j}^{(u)} \right) \right] - \sumj \xi^jX_j - \sumu z_R^{(u)}G &=& 0 \label{eqn:x} \\
-U \sumk \mu_k \left[ \sumu \left( \prod_{j=0}^{m-1} f_{j,k_j}^{(u)} \right) \right] - \sumj \xi^jY_j - \sumu z_R^{(u)}J^{(u)} &=& 0 \label{eqn:y} \\
-\sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f_{j,k_j}^{(u)} \right) \right] - \sumj \xi^jZ_j - \xi^m\sum_{j=0}^{T-1} Q_j - z_SG &=& 0 \label{eqn:z}
-\end{eqnarray}
-\end{itemize}
-\end{minipage}}
-\caption{Sigma protocol for $\mathcal{R}$ (continued)}
-\label{fig:sigma2}
-\end{figure}
-
-\section{Security}
-\begin{theorem}
-The sigma protocol in Figures \ref{fig:sigma} and \ref{fig:sigma2} reflects the relation $\mathcal{R}$ and is perfectly correct, $(m+1)$-special sound, and special honest-verifier zero knowledge.
+\begin{theorem}[Hardness of Discrete Logarithms of Linear Combinations Implies Unforgeability] \label{thm:nonsl}
+If a $(t, \epsilon, q)$-solver of the unforgeability exists for the scheme of Definition \ref{def:clsag} that makes $\kappa^\prime$ corruption oracle queries, then there exists a $(2(t+t_0) + t_1, \epsilon\left(\frac{\epsilon}{q} - \frac{1}{2^\eta}\right) - \mu, \lfloor \frac{q}{d}\rfloor)$-solver of the $2d\kappa^\prime$-one-more discrete logarithm of linear combinations problem in $\G$ for some negligible $\mu$ and some constants $t_0, t_1$.
 \end{theorem}
@@
 \begin{proof}
-The proof proceeds similarly to that of \cite{triptych}, which in turn follows the methods in \cite{groth,bootle}.
+Assume $\A$ is a $(t, \epsilon, q)$-solver of the non-slanderability game of Definition \ref{def:acst-nonsl}.
+We wrap $\A$ in an algorithm $\B$.
+The algorithm $\B$ executes $\A$ in a black box, handling oracle queries for $\A$.
+Then, $\B$ regurgitates the output of $\A$ together with an index $idx$.
+This way, $\B$ is suitable for use in the forking lemma.
+We wrap $\mathcal{F}^{\B}$ in a master algorithm $\texttt{M}$ that is a $(2(t+t_0) + t_1, \epsilon\left(\frac{\epsilon}{q} - \frac{1}{2^\eta}\right) - \mu, \lfloor \frac{q}{d}\rfloor)$-solver of the $\kappa$-one-more discrete logarithm of linear combinations problem in $\G$, where $\eta$ is as defined in Lemma \ref{lem:fork}.
 
-To show the protocol is perfectly complete, suppose a verifier receives an honest proof.
-We wish to show that all verifier equations hold.
-Equation \ref{eqn:ab} holds from the identity $$\sumi \sigma_{j,i}^{(u)} = 1$$ for all $0 \leq j < m$ and $0 \leq u > w$.
-Similarly, Equation \ref{eqn:cd} holds from the identity $$(\sigma_{j,i}^{(u)})^2 = \sigma_{j,i}^{(u)}$$ for all $0 \leq i < n$ and $0 \leq j < m$ and $0 \leq u < w$.
+If $\A$ produces a successful forgery, each verification query of the form $c_{\ell+1} = \Hs(m \mid \mid Q \mid \mid R_\ell \mid \mid L_\ell)$ occurs in the transcript between $\A$ and the random oracle $\Hs$.
+Indeed, the signature triple produced by $\A$ passes verification, so each challenge $c_{\ell+1}$, whether made with oracle queries in the transcript or not, must be matched by random oracle queries made by the verifier.
+The prover cannot guess the output of such a query before making it except with negligible probability.
+Hence, if $\A$ outputs a valid signature, all verification challenges are computed by an actual oracle query.
+See \cite{liu2004linkable} for a formal proof of this fact.
+Since all verification challenges are found through genuine oracle queries, which are well-ordered, there exists a first $\Hs$ query made by $\A$ for computing verification challenges, say $c = \Hs(m \mid \mid Q \mid \mid R^* \mid \mid L^*)$.
+This was not necessarily the first query made to $\Hs$ overall, though; say it was the $k^{th}$ query.
+Although the ring index for this query may not have been decided when this query was first issued by $\A$, by the end of the transcript the ring index has been decided.
 
-Next, we show that Equation \ref{eqn:x} holds:
-\begin{eqnarray*}
-&& \sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jX_j - \sumu z^{(u)}_RG \\
-&=& \sumk \mu_kM_k p_k(x) - \sumj x^j \left( \sumk p_{k,j}\mu_kM_k + \sumu \rho^{(u)}_jG \right) - \sumu z^{(u)}_RG \\
-&=& \sumk \mu_kM_k \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jG - \sumu z^{(u)}_RG \\
-&=& \sumk \mu_kM_k \left[ x^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_jG - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right]G \\
-&=& x^m\sumu \mu_{l^{(u)}}r^{(u)}G - \sumj x^j \sumu \rho^{(u)}_jG - x^m\sumu \mu_{l^{(u)}}r^{(u)}G + \sumj x^j \sumu \rho^{(u)}_jG \\
-&=& 0
-\end{eqnarray*}
+We construct $\B$ in the following way.
+We grant $\B$ access to the same oracles as $\A$.
+Any oracle queries made by $\A$ are passed along by $\B$ to the oracles.
+The responses are recorded and then passed back to $\A$.
+The algorithm $\B$ works by finding two indices to augment the output of $\A$.
+First, $\B$ finds the $\Hs$ query index $k$ corresponding to the first verification challenge computed by $\A$ used in verifying the purported foergery.
+Second, $\B$ inspects the transcript of $\A$ to find the anonymity set index $\ell$ in the transcript such that $c = c_{\ell+1}$ and $R^* = R_\ell$ and $L^* = L_\ell$.
+Now $\B$ outputs $idx = (k, \ell)$ along with whatever $\A$ outputs.
+Clearly, $\B$ makes the same number of corruption oracle queries as $\A$.
 
-Equation \ref{eqn:y} holds with similar algebra:
-\begin{eqnarray*}
-&& \sumk \mu_kU \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jY_j - \sumu z^{(u)}_RJ^{(u)} \\
-&=& \sumk \mu_kU p_k(x) - \sumj x^j \left( \sumk p_{k,j}\mu_kU + \sumu \rho^{(u)}_jJ^{(u)} \right) - \sumu z^{(u)}_RJ^{(u)} \\
-&=& \sumk \mu_kU \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \rho^{(u)}_jJ^{(u)} - \sumu z^{(u)}_RJ^{(u)} \\
-&=& \sumk \mu_kU \left[ x^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - \sumu\left[ \mu_{l^{(u)}}r^{(u)}x^m - \sumj \rho^{(u)}_jx^j \right](r^{(u)})^{-1}U \\
-&=& x^m\sumu \mu_{l^{(u)}}U - \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - x^m\sumu \mu_{l^{(u)}}U + \sumj x^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U \\
-&=& 0
-\end{eqnarray*}
+Note $\B$ succeeds whenever $\A$ does and runs in time at most $t$ just like $\A$, except for some additional time $t_0$ to search the transcript for $idx$.
+Since $\B$ is suitable for use in the forking lemma, we can use $\mathcal{F}^{\B}$ to construct $\texttt{M}$.
 
-Finally, we show that Equation \ref{eqn:z} holds:
-\begin{eqnarray*}
-&& \sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj x^jZ_j - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
-&=& \sumk P_k p_k(x) - \sumj x^j \left( \sumk p_{k,j}P_k + \sumu \overline{\rho}^{(u)}_jG \right) - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
-&=& \sumk P_k \left( p_k(x) - \sumj x^j p_{k,j} \right) - \sumj x^j \sumu \overline{\rho}^{(u)}_jG - x^m\sum_{j=0}^{T-1} Q_j - z_SG \\
-&=& x^m\sumu (s^{(u)}G + a_uH) - \sumj x^j \sumu \overline{\rho}^{(u)}_jG - x^m\sum_{j=0}^{T-1} (t_jG + b_jH) - x^m\left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right)G + \\
-&& \sumj x^j \sumu \overline{\rho}^{(u)}_jG \\
-&=& \left( \sumu a_u - \sum_{j=0}^{T-1} b_j \right)H \\
-&=& 0
-\end{eqnarray*}
-Hence, the protocol is perfectly complete.
+The algorithm $\mathcal{F}^{\B}$ is granted oracle access to the same oracles as $\B$ except $\Hs$ and $\texttt{SO}$.
+The algorithm $\mathcal{F}^{\B}$ simulates $\texttt{SO}$ queries made by $\B$ by simple back-patching of $\Hs$ and simulates the other queries made to $\Hs$ queries made by $\B$ using the random tapes $\textbf{h}, \textbf{h}^*$ as described in Section \ref{sec:hardness}.
+All other oracle queries made by $\B$ are passed along by $\mathcal{F}^{\B}$ to the actual oracles and handed back to $\B$.
 
-Next, we show that the sigma protocol is special honest-verifier zero knowledge.
-To do so, we construct a simulator that, when given a random verifier challenge $\xi$, can construct a proof transcript with identical distribution to a valid proof.
+Note that $\mathcal{F}^{\B}$ runs in time $2(t+t_0)$ and (with probability at least $\epsilon\left(\frac{\epsilon}{q} - \frac{1}{2^\eta}\right)$) outputs a pair of valid signature triples $(m, Q, \sigma)$, $(m^\prime, Q^\prime, \sigma^\prime)$.
+The messages and anonymity sets are selected before the fork point in the transcripts, so $m=m^\prime$ and $Q=Q^\prime$.
+Moreover, $\mathcal{F}^{\B}$ makes at most $2\kappa^\prime$ corruption queries.
+The challenges for the two transcripts are distinct since the forking algorithm outputs the failure symbol $\bot$ and terminates if the challenges for $c_{\ell + 1}$ are the same in each transcript.
+\[c_{\ell + 1} \leftarrow \Hs_0(m \mid \mid Q \mid \mid R_\ell \mid \mid L_\ell) \rightarrow c_{\ell+1}^\prime.\]
 
-Observe first that the simulator presented in the proof of Lemma 1 in \cite{bootle} translates nearly identically to our setting, since we can flatten tensor commitments to a matrix structure with the required sum property.
-The simulator first chooses $B \in \G$ uniformly at random; then, the cited lemma assures a valid simulation of the proof elements  $A,C,D,z_A,z_C,\{f^{(u)}_{j,i \neq 0}\}$, and from this we may compute $\{f^{(u)}_{j,0}\}$.
-In a valid proof, $B$ is also uniformly distributed.
+We wrap $\mathcal{F}^{\B}$ in an algorithm $\texttt{M}$ that plays the $\kappa$-one-more discrete logarithm game of Definition \ref{def:komdl} for $\kappa = 2\cdot d \cdot \kappa^\prime$.
+The algorithm $\texttt{M}$ has corruption oracle access and runs $\mathcal{F}^{\B}$ in a black box, passing corruption oracle queries made by $\mathcal{F}^{\B}$ along.
+The algorithm $\texttt{M}$ finds the following system of equations in the transcripts by inspecting the verification challenge queries
+\[R_\ell = s_\ell G + c_\ell X_\ell = s_\ell^\prime G + c_\ell^\prime X_\ell,\]
+\[L_\ell = s_\ell H_\ell + c_\ell \mathfrak{W} = s_\ell^\prime H_\ell + c_\ell^\prime \mathfrak{W}.\] This $\texttt{M}$ has enough information to compute
+\[ W_\ell = \frac{s_\ell - s_\ell^\prime}{c_\ell^\prime - c_\ell} G,  \mathfrak{W} = \frac{s_\ell - s_\ell^\prime}{c_\ell^\prime - c_\ell} H_\ell.\]
+and therefore the private key $w = \frac{s_{\ell} - s_\ell^\prime}{c_\ell^\prime - c_\ell}$. Formally, $\texttt{M}$ operates as follows.
 
-The proof elements $\{X_j\}_{j=1}^{m-1},\{Y_j\}_{j=1}^{m-1}, \{Z_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof since the elements of $\{\rho_j\},\{\overline{\rho}_j\}$ are uniformly distributed and the discrete logarithm problem in $\G$ is hard; hence, the simulator chooses them uniformly at random.
-Since the verification checks require that $X_0,Y_0,Z_0$ be uniquely determined by the other elements in the respective sets, they are selected by the simulator in this manner.
+\begin{enumerate}[(1)]
+\item $\texttt{M}$ inputs the set of discrete logarithm challenge public keys $S = \left\{\widetilde{pk}_i\right\}_{i=0}^{q-1}$.
 
-Finally, the elements $\{z^{(u)}_R\}_{u=0}^{w-1}$ and $z_S$ are independent and uniformly distributed in valid proofs given a random verifier challenge $\xi$, so the simulator may choose them uniformly at random.
-Hence the protocol is special honest verifier zero-knowledge.
+\item $\texttt{M}$ partitions the challenge keys into lists of $d$ keys
+\begin{align*}
+pk_0 =&  (X_0, Z_{0, 1}, \ldots, Z_{0, d-1}) := (\widetilde{pk}_0, \ldots, \widetilde{pk}_{d-1}) \\
+pk_1 =& (X_1, Z_{1, 1}, \ldots, Z_{1, d-1}) := (\widetilde{pk}_d, \ldots, \widetilde{pk}_{2d-1}) \\
+\vdots
+\end{align*} obtaining $S := \left\{pk_i\right\}_{i=0}^{\left\lfloor \frac{q}{d}\right\rfloor}$.
 
-We claim that the protocol is $(m+1)$-special sound, where $m > 1$.
-To show this, we construct an extractor that, when given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness for the statement.
-In particular, we produce a modified witness for the following relation that is based on the information presented in the prover algorithm, where we define aggregation coefficients $\mu_k$ as before:
-\begin{multline*}
-\mathcal{R}' \equiv \Bigg\{ \{M_k\}_{k=0}^{N-1},\{P_k\}_{k=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \\
-\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sumu \mu_{l^{(u)}} r^{(u)}G \text{ and } \sumu \mu_{l^{(u)}} r^{(u)}J^{(u)} = \sumu \mu_{l^{(u)}} U \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \Bigg\}
-\end{multline*}
-Observe that if we assume that the dual-target discrete logarithm problem is hard in $\G$, extraction of a witness for $\mathcal{R}'$ implies knowledge of a corresponding witness for $\mathcal{R}$; this in turn provides the desired soundness.
+\item $\texttt{M}$ picks two random tapes $\textbf{h}, \textbf{h}^\prime$ to simulate oracle query responses for $\mathcal{F}^{\B}$.
 
-Suppose that for a given statement, we have a set of $(m+1)$ distinct verifier challenges $\{\xi_e\}_{e=0}^m$ corresponding to distinct valid responses of this form:
-$$\left\{ \{{}_ef^{(u)}_{j,i}\}, \{{}_ez^{(u)}_R\}, {}_ez_S \right\}_{e=0}^m$$
-From the $3$-special soundness in \cite{bootle} and $m > 1$ we have valid extractions $\{\sigma^{(u)}_{j,i}\}_{u=0}^{w-1}$ and $\{a^{(u)}_{j,i}\}_{u=0}^{w-1}$, and the Pedersen binding property ensures that (with high probability) we have:
-$${}_ef^{(u)}_{j,i} = \sigma^{(u)}_{j,i}\xi_e + a^{(u)}_{j,i} \; \forall \: e \in [0,m]$$
-Using the extracted values, compute the polynomial
-$$p_k(x) \equiv \sum_{u=0}^{w-1}\left[ \prod_{j=0}^{m-1} \left( \sigma^{(u)}_{j,k}x + a^{(u)}_{j,k} \right) \right]$$
-for all $k \in [0,N)$.
-Extraction of $\{\sigma^{(u)}_{j,i}\}_{u=0}^{w-1}$ immediately yields the signing index set $\{l^{(u)}\}_{u=0}^{w-1}$.
+\item $\texttt{M}$ executes $\mathcal{F}^{\B}$ in a black box, using $S$ as input.
+Upon receiving a corruption query from $\mathcal{F}^{\B}$ on some $pk_i$, $\texttt{M}$ makes a $\texttt{CO}$ query on $X_i$ and each $Z_{j,i}$, passing $sk_i$ back to $\mathcal{F}^{\B}$.
+Each corruption query made by $\mathcal{F}^{\B}$ consists of $d$ corruption queries made to $\texttt{CO}$ by $\texttt{M}$.
 
-We have seen that $p_k$ is of degree $m$ only when $k \in \{l^{(u)}\}_{u=0}^{w-1}$.
-Hence there exist sets of coefficients $\{\overline{X}_j,\overline{Y}_j,\overline{Z}_j\}_{j=0}^{m-1}$, computed uniquely from the statement and extracted values, such that Equations \ref{eqn:x}, \ref{eqn:y}, and \ref{eqn:z} are of the following form:
-\begin{eqnarray*}
-\xi^m \sumu \mu_{l^{(u)}}M_{l^{(u)}} + \sumj \xi^j\overline{X}_j &=& \left( \sumu z^{(u)}_R \right)G \\
-\xi^m \sumu \mu_{l^{(u)}}U + \sumj \xi^j\overline{Y}_j &=& \sumu z^{(u)}_RJ^{(u)} \\
-\xi^m \sumu P_{l^{(u)}} + \sumj \xi^j\overline{Z}_j - \xi^m \sum_{j=0}^{T-1} Q_j &=& z_SG
-\end{eqnarray*}
+\item If $\mathcal{F}^{\B}$ fails, or if $\mathcal{F}^{\B}$ succeeds with all zero coefficients $\mu_X$ and $\mu_j$, then $\texttt{M}$ samples a random $w \in \F$, samples a random subset of challenge keys $\left\{pk^*_j\right\}_j \subseteq S$, samples random coefficients $\left\{h_j\right\}_j$, outputs $w, \left\{pk^*_j\right\}_j, \left\{h_j\right\}_j$, and terminates.
 
-Construct a Vandermonde matrix $V$ where the $e$ row is the vector $(1,\xi_e,\ldots,\xi^m_e)$.
-Since all $\xi_e$ are distinct, the rows of $V$ span $\F^{m+1}$; hence there exist weights $\{\theta_e\}_{e=0}^m$ such that the resulting linear combination of rows produces the vector $(0,\ldots,0,1)$.
-That is, $\sum_{e=0}^m \theta_e\xi_e^j = \delta(j,m)$.
+\item Otherwise, $\texttt{M}$ obtains two signature triples with the same message and ring, $(m, Q, \sigma), (m, Q, \sigma^\prime)$ at at least one non-zero aggregation coefficient.
+$\texttt{M}$ computes the challenge discrete logarithm $w = (c_\ell^\prime - c_\ell)^{-1}(s_\ell - s_\ell^\prime)$.
+$\texttt{M}$ outputs $w, \left\{\mu_X, \left\{\mu_j\right\}_j\right\}$, and $\left\{X_\ell, \left\{Z_{\ell, j}\right\}_j\right\}$.
+\end{enumerate}
 
-For each of the previous three equations, we can therefore build a linear combination over $e$. For the first:
-$$\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sum_{e=0}^m \theta_e\xi_e^m \left( \sumu \mu_{l^{(u)}} M_{l^{(u)}} \right) + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{X}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) G$$
-We therefore can define extractions for each $r^{(u)}$:
-$$r^{(u)} \equiv \frac{1}{\mu_{l^{(u)}}} \sum_{e=0}^m \theta_e {}_ez^{(u)}_R$$
-Observe that the same witnesses appear in the second:
-$$\sumu \mu_{l^{(u)}} U = \sum_{e=0}^m \theta_e\xi_e^m \left( \sumu \mu_{l^{(u)}} U \right) + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{Y}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) J^{(u)}$$
-This means the requirements on each $r^{(u)}$ are satisfied. The third equation proceeds similarly.
-$$\sumu P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = \sum_{e=0}^m \theta_e\xi_e^m \left( \sumu P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j \right) + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{Z}_j \right) = \left( \sum_{e=0}^m \theta_e {}_ez_S  \right)G$$
-Hence we have $y \equiv \sum_{e=0}^m \theta_e {}_ez_S$.
+Denote with $t_1$ the time it takes for $\mathcal{M}$ to inspect the transcript, perform field operations, and process corruption queries for $\mathcal{F}^{\B}$.
+Then the algorithm $\texttt{M}$ runs in time at most $2(t+t_0) + t_1$.
+
+To complete the proof, consider the overall success probability and timing of $\texttt{M}$.
+Since $\A$ is a $(t, \epsilon, q)$-solver of the unforgeability game and these are successful signatures, there must be at least one query made to $\texttt{SO}$ corresponding to an uncorrupted challenge key linking to these signatures.
+In particular, $w \cdot G = W_\ell = \mu_X X_\ell + \sum_j \mu_j Z_{\ell,j}$ for some $(X_\ell, \left\{Z_{\ell, j}\right\}_j) \in Q$.
+The algorithm $\texttt{M}$ succeeds at the discrete logarithms of linear combinations game whenever $\mathcal{F}^{\B}$ succeeds at forking $\B$ and at least one coefficient $\mu_X$ and $\mu_j$ is non-zero; we denote the probability of obtaining any zero coefficients as $\mu$.
+We note that $\mu$ is negligible under the random oracle model.
+Thus, $\texttt{M}$ runs in time at most $2(t+t_0) + t_1$, has success probability exceeding $\epsilon\left(\frac{\epsilon}{q} - \frac{1}{2^\eta}\right) - \mu$.
 \end{proof}
 
-\section{Transaction model}
-We now describe how to apply the sigma protocol for $\mathcal{R}$ in a confidential transaction model.
-In such a model, a transaction consumes so-called \textit{outputs} generated in previous transactions, and produces new outputs for use in later transactions.
-Notably, in a \textit{confidential} transaction model, we wish to introduce ambiguity as to which transaction inputs are being consumed, as well as the corresponding values represented by them.
+The proof of Theorem \ref{thm:nonsl} demonstrates that the validity of a triple implies that the aggregated private key $w$ is the discrete logarithm of the aggregated linking tag $\mathfrak{W}$ with respect to $H_\ell$ and is also the discrete logarithm of the aggregated key $W_\ell$ with respect to $G$.
+In this way, the linking tag of a valid signature must be the linking tag corresponding to at least one ring member, except possibly with negligible probability.
 
-Outputs are constructed as Pedersen commitments to zero, such that an output public key is of the form $M \equiv rG$ with signing key $r$.
-We do not consider here the method by which output keys are generated, but assume this is offloaded to another part of the transaction model.
-Each output comes equipped with a value commitment $P \equiv sG + aH$, where $a$ is the amount and $s$ a blinding factor.
+\begin{corollary}[No Alien Linking Tags]\label{cor:no-aliens}
+If there exists a PPT algorithm $\A$  that produces a valid signature triple $(m, Q, \sigma)$ with the scheme in Definition \ref{def:clsag}, then there exists a ring member in $Q$ whose aggregated key $W_\ell$ has the same discrete logarithm $w$ with respect to $G$ as $\mathfrak{W}$ has with respect to $H_\ell$, and this $w$ is known to $\A$ (except possibly with negligible probability).
+\end{corollary}
 
-A user of the protocol forms an anonymity set $\{M_i\}_{i=0}^{N-1}$ of outputs from previous transactions.
-Of these, suppose that the set $\{l^{(u)}\}_{u=0}^{w-1}$ represents the indices of the $w$ outputs for which the user wishes to sign; that is, the user knows $\{r^{(u)}\}_{u=0}^{w-1}$ such that $r^{(u)}G = M_{l^{(u)}}$ for all $0 \leq u < w$.
-To help ensure ambiguity of the signing indices, assume the user has shuffled the anonymity set.
-Each element of the anonymity set has a corresponding value commitment $\{P_i \equiv s_iG + a_iH\}_{i=0}^{N-1}$.
+\begin{theorem}\label{thm:linkabilty}
+The scheme in Definition \ref{def:clsag} is linkable under Definition \ref{def:acst-link-adv} and Definition \ref{def:pig-link}.
+\end{theorem}
 
-Further, the user generates a set of new outputs produced by the transaction, with corresponding value commitments of the form $\{Q_j \equiv t_jG + b_jH\}_{j=0}^{T-1}$.
-Because the transaction value must balance, the following must hold: $$\sum_{u=0}^{w-1} a_{l^{(u)}} = \sum_{j=0}^{T-1} b_j$$
-Note that there is no anonymity set for outputs generated by the transaction.
+\begin{proof}
+We show that valid, non-oracle signature triples from the scheme in Definition \ref{def:clsag} satisfying the corrupted key conditions in the game of Definition \ref{def:acst-link-adv} always link.
+Hence, any algorithm fails at that game except with negligible probability.
 
-These terms are used to form a statement using the relation $\mathcal{R}$.
-The user generates a proof showing the validity of this statement with the corresponding secret values as a witness set; the proof demonstrates knowledge of the signing keys $\{r^{(u)}\}_{u=0}^{w-1}$, and the witness $y$ formed by the commitment differences demonstrates that the input and output values balance.
-Provided the commitment scheme used for value representation is (at least computationally) binding, the user cannot produce such a value $y$ unless the values balance correctly; in our case, Pedersen commitments satisfy this requirement.
+Assume that $\A$,  while playing the game of ACST linkability from Definition \ref{def:acst-link-adv}, produces a pair of valid, non-oracle signature triples $(m, Q, \sigma)$, $(m^*, Q^*, \sigma^*)$ such that at most one key in $Q \cup Q^*$ is corrupted or outside of $S$.
+This algorithm can be forked and rewound as above to compute the aggregated private key used in computing each signature, say $w, w^*$.
+At most one key in $Q \cup Q^*$ is corrupted or outside of $S$.
+Since $\A$ has knowledge of $w$, then $w$ is corrupted or outside of $S$, and likewise $w^*$ is corrupted or outside of $S$.
+Since at most one key in $Q \cup Q^*$ can be corrupted or outside of $S$, we conclude $w = w^*$.
 
-We call the elements of the set $\{J^{(u)}\}_{u=0}^{w-1}$ the \textit{linking tags} for the transaction.
-Similar to their use in linkable ring signatures, they are used by the verifier to detect attempts to sign with a secret key multiple times, either within the same transaction or between multiple transactions.
-The construction $J^{(u)} = (r^{(u)})^{-1}U$ is an injective one-way verifiable random function \cite{dodis} using the secret key $r^{(u)}$; if the verifier sees the same linking tag used elsewhere, it knows that the (unknown) secret key was used again.
-In our confidential transaction model, this corresponds to an attempt to double-spend funds that would be rejected by the verifier.
+Since key aggregation is preimage-resistant by its construction using hash functions and $wG$ is the aggregated public key for some public key $(X_\ell, \left\{Z_{\ell, j}\right\}_j) \in Q \cap Q^*$, $w$ must be aggregated from a private key $(x_\ell, \left\{z_{\ell, j}\right\}_j)$ using the aggregation function.
+In both the case of single-key-oriented linkability and full-key-oriented linkability, the linkability tags are therefore exactly equal.
+Hence, with probability $1$, the pair of triples $(m, Q, \sigma)$, $(m^*, Q^*, \sigma^*)$ are linked, and $\A$ fails at ACST linkability except with negligible probability.
 
-Since the sigma protocol is special honest-verifier zero knowledge, it is witness indistinguishable \cite{cramer}.
-Note, however, that an observer who sees an input anonymity set containing a commitment for which the observer knows the opening can trivially test linking tags using its own secret keys to determine if they were used in the proof.
-Therefore, witness indistinguishability is assumed to apply among input commitments for which an observer does not know a corresponding opening.
+Similarly, an algorithm that outputs $q+1$ unlinked signatures can be rewound to compute $2(q+1)$ signatures from which $q+1$ aggregated keys can be computed.
+Moreover, if these signatures are unlinked, then the $q+1$ aggregated keys are distinct, violating $q$-pigeonhole linkability.
+\end{proof}
 
-\section{Efficiency}
-Observe that all group operations involved in verification occur in multiscalar multiplication operations that must evaluate to zero; methods such as those in \cite{straus,pippenger} provide efficient evaluation of these operations.
-Further, many group elements in these operations are globally-fixed generators that appear in all proofs.
-As a result, verification of many separate independent proofs may be batched similarly to the method described in \cite{bulletproofs} and elsewhere, where random weighting of verification equations is performed and common generators are used only once.
-The result is that a batch of independent proofs can be more efficiently verified using a single multiscalar multiplication operation, lowering the marginal cost per proof to verify.
+\begin{theorem}
+If there exists a $(t,\epsilon,q)$-solver of the linkable anonymity game of Definition \ref{linkable-anonymity-game} under the construction of Definition \ref{def:clsag}, then there exists a $(t+t',\epsilon/2,q)$-solver of the RO-DDH game of Definition \ref{def:rom-ddh} for some $t'$.
+\end{theorem}
 
-We follow the same notation as before: $N = 2^m$ is the size of the input anonymity set for varying $m > 1$, $w$ is the number of signing indices, and $T$ is the number of output commitments used in the balance check.
-Assuming that both elements of $\G$ and $\F$ occupy $32$ bytes of storage (as is the case for common elliptic curve groups using compressed point representations), we compare the size of proofs for RingCT 3.0 (two variants) \cite{rct3}, Triptych \cite{triptych}, and this work.
-Note that we make some assumptions in order to produce fair comparisons here.
-In Triptych and the original version of RingCT 3.0, certain commitment offsets are required as part of balance testing, which we consider, along with the multiple proofs needed in a transaction that wishes to sign for multiple inputs.
-However, we ignore input set representation (which depends on implementation), range proofs (which are required for all protocols and not part of the proving systems), and any auxiliary data that would otherwise appear as part of transactions.
-Table \ref{table:size} shows the results.
+\begin{proof}
+Let $\A$ be such a solver of the linkable anonymity game.
+We will construct an algorithm $\B$ that executes $\A$ in a black box and is a solver of the RO-DDH game, acting as the challenger for $\A$; the algorithm will pass on $\Hp$ random oracle queries to its own challenger, flip coins for $\Hs_0$ and $\{\Hs_j\}$ random oracle queries, and simulate signing oracle queries by backpatching.
+We assume that $\B$ keeps internal tables to maintain consistency between the random oracle queries needed to simulate signing oracle queries.
 
-\begin{table}
-\centering
-\begin{tabular}{|ll|}
+The algorithm $\B$ operates as follows:
+\begin{itemize}
+\item $\B$ receives a set of tuples $\{(R_i,R_i',R_i'')\}_{i=0}^{q-1}$ from its challenger, and chooses a bit $b' \in \{0,1\}$ uniformly at random.
+Note that $\B$ does not know if its tuples are RO-DDH triples or not, as its challenger chose a secret bit $b \in \{0,1\}$ uniformly at random to determine this.
+\item For all $i \in [0,q)$, $\B$ defines $X_i := R_i$ and records the $\Hp$ oracle mapping $\Hp(X_i) = R_i'$.
+It chooses $\{z_{i,j}\}_{j=1}^{d-1}$ from $\F$ uniformly at random, and builds a set of public keys $S := \{(X_i, z_{i,1}G, \ldots, z_{i,d-1}G)\}_{i=0}^{q-1}$.
+$\B$ provides the set $S$ to $\A$.
+\item $\A$ returns indices $0 \leq i_0,i_1 < q$ to $\B$.
+\item $\B$ receives signing oracle queries of the form $\texttt{SO}(m,Q,pk)$, where $0 \leq \ell < q$ is the index of $pk \in Q$, $pk \in S$, and $|Q| = n$.
+There are two cases, which determine how $\B$ simulates the oracle response, flipping coins for $\Hs_0$ and $\{\Hs_j\}$ oracle queries:
+\begin{itemize}
+\item If it is the case that $\{pk_{i_0},pk_{i_1}\} \not\subset Q$ or $pk \not\in \{pk_{i_0},pk_{i_1}\}$, then $\B$ proceeds with its signing oracle simulation using the key $pk$.
+\item Otherwise, there exists a bit $c \in \{0,1\}$ such that $pk = pk_{i_c}$.
+In this case, $\B$ sets $c' := c \oplus b'$ and proceeds with its signing oracle simulation using the key $pk_{i_{c'}}$.
+This is, if $b' = 0$, then $\B$ simulates a signature using the requested key from the player-provided index set.
+If instead $b' = 1$, then $\B$ simulates a signature using the other key.
+\end{itemize}
+In either case, $\B$ parses the public key set $Q$ provided by $\A$.
+For any key $pk_i := (X_i',Z_{i,1}',\ldots,Z_{i,d-1}') \in Q \setminus S$, it makes oracle queries to its challenger to obtain $\Hp(X_i')$.
+Then $\B$ simulates the signature:
+\begin{itemize}
+\item Define a map $\pi: [0,n) \to [0,q) \cup \{\bot\}$ that maps indices of elements of $Q$ to the corresponding elements of $S$ (or returns the distinguished failure symbol $\bot$ for indices not mapping to elements of $S$), and let $0 \leq \ell < n$ be the index of $pk \in Q$.
+\item Choose $c_{\ell}, \{s_i\}_{i=0}^{n-1} \in \F$ uniformly at random.
+\item Since $pk \in S$ by construction, $\pi(\ell) \neq \bot$.
+Set $\mathfrak{T} := R_{\pi(\ell)}''$ and $\{\mathfrak{D}_j\}_{j=1}^{d-1}$ such that each $\mathfrak{D}_j := z_{\pi(\ell),j}\Hp(X_{\pi(\ell)})$.
+\item Define the following:
+\begin{align*}
+\mu_X &\leftarrow \Hs_0(Q,\mathfrak{T},\{\mathfrak{D}_j\}) \\
+\mu_j &\leftarrow \Hs_j(Q,\mathfrak{T},\{\mathfrak{D}_j\}) \text{ for } j \in (0,d) \\
+\mathfrak{W}_i &:= \begin{cases} \mu_XX_{\pi(i)} + \sum_j \mu_jZ_{\pi(i),j} & (\pi(i) \neq \bot) \\ \mu_XX_i' + \sum_j \mu_jZ_{i,j}' & (\pi(i) = \bot) \end{cases} \\
+W &:= \mu_X\mathfrak{T} + \sum_j \mu_j\mathfrak{D}_j
+\end{align*}
+\item For each $i = \ell,\ell+1,\ldots,n-1,0,\ldots,\ell-1$ (that is, indexing modulo $n$), define the following:
+\begin{align*}
+L_i &:= s_iG + c_i\mathfrak{W}_i \\
+R_i &:= \begin{cases} s_i\Hp(X_{\pi(i)}) + c_iW & (\pi(i) \neq \bot) \\ s_i\Hp(X_i') + c_iW & (\pi(i) = \bot) \end{cases} \\
+c_{i+1} &\leftarrow \Hs_0(Q,m,L_i,R_i)
+\end{align*}
+\item $\B$ returns to $\A$ the tuple $(c_0,\{s_i\},\mathfrak{T},\{\mathfrak{D}_j\})$.
+\end{itemize}
+\item $\A$ returns a bit $b^*$ to $\B$.
+\item If $b^* = b'$, then $\B$ returns $0$ to its challenger. Otherwise, it returns $1$.
+\end{itemize}
+
+It is the case that $\B$ wins the RO-DDH game precisely when it correctly guesses the bit $b$ chosen by its challenger.
+Hence $\prob[\B \text{ wins}] = \frac{1}{2}\prob[\B \to 0 | b = 0] + \frac{1}{2}\prob[\B \to 1 | b = 1]$.
+
+If $b = 1$, then the RO-DDH challenger provided random points $\{R_i''\}$ that $\B$ used in its simulated signatures, so $\A$ can do no better than random chance at determining $b'$.
+Since $\B \to 1$ exactly when $\A$ loses the linkable anonymity game, we have $\prob[\B \to 1 | b = 1] = \frac{1}{2}$.
+
+On the other hand, if $b = 0$, then the RO-DDH challenger provided structured tuples that $\B$ used in its simulated signatures, and $\A$ wins the linkable anonymity game with non-negligible advantage $\epsilon$ over random chance.
+Since $\B \to 0$ exactly when $\A$ wins the linkable anonymity game, we have $\prob[\B \to 0 | b = 0] = \frac{1}{2} + \epsilon$.
+
+This means $\B$ wins the RO-DDH game with probability $\prob[\B \text{ wins}] = \frac{1}{2} + \frac{\epsilon}{2}$ and has non-negligible advantage $\frac{\epsilon}{2}$.
+Further, $\B$ finishes with an added time $t'$ used in simulating oracle queries and performing lookups.
+Hence, $\B$ is a $(t+t',\epsilon/2,q)$-solver of the RO-DDH game.
+\end{proof}
+
+\section{Efficiency}\label{sec:efficiency}
+Consider the space and time efficiency of Definition \ref{def:clsag}. We disregard any additional information typically broadcast alongside the signature, such as representations of the ring members.
+
+A $d$-CLSAG signature with a ring size of $n$ contains $n+1$ field elements and $d$ group elements; signature size is $k_s(n+1) + k_p d$ where $k_s$ describes the size of field elements and $k_p$ describes the size of group elements.
+
+To examine the verification time complexity, let $t_s$ and $t_p$ be the time complexity of evaluating the hash-to-field functions $\Hs$ and of evaluating the hash-to-group function $\Hp$, respectively.
+Let $t^{(i)}$ be the time complexity to evaluate a linear combination of $i$ terms; using specialized algorithms for multiscalar multiplication \cite{straus1964addition,pippenger1980evaluation}, such a linear combination can be evaluated much more quickly than a simple term-by-term computation.
+We note that it is also possible to cache multiples of group elements that are reused within verification for faster linear combination evaluation, but we do not differentiate this here.
+Using these, the time complexity of $d$-CLSAG verification is $(n+d)t_s + nt_p + 2nt^{(d+1)}$.
+
+To compare to the efficiency of an MLSAG implementation from \cite{noether2016ring}, observe that $2$-CLSAG has equivalent functionality to an MLSAG signature (which is a $2$-LRS).
+An MLSAG signature used in this way produces $2n+1$ field elements and $1$ group element.
+
+We produced a test implementation in C++ using the prime-order subgroup of \texttt{ed25519} and tested signing and verification for MLSAG and $2$-CLSAG on a 2.1 GHz Opteron processor.
+Table \ref{table:timing} shows the results for different ring sizes.
+In particular, we note that for smaller anonymity sizes, $2$-CLSAG is uniformly faster than MLSAG.
+However, at very large ring sizes, MLSAG is faster due to additional computations involved in computing aggregation coefficients and key prefixing.
+Despite this eventual inefficiency, we note that the linear space requirements generally preclude the use of very large ring sizes in practice, making $2$-CLSAG an efficient improvement over MLSAG in both space and time.
+
+\begin{table}[htp]
+\begin{center}
+\begin{tabular}{r|ll|ll}
+& \multicolumn{2}{c|}{Verify} & \multicolumn{2}{c}{Sign} \\
 \hline
-Protocol & Size (proof elements) \\
+Anonymity set & MLSAG & CLSAG & MLSAG & CLSAG \\
 \hline
-RingCT 3.0 (original) \cite{rct3} & $w(2 \lg N + 18) + w + 2$ \\
-RingCT 3.0 (updated) \cite{rct3} & $2\lceil \lg(Nw) \rceil + w + 17$ \\
-Triptych \cite{triptych} & $w(3 \lg N + 8) + w$ \\
-Arcturus (this work) & $(w + 3)\lg N + w + 7$ \\
-\hline
+2 & 2.4 & 2.0 & 2.3 & 2.7 \\
+4 & 4.7 & 4.0 & 4.6 & 4.6 \\
+8 & 9.5 & 7.8 & 9.4 & 8.5 \\
+16 & 18.9 & 15.9 & 18.9 & 16.5 \\
+32 & 37.8 & 32.3 & 37.8 & 33.0 \\
+64 & 75.4 & 67.5 & 75.9 & 68.3 \\
+128 & 150 & 147 & 151 & 148 \\
+256 & 301 & 344 & 303 & 346
 \end{tabular}
-\caption{Proof size (in group/field elements) with varying anonymity set size $N$ and signing keys $w$}
-\label{table:size}
+\end{center}
+\caption{Signing and verification times (ms) for MLSAG and $2$-CLSAG}
+\label{table:timing}
 \end{table}
 
-We also examine the verification complexity of these protocols.
-To do so, we examine the size of all multiscalar multiplication operations needed to verify one or more proofs in a transaction, along with balance proofs.
-Table \ref{table:time} shows the results for various transaction parameters.
-
-\begin{table}
-\centering
-\begin{tabular}{|ll|}
-\hline
-Protocol & Verification complexity \\
-\hline
-RingCT 3.0 (original) \cite{rct3} & $w(2\lg N + 11) + 4N + M + T + 7$ \\
-RingCT 3.0 (updated) \cite{rct3} & $2\lceil \lg(Nw) \rceil + N(w + 3) + M + T + 13$ \\
-Triptych \cite{triptych} & $(2 + 2w)\lg N + 2N + 4w + T + 2$ \\
-Arcturus (this work) & $(3 + 2w)\lg N + 2N + M + T$ \\
-\hline
-\end{tabular}
-\caption{Verification complexity with varying anonymity set size $N$, signing keys $w$, and outputs $T$}
-\label{table:time}
-\end{table}
-
-Since each compared protocol scales differently with the transaction parameters, it is instructive to examine the overall size effects under real-world conditions.
-To do this, we examine data from the Monero blockchain; in particular, for each transaction from 18 October 2018 to 14 February 2020, we extract the number of consumed outputs and the number of newly-generated outputs.
-Coinbase transactions, where new assets are generated by mining on a per-block basis, are ignored since they do not require this type of proof.
-Figure \ref{fig:size} shows this data run against the values in Table \ref{table:size} with additional transaction auxiliary data (including range proofs and recipient-specific data) for increasing anonymity set size $N$.
-Since verification complexity in all the protocols scales approximately linearly with $N$, overall verification time based on this parameter is an important bounding factor.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.6\textwidth]{size.png}
-\caption{Total chain growth by anonymity set size}
-\label{fig:size}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.6\textwidth]{time.png}
-\caption{Total verification time by anonymity set size}
-\label{fig:time}
-\end{figure}
-
-While the updated RingCT 3.0 protocol from \cite{rct3} yields superior space scaling, its requirement that $w$ be a power of two (padded to reach such a value) results in poor verification time scaling.
-Comparatively, our construction results in lower overall verification complexity at the expense of overall size scaling.
-
-\bibliographystyle{plain}
-\bibliography{main}
+\bibliographystyle{splncs04}
+\bibliography{bibliography}
 

### 2020-08-26 paper/iacr.tex
Fix paper notation

--- 2020-05-17 paper/iacr.tex
@@
 Then, the user generates $W$ spend proofs, each using the following prover inputs for $u \in [0,W)$:
-$$\mathcal{P}_{par}(\{M_{i,\alpha}\},r_u^{-1}U;(l_u,\{r_u,s_u-s'_u\}))$$
+$$\mathcal{P}_{par}(\{M_{k,0}\}_{k=0}^{N-1},\{M_{k,1}-P'_u\}_{k=0}^{N-1},r_u^{-1}U;(l_u,r_u,s_u-s'_u))$$
 

### 2020-08-27 slides/main.tex
Add presentation slides

@@
 \documentclass[aspectratio=169]{beamer}
+\usepackage[utf8]{inputenc}
+\usepackage{xcolor,colortbl}
+\usepackage{graphics}
+
 \usepackage{tikz}
-\usetikzlibrary{shapes.geometric}
-\usepackage{amsmath,amssymb}
+\usetikzlibrary{positioning,arrows.meta}
 
+\usecolortheme{wolverine}
+\definecolor{monerorange}{RGB}{255, 102, 0}
+\definecolor{otherorange}{RGB}{253, 188, 148}
+\definecolor{redd}{RGB}{253, 150, 179}
+\definecolor{grenn}{RGB}{150, 253, 189}
+\definecolor{yello}{RGB}{248, 253, 150}
+\setbeamercolor*{palette primary}{bg=otherorange}
+\setbeamercolor*{frametitle}{bg=otherorange}
+\setbeamercolor*{itemize item}{fg=monerorange}
+\setbeamercolor*{itemize subitem}{fg=monerorange}
 \setbeamertemplate{footline}[frame number]
-\setbeamertemplate{navigation symbols}{}
 
-\setbeamercolor{palette primary}{fg=black,bg=white}
-\setbeamercolor{palette secondary}{fg=black,bg=white}
-\setbeamercolor{structure}{fg=black,bg=white}
+\newcommand{\com}{\operatorname{Com}}
 
-% title frame
-\defbeamertemplate*{title page}{mytheme}[1][]
-{
-  \begin{tikzpicture}[remember picture,overlay]
-  \filldraw[white]
-    (current page.north west) --
-    (current page.north east) --
-    ([xshift=0cm,yshift=-2cm]current page.north east)  --
-    ([xshift=0cm,yshift=-2cm]current page.north west) -- cycle
-    ;
-
-  \node[opacity=0.2] at ([xshift=-1.5cm,yshift=-1cm]current page.north east) {\includegraphics[width=15cm]{monkon}};
-
-  \node[text=black,anchor=south west,font=\sffamily\LARGE,text width=.8\paperwidth] at ([xshift=-100pt,yshift=-1cm]current page.center)(title){\raggedright\inserttitle};
-
-  \node[text=black,anchor=south west,font=\sffamily\small,text width=.6\paperwidth] at ([xshift=-100pt,yshift=-1.5cm]current page.center)(institute){\raggedright\insertinstitute};
-
-  \node[text=black,font=\large\sffamily,anchor=south west] at ([xshift=30pt,yshift=0.5cm]current page.south west)(date){\insertdate};
-
-  \node[text=black,font=\large\sffamily,anchor=south west] at ([yshift=5pt]date.north west)(author){\insertauthor};
-  \end{tikzpicture}
-}
-
-% definition of the symbols used in itemize
-\newcommand\mysymbol{%
-  \begin{tikzpicture}[xscale=0.85]
-\draw[black, thick]  circle (1.5 pt);             
-  \end{tikzpicture}%
-  }
-
-% definition of the itemize templates
-\defbeamertemplate*{itemize item}{mysymbol}{\small\raise0.5pt\hbox{\mysymbol}}
-\defbeamertemplate*{itemize subitem}{mysymbol}{\footnotesize\raise0.5pt\hbox{\mysymbol}}
-\defbeamertemplate*{itemize subsubitem}{mysymbol}{\footnotesize\raise0.5pt\hbox{\mysymbol}}
-
-\title[Transaction efficiency then and now]{Transaction efficiency then and now}
+\title{Triptych}
+\subtitle{Logarithmic-sized linkable ring signatures with applications}
 \author{Sarang Noether, Ph.D.}
-\date{23 June 2019}
-
-\institute{Monero Konferenco}
-
+\institute{Monero Research Lab}
+\date{17 September 2020}
 \begin{document}
 
-\begin{frame}[plain]
-\maketitle
+\frame{\titlepage}
+
+\begin{frame}{Goal}
+We want to build a \textbf{confidential transaction} construction with the following properties:
+\begin{itemize}
+\item Trust-free setup and parameters
+\item Sublinear size scaling with anonymity set
+\item Batchable $O(n/\log(n))$ verification
+\item Safely compatible with one-time addressing
+\item Supports multisignature operations
+\end{itemize}
+~\\
+Our construction is \textbf{Triptych}.
+\\~\\
+This is joint work with \textbf{Brandon Goodell}.
 \end{frame}
 
-\begin{frame}
-\frametitle{Disclaimer}
-\begin{columns}
-\begin{column}{0.2\textwidth}
-\includegraphics[width=0.9\textwidth]{monero.png}
-\end{column}
-\begin{column}{0.8\textwidth}
-The views expressed in this presentation are solely those of the author, and do not necessarily reflect those of any other person, organization, or community. \\~\\
+\begin{frame}{Our strategy}
+\begin{center}
+\begin{tikzpicture}[> = {Straight Barb[angle=60:4pt 6]}]
+\node (general) {\underline{General structure}};
+\node (rs) [draw, below=10pt of general] {Ring signature};
+\node (lrs) [draw, below=of rs] {Linkable ring signature};
+\node (2lrs) [draw, below=of lrs] {2-linkable ring signature};
 
-The author receives funding support from the Monero community.
-\end{column}
-\end{columns}
-\end{frame}
+\node (monero) [right=50pt of general] {\underline{Monero protocol}};
+\node (schnorr) [below=10pt of monero] {Schnorr-type SAG};
+\node (lsag) [below=of schnorr] {LSAG};
+\node (clsag) [below=of lsag] {CLSAG/MLSAG};
+\node (ringct) [draw, below=of clsag, align=center] {\textbf{Ring confidential} \\ \textbf{transaction protocol}};
 
-\begin{frame}
-\frametitle{What is transaction efficiency?}
-\begin{columns}
+\node (this) [right=60pt of monero] {\underline{\textbf{This work}}};
+\node (gkb) [below=10pt of this] {\textbf{Groth/Kohlweiss/Bootle}};
+\node (triptych) [below=of gkb] {\textbf{Triptych}};
+\node (2triptych) [below=of triptych] {\textbf{2-Triptych}};
 
-\begin{column}{0.3\textwidth}
-\centering
-\includegraphics[width=0.4\textwidth]{icon-space.png} \\~\\
-\textbf{Space} \\
-Bandwidth/storage
-\end{column}
+\draw[->] (rs) to (lrs);
+\draw[->] (lrs) to (2lrs);
+\draw[->] (2lrs) to (ringct);
 
-\begin{column}{0.3\textwidth}
-\centering
-\includegraphics[width=0.4\textwidth]{icon-hourglass.png} \\~\\
-\textbf{Generation time} \\
-Low-capacity devices
-\end{column}
+\draw[->,dashed] (schnorr) to (lsag);
+\draw[->,dashed] (lsag) to (clsag);
+\draw[->,dashed] (clsag) to (ringct);
 
-\begin{column}{0.3\textwidth}
-\centering
-\includegraphics[width=0.4\textwidth]{icon-stopwatch.png} \\~\\
-\textbf{Verification time} \\
-Chain sync
-\end{column}
-
-\end{columns}
-\end{frame}
-
-\begin{frame}{Levels of optimization}
-\begin{columns}
-\begin{column}{0.5\textwidth}
-We can optimize at difference levels:
-\begin{itemize}
-\item low-level cryptographic operations
-\item higher-level constructions
-\item protocol parameters \\~\\
-\end{itemize}
-
-We will focus on \textit{constructions} today, but all of these have effects.
-\end{column}
-\begin{column}{0.5\textwidth}
-\centering
-\includegraphics[width=0.9\textwidth]{chain-growth.pdf} \\
-Chain growth over time
-\end{column}
-\end{columns}
-\end{frame}
-
-\begin{frame}
-\begin{figure}
-\begin{tikzpicture}[square/.style={regular polygon,regular polygon sides=4}]
-\node [square,draw,fill=lightgray] (sig) {\begin{tabular}{c}Ring \\ signature\end{tabular}};
-\node [ellipse,draw,left=60pt,at=(sig.west),above=20pt] (inputs) {Input keys};
-\node [ellipse,draw,left=60pt,at=(sig.west),below=20pt] (offsets) {\begin{tabular}{c}Commitment \\ offsets\end{tabular}};
-\node [rectangle,draw,right=20pt,at=(sig.east)] (image) {Key image};
-
-\draw [->] (inputs) -- (sig);
-\draw [->] (offsets) -- (sig);
-\draw [->] (sig) -- (image);
+\draw[->,dashed] (gkb) to (triptych);
+\draw[->,dashed] (triptych) to (2triptych);
+\draw[->,dashed] (2triptych) to (ringct);
 \end{tikzpicture}
-\end{figure}
-\centering
-The ring signature proves key ownership, helps demonstrate transaction balance, and asserts correct key image construction.
-\end{frame}
-
-\begin{frame}
-\begin{figure}
-\begin{tikzpicture}[square/.style={regular polygon,regular polygon sides=4}]
-\node [circle,draw] (data) {\begin{tabular}{c}Output data \\ \hline Amount ($v$)\\ Mask ($r$)\end{tabular}};
-\node [rectangle,draw,left=20pt,at=(data.west),fill=lightgray] (enc) {\begin{tabular}{c}Recipient data \\ \hline $\operatorname{Enc}(v)$ \\ $\operatorname{Enc}(r)$\end{tabular}};
-\node [rectangle,draw,right=20pt,at=(data.east)] (commit) {$\operatorname{Commit}(v,r)$};
-\node [rectangle,draw,below=20pt,at=(commit.south),fill=lightgray] (range) {\begin{tabular}{c}Range proof \\ $v \in [0,2^n)$\end{tabular}};
-
-\draw [->] (data) -- (enc);
-\draw [->] (data) -- (commit);
-\draw [->] (commit) -- (range);
-\end{tikzpicture}
-\end{figure}
-\centering
-The output constructions communicate output data to the recipient, are used (with auxiliary commitments) to show balance, and prevent amount overflow.
-\end{frame}
-
-\begin{frame}{Construction: ring signature}
-We use \textbf{MLSAG} signatures to prove ownership of spent outputs without revealing the specific output in question. This type of ring signature shows more, though.
-\begin{itemize}
-\item The signer controls one output among a given set
-\item The key image (used to detect double-spend attempts) was generated correctly
-\item The (hidden) transaction amounts balance \\~\\
-\end{itemize}
-
-These signatures scale \textit{linearly} with the ring size in space, signing time, and verify time.
-\end{frame}
-
-\begin{frame}{CLSAG: the new hotness}
-We propose \textbf{CLSAG} signatures to do the same thing, but more efficiently. \\~\\
-
-CLSAG signatures use a linear combination of output signing keys and commitment keys to provide a drop-in replacement to MLSAG signatures. \\~\\
-
-They still scale linearly, but take up less space and are faster to sign and verify. \\~\\
-
-Security is more formally proven.
-\end{frame}
-
-\begin{frame}{Signature size (11-ring)}
-\centering
-\includegraphics[width=0.7\textwidth]{sig-size.pdf}
-\end{frame}
-
-\begin{frame}{Timing (11-ring)}
-\begin{columns}
-\begin{column}{0.5\textwidth}
-\centering
-\includegraphics[width=\textwidth]{sig-sign.pdf} \\~\\
-\textbf{Signing}
-\end{column}
-\begin{column}{0.5\textwidth}
-\centering
-\includegraphics[width=\textwidth]{sig-verify.pdf} \\~\\
-\textbf{Verification}
-\end{column}
-\end{columns}
-\end{frame}
-
-\begin{frame}{Construction: commitments}
-All amounts are represented as Pedersen commitments with globally fixed base:
-$$\operatorname{Commit}(v,r) \equiv \underbrace{vH}_{\text{value}} + \underbrace{rG}_{\text{mask}}$$
-
-The recipient needs to know both $v$ and $r$ to reconstruct the commitment and later use it in a ring signature to spend the output. \\~\\
-
-Previously, both values were encrypted using the transaction shared secret $\operatorname{H}(aR,i)$:
-\begin{eqnarray*}
-\operatorname{Enc}(v) &\equiv& v + \operatorname{H}(\operatorname{H}(\operatorname{H}(aR,i))) \\
-\operatorname{Enc}(r) &\equiv& r + \operatorname{H}(\operatorname{H}(aR,i))
-\end{eqnarray*}
-\end{frame}
-
-\begin{frame}{New hotness: being clever}
-\textbf{This is wasteful}.
-If generated randomly, both $r$ and $\operatorname{Enc}(r)$ are uniformly distributed and known only to the sender and recipient.
-So why include $\operatorname{Enc}(r)$ in the transaction at all?
-\\~\\
-
-\textbf{Solution}: Do not include $\operatorname{Enc}(r)$.
-The sender and recipient both compute $$r \equiv \operatorname{H}(``\text{commitment\_mask}",\operatorname{H}(aR,i))$$ instead, and save $32$ bytes per output.
-\\~\\
-\end{frame}
-
-\begin{frame}{New hotness: being clever}
-\textbf{This is still wasteful}. The amount cannot be larger than $8$ bytes, but is represented as a $32$-byte scalar. \\~\\
-
-\textbf{Solution}: Restrict the amount representation to $8$ bytes and encrypt with a length-restricted XOR operation to save $24$ bytes per output:
-
-$$\operatorname{Enc}(v) \equiv \Big( v \oplus \operatorname{H}(``\text{amount}",\operatorname{H}(aR,i)) \Big)_{0-7}$$
-
-The full 32-byte scalar can be recovered in the same way.
-\end{frame}
-
-\begin{frame}{Commitment data size}
-\centering
-\includegraphics[width=0.7\textwidth]{commit.pdf}
-\end{frame}
-
-\begin{frame}{Construction: range proofs}
-Since amounts are represented as commitments and balance is proven using commitment sums and differences, amounts must be restricted (relative to scalar field size) to avoid overflow. \\~\\
-
-We must show that for $\operatorname{Commit}(v,r)$, the value $v$ is in the range $[0,2^{64})$. \\~\\
-
-\textbf{Strategy}: Show that $v$ can be decomposed to $64$ bits, each of which is $0$ or $1$, without revealing the value of the bits. \\~\\
-
-\textbf{Example}: $13_{10} = 1101_2 = (1 \times 2^3) + (1 \times 2^2) + (0 \times 2^1) + (1 \times 2^0)$
-\end{frame}
-
-\begin{frame}{Old way: bitwise ring signatures}
-The previous method, bitwise Borromean range proofs, used ring signatures.
-\begin{itemize}
-\item Construct $64$ commitments, each to a bit of $v$, with masks that sum appropriately.
-\item Build a ring signature over each bit commitment to show the value is either $0$ or $1$. \\~\\
-\end{itemize}
-
-To verify:
-\begin{itemize}
-\item Take a weighted sum of the bit commitments (using powers of $2$) and show it recovers the full amount commitment.
-\item Verify the ring signature to assert that each commitment is to $0$ or $1$. \\~\\
-\end{itemize}
-
-This scales in space and time linearly with the number of bits!
-\end{frame}
-
-\begin{frame}{Bulletproofs: the new hotness}
-Bulletproofs take a different approach.
-\begin{itemize}
-\item Reduce the range assertion to a set of vector inner product equations.
-\item Prove knowledge of vector components in zero knowledge.
-\item Compress this proof using a clever folding technique. \\~\\
-\end{itemize}
-
-This achieves precisely the same goal as bitwise Borromean proofs, but scales logarithmically with the number of bits. Plus:
-\begin{itemize}
-\item A prover can include multiple values in the same proof, to extend the logarithmic space scaling.
-\item Generation and verification are still linear in the bit length, but we can use tricks.
-\item Verification of a set of proofs adds only marginal time cost! (This is \textit{batching}.)
-\end{itemize}
-\end{frame}
-
-\begin{frame}{2-output verification}
-\centering
-\includegraphics[width=0.7\textwidth]{bp-2.pdf}
-\end{frame}
-
-\begin{frame}{16-output verification}
-\centering
-\includegraphics[width=0.7\textwidth]{bp-16.pdf}
-\end{frame}
-
-\begin{frame}{2-output 128-batch verification}
-\centering
-\includegraphics[width=0.7\textwidth]{bp-2-batch-128.pdf}
-\end{frame}
-
-\begin{frame}{Proof size}
-\centering
-\includegraphics[width=0.7\textwidth]{bp-size.pdf}
-\end{frame}
-
-\begin{frame}{Typical transaction}
-\begin{columns}
-\begin{column}{0.5\textwidth}
-\centering
-\includegraphics[width=\textwidth]{txn-size-2-2.pdf} \\~\\
-\textbf{Transaction size}
-\end{column}
-\begin{column}{0.5\textwidth}
-\centering
-\includegraphics[width=\textwidth]{txn-time-2-2.pdf} \\~\\
-\textbf{Verification time}
-\end{column}
-\end{columns}
-\begin{center}
-We save $85\%$ on space and up to $81\%$ on verification time!
 \end{center}
@@
 
-\begin{frame}
+\begin{frame}{Ring signatures}
+A \textbf{ring signature} is a signature construction that signs a message on behalf of a \underline{non-interactive} anonymity set of public keys.
+The signer knows the secret key to (at least) one of the public keys in the set.
+\\~\\
+The verifier learns only that one key in the public key set is the signer, but not which one. So
+$$\operatorname{Sign}(m,\{M_0,M_1,\ldots\};(l,r)) \to \sigma$$
+signs message $m$ such that $M_l$ has $r$ as its secret key, and
+$$\operatorname{Verify}(m,\{M_0,M_1,\ldots\},\sigma) \to \{0,1\}$$
+verifies.
+\end{frame}
+
+\begin{frame}{Ring signatures}
 \begin{center}
-\textbf{These are not complete scaling solutions!}
+\begin{tikzpicture}[
+    box/.style = {draw, minimum width=30pt, minimum height=20pt, rounded corners, align=center},
+    dot/.style = {draw, minimum width=30pt, minimum height=20pt, dashed, rounded corners, align=center},
+    > = {Straight Barb[angle=60:4pt 6]}
+]
+\node (rs) [draw, minimum width=100pt, minimum height=40pt] {Ring signature};
+\node (M1) [dot, left=of rs] {$M_1$};
+\node (M0) [box, above=of M1] {$M_0$};
+\node (M2) [box, below=of M1] {$M_2$};
+\node (msg) [box, below=of rs] {message};
+\node (sig) [box, right=of rs] {$\sigma$};
+
+\draw[-] (M0) to (M1);
+\draw[-] (M1) to (M2);
+\draw[->] (M1) to (rs);
+\draw[->] (msg) to (rs);
+\draw[->] (rs) to (sig);
+\end{tikzpicture}
 \end{center}
+\end{frame}
 
-These are incremental (but useful) improvements to slow blockchain growth and speed up new node sync time. \\~\\
+\begin{frame}{Groth/Kohlweiss/Bootle (GKB) ring signatures}
+A paper (IACR 2014/764) by \textbf{Groth} and \textbf{Kohlweiss} uses a novel zero-knowledge proving system to build a ring signature construction; it was made more efficient (IACR 2015/643) by \textbf{Bootle} and collaborators.
+\\~\\
+It builds a sigma protocol for the relation
+$$\Big\{\{M_0,\ldots,M_{N-1}\};(l,r) : 0 \leq l < N, M_l = \com(0,r)\Big\}$$
+for commitment scheme $\com$, logarithmic in size with $N$.
+\\~\\
+To transform into a ring signature scheme, use the Fiat-Shamir heuristic and embed the message into the transcript hash.
+\end{frame}
 
+\begin{frame}{Properties}
+Informally, we want several useful properties. These follow nicely from properties of the underlying sigma protocol.
+\\~\\
 \begin{itemize}
-\item Sublinear fixed-decoy transaction protocols
+\item \textbf{Correctness}. Honest signatures always verify.
 \begin{itemize}
-\item Lelantus
-\item Omniring
+\item Completeness
 \end{itemize}
-\item Efficient full-anonymity transaction protocols
+\item \textbf{Anonymity}. It is not feasible to determine the signing index.
 \begin{itemize}
-\item Bulletproofs (poor verification scaling for circuits)
-\item Older-style SNARKs (toxic; excellent space/time scaling)
-\item Newer-style SNARKs (nontoxic; better scaling, but not quite there)
+\item Zero knowledge
 \end{itemize}
-\item Off-chain transaction layers (requires new plumbing)
+\item \textbf{Unforgeability}. It is not feasible to generate a signature without secret key knowledge.
 \begin{itemize}
-\item Atomic swaps
-\item Payment channels/networks
+\item (Special) soundness
 \end{itemize}
@@
 
-\begin{frame}{Thank you!}
-\textbf{GitHub}: \texttt{https://github.com/SarangNoether}
+\begin{frame}{Linkable ring signatures}
+What if we wish to identify duplicate signing in a safe way?
+\\~\\
+A \textbf{linkable ring signature} is a ring signature that adds \underline{linkability} to the signature. Any two valid signatures that link were generated using the same (unknown) secret key. So
+$$\operatorname{Link}(\sigma,\sigma') \to \{0,1\}$$
+identifies whether two signatures were signed by the same key.
+\\~\\
+The selection of the anonymity sets can be extremely important for practical security.
+\\~\\
+It is possible to build constructions that are either dependent or independent of the anonymity set.
+\end{frame}
+
+\begin{frame}{Triptych linkable ring signature}
+We introduce (IACR 2020/018) \textbf{Triptych} by adding linkability to the GKB construction.
+\\~\\
+It builds a sigma protocol for the relation
+$$\Big\{\{M_0,\ldots,M_{N-1}\}, J;(l,r) : 0 \leq l < N, M_l = \com(0,r), rJ = U\Big\}$$
+for globally fixed $U$, where $J$ is the \underline{linking tag}. To check linkability, compare tags.
+\\~\\
+To transform into a linkable ring signature scheme, use the Fiat-Shamir heuristic and embed the message into the transcript hash.
+\end{frame}
+
+\begin{frame}{From GKB to Triptych}
+How does the extension from GKB to Triptych work? Treat commitments to zero as public keys, with group generator $G$.
+\\~\\
+In GKB, we prove knowledge of $r$ such that some commitment is of the form $rG = M$.
+\\~\\
+In Triptych, we reuse some of this hidden proof data about $r$ to show that $U$ is of the form $rJ = U$.
+Since $U$ is globally fixed, the prover can only do this if it specifies $J \equiv (1/r)U$, which is a verifiable random function.
+\\~\\
+Because the sigma protocol is (special) sound and the map $r \mapsto J$ is a bijection, we obtain linkability.
+\end{frame}
+
+\begin{frame}{2-linkable ring signatures}
+We now extend linkable ring signatures to show knowledge of keys in \underline{parallel lists} of public keys.
+\\~\\
+The signer provides two lists of public keys, and shows they know the secret key to \underline{both} public keys at the \underline{same} unknown index in both lists.
+\\~\\
+We will still retain linkability, but only for one of the lists (more on this soon)!
+\end{frame}
+
+\begin{frame}{2-linkable ring signatures}
+\begin{center}
+\begin{tikzpicture}[
+    box/.style = {draw, minimum width=30pt, minimum height=20pt, rounded corners, align=center},
+    dot/.style = {draw, minimum width=30pt, minimum height=20pt, dashed, rounded corners, align=center},
+    > = {Straight Barb[angle=60:4pt 6]}
+]
+\node (rs) [draw, minimum width=100pt, minimum height=40pt, align=center] {2-linkable \\ ring signature};
+\node (M1) [dot, left=of rs] {$M_1$};
+\node (M0) [box, above=of M1] {$M_0$};
+\node (M2) [box, below=of M1] {$M_2$};
+
+\node (P1) [dot, left=of M1] {$P_1$};
+\node (P0) [box, above=of P1] {$P_0$};
+\node (P2) [box, below=of P1] {$P_2$};
+
+\node (msg) [box, below=of rs] {message};
+\node (sig) [box, right=of rs] {$\sigma$};
+
+\draw[-] (M0) to (M1);
+\draw[-] (M1) to (M2);
+\draw[-] (M0) to (P0);
+\draw[-] (M1) to (P1);
+\draw[-] (M2) to (P2);
+\draw[->] (M1) to (rs);
+\draw[->] (msg) to (rs);
+\draw[->] (rs) to (sig);
+\end{tikzpicture}
+\end{center}
+\end{frame}
+
+\begin{frame}{Triptych 2-linkable ring signature}
+We modify Triptych to construct a 2-linkable ring signature; this can even be done more generally.
+\\~\\
+It builds a sigma protocol for the relation
+\begin{multline*}
+\Big\{\{M_0,\ldots,M_{N-1}\}, \{P_0,\ldots,P_{N-1}\}, J;(l,r,s) : \\
+0 \leq l < N, M_l = \com(0,r), P_l = \com(0,s), rJ = U\Big\}
+\end{multline*}
+that now includes two public key lists.
+\\~\\
+While we need new proof data about the secret key $s$, we can reuse existing proof data about the index $l$.
+\end{frame}
+
+\begin{frame}{Ring confidential transaction protocol}
+We wish to build a \textbf{confidential transaction} protocol that:
 \begin{itemize}
-\item \texttt{research-lab}: older research
-\item \texttt{skunkworks}: newer research (work in branches) \\~\\
+\item Consumes multiple transaction outputs
+\item Generates multiple transaction outputs
+\item Hides output amounts
+\item Hides signing indices
+\item Supports in-band stealth addressing
 \end{itemize}
+~\\
+We can do this using arbitrary 2-linkable ring signatures, like 2-Triptych or CLSAG.
+\end{frame}
 
-\textbf{GitLab}: \texttt{https://repo.getmonero.org/SarangNoether}
+\begin{frame}{Ring confidential transaction protocol}
+Define a Pedersen commitment $\com(v,r) \equiv vH + rG$ for group generators $G,H$.
+\\~\\
+We wish to generate a transaction consuming $W$ existing outputs and generating $T$ new outputs.
+\\~\\
+Form a single anonymity set of $N \geq W$ public keys $\{M_k\}_{k=0}^{N-1}$ such that for a secret index set $\{l_u\}_{u=0}^{W-1} \subset [0,N)$, we have $M_{l_u} = r_uG$ for all $0 \leq u < W$, where each $r_u$ is a secret key.
+\end{frame}
+
+\begin{frame}{Ring confidential transaction protocol}
+Let's see an example, where $W = 3$ and $N \geq 3$ is arbitrary.
+
+\begin{center}
+\begin{tikzpicture}
+\node (M0) {$M_0$};
+\node (M1) [right=of M0] {$M_1$};
+\node (M2) [right=of M1] {$M_2$};
+\node (dots) [right=of M2] {$\cdots$};
+\node (MN1) [right=of dots] {$M_{N-1}$};
+\node (r0) [below=of M2] {$r_0$};
+\node (r1) [below=of M0] {$r_1$};
+\node (r2) [below=of MN1] {$r_2$};
+
+\draw[-, dashed] (r0) to (M2);
+\draw[-, dashed] (r1) to (M0);
+\draw[-, dashed] (r2) to (MN1);
+\end{tikzpicture}
+\end{center}
+
+So the secret index set is $\{l_u\}_{u=1}^{W-1} = \{2, 0, N-1\}$.
+\end{frame}
+
+\begin{frame}{Ring confidential transaction protocol}
+Each of the $0 \leq u < W$ consumed outputs comes associated with a commitment to an amount $a_u$:
+$$P_{l_u} \equiv \com(a_u,s_u)$$
+
+Because the Triptych proving system assumes knowledge of commitments to zero, form an \underline{commitment offset} for each consumed output, with the same value but a uniformly random mask:
+$$P'_u \equiv \com(a_u,s'_u)$$
+
+This gives these commitments to zero:
+$$P_{l_u} - P'_u = \com(a_u,s_u) - \com(a_u,s'_u) = \com(0,s_u-s'_u)$$
+\end{frame}
+
+\begin{frame}{Ring confidential transaction protocol}
+Generate $0 \leq j < T$ new outputs, where each has an associated amount commitment (and range proof):
+$$Q_j \equiv \com(b_j,t_j)$$
+We choose, for $1 \leq j < T$, random masks $t_j$. Then we set
+$$t_0 \equiv \sum_{u=0}^{W-1} s'_u - \sum_{j=1}^{T-1} t_j$$
+such that, if the consumed and generated amounts balance, the verifier can perform this check:
+$$\sum_{u=0}^{W-1} P'_u - \sum_{j=0}^{T-1} Q_j = 0$$
+\end{frame}
+
+\begin{frame}{Ring confidential transaction protocol}
+Finally, generate a signature for each of the $0 \leq u < W$ consumed outputs, using the following 2-Triptych relation inputs:
+$$\Big\{\{M_k\}_{k=0}^{N-1},\{P_k-P'_u\}_{k=0}^{N-1},(1/r_u)U; (l_u,r_u,s_u-s'_u)\Big\}$$
+To verify such a transaction:
+\begin{itemize}
+\item Verify each of the linkable ring signatures
+\item Perform a linking test among all signatures
+\item Ensure the balance check succeeds
+\item Verify all output range proofs
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\centering
+\includegraphics[width=\textwidth]{protocol.jpeg}
+\end{frame}
+
+\begin{frame}{Comparison}
+\begin{center}
+\renewcommand{\arraystretch}{1.5}
+\begin{tabular}{|r|ccccc|}
+\hline
+& Size & Verification & Batching & Addressing & Aggregation \\
+\hline
+\textbf{Triptych} & \cellcolor{grenn} $O(\log N)$ & \cellcolor{yello} $O(N/\log N)$ & \cellcolor{grenn} yes & \cellcolor{grenn} yes & \cellcolor{redd} no \\
+Arcturus & \cellcolor{grenn} $O(\log N)$ & \cellcolor{yello} $O(N/\log N)$ & \cellcolor{grenn} yes & \cellcolor{grenn} yes & \cellcolor{grenn} yes \\
+CLSAG & \cellcolor{redd} $O(N)$ & \cellcolor{redd} $O(N)$ & \cellcolor{redd} no & \cellcolor{grenn} yes & \cellcolor{redd} no \\
+Lelantus & \cellcolor{grenn} $O(\log N)$ & \cellcolor{yello} $O(N/\log N)$ & \cellcolor{grenn} yes & \cellcolor{redd} no & \cellcolor{redd} no \\
+Omniring & \cellcolor{grenn} $O(\log N)$ & \cellcolor{yello} $O(N/\log N)$ & \cellcolor{redd} no & \cellcolor{grenn} yes & \cellcolor{grenn} yes \\
+RingCT 3.0 & \cellcolor{grenn} $O(\log N)$ & \cellcolor{yello} $O(N/\log N)$ & \cellcolor{grenn} yes & \cellcolor{grenn} yes & \cellcolor{yello} padded \\
+\hline
+\end{tabular}
+\end{center}
+
+\begin{center}
+This chart is intentionally oversimplified.
+\end{center}
+\end{frame}
+
+\begin{frame}{Conclusions}
+\textbf{Triptych} is a zero-knowledge proving system that can be used to construct a linkable (and 2-linkable!) ring signature construction, which in turn can power a confidential transaction model.
+It:
+\begin{itemize}
+\item Requires no trusted setup or parameters
+\item Scales logarithmically in size (with superior size for reasonable anonymity sets)
+\item Scales (sub)-linearly in verification time, with batching
+\item Is fully compatible with in-band stealth addressing
+\item Supports multisignature operations via Paillier secret sharing
+\end{itemize}
+\begin{center}
+~\\
+\textbf{\Large Questions?}
+\end{center}
 \end{frame}

### 2020-09-17 paper/iacr.tex
Updated security proof

--- 2020-05-17 paper/iacr.tex
@@
 \fbox{\begin{minipage}{0.95\textwidth}
-$\underline{\mathcal{P}_{\text{link}}(\{M_i\},J;(l,r)):}$
+$\underline{\mathcal{P}:}$
 \begin{itemize}
-\item Select random $r_A \in \F$ and $\left\{a_{j,i}\right\}_{i=1,j=0}^{n-1,m-1} \subset \F$.
-Set $$\{a_{j,0}\}_{j=0}^{m-1} \equiv -\sum_{i=1}^{n-1} a_{j,i}$$ and define $A \equiv \com(a,r_A)$.
-\item Define $\left\{\sigma_{j,i}\right\}_{i,j=0}^{n-1,j-1} \subset \F$ such that $\sigma_{j,i} \equiv \delta\left(l_j,i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
+\item Select random $r_A \in \F$ and $\left\{a_{j,i}^{(u)}\right\}_{i=1,j,u=0}^{n-1,m-1,w-1} \subset \F$.
+Set $$\{a_{j,0}^{(u)}\}_{j,u=0}^{m-1,w-1} \equiv -\sum_{i=1}^{n-1} a_{j,0}^{(u)}$$ and define $A \equiv \com(a,r_A)$.
+\item Define $\left\{\sigma_{j,i}^{(u)}\right\}_{i,j,u=0}^{n-1,m-1,w-1} \subset \F$ such that $\sigma_{j,i}^{(u)} \equiv \delta\left(l_j^{(u)},i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
 Define $B \equiv \com(\sigma,r_B)$.
@@
 \begin{proof}
-The proof follows similarly to that of \cite{bootle}.
+The proof proceeds similarly to that of \cite{triptych}, which in turn follows the methods in \cite{groth,bootle}.
 
-% Completeness
-We first show perfect completeness.
-Suppose the verifier receives a proof generated by an honest prover.
-Equation \ref{eqn:ab} holds using the identity $$\sumi \sigma_{j,i} = 1$$ for all $0 \leq j < m$.
-Equation \ref{eqn:cd} follows similarly, using the identity $$\left(\sigma_{j,i}\right)^2 = \sigma_{j,i}$$ for all $0 \leq j < m$.
-To show Equation \ref{eqn:x} holds:
+To show the protocol is perfectly complete, suppose a verifier receives an honest proof.
+We wish to show that all verifier equations hold.
+
+To show that Equation \ref{eqn:ab} holds, observe that since
 \begin{eqnarray*}
-&& \sumk M_k \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG \\
-&=& \sumk M_k p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}M_k + \rho_jG \right) - zG \\
-&=& \sumk M_k \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \rho_jG - zG \\
-&=& \sumk M_k \xi^m \delta(l,k) - \sumj \xi^j \rho_jG - \left( r\xi^m - \sumj \rho_j\xi^j \right)G \\
-&=& \xi^mrG - \sumj \xi^j \rho_jG - \xi^mrG + \sumj \xi^j \rho_jG \\
+A + \xi B &=& \com(a + \xi\sigma,r_A + \xi r_B) \\
+&=& \com(a + \xi\sigma,z_A),
+\end{eqnarray*}
+it suffices to show that $f_{j,i}^{(u)} = a_{j,i}^{(u)} + \xi\sigma_{j,i}^{(u)}$ for all $0 \leq i < n$ and $0 \leq j < m$ and $0 \leq u < w$.
+If $i \neq 0$, then this equation holds by definition of $f_{j,i}^{(u)}$.
+The case $i = 0$ proceeds differently.
+To show it, we will use the fact that $$\sumi \sigma_{j,i}^{(u)} = 1$$ for all $0 \leq j < m$ and $0 \leq u < w$ by construction:
+\begin{eqnarray*}
+f_{j,0}^{(u)} &=& \xi - \sum_{i=1}^{n-1} f_{j,i}^{(u)} \\
+&=& \xi - \sum_{i=1}^{n-1} \left( a_{j,i}^{(u)} + \xi\sigma_{j,i}^{(u)} \right) \\
+&=& \xi - \sum_{i=1}^{n-1} a_{j,i}^{(u)} - \xi\sum_{i=1}^{n-1} \sigma_{j,i}^{(u)} \\
+&=& \xi + a_{j,0}^{(u)} - \xi\left( 1 - \sigma_{j,0}^{(u)} \right) \\
+&=& a_{j,0}^{(u)} + \xi\sigma_{j,0}^{(u)}
+\end{eqnarray*}
+
+We now show that Equation \ref{eqn:cd} holds.
+Since
+\begin{eqnarray*}
+\xi C + D &=& \com(\xi a(1 - 2\sigma) - a^2,\xi r_C + r_D) \\
+&=& \com(\xi a(1 - 2\sigma) - a^2,z_C),
+\end{eqnarray*}
+it suffices to show that $$f_{j,i}^{(u)}\left( \xi - f_{j,i}^{(u)} \right) = \xi a_{j,i}^{(u)}\left( 1 - 2\sigma_{j,i}^{(u)} \right) - \left(a_{j,i}^{(u)}\right)^2$$ for all $0 \leq i < n$ and $0 \leq j < m$ and $0 \leq u < w$.
+We use our previous work and the fact that each $\left(\sigma_{j,i}^{(u)}\right)^2 = \sigma_{j,i}^{(u)}$ since $\sigma_{j,i}^{(u)} \in \{0,1\}$:
+\begin{eqnarray*}
+f_{j,i}^{(u)}\left( \xi - f_{j,i}^{(u)} \right) &=& \left( a_{j,i}^{(u)} + \xi\sigma_{j,i}^{(u)} \right)\left( \xi - a_{j,i}^{(u)} - \xi\sigma_{j,i}^{(u)} \right) \\
+&=& a_{j,i}^{(u)}\xi - \left(a_{j,i}^{(u)}\right)^2 - 2a_{j,i}^{(u)}\xi\sigma_{j,i}^{(u)} + \left( \xi^2\sigma_{j,i}^{(u)} - \xi^2\left(\sigma_{j,i}^{(u)}\right)^2 \right) \\
+&=& a_{j,i}^{(u)}\xi - \left(a_{j,i}^{(u)}\right)^2 - 2a_{j,i}^{(u)}\xi\sigma_{j,i}^{(u)} + \left( \xi^2\left(\sigma_{j,i}^{(u)}\right)^2 - \xi^2\left(\sigma_{j,i}^{(u)}\right)^2 \right) \\
+&=& \xi a_{j,i}^{(u)}\left( 1 - 2\sigma_{j,i}^{(u)} \right) - \left(a_{j,i}^{(u)}\right)^2
+\end{eqnarray*}
+
+Next, we show that Equation \ref{eqn:x} holds:
+\begin{eqnarray*}
+&& \sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj \xi^jX_j - \sumu z^{(u)}_RG \\
+&=& \sumk \mu_kM_k p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}\mu_kM_k + \sumu \rho^{(u)}_jG \right) - \sumu z^{(u)}_RG \\
+&=& \sumk \mu_kM_k \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \sumu \rho^{(u)}_jG - \sumu z^{(u)}_RG \\
+&=& \sumk \mu_kM_k \left[ \xi^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj \xi^j \sumu \rho^{(u)}_jG - \sumu\left[ \mu_{l^{(u)}}r^{(u)}\xi^m - \sumj \rho^{(u)}_j\xi^j \right]G \\
+&=& \xi^m\sumu \mu_{l^{(u)}}r^{(u)}G - \sumj \xi^j \sumu \rho^{(u)}_jG - \xi^m\sumu \mu_{l^{(u)}}r^{(u)}G + \sumj \xi^j \sumu \rho^{(u)}_jG \\
 &=& 0
 \end{eqnarray*}
-Equation \ref{eqn:y} follows similarly:
+
+Equation \ref{eqn:y} holds with similar algebra:
 \begin{eqnarray*}
-&& U \sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ \\
-&=& U \sumk p_k(\xi) - \sumj \xi^j \left( U \sumk p_{k,j} + \rho_jJ \right) - zJ \\
-&=& U \sumk \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \rho_jJ - zJ \\
-&=& U \sumk \xi^m \delta(l,k) - \sumj \xi^j \rho_jJ - \left( r\xi^m - \sumj \rho_j\xi^j \right)J \\
-&=& \xi^mU - \sumj \xi^j \rho_jG - \xi^mrJ + \sumj \xi^j \rho_jG \\
+&& \sumk \mu_kU \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj \xi^jY_j - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu_kU p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}\mu_kU + \sumu \rho^{(u)}_jJ^{(u)} \right) - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu_kU \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \sumu \rho^{(u)}_jJ^{(u)} - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu_kU \left[ \xi^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj \xi^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - \sumu\left[ \mu_{l^{(u)}}r^{(u)}\xi^m - \sumj \rho^{(u)}_j\xi^j \right](r^{(u)})^{-1}U \\
+&=& x^m\sumu \mu_{l^{(u)}}U - \sumj \xi^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - \xi^m\sumu \mu_{l^{(u)}}U + \sumj \xi^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U \\
 &=& 0
 \end{eqnarray*}
-since $J = r^{-1}U$ in a valid proof.
-Hence the protocol is perfectly complete.
 
-% SHVZK
-We next show that the protocol is special honest-verifier zero knowledge.
-To do so, we construct a simulator that, given a random verifier challenge $\xi$, can construct a proof transcript with identical distribution to a valid proof.
+Finally, we show that Equation \ref{eqn:z} holds:
+\begin{eqnarray*}
+&& \sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj \xi^jZ_j - \xi^m\sum_{j=0}^{T-1} Q_j - z_SG \\
+&=& \sumk P_k p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}P_k + \sumu \overline{\rho}^{(u)}_jG \right) - \xi^m\sum_{j=0}^{T-1} Q_j - z_SG \\
+&=& \sumk P_k \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \sumu \overline{\rho}^{(u)}_jG - \xi^m\sum_{j=0}^{T-1} Q_j - z_SG \\
+&=& \xi^m\sumu (s^{(u)}G + a_uH) - \sumj \xi^j \sumu \overline{\rho}^{(u)}_jG - \xi^m\sum_{j=0}^{T-1} (t_jG + b_jH) - \xi^m\left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right)G + \\
+&& \sumj \xi^j \sumu \overline{\rho}^{(u)}_jG \\
+&=& \left( \sumu a_u - \sum_{j=0}^{T-1} b_j \right)H \\
+&=& 0
+\end{eqnarray*}
+Hence, the protocol is perfectly complete.
 
-First, observe that the simulator presented in the proof of Lemma 1 in \cite{bootle} translates identically to our setting.
-If the simulator chooses $B \in \G$ uniformly at random, the cited lemma assures us a valid simulation of the proof elements $A,C,D,z_A,z_C,\{f^{(u)}_{j,i \neq 0}\}$; we may compute each $f^{(u)}_{j,0}$ from this.
-Further, in a valid proof, $B$ is independent and uniformly distributed as well.
+Next, we show that the sigma protocol is special honest-verifier zero knowledge.
+To do so, we construct a simulator that, when given a random verifier challenge $\xi$, can construct a proof transcript with identical distribution to a valid proof.
 
-The proof elements $\{X_j\}_{j=1}^{m-1}$ and $\{Y_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof since the set $\{\rho_j\}$ is random and the discrete logarithm problem in $\G$ is hard, so the simulator may choose these uniformly at random.
-The verification checks require that $X_0$ and $Y_0$ be uniquely determined by the other elements in the corresponding sets in both real proofs and by the simulator.
+Observe first that the simulator presented in the proof of Lemma 1 in \cite{bootle} translates nearly identically to our setting, since we can flatten tensor commitments to a matrix structure with the required sum property.
+The simulator first chooses $B \in \G$ uniformly at random; then, the cited lemma assures a valid simulation of the proof elements  $A,C,D,z_A,z_C,\{f^{(u)}_{j,i \neq 0}\}$, and from this we may compute $\{f^{(u)}_{j,0}\}$.
+In a valid proof, $B$ is also uniformly distributed.
 
-Finally, $z$ is uniformly distributed in valid proofs given random $\xi$, so the simulator may choose it uniformly at random.
-Hence the construction is special honest verifier zero-knowledge.
+The proof elements $\{X_j\}_{j=1}^{m-1},\{Y_j\}_{j=1}^{m-1}, \{Z_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof since the elements of $\{\rho_j\},\{\overline{\rho}_j\}$ are uniformly distributed and the discrete logarithm problem in $\G$ is hard; hence, the simulator chooses them uniformly at random.
+Since the verification checks require that $X_0,Y_0,Z_0$ be uniquely determined by the other elements in the respective sets, they are selected by the simulator in this manner.
 
-% Soundness
-It remains to show that the protocol is $(m+1)$-special sound, where $m > 1$.
-To show this, we construct an extractor that, given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness.
+Finally, the elements $\{z^{(u)}_R\}_{u=0}^{w-1}$ and $z_S$ are independent and uniformly distributed in valid proofs given a random verifier challenge $\xi$, so the simulator may choose them uniformly at random.
+Hence the protocol is special honest verifier zero-knowledge.
 
-Suppose that for a given statement, we have a set of $m+1$ distinct verifier challenges $\{\xi_e\}_{e=0}^m$ corresponding to unique valid responses of this form:
-$$\left\{ \{f^{(e)}_{j,i}\}, \{z_e\} \right\}_{e=0}^m$$
-From the $3$-special soundness in \cite{bootle} and $m > 1$ we have valid extractions $\{\sigma_{j,i}\}_{j,i=0}^{m-1,n-1}$ and $\{a_{j,i}\}_{j,i=0}^{m-1,n-1}$, and the Pedersen binding property ensures that (with high probability) we have:
-$$f^{(e)}_{j,i} = \sigma_{j,i}\xi_e + a_{j,i}$$
-for all $e \in [0,m]$.
-Using the extracted values, compute
-$$p_k(\xi) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}\xi + a_{j,k} \right)$$
+We claim that the protocol is $(m+1)$-special sound, where $m > 1$.
+To show this, we construct an extractor that, when given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness for the statement.
+In particular, we produce a modified witness for the following relation that is based on the information presented in the prover algorithm, where we define aggregation coefficients $\mu_k$ as before:
+\begin{multline*}
+\mathcal{R}' \equiv \Bigg\{ \{M_k\}_{k=0}^{N-1},\{P_k\}_{k=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \\
+\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sumu \mu_{l^{(u)}} r^{(u)}G \text{ and } \sumu \mu_{l^{(u)}} r^{(u)}J^{(u)} = \sumu \mu_{l^{(u)}} U \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \Bigg\}
+\end{multline*}
+Observe that if we assume that the dual-target discrete logarithm problem is hard in $\G$, extraction of a witness for $\mathcal{R}'$ implies knowledge of a corresponding witness for $\mathcal{R}$; this in turn provides the desired soundness.
+
+Suppose that for a given statement, we have a set of $(m+1)$ distinct verifier challenges $\{\xi_e\}_{e=0}^m$ corresponding to distinct valid responses of this form:
+$$\left\{ \{{}_ef^{(u)}_{j,i}\}, \{{}_ez^{(u)}_R\}, {}_ez_S \right\}_{e=0}^m$$
+From the $3$-special soundness in \cite{bootle} and $m > 1$ we have valid extractions $\{\sigma^{(u)}_{j,i}\}_{u=0}^{w-1}$ and $\{a^{(u)}_{j,i}\}_{u=0}^{w-1}$, and the Pedersen binding property ensures that (with high probability) we have:
+$${}_ef^{(u)}_{j,i} = \sigma^{(u)}_{j,i}\xi_e + a^{(u)}_{j,i} \; \forall \: e \in [0,m]$$
+Using the extracted values, compute the polynomial
+$$p_k(x) \equiv \sum_{u=0}^{w-1}\left[ \prod_{j=0}^{m-1} \left( \sigma^{(u)}_{j,k}x + a^{(u)}_{j,k} \right) \right]$$
 for all $k \in [0,N)$.
-Extraction of $\{\sigma_{j,i}\}_{j,i=0}^{m-1,n-1}$ immediately yields the signing index $l$.
+Extraction of $\{\sigma^{(u)}_{j,i}\}_{u=0}^{w-1}$ immediately yields the signing index set $\{l^{(u)}\}_{u=0}^{w-1}$.
 
-We have seen that $p_k$ is of degree $m$ only when $k = l$.
-Hence there exist coefficients $\{\overline{X}_j,\overline{Y}_j\}_{j=0}^{m-1}$, computed uniquely from the statement and extracted values, such that Equations \ref{eqn:x} and \ref{eqn:y} are of the following form:
+We have seen that $p_k$ is of degree $m$ only when $k \in \{l^{(u)}\}_{u=0}^{w-1}$.
+Hence there exist sets of coefficients $\{\overline{X}_j,\overline{Y}_j,\overline{Z}_j\}_{j=0}^{m-1}$, computed uniquely from the statement and extracted values, such that Equations \ref{eqn:x}, \ref{eqn:y}, and \ref{eqn:z} are of the following form:
 \begin{eqnarray*}
-\xi^m M_l + \sumj \xi^j\overline{X}_j &=& zG \\
-\xi^m U + \sumj \xi^j\overline{Y}_j &=& zJ \\
+\xi^m \sumu \mu_{l^{(u)}}M_{l^{(u)}} + \sumj \xi^j\overline{X}_j &=& \left( \sumu z^{(u)}_R \right)G \\
+\xi^m \sumu \mu_{l^{(u)}}U + \sumj \xi^j\overline{Y}_j &=& \sumu z^{(u)}_RJ^{(u)} \\
+\xi^m \sumu P_{l^{(u)}} + \sumj \xi^j\overline{Z}_j - \xi^m \sum_{j=0}^{T-1} Q_j &=& z_SG
 \end{eqnarray*}
@@
 
-For each of the previous two equations, we can therefore build a linear combination over $e$.
-For the first:
-$$M_l = \sum_{e=0}^m \theta_e\xi_e^m M_l + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{X}_j \right) = \left( \sum_{e=0}^m \theta_e z_e \right) G$$
-Hence we extract $r \equiv \sum_{e=0}^m \theta_e z_e$.
-For the second:
-$$U = \sum_{e=0}^m \theta_e\xi_e^m U + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{X}_j \right) = \left( \sum_{e=0}^m \theta_e z_e \right) J$$
-This implies that $rJ = U$, as required.
-Hence the protocol is $(m+1)$-special sound, which completes the proof.
+For each of the previous three equations, we can therefore build a linear combination over $e$. For the first:
+$$\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sum_{e=0}^m \theta_e\xi_e^m \left( \sumu \mu_{l^{(u)}} M_{l^{(u)}} \right) + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{X}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) G$$
+We therefore can define extractions for each $r^{(u)}$:
+$$r^{(u)} \equiv \frac{1}{\mu_{l^{(u)}}} \sum_{e=0}^m \theta_e {}_ez^{(u)}_R$$
+Observe that the same witnesses appear in the second:
+$$\sumu \mu_{l^{(u)}} U = \sum_{e=0}^m \theta_e\xi_e^m \left( \sumu \mu_{l^{(u)}} U \right) + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{Y}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) J^{(u)}$$
+This means the requirements on each $r^{(u)}$ are satisfied. The third equation proceeds similarly.
+$$\sumu P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = \sum_{e=0}^m \theta_e\xi_e^m \left( \sumu P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j \right) + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{Z}_j \right) = \left( \sum_{e=0}^m \theta_e {}_ez_S  \right)G$$
+Hence we have $y \equiv \sum_{e=0}^m \theta_e {}_ez_S$.
 \end{proof}
 
-\section{Security: linkable ring signature}
-Informally, a linkable ring signature is a construction permitting signatures on messages using a signer-selected anonymity set (called a \textit{ring}) of possible signers.
-A valid signature convinces a verifier that the signer knows (at least) one of the private keys to a ring member.
-The construction is linkable if it is possible to determine whether two signatures were generated using the same private key, regardless of the ring members used.
+\section{Transaction model}
+We now describe how to apply the sigma protocol for $\mathcal{R}$ in a confidential transaction model.
+In such a model, a transaction consumes so-called \textit{outputs} generated in previous transactions, and produces new outputs for use in later transactions.
+Notably, in a \textit{confidential} transaction model, we wish to introduce ambiguity as to which transaction inputs are being consumed, as well as the corresponding values represented by them.
 
-We use the security definitions in \cite{groth} as a starting point, directly adopting definitions for correctness and unforgeability that also appear in more recent work like \cite{backes}.
-However, we modify the definition of anonymity to account for linking tags, such that the adversary is required to differentiate between at least two possible honest signers that the adversary has not corrupted.
-To account for the linking properties desired in our construction, we use the clever linkability definition from \cite{backes}, which uses a set-theoretic approach.
-We use a straightforward definition for non-frameability, where the adversary produces a target signature on an honest key after receiving signing and corruption oracle access, and must then produce a new signature that links.
+Outputs are constructed as Pedersen commitments to zero, such that an output public key is of the form $M \equiv rG$ with signing key $r$.
+We do not consider here the method by which output keys are generated, but assume this is offloaded to another part of the transaction model.
+Each output comes equipped with a value commitment $P \equiv sG + aH$, where $a$ is the amount and $s$ a blinding factor.
 
-More formally, a \textit{linkable ring signature} (LRS) construction is a set of algorithms \text{KeyGen}, \text{Sign}, \text{Verify}, and \text{Link} satisfying certain properties.
-A set of public parameters is assumed to be available to each algorithm.
-\begin{itemize}
-\item $\text{KeyGen}(r) \to (x,X)$: Generates a secret key $x$ and corresponding public key $X$, optionally using randomness $r$; if not specified, the secret key is sampled uniformly at random.
-\item $\text{Sign}(x,M,R) \to \sigma$: Generates a signature $\sigma$ on a message $M \in \{0,1\}^*$ with respect to the ring $R = \{X_1,\ldots,X_n\}$, provided that $x$ is a secret key corresponding to some $X_i \in R$ generated by $\text{KeyGen}$.
-\item $\text{Verify}(\sigma,M,R) \to \{0,1\}$: Verifies a signature $\sigma$ on a message $M$ with respect to the ring $R$.
-Outputs $0$ is the signature is rejected, and $1$ if accepted.
-\item $\text{Link}(\sigma,\sigma') \to \{0,1\}$: Determines if signatures $\sigma$ and $\sigma'$ were signed using the same private key.
-Outputs $0$ if the signatures were signed using different private keys, and $1$ if they were signed using the same private key.
-\end{itemize}
+A user of the protocol forms an anonymity set $\{M_i\}_{i=0}^{N-1}$ of outputs from previous transactions.
+Of these, suppose that the set $\{l^{(u)}\}_{u=0}^{w-1}$ represents the indices of the $w$ outputs for which the user wishes to sign; that is, the user knows $\{r^{(u)}\}_{u=0}^{w-1}$ such that $r^{(u)}G = M_{l^{(u)}}$ for all $0 \leq u < w$.
+To help ensure ambiguity of the signing indices, assume the user has shuffled the anonymity set.
+Each element of the anonymity set has a corresponding value commitment $\{P_i \equiv s_iG + a_iH\}_{i=0}^{N-1}$.
 
-We require that an LRS have the properties of correctness, anonymity, unforgeability, linkability, and non-frameability.
+Further, the user generates a set of new outputs produced by the transaction, with corresponding value commitments of the form $\{Q_j \equiv t_jG + b_jH\}_{j=0}^{T-1}$.
+Because the transaction value must balance, the following must hold: $$\sum_{u=0}^{w-1} a_{l^{(u)}} = \sum_{j=0}^{T-1} b_j$$
+Note that there is no anonymity set for outputs generated by the transaction.
 
-Correctness requires that a signature generated honestly will always verify.
-\begin{definition}[Correctness]
-Consider this game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item The challenger runs $\text{KeyGen} \to (x,X)$ and supplies the keys to $\A$.
-\item The adversary $\A$ chooses a ring such that $X \in R$ and a message $M \in \{0,1\}^*$, and sends them to the challenger.
-\item The challenger signs the message with $\text{Sign}(x,M,R) \to \sigma$.
-\end{itemize}
-If $\text{Pr}[ \text{Verify}(\sigma,M,R) = 1 ] = 1$, we say that the LRS is \textit{perfectly correct}.
-\end{definition}
-Note that we do not require any ring members (except for $X$) to have been generated by $\text{KeyGen}$.
-However, distributed applications may in practice place additional restrictions on public keys used in anonymity sets.
-This allows for the possibility that $\A$ maliciously chooses ring members.
+These terms are used to form a statement using the relation $\mathcal{R}$.
+The user generates a proof showing the validity of this statement with the corresponding secret values as a witness set; the proof demonstrates knowledge of the signing keys $\{r^{(u)}\}_{u=0}^{w-1}$, and the witness $y$ formed by the commitment differences demonstrates that the input and output values balance.
+Provided the commitment scheme used for value representation is (at least computationally) binding, the user cannot produce such a value $y$ unless the values balance correctly; in our case, Pedersen commitments satisfy this requirement.
 
-Unforgeability requires that an adversary who does not control the private key to a ring member cannot generate a valid signature on any message using that ring.
-\begin{definition}[Unforgeability]
-Consider this game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item The adversary $\A$ is granted access to a public-key oracle $\text{GenOracle}$ that (on the $i^\text{th}$ invocation) runs $\text{KeyGen} \to (x_i,X_i)$ and returns $X_i$ to $\A$.
-\item The adversary $\A$ is granted access to a corruption oracle $\text{CorruptOracle}(i)$ that returns $x_i$ if it corresponds to a query to $\text{GenOracle}$.
-\item The adversary $\A$ is granted access to a signing oracle $\text{SignOracle}(X,M,R)$ that runs $\text{Sign}(x,M,R) \to \sigma$ and returns $\sigma$ to $\A$, provided that $X$ corresponds to a query to $\text{GenOracle}$ and $X \in R$.
-\item Then, $\A$ outputs $(\sigma,M,R)$ such that $\text{SignOracle}$ was not queried with $(-,M,R)$, all keys in $R$ were generated by queries to $\text{GenOracle}$, and no key in $R$ was corrupted by $\text{CorruptOracle}$.
-\end{itemize}
-If $\text{Pr}[ \text{Verify}(\sigma,M,R) = 1 ] \approx 0$, we say that the LRS is $\textit{unforgeable with respect to insider corruption}$.
-\end{definition}
+We call the elements of the set $\{J^{(u)}\}_{u=0}^{w-1}$ the \textit{linking tags} for the transaction.
+Similar to their use in linkable ring signatures, they are used by the verifier to detect attempts to sign with a secret key multiple times, either within the same transaction or between multiple transactions.
+The construction $J^{(u)} = (r^{(u)})^{-1}U$ is an injective one-way verifiable random function \cite{dodis} using the secret key $r^{(u)}$; if the verifier sees the same linking tag used elsewhere, it knows that the (unknown) secret key was used again.
+In our confidential transaction model, this corresponds to an attempt to double-spend funds that would be rejected by the verifier.
 
-Anonymity requires that as long as a ring contains at least two members that have not been corrupted, an adversary can do no better than guessing at determining the signer of an honest signature.
-\begin{definition}[Anonymity]
-Consider this game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item The adversary $\A$ is granted access to the public-key oracle $\text{GenOracle}$ and the corruption oracle $\text{CorruptOracle}$.
-\item The adversary $\A$ chooses a message $M \in \{0,1\}^*$, a ring $R$, and indices $i_0$ and $i_1$, and sends them to the challenger.
-We require that $X_{i_0},X_{i_1} \in R$ such that both keys were generated by queries to $\text{GenOracle}$, and neither key was queried to $\text{CorruptOracle}$.
-\item The challenger selects a uniformly random bit $b \in \{0,1\}$, generates the signature $\text{Sign}(x_{i_b},M,R) \to \sigma$, and sends it to $\A$.
-\item The adversary $\A$ chooses a bit $b' \in \{0,1\}$.
-\end{itemize}
-If $\text{Pr}[ b' = b ] \approx 1/2$ and $\A$ did not make any corruption queries after receiving the challenge bit, we say that the LRS is \textit{anonymous}.
-\end{definition}
-We observe that this definition permits the adversary to have corrupted or maliciously generated all but two keys in the ring.
-Some definitions allow the adversary to corrupt more keys, but we will see that this is inconsistent with our linkability construction, where an adversary in control of a ring member's private key can trivially determine if it was the signer by examining the linking tag associated to a signature.
-
-Linkability requires that an adversary be unable to produce $k+1$ non-linked signatures on a combined anonymity set of $k$ public keys.
-\begin{definition}[Linkability]
-Consider the following game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item For $i \in [0,k-1]$, the adversary $\A$ produces a public key $X_i$, message $M_i$, ring $R_i$, and signature $\sigma_i$.
-\item The adversary $\A$ produces another message M, ring R, and signature $\sigma$.
-\item All tuples $(X_i,M_i,R_i,\sigma_i)$ and $(M,R,\sigma)$ are sent to the challenger.
-\item The challenger checks the following:
-\begin{itemize}
-\item $\left| V \right| = k$, where $V \equiv \bigcup_{i=0}^{k-1} R_i$.
-\item Each $X_i \in V$.
-\item Each $R_i \subset V$.
-\item $\text{Verify}(\sigma_i,M_i,R_i) = 1$ for all $i$.
-\item $\text{Verify}(\sigma,M,R) = 1$.
-\item For all $i \neq j$, we have $\text{Link}(\sigma_i,\sigma_j) = \text{Link}(\sigma_i,\sigma) = 0$.
-\end{itemize}
-\item If all checks pass, $\A$ wins.
-\end{itemize}
-If $\A$ wins with only negligible probability for all $k$, we say the LRS is \textit{linkable}.
-\end{definition}
-
-Non-frameability requires that an adversary be unable to generate a signature that links with an honest signature.
-\begin{definition}[Non-frameability]
-Consider also the following game between a challenger and a probabilistic polynomial-time adversary $\A$:
-\begin{itemize}
-\item The adversary $\A$ is granted access to the public-key oracle $\text{GenOracle}$.
-\item The adversary $\A$ is granted access to the corruption oracle $\text{CorruptOracle}$.
-\item The adversary $\A$ is granted access to the signing oracle $\text{SignOracle}$.
-\item The adversary $\A$ chooses a public key $X$ that was generated by a query to $\text{GenOracle}$, but was not presented as a query to $\text{CorruptOracle}$.
-It selects a message $M \in \{0,1\}^*$ and ring $R$ such that $X \in R$.
-It queries $\text{SignOracle}(X,M,R) \to \sigma$.
-\item The adversary $\A$ then produces a tuple $(M',R',\sigma')$ and sends $(M',R',\sigma')$ to the challenger, along with $(X,M,R,\sigma)$.
-\item If $\text{Verify}(\sigma',M',R') = 0$ or if $\sigma'$ was produced using a query to $\text{SignOracle}$, the challenger aborts.
-\end{itemize}
-If $\text{Pr}[ \text{Link}(\sigma,\sigma') = 1 \approx 0$, we say that the LRS is \textit{non-frameable}.
-\end{definition}
-
-\section{Application: linkable ring signature}
-The constructions in \cite{groth,bootle} describe how to use a similar sigma protocol to construct a simple ring signature scheme.
-Using our modifications, we can easily extend this to account for linkability and non-frameability.
-We briefly show how to do so.
-
-\begin{figure}[htbp]
-\centering
-\fbox{\begin{minipage}{0.95\textwidth}
-    $\underline{\text{KeyGen}(r):}$
-    \begin{itemize}
-        \item If not specified, select $r \in \F$ uniformly at random.
-        \item Compute $R = rG$.
-        \item Return $(x,X) = (r,R)$.
-    \end{itemize}
-
-    $\underline{\text{Sign}(x,M,R):}$
-    \begin{itemize}
-        \item Let $R = \{X_0,\ldots,X_{N-1}\}$ such that $X_l = x_lG$.
-        \item Compute $J \equiv x_l^{-1}U$.
-        \item Run $\mathcal{P}_{\text{link}}(R,J;(l,x_l)) \to a$ (up to the verifier challenge).
-        \item Set $\xi \equiv \hs(M,R,a)$.
-        \item Run $\mathcal{P}_{\text{link}}(\xi) \to z$ (after the verifier challenge).
-        \item Return $\sigma = (a,z,J)$.
-    \end{itemize}
-
-    $\underline{\text{Verify}(\sigma,M,R):}$
-    \begin{itemize}
-        \item Let $R = \{X_0,\ldots,X_{N-1}\}$ such that $X_l - x_lG$.
-        \item Let $\sigma = (a,z,J)$.
-        \item Set $\xi \equiv \hs (M,R,a)$.
-        \item Return $\mathcal{V}_{\text{link}}(R,J,a,z)$.
-    \end{itemize}
-
-    $\underline{\text{Link}(\sigma,\sigma'):}$
-    \begin{itemize}
-        \item We implicitly assume that $\sigma$ and $\sigma'$ have been previously verified.
-        \item Let $\sigma = (a,z,J)$ and $\sigma' = (a',z',J')$.
-        \item If $J = J'$, return $1$.
-        Otherwise, return $0$.
-    \end{itemize}
-\end{minipage}}
-    \caption{Linkable ring signature using $\mathcal{R}_{\text{link}}$}
-    \label{fig:lrs}
-\end{figure}
-
-\begin{theorem}
-The protocol in Figure \ref{fig:lrs} is a linkable ring signature construction.
-\end{theorem}
-
-\begin{proof}
-Perfect correctness follows immediately from the perfect completeness of the proving system for $\mathcal{R}_{link}$.
-
-Similarly, anonymity follows since the proving system is special honest-verifier zero knowledge, and therefore witness indistinguishable \cite{cramer}.
-Any adversarial advantage in breaking anonymity must therefore arise from distinguishing either input commitments or linking tags in signatures.
-Since honestly-generated input Pedersen commitments are perfectly hiding, they are indistinguishable from elements of $\G$ selected uniformly at random; we assume by definition that at least two such commitments are present in such a signature.
-Further, honestly-generated linking tags are generated from a one-way pseudorandom function, and therefore in the random oracle model are independently uniformly distributed from other proof elements and input commitments.
-
-The proof for unforgeability in \cite{groth} relies on the (special) soundness of the underlying sigma protocol; it applies directly to our modification for $\mathcal{R}_{link}$, and is not repeated here.
-
-To show linkability, observe first that $\text{Link}$ simply compares linking tags, so two signatures link if and only if they share a common linking tag.
-Suppose an adversary can win the linkability game with non-negligible probability for some $k > 1$.
-Since all provided signatures verify, soundness implies extraction of a witness $x_i$ from signature $\sigma_i$ for all $i$, and of a witness $x$ from $\sigma$.
-Note that all $\{x_i\}$ and $x$ are distinct.
-If $x_i = x_j$ for $i \neq j$, then the corresponding linking tags $J_i$ and $J_j$ are such that $x_iJ_i = x_jJ_j = U$; then $J_i = J_j$, which contradicts $\text{Link}(\sigma_i,\sigma_j) = 0$.
-The same reasoning holds to show $x$ is similarly distinct.
-Soundness also implies that for all $i$, there exists $X_i \in R_i$ such that $x_iG = X_i$; similarly, there exists $X \in R$ such that $xG = X$.
-By assumption we have $$\{X_0,\ldots,X_{k-1},X\} \subset \left( \bigcup_{i=0}^{k-1} R_i \right) \cup R \subset V.$$
-However, note that $\left| \{X_0,\ldots,X_{k-1},X\} \right| = k+1$, but that $\left| V \right| = k$, a contradiction.
-
-Finally, we show non-frameability and assume an adversary has a non-negligible advantage in breaking this property.
-Because we have $\text{Verify}(\sigma',M',R') = 1$, soundness implies extraction of a witness $x' \in \F$ such that $x'G \in R'$; we also have a witness $x$ such that $xG \in R$ from the known signature $\sigma$.
-Since $\text{Link}(\sigma,\sigma') = 1$, the corresponding linking tags $J$ and $J'$ are equal by definition; hence by soundness $xJ = x'J' = U$, giving $x = x'$.
-However, the adversary did not query $\text{CorruptOracle}$ with $X$, meaning it breaks the discrete logarithm problem non-negligibly.
-\end{proof}
-
-\section{Protocol: parallel linkable one-of-many commitment}
-In this section, we describe a modification of the sigma protocol for $\mathcal{R}_{\text{link}}$ that permits us to prove knowledge of multiple commitments in $d > 1$ separate sets at the same index position, while retaining the linking property in the first commitment set only.
-This forms a version of Triptych with the same functionality as the $d$-linkable ring signature construction in \cite{clsag}, although the precise security model is a bit different.
-We later show how to apply such a construction to a signer-ambiguous transaction protocol that can demonstrate balance preservation.
-
-We wish to produce a sigma protocol for the following relation, for some given vector dimension $d > 1$.
-$$\mathcal{R}_{\text{par}} = \left\{ \{M_{i,\alpha}\}_{i,\alpha=0}^{N-1,d-1} \subset \G^d, J \in G ; \left(l, \{r_\alpha\}_{\alpha=0}^{d-1}\right) : \{M_{l,\alpha} = r_\alpha G\}_{\alpha=0}^{d-1} \text{ and } U = r_0 J \right\}$$
-This requires only minor modifications to the protocol for $\mathcal{R}_{\text{link}}$, so we document only the modified proof elements constructed and verified in Figure \ref{fig:par}.
-All other proof elements are generated and verified identically.
-
-\begin{figure}[htbp]
-\centering
-\fbox{\begin{minipage}{0.95\textwidth}
-$\underline{\mathcal{P}_{\text{par}}\left(\{M_{i,\alpha}\},J;\left(l,\{r_\alpha\}\right)\right):}$
-\begin{itemize}
-\item Define $K_\alpha \equiv r_\alpha J$ for $\alpha \in (0,d)$.
-\item Define $\mu_\alpha \equiv \hs\left(\alpha,\{M_{i,\alpha}\},J,\{K_\alpha\}\right)$ for $\alpha \in (0,d)$.
-\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}\left(M_{k,0} + \sum_{\alpha=1}^{d-1} \mu_\alpha M_{k,\alpha}\right) + \rho_jG$$
-\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv \left(U + \sum_{\alpha=1}^{d-1} \mu_\alpha K_\alpha\right)\sumk p_{k,j} + \rho_jG$$
-\end{itemize}
-
-$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
-$\{K_\alpha\},\{X_j\},\{Y_j\}$ \\
-
-$\underline{\mathcal{V} \to \mathcal{P}:}$ \\
-$\xi \in \{0,1\}^*$ \\
-
-$\underline{\mathcal{P}(\xi):}$
-\begin{itemize}
-\item Define $z \equiv \left(r_0 + \sum_{\alpha=1}^{d-1} \mu_\alpha r_\alpha\right)\xi^m - \sumj \rho_j\xi^j$.
-\end{itemize}
-
-$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
-$z$ \\
-
-$\underline{\mathcal{V}_{\text{par}}(\{M_{i,\alpha}\},J):}$
-\begin{itemize}
-\item Define $\mu_\alpha \equiv \hs\left(\alpha,\{M_{i,\alpha}\},J,\{K_\alpha\}\right)$ for $\alpha \in (0,d)$.
-\item Accept if and only if:
-\begin{eqnarray*}
-\sumk \left(M_{k,0} + \sum_{\alpha=1}^{d-1} \mu_\alpha M_{k,\alpha}\right) \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG &=& 0 \\
-\left(U + \sum_{\alpha=1}^{d-1} \mu_\alpha K_\alpha\right)\sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ &=& 0
-\end{eqnarray*}
-\end{itemize}
-\end{minipage}}
-\caption{Sigma protocol (abbreviated) for $\mathcal{R}_{\text{par}}$}
-\label{fig:par}
-\end{figure}
-
-\begin{theorem}
-The protocol in Figure \ref{fig:par} is perfectly complete, special honest-verifier zero knowledge, and $(m+1)$-special sound.
-\end{theorem}
-
-\begin{proof}
-In the random oracle model, extraction of a witness of the form $r_0 + \sum_{\alpha} \mu_\alpha r_\alpha$ implies knowledge of all $\{r_\alpha\}$ such that $r_\alpha G = M_{l,\alpha}$, similarly to the key-aggregation arguments in \cite{musig}.
-The same extraction shows that $\left(r_0 + \sum_{\alpha} \mu_\alpha r_\alpha\right)J = U + \sum_{\alpha} \mu_\alpha K_\alpha$, which implies in particular that $r_0J = U$, as required.
-
-The rest of the proof follows with only trivial modifications from the proof for $\mathcal{R}_{\text{link}}$.
-\end{proof}
-
-\section{Application: signer-ambiguous transaction protocol}
-The parallel construction described in Figure \ref{fig:par} can be used with $d = 2$ in a signer-ambiguous transaction protocol.
-
-Suppose a user wishes to generate a transaction consuming $W$ previously-generated outputs and generating $T$ fresh outputs.
-The user shuffles the consumed outputs within a larger list of $N$ outputs $\{M_{k,0}\}_{k=0}^{N-1}$, such that there exist indices $\{l_u\}_{u=0}^{W-1}$ where each $M_{l_u,0} = r_u$ for some known private key $r_u$.
-Further, assume each $M_{l_u,0}$ comes equipped with an amount commitment of the form $M_{l_u,1} \equiv \com(a_u,s_u)$ for amount $a_u$ and mask $s_u$.
-(All other $M_{k,0}$ also come equipped with a corresponding $M_{k,1}$, but the structure of these points is not relevant here.)
-
-The user generates $W$ auxiliary commitments $P'_u \equiv \com(a_u,s'_u)$ to the same amounts, but with different masks $\{s'_u\}$ chosen uniformly at random from $\F$.
-Then, the user generates $W$ spend proofs, each using the following prover inputs for $u \in [0,W)$:
-$$\mathcal{P}_{par}(\{M_{i,\alpha}\},r_u^{-1}U;(l_u,\{r_u,s_u-s'_u\}))$$
-
-For $j \in [0,T)$, the user generates a fresh output of the form $Q_j \equiv \com(b_j,t_j)$ for amount $b_j$ and mask $t_j$.
-The masks are chosen such that for $j \in [1,T)$, we have $t_j$ chosen uniformly at random from $\F$.
-We then choose $$t_0 \equiv \sum_{u=0}^{W-1} s_u' -\sum_{j=1}^{T-1} t_j$$ and include all $\{P'_u\}$ auxiliary commitments in the transaction.
-
-To verify such a transaction, the verifier first performs verification on each spend proof to ensure it is valid.
-Then, the verifier ensures that $$\sum_{u=0}^{W-1} P'_u - \sum_{j=0}^{T-1} Q_j = 0$$ such that the transaction balances.
-This succeeds since the commitments sum to zero if and only if the difference of input and output amounts is zero, which holds since the Pedersen commitment construction is computationally binding.
+Since the sigma protocol is special honest-verifier zero knowledge, it is witness indistinguishable \cite{cramer}.
+Note, however, that an observer who sees an input anonymity set containing a commitment for which the observer knows the opening can trivially test linking tags using its own secret keys to determine if they were used in the proof.
+Therefore, witness indistinguishability is assumed to apply among input commitments for which an observer does not know a corresponding opening.
 
 \section{Efficiency}
-Triptych proofs scale logarithmically with the size of the input anonymity set; this is the best asymptotic scaling known for ring signatures that do not require a trusted setup process over non-pairing groups.
-Related protocols based on the inner-product compression method of \cite{bulletproofs} include Omniring \cite{omniring} and RingCT 3.0 \cite{omniring}.
-However, it is challenging to directly compare these protocols' efficiency.
-Omniring includes all transaction input signatures, output range proofs, and balance within a single proof structure; however, it is not possible to verify a batch of proofs more efficiently by combining common generators.
-While an early version of RingCT 3.0 used separate input, range, and balance proofs, the most recent version merges all input and balance proofs together but outsources the range proofs to an efficient construction like \cite{bulletproofs}; this comes at the cost of requiring that the number of inputs be a power of two or otherwise carefully padded (affecting verification time).
-Therefore, for the purpose of comparison we modify slightly the earlier version of RingCT 3.0 with a soundness fix applied from the updated version, ignoring the size and verification cost of non-proof elements.
-Another more direct comparison is to CLSAG, a linear-sized linkable ring signature construction \cite{clsag}.
+Observe that all group operations involved in verification occur in multiscalar multiplication operations that must evaluate to zero; methods such as those in \cite{straus,pippenger} provide efficient evaluation of these operations.
+Further, many group elements in these operations are globally-fixed generators that appear in all proofs.
+As a result, verification of many separate independent proofs may be batched similarly to the method described in \cite{bulletproofs} and elsewhere, where random weighting of verification equations is performed and common generators are used only once.
+The result is that a batch of independent proofs can be more efficiently verified using a single multiscalar multiplication operation, lowering the marginal cost per proof to verify.
 
-We now show size and verification comparisons of the parallel instantiation of Triptych with $d = 2$, the earlier (modified) version of RingCT 3.0, and $2$-CLSAG.
-For verification scaling, we also account for the use of batching in Triptych and RingCT 3.0, where generators common to multiple proofs are used only once in verification.
-Further, since verification in both of these constructions reduces to checking whether several multiscalar multiplications are zero, we may apply random weighting such that verifying a batch of multiple proofs reduces to a single multiscalar multiplication.
-The use of efficient multiscalar multiplication algorithms like \cite{straus,pippenger} means that an $n$-multiscalar multiplication evaluates as $O(n/\log n)$.
-This form of batching does not apply to CLSAG, where verification consists of a sequence of hash function evaluations.
+We follow the same notation as before: $N = 2^m$ is the size of the input anonymity set for varying $m > 1$, $w$ is the number of signing indices, and $T$ is the number of output commitments used in the balance check.
+Assuming that both elements of $\G$ and $\F$ occupy $32$ bytes of storage (as is the case for common elliptic curve groups using compressed point representations), we compare the size of proofs for RingCT 3.0 (two variants) \cite{rct3}, Triptych \cite{triptych}, and this work.
+Note that we make some assumptions in order to produce fair comparisons here.
+In Triptych and the original version of RingCT 3.0, certain commitment offsets are required as part of balance testing, which we consider, along with the multiple proofs needed in a transaction that wishes to sign for multiple inputs.
+However, we ignore input set representation (which depends on implementation), range proofs (which are required for all protocols and not part of the proving systems), and any auxiliary data that would otherwise appear as part of transactions.
+Table \ref{table:size} shows the results.
 
-Table \ref{table:size} compares proof/signature sizes and verification complexity for these constructions as a function of the anonymity set size $N$ and batch size $B$.
-Verification complexity is separated into the number of hash-to-$\F$ operations (denoted $\hs$), hash-to-$\G$ operations (denoted $\hp$), and $i$-multiscalar multiplication operations of size $k(i)$.
-Figure \ref{fig:size} examines size as a function of input anonymity set size, under the assumption that elements of both $\G$ and $\F$ occupy $32$ bytes of space.
-We note that although RingCT 3.0 proofs are slightly smaller for large $N$, Triptych proofs are smaller for $N < 512$, a limited but reasonable range given practical verification times.
-We also note that the application of Triptych in a complete transaction protocol is not directly compared to RingCT 3.0 here, as the use of non-proof/signature auxiliary data in such a protocol may differ based on particular implementations.
-
-\begin{table}[h]
+\begin{table}
 \centering
-\begin{tabular}{r|ll|l}
-& Size ($\G$) & Size ($\F$) & Verification (batch total) \\
+\begin{tabular}{|ll|}
 \hline
-CLSAG \cite{clsag} & $2$ & $N + 1$ & $B(N + 2) \hs + BN \hp + 2BN k(3)$ \\
-RingCT 3.0 \cite{rct3} & $2\lg(N) + 9$ & $9$ & $k(B[2N + 2\lg(N) + 9] + 2N + 5)$ \\
-Triptych (this work) & $2\lg(N) + 6$ & $\lg(N) + 3$ & $k(B[2N + 2\lg(N) + 2] + 2\lg(N) + 3)$
+Protocol & Size (proof elements) \\
+\hline
+RingCT 3.0 (original) \cite{rct3} & $w(2 \lg N + 18) + w + 2$ \\
+RingCT 3.0 (updated) \cite{rct3} & $2\lceil \lg(Nw) \rceil + w + 17$ \\
+Triptych \cite{triptych} & $w(3 \lg N + 8) + w$ \\
+Arcturus (this work) & $(w + 3)\lg N + w + 7$ \\
+\hline
 \end{tabular}
-\caption{Proof sizes and verification complexity, for anonymity set size $N$ and batch size $B$}
+\caption{Proof size (in group/field elements) with varying anonymity set size $N$ and signing keys $w$}
 \label{table:size}

### 2020-09-18 paper/iacr.tex
Minor paper updates

@@
 \end{multline*}
-Observe that if we assume that the dual-target discrete logarithm problem is hard in $\G$, extraction of a witness for $\mathcal{R}'$ implies knowledge of a corresponding witness for $\mathcal{R}$; this in turn provides the desired soundness.
+Observe that if we assume that the dual-target discrete logarithm problem is hard in $\G$ and $\hs$ is modeled as a random oracle, a witness for $\mathcal{R}'$ produced by the extractor must also be a witness for $\mathcal{R}$ using the same statement.
+This means that extraction of a witness for $\mathcal{R}'$ is sufficient to establish the desired soundness.
 
@@
 
-These terms are used to form a statement using the relation $\mathcal{R}$.
+These terms are used to form a statement tuple for the relation $\mathcal{R}$:
+$$\left( \{M_i\}_{i=0}^{N-1}, \{P_i\}_{i=0}^{N-1}, \{(r^{(u)})^{-1}U\}_{u=0}^{w-1}, \{Q_j\}_{j=0}^{T-1} \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, \sumu a_{l^{(u)}} - \sum_{j=0}^{T-1} b_j \right) \right)$$
 The user generates a proof showing the validity of this statement with the corresponding secret values as a witness set; the proof demonstrates knowledge of the signing keys $\{r^{(u)}\}_{u=0}^{w-1}$, and the witness $y$ formed by the commitment differences demonstrates that the input and output values balance.
@@
 Similar to their use in linkable ring signatures, they are used by the verifier to detect attempts to sign with a secret key multiple times, either within the same transaction or between multiple transactions.
-The construction $J^{(u)} = (r^{(u)})^{-1}U$ is an injective one-way verifiable random function \cite{dodis} using the secret key $r^{(u)}$; if the verifier sees the same linking tag used elsewhere, it knows that the (unknown) secret key was used again.
+The map $r^{(u)} \mapsto J^{(u)} \equiv (r^{(u)})^{-1}U$ is an injective one-way pseudorandom function \cite{dodis}; if the verifier sees the same linking tag used elsewhere, it knows that the (unknown) secret key was used again.
 In our confidential transaction model, this corresponds to an attempt to double-spend funds that would be rejected by the verifier.

### 2020-09-18 arcturus/arcturus.py
Efficient verifier

@@ -1,6 +1,7 @@
 # Proof-of-concept implementation of https://github.com/monero-project/research-lab/issues/56
 
 from dumb25519 import hash_to_point, random_scalar, Scalar, hash_to_scalar, G, random_point, Z
+from dumb25519 import ScalarVector, PointVector
 import dumb25519
 import random
 import transcript
@@ -196,13 +197,13 @@ def prove(M,P,Q,l,r,s,t,a,b,m,seed=None,aux1=Scalar(0),aux2=Scalar(0)):
     X = [dumb25519.Z for _ in range(m)]
     Y = [dumb25519.Z for _ in range(m)]
     Z = [dumb25519.Z for _ in range(m)]
-    mu = [hash_to_scalar(i,M,P,Q,J,A,B,C,D) for i in range(N)] # aggregation coefficients
+    mu = hash_to_scalar('Arcturus mu',M,P,Q,J,A,B,C,D)
     rho_R = [[random_scalar() for _ in range(m)] for _ in range(w)]
     rho_S = [[random_scalar() for _ in range(m)] for _ in range(w)]
     for j in range(m):
         for i in range(N):
-            X[j] += M[i]*p[0][i][j]*mu[i]
-            Y[j] += U*p[0][i][j]*mu[i]
+            X[j] += M[i]*p[0][i][j]*mu**i
+            Y[j] += U*p[0][i][j]*mu**i
             Z[j] += P[i]*p[0][i][j]
         for u in range(w):
             X[j] += rho_R[u][j]*G
@@ -246,7 +247,7 @@ def prove(M,P,Q,l,r,s,t,a,b,m,seed=None,aux1=Scalar(0),aux2=Scalar(0)):
     zR = []
     zS = Scalar(0)
     for u in range(w):
-        zR.append(mu[l[u]]*r[u]*x**m)
+        zR.append(mu**l[u]*r[u]*x**m)
         zS += s[u]*x**m
     for j in range(m):
         for u in range(w):
@@ -313,70 +314,105 @@ def verify(M,P,Q,proof,m):
     tr.update(Z)
     x = tr.challenge()
 
-    # Reconstruct matrix
-    for j in range(m):
-        for u in range(w):
-            f[u][j][0] = x
-            for i in range(1,n):
-                f[u][j][i] = proof.f[u][j][i-1]
-                f[u][j][0] -= f[u][j][i]
+    # Random weights for verification
[…]

### 2020-09-18 paper/iacr.tex
Updated aggregation coefficients for efficiency

@@
 \item $\A$ chooses and returns sets $\{G_i\}_{i=0}^{n-1},\{H_i\}_{i=0}^{n-1} \subset \G$ to the challenger.
-\item The challenger chooses a set $\{\mu_i\}_{i=0}^{n-1} \subset \F$ uniformly at random and sends it to $\A$.
+\item The challenger chooses a set $\{\mu^i\}_{i=0}^{n-1} \subset \F$ uniformly at random and sends it to $\A$.
 \item $\A$ chooses and returns a set $\{x_i\}_{i=0}^{n-1} \subset \F$ to the challenger.
@@
 \begin{itemize}
-\item $\sumi \mu_i \left( G_i - x_iG \right) = 0$
-\item $\sumi \mu_i \left( H - x_iH_i \right) = 0$
+\item $\sumi \mu^i \left( G_i - x_iG \right) = 0$
+\item $\sumi \mu^i \left( H - x_iH_i \right) = 0$
 \item There exists an index $0 \leq i < n$ such that either $x_iG \neq G_i$ or $x_iH_i \neq H$.
@@
 \item Select random $\left\{\rho_j\right\}_{j,u=0}^{m-1,w-1}, \left\{\overline{\rho}_j^{(u)}\right\}_{j,u=0}^{m-1,w-1} \subset \F$.
-\item Define aggregation coefficients $\{\mu_k\}_{k=0}^{N-1}$ using a $k$-indexed $\hs$ operation, containing all Fiat-Shamir transcript public parameters and proof elements.
-\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}\mu_kM_k + \sumu \rho_j^{(u)}G$$
-\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv U \sumk p_{k,j}\mu_k + \sumu \rho_j^{(u)}J^{(u)}$$
+\item Set $\mu \equiv \hs(\{M_k\},\{P_k\},\{J^{(u)}\})$ (to include all public parameters as well).
+\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}\mu^kM_k + \sumu \rho_j^{(u)}G$$
+\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv U \sumk p_{k,j}\mu^k + \sumu \rho_j^{(u)}J^{(u)}$$
 \item Define $\{Z_j\}_{j=0}^{m-1} \subset \G$ such that: $$Z_j \equiv \sumk p_{k,j}P_k + \sumu \overline{\rho}_j^{(u)}G$$
@@
 \item Define $z_A \equiv r_A + \xi r_B$ and $z_C \equiv \xi r_C + r_D$.
-\item Define $\left\{z_R^{(u)}\right\}_{u=0}^{w-1} \subset \F$ such that: $$z_R^{(u)} \equiv \mu_{l^{(u)}}r^{(u)}\xi^m - \sumj \rho_j^{(u)}\xi^j$$
+\item Define $\left\{z_R^{(u)}\right\}_{u=0}^{w-1} \subset \F$ such that: $$z_R^{(u)} \equiv \mu^{l^{(u)}}r^{(u)}\xi^m - \sumj \rho_j^{(u)}\xi^j$$
 \item Define: $$z_S \equiv \xi^m \left( \sumu s^{(u)} - \sum_{j=0}^{T-1} t_j \right) - \sumj \left( \xi^j \sumu \overline{\rho}_j^{(u)} \right)$$
@@
 \xi C + D &=& \com(f(\xi-f),z_C) \label{eqn:cd} \\
-\sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f_{j,k_j}^{(u)} \right) \right] - \sumj \xi^jX_j - \sumu z_R^{(u)}G &=& 0 \label{eqn:x} \\
-U \sumk \mu_k \left[ \sumu \left( \prod_{j=0}^{m-1} f_{j,k_j}^{(u)} \right) \right] - \sumj \xi^jY_j - \sumu z_R^{(u)}J^{(u)} &=& 0 \label{eqn:y} \\
+\sumk \mu^kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f_{j,k_j}^{(u)} \right) \right] - \sumj \xi^jX_j - \sumu z_R^{(u)}G &=& 0 \label{eqn:x} \\
+U \sumk \mu^k \left[ \sumu \left( \prod_{j=0}^{m-1} f_{j,k_j}^{(u)} \right) \right] - \sumj \xi^jY_j - \sumu z_R^{(u)}J^{(u)} &=& 0 \label{eqn:y} \\
 \sumk P_k \left[ \sumu \left( \prod_{j=0}^{m-1} f_{j,k_j}^{(u)} \right) \right] - \sumj \xi^jZ_j - \xi^m\sum_{j=0}^{T-1} Q_j - z_SG &=& 0 \label{eqn:z}
@@
 \begin{eqnarray*}
-&& \sumk \mu_kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj \xi^jX_j - \sumu z^{(u)}_RG \\
-&=& \sumk \mu_kM_k p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}\mu_kM_k + \sumu \rho^{(u)}_jG \right) - \sumu z^{(u)}_RG \\
-&=& \sumk \mu_kM_k \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \sumu \rho^{(u)}_jG - \sumu z^{(u)}_RG \\
-&=& \sumk \mu_kM_k \left[ \xi^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj \xi^j \sumu \rho^{(u)}_jG - \sumu\left[ \mu_{l^{(u)}}r^{(u)}\xi^m - \sumj \rho^{(u)}_j\xi^j \right]G \\
-&=& \xi^m\sumu \mu_{l^{(u)}}r^{(u)}G - \sumj \xi^j \sumu \rho^{(u)}_jG - \xi^m\sumu \mu_{l^{(u)}}r^{(u)}G + \sumj \xi^j \sumu \rho^{(u)}_jG \\
+&& \sumk \mu^kM_k \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj \xi^jX_j - \sumu z^{(u)}_RG \\
+&=& \sumk \mu^kM_k p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}\mu^kM_k + \sumu \rho^{(u)}_jG \right) - \sumu z^{(u)}_RG \\
+&=& \sumk \mu^kM_k \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \sumu \rho^{(u)}_jG - \sumu z^{(u)}_RG \\
+&=& \sumk \mu^kM_k \left[ \xi^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj \xi^j \sumu \rho^{(u)}_jG - \sumu\left[ \mu^{l^{(u)}}r^{(u)}\xi^m - \sumj \rho^{(u)}_j\xi^j \right]G \\
+&=& \xi^m\sumu \mu^{l^{(u)}}r^{(u)}G - \sumj \xi^j \sumu \rho^{(u)}_jG - \xi^m\sumu \mu^{l^{(u)}}r^{(u)}G + \sumj \xi^j \sumu \rho^{(u)}_jG \\
 &=& 0
@@
 \begin{eqnarray*}
-&& \sumk \mu_kU \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj \xi^jY_j - \sumu z^{(u)}_RJ^{(u)} \\
-&=& \sumk \mu_kU p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}\mu_kU + \sumu \rho^{(u)}_jJ^{(u)} \right) - \sumu z^{(u)}_RJ^{(u)} \\
-&=& \sumk \mu_kU \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \sumu \rho^{(u)}_jJ^{(u)} - \sumu z^{(u)}_RJ^{(u)} \\
-&=& \sumk \mu_kU \left[ \xi^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj \xi^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - \sumu\left[ \mu_{l^{(u)}}r^{(u)}\xi^m - \sumj \rho^{(u)}_j\xi^j \right](r^{(u)})^{-1}U \\
-&=& x^m\sumu \mu_{l^{(u)}}U - \sumj \xi^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - \xi^m\sumu \mu_{l^{(u)}}U + \sumj \xi^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U \\
+&& \sumk \mu^kU \left[ \sumu \left( \prod_{j=0}^{m-1} f^{(u)}_{j,k_j} \right) \right] - \sumj \xi^jY_j - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu^kU p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}\mu^kU + \sumu \rho^{(u)}_jJ^{(u)} \right) - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu^kU \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \sumu \rho^{(u)}_jJ^{(u)} - \sumu z^{(u)}_RJ^{(u)} \\
+&=& \sumk \mu^kU \left[ \xi^m \sumu \delta\left( l^{(u)},k \right) \right] - \sumj \xi^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - \sumu\left[ \mu^{l^{(u)}}r^{(u)}\xi^m - \sumj \rho^{(u)}_j\xi^j \right](r^{(u)})^{-1}U \\
+&=& x^m\sumu \mu^{l^{(u)}}U - \sumj \xi^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U - \xi^m\sumu \mu^{l^{(u)}}U + \sumj \xi^j \sumu \rho^{(u)}_j(r^{(u)})^{-1}U \\
 &=& 0
@@
 To show this, we construct an extractor that, when given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness for the statement.
-In particular, we produce a modified witness for the following relation that is based on the information presented in the prover algorithm, where we define aggregation coefficients $\mu_k$ as before:
+In particular, we produce a modified witness for the following relation that is based on the information presented in the prover algorithm, where we define $\mu$ as before:
 \begin{multline*}
 \mathcal{R}' \equiv \Bigg\{ \{M_k\}_{k=0}^{N-1},\{P_k\}_{k=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \\
-\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sumu \mu_{l^{(u)}} r^{(u)}G \text{ and } \sumu \mu_{l^{(u)}} r^{(u)}J^{(u)} = \sumu \mu_{l^{(u)}} U \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \Bigg\}
+\sumu \mu^{l^{(u)}} M_{l^{(u)}} = \sumu \mu^{l^{(u)}} r^{(u)}G \text{ and } \sumu \mu^{l^{(u)}} r^{(u)}J^{(u)} = \sumu \mu^{l^{(u)}} U \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \Bigg\}
 \end{multline*}
@@
 \begin{eqnarray*}
-\xi^m \sumu \mu_{l^{(u)}}M_{l^{(u)}} + \sumj \xi^j\overline{X}_j &=& \left( \sumu z^{(u)}_R \right)G \\
-\xi^m \sumu \mu_{l^{(u)}}U + \sumj \xi^j\overline{Y}_j &=& \sumu z^{(u)}_RJ^{(u)} \\
+\xi^m \sumu \mu^{l^{(u)}}M_{l^{(u)}} + \sumj \xi^j\overline{X}_j &=& \left( \sumu z^{(u)}_R \right)G \\
+\xi^m \sumu \mu^{l^{(u)}}U + \sumj \xi^j\overline{Y}_j &=& \sumu z^{(u)}_RJ^{(u)} \\
 \xi^m \sumu P_{l^{(u)}} + \sumj \xi^j\overline{Z}_j - \xi^m \sum_{j=0}^{T-1} Q_j &=& z_SG
@@
 For each of the previous three equations, we can therefore build a linear combination over $e$. For the first:
-$$\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sum_{e=0}^m \theta_e\xi_e^m \left( \sumu \mu_{l^{(u)}} M_{l^{(u)}} \right) + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{X}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) G$$
+$$\sumu \mu^{l^{(u)}} M_{l^{(u)}} = \sum_{e=0}^m \theta_e\xi_e^m \left( \sumu \mu^{l^{(u)}} M_{l^{(u)}} \right) + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{X}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) G$$
 We therefore can define extractions for each $r^{(u)}$:
-$$r^{(u)} \equiv \frac{1}{\mu_{l^{(u)}}} \sum_{e=0}^m \theta_e {}_ez^{(u)}_R$$
+$$r^{(u)} \equiv \frac{1}{\mu^{l^{(u)}}} \sum_{e=0}^m \theta_e {}_ez^{(u)}_R$$
 Observe that the same witnesses appear in the second:
-$$\sumu \mu_{l^{(u)}} U = \sum_{e=0}^m \theta_e\xi_e^m \left( \sumu \mu_{l^{(u)}} U \right) + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{Y}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) J^{(u)}$$
+$$\sumu \mu^{l^{(u)}} U = \sum_{e=0}^m \theta_e\xi_e^m \left( \sumu \mu^{l^{(u)}} U \right) + \sum_{e=0}^m \theta_e \left( \sumj \xi_e^j \overline{Y}_j \right) = \sumu \left( \sum_{e=0}^m \theta_e {}_ez^{(u)}_R \right) J^{(u)}$$
 This means the requirements on each $r^{(u)}$ are satisfied. The third equation proceeds similarly.
